### 2020-07-11 Manuscript/ms.tex
新增论文版文件夹.

%! TEX root = ms.tex
%! TEX program = pdflatex
\documentclass[review]{elsarticle}
\usepackage{lineno,hyperref}
\usepackage{amsmath, amsthm}
\modulolinenumbers[5]
\bibliographystyle{elsarticle-num}

\begin{document}

\begin{frontmatter}

\title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
\author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Yihua Huang\corref{correspondingauthor}}
\cortext[correspondingauthor]{Corresponding author}
\ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, yhuang\}@nju.edu.cn}
\address{State Key Laboratory for Novel Software Technology, Department of Computer Science and Technology, Nanjing University, Nanjing 210023, China}

\begin{abstract}
    This is the abstract.
\end{abstract}

\begin{keyword}
    Keyword 1
\end{keyword}

\end{frontmatter}

\linenumbers

\input{sec1-introduction.tex}
\input{sec2-review-of-graph-neural-network.tex}
\input{sec3-experiment-design.tex}
\input{sec4-experiments.tex}
\input{sec5-insights.tex}
\input{sec6-related-work.tex}
\input{sec7-conclusion.tex}

\section*{Acknowledgment}

\bibliography{gnnref.bib}

\end{document}

### 2020-07-11 Manuscript/sec1-introduction.tex

\section{Introduction}

This is a survey \cite{zhou2018_gnn_review}.

### 2020-07-11 Manuscript/sec2-review-of-graph-neural-network.tex

\section{Review of Graph Neural Networks}

In this section, we introduce the concepts related to the graph neural network and breifly survey typical graph neural networks.
We denote a simple graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
Let $n=|\mathcal{V}|$ and $m=|\mathcal{E}|$ as the number of vertices/edges. 
We use $v_i$ $(0 \leq i < n)$ to denote a vertex and $e_{i,j}=(v_i, v_j)$ to denote the edge pointing from $v_i$ to $v_j$.
The adjacency set of $v_i$ is $\mathcal{N}(v_i)=\{v|(v_i, v) \in \mathcal{E}\}$.
We denote a \emph{vector} with a bold lower case letter like $\boldsymbol{x}$ and a \emph{matri}x with a bold upper case letter like $\boldsymbol{X}$.

\subsection{General Structure of Graph Neural Networks}

As illustracted in \figurename~\ref{fig:general_structure_of_gnn}, a typical GNN can be decomposed into three parts \cite{comprehensive-survey-wu-2020}: an input layer + several GNN layers + a prediction layer.

A GNN receives a graph $\mathcal{G}$ as the input.
Every vertex $v_i$ in $\mathcal{G}$ is attached with a feature vector $\boldsymbol{x}_i$ to describe the properties of the vertex.
The input layer of the GNN receives the feature vectors from all vertices and passes them to GNN layers.
A GNN layer consists of $n$ GNN units with each GNN unit corresponding to a vertex.
A GNN unit $v_i$ receives feature vectors from the GNN/input units of the previous layer that are adjacent to $v_i$ in $\mathcal{G}$.
For example, in \figurename~\ref{fig:general_structure_of_gnn}, 
A GNN outputs an embedding vector $\boldsymbol{o_i}$ for every vertex in $G$.
The GNN assumes that every vertex $v_i$ in $G$ is attached with a feature vector $\boldsymbol{x}_i$ in the input.
GNNs assume that every vertex in the feature vectors attached to every vertex of the 
The input layer receives feature vectors of different vertices.

\begin{figure}
	\centering
	\includegraphics[width=0.95\columnwidth]{figs/illustration/GNN_common_architecture.png}
	\caption{Structure of a typical graph neural network. (a) Demo GNN; (b) GNN unit; (c) Demo graph. The target application is the node classification. The demo GNN has two GNN layers.}
	\label{fig:general_structure_of_gnn}
\end{figure}

### 2020-07-11 main_full.py
更新, for exp_sampling_memory_usage实验

@@ -1,0 +1,194 @@
+# for batch full experiment
+import torch
+import torch.nn.functional as F
+import numpy as np
+import argparse
+import time
+import sys
+import json
+import os.path as osp
+
+from gaan.models import GaAN
+from ggnn.models import GGNN
+from gat.models import GAT
+from gcn.models import GCN
+from utils import get_dataset, get_split_by_file, nvtx_push, nvtx_pop, log_memory, small_datasets
+
+parser = argparse.ArgumentParser()
+parser.add_argument('--dataset', type=str, default='cora', help="dataset: [cora, flickr, com-amazon, reddit, com-lj,"
+                                                                    "amazon-computers, amazon-photo, coauthor-physics, pubmed]")
+
+parser.add_argument('--model', type=str, default='gcn', help="gnn models: [gcn, ggnn, gat, gaan]")
+parser.add_argument('--epochs', type=int, default=50, help="epochs for training")
+parser.add_argument('--layers', type=int, default=2, help="layers for hidden layer")
+parser.add_argument('--hidden_dims', type=int, default=64, help="hidden layer output dims")
+parser.add_argument('--heads', type=int, default=8, help="gat or gaan model: heads")
+parser.add_argument('--head_dims', type=int, default=8, help="gat model: head dims") # head_dims * heads = hidden_dims
+parser.add_argument('--d_v', type=int, default=8, help="gaan model: vertex's dim") # d_v * heads = hidden_dims?
+parser.add_argument('--d_a', type=int, default=8, help="gaan model: each vertex's dim in edge attention") # d_a = head_dims
+parser.add_argument('--d_m', type=int, default=64, help="gaan model: gate: max aggregator's dim, default=64")
+
+parser.add_argument('--x_sparse', action='store_true', default=False, help="whether to use data.x sparse version")
+parser.add_argument('--seed', type=int, default=1, help="random seed")
+parser.add_argument('--cpu', action='store_true', default=False, help='use cpu, not use gpu')
+parser.add_argument('--device', type=str, default='cuda:0', help='[cpu, cuda:id]')
+parser.add_argument('--lr', type=float, default=0.01, help="adam's learning rate")
+parser.add_argument('--weight_decay', type=float, default=0.0005, help="adam's weight decay")
[…]

### 2020-07-11 main_sampling.py

@@ -101,6 +101,8 @@ elif args.mode == 'graphsage':
                                num_workers=args.num_workers) # inductive learning
 loader_time = time.time() - loader_time
 
+#t1 = data.edge_index.numpy()
+#np.save("amp_graph.npy", t1)
 
 # 3. set model
 if args.model == 'gcn':
@@ -145,10 +147,9 @@ def train(epoch):
     total_nodes = int(data.train_mask.sum())
 
     total_loss = 0
-    
-    sampling_time = to_time = train_time = 0.0
 
-    all_nodes, all_edges = 0, 0
+    sampling_time, to_time, train_time = 0.0, 0.0, 0.0
+
     train_iter = iter(train_loader)
     cnt = 0
     while True:
@@ -166,8 +167,8 @@ def train(epoch):
                 t2 = time.time()
                 to_time += t2 - t1
                 optimizer.zero_grad()
-                nodes, edges = batch.x.shape[0], batch.edge_index.shape[1]
-                print(f"nodes: {nodes}, edges: {edges}")
+                #nodes, edges = batch.x.shape[0], batch.edge_index.shape[1]
+                #print(f"nodes: {nodes}, edges: {edges}")
                 out = model(batch.x, batch.edge_index)
                 if args.dataset in ['yelp', 'amazon']:
                     loss = torch.nn.BCEWithLogitsLoss()(out[batch.train_mask, :], batch.y[batch.train_mask, :])
@@ -177,8 +178,8 @@ def train(epoch):
             elif args.mode == 'graphsage':
                 batch_size, n_id, adjs = batch
                 adjs = [adj.to(device) for adj in adjs] # 这里等于成熟
-                nodes, edges = adjs[0][2][0], adjs[0][0].shape[1]
-                print(f"nodes: {nodes}, edges: {edges}")
+                #print(f"nodes: {nodes}, edges: {edges}")
+                #print(adjs[0][2], adjs[1][2])
                 x = data.x[n_id].to(device)
                 if args.dataset in ['yelp', 'amazon']:
                     y = data.y[n_id[:batch_size], :].to(device)
@@ -198,14 +199,13 @@ def train(epoch):
             nvtx_push(gpu, "backward")
             loss.backward()
             optimizer.step()
+            train_times += time.time() - t2
             nvtx_pop(gpu)
             
-            train_time += time.time() - t2
             log_memory(flag, device, 'backward_end')
             total_loss += loss.item() * batch_size            
[…]

### 2020-07-11 pics_degrees_dirtribution.py

@@ -1,0 +1,64 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import sys
+plt.style.use("ggplot")
+plt.rcParams['font.size'] = 12
+
+graph_path = "amp_graph.npy"
+cluster_path = "amp_cluster.npy"
+graphsage_path = "amp_graphsage.npy"
+
+paths = [graph_path, cluster_path, graphsage_path]
+names = ['Original Graph', 'Cluster-GCN Sampling', 'GraphSAGE Sampling']
+
+def get_degrees_counts(path):
+    # 1. 统计出每个节点的度数
+    in_degrees = {}
+    out_degrees = {}
+
+    graph = np.load(path)
+    for i in graph[0, :]:
+        if i not in in_degrees.keys():
+            in_degrees[i] = 1
+        else:
+            in_degrees[i] += 1
+
+    for i in graph[1, :]:
+        if i not in out_degrees.keys():
+            out_degrees[i] = 1
+        else:
+            out_degrees[i] += 1
+
+    degrees_counts = {}
+    for i in in_degrees.values():
+        if i not in degrees_counts.keys():
+            degrees_counts[i] = 1
+        else:
+            degrees_counts[i] += 1
+
+    for i in out_degrees.values():
+        if i not in degrees_counts.keys():
+            degrees_counts[i] = 1
+        else:
+            degrees_counts[i] += 1
+    return degrees_counts 
+
+
+fig, ax = plt.subplots()
+ax.set_yscale('log')
+ax.set_xscale('log')
+ax.set_xlabel("Degrees")
+ax.set_ylabel("Numbers")
+
+markers='oD^'
+colors = 'rgb'
+for i, path in enumerate(paths):
+    degrees_counts = get_degrees_counts(path)
+    xs = list(degrees_counts.keys())
+    ys = [degrees_counts[d] for d in xs]
+    ax.scatter(xs, ys, color=colors[i], label=names[i], marker=markers[i])
+
+ax.legend()
+
+fig.savefig("exp_sampling_minibatch_degrees_distribution_amazon-photo.png")
+

### 2020-07-11 run_7_11.sh

@@ -1,0 +1,21 @@
+date
+cd /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/sampling_exp 
+echo "begin sampling"
+bash sampling_batch_time.sh >>batch_time.log 2>&1
+date
+bash sampling_batch_time_full.sh >>batch_time.log 2>&1
+date
+
+echo "begin exp degrees"
+cd /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/graph_degrees_exp
+bash exp_avg_degrees.sh >>exp_avg_degrees_7_11.log 2>&1
+date
+echo "begin memory degrees"
+bash memory_avg_degrees.sh >>memory_avg_degrees_7_11.log 2>&1
+date
+
+echo "begin memory edges"
+cd /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/graph_nodes_exp
+bash memory_edges.sh >>memory_edges_7_11.log 2>&1
+echo "end..."
+date

### 2020-07-11 scalablity_exp.py

@@ -82,16 +82,17 @@ def graph_scale_exp(seed=1):
             os.makedirs(raw_dir)
 
         print("get adj_full.npz...")
-        # 1. gen adj_full
-        row = []
-        col = []
+        edges_list = []
         for e in graph.Edges():
             r, c = e.GetSrcNId(), e.GetDstNId()
-            row.append(r)
-            col.append(c)
-            row.append(c)
-            col.append(r)
-        f = sp.csr_matrix(([1] * 2 * edges, (row, col)), shape=(nodes, nodes)) # directed -> undirected, edges*2
+            edges_list.append((r, c))
+            edges_list.append((c, r))
+        
+        edges_list = set(edges_list)
+        row = [i[0] for i in edges_list]
+        col = [i[1] for i in edges_list]
+        print(edges, len(row))
+        f = sp.csr_matrix(([1] * len(row), (row, col)), shape=(nodes, nodes)) # directed -> undirected, edges*2
         np.savez(raw_dir + "/adj_full", data=f.data, indptr=f.indptr, indices=f.indices, shape=f.shape)
         gen_graph(raw_dir, nodes, edges)
 
@@ -108,29 +109,29 @@ def graph_scale_exp(seed=1):
 
         print("get adj_full.npz...")
         # gen adj_full
-        row = []
-        col = []
+        edges_list = []
         for e in graph.Edges():
             r, c = e.GetSrcNId(), e.GetDstNId()
-            row.append(r)
-            col.append(c)
-            row.append(c)
-            col.append(r)
-        f = sp.csr_matrix(([1] * 2 * edges, (row, col)), shape=(nodes, nodes)) # directed -> undirected, edges*2
+            edges_list.append((r, c))
+            edges_list.append((c, r))
+        
+        edges_list = set(edges_list)
+        row = [i[0] for i in edges_list]
+        col = [i[1] for i in edges_list]
+        print(edges, len(row))
+        f = sp.csr_matrix(([1] * len(row), (row, col)), shape=(nodes, nodes)) # directed -> undirected, edges*2
         np.savez(raw_dir + "/adj_full", data=f.data, indptr=f.indptr, indices=f.indices, shape=f.shape)
         gen_graph(raw_dir, nodes, edges)
 
-def gen_nodes_exp(seed=1):
+def gen_real_degrees_exp(seed=1):
[…]

### 2020-07-12 Manuscript/sec2-review-of-graph-neural-network.tex

@@
 
-In this section, we introduce the concepts related to the graph neural network and breifly survey typical graph neural networks.
+In this section, we introduce the concepts related to the graph neural network (GNN, for short) and breifly survey typical graph neural networks.
 We denote a simple graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
@@
 
-As illustracted in \figurename~\ref{fig:general_structure_of_gnn}, a typical GNN can be decomposed into three parts \cite{comprehensive-survey-wu-2020}: an input layer + several GNN layers + a prediction layer.
-
-A GNN receives a graph $\mathcal{G}$ as the input.
-Every vertex $v_i$ in $\mathcal{G}$ is attached with a feature vector $\boldsymbol{x}_i$ to describe the properties of the vertex.
-The input layer of the GNN receives the feature vectors from all vertices and passes them to GNN layers.
-A GNN layer consists of $n$ GNN units with each GNN unit corresponding to a vertex.
-A GNN unit $v_i$ receives feature vectors from the GNN/input units of the previous layer that are adjacent to $v_i$ in $\mathcal{G}$.
-For example, in \figurename~\ref{fig:general_structure_of_gnn}, 
-A GNN outputs an embedding vector $\boldsymbol{o_i}$ for every vertex in $G$.
-The GNN assumes that every vertex $v_i$ in $G$ is attached with a feature vector $\boldsymbol{x}_i$ in the input.
-GNNs assume that every vertex in the feature vectors attached to every vertex of the 
-The input layer receives feature vectors of different vertices.
+As illustracted in \figurename~\ref{fig:general_structure_of_gnn}, a typical GNN can be decomposed into three parts: an input layer + several GNN layers + a prediction layer.
 
@@
 \end{figure}
+
+A GNN receives a graph $\mathcal{G}$ as the input.
+Every vertex $v_i$ in $\mathcal{G}$ is attached with a feature vector $\boldsymbol{x}_i$ to describe the properties of the vertex.
+The input layer of a GNN receives feature vectors from all vertices and passes them to GNN layers.
+
+A GNN layer consists of $n$ GNN units, where $n$ is the number of vertices in $\mathcal{G}$.
+Each GNN unit correspond to a vertex in $\mathcal{G}$.
+In the first GNN layer (Layer 0), the GNN unit of the vertex $v_i$ collects input feature vectors of the vertices $\boldsymbol{x}_j$ that are adjacent to $v_i$ in $\mathcal{G}$ (i.e., $j \in \mathcal{N}(v_i)$) from the input layer.
+In other words, the connection between the input layer and the first GNN layer is determined by the topology of $\mathcal{G}$.
+In the traditional neural networks, the neural units of neighboring layers are fully connected.
+In GNNs, two GNN units are connected only if they have an edge between them in $\mathcal{G}$, which is usually \emph{sparse}.
+After aggregating input feature vectors and applying non-linear transformation, the GNN unit outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
+
+In the next GNN layer (Layer 1), the GNN unit of $v_i$ collects the hidden feature vectors $\boldsymbol{h}^1_j$ of $v_i$'s neighbors (i.e., $j \in \mathcal{N}(v_i)$) from the \emph{previous} GNN layer.
+The connection between neighboring GNN layers are also determined by $\mathcal{E}$ of $\mathcal{G}$.
+Based on the collected hidden vectors, the GNN unit in Layer 1 outputs a new hidden feature vector $\boldsymbol{h}^2_i$ for $v_i$.
+A GNN allows to stack more GNN layers to support deeper graph analysis.
+%In \figurename~\ref{fig:general_structure_of_gnn}, we shows a GNN with two layers.
+
+Assume there are $L$ GNN layers.
+The last GNN layer (Layer $L-1$) outputs a hidden feature vector $\boldsymbol{h}^{L}_i$ for every vertex $v_i$.
+As an embedding vector, $\boldsymbol{h}^L_i$ encodoes the knowledge learned from the input layer and all the previous GNN layers.
+Finally, $\boldsymbol{h}^L_i$ is affected by $v_i$ and all the vertices in the $L$-hop neighborhood of $v_i$.
+Analyzing with deeper GNNs means analyzing each vertices with a wider scope.
+
+The hidden feature vectors $\boldsymbol{h}^L_i$ of the last GNN layer are fed to the prediction layer to generate the output of the whole GNN.
+The prediction layer is a standard nerual network.
+The structure of the prediction layer depends on the prediction task of the GNN.
+Take the node classification task as the example, as shown in \figurename~\ref{fig:general_structure_of_gnn}.
+The node classification predicts a label for every vertex in $\mathcal{G}$.
+In this case, the prediction layer can be a simple softmax layer with $\boldsymbol{h}^L_i$ as the input and a vector of probabilities as the output.
+If the prediction task is edge prediction, the hidden feature vectors of two vertices are concatenated and fed into a softmax layer.
+If we need to predict a label for the whole graph, a pooling (max/mean/...) layer is added to generate an embedding vector for the whole graph and the embedding vector is used to produce the final prediction.
+
+Supporting end-to-end training is a prominent advantage of GNN, compared with other graph-based machine learning methods.
+We can calculate the gradients of the loss function on the model parameters from the prediction layer directly.
+With the help of the back proporgation technique, the gradient is propogated from the prediction layer back to the previous GNN layers layer by layer.
+The model parameters are updated with a gradient descent optimizer like Adam.
+Except for the input feature vector, there is no need to conduct handworked feature extraction.
+In a fully parameterized way, the GNN automatically extracts an embedding vector for each vertex from its $L$-hop neighborhood.
+The parameters are tuned according to the specific prediction task, leading to high prediction accuracy.
+
+\subsection{GNN Unit and Message-passing Model}

### 2020-07-12 main.py
add for sampling_exp

@@ -110,6 +110,8 @@ optimizer = torch.optim.Adam(model.parameters(),
                              lr=args.lr,
                              weight_decay=args.weight_decay)
 
+log_memory(flag, device, 'data load')
+
 def train(epoch):
     t = time.time()
 

### 2020-07-12 main_full.py

@@ -139,7 +139,7 @@ def train(epoch):
     log = 'Epoch: {:03d}, train_loss: {:.8f}, train_time: {:.4f}s'
     t = time.time() - t
     print(log.format(epoch, loss.data.item(), t))
-    return 
+    return train_time
 
 @torch.no_grad()
 def test():
@@ -167,18 +167,16 @@ else:
         with torch.autograd.profiler.emit_nvtx(record_shapes=not args.no_record_shapes):
             train_time = 0
             for epoch in range(args.epochs):
-                t0 = time.time()
                 nvtx_push(gpu, "epochs" + str(epoch))
                 nvtx_push(gpu, "train")
-                train(epoch)
+                train_time += train(epoch)
                 nvtx_pop(gpu)
-                train_time += time.time() - t0
                 #nvtx_push(gpu, "eval")
                 #log = 'Accuracy: Train: {:.4f}, Val: {:.4f}, Test: {:.4f}'
                 #print(log.format(*test()))
                 
                 # add 
-                #log_memory(flag, device, 'eval_end')
+                log_memory(flag, device, 'eval_end')
                 
                 #nvtx_pop(gpu)
                 nvtx_pop(gpu)

### 2020-07-12 main_sampling_memory.py

@@ -140,6 +140,7 @@ elif args.model == 'gaan':
 device = torch.device(f'cuda: {args.gpu}' if gpu else 'cpu') # todo: model's device
 model = model.to(device)
 optimizer = torch.optim.Adam(model.parameters(), lr=args.lr, weight_decay=args.weight_decay)
+log_memory(flag, device, 'model load')
 
 def train(epoch):
     model.train()
@@ -159,7 +160,7 @@ def train(epoch):
             t1 = time.time()
             sampling_time += t1 - t0
             nvtx_push(gpu, "batch" + str(cnt))
-            log_memory(flag, device, 'forward_start')
+            log_memory(flag, device, 'batch_start') # tag
             nvtx_push(gpu, "forward")
             
             if args.mode == "cluster":
@@ -167,6 +168,7 @@ def train(epoch):
                 t2 = time.time()
                 to_time += t2 - t1
                 optimizer.zero_grad()
+                log_memory(flag, device, 'data load') # tag
                 #nodes, edges = batch.x.shape[0], batch.edge_index.shape[1]
                 #print(f"nodes: {nodes}, edges: {edges}")
                 out = model(batch.x, batch.edge_index)
@@ -185,6 +187,7 @@ def train(epoch):
                     y = data.y[n_id[:batch_size], :].to(device)
                 else:
                     y = data.y[n_id[:batch_size]].to(device)
+                log_memory(flag, device, 'to_end') # tag
                 t2 = time.time()
                 to_time += t2 - t1
                 optimizer.zero_grad()            
@@ -195,14 +198,14 @@ def train(epoch):
                     loss = F.nll_loss(out.log_softmax(dim=-1), y)
             nvtx_pop(gpu)
             
-            log_memory(flag, device, 'forward_end')
+            log_memory(flag, device, 'forward_end') # tag
             nvtx_push(gpu, "backward")
             loss.backward()
             optimizer.step()
             train_time += time.time() - t2
             nvtx_pop(gpu)
             
-            log_memory(flag, device, 'backward_end')
+            log_memory(flag, device, 'backward_end') # tag
             total_loss += loss.item() * batch_size            
             nvtx_pop(gpu)
             
@@ -210,9 +213,6 @@ def train(epoch):
         except StopIteration:
             break
 
-    #print("batchs", cnt, args.batch_size * cnt)
-    #print("sampling", all_nodes, all_edges)
[…]

### 2020-07-12 pics_degrees_dirtribution.py

@@ -9,7 +9,7 @@ cluster_path = "amp_cluster.npy"
 graphsage_path = "amp_graphsage.npy"
 
 paths = [graph_path, cluster_path, graphsage_path]
-names = ['Original Graph', 'Cluster-GCN Sampling', 'GraphSAGE Sampling']
+names = ['Original Graph', 'Cluster Sampling', 'Neighbor Sampling']
 
 def get_degrees_counts(path):
     # 1. 统计出每个节点的度数
@@ -45,8 +45,13 @@ def get_degrees_counts(path):
 
 
 fig, ax = plt.subplots()
+
+#ax.set_yscale("symlog", basey=2)
+#ax.set_xscale("symlog", basey=2)
 ax.set_yscale('log')
 ax.set_xscale('log')
+ax.set_ylim(ymin=0.5, ymax=1e4)
+ax.set_xlim(xmin=0.5, xmax=1e4)
 ax.set_xlabel("Degrees")
 ax.set_ylabel("Numbers")
 

### 2020-07-12 Manuscript/sec2-review-of-graph-neural-network.tex
Update the section of reviewing GNN units.

@@
 	\centering
-	\includegraphics[width=0.95\columnwidth]{figs/illustration/GNN_common_architecture.png}
-	\caption{Structure of a typical graph neural network. (a) Demo GNN; (b) GNN unit; (c) Demo graph. The target application is the node classification. The demo GNN has two GNN layers.}
+	\includegraphics[width=1.1\columnwidth]{figs/illustration/GNN_common_architecture.png}
+	\caption{Structure of a typical graph neural network. (a) Demo GNN, (b) Demo graph. The target application is the node classification. The demo GNN has two GNN layers.}
 	\label{fig:general_structure_of_gnn}
@@
 Each GNN unit correspond to a vertex in $\mathcal{G}$.
-In the first GNN layer (Layer 0), the GNN unit of the vertex $v_i$ collects input feature vectors of the vertices $\boldsymbol{x}_j$ that are adjacent to $v_i$ in $\mathcal{G}$ (i.e., $j \in \mathcal{N}(v_i)$) from the input layer.
-In other words, the connection between the input layer and the first GNN layer is determined by the topology of $\mathcal{G}$.
+In the first GNN layer (Layer 0), the GNN unit of the vertex $v_i$ collects input feature vectors of itself and the vertices $\boldsymbol{x}_j$ that are adjacent to $v_i$ in $\mathcal{G}$ (i.e., $j \in \mathcal{N}(v_i)$) from the input layer.
+After aggregating input feature vectors and applying non-linear transformation, the GNN unit outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
+Take the demo DNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as the example.
+Since $\mathcal{N}(v_3) = \{v_1, v_2, v_4, v_5, v_6\}$, the GNN unit of $v_1$ at layer 0 collects the feature vectors \{$\boldsymbol{x}_1$, $\boldsymbol{x}_2$, $\boldsymbol{x}_3$, $\boldsymbol{x}_4$, $\boldsymbol{x}_5$, $\boldsymbol{x}_6$\} from the input layer and outputs $\boldsymbol{h}^1_1$.
+We elaborate on the details of GNN units later.
+
+The connection between the input layer and the first GNN layer is determined by the topology of $\mathcal{G}$.
 In the traditional neural networks, the neural units of neighboring layers are fully connected.
-In GNNs, two GNN units are connected only if they have an edge between them in $\mathcal{G}$, which is usually \emph{sparse}.
-After aggregating input feature vectors and applying non-linear transformation, the GNN unit outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
+In GNNs, two GNN units are connected only if they have an edge between them in $\mathcal{G}$.
+Real-world graphs are usually very \emph{sparse}, i.e. $|\mathcal{E}| \ll |\mathcal{V}|^2$.
 
-In the next GNN layer (Layer 1), the GNN unit of $v_i$ collects the hidden feature vectors $\boldsymbol{h}^1_j$ of $v_i$'s neighbors (i.e., $j \in \mathcal{N}(v_i)$) from the \emph{previous} GNN layer.
-The connection between neighboring GNN layers are also determined by $\mathcal{E}$ of $\mathcal{G}$.
+In the next GNN layer (Layer 1), the GNN unit of $v_i$ collects the hidden feature vectors of itself $\boldsymbol{h}^1_i$ and its neighbors ($\boldsymbol{h}^1_j$ with $j \in \mathcal{N}(v_i)$) from the \emph{previous} GNN layer.
 Based on the collected hidden vectors, the GNN unit in Layer 1 outputs a new hidden feature vector $\boldsymbol{h}^2_i$ for $v_i$.
-A GNN allows to stack more GNN layers to support deeper graph analysis.
+Though there are only two GNN layers in \figurename~\ref{fig:general_structure_of_gnn}, a GNN allows to stack more GNN layers to support deeper graph analysis.
 %In \figurename~\ref{fig:general_structure_of_gnn}, we shows a GNN with two layers.
@@
 As an embedding vector, $\boldsymbol{h}^L_i$ encodoes the knowledge learned from the input layer and all the previous GNN layers.
-Finally, $\boldsymbol{h}^L_i$ is affected by $v_i$ and all the vertices in the $L$-hop neighborhood of $v_i$.
-Analyzing with deeper GNNs means analyzing each vertices with a wider scope.
+Since $\boldsymbol{h}^L_i$ is affected by $v_i$ and the vertices in the $L$-hop neighborhood of $v_i$, analyzing a graph with a \emph{deeper} GNN means analyzing each vertex with a \emph{wider} scope.
 
@@
 \subsection{GNN Unit and Message-passing Model}
+
+GNN units are building blocks of a GNN.
+A GNN layer consists of $|\mathcal{V}|$ units.
+Each vertex has a corresponding GNN unit.
+A GNN unit is a small neural network with the structure shown in \figurename~\ref{fig:general_structure_of_gnn}.
+The GNN unit of $v_i$ at layer $l$ receives hidden feature vectors $\boldsymbol{h}^l_j$ from the GNN units of itself and its neighbors ($j \in \{i\} \cup \mathcal{N}(v_i)$) at the previous GNN layer \footnote{For the GNN layer 0, GNN units receive input feature vectors, i.e., $\boldsymbol{h}^0_i=\boldsymbol{x}_i$}.
+The GNN unit aggregates the received hidden feature vectors, applies non-linear transformations, and outputs a new hidden feature vector $\boldsymbol{h}_i^{l+1}$.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.6\columnwidth]{figs/illustration/GNN_Unit.png}
+	\caption{The GNN Unit of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}(b).}
+	\label{fig:GNN_unit}
+\end{figure}
+
+We follow the message-passing model \cite{gilmer_messgae_passing} to formally define a GNN unit.
+The message-passing model is widely used in the cutting-edge GNN training systems like PyTorch Geometric (PyG) \cite{PyG} and Deep Graph Library (DGL) \cite{DGL}.
+\figurename~\ref{fig:GNN_unit} shows the structure of a GNN unit.

### 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 2 of manuscript.

@@
 Every vertex $v_i$ in $\mathcal{G}$ is attached with a feature vector $\boldsymbol{x}_i$ to describe the properties of the vertex.
+The edges of $\mathcal{G}$ may also be attached with feature vectors $\boldsymbol{e}_{i,j}$
 The input layer of a GNN receives feature vectors from all vertices and passes them to GNN layers.
 
-A GNN layer consists of $n$ GNN units, where $n$ is the number of vertices in $\mathcal{G}$.
-Each GNN unit correspond to a vertex in $\mathcal{G}$.
-In the first GNN layer (Layer 0), the GNN unit of the vertex $v_i$ collects input feature vectors of itself and the vertices $\boldsymbol{x}_j$ that are adjacent to $v_i$ in $\mathcal{G}$ (i.e., $j \in \mathcal{N}(v_i)$) from the input layer.
-After aggregating input feature vectors and applying non-linear transformation, the GNN unit outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
+A GNN layer consists of $n$ graph neurons, where $n$ is the number of vertices in $\mathcal{G}$.
+Each graph neuron corresponds to a vertex in $\mathcal{G}$.
+In the first GNN layer (Layer 0), the graph neuron of the vertex $v_i$ collects input feature vectors of itself and the vertices $\boldsymbol{x}_j$ that are adjacent to $v_i$ in $\mathcal{G}$ (i.e., $v_j \in \mathcal{N}(v_i)$) from the input layer.
+After aggregating input feature vectors and applying non-linear transformation, the graph neuron outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
 Take the demo DNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as the example.
-Since $\mathcal{N}(v_3) = \{v_1, v_2, v_4, v_5, v_6\}$, the GNN unit of $v_1$ at layer 0 collects the feature vectors \{$\boldsymbol{x}_1$, $\boldsymbol{x}_2$, $\boldsymbol{x}_3$, $\boldsymbol{x}_4$, $\boldsymbol{x}_5$, $\boldsymbol{x}_6$\} from the input layer and outputs $\boldsymbol{h}^1_1$.
-We elaborate on the details of GNN units later.
+Since $\mathcal{N}(v_3) = \{v_1, v_2, v_4, v_5, v_6\}$, the graph neuron of $v_1$ at layer 0 collects the feature vectors \{$\boldsymbol{x}_1$, $\boldsymbol{x}_2$, $\boldsymbol{x}_3$, $\boldsymbol{x}_4$, $\boldsymbol{x}_5$, $\boldsymbol{x}_6$\} from the input layer and outputs $\boldsymbol{h}^1_1$.
+Different GNNs mainly differ in the graph neurons that they use.
+We elaborate on their details later.
 
 The connection between the input layer and the first GNN layer is determined by the topology of $\mathcal{G}$.
-In the traditional neural networks, the neural units of neighboring layers are fully connected.
-In GNNs, two GNN units are connected only if they have an edge between them in $\mathcal{G}$.
-Real-world graphs are usually very \emph{sparse}, i.e. $|\mathcal{E}| \ll |\mathcal{V}|^2$.
+In the traditional neural networks, neurons of neighboring layers are fully connected.
+In GNNs, two graph neurons are connected only if their corresponding vertices have an edge between them in $\mathcal{G}$.
+Most real-world graphs are very \emph{sparse}, i.e. $|\mathcal{E}| \ll |\mathcal{V}|^2$.
 
-In the next GNN layer (Layer 1), the GNN unit of $v_i$ collects the hidden feature vectors of itself $\boldsymbol{h}^1_i$ and its neighbors ($\boldsymbol{h}^1_j$ with $j \in \mathcal{N}(v_i)$) from the \emph{previous} GNN layer.
-Based on the collected hidden vectors, the GNN unit in Layer 1 outputs a new hidden feature vector $\boldsymbol{h}^2_i$ for $v_i$.
+In the next GNN layer (Layer 1), the graph neuron of $v_i$ collects the hidden feature vectors of itself $\boldsymbol{h}^1_i$ and its neighbors ($\boldsymbol{h}^1_j$ with $v_j \in \mathcal{N}(v_i)$) from the \emph{previous} GNN layer.
+Based on the collected hidden vectors, the graph neuron in Layer 1 outputs a new hidden feature vector $\boldsymbol{h}^2_i$ for $v_i$.
 Though there are only two GNN layers in \figurename~\ref{fig:general_structure_of_gnn}, a GNN allows to stack more GNN layers to support deeper graph analysis.
@@
 
-\subsection{GNN Unit and Message-passing Model}
+\subsection{Graph Neuron and Message-passing Model}
 
-GNN units are building blocks of a GNN.
-A GNN layer consists of $|\mathcal{V}|$ units.
-Each vertex has a corresponding GNN unit.
-A GNN unit is a small neural network with the structure shown in \figurename~\ref{fig:general_structure_of_gnn}.
-The GNN unit of $v_i$ at layer $l$ receives hidden feature vectors $\boldsymbol{h}^l_j$ from the GNN units of itself and its neighbors ($j \in \{i\} \cup \mathcal{N}(v_i)$) at the previous GNN layer \footnote{For the GNN layer 0, GNN units receive input feature vectors, i.e., $\boldsymbol{h}^0_i=\boldsymbol{x}_i$}.
-The GNN unit aggregates the received hidden feature vectors, applies non-linear transformations, and outputs a new hidden feature vector $\boldsymbol{h}_i^{l+1}$.
+Graph neurons are building blocks of a GNN.
+A GNN layer consists of $|\mathcal{V}|$ graph neurons.
+Each vertex corresponds to a graph neuron.
+A graph neuron as shown in \figurename~\ref{fig:graph_neuron_structure} is a small neural network.
+The graph neuron of $v_i$ at layer $l$ receives hidden feature vectors $\boldsymbol{h}^l_j$ from the graph neurons of $v_i$ and its neighbors ($v_j \in \{v_i\} \cup \mathcal{N}(v_i)$) at the previous GNN layer \footnote{For the GNN layer 0, graph neurons receive input feature vectors, i.e., $\boldsymbol{h}^0_i=\boldsymbol{x}_i$}.
+The graph neuron aggregates the received hidden feature vectors, applies non-linear transformations, and outputs a new hidden feature vector $\boldsymbol{h}_i^{l+1}$.
 
@@
 	\includegraphics[width=0.6\columnwidth]{figs/illustration/GNN_Unit.png}
-	\caption{The GNN Unit of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}(b).}
-	\label{fig:GNN_unit}
+	\caption{Graph neuron of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}(b).
+$\phi$/$\Sigma$/$\gamma$ are the message/aggregation/vertex update functions in the message-passing model, respecitvely.}
+	\label{fig:graph_neuron_structure}
 \end{figure}
 
-We follow the message-passing model \cite{gilmer_messgae_passing} to formally define a GNN unit.
+We follow the message-passing model \cite{gilmer_messgae_passing} to formally define a graph neuron.
 The message-passing model is widely used in the cutting-edge GNN training systems like PyTorch Geometric (PyG) \cite{PyG} and Deep Graph Library (DGL) \cite{DGL}.
-\figurename~\ref{fig:GNN_unit} shows the structure of a GNN unit.
+\figurename~\ref{fig:graph_neuron_structure} shows the structure of a graph neuron in the message-passing model.
+Graph neurons at layer $l$ are made of three \emph{differentiable} functions: $\phi^l$, $\Sigma^l$ and $\gamma^l$.
+The graph neuron calculates the output hidden vector $\boldsymbol{h}^{l+1}_i$ by
+$$
+\boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \mathlarger{\Sigma}^l_{v_j \in \mathcal{N}(v_i)}{\phi^l(\boldsymbol{h}^l_i, \boldsymbol{h}^l_j,	\boldsymbol{e}_{j,i})}).
+$$
+
+$\phi^l$ is the \emph{message} function.
+For every incident edge $(v_j, v_i)$ of $v_i$, $\phi$ receives the output hidden feature vectors $\boldsymbol{h}^l_i$ and $\boldsymbol{h}^l_j$ of the previous GNN layer and the edge feature vector $\boldsymbol{e}_{j,i}$ as the input.
+$\phi^l$ outputs a message vector $\boldsymbol{m}^l_{j,i}$ for every edge $(v_j, v_i)$ at layer $l$, i.e., $\boldsymbol{m}^l_{j,i}=\phi^l(\boldsymbol{h}^l_i, \boldsymbol{h}^l_j, \boldsymbol{e}_{j,i})$.
+For $v_i$, the message vectors $\boldsymbol{m}^l_{x,j}$ with $v_x \in \mathcal{N}(v_i)$ are aggregated by the \emph{aggregation} function $\Sigma^l$ to produce an aggregated vector $\boldsymbol{s}^l_i$, i.e., $\boldsymbol{s}^l_i=\mathlarger{\Sigma}^l_{v_j \in \mathcal{N}(v_i)}\boldsymbol{m}^l_{j,i}$.
+$v_i$'s aggregated vector $\boldsymbol{s}^l_i$ and its hidden vector $\boldsymbol{h}^l_i$ from the previous GNN layer are fed into the \emph{vertex update} function $\gamma^l$ to calculate the output hidden vector $\boldsymbol{h}^{l+1}_i$ of the current layer $l$, i.e., $\boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \boldsymbol{s}^l_i)$
+The end-to-end training requires $\phi^l$ and $\gamma^l$ (like multi layer perceptrons and GRU) and $\Sigma_l$ (like mean, sum, element-wise min/max) are \emph{differentiable} to make the whole GNN differentialble.
+
+Different GNNs adopt different kinds of graph neurons and have different definitions of the three functions.
+$\phi$ and $\Sigma$ are the \emph{edge computation} functions.
+They are conducted over every edge in $\mathcal{G}$.
+$\gamma$ is the \emph{vertex computation} function.
+It is conducted over every vertex in $\mathcal{G}$.
+\tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
+
+\begin{table}
+	\hspace{-10em}
+    \begin{footnotesize}
+        \begin{tabular}{ccp{8em}p{22em}r}
+		\toprule
+		GNN &
+		Type &
+		$\Sigma$ &
+		$\phi$ &
+		Complexity \\ \midrule
+		ChebNet \cite{defferrad2016_chebnet} &
+		Spectral &
+		sum &
+		$\boldsymbol{m}_{j, i, , k}^l = T_k(\widetilde{L} )_{j, i} \boldsymbol{h}_j^l$ &
+		$O(K * d_{in})$ \\
+		\textbf{GCN} &
+		Spectral &
+		sum &
+		$\boldsymbol{m}_{j, i}^l = e_{j, i} \boldsymbol{h}_j^l$ &
+		$O(d_{in})$ \\
+		AGCN &
+		Spectral &
+		sum &
+		$\boldsymbol{m}_{j, i}^l = \tilde{e}_{j, i}^l \boldsymbol{h}_j^l$ &
+		$O(d_{in})$ \\
+		GraphSAGE &
+		Non-spectral &
+		mean/LSTM/max &
+		$\boldsymbol{m}_{j, i}^l =  \boldsymbol{h}_j^l$ &
+		$O(1)$ \\
+		Neural FPs &
+		Non-spectral &
+		sum &
+		$\boldsymbol{m}_{j, i}^l = \boldsymbol{h}_j^l$ &
+		$O(d_{in})$ \\
+		SSE &
+		Recurrent &
+		sum &
+		$\boldsymbol{m}_{j, i}^l = [\boldsymbol{h}_i^{l} \parallel \boldsymbol{h}_j^l]$ &
+		$O(1)$ \\
+		\textbf{GGNN} &
+		Gated &
+		sum &
+		$\boldsymbol{m}_{j, i} = \textcolor{blue}{\boldsymbol{W}^l} \boldsymbol{h}_j^l$ &
+		$O(d_{in} * d_{out})$ \\
+		Tree-LSTM &
+		LSTM &
+		sum &
+		$\boldsymbol{m}_{j, i}^l = \boldsymbol{h}_j^l$ &
+		$O(1)$ \\
+		\textbf{GAT}&
+		Attention &
+		sum  &
+		\begin{scriptsize}
+			$\begin{aligned}[t]
+			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
+			&  \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l})
+			\end{aligned}$
+		\end{scriptsize} &
+		$O(K * d_{in} * d_{out})$ \\
+		\textbf{GaAN} &
+		Attention &
+		sum,max,mean &
+		\begin{scriptsize}
+			$\begin{aligned}[t]
+			&\alpha_{j, i}^k = \frac {\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l, k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}} \boldsymbol{h}_i^l] )} {\sum_{k \in \mathcal{N}(j)}\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}}  \boldsymbol{h}_k^l] )} \\
+			&\boldsymbol{m}_{j, i, 1}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}_v} \boldsymbol{h}_j^{l}) \\
+			&\boldsymbol{m}_{j, i, 2}^l = \textcolor{blue}{\boldsymbol{W}^l_m} \boldsymbol{h}_j^{l} \\
+			&\boldsymbol{m}_{j, i, 3}^l = \boldsymbol{h}_j^l
+			\end{aligned}$
+		\end{scriptsize} &
+		$O(max(d_a, d_m) * K * d_{in})$ \\
+		\bottomrule
+	\end{tabular}
+\end{footnotesize}
+	\caption{Typical graph neural networks and their edge computation functions.$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
+Blue variables are model parameters to learn.}
+	\label{tab:gnn_overview_edge}
+\end{table}
+
+\begin{table}
+	\hspace{-3em}
+    \begin{footnotesize}
+        \begin{tabular}{cp{20em}r}
+		\toprule
+		GNN &
+		$\gamma$ &
+		Complexity \\ \midrule
+		ChebNet \cite{defferrad2016_chebnet} &
+		$\boldsymbol{h}_i^{l+1} = \sum_{k=0}^K \textcolor{blue}{\boldsymbol{W}}^{l,k}  \boldsymbol{s}_{i, k}^{l} $ &
+		$O(d_{in} * d_{out})$ \\
+		\textbf{GCN} &
+		$\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l  \boldsymbol{s}_i^{l}$ &
+		$O(d_{in} * d_{out})$ \\
+		AGCN &
+		$\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l  \boldsymbol{s}_i^{l}$ &
+		$O(d_{in} * d_{out})$ \\
+		GraphSAGE &	
+		$\boldsymbol{h}_i^{l+1} =   \delta(\textcolor{blue}{\boldsymbol{W}}^l  [\boldsymbol{s}_i^{l} \parallel \boldsymbol{h}_i^l])$ &
+		$O(d_{in} * d_{out})$ \\
+		Neural FPs &
+		$\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{\boldsymbol{N}_i}  \boldsymbol{s}_i^{l})$ &
+		$O(d_{in} * d_{out})$ \\
+		SSE &
+		$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2), \boldsymbol{s}_i^l)$ &
+		$O(d_{in} * d_{out})$ \\
+		\textbf{GGNN} &
+		\begin{scriptsize}
+		$\begin{aligned}[t]
+			& \textcolor{blue}{\boldsymbol{z}}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^z \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^{sz} + \textcolor{blue}{\boldsymbol{U}}^z \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hz}) \\
+			&\boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^r \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}}^{sr} +\textcolor{blue}{\boldsymbol{U}}^r \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hr}) \\
+			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}}^l \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^h))) \\
+			&\boldsymbol{h}_i^{l+1} = (1 - \textcolor{blue}{\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l +  \textcolor{blue}{\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
+		\end{aligned}$
+		\end{scriptsize}
+		&
+		$O(max(d_{in}, d_{out}) * d_{out})$ \\
+		Tree-LSTM &
+		$h_i^{l+1} = LSTM(\boldsymbol{s}_i^l, \boldsymbol{h}_i^{l})$ &
+		$O(d_{in} * d_{out})$ \\
+		\textbf{GAT}&
+		$\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
+		$O(1)$ \\
+		\textbf{GaAN} &
+		\begin{scriptsize}
+			$\begin{aligned}[t]
+			&\boldsymbol{g}_i = \textcolor{blue}{\boldsymbol{W}}^l_g  [\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i, 2}^l \parallel \boldsymbol{s}_{i, 3}^l]  \\
+			&\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l_o [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i, 3}^l) ]
+			\end{aligned}$ 
+		\end{scriptsize}&
+		$O(max(d_{in} + K * d_v, 2 * d_{in} + d_m) d_{out})$ \\ \bottomrule
+	\end{tabular}
+\end{footnotesize}
+	\caption{Typical graph neural networks and their vertex computation functions.
+$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
+Blue variables are model parameters to learn.}
+	\label{tab:gnn_overview_vertex}
+\end{table}
+
+\subsection{Classification of GNNs}
+
+Since we focus on analyzing the performance bottleneck in training GNNs, we classify the typical GNNs from the view of computational complexity.
+The computational complexity of a GNN layer is related to the complexity of its vertex and edge functions, i.e.
+$O(m * (O_\phi + O_\Sigma) + n * O_\gamma)$, where $O_\phi$/$O_\Sigma$/$O_\gamma$ are the computational complexity of the three functions.
+
+The complexity can be decomposed into two parts: the edge computation complexity $O_\phi$ + $O_\Sigma$ and the vertex computation complexity $O_\gamma$.
+In \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we list the edge and vertex computation complexity, respectively.
+The edge/vertex complexity of a graph neuron are affected by the dimensions of the input/output hidden vectors $d_{in}$ and $d_{out}$ and the dimensions of the model parameters (like the number of heads $K$ in GAT and the dimensions of the view vectors $d_a$/$d_v$ in GaAN).
+
+We classify the typical GNNs into four groups based on their edge/vertex complexity.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.6\columnwidth]{figs/illustration/GNN_complexity_quadrant.png}
+	\caption{Complexity quadrant of typical GNNs. If two GNNs have the same big-O complexity, we further compare their complexity according to the number of parameters.}
+\end{figure}

### 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
更新了complexity_quadrant图像和公式

@@
 		Neural FPs &
-		$\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{\boldsymbol{N}_i}  \boldsymbol{s}_i^{l})$ &
+		$\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{h}_i^l +\boldsymbol{W}}^{\boldsymbol{N}_i}  \boldsymbol{s}_i^{l})$ &
 		$O(d_{in} * d_{out})$ \\

### 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
更新复杂度分析。
更新了GNN_complexity_quadrant图（去除了Tree-LSTM, 点计算公式缩写不大对，太麻烦)

--- 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 		Non-spectral &
-		mean/LSTM/max &
+		mean/LSTM &
 		$\boldsymbol{m}_{j, i}^l =  \boldsymbol{h}_j^l$ &
@@
 		$O(d_{in} * d_{out})$ \\
-		Tree-LSTM &
-		LSTM &
-		sum &
-		$\boldsymbol{m}_{j, i}^l = \boldsymbol{h}_j^l$ &
-		$O(1)$ \\
 		\textbf{GAT}&
@@
 		$\boldsymbol{h}_i^{l+1} = \sum_{k=0}^K \textcolor{blue}{\boldsymbol{W}}^{l,k}  \boldsymbol{s}_{i, k}^{l} $ &
-		$O(d_{in} * d_{out})$ \\
+		$O(K * d_{in} * d_{out})$ \\
 		\textbf{GCN} &
@@
 		Neural FPs &
-		$\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{\boldsymbol{N}_i}  \boldsymbol{s}_i^{l})$ &
+		$\boldsymbol{h}_i^{l+1} = \delta(\boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{W}}^{\boldsymbol{N}_i}  \boldsymbol{s}_i^{l})$ &
 		$O(d_{in} * d_{out})$ \\
@@
 		$O(max(d_{in}, d_{out}) * d_{out})$ \\
-		Tree-LSTM &
-		$h_i^{l+1} = LSTM(\boldsymbol{s}_i^l, \boldsymbol{h}_i^{l})$ &
-		$O(d_{in} * d_{out})$ \\
 		\textbf{GAT}&
@@
 	\centering
-	\includegraphics[width=0.6\columnwidth]{figs/illustration/GNN_complexity_quadrant.png}
+	\includegraphics[width=0.7\columnwidth]{figs/illustration/GNN_complexity_quadrant.png}
 	\caption{Complexity quadrant of typical GNNs. If two GNNs have the same big-O complexity, we further compare their complexity according to the number of parameters.}

### 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
Update the ChebNet complexity analysis.

@@
 \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
+For ChebNet, we report its GNN layer in the tables \footnote{A layer of ChebNet consists of $K$ GNN sub-layers and a summation layer, i.e., $\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with GNN layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$.
+$\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
+In the table, we report the GNN sub-layer of ChebNet that calculates $\boldsymbol{Z}^{(k)}$}.
 
@@
 		sum &
-		$\boldsymbol{m}_{j, i, , k}^l = T_k(\widetilde{L} )_{j, i} \boldsymbol{h}_j^l$ &
-		$O(K * d_{in})$ \\
+		$\boldsymbol{m}_{j, i}^{(k)} = e_{j, i}\boldsymbol{z}_j^{(k-1)}$ &
+		$O(d_{in})$ \\
 		\textbf{GCN} &
@@
 	\caption{Typical graph neural networks and their edge computation functions.$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
-Blue variables are model parameters to learn.}
+		Blue variables are model parameters to learn. For ChebNet, we report its GNN sub-layer.}
 	\label{tab:gnn_overview_edge}
@@
 		ChebNet \cite{defferrad2016_chebnet} &
-		$\boldsymbol{h}_i^{l+1} = \sum_{k=0}^K \textcolor{blue}{\boldsymbol{W}}^{l,k}  \boldsymbol{s}_{i, k}^{l} $ &
-		$O(K * d_{in} * d_{out})$ \\
+		$\boldsymbol{z}_i^{(k)} = 2\boldsymbol{s}^{(k)}_{i} - \boldsymbol{z}_i^{(k-2)}$&
+		$O(d_{in})$ \\
 		\textbf{GCN} &
@@
 $d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
-Blue variables are model parameters to learn.}
+Blue variables are model parameters to learn.
+For ChebNet, we report its GNN sub-layer.}
 	\label{tab:gnn_overview_vertex}

### 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
更新了Manuscripts中的公式和图片

@@
 		$O(1)$ \\
+		GraphSAGE-pool &
+		Non-spectral &
+		max &
+		$\boldsymbol{m}_{j, i}^l =  \delta(\textcolor{blue}{\boldsymbol{W}^l_{pool}} \boldsymbol{h}_j^l + \textcolor{blue}{b}^l)$  &
+		$O(d_{in} * d_{out})$ \\
 		Neural FPs &
@@
 		$\boldsymbol{m}_{j, i}^l = \boldsymbol{h}_j^l$ &
-		$O(d_{in})$ \\
+		$O(1)$ \\
 		SSE &
@@
 		$\boldsymbol{m}_{j, i}^l = [\boldsymbol{h}_i^{l} \parallel \boldsymbol{h}_j^l]$ &
-		$O(1)$ \\
+		$O(d_{in})$ \\
 		\textbf{GGNN} &
@@
 			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
-			&  \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l})
+			& Multi-head\ concatenation: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l}) \\
+			& Multi-head\ average: \boldsymbol{m}_{j, i}^l = \frac{1}{K} \sum_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l})
 			\end{aligned}$
@@
 		\end{scriptsize} &
-		$O(max(d_a, d_m) * K * d_{in})$ \\
+		$O(max(d_a, d_m, d_v) * K * d_{in})$ \\
 		\bottomrule
@@
 	\caption{Typical graph neural networks and their edge computation functions.$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
-		Blue variables are model parameters to learn. For ChebNet, we report its GNN sub-layer.}
+		Blue variables are model parameters to learn.
+For ChebNet, we report its GNN sub-layer.
+Because two sum operator are interchangeable and sum operator and concatenation operator are interchangeable, we do it for GAT to explain more clearly in edge computations functions.}
 	\label{tab:gnn_overview_edge}
@@
 		$O(d_{in} * d_{out})$ \\
+		GraphSAGE-pool &	
+		$\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
+		$O(1)$ \\
 		Neural FPs &
-		$\boldsymbol{h}_i^{l+1} = \delta(\boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{W}}^{\boldsymbol{N}_i}  \boldsymbol{s}_i^{l})$ &
+		$\boldsymbol{h}_i^{l+1} = \delta(\boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  \boldsymbol{s}_i^{l})$ &
 		$O(d_{in} * d_{out})$ \\
 		SSE &
-		$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2), \boldsymbol{s}_i^l)$ &
+		$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 \boldsymbol{s}_i^l))$ &
 		$O(d_{in} * d_{out})$ \\
@@
 			&\boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^r \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}}^{sr} +\textcolor{blue}{\boldsymbol{U}}^r \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hr}) \\
-			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}}^l \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^h))) \\
+			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^h))) \\
 			&\boldsymbol{h}_i^{l+1} = (1 - \textcolor{blue}{\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l +  \textcolor{blue}{\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
@@
 			&\boldsymbol{g}_i = \textcolor{blue}{\boldsymbol{W}}^l_g  [\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i, 2}^l \parallel \boldsymbol{s}_{i, 3}^l]  \\
-			&\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l_o [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i, 3}^l) ]
+			&\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l_o [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i, 1}^l) ]
 			\end{aligned}$ 
 		\end{scriptsize}&
-		$O(max(d_{in} + K * d_v, 2 * d_{in} + d_m) d_{out})$ \\ \bottomrule
+		$O(max(K * d_v + d_{in}, 2 * d_{in} + d_m) * d_{out})$ \\ \bottomrule
 	\end{tabular}
@@
 Blue variables are model parameters to learn.
-For ChebNet, we report its GNN sub-layer.}
+For ChebNet, we report its GNN sub-layer.For Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for nodes with degree
+	$|\mathcal{N}(i)|$ at layer $l$.}
 	\label{tab:gnn_overview_vertex}

### 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 2.

--- 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 		$O(d_{in})$ \\
-		\textbf{GCN} &
+		\textbf{GCN} \cite{kipf2017_gcn} &
 		Spectral &
@@
 		$O(d_{in})$ \\
-		\textbf{GCN} &
+		\textbf{GCN} \cite{kipf2017_gcn} &
 		$\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l  \boldsymbol{s}_i^{l}$ &
@@
 
-We classify the typical GNNs into four groups based on their edge/vertex complexity.
+We classify the typical GNNs into four quadrants based on their edge/vertex complexity as shown in \figurename~\ref{fig:gnn_complexity_quadrant}.
+We pick GCN, GGNN, GAT and GaAN as the representative GNNs of the four quadrants.
 
@@
 	\includegraphics[width=0.7\columnwidth]{figs/illustration/GNN_complexity_quadrant.png}
-	\caption{Complexity quadrant of typical GNNs. If two GNNs have the same big-O complexity, we further compare their complexity according to the number of parameters.}
+	\caption{Complexity quadrants of typical GNNs. If two GNNs have the same complexity under the Big-O notation, we further compare their complexity according to how many parameters they need to train.}
+	\label{fig:gnn_complexity_quadrant}
 \end{figure}
+
+\textbf{GCN} \cite{kipf2017_gcn} (low vertex \& edge computational complexity): Graph convolution network (GCN) is the first-order approximation of the spectral-based graph convolutions.
+%By combining the advantages of both the spectral-based and the spatial-based convolution, it can learn the representation of the local topological structure and vertex features efficiently.
+It has only one parameter to learn at each layer, i.e. the weight matrix $\boldsymbol{W}^l$ in $\gamma$.
+A GCN graph neuron can be expressed as $\boldsymbol{h}^{l+1}_i = \boldsymbol{W}^l\sum_{v_j \in \mathcal{N}(v_i)}{e_{j,i}\boldsymbol{h}^l_j}$, where $e_{j,i}$ is the normalized weight of the edge $(v_j, v_i)$.
+%In the matrix view, $\boldsymbol{H}^{l+1} = (\boldsymbol{A}\boldsymbol{H}^l)\boldsymbol{W}^l$.
+According to the associative law of the matrix multiplication, $\boldsymbol{h}^{l+1}_i = \sum_{v_j \in \mathcal{N}(v_i)}{e_{j,i}\boldsymbol{W}^l\boldsymbol{h}^l_j}$.
+Since the dimension of $\boldsymbol{h}^{l+1}_i$ is usually smaller than $\boldsymbol{h}^l_i$ in practical GCNs, the implementation of GCN \footnote{The implementation of GCN in PyTorch Geometric: \url{ https://github.com/rusty1s/pytorch_geometric/blob/1.5.0/torch_geometric/nn/conv/gcn_conv.py}} chooses to first conduct the vertex computation $\hat{\boldsymbol{h}}^l_j = \boldsymbol{W}^l\boldsymbol{h}^l_j$ for each vertex $v_j$ and then conduct the edge computation $\boldsymbol{h}^{l+1}_i=\sum_{v_j\in\mathcal{N}(v_i)}{\hat{\boldsymbol{h}}^l_j}$.
+As $\hat{\boldsymbol{h}}^l_j$ has the same dimension as $\boldsymbol{h}^{l+1}_i$, the implementation significantly reduces the  computation cost of the edge computation.

### 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 2.

@@
 			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
-			& Multi-head\ concatenation: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l}) \\
-			& Multi-head\ average: \boldsymbol{m}_{j, i}^l = \frac{1}{K} \sum_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l})
+			& \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l}) \\
+			& \text{Multi-head average}: \boldsymbol{m}_{j, i}^l = \frac{1}{K} \sum_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l})
 			\end{aligned}$

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
修正了Neural FPs和GGNN的错误

--- 2020-07-13 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 		Neural FPs &
-		$\boldsymbol{h}_i^{l+1} = \delta(\boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  \boldsymbol{s}_i^{l})$ &
+		$\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  (\boldsymbol{h}_i^l + \boldsymbol{s}_i^{l}))$ &
 		$O(d_{in} * d_{out})$ \\
@@
 			&\boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^r \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}}^{sr} +\textcolor{blue}{\boldsymbol{U}}^r \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hr}) \\
-			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^h))) \\
+			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}}^h)) \\
 			&\boldsymbol{h}_i^{l+1} = (1 - \textcolor{blue}{\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l +  \textcolor{blue}{\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
修正了SSE的错误

@@
 		sum &
-		$\boldsymbol{m}_{j, i}^l = [\boldsymbol{h}_i^{l} \parallel \boldsymbol{h}_j^l]$ &
+		$\boldsymbol{m}_{j, i}^l = [\boldsymbol{x}_j \parallel \boldsymbol{h}_j^l]$ &
 		$O(d_{in})$ \\
@@
 		SSE &
-		$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 \boldsymbol{s}_i^l))$ &
-		$O(d_{in} * d_{out})$ \\
+		$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 [\boldsymbol{x}_i \parallel \boldsymbol{s}_i^l]))$ &
+		$O((2 * f + d_{in}) * d_{out})$ \\
 		\textbf{GGNN} &

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
更新Section2

--- 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 	\centering
-	\includegraphics[width=1.1\columnwidth]{figs/illustration/GNN_common_architecture.png}
+	\includegraphics[width=1\columnwidth]{figs/illustration/GNN_common_architecture.png}
 	\caption{Structure of a typical graph neural network. (a) Demo GNN, (b) Demo graph. The target application is the node classification. The demo GNN has two GNN layers.}
@@
 \begin{table}
-	\hspace{-10em}
+	\hspace{-5em}
     \begin{footnotesize}
@@
 		$\boldsymbol{m}_{j, i}^l =  \boldsymbol{h}_j^l$ &
-		$O(1)$ \\
+		$O(d_{in})$ \\
 		GraphSAGE-pool &
@@
 		$\boldsymbol{m}_{j, i}^l = \boldsymbol{h}_j^l$ &
-		$O(1)$ \\
+		$O(d_{in})$ \\
 		SSE &
@@
 		$\boldsymbol{z}_i^{(k)} = 2\boldsymbol{s}^{(k)}_{i} - \boldsymbol{z}_i^{(k-2)}$&
-		$O(d_{in})$ \\
+		$O(d_{out})$ \\
 		\textbf{GCN} \cite{kipf2017_gcn} &
@@
 		$\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
-		$O(1)$ \\
+		$O(d_{out})$ \\
 		Neural FPs &
-		$\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  (\boldsymbol{h}_i^l + \boldsymbol{s}_i^{l}))$ &
+		$\boldsymbol{h}_i^{l+1} = \delta(\boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  \boldsymbol{s}_i^{l})$ &
 		$O(d_{in} * d_{out})$ \\
@@
 		$\begin{aligned}[t]
-			& \textcolor{blue}{\boldsymbol{z}}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^z \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^{sz} + \textcolor{blue}{\boldsymbol{U}}^z \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hz}) \\
+			& {\boldsymbol{z}}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^z \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^{sz} + \textcolor{blue}{\boldsymbol{U}}^z \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hz}) \\
 			&\boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^r \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}}^{sr} +\textcolor{blue}{\boldsymbol{U}}^r \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hr}) \\
-			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}}^h)) \\
-			&\boldsymbol{h}_i^{l+1} = (1 - \textcolor{blue}{\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l +  \textcolor{blue}{\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
+			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^h))) \\
+			&\boldsymbol{h}_i^{l+1} = (1 - {\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l +  {\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
 		\end{aligned}$
@@
 		&
-		$O(max(d_{in}, d_{out}) * d_{out})$ \\
+		$O(d_{in} * d_{out})$ \\
 		\textbf{GAT}&
 		$\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
-		$O(1)$ \\
+		$O(d_{out})$ \\
 		\textbf{GaAN} &
@@
 As $\hat{\boldsymbol{h}}^l_j$ has the same dimension as $\boldsymbol{h}^{l+1}_i$, the implementation significantly reduces the  computation cost of the edge computation.
+
+\textbf{GGNN} ()

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex

@@
 		Neural FPs &
-		$\boldsymbol{h}_i^{l+1} = \delta(\boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  \boldsymbol{s}_i^{l})$ &
+		$\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  (\boldsymbol{h}_i^l + \boldsymbol{s}_i^{l}))$ &
 		$O(d_{in} * d_{out})$ \\
 		SSE &
-		$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 \boldsymbol{s}_i^l))$ &
-		$O(d_{in} * d_{out})$ \\
+		$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 [\boldsymbol{x}_i \parallel \boldsymbol{s}_i^l]))$ &
+		$O((2 * f + d_{in}) * d_{out})$ \\
 		\textbf{GGNN} &
@@
 			&\boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^r \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}}^{sr} +\textcolor{blue}{\boldsymbol{U}}^r \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hr}) \\
-			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^h))) \\
-			&\boldsymbol{h}_i^{l+1} = (1 - {\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l +  {\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
+			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}}^h)) \\
+			&\boldsymbol{h}_i^{l+1} = (1 - \textcolor{blue}{\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l +  \textcolor{blue}{\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
 		\end{aligned}$

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
更新复杂度分析.

@@
 			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}}^h)) \\
-			&\boldsymbol{h}_i^{l+1} = (1 - \textcolor{blue}{\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l +  \textcolor{blue}{\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
+			&\boldsymbol{h}_i^{l+1} = (1 - {\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l + {\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
 		\end{aligned}$

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 2.

@@
 		$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 [\boldsymbol{x}_i \parallel \boldsymbol{s}_i^l]))$ &
-		$O((2 * f + d_{in}) * d_{out})$ \\
+		$O((f + d_{in}) * d_{out})$ \\
 		\textbf{GGNN} &

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
Update complexity analysis.

@@
 		$\boldsymbol{m}_{j, i}^l =  \boldsymbol{h}_j^l$ &
-		$O(d_{in})$ \\
+		$O(1)$ \\
 		GraphSAGE-pool &
@@
 		$\boldsymbol{m}_{j, i}^l = [\boldsymbol{x}_j \parallel \boldsymbol{h}_j^l]$ &
-		$O(d_{in})$ \\
+		$O(f+d_{in})$ \\
 		\textbf{GGNN} &
@@
 		$\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
-		$O(d_{out})$ \\
+		$O(1)$ \\
 		Neural FPs &
@@
 		$\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
-		$O(d_{out})$ \\
+		$O(1)$ \\
 		\textbf{GaAN} &

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
update section 2.

@@
 \figurename~\ref{fig:graph_neuron_structure} shows the structure of a graph neuron in the message-passing model.
+A graph neuron collects messages from its neighbor graph neurons and outputs a hidden feature vector according to the aggregated messages.
 Graph neurons at layer $l$ are made of three \emph{differentiable} functions: $\phi^l$, $\Sigma^l$ and $\gamma^l$.
@@
 For every incident edge $(v_j, v_i)$ of $v_i$, $\phi$ receives the output hidden feature vectors $\boldsymbol{h}^l_i$ and $\boldsymbol{h}^l_j$ of the previous GNN layer and the edge feature vector $\boldsymbol{e}_{j,i}$ as the input.
-$\phi^l$ outputs a message vector $\boldsymbol{m}^l_{j,i}$ for every edge $(v_j, v_i)$ at layer $l$, i.e., $\boldsymbol{m}^l_{j,i}=\phi^l(\boldsymbol{h}^l_i, \boldsymbol{h}^l_j, \boldsymbol{e}_{j,i})$.
-For $v_i$, the message vectors $\boldsymbol{m}^l_{x,j}$ with $v_x \in \mathcal{N}(v_i)$ are aggregated by the \emph{aggregation} function $\Sigma^l$ to produce an aggregated vector $\boldsymbol{s}^l_i$, i.e., $\boldsymbol{s}^l_i=\mathlarger{\Sigma}^l_{v_j \in \mathcal{N}(v_i)}\boldsymbol{m}^l_{j,i}$.
+$\phi^l$ emits a message vector $\boldsymbol{m}^l_{j,i}$ for every edge $(v_j, v_i)$ at layer $l$, i.e., $\boldsymbol{m}^l_{j,i}=\phi^l(\boldsymbol{h}^l_i, \boldsymbol{h}^l_j, \boldsymbol{e}_{j,i})$.
+For $v_i$, the message vectors $\boldsymbol{m}^l_{x,j}$ of its adjacent edges ($v_x \in \mathcal{N}(v_i)$) are aggregated by the \emph{aggregation} function $\Sigma^l$ to produce an aggregated vector $\boldsymbol{s}^l_i$, i.e., $\boldsymbol{s}^l_i=\mathlarger{\Sigma}^l_{v_j \in \mathcal{N}(v_i)}\boldsymbol{m}^l_{j,i}$.
 $v_i$'s aggregated vector $\boldsymbol{s}^l_i$ and its hidden vector $\boldsymbol{h}^l_i$ from the previous GNN layer are fed into the \emph{vertex update} function $\gamma^l$ to calculate the output hidden vector $\boldsymbol{h}^{l+1}_i$ of the current layer $l$, i.e., $\boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \boldsymbol{s}^l_i)$
@@
 			$\begin{aligned}[t]
-			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
+			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_i^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
 			& \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l}) \\
@@
 
-\textbf{GGNN} ()
+\textbf{GGNN} (high vertex \& low edge computational complexity):
+GGNN introduces the gated recurrent unit (GRU) into the graph neural networks.
+The vertex update function $\phi$ of GGNN is a modified GRU unit that has 12 model parameters to learn, having high computational complexity.
+To lower the training cost, all GNN layers share the same group of parameters in GGNN.
+GGNN further requires the dimension of $\boldsymbol{h}^{l+1}$ is equal to the dimension of $\boldsymbol{h}^l$.
+
+\textbf{GAT} (low vertex \& high edge computational complexity):
+GAT introduces the attention mechanism into the graph neural networks.
+During the message passing, it dynamically determines the weight for an edge based on the hidden feature vectors of its two end vertices.
+Moreover, it adopts the multi-head mechanism that generates $K$ independent views for an edge, where $K$ is a hyperparameter.
+In its message function $\phi$, $\$

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
更正了GAT的j

--- 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 			$\begin{aligned}[t]
-			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
+			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_i^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
 			& \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l}) \\

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex

--- 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 			$\begin{aligned}[t]
-			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_i^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
+			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_i^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
 			& \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l}) \\

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
Update the functions of GAT.

@@
 			$\begin{aligned}[t]
-			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_i^l] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}}  \boldsymbol{h}_k^l] ))} \\
+			& \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))} \\
 			& \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l}) \\
@@
 \begin{table}
-	\hspace{-3em}
     \begin{footnotesize}
@@
 		\textbf{GAT}&
-		$\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
-		$O(1)$ \\
+		$\hat{\boldsymbol{h}}^{l,k}_{i}} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ (pre-edge), $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
+		$O(d_{in} * d_{out})$ \\
 		\textbf{GaAN} &
@@
 Moreover, it adopts the multi-head mechanism that generates $K$ independent views for an edge, where $K$ is a hyperparameter.
-In its message function $\phi$, $\$
+In its message function $\phi$.

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
更新GAT的公式
Finish section 2.

@@
 
-In this section, we introduce the concepts related to the graph neural network (GNN, for short) and breifly survey typical graph neural networks.
+In this section, we formally define the graph neural network (GNN, for short) and breifly survey typical graph neural networks.
 We denote a simple graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
@@
 			$O(d_{in} * d_{out})$                                                                                                       \\
-		\textbf{GAT}&
+			\textbf{GAT}                                                                                                              &
 			Attention                                                                                                                 &
@@
 				$\begin{aligned}[t]
-			&\alpha_{j, i}^k = \frac {\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l, k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}} \boldsymbol{h}_i^l] )} {\sum_{k \in \mathcal{N}(j)}\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}}  \boldsymbol{h}_k^l] )} \\
-			&\boldsymbol{m}_{j, i, 1}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}_v} \boldsymbol{h}_j^{l}) \\
-			&\boldsymbol{m}_{j, i, 2}^l = \textcolor{blue}{\boldsymbol{W}^l_m} \boldsymbol{h}_j^{l} \\
-			&\boldsymbol{m}_{j, i, 3}^l = \boldsymbol{h}_j^l
+						 & \alpha_{j, i}^k = \frac {\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l, k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}} \boldsymbol{h}_i^l] )} {\sum_{k \in \mathcal{N}(j)}\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}}  \boldsymbol{h}_k^l] )} \\
+						 & \boldsymbol{m}_{j, i, 1}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}_v} \boldsymbol{h}_j^{l})                                                                                                                                                                                                                                                                                               \\
+						 & \boldsymbol{m}_{j, i, 2}^l = \textcolor{blue}{\boldsymbol{W}^l_m} \boldsymbol{h}_j^{l}                                                                                                                                                                                                                                                                                                                                             \\
+						 & \boldsymbol{m}_{j, i, 3}^l = \boldsymbol{h}_j^l
 					\end{aligned}$
@@
 			ChebNet \cite{defferrad2016_chebnet}                                                                                                                                                                             &
-		$\boldsymbol{z}_i^{(k)} = 2\boldsymbol{s}^{(k)}_{i} - \boldsymbol{z}_i^{(k-2)}$&
+			$\boldsymbol{z}_i^{(k)} = 2\boldsymbol{s}^{(k)}_{i} - \boldsymbol{z}_i^{(k-2)}$                                                                                                                                  &
 			$O(d_{out})$                                                                                                                                                                                                       \\
@@
 						 & {\boldsymbol{z}}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^z \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^{sz} + \textcolor{blue}{\boldsymbol{U}}^z \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hz})                    \\
-			&\boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^r \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}}^{sr} +\textcolor{blue}{\boldsymbol{U}}^r \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hr}) \\
-			&\boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}}^h)) \\
-			&\boldsymbol{h}_i^{l+1} = (1 - {\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l + {\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
+						 & \boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^r \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}}^{sr} +\textcolor{blue}{\boldsymbol{U}}^r \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hr})                        \\
+						 & \boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}}^h)) \\
+						 & \boldsymbol{h}_i^{l+1} = (1 - {\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l + {\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
 					\end{aligned}$
@@
 			$O(d_{in} * d_{out})$                                                                                                                                                                                              \\
-		\textbf{GAT}&
-		$\hat{\boldsymbol{h}}^{l,k}_{i}} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ (pre-edge), $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
+			\textbf{GAT}                                                                                                                                                                                                     &
+			$\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ (pre-edge), $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$                                                         &
 			$O(d_{in} * d_{out})$                                                                                                                                                                                              \\
@@
 				$\begin{aligned}[t]
-			&\boldsymbol{g}_i = \textcolor{blue}{\boldsymbol{W}}^l_g  [\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i, 2}^l \parallel \boldsymbol{s}_{i, 3}^l]  \\
-			&\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l_o [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i, 1}^l) ]
+						 & \boldsymbol{g}_i = \textcolor{blue}{\boldsymbol{W}}^l_g  [\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i, 2}^l \parallel \boldsymbol{s}_{i, 3}^l] \\
+						 & \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l_o [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i, 1}^l) ]
 					\end{aligned}$
-		\end{scriptsize}&
+			\end{scriptsize}                                                                                                                                                                                   &
 			$O(max(K * d_v + d_{in}, 2 * d_{in} + d_m) * d_{out})$                                                                                                                                                             \\ \bottomrule
@@
 We classify the typical GNNs into four quadrants based on their edge/vertex complexity as shown in \figurename~\ref{fig:gnn_complexity_quadrant}.
-We pick GCN, GGNN, GAT and GaAN as the representative GNNs of the four quadrants.
+We pick GCN, GGNN, GAT and GaAN as the \emph{representative GNNs} of the four quadrants.
 
@@
 Moreover, it adopts the multi-head mechanism that generates $K$ independent views for an edge, where $K$ is a hyperparameter.
-In its message function $\phi$.
+GAT moves the vertex update function $\gamma$ before the edge computation.
+$\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ with $1 \leq k \leq K$ are conducted for every vertex $v_i$ before the message function $\phi$.
+$\phi$ uses $\hat{\boldsymbol{h}}^{l,k}_{i}$ to get the weight of each edge in every head $k$.
+After the edge computation, GAT uses the aggreated vector $\boldsymbol{s}^l_i$ directly as the output hidden vector.
+
+\textbf{GaAN} (high vertex \& edge computational complexity):
+Based on the multi-head machanism, GaAN introduces a convolutional subnetwork to control the weight of each head.
+Thus, it introduces more edge-related parameters to train.
+Moreover, GaAN aggregates three messages simutaneously, further increasing the edge computational complexity.
+
+\subsection{Sampling Techniques}
+
+By default, GNNs are trained in a full-batch way, using the whole graph in each iteration.
+The full-batch gradient descent has two disadvantages \cite{chiang2019_cluster_gcn}.
+It has to cache intermediate results of all vertices in the forward phase, which consumes lots of memory space.
+It updates the parameters only once for each epoch, slowing the convergence of gradient descent.
+
+To train GNNs in a mini-batch way, several sampling techniques \cite{chiang2019_cluster_gcn} are proposed.
+In each mini-batch, they sample a small subgraph from the whole graph $\mathcal{G}$ and uses the subgraph to update the model parameters.
+In other words, the sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:graph_sampling}.
+Inactive graph neurons and connetions do not participate in the training of this mini-batch, saving lots of computation and storage costs.
+Moreover, it may reduce the risk of overfitting the training graph.
+Based on whether different GNN layers sample different subgraphs, the existing sampling techniques can be devided into two groups \cite{zeng2020_graphsaint}: the neighbor sampling and the graph sampling.
+
+The neighbor sampling techniques \cite{hamilton2017_graphsage, ying2018_pinsage, chen2018_fastgcn, chen2018_sgcn, huang2018_adap} sample the subgraphs layer by layer.
+They first sample several vertices from $\mathcal{V}$ in the last GNN layer.
+Then they repeatedly sample the neighbors of those vertices in the previous layer until the input layer.
+The sampled subgraphs of different GNN layers may be \emph{different}, as shown in \figurename~\ref{fig:gnn_sampling_neigbhor_sampling}.
+GraphSAGE \cite{hamilton2017_graphsage} is the representative technique.
+For every sampled vertex $v_i$ in the GNN layer $l$, GraphSAGE samples at most $S^l$ neighbors of $v_i$ in the previous GNN layer.
+$S^l$ is the hyperparameter that is usually much smaller than $|\mathcal{V}|$.
+By this way, GraphSAGE limits the neighborhood sizes of the vertices in the sampled subgraph, especially high-degree vertices.
+
+\begin{figure}
+	\centering
+	\subfloat[Neighbor sampling\label{fig:gnn_sampling_neigbhor_sampling}]{\includegraphics[height=4cm]{figs/illustration/layer_sampling.png}}
+	%
+	\subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4cm]{figs/illustration/graph_sampling.png}}
+	\caption{Training a GNN with sampling techniques. The faded graph neurons and their connections are inactivated.}
+	\label{fig:gnn_sampling}
+\end{figure}
+
+The graph sampling techniques \cite{zeng2018_aesg, chiang2019_cluster_gcn, zeng2020_graphsaint} sample a subgraph for each mini-batch and use the same sampled graph for all GNN layers, as shown in \figurename~\ref{fig:gnn_sampling_graph_sampling}.
+They differ in the methods to sample subgraphs.
+The cluster sampler technique \cite{chiang2019_cluster_gcn} is the representative technique.
+Given a training graph $\mathcal{G}$, it partitions $\mathcal{G}$ into closely connected clusters.
+For each mini-batch, it randomly picks $K$ clusters, where $K$ is the hyperparameter.
+The technique ignores the inter-cluster edges and only keeps the intra-cluster edges in the subgraph.

### 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex

--- 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 		\textbf{GAT}&
-		$\hat{\boldsymbol{h}}^{l,k}_{i}} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ (pre-edge), $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
+		$\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ (pre-edge), $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$ &
 		$O(d_{in} * d_{out})$ \\
@@
 Moreover, it adopts the multi-head mechanism that generates $K$ independent views for an edge, where $K$ is a hyperparameter.
-In its message function $\phi$.
+GAT moves the vertex update function $\gamma$ before the edge computation. 
+$\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ with $1 \leq k \leq K$ are conducted for every vertex $v_i$ before the message function $\phi$.
+$\phi$ uses $\hat{\boldsymbol{h}}^{l,k}_{i}$ to get the weight of each edge in every head $k$.
+After the edge computation, GAT uses the aggreated vector $\boldsymbol{s}^l_i$ directly as the output hidden vector.
+
+\textbf{GaAN} (high vertex \& edge computational complexity):
+Based on the multi-head machanism, GaAN introduces a convolutional subnetwork to control the weight of each head.
+Thus, it introduces more edge-related parameters to train.
+Moreover, GaAN aggregates three messages simutaneously, further increasing the edge computational complexity.
+
+\subsection{Sampling Techniques}
+
+By default, GNNs are trained in a full-batch way, using the whole graph in each iteration.
+The full-batch gradient descent has two disadvantages \cite{chiang2019_cluster_gcn}.
+It has to cache intermediate results of all vertices in the forward phase, which consumes lots of memory space.
+It updates the parameters only once for each epoch, slowing the convergence of gradient descent.
+
+To train GNNs in a mini-batch way, several sampling techniques \cite{chiang2019_cluster_gcn} are proposed.
+In each mini-batch, they sample a small subgraph from the whole graph $\mathcal{G}$ and uses the subgraph to update the model parameters.
+In other words, the sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:graph_sampling}.
+Inactive graph neurons and connetions do not participate in the training of this mini-batch, saving lots of computation and storage costs.
+Moreover, it may reduce the risk of overfitting the training graph.
+Based on whether different GNN layers sample different subgraphs, the existing sampling techniques can be devided into two groups \cite{zeng2020_graphsaint}: the neighbor sampling and the graph sampling.
+
+The neighbor sampling techniques \cite{hamilton2017_graphsage, ying2018_pinsage, chen2018_fastgcn, chen2018_sgcn, huang2018_adap} sample the subgraphs layer by layer.
+They first sample several vertices from $\mathcal{V}$ in the last GNN layer.
+Then they repeatedly sample the neighbors of those vertices in the previous layer until the input layer.
+The sampled subgraphs of different GNN layers may be \emph{different}, as shown in \figurename~\ref{fig:gnn_sampling_neigbhor_sampling}.
+GraphSAGE \cite{hamilton2017_graphsage} is the representative technique.
+For every sampled vertex $v_i$ in the GNN layer $l$, GraphSAGE samples at most $S^l$ neighbors of $v_i$ in the previous GNN layer. 
+$S^l$ is the hyperparameter that is usually much smaller than $|\mathcal{V}|$.
+By this way, GraphSAGE limits the neighborhood sizes of the vertices in the sampled subgraph, especially high-degree vertices.
+
+\begin{figure}
+	\centering
+	\subfloat[Neighbor sampling\label{fig:gnn_sampling_neigbhor_sampling}]{\includegraphics[height=4cm]{figs/illustration/layer_sampling.png}}
+	%
+	\subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4cm]{figs/illustration/graph_sampling.png}}
+	\caption{Training a GNN with sampling techniques. The faded graph neurons and their connections are inactivated.}
+	\label{fig:gnn_sampling}
+\end{figure}

### 2020-07-14 Manuscript/sec3-experiment-design.tex
更新论文section 3.

\section{Experiment Design}

We design a series of experiments to find out the performance bottleneck in training graph neural networks.
We first introduce the experimental setting in Section~\ref{sec:experimental_env} and then give out our experimental scheme in Section~\ref{sec:experimental_scheme}.
The experiment results are presented and analyzed later in Section~\ref{sec:experiment_results}.

\subsection{Experimental Setting}
\label{sec:experimental_env}

\paragraph{Experimental Environment}
All the experiments were conducted in a CentOS 7 Linux server with the kernel version 3.10.0.
The server had 40 cores and 90 GB main meory.
The server was also equipped with a NVIDIA Tesla T4 GPU card with 16GB GDDR6 memory.
For the software environment, we adopted Python 3.7.7, PyTorch 1.5.0 and CUDA 10.1.
We implemented all the GNNs with PyTorch Geometric 1.5.0.
The execution time decomposition was collected with NVIDIA Nsight systems.

\paragraph{Dataset}
We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervise, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
For directed graphs, PyG converts them into undirected ones during the data loading.
Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
For an undirected graph, $\mathcal{E}$ already contains two-direction edges and $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
For the \texttt{cam} dataset, we generated random dense feature vectors.
Since we mainly focus on the training efficiency of GNNs instead of accuracies, we also used random graphs in the experiments.
To evaluate the effects of graph topological characteristics (like the average degree) on the performance bottleneck uniformly, we used the R-MAT graph generator \cite{rmat-generator}.
Input feature vectors of the random graphs were random dense vectors with the dimension of 32.
Vertices were divided into 10 classes randomly.

\begin{table}
    \centering
    \small
    \begin{tabular}{cccccccc}
        \toprule
        Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $|\boldsymbol{x}|$ & Sparsity & \#Class & Directed \\
        \midrule
        pubmed (pub) \cite{yang2016_revisiting_semisupervised}  & 19,717          & 44,324          & 4.5       & 500                & 0.90     & 3       & Yes      \\
        amazon-photo (amp) \cite{shchur2018_pitfall_of_gnn}     & 7,650           & 119,081         & 31.1      & 745                & 0.65     & 8       & Yes      \\
        amazon-computers (amc) \cite{shchur2018_pitfall_of_gnn} & 13,752          & 245,861         & 35.8      & 767                & 0.65     & 10      & Yes      \\
        coauthor-physics (cph) \cite{shchur2018_pitfall_of_gnn} & 34,493          & 247,962         & 14.4      & 8415               & 0.996    & 5       & Yes      \\
        flickr (fli) \cite{zeng2020_graphsaint}                 & 89,250          & 899,756         & 10.1      & 500                & 0.54     & 7       & No       \\
        com-amazon (cam) \cite{ang2012_defining}                & 334,863         & 925,872         & 2.8       & 32                 & 0.0      & 10      & No       \\
        \bottomrule
    \end{tabular}
    \caption{Dataset overview. $\bar{d}$ represents the average vertex degree. $|\boldsymbol{x}|$ is the dimension of the input feature vector. The sparsity is the proportion of zero elements in the input feature vectors.}
    \label{tab:dataset_overview}
\end{table}

\paragraph{Learning Task}
We used the node classification as the target task in GNNs due to its popularity in real-world applications.
We trained GNNs with the semi-supervised learning setting.
The whole data graph was used in the forward/backward/evaluation phases, but only parts of vertices had labels during the forward phase and they were used to calculate the loss and gradients.
The remaining vertices were used in the evaluation phsae to check the accuracy of the current parameters.
Since model parameters of GNNs were not restricted by the topological structure of $\mathcal{G}$, the model learned from the semi-supervised learning can directly extrapolate to unseen vertices.

\paragraph{GNN Implementation}
We implemented the four typical GNNs--GCN, GGNN, GAT, GaAN--with PyTorch Geometric 1.5.0.
To compare the performance characteristics of four GNNs side-by-side, we used a unified GNN structure for them: Input Layer $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ Softmax Layer (to prediction).
The structure was popular in the experimental evaluation of GCN \cite{kipf2017_gcn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan}.
Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, we added two MLP layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.

\paragraph{Hyper-parameters}
We picked the hyper-parameters of all GNNs according to their popularity in the experimental evaluation in their original papers.
We use $|\boldsymbol{v}|$ to denote the dimension of a vector $\boldsymbol{v}$.
For GCN/GAT/GaAN, $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, i.e. the input feature vector.
$|\boldsymbol{h}^1_i|$ was 64 and $|\boldsymbol{h}^2_i|$ was the number of classes.
For GGNN, $|\boldsymbol{h}^0_i| = |\boldsymbol{h}^1_i| = |\boldsymbol{h}^2_i| = 64$.
We used 8 heads in GAT and GaAN.
$d_{head}=8$ in GAT.
$d_a=d_v=8$ and $d_m=64$ in GaAN.

\subsection{Experimental Scheme}
\label{sec:experimental_scheme}

### 2020-07-14 Manuscript/sec4-experiments.tex
更新论文section 3.

\section{Experiment Results and Analysis}
\label{sec:experiment_results}

### 2020-07-14 Manuscript/sec3-experiment-design.tex

@@
 The whole data graph was used in the forward/backward/evaluation phases, but only parts of vertices had labels during the forward phase and they were used to calculate the loss and gradients.
-The remaining vertices were used in the evaluation phsae to check the accuracy of the current parameters.
-Since model parameters of GNNs were not restricted by the topological structure of $\mathcal{G}$, the model learned from the semi-supervised learning can directly extrapolate to unseen vertices.
+The vertices with unseed labels were used in the evaluation phsae to check the accuracy of the current parameters.
+%Since model parameters of GNNs were not restricted by the topological structure of $\mathcal{G}$, the model learned from the semi-supervised learning can directly extrapolate to unseen vertices.
 
@@
 The structure was popular in the experimental evaluation of GCN \cite{kipf2017_gcn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan}.
-Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, we added two MLP layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
+Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, for GGNN, we added two MLP layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
 

### 2020-07-14 Manuscript/sec3-experiment-design.tex
Update section 3.

@@
 We trained GNNs with the semi-supervised learning setting.
-The whole data graph was used in the forward/backward/evaluation phases, but only parts of vertices had labels during the forward phase and they were used to calculate the loss and gradients.
+All veritces and their input feature vectors were used used, but only parts of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
 The vertices with unseed labels were used in the evaluation phsae to check the accuracy of the current parameters.
@@
 Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, for GGNN, we added two MLP layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
+We stored the dataset and the model parameters in the memory of GPU.
+We conducted all the training on GPU.
 
 \paragraph{Hyper-parameters}
-We picked the hyper-parameters of all GNNs according to their popularity in the experimental evaluation in their original papers.
+We picked the hyper-parameters of allupdated GNNs according to their popularity in the experimental evaluation in their original papers.
 We use $|\boldsymbol{v}|$ to denote the dimension of a vector $\boldsymbol{v}$.
@@
 \label{sec:experimental_scheme}
+
+To find out performance bottleneck in GNN training, we decompose the bottleneck analysis into four questions.
+The answers to those questions will give us a more comprehensive view on the performance characteristics of GNN training.
+We design extensive experiments to find the answers emperically.
+\begin{itemize}
+
+	\item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?}
+	\begin{itemize}
+		\item Every GNN has a group of hyper-parameters like the number of GNN layers and the dimision of hidden feature vectors.
+The hyper-parameters affect the training time per epoch and the peak memory usage during the training.
+
+		\item To evaluate their effects, we measured how the training time per epoch and the peak memory usage (of GPU) changed as we increased the values of the hyper-parameters.
+
+		\item Through the experiments, we want to verify the validity of the computational complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
+		If the complexity analysis is valid, we can analyze the bottleneck theoretically.
+	\end{itemize}
+
+	\item[Q2] \emph{Which stage is the most time-consuming stage in GNN training?}
+	\begin{itemize}
+		\item We can decompose the training time on different levels: layer level, vertex/edge computation level and the basic operator level.
+		\item On each level, we breakdown the training time of an epoch into several stages.
+The most time-consuming stage is the performance bottleneck in time.
+Optimizing its implementation can significantly reduce the training time.
+	\end{itemize}
+	\item[Q3] \emph{Which factor prevents us training GNNs on big graphs?}
+	\begin{itemize}
+		\item 
+	\end{itemize}
+	\item[Q4] \emph{Can the sampling techniques remove the performance bottleneck in GNN training?}
+\end{itemize}

### 2020-07-14 Manuscript/sec3-experiment-design.tex
Update section 3.

@@
 
-To find out performance bottleneck in GNN training, we decompose the bottleneck analysis into four questions.
+To find out performance bottleneck in GNN training, we conduct the bottleneck analysis with four questions.
 The answers to those questions will give us a more comprehensive view on the performance characteristics of GNN training.
@@
 	\item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?}
-	\begin{itemize}
-		\item Every GNN has a group of hyper-parameters like the number of GNN layers and the dimision of hidden feature vectors.
+
+			Every GNN has a group of hyper-parameters like the number of GNN layers and the dimision of hidden feature vectors.
 The hyper-parameters affect the training time per epoch and the peak memory usage during the training.
-
-		\item To evaluate their effects, we measured how the training time per epoch and the peak memory usage (of GPU) changed as we increased the values of the hyper-parameters.
-
-		\item Through the experiments, we want to verify the validity of the computational complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
+			To evaluate their effects, we measured how the training time per epoch and the peak memory usage (of GPU) changed as we increased the values of the hyper-parameters.
+			Through the experiments, we want to verify the validity of the computational complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
 			If the complexity analysis is valid, we can analyze the bottleneck theoretically.
-	\end{itemize}
 
 	\item[Q2] \emph{Which stage is the most time-consuming stage in GNN training?}
-	\begin{itemize}
-		\item We can decompose the training time on different levels: layer level, vertex/edge computation level and the basic operator level.
-		\item On each level, we breakdown the training time of an epoch into several stages.
-The most time-consuming stage is the performance bottleneck in time.
+
+			We can decompose the training time on different levels: layer level, vertex/edge computation level and the basic operator level.
+			On each level, we breakdown the training time of an epoch into several stages. The most time-consuming stage is the performance bottleneck in time.
 			Optimizing its implementation can significantly reduce the training time.
+
+	\item[Q3] \emph{Which consumes most of memory in GNN training?}
+
+			The limited memory capacity of a GPU card is the main factor preventing us training GNNs on big graphs.
+			We measured the peak memory usage in the GNN training under different graph scales, hyper-parameters and average vertex degrees.
+			Based on the results, we analyze which is the most memory-consuming component.
+			Reducing its memory usage will enable us training bigger GNNs under the same memory capacity.
+
+	\item[Q4] \emph{Can the sampling techniques remove the performance bottleneck in GNN training?}
+
+			In theory, the sampling techniques can significantly reduce the graph neurons that participate in the training of a batch.
+			Consequently, the training time and the memory usage should also decrease.
+			To validate the effectiveness of the sampling techniques, we measured the training time and peak memory usage under different batch sizes.
+			If the sampling techniques are effective, they are the keys to conduct GNN training on very big graphs.
+			If they are not effective, we want to find out which impairs its efficiency.
 \end{itemize}
-	\item[Q3] \emph{Which factor prevents us training GNNs on big graphs?}
-	\begin{itemize}
-		\item 
-	\end{itemize}
-	\item[Q4] \emph{Can the sampling techniques remove the performance bottleneck in GNN training?}
-\end{itemize}

### 2020-07-14 Manuscript/sec3-experiment-design.tex
Add sketch of Section 4.

@@
 
-	\item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?}
+	\item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
 
@@
 
-	\item[Q2] \emph{Which stage is the most time-consuming stage in GNN training?}
+	\item[Q2] \emph{Which stage is the most time-consuming stage in GNN training?} (Section~\ref{sec:training_time_breakdown})
 
@@
 
-	\item[Q3] \emph{Which consumes most of memory in GNN training?}
+	\item[Q3] \emph{Which consumes most of memory in GNN training?} (Section~\ref{sec:memory_usage_analysis})
 
@@
 
-	\item[Q4] \emph{Can the sampling techniques remove the performance bottleneck in GNN training?}
+	\item[Q4] \emph{Can the sampling techniques remove the performance bottleneck in GNN training?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
 

### 2020-07-14 Manuscript/sec4-experiments.tex
Add sketch of Section 4.

@@
 \label{sec:experiment_results}
+
+In this section, we answers the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
+
+\subsection{Effects of Hyper-parameters on Performance}
+\label{sec:effects_of_hyper-parameters_on_performance}
+
+\subsection{Training Time Breakdown}
+\label{sec:training_time_breakdown}
+
+\subsection{Memory Usage Analysis}
+\label{sec:memory_usage_analysis}
+
+\subsection{Effects of Sampling Techniques on Performance}
+\label{sec:effects_of_sampling_techniques_on_performance}

### 2020-07-14 Manuscript/sec6-related-work.tex
更新了sec6-related-work

\section{Related Work}

In this section, we brefily review the graph neural network models survey (GNNs survey), 
graph neural network system(GNN system) and GNNs performance bottleneck analysis work.

\subsection{GNNs survey}
GNNs survey: Zhou et al \cite{zhou2018_gnn_review}, Zhang et al \cite{zhou2018_gnn_review} and Wu et al \cite{comprehensive-survey-wu-2020} 
surveyed existing graph neural works models in different categorizations and viewpoints and provided a comprehensive review about GNNs' model 
architecture, principle and application. Dwived et al \cite{dwivedi2020_benchmark_of_gnn} discussed the performance of different GNN algorithms 
under the graph dataset of different scenes, and gived the key operators of designing effective GNNs in different scenarios. 
However, these efforts are focused on the GNN algorithm itself and accuracy, without a detailed analysis of memory usage and running time.

\subsection{GNN system}
PyG \cite{PyG}, DGL \cite{DGL} designed the graph neural network system based on the message-passing model. 
PyG \cite{PyG} built upon PyTorch and obtained high data throught with sparse GPU accleration by providing dedicated CUDA kernels 
and mini-batch technologies. DGL \cite{DGL} supported a variety of computing backends (Tensorflow, MXNet, PyTorch) and leveraged
fusion kernel techniques, which combine message function with update function to provide further performance improvements compared to PyG \cite{PyG}. 
NeuGraph \cite{ma2019_neugraph} proposed a new programming model, SAGA-NN(Scatter-ApplyEdge-Gather-ApplyVertex with Neural Networks), and achieved excellent
performance in a single machine with mutliple GPUs by using graph computation optimization such as data partitioning management, scheduling and parall mutli-gpu processing.
AliGraph \cite{zhu2019_aligraph} targetd at Attributed Heterogeneous Graph data model, disassembed each layer of GNN into there basic operations: Sampling, Aggregate and Combine,
and leveraged graph parition, spearate storage of attributes and the importance-base vertex caching strategy in storage layer. 
In general, various optimization techniques are used in these GNN systems' design, but whether these optimization techniques match the bottlenecks of GNN performance is a question
worth studying.

\subsection{GNNs performance bottleneck analysis work}
Yan et al \cite{yan2020_analysis_gcns_gpu} compared the performance characteristics of GNN algorithms, Graph Processing and MLP-based Neural Network, provided guidelines in software optimizaton and hardware optimization.
Zhang et \cite{zhang2020_analysis_neugraph} characterized the GNN computation at the inference stage based on SAGA-NN (Scatter-ApplyEdge-Gather-ApplyVertex with Neural Networks) programming model, 
and found that GNN computation has no fixed performance bottlenecks, and believed that each part has the value of optimization. 
Compared to their works, the classification angle of our work is unique, and neither of their works consider the graph scalabilty and the access of sampling technology,
which coverred in this paper.

### 2020-07-14 Manuscript/sec4-experiments.tex
完成了4.1节的书写

@@
 \label{sec:effects_of_hyper-parameters_on_performance}
+
+The goal of this experiment is to verify the accuracy of complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex} 
+by observing the effects the hyper-parameters of the GNN on training time-consuming and memory usage.
+
+\begin{figure}
+	\centering
+    \subfloat[pubmed\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.png}}
+    \subfloat[amazon-photo\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.png}}
+    \subfloat[coauthor-physics\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.png}} \\
+    \subfloat[amazon-computers\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.png}}
+    \subfloat[flickr\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.png}}
+    \subfloat[com-amazon\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.png}}
+    \caption{Different Datasets's absolute training time per epoch in four GNN models. (total 50 epochs)}
+	\label{fig:exp_absolute_training_time}
+\end{figure}
+
+Fig~\ref{fig:exp_absolute_training_time} compares the training time per epoch for each GNN model, the ranking is $\boldsymbol{GaAN} \gg \boldsymbol{GAT} > \boldsymbol{GGNN} > \boldsymbol{GCN}$.
+Its time-consuming ranking is consistent with the complexity analysis because the number of edges in the graph generally far exceeds the number of nodes, 
+the GAT algorithm with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
+Fig~\ref{fig:exp_absolute_training_time} shows that the training time of individual epochs is abnormally high, which is mainly caused by profiling overhead and the GC pause of the Python interpreter.
+This phenomenon confirms the necessity of removing abnormal epochs.
+
+According to Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN is linearly related to the 
+hyper-parameters of each model(such as $d_{dims}$, $K$, etc). In order to vertex this linear relationship, we measured the change of the training time of each GNN with the hyperparameters.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.png}
+    \caption{GCN}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}
+    \caption{GGNN}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
+\end{figure}
+
+The computational complexity of GCN and GGNN is affected by the hidden vector dimension $d_{dim}$. $d_{dim}$ affects both the output hidden vector dimension fo Layer0 and
+the input hidden vector dimension of Layer1(ie $d_{dim} = d^0_{out} = d^1_{in}$).
+Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}, Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
+show that the training time of GCN and GGNN is affected by $d_{dim}$. As $d_{dim}$ increases, the training time increases linearly.
+
+GAT uses a multi-head mechanism, and its computational complexity is affected by the input hidden vector dimension $d_{in}$, the hidden vector dimension $d_{head}$ of each head, and the number of heads $K$.
+The output hidden vector dimension of each layer is $d_{out}=K d_{head}$.
+Because in the GAT model $d^1_{in}=d^0_{out}$, adjusting $d_{head}$ and $K$ is equivalent to adjusting Layer1’s $d^1_{in}$.
+Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time is affected by the hyperparameters $d_{head}$ and $K$, 
+GAT training time increases linearly with $d_{head}$ and $K$.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}
+    \caption{GAT}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
+\end{figure}
+
+GaAN also uses a multi-head mechanism, and its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
+Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is affected by hyperparameters.
+The experiment verifies the complexity analysis results given in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}.
+The training time of each GNN algorithm increases linearly with the increase of hyperparameters.
+When the hidden vector dimension $d_(in)$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time, resulting in an insignificant change in the total training time.
+When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}
+    \caption{GaAN}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
+\end{figure}
+
+Fig~\ref{fig:exp_hyperparameter_memory_usage} also shows how each GNN's use of GPU memory varies with the algorithm's hyperparameters.
+With the increase of hyperparameters, GNN's memory usage has also increased linearly.
+
+\begin{figure}
+	\centering
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.png}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.png}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.png}}\\
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
+    \caption{The memory Usage of each GNN Model in different hyperparameter}
+	\label{fig:exp_hyperparameter_memory_usage}
+\end{figure}
+
+The experiment verifies the effectiveness of the complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}.
+\textbf{GNN training time and memory usage are linearly related to hyperparameters}.
+This allows algorithm engineers to use larger hyperparameters to increase the complexity of GNN Without worrying about the time-consuming training and the explosive growth of memory usage.
 

### 2020-07-14 Manuscript/sec4-experiments.tex
粗略地完成了sec4

@@
 
-According to Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN is linearly related to the 
-hyper-parameters of each model(such as $d_{dims}$, $K$, etc). In order to vertex this linear relationship, we measured the change of the training time of each GNN with the hyperparameters.
+According to Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN model is linearly related to the 
+hyper-parameters of each model(such as $d_{dims}$, $K$, etc). In order to vertex this linear relationship, we measured the change of the training time of each GNN model with the hyperparameters.
 
@@
 The experiment verifies the complexity analysis results given in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}.
-The training time of each GNN algorithm increases linearly with the increase of hyperparameters.
+The training time of each GNN model algorithm increases linearly with the increase of hyperparameters.
 When the hidden vector dimension $d_(in)$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time, resulting in an insignificant change in the total training time.
@@
 
-Fig~\ref{fig:exp_hyperparameter_memory_usage} also shows how each GNN's use of GPU memory varies with the algorithm's hyperparameters.
+Fig~\ref{fig:exp_hyperparameter_memory_usage} also shows how each GNN model's use of GPU memory varies with the algorithm's hyperparameters.
 With the increase of hyperparameters, GNN's memory usage has also increased linearly.
@@
 
+The goal of this experiment is to discover the computational performance bottleneck in GNN training
+by decomposing the time-consuming training.
+
+\paragraph{vertex/edge calculation time-consuming proportion analysis}
+
+For vertex calculation and edge calculation, Fig~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers in each algorithm
+to the total training time (including forward, backward and evaluation stages). The GCN algorithm takes the most time to calculate on most datasets, 
+only the cph dataset is a special case, because the dimension of the input feature vector of this dataset is very high, resulting in the 
+high vertex calculation time-consuming of Layer0. Because of its high vertex calculation complexity, GGNN makes its vertex calculation time-consuming\
+ratio significantly higher than other algorithms, but on most datasets, edge calculation still occupies the main calculation time-consuming. 
+Only in pub and cam dataset, the edge calculation cost and the vertex calculation cost are close, because the average degree of the two datasets is low (only 4.5 and 2.8).
+For the GAT and GaAN algorithms, because of their high edge calculation complexity, their edge calculation cost Time is absolutely dominant. 
+In summary, \textbf{edge calculation is the main time-consuming factor of GNN training}, especially in the case of more complicated edge calculation.
+
+\begin{figure}
+	\centering
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gcn.png}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_ggnn.png}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gat.png}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gaan.png}}
+    \caption{The vertex calculation and edge calculation of each GNN Model}
+	\label{fig:exp_vertex_edge_cal_proportion}
+\end{figure}
+
+Experiments also show that \textbf{the average degree of the dataset affects the time-consuming proportion of vertex/edge calculation}. 
+Our fixed graph has 50k vertices, and the R-MAT generator is used to generate a random graph with an average degree between 10 and 100.
+We measure the change of the time-consuming proportion of the vertex/edge calculation in each GNN model varies with the average degree of the graph,
+as shown in Fig~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}. The time calculation of the edge increases linearly with the increase of the average degree,
+\textbf{The time calculation of the edge calculation dominates the entire calculation time in most cases}. 
+Only when the vertex calculation complexity is very high and the average degree is very low, the vertex calculation time can overtake the edge calculation time.
+Therefore, the focus of \textbf{GNN training optimization should improve the efficiency of edge calculation}.
+
+\begin{figure}
+	\centering
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.png}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_ggnn.png}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gat.png}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.png}}
+    \caption{The vertex calculation and edge calculation of each GNN Model}
+	\label{fig:exp_avg_degree_on_vertex_edge_cal_time}
+\end{figure}
+
+\paragraph{Time-consuming decomposition analysis of edge calculation}
+The edge calculation phase can be further decomposed into four steps of collect, message, aggregate and update,
+as shown in Fig~\ref{fig:steps_in_edge_calculation}. The figure shows the $l$ layer The edge calculation process of GNN.
+edge index is a matrix that holds the size of the edge set of the graph as $M*2$, where $M$ is the number of edges of the graph,
+and the two columns of the matrix respectively store the source vertex and the target vertex of each edge.
+The edge index remains unchanged throughout the calculation process.
+The collect step is used to prepare the data structure required for edge calculation.
+This step will input the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \ leq N)$
+is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the input edge calculation function $\phi$
+(including $\boldsymbol{h}_i^l$,$\boldsymbol{h}_j^ l$ and $\boldsymbol{e}_{j, i}^l$).
+There is no calculation in this step, only data access is involved. The message step calls the function given by the user $\phi$ to
+complete the edge calculation process, and get each The message vector of each edge $\boldsymbol{m}_{j, i}^l (\boldsymbol{e}_{j, i}^l \in E(G))$.
+The aggregate step is based on the target of each edge, the message vector with the same target vertex is aggregated by the aggregation operator $\Sigma$,
+and each vertex aggregation vector $\boldsymbol{a}_i^l (1 \leq i \leq N)$ is obtained. 
+The last update The step is optional, and it can perform additional correction processing on the aggregated vector (for example, adding bias to GCN).
+The aggregated vector $a_i^l$ after the update process will be input into the vertex calculation function $\gamma$ As an input parameter.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
+    \caption{Steps in edge calculation}
+    \label{fig:steps_in_edge_calculation}
+\end{figure}
+
+We performed the execution time decomposition of the edge calculation process of each GNN algorithm on different datasets,
+and the results are shown in Fig~\ref{fig:exp_edge_calc_decomposition}.
+The time-consuming decomposition of the edge calculation of each GNN is relatively stable, 
+and the dataset correlation is not strong. Although the collect step only performs data preparation,
+it occupies a lot of execution time in all GNNs. For the message step, in the GNN (GAT and GaAN) with high edge calculation complexity, 
+Which occupies the absolute dominant. Although its side calculation in GCN only has a simple multiplication operation, it still takes more than 20\% of the time; 
+In GGNN, because its side calculation function $\boldsymbol{m}_{j,i }^l=\boldsymbol{W}^l\boldsymbol{h}_{j}^l$ is only related to the source vertex, 
+so in the implementation of PyG will be $\boldsymbol{W}^l\boldsymbol{h}_j The calculation of ^l$ is carried out before the edge calculation starts
+(because this part of the calculation is only related to vertices, so we count the calculation into the vertex calculation phase),
+the calculated result is cached, and it is directly read when the message step is performed The result is that the message step of GGNN takes 0.
+For the aggregate step, it occupies at least 35\% of the time-consuming GNN (GCN and GGNN) with low computational complexity,
+while the GNN with high computational complexity ( GAT and GaAN), whose time consumption is close to the collect step,
+and both are much lower than the message step. Experiments show that \textbf{for an algorithm with high edge calculation complexity,
+the message step is the bottleneck of its performance, and it should be optimized}; and \textbf{For algorithms with low computational complexity,
+optimizing the collect and aggregate steps can significantly reduce training time}.
+
+\begin{figure}
+	\centering
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gcn.png}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_ggnn.png}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gat.png}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.png}}
+    \caption{The vertex calculation and edge calculation of each GNN Model}
+	\label{fig:exp_edge_calc_decomposition}
+\end{figure}
+
+\paragraph{Hot-spot operator analysis}
+Various functions for vertex/edge calculation $\phi, \Sigma,\gamma$ consist of a series of basic operators,
+which are mapped to specific basic operators on the GPU (Matrix multiplication mm, elementwise\_kernel multiplied by number of elements and index\_select selected by index.)
+
+Figure~\ref{fig:exp_top_basic_ops} shows the five operators with the highest time-consuming proportion in each GNN, 
+the operator in the legend The order is determined by the average time-consuming ratio.
+
+\begin{figure}
+	\centering
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gcn.png}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_ggnn.png}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gat.png}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gaan.png}}
+    \caption{The time-consuming ratio of basic operators (including the forward, backward and evaluation stages)}
+	\label{fig:exp_top_basic_ops}
+\end{figure}
+
+The analysis of the time-consuming operators of each algorithm is as follows:
+
+\begin{enumerate}
+    \item The matrix multiplication operator mm in GCN is mainly used for vertex calculation $\gamma$, 
+    this operator is particularly time-consuming on the cph dataset, 
+    because the dimensionality of the vertex feature vector input by cph is very high,
+    making the matrix multiplication in the vertex calculation of Layer0 The calculation is very high.
+    Mul is the multiplication operation in the edge calculation function $\phi$.
+    Both scatter\_add and gather are used to implement the aggregation step $\Sigma$ in the edge calculation,
+    where the former is used in the forward stage and the latter is used in backward Phase.
+    The index\_select operator is used in the collect step of the edge calculation.
+    For the GCN algorithm, the edge calculation related operators occupy the main time-consuming.
+    The time-consuming among the operators is relatively average, and there is no particularly outstanding performance bottleneck.
+    \item The most time consuming in GGNN is also the matrix multiplication mm operator,
+    which is mainly used for the vertex calculation function $\gamma$. The scatter\_add, index\_select and gather operators
+    are used for edge calculations. And the \_thnn\_fused\_gru\_cell is used in the backward calculation of GRU.
+    GGNN because of vertices With the increase in calculation complexity, the time-consuming time of the mm operator has increased significantly.
+    \item The four most time-consuming operators in GAT are all related to the edge calculation. 
+    Mul, \_index\_put\_impl and sum are used to implement the edge calculation function $\phi$.
+    The index\_select operator is used in the collect phase of the edge calculation. 
+    The mm operator is used vertex calculation function $\gamma$.
+    \item The most time-consuming matrix multiplication operator mm in GaAN is used for both edge calculation and edge calculation,
+    where edge calculation is dominant. Mul and cat are used for the $\phi$ function in edge calculation.
+\end{enumerate}
+
+In terms of commonality, 
+\textbf{The main time-consuming of GNN calculation is still matrix multiplication mm, multiplication of mul and other operators by the number of elements},
+so it is very suitable for calculation with GPU. Although the calculation of the aggregate step in edge calculation is relatively simple,
+but Because it involves data synchronization and non-regular calculations (the degree of different vertices is very different),
+the related operators scatter\_add and gather still occupy a certain amount of time.
+Although the collection step in the side calculation does not have any calculations,
+but the related calculations The index\_select operator still accounts for about 10\% of the time-consuming.
+\textbf{aggregate step and collect step are one of the computational performance bottlenecks of all GNN training},
+optimizing the corresponding operator will improve the training efficiency of all GNNs.
+
+\paragraph{Summary of performance bottlenecks}
+
+\begin{itemize}
+    \item \textbf{The performance bottleneck of GNN training is affected by the average degree of the dataset}. 
+    Because the average degree of most real-world graphs is above 10 degrees \cite{network-repository}, 
+    the performance bottleneck of GNN training will be concentrated on the edges Calculation section.
+    \item \textbf{According to the calculation complexity of the edge calculation function $\phi$, the performance bottleneck of GNN in edge calculation is different}:
+    \begin{itemize}
+        \item If the computational complexity of $\phi$ is high, the performance bottleneck is concentrated on the basic operators used to implement $\phi$.
+        Optimizing the implementation of the corresponding basic operators will improve the training performance of this type of GNN.
+        Taking GAT as an example, The most time-consuming operator \_index\_put\_impl in GAT is mainly used in the backward stage of the softmax calculation ($\alpha^k_{ij}$) in $\phi$,
+        which only involves data movement.
+        The optimized softmax implementation on the GPU can Significantly reduce GAT training time.
+        \item If the computational complexity of $\phi$ is low, the collect and aggregate steps in its side calculations are bottlenecks in computational performance.
+The collect step only involves a large amount of data movement.
+The aggregate step calculation is relatively simple (such as sum/average/maximum) Value, etc.), but because it involves data synchronization and irregular calculation, its time-consuming is still significant.
+         Optimizing the implementation of these two steps on the GPU will improve the training performance of this type of GNN.
+    \end{itemize}
+\end{itemize}
+
 \subsection{Memory Usage Analysis}
+
+At present, all data (including datasets and intermediate calculation results) of PyG in the process of training GNN with GPU
+are stored in GPU memory. Compared with the main memory of the system, the memory capacity on GPU is very limited.
+\textbf{GPU memory capacity is limited to Determinants of the size of the training dataset}. 
+GaAN was unable to complete the training due to memory overflow during the training of the `cph` dataset.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_usage_stage_amp.png}
+    \caption{Figure: Maximum memory usage in each stage. Data Load refers to memory usage after data is loaded. Data set: amp. Other datasets are similar}
+    \label{fig:exp_memory_usage_stage_amp}
+\end{figure}
+
+Fig~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each stage when each GNN is trained on the cam dataset, the situation is similar on other datasets.
+\textbf{The memory usage in GNN training is forward The peak in the phase and the backward phase}, 
+because a large number of temporary calculation results will be generated in the forward phase,
+and the key intermediate calculation results will be cached.
+The cached intermediate results will be used in the gradient calculation of the backward phase.
+Fig~\ref{fig:ggnn_vertex_func_computation_graph} shows the calculation graph of GGNN's vertex calculation function $\gamma$.
+It can be seen that a large number of operators are involved in GGNN vertex calculation and a large number of intermediate calculation results are generated.The key calculation results will also be cached,
+which is exacerbated Memory usage. Most of the peak memory usage in the loss phase comes from the intermediate calculation results of the cache.
+With the end of the backward phase, the memory of the intermediate calculation results is released.
+In the evaluation phase, there is no need to cache intermediate results for gradient calculations, Peak memory usage dropped significantly.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/illustration/ggnn_vertex_func_computation_graph.png}
+    \caption{The calculation graph of the GGNN vertex calculation function $\gamma$. The output of the Cached Operator will be cached for gradient calculation in the backward process}
+    \label{fig:ggnn_vertex_func_computation_graph}
+\end{figure}
+
+It is worth noting that *the peak memory during GNN training far exceeds the memory usage of the dataset itself.
+The ratio of the highest peak memory usage during our training compared to the memory usage after Data Load is
+defined as the memory expansion ratio. Fig~\ref{fig:exp_memory_expansion_ratio} compares the memory expansion ratios
+of different GNNs on different datasets. The expansion ratio of GCN is the lowest, between 5-14 times,
+and the expansion ratio of GaAN is the highest, up to 101 times
+\textbf{Very high expansion ratio severely limits the data scalability of GNN, making GPU unable to process large-scale graph datasets},
+especially restricting GNN with high edge calculation complexity.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio.png}
+    \caption{The proportion of memory expansion of each GNN on different datasets.}
+    \label{fig:exp_memory_expansion_ratio}
+\end{figure}
+
+Fig~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
+Because the input feature dimension of the cph data set is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
+of the graph is much higher than the matrix size of the intermediate calculation result of the cache, 
+so its expansion ratio is particularly low, and the cam data set is the opposite. In order to measure the effect of the input feature vector dimension on the memory
+expansion ratio , We randomly generated feature vectors of specific dimensions for different datasets.
+Fig~\ref{fig:exp_memory_expension_ratio_input_feature_dimension} shows the change in the expansion ratio under different input feature vector dimensions.
+\textbf{In the same GNN structure and hyperparameter settings, using a higher-dimensional input feature vector can reduce memory expansion ratio} .
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.png}
+    \caption{The change of the memory expansion ratio with the dimension of the input feature vector. Data set: cam, other datasets are similar}
+    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
+\end{figure}
+
+Different GNNs have different vertex/edge calculation complexity, and the scale of the generated intermediate results has different sensitivity
+to the number of vertices/edges in the graph, resulting in the memory expansion ratio being affected by the average degree of the graph.
+We measured the GPU peak memory The usage and expansion ratios are affected by the scale of the graph.
+
+In the case of a fixed number of vertices in the graph, we use the R-MAT generator to generate random graphs with different average degrees (number of edges).
+The Fig~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage during training varies with the average degree.
+\textbf{As the average degree increases, the peak memory usage increases linearly.
+The intermediate results generated by the side calculation gradually dominate, and the memory expansion ratio of each GNN gradually stabilizes}. 
+The expansion ratio is affected by the complexity of the side calculation.
+Except for GGNN, the memory expansion ratio of other GNNs increases with the increase of degree. GGNN has a high vertex calculation complexity.
+When the average degree is low, its memory expansion ratio is mainly affected by the intermediate results of vertex calculation;
+when the average When the degree is increased, the memory expansion ratio is gradually determined by the edge calculation complexity.
+Because GGNN has the lowest edge calculation complexity, its stable expansion ratio is the lowest.
+
+\begin{figure}
+    \centering
+    \subfloat[]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_peak_memory.png}}
+    \subfloat[]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_expansion_ratio.png}}
+    \caption{The change of memory usage with the average degree of the graph (R-MAT random graph, the number of vertices is fixed at 10k, and the input feature vector dimension is 32}
+    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
+\end{figure}
+
+In the case of a fixed number of edges in the graph, we use the R-MAT generator to generate random graphs with different numbers of vertices
+Fig~\ref{@fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows the change of memory usage with the number of vertices during training.
+Except for GGNN, the number of vertices increases, the number of vertices increases, the number of vertices increases,
+and the number of vertices increases. The size of the eigenvector matrix of the vertex input becomes larger, 
+but the peak memory usage only increases slightly, which makes the proportion of memory expansion decrease to a certain extent. 
+Only GGNN has a large number of intermediate calculation results during the vertex calculation process because of the high vertex calculation complexity. 
+The memory expansion factor has a small increase. The experimental data shows that \textbf{the intermediate result produced by the edge calculation is the dominant factor
+in memory usage, and the peak memory usage of each GNN increases linearly with the increase in the number of edges}.
+
+\begin{figure}
+    \centering
+    \subfloat[]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_peak_memory.png}}
+    \subfloat[]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_expansion_ratio.png}}
+    \caption{Memory usage changes with the number of graph vertices (R-MAT random graph, the number of edges is fixed at 500k, and the input feature vector dimension is 32)}
+    \label{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge}
+\end{figure}
+
+\paragraph{Bottleneck restricting data scalability}
+\begin{itemize}
+    \item \textbf{GPU memory capacity is the decisive factor limiting the scalability of the training dataset}.
+    \item \textbf{GPU memory usage mainly comes from the intermediate calculation results generated during the calculation process,
+     especially the intermediate calculation results of the edge calculation*. Because part of the intermediate calculation results
+    will be cached to participate in backward calculation, high GPU memory usage runs through the forward and backward stages.}
+    \item \textbf{GNN's peak memory usage during training can reach tens or even hundreds of times the size of the input data}.
+The limited memory capacity of the GPU severely limits the size of the input data that can be trained.
+    \item \textbf{In the case of a fixed number of vertices, *The peak memory usage of GNN increases linearly with the increase of the number of edges of the graph*, *The proportion of memory expansion will gradually stabilize to a fixed value determined by the complexity of the edge calculation}.
+    \item \textbf{In the case where the network structure and various hyperparameters are fixed, *using a higher-dimensional input feature vector can reduce the expansion ratio of GPU memory usage}.
+\end{itemize}
+
 \label{sec:memory_usage_analysis}
+\subsection{Effects of Sampling Techniques on Performance}
 
-\subsection{Effects of Sampling Techniques on Performance}
+Before the sampling technique, GNN training is full batch, that is, all the vertices and edges in the training set participate in the training and calculate the gradient at the same time.
+Full batch training can ensure convergence, but the training overhead is large each time, resulting in slow convergence.
+Inspired by the mini batch training method in stochastic gradient descent, a series of GNN sampling techniques are proposed.
+The sampling technique decomposes the training of the full graph (ie epoch) into several batches, and
+each batch uses only part of the graph vertices and edges to participate Training and performing gradient
+updates greatly reduces the training time of each batch, allowing multiple rounds of gradient descent to
+be performed within a fixed time, thereby accelerating convergence. The experiments in this section mainly
+analyze the impact of sampling techniques on training performance.
+
+In the current implementation of PyG, the GNN model parameters always reside on the GPU,
+and the data set resides in the main memory. When processing each epoch, the CPU samples
+the graph data set in the main memory and generates several batches,
+Each batch is a small-scale subgraph of the data set. When training each batch, 
+PyG copies the subgraph data corresponding to the batch to the GPU's memory,
+trains based on the subgraph and updates the model parameters according to the gradient.
+Based on the sampling technology and SGD optimization technology, 
+the evaluation of the model parameters is performed every several epochs. 
+The evaluation can be carried out on the CPU or on the GPU. 
+Therefore, the statistical data in the experiments in this section does not include the evaluation phase. 
+Neighbor is selected in this section Sampler and cluster sampler are two typical graph sampling techniques for analysis.
+
+Fig~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraphs sampled in the two sampling techniques varies with the batch size.
+For the neighbor sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph The proportion of points.
+For cluster sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole image.
+\textbf{neighbor sampler is very sensitive to the increase in batch size*. As the batch size increases, 
+the sampling sub-graph The number of vertices/edges and the average degree both increase rapidly and tend to stabilize}.
+\textbf{cluster sampler is less sensitive to the increase in batch size*, the number of vertices/average degree increases
+linearly with the increase in batch size, and the number of edges is in the batch When the size is relatively small,
+it also increases linearly.}
+
+It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole picture,
+especially when the relative batch size is low}. Taking the neighbor sampler at a relative batch size of 6\% as an example,
+The average degree of the amp dataset is 31.1, but the average degree of the sampled subgraphs is only 5.8,
+which is much lower than the average degree of the full picture;
+the average degree of the subgraphs sampled by the cluster sampler is lower, only 3.0.
+Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled sub-graphs with the original image.
+The overall distribution of the samples sampled by the two sampling techniques is lower than that of the original image. 
+The reason is that the distribution of vertices in the actual graph data set follows a power-rate distribution, and a small number of vertices The degree is very high,
+which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
+so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraphs will increase the time-consuming
+proportion of point calculation. For GGNN with high point calculation complexity, point calculation will replace edge calculation and become a performance bottleneck.
+
+\begin{figure}
+    \centering
+    \subfloat[Neighbor Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_graphsage_gcn.png}}
+    \subfloat[Cluster Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_cluster_gcn.png}}
+    \caption{The size of the sampled subgraph changes with the batch size.
+Each batch size is sampled 50 times, and the error bar represents the standard deviation.
+The relative batch size is the ratio relative to the full image.)}
+    \label{fig:exp_sampling_minibatch_graph_info}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.png}
+    \caption{Comparison of the vertex degree distribution of the sampled subgraph and the original graph. Data set: amp. Batch size = 512 (neighbor sampler) / 20 (cluster sampler)}
+    \label{fig:exp_sampling_minibatch_degrees_distribution}
+\end{figure}
+
+Fig~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the `amc` and `fli` datasets with the batch size after using the sampling technique.
+For the neighbor sampler, only when the batch size is very small The time spent in the training phase is significantly reduced compared to full-picture training. 
+When the batch size is particularly small, the training time is significantly reduced. However, because the sampling itself has additional overhead, 
+and there is also an overhead in transferring the sampled sub-image to the GPU, the training time of the entire batch may exceed the full image. 
+Training is time-consuming. For cluster sampler, the sampled subgraph is smaller than neighbor sampler under the same relative batch size,
+which makes the effect of sampling technology more obvious. But when the relative batch size increases, 
+the additional cost of sampling technology The increase is very obvious. When the relative batch size $\geq$ 25\%,
+the total time of each batch of the sampling technique even exceeds the time of the full image training. 
+Experiments show that \textbf{the implementation of sampling technology in PyG at this stage is very inefficient and the extra overhead is high}.
+When the batch size is slightly larger, the additional cost of sampling technology accounts for more than 50\% of the total training cost of the entire batch.
+\textbf{Sampling technology can reduce training time only on very small batches}.
+
+\begin{figure}
+    \centering
+    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_amazon-computers.png}}
+    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.png}}
+    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_amazon-computers.png}}
+    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_flickr.png}}
+    \caption{The training time of each batch changes with the batch size. FULL means that the full image participates in the training phase (excluding evaluation).}
+    \label{fig:exp_sampling_batch_train_time}
+\end{figure}
+
+However, \textbf{the advantage of the sampling technique is that it can greatly reduce the peak memory usage overhead,
+making large-scale graph neural network training possible}. 
+Fig~\ref{fig:exp_sampling_memory_usage} shows how the peak memory usage changes with the relative batch size during the training process after sampling technology is used.
+After sampling sampling technology, peak memory usage is greatly reduced. 
+The decrease of cluster sampler is greater than that of neighbor sampler.
+
+\begin{figure}
+    \centering
+    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_amazon-computers_peak_memory.png}}
+    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.png}}
+    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_amazon-computers_peak_memory.png}}
+    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_flickr_peak_memory.png}}
+    \caption{Change in peak memory usage with batch size. FULL indicates the case when the sampling technique is not used (excluding the evaluation stage).}
+    \label{fig:exp_sampling_batch_train_time}
+\end{figure}
 \label{sec:effects_of_sampling_techniques_on_performance}

### 2020-07-14 Manuscript/figs/experiments/sec4-experiments.tex
update

--- 2020-07-14 Manuscript/sec4-experiments.tex
@@
     \centering
-    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_amazon-computers_peak_memory.png}}
-    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.png}}
-    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_amazon-computers_peak_memory.png}}
-    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_flickr_peak_memory.png}}
+    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_amazon-computers.png}}
+    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.png}}
+    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_amazon-computers.png}}
+    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_flickr.png}}
     \caption{Change in peak memory usage with batch size. FULL indicates the case when the sampling technique is not used (excluding the evaluation stage).}

### 2020-07-14 Manuscript/sec4-experiments.tex
修改sec4一些图

@@
     \subfloat[com-amazon\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.png}}
-    \caption{Different Datasets's absolute training time per epoch in four GNN models. (total 50 epochs)}
+    \caption{The impact of training time}
 	\label{fig:exp_absolute_training_time}
@@
 	\centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.png}
-    \caption{GCN}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}
-    \caption{GGNN}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
+    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.png}}\\
+    \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}}\\
+    \subfloat[GAT\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}}\\
+    \subfloat[GaAN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}}
+    \caption{The influence of hyperparameters on GNN vertex/edge calculation time}
+	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
 \end{figure}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}
-    \caption{GAT}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
-\end{figure}
-
 GaAN also uses a multi-head mechanism, and its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
@@
 When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}
-    \caption{GaAN}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
-\end{figure}
 
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
-    \caption{The memory Usage of each GNN Model in different hyperparameter}
+    \caption{The effect of hyperparameters on GPU memory usage during the training phase (excluding the dataset itself)}
 	\label{fig:exp_hyperparameter_memory_usage}
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gaan.png}}
-    \caption{The vertex calculation and edge calculation of each GNN Model}
+    \caption{Vertex/edge calculation time-consuming ratio.}
 	\label{fig:exp_vertex_edge_cal_proportion}
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.png}}
-    \caption{The vertex calculation and edge calculation of each GNN Model}
+    \caption{The effect of the average vertex degree on the time-consuming proportion of vertex/edge calculation.}
 	\label{fig:exp_avg_degree_on_vertex_edge_cal_time}
@@
 The collect step is used to prepare the data structure required for edge calculation.
-This step will input the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \ leq N)$
+This step will input the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
 is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the input edge calculation function $\phi$
@@
     \includegraphics[width=0.7\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
-    \caption{Steps in edge calculation}
+    \caption{Step decomposition of edge calculation}
     \label{fig:steps_in_edge_calculation}
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.png}}
-    \caption{The vertex calculation and edge calculation of each GNN Model}
+    \caption{Time-consuming decomposition of edge calculations (including Layer0 and Layer1).}
 	\label{fig:exp_edge_calc_decomposition}
@@
     \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_usage_stage_amp.png}
-    \caption{Figure: Maximum memory usage in each stage. Data Load refers to memory usage after data is loaded. Data set: amp. Other datasets are similar}
+    \caption{Maximum memory usage in each stage. Data Load refers to memory usage after data is loaded. dataset: amp. Other datasets are similar}
     \label{fig:exp_memory_usage_stage_amp}
@@
 Fig~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
-Because the input feature dimension of the cph data set is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
+Because the input feature dimension of the cph dataset is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
 of the graph is much higher than the matrix size of the intermediate calculation result of the cache, 
-so its expansion ratio is particularly low, and the cam data set is the opposite. In order to measure the effect of the input feature vector dimension on the memory
+so its expansion ratio is particularly low, and the cam dataset is the opposite. In order to measure the effect of the input feature vector dimension on the memory
 expansion ratio , We randomly generated feature vectors of specific dimensions for different datasets.
@@
     \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.png}
-    \caption{The change of the memory expansion ratio with the dimension of the input feature vector. Data set: cam, other datasets are similar}
+    \caption{The change of the memory expansion ratio with the dimension of the input feature vector. dataset: cam, other datasets are similar}
     \label{fig:exp_memory_expension_ratio_input_feature_dimension}
@@
 In the current implementation of PyG, the GNN model parameters always reside on the GPU,
-and the data set resides in the main memory. When processing each epoch, the CPU samples
-the graph data set in the main memory and generates several batches,
-Each batch is a small-scale subgraph of the data set. When training each batch, 
+and the dataset resides in the main memory. When processing each epoch, the CPU samples
+the graph dataset in the main memory and generates several batches,
+Each batch is a small-scale subgraph of the dataset. When training each batch, 
 PyG copies the subgraph data corresponding to the batch to the GPU's memory,
@@
 Fig~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraphs sampled in the two sampling techniques varies with the batch size.
-For the neighbor sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph The proportion of points.
+For the neighbor sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph The proportion of verticess.
 For cluster sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole image.
@@
 The overall distribution of the samples sampled by the two sampling techniques is lower than that of the original image. 
-The reason is that the distribution of vertices in the actual graph data set follows a power-rate distribution, and a small number of vertices The degree is very high,
+The reason is that the distribution of vertices in the actual graph dataset follows a power-rate distribution, and a small number of vertices The degree is very high,
 which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
 so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraphs will increase the time-consuming
-proportion of point calculation. For GGNN with high point calculation complexity, point calculation will replace edge calculation and become a performance bottleneck.
+proportion of vertex calculation. For GGNN with high vertex calculation complexity, vertex calculation will replace edge calculation and become a performance bottleneck.
 
@@
     \centering
-    \subfloat[Neighbor Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_graphsage_gcn.png}}
+    \subfloat[Neighbor Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_graphsage_gcn.png}} \\
     \subfloat[Cluster Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_cluster_gcn.png}}
@@
     \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.png}
-    \caption{Comparison of the vertex degree distribution of the sampled subgraph and the original graph. Data set: amp. Batch size = 512 (neighbor sampler) / 20 (cluster sampler)}
+    \caption{Comparison of the vertex degree distribution of the sampled subgraph and the original graph. dataset: amp. Batch size = 512 (neighbor sampler) / 20 (cluster sampler)}
     \label{fig:exp_sampling_minibatch_degrees_distribution}
@@
     \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_amazon-computers.png}}
-    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.png}}
+    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.png}} \\
     \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_amazon-computers.png}}
@@
     \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_amazon-computers_peak_memory.png}}
-    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.png}}
+    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.png}} \\
     \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_amazon-computers_peak_memory.png}}
@@
     \caption{Change in peak memory usage with batch size. FULL indicates the case when the sampling technique is not used (excluding the evaluation stage).}
-    \label{fig:exp_sampling_batch_train_time}
+    \label{fig:exp_sampling_memory_usage}
 \end{figure}

### 2020-07-15 Manuscript/sec4-experiments.tex
更新了一些问题

@@
 
-Fig~\ref{fig:exp_absolute_training_time} compares the training time per epoch for each GNN model, the ranking is $\boldsymbol{GaAN} \gg \boldsymbol{GAT} > \boldsymbol{GGNN} > \boldsymbol{GCN}$.
-Its time-consuming ranking is consistent with the complexity analysis because the number of edges in the graph generally far exceeds the number of nodes, 
-the GAT algorithm with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
+Fig~\ref{fig:exp_absolute_training_time} compares the training time per epoch for each GNN model, the ranking is GaAN $\gg$ GAT $>$ GGNN $>$ GCN.
+Its time-consuming ranking is consistent with the complexity analysis. Because the number of edges in the graph generally far exceeds the number of nodes, 
+the GAT with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
 Fig~\ref{fig:exp_absolute_training_time} shows that the training time of individual epochs is abnormally high, which is mainly caused by profiling overhead and the GC pause of the Python interpreter.
@@
     \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}}\\
-    \subfloat[GAT\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}}\\
-    \subfloat[GaAN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}}
-    \caption{The influence of hyperparameters on GNN vertex/edge calculation time}
+    \caption{The influence of hyperparameters on GCN/GGNN vertex/edge calculation time}
 	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \includegraphics[height=8cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}
+    \caption{The influence of hyperparameters on GAT vertex/edge calculation time}
+	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
+\end{figure}
+
+\begin{figure}
+	\centering
+    \includegraphics[height=8cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}
+    \caption{The influence of hyperparameters on GaAN vertex/edge calculation time}
+	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
 \end{figure}
@@
 Only when the vertex calculation complexity is very high and the average degree is very low, the vertex calculation time can overtake the edge calculation time.
-Therefore, the focus of \textbf{GNN training optimization should improve the efficiency of edge calculation}.
+Therefore, \textbf{the focus of GNN training optimization should improve the efficiency of edge calculation}.
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
+    \includegraphics[width=1\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
     \caption{Step decomposition of edge calculation}
@@
 When the batch size is particularly small, the training time is significantly reduced. However, because the sampling itself has additional overhead, 
-and there is also an overhead in transferring the sampled sub-image to the GPU, the training time of the entire batch may exceed the full image. 
+and there is also an overhead in transferring the sampled subgraph to the GPU, the training time of the entire batch may exceed the full image. 
 Training is time-consuming. For cluster sampler, the sampled subgraph is smaller than neighbor sampler under the same relative batch size,

### 2020-07-15 Manuscript/sec4-experiments.tex
更新了一些问题

@@
 The goal of this experiment is to verify the accuracy of complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex} 
-by observing the effects the hyper-parameters of the GNN on training time-consuming and memory usage.
+by observing the effects the hyper-parameters of each GNN model on training time per epoch and memory usage.
 
@@
 Its time-consuming ranking is consistent with the complexity analysis. Because the number of edges in the graph generally far exceeds the number of nodes, 
-the GAT with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
+the algorithm GAT with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
 Fig~\ref{fig:exp_absolute_training_time} shows that the training time of individual epochs is abnormally high, which is mainly caused by profiling overhead and the GC pause of the Python interpreter.
@@
 The training time of each GNN model algorithm increases linearly with the increase of hyperparameters.
-When the hidden vector dimension $d_(in)$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time, resulting in an insignificant change in the total training time.
+When the hidden vector dimension $d_{in}$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time, resulting in an insignificant change in the total training time.
 When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.
 
-Fig~\ref{fig:exp_hyperparameter_memory_usage} also shows how each GNN model's use of GPU memory varies with the algorithm's hyperparameters.
-With the increase of hyperparameters, GNN's memory usage has also increased linearly.
+Fig~\ref{fig:exp_hyperparameter_memory_usage} also shows how each GNN model's GPU memory usage varies with the algorithm's hyperparameters.
+With the increase of hyperparameters, GNN's memory usage also increases linearly.
 
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
-    \caption{The effect of hyperparameters on GPU memory usage during the training phase (excluding the dataset itself)}
+    \caption{The effect of hyperparameters on GPU memory usage during the training phase (excluding the dataset memory)}
 	\label{fig:exp_hyperparameter_memory_usage}
@@
 \textbf{GNN training time and memory usage are linearly related to hyperparameters}.
-This allows algorithm engineers to use larger hyperparameters to increase the complexity of GNN Without worrying about the time-consuming training and the explosive growth of memory usage.
+This allows algorithm engineers to use larger hyperparameters to increase the complexity of GNN without worrying about the time-consuming training and the explosive growth of memory usage.
 
@@
 to the total training time (including forward, backward and evaluation stages). The GCN algorithm takes the most time to calculate on most datasets, 
-only the cph dataset is a special case, because the dimension of the input feature vector of this dataset is very high, resulting in the 
+only the \textit{cph} dataset is a special case, because the dimension of the input feature vector of this dataset is very high, resulting in the 
 high vertex calculation time-consuming of Layer0. Because of its high vertex calculation complexity, GGNN makes its vertex calculation time-consuming\
 ratio significantly higher than other algorithms, but on most datasets, edge calculation still occupies the main calculation time-consuming. 
-Only in pub and cam dataset, the edge calculation cost and the vertex calculation cost are close, because the average degree of the two datasets is low (only 4.5 and 2.8).
-For the GAT and GaAN algorithms, because of their high edge calculation complexity, their edge calculation cost Time is absolutely dominant. 
+Only in \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close, because the average degree of the two datasets is low (only 4.5 and 2.8).
+For the GAT and GaAN algorithms, because of their high edge calculation complexity, their edge calculation cost time is absolutely dominant. 
 In summary, \textbf{edge calculation is the main time-consuming factor of GNN training}, especially in the case of more complicated edge calculation.
@@
 it occupies a lot of execution time in all GNNs. For the message step, in the GNN (GAT and GaAN) with high edge calculation complexity, 
-Which occupies the absolute dominant. Although its side calculation in GCN only has a simple multiplication operation, it still takes more than 20\% of the time; 
-In GGNN, because its side calculation function $\boldsymbol{m}_{j,i }^l=\boldsymbol{W}^l\boldsymbol{h}_{j}^l$ is only related to the source vertex, 
+which occupies the absolute dominant. Although its edge calculation in GCN only has a simple multiplication operation, it still takes more than 20\% of the time; 
+In GGNN, because its edge calculation function $\boldsymbol{m}_{j,i }^l=\boldsymbol{W}^l\boldsymbol{h}_{j}^l$ is only related to the source vertex, 
 so in the implementation of PyG will be $\boldsymbol{W}^l\boldsymbol{h}_j The calculation of ^l$ is carried out before the edge calculation starts
@@
     \item The matrix multiplication operator mm in GCN is mainly used for vertex calculation $\gamma$, 
-    this operator is particularly time-consuming on the cph dataset, 
-    because the dimensionality of the vertex feature vector input by cph is very high,
+    this operator is particularly time-consuming on the \textit{cph} dataset, 
+    because the dimensionality of the vertex feature vector input by \textit{cph} is very high,
     making the matrix multiplication in the vertex calculation of Layer0 The calculation is very high.
@@
 the related operators scatter\_add and gather still occupy a certain amount of time.
-Although the collection step in the side calculation does not have any calculations,
+Although the collection step in the edge calculation does not have any calculations,
 but the related calculations The index\_select operator still accounts for about 10\% of the time-consuming.
@@
         The optimized softmax implementation on the GPU can Significantly reduce GAT training time.
-        \item If the computational complexity of $\phi$ is low, the collect and aggregate steps in its side calculations are bottlenecks in computational performance.
+        \item If the computational complexity of $\phi$ is low, the collect and aggregate steps in its edge calculations are bottlenecks in computational performance.
 The collect step only involves a large amount of data movement.
@@
 \textbf{GPU memory capacity is limited to Determinants of the size of the training dataset}. 
-GaAN was unable to complete the training due to memory overflow during the training of the `cph` dataset.
+GaAN was unable to complete the training due to memory overflow during the training of the `\textit{cph}` dataset.
 
@@
 Fig~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
-Because the input feature dimension of the cph dataset is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
+Because the input feature dimension of the \textit{cph} dataset is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
 of the graph is much higher than the matrix size of the intermediate calculation result of the cache, 
@@
 \textbf{As the average degree increases, the peak memory usage increases linearly.
-The intermediate results generated by the side calculation gradually dominate, and the memory expansion ratio of each GNN gradually stabilizes}. 
-The expansion ratio is affected by the complexity of the side calculation.
+The intermediate results generated by the edge calculation gradually dominate, and the memory expansion ratio of each GNN gradually stabilizes}. 
+The expansion ratio is affected by the complexity of the edge calculation.
 Except for GGNN, the memory expansion ratio of other GNNs increases with the increase of degree. GGNN has a high vertex calculation complexity.
@@
 especially when the relative batch size is low}. Taking the neighbor sampler at a relative batch size of 6\% as an example,
-The average degree of the amp dataset is 31.1, but the average degree of the sampled subgraphs is only 5.8,
+The average degree of the \textit{amp} dataset is 31.1, but the average degree of the sampled subgraphs is only 5.8,
 which is much lower than the average degree of the full picture;
@@
 
-Fig~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the `amc` and `fli` datasets with the batch size after using the sampling technique.
+Fig~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the \textit{amc} and \textit{fli} datasets with the batch size after using the sampling technique.
 For the neighbor sampler, only when the batch size is very small The time spent in the training phase is significantly reduced compared to full-picture training. 

### 2020-07-15 Manuscript/sec4-experiments.tex
更新了一些问题

@@
 Therefore, the statistical data in the experiments in this section does not include the evaluation phase. 
-Neighbor is selected in this section Sampler and cluster sampler are two typical graph sampling techniques for analysis.
+Neighbor is selected in this section Sampler and Cluster Sampler are two typical graph sampling techniques for analysis.
 
-Fig~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraphs sampled in the two sampling techniques varies with the batch size.
-For the neighbor sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph The proportion of verticess.
-For cluster sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole image.
-\textbf{neighbor sampler is very sensitive to the increase in batch size*. As the batch size increases, 
-the sampling sub-graph The number of vertices/edges and the average degree both increase rapidly and tend to stabilize}.
-\textbf{cluster sampler is less sensitive to the increase in batch size*, the number of vertices/average degree increases
+Fig~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraph sampled in the two sampling techniques varies with the batch size.
+For the Neighbor Sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph The proportion of verticess.
+For Cluster Sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole image.
+\textbf{Neighbor Sampler is very sensitive to the increase in batch size*. As the batch size increases, 
+the sampling subgraph The number of vertices/edges and the average degree both increase rapidly and tend to stabilize}.
+\textbf{Cluster Sampler is less sensitive to the increase in batch size*, the number of vertices/average degree increases
 linearly with the increase in batch size, and the number of edges is in the batch When the size is relatively small,
@@
 It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole picture,
-especially when the relative batch size is low}. Taking the neighbor sampler at a relative batch size of 6\% as an example,
-The average degree of the \textit{amp} dataset is 31.1, but the average degree of the sampled subgraphs is only 5.8,
+especially when the relative batch size is low}. Taking the Neighbor Sampler at a relative batch size of 6\% as an example,
+The average degree of the \textit{amp} dataset is 31.1, but the average degree of the sampled subgraph is only 5.8,
 which is much lower than the average degree of the full picture;
-the average degree of the subgraphs sampled by the cluster sampler is lower, only 3.0.
-Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled sub-graphs with the original image.
+the average degree of the subgraph sampled by the Cluster Sampler is lower, only 3.0.
+Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled subgraph with the original image.
 The overall distribution of the samples sampled by the two sampling techniques is lower than that of the original image. 
@@
 which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
-so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraphs will increase the time-consuming
+so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraph will increase the time-consuming
 proportion of vertex calculation. For GGNN with high vertex calculation complexity, vertex calculation will replace edge calculation and become a performance bottleneck.
@@
     \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.png}
-    \caption{Comparison of the vertex degree distribution of the sampled subgraph and the original graph. dataset: amp. Batch size = 512 (neighbor sampler) / 20 (cluster sampler)}
+    \caption{Comparison of the vertex degree distribution of the sampled subgraph and the original graph. dataset: amp. Batch size = 512 (Neighbor Sampler) / 20 (Cluster Sampler)}
     \label{fig:exp_sampling_minibatch_degrees_distribution}
@@
 Fig~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the \textit{amc} and \textit{fli} datasets with the batch size after using the sampling technique.
-For the neighbor sampler, only when the batch size is very small The time spent in the training phase is significantly reduced compared to full-picture training. 
+For the Neighbor Sampler, only when the batch size is very small The time spent in the training phase is significantly reduced compared to full-batch training. 
 When the batch size is particularly small, the training time is significantly reduced. However, because the sampling itself has additional overhead, 
 and there is also an overhead in transferring the sampled subgraph to the GPU, the training time of the entire batch may exceed the full image. 
-Training is time-consuming. For cluster sampler, the sampled subgraph is smaller than neighbor sampler under the same relative batch size,
+Training is time-consuming. For Cluster Sampler, the sampled subgraph is smaller than Neighbor Sampler under the same relative batch size,
 which makes the effect of sampling technology more obvious. But when the relative batch size increases, 
@@
 After sampling sampling technology, peak memory usage is greatly reduced. 
-The decrease of cluster sampler is greater than that of neighbor sampler.
+The decrease of Cluster Sampler is greater than that of Neighbor Sampler.
 

### 2020-07-15 Manuscript/sec4-experiments.tex
更新了一些问题

@@
 
-Fig~\ref{fig:exp_absolute_training_time} compares the training time per epoch for each GNN model, the ranking is GaAN $\gg$ GAT $>$ GGNN $>$ GCN.
-Its time-consuming ranking is consistent with the complexity analysis. Because the number of edges in the graph generally far exceeds the number of nodes, 
+Fig~\ref{fig:exp_absolute_training_time} compares the training time per epoch of each GNN model, the ranking is GaAN $\gg$ GAT $>$ GGNN $>$ GCN.
+The time-consuming ranking is consistent with the complexity analysis. Because the number of edges in the graph generally far exceeds the number of nodes, 
 the algorithm GAT with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
@@
 According to Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN model is linearly related to the 
-hyper-parameters of each model(such as $d_{dims}$, $K$, etc). In order to vertex this linear relationship, we measured the change of the training time of each GNN model with the hyperparameters.
+hyper-parameters of each model(such as $d_{dim}$, $K$, etc at al). In order to prove this linear relationship, we measured the change of the training time of each GNN model with the hyperparameters.
 
@@
 Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is affected by hyperparameters.
-The experiment verifies the complexity analysis results given in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}.
-The training time of each GNN model algorithm increases linearly with the increase of hyperparameters.
+\\
+The above experiments prove the complexity analysis results given in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}. 
+And the training time of each GNN model algorithm increases linearly with the increase of hyperparameters.
 When the hidden vector dimension $d_{in}$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time, resulting in an insignificant change in the total training time.
@@
 
-The experiment verifies the effectiveness of the complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}.
+The experiment proves the effectiveness of the complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}.
 \textbf{GNN training time and memory usage are linearly related to hyperparameters}.
@@
 
-For vertex calculation and edge calculation, Fig~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers in each algorithm
-to the total training time (including forward, backward and evaluation stages). The GCN algorithm takes the most time to calculate on most datasets, 
-only the \textit{cph} dataset is a special case, because the dimension of the input feature vector of this dataset is very high, resulting in the 
+For vertex calculation and edge calculation, Fig~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers in each GNN
+to the total training time (including forward, backward and evaluation stages). The GCN algorithm spends most of time on edge calculation in most datasets.
+Only the \textit{cph} dataset is a special case, because the dimension of the input feature vector of this dataset is very high, resulting in the 
 high vertex calculation time-consuming of Layer0. Because of its high vertex calculation complexity, GGNN makes its vertex calculation time-consuming\
-ratio significantly higher than other algorithms, but on most datasets, edge calculation still occupies the main calculation time-consuming. 
+ratio significantly higher than other algorithms, but in most datasets, edge calculation still occupies the majority of total time. 
 Only in \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close, because the average degree of the two datasets is low (only 4.5 and 2.8).
@@
 The edge calculation phase can be further decomposed into four steps of collect, message, aggregate and update,
-as shown in Fig~\ref{fig:steps_in_edge_calculation}. The figure shows the $l$ layer The edge calculation process of GNN.
-edge index is a matrix that holds the size of the edge set of the graph as $M*2$, where $M$ is the number of edges of the graph,
+as shown in Fig~\ref{fig:steps_in_edge_calculation}. The figure shows the edge calculation process of GNN layer $l$.
+edge index is a matrix that holds the edge sets of the graph with shape $M*2$, where $M$ is the number of edges,
 and the two columns of the matrix respectively store the source vertex and the target vertex of each edge.
@@
 The collect step is used to prepare the data structure required for edge calculation.
-This step will input the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
-is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the input edge calculation function $\phi$
+This step will use the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
+as input, which is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the edge calculation function $\phi$
 (including $\boldsymbol{h}_i^l$,$\boldsymbol{h}_j^ l$ and $\boldsymbol{e}_{j, i}^l$).
 There is no calculation in this step, only data access is involved. The message step calls the function given by the user $\phi$ to
-complete the edge calculation process, and get each The message vector of each edge $\boldsymbol{m}_{j, i}^l (\boldsymbol{e}_{j, i}^l \in E(G))$.
+complete the edge calculation process, and get message vector of each edge $\boldsymbol{m}_{j, i}^l (\boldsymbol{e}_{j, i}^l \in E(G))$.
 The aggregate step is based on the target of each edge, the message vector with the same target vertex is aggregated by the aggregation operator $\Sigma$,
-and each vertex aggregation vector $\boldsymbol{a}_i^l (1 \leq i \leq N)$ is obtained. 
-The last update The step is optional, and it can perform additional correction processing on the aggregated vector (for example, adding bias to GCN).
+and then each vertex aggregation vector $\boldsymbol{a}_i^l (1 \leq i \leq N)$ is obtained. 
+The last update step is optional, and it can perform additional correction processing on the aggregated vector (for example, adding bias to GCN).
 The aggregated vector $a_i^l$ after the update process will be input into the vertex calculation function $\gamma$ As an input parameter.
@@
 so in the implementation of PyG will be $\boldsymbol{W}^l\boldsymbol{h}_j The calculation of ^l$ is carried out before the edge calculation starts
-(because this part of the calculation is only related to vertices, so we count the calculation into the vertex calculation phase),
-the calculated result is cached, and it is directly read when the message step is performed The result is that the message step of GGNN takes 0.
-For the aggregate step, it occupies at least 35\% of the time-consuming GNN (GCN and GGNN) with low computational complexity,
-while the GNN with high computational complexity ( GAT and GaAN), whose time consumption is close to the collect step,
+(because this part of the calculation is only related to vertices, so we count the calculation into the vertex calculation phase).
+The calculated result is cached, and it is directly read when the message step is performed. As a result, the message step of GGNN gets 0.
+For the aggregate step, it occupies at least 35\% of training time of GNN (GCN and GGNN) with low edge computational complexity,
+while the GNN with high edge computational complexity (GAT and GaAN), whose time consumption is close to the collect step,
 and both are much lower than the message step. Experiments show that \textbf{for an algorithm with high edge calculation complexity,
@@
 Various functions for vertex/edge calculation $\phi, \Sigma,\gamma$ consist of a series of basic operators,
-which are mapped to specific basic operators on the GPU (Matrix multiplication mm, elementwise\_kernel multiplied by number of elements and index\_select selected by index.)
+which are mapped to specific basic operators on the GPU (matrix multiplication mm, elementwise multiplication mul and index by tensor index\_select)
 

### 2020-07-15 Manuscript/sec4-experiments.tex
更新了一些问题

@@
     The mm operator is used vertex calculation function $\gamma$.
-    \item The most time-consuming matrix multiplication operator mm in GaAN is used for both edge calculation and edge calculation,
+    \item The most time-consuming matrix multiplication operator mm in GaAN is used for both edge calculation and vertex calculation,
     where edge calculation is dominant. Mul and cat are used for the $\phi$ function in edge calculation.
@@
 In terms of commonality, 
-\textbf{The main time-consuming of GNN calculation is still matrix multiplication mm, multiplication of mul and other operators by the number of elements},
+\textbf{The main time-consuming of GNN calculation is still matrix multiplication mm, elementwise multiplication mul},
 so it is very suitable for calculation with GPU. Although the calculation of the aggregate step in edge calculation is relatively simple,
-but Because it involves data synchronization and non-regular calculations (the degree of different vertices is very different),
+but it involves data synchronization and non-regular calculations (the degree of different vertices is very different),
 the related operators scatter\_add and gather still occupy a certain amount of time.
-Although the collection step in the edge calculation does not have any calculations,
-but the related calculations The index\_select operator still accounts for about 10\% of the time-consuming.
+Although the collection step in the edge calculation does not have any calculationss,
+but the related calculations index\_select operator still accounts for about 10\% of the time-consuming.
 \textbf{aggregate step and collect step are one of the computational performance bottlenecks of all GNN training},
@@
     Because the average degree of most real-world graphs is above 10 degrees \cite{network-repository}, 
-    the performance bottleneck of GNN training will be concentrated on the edges Calculation section.
+    the performance bottleneck of GNN training will be concentrated on the edges calculation section.
     \item \textbf{According to the calculation complexity of the edge calculation function $\phi$, the performance bottleneck of GNN in edge calculation is different}:
@@
         which only involves data movement.
-        The optimized softmax implementation on the GPU can Significantly reduce GAT training time.
-        \item If the computational complexity of $\phi$ is low, the collect and aggregate steps in its edge calculations are bottlenecks in computational performance.
+        The optimized softmax implementation on the GPU can significantly reduce GAT training time.
+        \item If the computational complexity of $\phi$ is low, the collect and aggregate steps in its edge calculation are bottlenecks in computational performance.
 The collect step only involves a large amount of data movement.
@@
 
-It is worth noting that *the peak memory during GNN training far exceeds the memory usage of the dataset itself.
-The ratio of the highest peak memory usage during our training compared to the memory usage after Data Load is
+It is worth noting that \textbf{the peak memory during GNN training far exceeds the memory usage of the dataset itself}.
+The ratio of the highest peak memory usage during our training compared to the memory usage after data Load is
 defined as the memory expansion ratio. Fig~\ref{fig:exp_memory_expansion_ratio} compares the memory expansion ratios
 of different GNNs on different datasets. The expansion ratio of GCN is the lowest, between 5-14 times,
-and the expansion ratio of GaAN is the highest, up to 101 times
+and the expansion ratio of GaAN is the highest, up to 101 times.
 \textbf{Very high expansion ratio severely limits the data scalability of GNN, making GPU unable to process large-scale graph datasets},
@@
 Full batch training can ensure convergence, but the training overhead is large each time, resulting in slow convergence.
-Inspired by the mini batch training method in stochastic gradient descent, a series of GNN sampling techniques are proposed.
-The sampling technique decomposes the training of the full graph (ie epoch) into several batches, and
-each batch uses only part of the graph vertices and edges to participate Training and performing gradient
+Inspired by the minibatch training method in stochastic gradient descent, a series of GNN sampling techniques are proposed.
+The sampling technique decomposes the training of the full graph (i.e. epoch) into several batches, and
+each batch uses only part of the graph vertices and edges to participate training and performing gradient
 updates greatly reduces the training time of each batch, allowing multiple rounds of gradient descent to
@@
 Therefore, the statistical data in the experiments in this section does not include the evaluation phase. 
-Neighbor is selected in this section Sampler and Cluster Sampler are two typical graph sampling techniques for analysis.
+Neighbor Sampler and Cluster Sampler is selected in this section as they are two typical graph sampling techniques for analysis.
 
 Fig~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraph sampled in the two sampling techniques varies with the batch size.
-For the Neighbor Sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph The proportion of verticess.
-For Cluster Sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole image.
+For Neighbor Sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph the proportion of vertices.
+For Cluster Sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole graph.
 \textbf{Neighbor Sampler is very sensitive to the increase in batch size*. As the batch size increases, 
@@
 
-It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole picture,
-especially when the relative batch size is low}. Taking the Neighbor Sampler at a relative batch size of 6\% as an example,
+It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole graph,
+especially when the relative batch size is low}. Taking Neighbor Sampler at a relative batch size of 6\% as an example,
 The average degree of the \textit{amp} dataset is 31.1, but the average degree of the sampled subgraph is only 5.8,
-which is much lower than the average degree of the full picture;
-the average degree of the subgraph sampled by the Cluster Sampler is lower, only 3.0.
-Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled subgraph with the original image.
-The overall distribution of the samples sampled by the two sampling techniques is lower than that of the original image. 
-The reason is that the distribution of vertices in the actual graph dataset follows a power-rate distribution, and a small number of vertices The degree is very high,
+which is much lower than the average degree of the full graph.
+The average degree of the subgraph sampled by the Cluster Sampler is lower, only 3.0.
+Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled subgraph with the original graph.
+The vertex dregree distribution of subgraphs sampled by the two sampling techniques is lower than that of the original graph. 
+The reason is that the degree distribution of vertex in the actual graph dataset follows a power-rate distribution and only a small number of vertices is very high,
 which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
-so that the average degree drops significantly. Combined with the experimental results in section 4.2 The decrease in the average degree of sampling subgraph will increase the time-consuming
+so that the average degree drops significantly. Combined with the experimental results in section 4.2, the decrease in the average degree of sampled subgraph will increase the time-consuming
 proportion of vertex calculation. For GGNN with high vertex calculation complexity, vertex calculation will replace edge calculation and become a performance bottleneck.
@@
 Each batch size is sampled 50 times, and the error bar represents the standard deviation.
-The relative batch size is the ratio relative to the full image.)}
+The relative batch size is the ratio relative to the full graph.)}
     \label{fig:exp_sampling_minibatch_graph_info}
@@
 Fig~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the \textit{amc} and \textit{fli} datasets with the batch size after using the sampling technique.
-For the Neighbor Sampler, only when the batch size is very small The time spent in the training phase is significantly reduced compared to full-batch training. 
+For the Neighbor Sampler, the time spent in the training phase is significantly reduced compared to full-batch training only when the batch size is very small. 
 When the batch size is particularly small, the training time is significantly reduced. However, because the sampling itself has additional overhead, 
-and there is also an overhead in transferring the sampled subgraph to the GPU, the training time of the entire batch may exceed the full image. 
-Training is time-consuming. For Cluster Sampler, the sampled subgraph is smaller than Neighbor Sampler under the same relative batch size,
+and there is also an overhead in transferring the sampled subgraph to the GPU, the training time of the entire batch may exceed the full graph. 
+training is time-consuming. For Cluster Sampler, the sampled subgraph is smaller than Neighbor Sampler under the same relative batch size,
 which makes the effect of sampling technology more obvious. But when the relative batch size increases, 
-the additional cost of sampling technology The increase is very obvious. When the relative batch size $\geq$ 25\%,
-the total time of each batch of the sampling technique even exceeds the time of the full image training. 
+the increment by additional cost of sampling technology is very obvious. When the relative batch size $\geq$ 25\%,
+the total time of each batch of the sampling technique even exceeds the time of the full graph training. 
 Experiments show that \textbf{the implementation of sampling technology in PyG at this stage is very inefficient and the extra overhead is high}.
@@
     \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_flickr.png}}
-    \caption{The training time of each batch changes with the batch size. FULL means that the full image participates in the training phase (excluding evaluation).}
+    \caption{The training time of each batch changes with the batch size. FULL means that the full graph participates in the training phase (excluding evaluation).}
     \label{fig:exp_sampling_batch_train_time}
@@
 Fig~\ref{fig:exp_sampling_memory_usage} shows how the peak memory usage changes with the relative batch size during the training process after sampling technology is used.
-After sampling sampling technology, peak memory usage is greatly reduced. 
-The decrease of Cluster Sampler is greater than that of Neighbor Sampler.
+After sampling sampling technology, peak memory usage is greatly reduced and the decrease of Cluster Sampler is greater than that of Neighbor Sampler.
 

### 2020-07-15 Manuscript/ms.tex
Update section 2 of manuscript.
更新Section2
更新sampling技巧部分.
update初稿

@@
 %! TEX program = pdflatex
-\documentclass[review]{elsarticle}
+\documentclass{elsarticle}
+\usepackage{geometry}
+\geometry{left=3cm, right=3cm, top=2.5cm, bottom=2.5cm} 
 \usepackage{lineno,hyperref}
 \usepackage{amsmath, amsthm}
+\usepackage{relsize}
+\usepackage{booktabs}
+\usepackage{lscape}
+\usepackage{xcolor}
+\usepackage{subfig}
 \modulolinenumbers[5]
@@
 \begin{abstract}
-    This is the abstract.
+    Graph neural network has become a research hotspot in the field of artificial intelligence due to the high accuracy results 
+    obtained in many grpah-related task. At the same time, various of graph neural network system has emrged one after another.
+    These systems have used their own skills in implementation, but there is very few work to discuss the performance bottleneck
+    on graph neural network. In contrast to prior works that presents characterization of GCNs and selcts GNNs cover GNN workloads,
+    we select typical algorithm by complexity of vertex/edge calculation. We analyze the performance bottleneck by breaking down training
+    time, study the affects of hyper-parameters and sampling technology and find factors of memory usage. We finally put forwrd some key
+    findings for GNN training and hope our work can help GNN system researchers. 
 \end{abstract}
@@
 \begin{keyword}
-    Keyword 1
+    graph neural network, performance bottleneck, deep learning, characterization
 \end{keyword}

### 2020-07-15 Manuscript/sec1-introduction.tex
update初稿

@@
 
-This is a survey \cite{zhou2018_gnn_review}.
+In recent years, graph neural network is a hot reasearch topic in the field of artifical intelligence, 
+and has achieved excellent performance on tasks such as node classification, link prediction and graph classification.\cite{comprehensive-survey-wu-2020}
+\cite{zhou2018_gnn_review}, \cite{zhou2018_gnn_review}. These successes is related to graph strucure which reflects the vast majority of real-word data compared
+to grid data strucure such as citation network and knowledge graph and deep learning's end-to-end learning capability.
+At the same time, a series of parallel or distributed graph neural network systems have appeared.  
+These systems abstract the graph neural network computing model from a large number of graph neural networks,
+and design efficient implementations for the computing model with a lot of performance optimization.
+
+\begin{itemize}
+    \item message-passing general model \cite{gilmer_messgae_passing}. PyG and DGL is typical graph neural network system.
+    The graph convolution operation is defined as the message operation function, reduce operation function and update operation function.
+    PyG \cite{PyG} built upon PyTorch and obtained high data throught with sparse GPU accleration by providing dedicated CUDA kernels 
+    and mini-batch technologies. DGL \cite{DGL} supported a variety of computing backends (Tensorflow, MXNet, PyTorch) and leveraged
+    fusion kernel techniques, which combine message function with update function to provide further performance improvements compared to PyG \cite{PyG}. 
+    \item SAGA-NN general model
+    NeuGraph \cite{ma2019_neugraph} proposed SAGA-NN (Scatter-ApplyEdge-Gather-ApplyVertex with Neural Networks) programming model for graph neural network training.
+    The SAGA-NN model divides the forward calculation of each layer in the graph neural network into four stages: Scatter, ApplyEdge, Gather, and ApplyVertex. 
+    The ApplyEdge and ApplyVertex stages perform the calculation of the edge feature vector and vertex feature vector based on the neural network provided by the user. 
+    Scatter and Gather are stages implicitly triggered by the NeuGraph system. These two stages prepare data for the ApplyEdge and ApplyVertex stages. 
+    When programming, users only need to use the given operator to implement the ApplyEdge and ApplyVertex functions, and specify the Gather method,
+    then they can use NeuGraph to automatically complete GNN training.
+    \item Sample + Aggregate + Combine general model
+    In the general GNN framework supported by AliGraph \cite{zhu2019_aligraph}, 
+    each layer of GNN is disassembled into three basic operators: Sample, Aggregate and Combine. 
+    Sample corresponds to sampling, Aggregate performs edge calculation, 
+    and Combine corresponds to vertex calculation. 
+    Because AliGraph is faced with actual large-scale graph data, AliGraph focuses on graph storage, 
+    graph sampling, and graph calculation. In graph storage, the vertex-cut method is adopted, 
+    that is, different edges are allocated to different machines. 
+    In graph sampling, three sampling methods are supported, 
+    Traverse: sampling a batch of vertices from a graph partition;
+    Neighborhood: sample the 1-hop or multi-hop neighborhood of a vertex;
+    Negative: generate negative sampling samples to accelerate convergence. 
+    In particular, the weights in the Sampler also allow updating according to the gradient.
+\end{itemize}
+
+In the implementation of these graph neural network computing systems, 
+different performance optimization techniques are used, 
+but whether these performance optimization techniques really reflect the performance bottleneck
+research in the GNN training process is still in doubt. 
+At present, there is very little analysis of the specific performance bottlenecks of graph 
+neural network training. Yan et al\cite{yan2020_analysis_gcns_gpu} analyzed the characteristics of GCN-like algorithms
+in the inference phase with the classic graph analysis algorithm (PageRank) and MLP-based classic
+The characteristics of the neural network were compared and analyzed, 
+and it was found that the distribution of vertex degrees in the actual graph conforms
+ to the idempotent distribution. Therefore, the vertex of the cache height may increase the hardware
+cache hit rate, because vectorized atomic access can improve the efficiency of the aggregation stage, 
+but this work only selects a specific GNN algorithm, which cannot well represent most of the GNN training
+analysis. Zhange et al\cite{zhang2020_analysis_neugraph} experiment is based on the SAGA-NN programming model and DGL computing system,
+the author believes that GNN has no fixed performance bottlenecks, performance bottlenecks will vary with different datasets and algorithms, 
+but the degrees of the selected datasets is very low.Therefore, the performance bottleneck of GNN training deserves more research.
+
+Since the most essential operation of each layer of the graph neural network can actually be summarized into two operations,
+aggregate and update, the aggregate operation collects the information of neighboring vertices, 
+and the edge operation is reflected on the graph; the update operation transforms the vertex information, 
+which is reflected as vertex operation. Therefore, when studying the performance bottleneck of GNN training in this paper,
+vertex operation and edge operation can be used as the basis for selecting typical algorithms to
+study the performance bottleneck of GNN algorithm training. In survey\cite{comprehensive-survey-wu-2020}, \cite{zhou2018_gnn_review}, \cite{zhang2018_gnn_survey}, 
+we performed point-edge complexity analysis on most GNN algorithms, and classified different algorithms into different quadrants. 
+Four typical algorithms GCN, GGNN, GAT and GaAN are selected from the four quadrants. 
+In the experiment, we selected six data sets with different characteristics, and considered the R-MAT generator to generate random graphs, 
+and fixed the number of layers and common hyperparameters of the four algorithms. \\
+To explore the bottleneck of GNN training, we transformed into discussing the following four issues:
+Q1. How do hyperparameters affect training time and memory usage? Does it meet the time complexity analysis?\\
+Q2. Which stage of GNN training is the most time-consuming?\\
+Q3. Which factor has the greatest impact on memory in GNN training?\\
+Q4. Can the sampling technique solve the performance bottleneck of GNN training?\\
+For the above four problems, our Key Findings are:\\
+For Q1, for each algorithm, we analyzed the impact of its various parameters on training time and memory usage. 
+Experiments show that hyperparameters meet the time complexity analysis for training time and memory usage \\
+For Q2, we can divide the training time into different levels: layer level, vertex/edge computation leval 
+and basic operator leval, our training time of bareakdowon to different stages. We found that the characteristics of GNN
+calculation are in line with GPU operations, and the bottleneck of GNN training is affected by the average degree.
+In the real world, the average degree is more than 10 degrees, concentrated in the edge calculation part. 
+When the calculation complexity is high, the performance bottleneck is concentrated on the basic operator of the calculation; 
+while the calculation complexity is low, optimizing collect and aggreagte can improve performance \\
+For Q3, we measured the impact of peak memory usage and expansion ratio on the scale, points and edges of input features dims, graphs. 
+The peak memory usage of GNN during training can reach tens of times or even hundreds times, under fixed vertices, 
+the peak memory of GNN increases linearly with the growth of edges; 
+under the condition that the hyperparameters of the network structure are fixed, 
+higher-dimensional input feature vectors can reduce the proportion of GPU memory expansion \\
+For Q4, in order to verify the effectiveness of the sampling algorithm, we measured the change of training time
+and memory with batch size. 
+We found that the sampling technique can indeed greatly alleviate the memory problem, 
+thereby extending the GNN algorithm to large-scale graphs. However, after the batching technique is increased, 
+the sampling technique itself will cause more extra time, but it will be more time-consuming.\\
+Through the above analysis, we provide the following suggestions for the GNN system:\\
+1. The performance of hyperparameters in memory and training time is consistent with time complexity, 
+we can theoretically analyze performance bottlenecks\\
+2. GPU memory expansion is the most significant factor restricting the scalability of the GNN algorithm. 
+When dealing with large-scale graphs, how to effectively save memory is always a priority; memory and edge complexity are linearly related \\
+3. For real-world graphs, edge calculation is the time-consuming bottleneck. 
+The collection, message, and aggregation of edge calculation are worth optimizing at each stage, especially the message stage. 
+When the complexity of edge calculation is high, it is the most significant time-consuming; \\
+4. The advantage of sampling technology is that it greatly reduces the overhead of peak memory usage, 
+making large-scale graph neural network training possible, 
+and the time-consuming optimization of sampling technology will also bring great gains to the entire training.

### 2020-07-15 Manuscript/sec4-experiments.tex
update初稿

@@
 
-The goal of this experiment is to verify the accuracy of complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex} 
-by observing the effects the hyper-parameters of each GNN model on training time per epoch and memory usage.
+To verify the accuracy of complexity analysis in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}, we 
+design following experiments to observe the effects the hyper-parameters on training time and memory usage of a GNN. Especially, the memory usage
+points to GPU memory usage, same to below.
+
+\paragraph{the neccessity of removing abnormal epochs}
+The absolute training time of four GNN models is shown in \figurename~\ref{fig:exp_absolute_training_time}.
+In figure, we can conclude that the time ranking is GaAN $\gg$ GAT $>$ GGNN $>$ GCN.
+In all datasets, the number of edges is greater than that of nodes, so the correlation of training time between GAT and GGNN is
+GAT $>$ GGNN.
+And the remaining relationship is consistent with complexity analysis.
+In addition, we find that there are some outliers in \figurename~\ref{fig:exp_absolute_training_time} because of profiling overhead
+and GC pause of the Python interpreter. So in all the experiments below, we will remove abnormal epochs and use the average of remaining epochs to analysis.
 
@@
 
-Fig~\ref{fig:exp_absolute_training_time} compares the training time per epoch of each GNN model, the ranking is GaAN $\gg$ GAT $>$ GGNN $>$ GCN.
-The time-consuming ranking is consistent with the complexity analysis. Because the number of edges in the graph generally far exceeds the number of nodes, 
-the algorithm GAT with higher edge computing complexity is more time-consuming than the algorithm GGNN with high vertex computational complexity. At the same time, 
-Fig~\ref{fig:exp_absolute_training_time} shows that the training time of individual epochs is abnormally high, which is mainly caused by profiling overhead and the GC pause of the Python interpreter.
-This phenomenon confirms the necessity of removing abnormal epochs.
+\paragraph{the effects of hyper-parameters on training time}
 
-According to Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN model is linearly related to the 
-hyper-parameters of each model(such as $d_{dim}$, $K$, etc at al). In order to prove this linear relationship, we measured the change of the training time of each GNN model with the hyperparameters.
+According to \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN is linearly related to the 
+hyper-parameters of each model(such as $d_{dim}$, $K$, etc at al). 
+In order to prove this linear relationship, we measured the change of the training time of each GNN model with the hyperparameters.
 
@@
 
-The computational complexity of GCN and GGNN is affected by the hidden vector dimension $d_{dim}$. $d_{dim}$ affects both the output hidden vector dimension fo Layer0 and
-the input hidden vector dimension of Layer1(ie $d_{dim} = d^0_{out} = d^1_{in}$).
-Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}, Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
-show that the training time of GCN and GGNN is affected by $d_{dim}$. As $d_{dim}$ increases, the training time increases linearly.
+For GCN and GGNN, the computational complexity is affected by the hidden vector dimension $d_{dim}$. $d_{dim}$ affects both the output hidden vector dimension of Layer0 and
+the input hidden vector dimension of Layer1($d_{dim} = d^0_{out} = d^1_{in}$).
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
+display that the training time of GCN and GGNN is affected by $d_{dim}$. As $d_{dim}$ increases, the training time increases linearly.
 
-GAT uses a multi-head mechanism, and its computational complexity is affected by the input hidden vector dimension $d_{in}$, the hidden vector dimension $d_{head}$ of each head, and the number of heads $K$.
+For GAT,  which uses a multi-head mechanism, its computational complexity is affected by the input hidden vector dimension $d_{in}$ and the hidden vector dimension $d_{head}$ of each head, and the number of heads $K$.
 The output hidden vector dimension of each layer is $d_{out}=K d_{head}$.
-Because in the GAT model $d^1_{in}=d^0_{out}$, adjusting $d_{head}$ and $K$ is equivalent to adjusting Layer1’s $d^1_{in}$.
-Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time is affected by the hyperparameters $d_{head}$ and $K$, 
-GAT training time increases linearly with $d_{head}$ and $K$.
+Because of GAT model structure $d^1_{in}=d^0_{out}$, adjusting $d_{head}$ and $K$ is equivalent to adjusting Layer1’s $d^1_{in}$.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time increases linearly with $d_{head}$ and $K$, two.
 
-GaAN also uses a multi-head mechanism, and its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
-Fig~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is affected by hyperparameters.
+For GaAN, which also has a multi-head mechanism, its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is linearly affected by hyperparameters.
 \\
-The above experiments prove the complexity analysis results given in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}. 
-And the training time of each GNN model algorithm increases linearly with the increase of hyperparameters.
-When the hidden vector dimension $d_{in}$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time, resulting in an insignificant change in the total training time.
+The above experiments prove the complexity analysis results given in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}. 
+The training time of each GNN model increases linearly with the increase of hyperparameters.
+When the hidden vector dimension $d_{in}$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time,
+resulting in an insignificant change in the total training time.
 When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.
 
-Fig~\ref{fig:exp_hyperparameter_memory_usage} also shows how each GNN model's GPU memory usage varies with the algorithm's hyperparameters.
+\paragraph{the effects of hyper-parameters on memory usage}
+
+\figurename~\ref{fig:exp_hyperparameter_memory_usage} shows how each GNN model's memory usage varies with the algorithm's hyperparameters.
 With the increase of hyperparameters, GNN's memory usage also increases linearly.
@@
 
-The experiment proves the effectiveness of the complexity analysis in Table~\ref{tab:gnn_overview_edge}, Table~\ref{tab:gnn_overview_vertex}.
+\paragraph{Summary}
+
+We can answer the question Q1 \ref{sec:experimental_env}: the complexity analysis in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex} is valid. 
 \textbf{GNN training time and memory usage are linearly related to hyperparameters}.
@@
 
-The goal of this experiment is to discover the computational performance bottleneck in GNN training
-by decomposing the time-consuming training.
+In thi subsection, we aims to find what stage is the most time-consuming stage in GNN training by decomposing the time-consuming training.
 
@@
 
-For vertex calculation and edge calculation, Fig~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers in each GNN
-to the total training time (including forward, backward and evaluation stages). The GCN algorithm spends most of time on edge calculation in most datasets.
-Only the \textit{cph} dataset is a special case, because the dimension of the input feature vector of this dataset is very high, resulting in the 
-high vertex calculation time-consuming of Layer0. Because of its high vertex calculation complexity, GGNN makes its vertex calculation time-consuming\
+For vertex calculation and edge calculation, \figurename~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers in each GNN
+to the total training time (including forward, backward and evaluation stages). 
+The GCN algorithm spends most of time on edge calculation in most datasets except \textit{cph} dataset on account of
+the dimension of the input feature vector of this dataset is very high, resulting in the high vertex calculation time-consuming of Layer0.
+Because of its high vertex calculation complexity, GGNN makes its vertex calculation time-consuming\
 ratio significantly higher than other algorithms, but in most datasets, edge calculation still occupies the majority of total time. 
-Only in \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close, because the average degree of the two datasets is low (only 4.5 and 2.8).
+Only in \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close for GGNN 
+because the average degree of the two datasets is low (only 4.5 and 2.8).
 For the GAT and GaAN algorithms, because of their high edge calculation complexity, their edge calculation cost time is absolutely dominant. 
@@
 Experiments also show that \textbf{the average degree of the dataset affects the time-consuming proportion of vertex/edge calculation}. 
-Our fixed graph has 50k vertices, and the R-MAT generator is used to generate a random graph with an average degree between 10 and 100.
-We measure the change of the time-consuming proportion of the vertex/edge calculation in each GNN model varies with the average degree of the graph,
-as shown in Fig~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}. The time calculation of the edge increases linearly with the increase of the average degree,
-\textbf{The time calculation of the edge calculation dominates the entire calculation time in most cases}. 
+We use the R-MAT generator to generate random graphs with an average degree between 10 and 100. The number of nodes of these graphs is fixed at 50k.
+Then we measure the change of the time-consuming proportion of the vertex/edge calculation in each GNN model varies with the average degree of the graph,
+as shown in \figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}. The edge calculation time increases linearly with the increase of the average degree,
+\textbf{The edge calculation time dominates the entire calculation time in most cases}. 
 Only when the vertex calculation complexity is very high and the average degree is very low, the vertex calculation time can overtake the edge calculation time.
@@
 \paragraph{Time-consuming decomposition analysis of edge calculation}
+
 The edge calculation phase can be further decomposed into four steps of collect, message, aggregate and update,
-as shown in Fig~\ref{fig:steps_in_edge_calculation}. The figure shows the edge calculation process of GNN layer $l$.
+as shown in \figurename~\ref{fig:steps_in_edge_calculation}. The figure shows the edge calculation process of GNN layer $l$.
 edge index is a matrix that holds the edge sets of the graph with shape $M*2$, where $M$ is the number of edges,
@@
 The edge index remains unchanged throughout the calculation process.
-The collect step is used to prepare the data structure required for edge calculation.
-This step will use the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
+The collect step is used to prepare the data structure required for edge calculation and will use the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
 as input, which is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the edge calculation function $\phi$
 (including $\boldsymbol{h}_i^l$,$\boldsymbol{h}_j^ l$ and $\boldsymbol{e}_{j, i}^l$).
-There is no calculation in this step, only data access is involved. The message step calls the function given by the user $\phi$ to
-complete the edge calculation process, and get message vector of each edge $\boldsymbol{m}_{j, i}^l (\boldsymbol{e}_{j, i}^l \in E(G))$.
+There is no calculation in this step, only data access is involved. 
+The message step calls the function given by the user $\phi$ to complete the edge calculation process, and get message vector of each edge $\boldsymbol{m}_{j, i}^l (\boldsymbol{e}_{j, i}^l \in E(G))$.
 The aggregate step is based on the target of each edge, the message vector with the same target vertex is aggregated by the aggregation operator $\Sigma$,
@@
 The last update step is optional, and it can perform additional correction processing on the aggregated vector (for example, adding bias to GCN).
-The aggregated vector $a_i^l$ after the update process will be input into the vertex calculation function $\gamma$ As an input parameter.
+The aggregated vector $a_i^l$ after the update process will be input into the vertex calculation function $\gamma$ as an input parameter.
 
@@
 We performed the execution time decomposition of the edge calculation process of each GNN algorithm on different datasets,
-and the results are shown in Fig~\ref{fig:exp_edge_calc_decomposition}.
-The time-consuming decomposition of the edge calculation of each GNN is relatively stable, 
-and the dataset correlation is not strong. Although the collect step only performs data preparation,
-it occupies a lot of execution time in all GNNs. For the message step, in the GNN (GAT and GaAN) with high edge calculation complexity, 
-which occupies the absolute dominant. Although its edge calculation in GCN only has a simple multiplication operation, it still takes more than 20\% of the time; 
+and the results are shown in \figurename~\ref{fig:exp_edge_calc_decomposition}.
+The time-consuming decomposition of the edge calculation of each GNN is relatively stable and rarely affected by dataset.
+Although the collect step only performs data preparation, it occupies a lot of execution time in all GNNs.
+The message step in the GNN (GAT and GaAN) with high edge calculation complexity occupies the absolute dominant.
+Although its edge calculation in GCN only has a simple multiplication operation, it still takes more than 20\% of the time; 
 In GGNN, because its edge calculation function $\boldsymbol{m}_{j,i }^l=\boldsymbol{W}^l\boldsymbol{h}_{j}^l$ is only related to the source vertex, 
@@
 
-Fig~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each stage when each GNN is trained on the cam dataset, the situation is similar on other datasets.
+\figurename~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each stage when each GNN is trained on the cam dataset, the situation is similar on other datasets.
 \textbf{The memory usage in GNN training is forward The peak in the phase and the backward phase}, 
@@
 The cached intermediate results will be used in the gradient calculation of the backward phase.
-Fig~\ref{fig:ggnn_vertex_func_computation_graph} shows the calculation graph of GGNN's vertex calculation function $\gamma$.
+\figurename~\ref{fig:ggnn_vertex_func_computation_graph} shows the calculation graph of GGNN's vertex calculation function $\gamma$.
 It can be seen that a large number of operators are involved in GGNN vertex calculation and a large number of intermediate calculation results are generated.The key calculation results will also be cached,
@@
 The ratio of the highest peak memory usage during our training compared to the memory usage after data Load is
-defined as the memory expansion ratio. Fig~\ref{fig:exp_memory_expansion_ratio} compares the memory expansion ratios
+defined as the memory expansion ratio. \figurename~\ref{fig:exp_memory_expansion_ratio} compares the memory expansion ratios
 of different GNNs on different datasets. The expansion ratio of GCN is the lowest, between 5-14 times,
@@
 
-Fig~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
+\figurename~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
 Because the input feature dimension of the \textit{cph} dataset is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
@@
 expansion ratio , We randomly generated feature vectors of specific dimensions for different datasets.
-Fig~\ref{fig:exp_memory_expension_ratio_input_feature_dimension} shows the change in the expansion ratio under different input feature vector dimensions.
+\figurename~\ref{fig:exp_memory_expension_ratio_input_feature_dimension} shows the change in the expansion ratio under different input feature vector dimensions.
 \textbf{In the same GNN structure and hyperparameter settings, using a higher-dimensional input feature vector can reduce memory expansion ratio} .
@@
 In the case of a fixed number of vertices in the graph, we use the R-MAT generator to generate random graphs with different average degrees (number of edges).
-The Fig~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage during training varies with the average degree.
+The \figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage during training varies with the average degree.
 \textbf{As the average degree increases, the peak memory usage increases linearly.
@@
 In the case of a fixed number of edges in the graph, we use the R-MAT generator to generate random graphs with different numbers of vertices
-Fig~\ref{@fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows the change of memory usage with the number of vertices during training.
+\figurename~\ref{@fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows the change of memory usage with the number of vertices during training.
 Except for GGNN, the number of vertices increases, the number of vertices increases, the number of vertices increases,
@@
     \item \textbf{GPU memory usage mainly comes from the intermediate calculation results generated during the calculation process,
-     especially the intermediate calculation results of the edge calculation*. Because part of the intermediate calculation results
+     especially the intermediate calculation results of the edge calculation. Because part of the intermediate calculation results
     will be cached to participate in backward calculation, high GPU memory usage runs through the forward and backward stages.}
-    \item \textbf{GNN's peak memory usage during training can reach tens or even hundreds of times the size of the input data}.
-The limited memory capacity of the GPU severely limits the size of the input data that can be trained.
-    \item \textbf{In the case of a fixed number of vertices, *The peak memory usage of GNN increases linearly with the increase of the number of edges of the graph*, *The proportion of memory expansion will gradually stabilize to a fixed value determined by the complexity of the edge calculation}.
-    \item \textbf{In the case where the network structure and various hyperparameters are fixed, *using a higher-dimensional input feature vector can reduce the expansion ratio of GPU memory usage}.
+    \item \textbf{GNN's peak memory usage during training can reach tens or even hundreds of times the size of the input data.
+The limited memory capacity of the GPU severely limits the size of the input data that can be trained}.
+    \item \textbf{In the case of a fixed number of vertices, The peak memory usage of GNN increases linearly with the increase of the number of edges of the graph, The proportion of memory expansion will gradually stabilize to a fixed value determined by the complexity of the edge calculation}.
+    \item \textbf{In the case where the network structure and various hyperparameters are fixed, using a higher-dimensional input feature vector can reduce the expansion ratio of GPU memory usage}.
 \end{itemize}
@@
 
-Fig~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraph sampled in the two sampling techniques varies with the batch size.
+\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraph sampled in the two sampling techniques varies with the batch size.
 For Neighbor Sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph the proportion of vertices.
@@
 The average degree of the subgraph sampled by the Cluster Sampler is lower, only 3.0.
-Fig~\ref{fig:exp_sampling_minibatch_degrees_distribution) shows the comparison of the distribution of the sampled subgraph with the original graph.
+\figurename~\ref{fig:exp_sampling_minibatch_degrees_distribution} shows the comparison of the distribution of the sampled subgraph with the original graph.
 The vertex dregree distribution of subgraphs sampled by the two sampling techniques is lower than that of the original graph. 
@@
 
-Fig~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the \textit{amc} and \textit{fli} datasets with the batch size after using the sampling technique.
+\figurename~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the \textit{amc} and \textit{fli} datasets with the batch size after using the sampling technique.
 For the Neighbor Sampler, the time spent in the training phase is significantly reduced compared to full-batch training only when the batch size is very small. 
@@
 making large-scale graph neural network training possible}. 
-Fig~\ref{fig:exp_sampling_memory_usage} shows how the peak memory usage changes with the relative batch size during the training process after sampling technology is used.
+\figurename~\ref{fig:exp_sampling_memory_usage} shows how the peak memory usage changes with the relative batch size during the training process after sampling technology is used.
 After sampling sampling technology, peak memory usage is greatly reduced and the decrease of Cluster Sampler is greater than that of Neighbor Sampler.

### 2020-07-15 Manuscript/sec5-insights.tex
update初稿

\section{Insights}

Through our experiments, we prove the existing graph neural network system's performance optimization
technologies. For exampling, \ref{sec:effects_of_sampling_techniques_on_performance} finds that the advantage of 
sampling techniques can greatly reduce the peak memory usage, which clearly explains that when scaling up to large-scale
graph sampling layer is an essential part of AliGraph \cite{zhu2019_aligraph}. \ref{sec:training_time_breakdown} shows that in real graph datasets
(average degress over than 10), collect step of edge calculation is performance bottleneck. DGL \cite{DGL}'s key optimization
methods kernel fusion operation that combines message function with update funsion and requires message function withour parameters.

Compared to \cite{zhang2020_analysis_neugraph}, the autor thinks that computation-intensive GEMM kernel is not the bottleneck of GNN training. This
is not consistent with the hotspot analysis in \ref{sec:training_time_breakdown}. This is because the standard of selecting algorithms of the paper is to cover the varieties for GNN workloads 
while ignoring the complexity of GNN, which is mainly brought by matrix multiplication. In addition, the author's conclusion that kernel fusion can imporove performance
that is similar to our findings.

According to our experiments, we propose the following key findings:

\begin{itemize}
    \item The edge/vertex complexity analysis can be used to theoretically analyze performance bottleneck. And it allows algorithm engineers to use larger hyperparameters to
    increase the complexity of GNN without worrying about the time-consuming training and the explosive growth of memory usage.
    \item Edge computation is performance bottleneck of GNN training for real-world graphs. When the complexity of edge calculation is high, 
    optimization on collect step is most important. When the complexity of edge calculation is low, the collect and aggregate step is the main performance bottleneck.
    \item GPU memory expansion is the most significant fator restricting the scalabiltiy of the GNN algorithm. When dealing with larger-scale graphs, how to effectively save memory is always
    a priority
    \item The advantage of sampling technology is that it greatly reduces the overhead of peak memory usage, making large-scale graph neural network training possible.
    And the time-consuming optimization of sampling technology will also bring great gains to the entire training.
\end{itemize}

### 2020-07-15 Manuscript/sec6-related-work.tex
update初稿

@@
 \subsection{GNNs survey}
-GNNs survey: Zhou et al \cite{zhou2018_gnn_review}, Zhang et al \cite{zhou2018_gnn_review} and Wu et al \cite{comprehensive-survey-wu-2020} 
+Zhou et al \cite{zhou2018_gnn_review}, Zhang et al \cite{zhang2018_gnn_survey} and Wu et al \cite{comprehensive-survey-wu-2020} 
 surveyed existing graph neural works models in different categorizations and viewpoints and provided a comprehensive review about GNNs' model 

### 2020-07-15 Manuscript/sec7-conclusion.tex
update初稿

\section{Conclusion and Future Work}

We systematically study the performance bottleneck of graph neural networks. We first analyze the GNN training
from the perspective of edge/vertex time complexity and prove the validity of computation analysis on training
time and memory usage. We then decompose the training time from top to bottom and analyze factors that affected GPU memory and
the impact of sampling technology. Our analysis suggests that the edge calculation is the performance bottleneck of GNN model
and optimizing the collection stage and aggregation stage is always worth doing, but when the complexity of computing is high, the message stage is
the most stage that should be optimized. In addition, the huge memory usage is a big problem of GNN training and is linearly related of the number for edges.
Sampling technology is one of ways to greatly reduce the peak memory usage overhead.

In our work, the aggregator required by the selected algorithm is generally min, max, and mean.
When the aggregate becomes complicated, whether the performance brings further changes can be used as future research work.

### 2020-07-15 Manuscript/sec1-introduction.tex
更新了bib文件

@@
 and has achieved excellent performance on tasks such as node classification, link prediction and graph classification.\cite{comprehensive-survey-wu-2020}
-\cite{zhou2018_gnn_review}, \cite{zhou2018_gnn_review}. These successes is related to graph strucure which reflects the vast majority of real-word data compared
+\cite{zhou2018_gnn_review}, \cite{zhang2018_gnn_survey}. These successes is related to graph strucure which reflects the vast majority of real-word data compared
 to grid data strucure such as citation network and knowledge graph and deep learning's end-to-end learning capability.
@@
     The SAGA-NN model divides the forward calculation of each layer in the graph neural network into four stages: Scatter, ApplyEdge, Gather, and ApplyVertex. 
-    The ApplyEdge and ApplyVertex stages perform the calculation of the edge feature vector and vertex feature vector based on the neural network provided by the user. 
+    The ApplyEdge and ApplyVertex stages perform the calculation of the edge  cfeature vector and vertex feature vector based on the neural network provided by the user. 
     Scatter and Gather are stages implicitly triggered by the NeuGraph system. These two stages prepare data for the ApplyEdge and ApplyVertex stages. 
@@
 In the experiment, we selected six data sets with different characteristics, and considered the R-MAT generator to generate random graphs, 
-and fixed the number of layers and common hyperparameters of the four algorithms. \\
+and fixed the number of layers and common hyperparameters of the four algorithms. \par
 To explore the bottleneck of GNN training, we transformed into discussing the following four issues:
-Q1. How do hyperparameters affect training time and memory usage? Does it meet the time complexity analysis?\\
-Q2. Which stage of GNN training is the most time-consuming?\\
-Q3. Which factor has the greatest impact on memory in GNN training?\\
-Q4. Can the sampling technique solve the performance bottleneck of GNN training?\\
-For the above four problems, our Key Findings are:\\
-For Q1, for each algorithm, we analyzed the impact of its various parameters on training time and memory usage. 
-Experiments show that hyperparameters meet the time complexity analysis for training time and memory usage \\
-For Q2, we can divide the training time into different levels: layer level, vertex/edge computation leval 
+\begin{itemize}
+    \item Q1 How do hyperparameters affect training time and memory usage? Does it meet the time complexity analysis?
+    \item Q2 Which stage of GNN training is the most time-consuming?
+    \item Q3 Which factor has the greatest impact on memory in GNN training?
+    \item Q4 Can the sampling technique solve the performance bottleneck of GNN training?
+\end{itemize}
+
+For the above four problems, our Key Findings are:
+\begin{itemize}
+    \item For Q1, for each algorithm, we analyzed the impact of its various parameters on training time and memory usage. 
+    Experiments show that hyperparameters meet the time complexity analysis for training time and memory usage 
+    \item For Q2, we can divide the training time into different levels: layer level, vertex/edge computation leval 
     and basic operator leval, our training time of bareakdowon to different stages. We found that the characteristics of GNN
@@
     When the calculation complexity is high, the performance bottleneck is concentrated on the basic operator of the calculation; 
-while the calculation complexity is low, optimizing collect and aggreagte can improve performance \\
-For Q3, we measured the impact of peak memory usage and expansion ratio on the scale, points and edges of input features dims, graphs. 
+    while the calculation complexity is low, optimizing collect and aggreagte can improve performance.
+    \item For Q3, we measured the impact of peak memory usage and expansion ratio on the scale, points and edges of input features dims, graphs. 
     The peak memory usage of GNN during training can reach tens of times or even hundreds times, under fixed vertices, 
@@
     under the condition that the hyperparameters of the network structure are fixed, 
-higher-dimensional input feature vectors can reduce the proportion of GPU memory expansion \\
-For Q4, in order to verify the effectiveness of the sampling algorithm, we measured the change of training time
+    higher-dimensional input feature vectors can reduce the proportion of GPU memory expansion 
+    \item For Q4, in order to verify the effectiveness of the sampling algorithm, we measured the change of training time
     and memory with batch size. 
@@
     thereby extending the GNN algorithm to large-scale graphs. However, after the batching technique is increased, 
-the sampling technique itself will cause more extra time, but it will be more time-consuming.\\
-Through the above analysis, we provide the following suggestions for the GNN system:\\
-1. The performance of hyperparameters in memory and training time is consistent with time complexity, 
-we can theoretically analyze performance bottlenecks\\
-2. GPU memory expansion is the most significant factor restricting the scalability of the GNN algorithm. 
-When dealing with large-scale graphs, how to effectively save memory is always a priority; memory and edge complexity are linearly related \\
-3. For real-world graphs, edge calculation is the time-consuming bottleneck. 
+    the sampling technique itself will cause more extra time, but it will be more time-consuming.
+\end{itemize}
+
+Through the above analysis, we provide the following suggestions for the GNN system:
+
+\begin{itemize}
+    \item The performance of hyperparameters in memory and training time is consistent with time complexity, 
+    we can theoretically analyze performance bottlenecks
+    \item GPU memory expansion is the most significant factor restricting the scalability of the GNN algorithm. 
+    When dealing with large-scale graphs, how to effectively save memory is always a priority; memory and edge complexity are linearly related 
+    \item For real-world graphs, edge calculation is the time-consuming bottleneck. 
     The collection, message, and aggregation of edge calculation are worth optimizing at each stage, especially the message stage. 
-When the complexity of edge calculation is high, it is the most significant time-consuming; \\
-4. The advantage of sampling technology is that it greatly reduces the overhead of peak memory usage, 
+    When the complexity of edge calculation is high, it is the most significant time-consuming 
+    \item The advantage of sampling technology is that it greatly reduces the overhead of peak memory usage, 
     making large-scale graph neural network training possible, 
-and the time-consuming optimization of sampling technology will also bring great gains to the entire training.
+    and the time\-consuming optimization of sampling technology will also bring great gains to the entire training.
+\end{itemize}

### 2020-07-15 Manuscript/sec4-experiments.tex
更新了bib文件

@@
 For Cluster Sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole graph.
-\textbf{Neighbor Sampler is very sensitive to the increase in batch size*. As the batch size increases, 
+\textbf{Neighbor Sampler is very sensitive to the increase in batch size. As the batch size increases, 
 the sampling subgraph The number of vertices/edges and the average degree both increase rapidly and tend to stabilize}.
-\textbf{Cluster Sampler is less sensitive to the increase in batch size*, the number of vertices/average degree increases
+\textbf{Cluster Sampler is less sensitive to the increase in batch size, the number of vertices/average degree increases
 linearly with the increase in batch size, and the number of edges is in the batch When the size is relatively small,

### 2020-07-16 Manuscript/sec4-experiments.tex
update section4

@@
 
-\paragraph{the neccessity of removing abnormal epochs}
+\paragraph{The neccessity of removing abnormal epochs}
 The absolute training time of four GNN models is shown in \figurename~\ref{fig:exp_absolute_training_time}.
@@
 
-\paragraph{the effects of hyper-parameters on training time}
-
-According to \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN is linearly related to the 
-hyper-parameters of each model(such as $d_{dim}$, $K$, etc at al). 
-In order to prove this linear relationship, we measured the change of the training time of each GNN model with the hyperparameters.
-
 \begin{figure}
@@
 \end{figure}
+
+\paragraph{The effects of hyper-parameters on training time}
+According to \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN is linearly related to the 
+hyper-parameters of each model(such as $d_{dim}$, $K$, etc at al). In order to prove this linear relationship, we measured the change of the training time of each GNN model with the hyperparameters.
+For GCN and GGNN, the computational complexity is affected by the hidden vector dimension $d_{dim}$. $d_{dim}$ affects both the output hidden vector dimension of Layer0 and
+the input hidden vector dimension of Layer1($d_{dim} = d^0_{out} = d^1_{in}$).
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
+display that the training time of GCN and GGNN is affected by $d_{dim}$. As $d_{dim}$ increases, the training time increases linearly.
+For GAT,  which uses a multi-head mechanism, its computational complexity is affected by the input hidden vector dimension $d_{in}$ and the hidden vector dimension $d_{head}$ of each head, and the number of heads $K$.
+The output hidden vector dimension of each layer is $d_{out}=K d_{head}$.
+Because of GAT model structure $d^1_{in}=d^0_{out}$, adjusting $d_{head}$ and $K$ is equivalent to adjusting Layer1’s $d^1_{in}$.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time increases linearly with $d_{head}$ and $K$, two.
+For GaAN, which also has a multi-head mechanism, its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is linearly affected by hyperparameters.
+These experiments prove the complexity analysis results given in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}. 
+The training time of each GNN model increases linearly with the increase of hyperparameters.
+When the hidden vector dimension $d_{in}$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time,
+resulting in an insignificant change in the total training time.
+When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.
 
@@
 
-For GCN and GGNN, the computational complexity is affected by the hidden vector dimension $d_{dim}$. $d_{dim}$ affects both the output hidden vector dimension of Layer0 and
-the input hidden vector dimension of Layer1($d_{dim} = d^0_{out} = d^1_{in}$).
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
-display that the training time of GCN and GGNN is affected by $d_{dim}$. As $d_{dim}$ increases, the training time increases linearly.
-
-For GAT,  which uses a multi-head mechanism, its computational complexity is affected by the input hidden vector dimension $d_{in}$ and the hidden vector dimension $d_{head}$ of each head, and the number of heads $K$.
-The output hidden vector dimension of each layer is $d_{out}=K d_{head}$.
-Because of GAT model structure $d^1_{in}=d^0_{out}$, adjusting $d_{head}$ and $K$ is equivalent to adjusting Layer1’s $d^1_{in}$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time increases linearly with $d_{head}$ and $K$, two.
-
-For GaAN, which also has a multi-head mechanism, its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is linearly affected by hyperparameters.
-\\
-The above experiments prove the complexity analysis results given in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}. 
-The training time of each GNN model increases linearly with the increase of hyperparameters.
-When the hidden vector dimension $d_{in}$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time,
-resulting in an insignificant change in the total training time.
-When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.
-
-\paragraph{the effects of hyper-parameters on memory usage}
-
+\paragraph{The effects of hyper-parameters on memory usage}
 \figurename~\ref{fig:exp_hyperparameter_memory_usage} shows how each GNN model's memory usage varies with the algorithm's hyperparameters.
@@
 
-We can answer the question Q1 \ref{sec:experimental_env}: the complexity analysis in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex} is valid. 
+We can answer the question Q1 in \ref{sec:experimental_env}: the complexity analysis in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex} is valid. 
 \textbf{GNN training time and memory usage are linearly related to hyperparameters}.
@@
 
-In thi subsection, we aims to find what stage is the most time-consuming stage in GNN training by decomposing the time-consuming training.
+In this subsection, we aims to find what stage is the most time-consuming stage in GNN training by decomposing the time-consuming training.
 
-\paragraph{vertex/edge calculation time-consuming proportion analysis}
+\paragraph{Vertex/edge calculation time-consuming proportion analysis}
 
-For vertex calculation and edge calculation, \figurename~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers in each GNN
-to the total training time (including forward, backward and evaluation stages). 
-The GCN algorithm spends most of time on edge calculation in most datasets except \textit{cph} dataset on account of
-the dimension of the input feature vector of this dataset is very high, resulting in the high vertex calculation time-consuming of Layer0.
-Because of its high vertex calculation complexity, GGNN makes its vertex calculation time-consuming\
-ratio significantly higher than other algorithms, but in most datasets, edge calculation still occupies the majority of total time. 
-Only in \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close for GGNN 
+\figurename~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers
+to the total training time (including forward, backward and evaluation). GCN spends most of time on edge calculation in most datasets. A special case is  \textit{cph} dataset because of
+the dimension of the input feature vector of this dataset is very high, resulting in the high vertex calculation of Layer0.
+High vertex calculation makes GGNN's vertex calculation time-consuming ratio significantly higher than other algorithms.
+But in most datasets, for GGNN, edge calculation still occupies the majority of total time. 
+In \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close for GGNN 
 because the average degree of the two datasets is low (only 4.5 and 2.8).
-For the GAT and GaAN algorithms, because of their high edge calculation complexity, their edge calculation cost time is absolutely dominant. 
+For the GAT and GaAN algorithms, due to their high edge calculation complexity, their edge calculation cost time is absolutely dominant. 
 In summary, \textbf{edge calculation is the main time-consuming factor of GNN training}, especially in the case of more complicated edge calculation.
+
+Experiments also show that \textbf{the average degree of the dataset affects the time-consuming proportion of vertex/edge calculation}. 
+We use the R-MAT generator to generate random graphs with an average degree between 10 and 100. The number of nodes of these graphs is fixed at 50k.
+Then we measure the change of the time-consuming proportion of the vertex/edge calculation in each GNN model varies with the average degree of the graph,
+as shown in \figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}. The edge calculation time increases linearly with the increase of the average degree,
+\textbf{The edge calculation time dominates the entire calculation time in most cases}. 
+Only when the vertex calculation complexity is very high and the average degree is very low, the vertex calculation time can overtake the edge calculation time.
+Therefore, \textbf{the focus of GNN training optimization should improve the efficiency of edge calculation}.
 
@@
 \end{figure}
-
-Experiments also show that \textbf{the average degree of the dataset affects the time-consuming proportion of vertex/edge calculation}. 
-We use the R-MAT generator to generate random graphs with an average degree between 10 and 100. The number of nodes of these graphs is fixed at 50k.
-Then we measure the change of the time-consuming proportion of the vertex/edge calculation in each GNN model varies with the average degree of the graph,
-as shown in \figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}. The edge calculation time increases linearly with the increase of the average degree,
-\textbf{The edge calculation time dominates the entire calculation time in most cases}. 
-Only when the vertex calculation complexity is very high and the average degree is very low, the vertex calculation time can overtake the edge calculation time.
-Therefore, \textbf{the focus of GNN training optimization should improve the efficiency of edge calculation}.
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=1\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
+    \caption{Step decomposition of edge calculation}
+    \label{fig:steps_in_edge_calculation}
+\end{figure}
+
 The edge calculation phase can be further decomposed into four steps of collect, message, aggregate and update,
-as shown in \figurename~\ref{fig:steps_in_edge_calculation}. The figure shows the edge calculation process of GNN layer $l$.
+as shown in \figurename~\ref{fig:steps_in_edge_calculation}. The figure shows the edge calculation process of GNN layer $l$, 
 edge index is a matrix that holds the edge sets of the graph with shape $M*2$, where $M$ is the number of edges,
-and the two columns of the matrix respectively store the source vertex and the target vertex of each edge.
-The edge index remains unchanged throughout the calculation process.
-The collect step is used to prepare the data structure required for edge calculation and will use the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
+and two columns of the matrix respectively store the source vertex and the target vertex of each edge.
+Edge index remains unchanged throughout the calculation process.
+The collect step is used to prepare data structure required for edge calculation and will use the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
 as input, which is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the edge calculation function $\phi$
@@
 The aggregated vector $a_i^l$ after the update process will be input into the vertex calculation function $\gamma$ as an input parameter.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=1\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
-    \caption{Step decomposition of edge calculation}
-    \label{fig:steps_in_edge_calculation}
-\end{figure}
 

### 2020-07-16 Manuscript/ms.tex
update section4
update 语法

@@
 \title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
-\author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Yihua Huang\corref{correspondingauthor}}
+\author{Zhaokang Wang, Yunpan Wang}
 \cortext[correspondingauthor]{Corresponding author}
@@
     Graph neural network has become a research hotspot in the field of artificial intelligence due to the high accuracy results 
-    obtained in many grpah-related task. At the same time, various of graph neural network system has emrged one after another.
-    These systems have used their own skills in implementation, but there is very few work to discuss the performance bottleneck
-    on graph neural network. In contrast to prior works that presents characterization of GCNs and selcts GNNs cover GNN workloads,
+    obtained in many grpah-related tasks. At the same time, various of graph neural network system has emrged one after another.
+    These systems have used their own skills in implementation, but there are very few works to discuss the performance bottleneck
+    on graph neural network training. In contrast to prior works that present characterization of GCNs and select GNNs cover GNN workloads,
     we select typical algorithm by complexity of vertex/edge calculation. We analyze the performance bottleneck by breaking down training
@@
 
-\section*{Acknowledgment}
-
 \bibliography{gnnref.bib}

### 2020-07-16 Manuscript/ms.tex
update 语法

--- 2020-07-11 Manuscript/ms.tex
@@
 \begin{abstract}
-    This is the abstract.
+    Graph neural network has become a research hotspot in the field of artificial intelligence due to state-of-the-art of performance
+    achieved in many grpah-related tasks. At the same time, various of graph neural network system has emrged one after another.
+    These systems have used their own skills in implementation, but there are very few works to study the performance bottleneck
+    on graph neural network training. In contrast to prior works that present characterization of GCNs and select GNNs cover GNN workloads,
+    we select typical algorithms by complexity of edge/vertex calculation. We analyze the performance bottleneck by breaking down training
+    time, study the affects of hyper-parameters and sampling technologies and find factors of memory usage. We finally put forward some key
+    findings for GNN training and hope our work can help GNN system researchers. 
 \end{abstract}

### 2020-07-17 Manuscript/sec4-experiments.tex
Update section 4.

--- 2020-07-15 Manuscript/sec4-experiments.tex
@@
 In this section, we answers the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
+Without otherwise mentioned, when we report the training time per epoch of a GNN, we measure the training time of 50 epoches, exclude the epoches with abnormal training time \footnote{During the training of some epoches, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
+Assume Q1 and Q3 are the 25\% and 75\% quantiles of the training time of 50 epoches, respectively.
+We regard the epoches with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epoches.} and report the average time of the remaining epoches.
 
@@
 
-To verify the accuracy of complexity analysis in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}, we 
-design following experiments to observe the effects the hyper-parameters on training time and memory usage of a GNN. Especially, the memory usage
-points to GPU memory usage, same to below.
-
-\paragraph{the neccessity of removing abnormal epochs}
-The absolute training time of four GNN models is shown in \figurename~\ref{fig:exp_absolute_training_time}.
-In figure, we can conclude that the time ranking is GaAN $\gg$ GAT $>$ GGNN $>$ GCN.
-In all datasets, the number of edges is greater than that of nodes, so the correlation of training time between GAT and GGNN is
-GAT $>$ GGNN.
-And the remaining relationship is consistent with complexity analysis.
-In addition, we find that there are some outliers in \figurename~\ref{fig:exp_absolute_training_time} because of profiling overhead
-and GC pause of the Python interpreter. So in all the experiments below, we will remove abnormal epochs and use the average of remaining epochs to analysis.
+To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compare the training time of the four GNNs on the same dataset.
+\figurename~\ref{fig:exp_absolute_training_time} shows the wall-clock training time per epoch of the GNNs on the real-world datasets.
+The ranking of the training time was GaAN $\gg$ GAT $>$ GGNN $>$ GCN in all cases.
+Since the real-world graphs had more edges than edges ($m > n$), the time complexity of the edge computation affected more than the vertex computation.
+The ranking was consistent with the time complexity analysis.
 
@@
 	\centering
-    \subfloat[pubmed\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.png}}
-    \subfloat[amazon-photo\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.png}}
-    \subfloat[coauthor-physics\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.png}} \\
-    \subfloat[amazon-computers\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.png}}
-    \subfloat[flickr\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.png}}
-    \subfloat[com-amazon\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.png}}
-    \caption{The impact of training time}
+    \subfloat[\texttt{pub}\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.png}}	
+    \subfloat[\texttt{aph}\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.png}}
+    \subfloat[\texttt{cph}\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.png}} \\
+    \subfloat[\texttt{amc}\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.png}}
+    \subfloat[\texttt{fli}\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.png}}
+    \subfloat[\texttt{cam}\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.png}}
+    \caption{Distribution of the wall-clock training time of 50 epoches on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
 	\label{fig:exp_absolute_training_time}
@@
 
-\paragraph{the effects of hyper-parameters on training time}
-
-According to \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}, the computational complexity of edge and vetex of each GNN is linearly related to the 
-hyper-parameters of each model(such as $d_{dim}$, $K$, etc at al). 
-In order to prove this linear relationship, we measured the change of the training time of each GNN model with the hyperparameters.
+Fixing other hyper-parameters, the time complexity of $\phi$/$\gamma$ is linear to each hyper-parameter separately, according to the analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
+If we increase one of the hyper-parameters, the training time should also increase linearly.
+In order to verify the linearity, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.
 
@@
 	\centering
-    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.png}}\\
-    \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}}\\
-    \caption{The influence of hyperparameters on GCN/GGNN vertex/edge calculation time}
+    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.png}}
+    %
+    \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}}
+
+    \subfloat[GAT]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}}
+
+    \subfloat[GaAN]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}}
+
+    \caption{Effects of hyper-parameters on vertex/edge calculation time.}
 	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
@@
 
-\begin{figure}
-	\centering
-    \includegraphics[height=8cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}
-    \caption{The influence of hyperparameters on GAT vertex/edge calculation time}
-	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
-\end{figure}
-
-\begin{figure}
-	\centering
-    \includegraphics[height=8cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}
-    \caption{The influence of hyperparameters on GaAN vertex/edge calculation time}
-	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
-\end{figure}
-
-For GCN and GGNN, the computational complexity is affected by the hidden vector dimension $d_{dim}$. $d_{dim}$ affects both the output hidden vector dimension of Layer0 and
-the input hidden vector dimension of Layer1($d_{dim} = d^0_{out} = d^1_{in}$).
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
-display that the training time of GCN and GGNN is affected by $d_{dim}$. As $d_{dim}$ increases, the training time increases linearly.
+For GCN (\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}) and GGNN (\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}), the only modifiable hyper-parameter is the hidden dimension $dim(\boldsymbol{h}^1)$, as $dim(\boldsymbol{h}^0)$ and $dim(\boldsymbol{h}^2)$ is determined by the dataset with $dim(\boldsymbol{h}^0)=dim(\boldsymbol{x})$ and $dim(\boldsymbol{h}^2)=$\#Classes.
+$dim(\boldsymbol{h}^1)$ affects the dimensions of the output hidden feature vector $d_{out}$ of Layer 0 and the input hidden feature vector $d_{in}$ of Layer 1 simultaneously, i.e., $dim(\boldsymbol{h}^1) = d^0_{out} = d^1_{in}$.
+The training time of GCN and GGNN increased linearly under big $dim(\boldsymbol{h}^1)$, consistent with the time complexity analysis.
 

### 2020-07-17 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 3.

--- 2020-07-14 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 	\centering
-	\includegraphics[width=0.6\columnwidth]{figs/illustration/GNN_Unit.png}
+	\includegraphics[width=0.5\columnwidth]{figs/illustration/GNN_Unit.png}
 	\caption{Graph neuron of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}(b).
@@
 Different GNNs adopt different kinds of graph neurons and have different definitions of the three functions.
-$\phi$ and $\Sigma$ are the \emph{edge computation} functions.
+$\phi$ and $\Sigma$ are the \emph{edge calculation} functions.
 They are conducted over every edge in $\mathcal{G}$.
-$\gamma$ is the \emph{vertex computation} function.
+$\gamma$ is the \emph{vertex calculation} function.
 It is conducted over every vertex in $\mathcal{G}$.
@@
 	\end{footnotesize}
-	\caption{Typical graph neural networks and their edge computation functions.$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
+	\caption{Typical graph neural networks and their edge calculation functions.$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
 		Blue variables are model parameters to learn.
 For ChebNet, we report its GNN sub-layer.
-Because two sum operator are interchangeable and sum operator and concatenation operator are interchangeable, we do it for GAT to explain more clearly in edge computations functions.}
+Because two sum operator are interchangeable and sum operator and concatenation operator are interchangeable, we do it for GAT to explain more clearly in edge calculations functions.}
 	\label{tab:gnn_overview_edge}
@@
 	\end{footnotesize}
-	\caption{Typical graph neural networks and their vertex computation functions.
+	\caption{Typical graph neural networks and their vertex calculation functions.
         $d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
-Blue variables are model parameters to learn.
-For ChebNet, we report its GNN sub-layer.For Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for nodes with degree
-		$|\mathcal{N}(i)|$ at layer $l$.}
+        Blue variables are model parameters to learn. For ChebNet, we report its GNN sub-layer.
+        For Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for nodes with degree $|\mathcal{N}(i)|$ at layer $l$.}
 	\label{tab:gnn_overview_vertex}
@@
 
-Since we focus on analyzing the performance bottleneck in training GNNs, we classify the typical GNNs from the view of computational complexity.
-The computational complexity of a GNN layer is related to the complexity of its vertex and edge functions, i.e.
-$O(m * (O_\phi + O_\Sigma) + n * O_\gamma)$, where $O_\phi$/$O_\Sigma$/$O_\gamma$ are the computational complexity of the three functions.
+Since we focus on analyzing the performance bottleneck in training GNNs, we classify the typical GNNs from the view of time complexity.
+We use $O_\phi$/$O_\Sigma$/$O_\gamma$ to denote the time complexity of the three functions in the message-passing model.
+The time complexity of a GNN layer is made up of two parts: the edge calculation complexity $m * (O_\phi$ + $O_\Sigma)$ and the vertex calculation complexity $n * O_\gamma$.
 
-The complexity can be decomposed into two parts: the edge computation complexity $O_\phi$ + $O_\Sigma$ and the vertex computation complexity $O_\gamma$.
-In \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we list the edge and vertex computation complexity, respectively.
-The edge/vertex complexity of a graph neuron are affected by the dimensions of the input/output hidden vectors $d_{in}$ and $d_{out}$ and the dimensions of the model parameters (like the number of heads $K$ in GAT and the dimensions of the view vectors $d_a$/$d_v$ in GaAN).
+In \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we list the edge and vertex calculation complexity, respectively.
+The time complexity of a graph neuron are affected by the dimensions of the input/output hidden vectors $d_{in}$ and $d_{out}$ and the dimensions of the model parameters (like the number of heads $K$ in GAT and the dimensions of the view vectors $d_a$/$d_v$ in GaAN).
 
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{figs/illustration/GNN_complexity_quadrant.png}
+	\includegraphics[width=0.7\columnwidth]{fig_GNN_complexity_quadrant.pdf}
 	\caption{Complexity quadrants of typical GNNs. If two GNNs have the same complexity under the Big-O notation, we further compare their complexity according to how many parameters they need to train.}
@@
 
-\textbf{GCN} \cite{kipf2017_gcn} (low vertex \& edge computational complexity): Graph convolution network (GCN) is the first-order approximation of the spectral-based graph convolutions.
+\textbf{GCN} \cite{kipf2017_gcn} (low vertex \& edge calculation complexity): Graph convolution network (GCN) is the first-order approximation of the spectral-based graph convolutions.
 %By combining the advantages of both the spectral-based and the spatial-based convolution, it can learn the representation of the local topological structure and vertex features efficiently.
@@
 According to the associative law of the matrix multiplication, $\boldsymbol{h}^{l+1}_i = \sum_{v_j \in \mathcal{N}(v_i)}{e_{j,i}\boldsymbol{W}^l\boldsymbol{h}^l_j}$.
-Since the dimension of $\boldsymbol{h}^{l+1}_i$ is usually smaller than $\boldsymbol{h}^l_i$ in practical GCNs, the implementation of GCN \footnote{The implementation of GCN in PyTorch Geometric: \url{ https://github.com/rusty1s/pytorch_geometric/blob/1.5.0/torch_geometric/nn/conv/gcn_conv.py}} chooses to first conduct the vertex computation $\hat{\boldsymbol{h}}^l_j = \boldsymbol{W}^l\boldsymbol{h}^l_j$ for each vertex $v_j$ and then conduct the edge computation $\boldsymbol{h}^{l+1}_i=\sum_{v_j\in\mathcal{N}(v_i)}{\hat{\boldsymbol{h}}^l_j}$.
-As $\hat{\boldsymbol{h}}^l_j$ has the same dimension as $\boldsymbol{h}^{l+1}_i$, the implementation significantly reduces the  computation cost of the edge computation.
+Since the dimension of $\boldsymbol{h}^{l+1}_i$ is usually smaller than $\boldsymbol{h}^l_i$ in practical GCNs, the implementation of GCN in PyTorch Geometric chooses to first conduct the vertex calculation $\hat{\boldsymbol{h}}^l_j = \boldsymbol{W}^l\boldsymbol{h}^l_j$ for each vertex $v_j$ and then conduct the edge calculation $\boldsymbol{h}^{l+1}_i=\sum_{v_j\in\mathcal{N}(v_i)}{\hat{\boldsymbol{h}}^l_j}$.
+As $\hat{\boldsymbol{h}}^l_j$ has the same dimension as $\boldsymbol{h}^{l+1}_i$, the implementation significantly reduces the  computation cost of the edge calculation.
 
-\textbf{GGNN} (high vertex \& low edge computational complexity):
+\textbf{GGNN} (high vertex \& low edge calculation complexity):
 GGNN introduces the gated recurrent unit (GRU) into the graph neural networks.
@@
 
-\textbf{GAT} (low vertex \& high edge computational complexity):
+\textbf{GAT} (low vertex \& high edge calculation complexity):
 GAT introduces the attention mechanism into the graph neural networks.
@@
 Moreover, it adopts the multi-head mechanism that generates $K$ independent views for an edge, where $K$ is a hyperparameter.
-GAT moves the vertex update function $\gamma$ before the edge computation.
+GAT moves the vertex update function $\gamma$ before the edge calculation.
 $\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ with $1 \leq k \leq K$ are conducted for every vertex $v_i$ before the message function $\phi$.
 $\phi$ uses $\hat{\boldsymbol{h}}^{l,k}_{i}$ to get the weight of each edge in every head $k$.
-After the edge computation, GAT uses the aggreated vector $\boldsymbol{s}^l_i$ directly as the output hidden vector.
+After the edge calculation, GAT uses the aggreated vector $\boldsymbol{s}^l_i$ directly as the output hidden vector.
 
-\textbf{GaAN} (high vertex \& edge computational complexity):
+\textbf{GaAN} (high vertex \& edge calculation complexity):
 Based on the multi-head machanism, GaAN introduces a convolutional subnetwork to control the weight of each head.
 Thus, it introduces more edge-related parameters to train.
-Moreover, GaAN aggregates three messages simutaneously, further increasing the edge computational complexity.
+Moreover, GaAN aggregates three messages simutaneously, further increasing the edge calculational complexity.
 

### 2020-07-17 Manuscript/sec3-experiment-design.tex
update

@@
 \paragraph{Dataset}
-We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervise, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
+We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervised, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
 For directed graphs, PyG converts them into undirected ones during the data loading.
@@
         \toprule
-        Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $|\boldsymbol{x}|$ & Sparsity & \#Class & Directed \\
+        Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $dim(\boldsymbol{x})$ & Sparsity & \#Class & Directed \\
         \midrule
@@
         flickr (fli) \cite{zeng2020_graphsaint}                 & 89,250          & 899,756         & 10.1      & 500                & 0.54     & 7       & No       \\
-        com-amazon (cam) \cite{ang2012_defining}                & 334,863         & 925,872         & 2.8       & 32                 & 0.0      & 10      & No       \\
+        com-amazon (cam) \cite{yang2012_defining}                & 334,863         & 925,872         & 2.8       & 32                 & 0.0      & 10      & No       \\
         \bottomrule
@@
 $\bar{d}$ represents the average vertex degree.
-$|\boldsymbol{x}|$ is the dimension of the input feature vector.
+$dim(\boldsymbol{x})$ is the dimension of the input feature vector.
 The sparsity is the proportion of zero elements in the input feature vectors.}
@@
 \paragraph{Hyper-parameters}
-We picked the hyper-parameters of allupdated GNNs according to their popularity in the experimental evaluation in their original papers.
-We use $|\boldsymbol{v}|$ to denote the dimension of a vector $\boldsymbol{v}$.
-For GCN/GAT/GaAN, $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, i.e. the input feature vector.
-$|\boldsymbol{h}^1_i|$ was 64 and $|\boldsymbol{h}^2_i|$ was the number of classes.
-For GGNN, $|\boldsymbol{h}^0_i| = |\boldsymbol{h}^1_i| = |\boldsymbol{h}^2_i| = 64$.
+We use $dim(\boldsymbol{v}$ to denote the dimension of a vector $\boldsymbol{v}$.
+We picked the hyper-parameters of GNNs according to their original papers.
+As a GNN used different hyper-parameters for different tasks, we picked the most popular hyper-parameters.
+Some hyper-parameters, such as the numbers of GNN layers and the dimensions of hidden feature vectors, were common hyper-parameters in all the GNNs.
+We set them to the same values in the four GNNs.
+For GCN/GAT/GaAN, $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, $dim(\boldsymbol{h}^1_i)=64$, and $dim(\boldsymbol{h}^2_i)$ was the number of classes.
+For GGNN, since it uses extra MLP layers to transform the dimensions of the input/output feature vectors, we set $dim(\boldsymbol{h}^0_i) = dim(\boldsymbol{h}^1_i) = dim(\boldsymbol{h}^2_i) = 64$.
 We used 8 heads in GAT and GaAN.
@@
 			The limited memory capacity of a GPU card is the main factor preventing us training GNNs on big graphs.
-			We measured the peak memory usage in the GNN training under different graph scales, hyper-parameters and average vertex degrees.
+			We measured the peak memory usage in the GNN training under different graph scales, input feature dims and average vertex degrees.
 			Based on the results, we analyze which is the most memory-consuming component.

### 2020-07-17 Manuscript/sec4-experiments.tex

@@
 \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time increases linearly with $d_{head}$ and $K$, two.
-
 For GaAN, which also has a multi-head mechanism, its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
 \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is linearly affected by hyperparameters.
-\\
-The above experiments prove the complexity analysis results given in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}. 
+These experiments prove the complexity analysis results given in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}. 
 The training time of each GNN model increases linearly with the increase of hyperparameters.
@@
 
-\paragraph{the effects of hyper-parameters on memory usage}
+\begin{figure}
+	\centering
+    \includegraphics[height=8cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}
+    \caption{The influence of hyperparameters on GAT vertex/edge calculation time}
+	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
+\end{figure}
 
+\begin{figure}
+	\centering
+    \includegraphics[height=8cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}
+    \caption{The influence of hyperparameters on GaAN vertex/edge calculation time}
+	\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
+\end{figure}
+
+\paragraph{The effects of hyper-parameters on memory usage}
 \figurename~\ref{fig:exp_hyperparameter_memory_usage} shows how each GNN model's memory usage varies with the algorithm's hyperparameters.

### 2020-07-18 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 2.

@@
 \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
-For ChebNet, we report its GNN layer in the tables \footnote{A layer of ChebNet consists of $K$ GNN sub-layers and a summation layer, i.e., $\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with GNN layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$.
-$\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
-In the table, we report the GNN sub-layer of ChebNet that calculates $\boldsymbol{Z}^{(k)}$}.
+For ChebNet, we report its GNN sub-layer in the tables. 
+A ChebNet layer consists of $K$ GNN sub-layers and a summation layer:
+$\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with the GNN sub-layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}^l$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}^l$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$, where $\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
+For GAT, a GAT layer consists of two sub-layers:
+the first sub-layer calculates the summation $\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))$, and the second sub-layer calculates $\alpha_{j, i}^k$ and $\boldsymbol{m}^l_{j,i}$.
+The vertex calculation of a GAT layer is decomposed into two parts: $\hat{\boldsymbol{h}}^{l,k}_{i}$/$\boldsymbol{h}^{l+1}_i$ is calculated for every vertex before/after the message-passing, respectively.
+The edge calculation of GAT uses $\hat{\boldsymbol{h}}^{l,k}_{i}$ during the message-passing.
+For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\sum_{k \in \mathcal{N}(j)}\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}}  \boldsymbol{h}_k^l] )$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
 
@@
 						 & \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))} \\
-						 & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l})                                                                                                                                             \\
-						 & \text{Multi-head average}: \boldsymbol{m}_{j, i}^l = \frac{1}{K} \sum_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_j^{l})
+						 & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \hat{\boldsymbol{h}}^{l,k}_j)                                                                                                                                             \\
+						 & \text{Multi-head average}: \boldsymbol{m}_{j, i}^l = \frac{1}{K} \sum_{k=1}^K \delta(\alpha_{j, i}^k \hat{\boldsymbol{h}}^{l,k}_j)
 					\end{aligned}$
 			\end{scriptsize}                                                                                             &
-			$O(K * d_{in} * d_{out})$                                                                                                   \\
+			\makecell[r]{concat: $O(d_{in}*d_{out})$ \\
+                 average: $O(K * d_{in} * d_{out})$  \\ Two sub-layers} 
+             \\
 			\textbf{GaAN}                                                                                                             &
@@
 			\end{scriptsize}                                                                                            &
-			$O(max(d_a, d_m, d_v) * K * d_{in})$                                                                                        \\
+			\makecell[r]{$O(max(d_a, d_m, d_v) * K * d_{in})$ \\
+                        Four sub-layers}\\
 			\bottomrule
@@
 	\end{footnotesize}
-	\caption{Typical graph neural networks and their edge calculation functions.$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
+	\caption{Typical graph neural networks and their edge calculation functions.
+		$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
 		Blue variables are model parameters to learn.
-For ChebNet, we report its GNN sub-layer.
-Because two sum operator are interchangeable and sum operator and concatenation operator are interchangeable, we do it for GAT to explain more clearly in edge calculations functions.}
+	}
 	\label{tab:gnn_overview_edge}
@@
 			\textbf{GAT}                                                                                                                                                                                                     &
-			$\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ (pre-edge), $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$                                                         &
-			$O(d_{in} * d_{out})$                                                                                                                                                                                              \\
+			\makecell[l]{$\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ (pre edge calculation),\\ $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$}                                                         &
+			\makecell[r]{concat: $O(d_{in}*d_{out}/K)$\\ average: $O(d_{in}*d_{out})$
+             \\ Two sub-layers}
+			\\
 			\textbf{GaAN}                                                                                                                                                                                                    &
@@
 			\end{scriptsize}                                                                                                                                                                                   &
-			$O(max(K * d_v + d_{in}, 2 * d_{in} + d_m) * d_{out})$                                                                                                                                                             \\ \bottomrule
+			\makecell[r]{$O(max(K * d_v + d_{in}, 2 * d_{in} + d_m) * d_{out})$\\
+                         Four sub-layers}
+            \\ \bottomrule
 		\end{tabular}
@@
 		$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
-        Blue variables are model parameters to learn. For ChebNet, we report its GNN sub-layer.
+		Blue variables are model parameters to learn.
 		For Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for nodes with degree $|\mathcal{N}(i)|$ at layer $l$.}
@@
 	\centering
-	\includegraphics[width=0.7\columnwidth]{fig_GNN_complexity_quadrant.pdf}
+	\includegraphics[width=0.7\columnwidth]{figs/illustration/GNN_complexity_quadrant.pdf}
 	\caption{Complexity quadrants of typical GNNs. If two GNNs have the same complexity under the Big-O notation, we further compare their complexity according to how many parameters they need to train.}
@@
 	\centering
-	\subfloat[Neighbor sampling\label{fig:gnn_sampling_neigbhor_sampling}]{\includegraphics[height=4cm]{figs/illustration/layer_sampling.png}}
+	\subfloat[Neighbor sampling\label{fig:gnn_sampling_neigbhor_sampling}]{\includegraphics[height=4cm]{figs/illustration/layer_sampling.pdf}}
 	%
-	\subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4cm]{figs/illustration/graph_sampling.png}}
+	\subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4cm]{figs/illustration/graph_sampling.pdf}}
 	\caption{Training a GNN with sampling techniques. The faded graph neurons and their connections are inactivated.}

### 2020-07-18 Manuscript/sec4-experiments.tex

@@
     \centering
-    \subfloat[\texttt{pub}\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.png}}	
-    \subfloat[\texttt{aph}\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.png}}
-    \subfloat[\texttt{cph}\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.png}} \\
-    \subfloat[\texttt{amc}\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.png}}
-    \subfloat[\texttt{fli}\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.png}}
-    \subfloat[\texttt{cam}\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.png}}
+    \subfloat[\texttt{pub}\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}}
+    \subfloat[\texttt{aph}\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}}
+    \subfloat[\texttt{cph}\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}} \\
+    \subfloat[\texttt{amc}\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}}
+    \subfloat[\texttt{fli}\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}}
+    \subfloat[\texttt{cam}\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}}
     \caption{Distribution of the wall-clock training time of 50 epoches on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
@@
     \centering
-    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.png}}
+    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
     %
-    \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.png}}
+    \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}
 
-    \subfloat[GAT]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}}
+    \subfloat[GAT]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}}
 
-    \subfloat[GaAN]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}}
+    \subfloat[GaAN]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}}
 
@@
 For GCN (\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}) and GGNN (\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}), the only modifiable hyper-parameter is the hidden dimension $dim(\boldsymbol{h}^1)$, as $dim(\boldsymbol{h}^0)$ and $dim(\boldsymbol{h}^2)$ is determined by the dataset with $dim(\boldsymbol{h}^0)=dim(\boldsymbol{x})$ and $dim(\boldsymbol{h}^2)=$\#Classes.
-$dim(\boldsymbol{h}^1)$ affects the dimensions of the output hidden feature vector $d_{out}$ of Layer 0 and the input hidden feature vector $d_{in}$ of Layer 1 simultaneously, i.e., $dim(\boldsymbol{h}^1) = d^0_{out} = d^1_{in}$.
+$dim(\boldsymbol{h}^1)$ affects the dimensions of the output hidden feature vector of Layer 0 $d^{0}_{out}$ and the input hidden feature vector of Layer 1 $d^1_{in}$ simultaneously, i.e., $dim(\boldsymbol{h}^1) = d^0_{out} = d^1_{in}$.
 The training time of GCN and GGNN increased linearly under big $dim(\boldsymbol{h}^1)$, consistent with the time complexity analysis.
 
-For GAT,  which uses a multi-head mechanism, its computational complexity is affected by the input hidden vector dimension $d_{in}$ and the hidden vector dimension $d_{head}$ of each head, and the number of heads $K$.
+For GAT (\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}), it uses the multi-head mechanism.
+Each head outputs a hidden feature vector of dimension $d_{out}$.
+Its time complexity is affected by the dimensions of the input/output hidden vectors $d_{in}$/$d_{out}$ and the number of heads $K$.
 The output hidden vector dimension of each layer is $d_{out}=K d_{head}$.

### 2020-07-19 Manuscript/sec2-review-of-graph-neural-network.tex
更新GAT的公式.

@@
 the first sub-layer calculates the summation $\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))$, and the second sub-layer calculates $\alpha_{j, i}^k$ and $\boldsymbol{m}^l_{j,i}$.
-The vertex calculation of a GAT layer is decomposed into two parts: $\hat{\boldsymbol{h}}^{l,k}_{i}$/$\boldsymbol{h}^{l+1}_i$ is calculated for every vertex before/after the message-passing, respectively.
+The vertex calculation of a GAT layer is also decomposed into two parts: $\hat{\boldsymbol{h}}^{l,k}_{i}$/$\boldsymbol{h}^{l+1}_i$ is calculated for every vertex before/after the message-passing, respectively.
 The edge calculation of GAT uses $\hat{\boldsymbol{h}}^{l,k}_{i}$ during the message-passing.
@@
 				$\begin{aligned}[t]
-						 & \alpha_{j, i}^k = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))} {\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))} \\
-						 & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \hat{\boldsymbol{h}}^{l,k}_j)                                                                                                                                             \\
-						 & \text{Multi-head average}: \boldsymbol{m}_{j, i}^l = \frac{1}{K} \sum_{k=1}^K \delta(\alpha_{j, i}^k \hat{\boldsymbol{h}}^{l,k}_j)
+                         & \text{Sub-layer 0:}\\
+                         & \boldsymbol{m}^{l,0}_{j,i,(k)} = \exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j, (k)}]))\\
+                         & \text{Sub-layer 1:}\\
+						 & \alpha_{j, i, (k)} = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j,(k)}] ))} {\hat{\boldsymbol{a}}^{l,0}_{i,(k)}} \\
+						 & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^{l,1} = \parallel_{k=1}^K \delta(\alpha_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)})                                                                                                                                             \\
+						 & \text{Multi-head average}: \boldsymbol{m}_{j, i}^{l,1} = \frac{1}{K} \sum_{k=1}^K \delta(\alpha_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)})
 					\end{aligned}$
-			\end{scriptsize}                                                                                             &
-			\makecell[r]{concat: $O(d_{in}*d_{out})$ \\
-                 average: $O(K * d_{in} * d_{out})$  \\ Two sub-layers} 
+			\end{scriptsize}
+             &
+             $
+             \begin{aligned}[t]
+                \text{concat: } O(d_{out}) &\\
+                \text{average: } O(K * d_{out}) &\\
+                \text{Two sub-layers} &
+             \end{aligned}
+             $ 
              \\
@@
 			\textbf{GAT} &
-			\makecell[l]{$\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ (pre edge calculation),\\ $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$}                                                         &
-			\makecell[r]{concat: $O(d_{in}*d_{out}/K)$\\ average: $O(d_{in}*d_{out})$
-             \\ Two sub-layers}
+            \begin{scriptsize}
+                $\begin{aligned}[t]
+                & \text{Before edge calculation:}\\
+                & \hat{\boldsymbol{h}}^{l}_{i,(k)} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}\\
+                & \text{Sub-layer 0:}\\
+                & \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}\\
+                & \text{Sub-layer 1:}\\
+                & \boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^{l,1}
+                \end{aligned}
+                $
+            \end{scriptsize} &
+             $
+             \begin{aligned}[t]
+             \text{concat:} O(d_{in}*d_{out}) &\\
+             \text{average:} O(K*d_{in}*d_{out}) &\\
+             \text{Two sub-layers}&
+            \end{aligned}
+             $
            \\
@@
 GAT introduces the attention mechanism into the graph neural networks.
+Each GAT layer consists of two sub-layers.
+The first sub-layer calculates the attention weights of every edge $(v_i, v_j)$ $\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j]$ and aggregates the attention weights of all adjacency edges of every vertex $v_i$ as $\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))$.
+The second sub-layer uses 
 During the message passing, it dynamically determines the weight for an edge based on the hidden feature vectors of its two end vertices.

### 2020-07-19 Manuscript/sec4-experiments.tex
更新GAT的公式.

@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gcn.png}}
-    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_ggnn.png}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gat.png}}
-    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gaan.png}}
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gat.pdf}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gaan.pdf}}
     \caption{Vertex/edge calculation time-consuming ratio.}

### 2020-07-19 Manuscript/sec2-review-of-graph-neural-network.tex
更新GAT的描述.

@@
 $\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with the GNN sub-layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}^l$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}^l$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$, where $\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
-For GAT, a GAT layer consists of two sub-layers:
-the first sub-layer calculates the summation $\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))$, and the second sub-layer calculates $\alpha_{j, i}^k$ and $\boldsymbol{m}^l_{j,i}$.
-The vertex calculation of a GAT layer is also decomposed into two parts: $\hat{\boldsymbol{h}}^{l,k}_{i}$/$\boldsymbol{h}^{l+1}_i$ is calculated for every vertex before/after the message-passing, respectively.
-The edge calculation of GAT uses $\hat{\boldsymbol{h}}^{l,k}_{i}$ during the message-passing.
+For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
 For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\sum_{k \in \mathcal{N}(j)}\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}}  \boldsymbol{h}_k^l] )$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
@@
                 $\begin{aligned}[t]
-                & \text{Before edge calculation:}\\
+                & \text{Preprocessing:}\\
                 & \hat{\boldsymbol{h}}^{l}_{i,(k)} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}\\
@@
 \textbf{GAT} (low vertex \& high edge calculation complexity):
-GAT introduces the attention mechanism into the graph neural networks.
-Each GAT layer consists of two sub-layers.
-The first sub-layer calculates the attention weights of every edge $(v_i, v_j)$ $\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j]$ and aggregates the attention weights of all adjacency edges of every vertex $v_i$ as $\sum_{k \in \mathcal{N}(i)}\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l,k}_i \parallel \hat{\boldsymbol{h}}^{l,k}_j] ))$.
-The second sub-layer uses 
-During the message passing, it dynamically determines the weight for an edge based on the hidden feature vectors of its two end vertices.
-Moreover, it adopts the multi-head mechanism that generates $K$ independent views for an edge, where $K$ is a hyperparameter.
-GAT moves the vertex update function $\gamma$ before the edge calculation.
-$\hat{\boldsymbol{h}}^{l,k}_{i} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}$ with $1 \leq k \leq K$ are conducted for every vertex $v_i$ before the message function $\phi$.
-$\phi$ uses $\hat{\boldsymbol{h}}^{l,k}_{i}$ to get the weight of each edge in every head $k$.
-After the edge calculation, GAT uses the aggreated vector $\boldsymbol{s}^l_i$ directly as the output hidden vector.
+GAT introduces the attention and multi-head mechanism into the graph neural networks.
+The $K$ heads generate $K$ independent views for an edge, where $K$ is a hyper-parameter.
+Each GAT layer consists of a preprocessing step and two sub-layers.
+In the preprocessing step, GAT calculates the attention vectors $\hat{\boldsymbol{h}}^{l}_{i,(k)}$ for every vertex $v_i$ in every head $k$.
+The first sub-layer uses the attention vectors to calculate the attention weights of every edge in every head $\boldsymbol{m}^{l,0}_{j,i,(k)}$.
+After the message-passing, the first-layer gets the summation of attention weights of every vertex in every head $\hat{\boldsymbol{a}}^{l,0}_{i,(k)}$.
+The second sub-layer gets the normalized attention weights $\alpha_{j, i, (k)}$ for every edge in every head and aggregates the hidden feature vectors with the normalized weights in the message-passing.
+GAT uses the aggreated vector $\boldsymbol{s}^{l,1}_i$ of the second sub-layer as the output hidden vector directly.
 

### 2020-07-19 Manuscript/sec2-review-of-graph-neural-network.tex
更新GAT的描述

@@
 	\includegraphics[width=0.7\columnwidth]{figs/illustration/GNN_complexity_quadrant.pdf}
-	\caption{Complexity quadrants of typical GNNs. If two GNNs have the same complexity under the Big-O notation, we further compare their complexity according to how many parameters they need to train.}
+	\caption{Complexity quadrants of typical GNNs. We compare the complexity according to the number of sub-layers, the Big-O notation and the number of parameters to train.}
 	\label{fig:gnn_complexity_quadrant}
@@
 The $K$ heads generate $K$ independent views for an edge, where $K$ is a hyper-parameter.
+The views of $K$ heads can be merged by concatenating or by averaging.
+For concatenating, the dimension of the hidden feature vector of each view is $d_{out}/K$.
+For averaging, the dimension is $d_{out}$, multiplying the complexity by $K$.
 Each GAT layer consists of a preprocessing step and two sub-layers.

### 2020-07-19 Manuscript/sec2-review-of-graph-neural-network.tex
更新GAT的算法描述和实验设置描述。

@@
 The views of $K$ heads can be merged by concatenating or by averaging.
-For concatenating, the dimension of the hidden feature vector of each view is $d_{out}/K$.
-For averaging, the dimension is $d_{out}$, multiplying the complexity by $K$.
+For concatenating, the dimension of the hidden feature vector of each head $d_{head}$ is $d_{out}/K$.
+For averaging, $d_{head}$ is $d_{out}$, multiplying the complexity by $K$.
 Each GAT layer consists of a preprocessing step and two sub-layers.

### 2020-07-19 Manuscript/sec3-experiment-design.tex
更新GAT的算法描述和实验设置描述。

@@
 The server had 40 cores and 90 GB main meory.
-The server was also equipped with a NVIDIA Tesla T4 GPU card with 16GB GDDR6 memory.
+The server was equipped with a NVIDIA Tesla T4 GPU card with 16GB GDDR6 memory.
 For the software environment, we adopted Python 3.7.7, PyTorch 1.5.0 and CUDA 10.1.
 We implemented all the GNNs with PyTorch Geometric 1.5.0.
-The execution time decomposition was collected with NVIDIA Nsight systems.
 
@@
 \paragraph{GNN Implementation}
-We implemented the four typical GNNs--GCN, GGNN, GAT, GaAN--with PyTorch Geometric 1.5.0.
+We implemented the four typical GNNs (GCN, GGNN, GAT, GaAN) with PyTorch Geometric 1.5.0.
 To compare the performance characteristics of four GNNs side-by-side, we used a unified GNN structure for them: Input Layer $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ Softmax Layer (to prediction).
 The structure was popular in the experimental evaluation of GCN \cite{kipf2017_gcn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan}.
-Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, for GGNN, we added two MLP layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
+Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, we added two MLP layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
 We stored the dataset and the model parameters in the memory of GPU.
-We conducted all the training on GPU.
+All the training was conducted on GPU.
 
 \paragraph{Hyper-parameters}
-We use $dim(\boldsymbol{v}$ to denote the dimension of a vector $\boldsymbol{v}$.
+We use $dim(\boldsymbol{v})$ to denote the dimension of a vector $\boldsymbol{v}$.
 We picked the hyper-parameters of GNNs according to their original papers.
-As a GNN used different hyper-parameters for different tasks, we picked the most popular hyper-parameters.
-Some hyper-parameters, such as the numbers of GNN layers and the dimensions of hidden feature vectors, were common hyper-parameters in all the GNNs.
+As GNNs used different hyper-parameters for different datasets, we picked the most popular hyper-parameters and used the same set of hyper-parameters for all the datasets in our experiments.
+Some hyper-parameters like the dimensions of hidden feature vectors were common hyper-parameters.
 We set them to the same values in the four GNNs.
-For GCN/GAT/GaAN, $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, $dim(\boldsymbol{h}^1_i)=64$, and $dim(\boldsymbol{h}^2_i)$ was the number of classes.
+For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, $dim(\boldsymbol{h}^1_i)=64$, and $dim(\boldsymbol{h}^2_i)=\#Classes$.
+For GAT, we set the hyper-parameters according to \cite{huang2018_gat}.
+The first GAT layer had 8 heads with $d^0_{head}=8$ and merged the heads by concatenating.
+The second GAT layer used a single head with $d^1_{head}=d^1_{out}=\#Classes$.
 For GGNN, since it uses extra MLP layers to transform the dimensions of the input/output feature vectors, we set $dim(\boldsymbol{h}^0_i) = dim(\boldsymbol{h}^1_i) = dim(\boldsymbol{h}^2_i) = 64$.
-We used 8 heads in GAT and GaAN.
-$d_{head}=8$ in GAT.
-$d_a=d_v=8$ and $d_m=64$ in GaAN.
+We used 8 heads in the both GaAN layers with $d_a=d_v=8$ and $d_m=64$.
 

### 2020-07-19 Manuscript/sec4-experiments.tex
增加了没有添加的图片

@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gcn.pdf}}
-    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gat.pdf}}
-    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_vertex_edge_cal_proportion_gaan.pdf}}
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_gat.pdf}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_gaan.pdf}}
     \caption{Vertex/edge calculation time-consuming ratio.}

### 2020-07-19 Manuscript/sec2-review-of-graph-neural-network.tex
update

--- 2020-07-19 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 In each mini-batch, they sample a small subgraph from the whole graph $\mathcal{G}$ and uses the subgraph to update the model parameters.
-In other words, the sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:graph_sampling}.
+In other words, the sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:gnn_sampling}.
 Inactive graph neurons and connetions do not participate in the training of this mini-batch, saving lots of computation and storage costs.
@@
 Then they repeatedly sample the neighbors of those vertices in the previous layer until the input layer.
-The sampled subgraphs of different GNN layers may be \emph{different}, as shown in \figurename~\ref{fig:gnn_sampling_neigbhor_sampling}.
+The sampled subgraphs of different GNN layers may be \emph{different}, as shown in \figurename~\ref{fig:gnn_sampling_neighbor_sampling}.
 GraphSAGE \cite{hamilton2017_graphsage} is the representative technique.
@@
 	\centering
-	\subfloat[Neighbor sampling\label{fig:gnn_sampling_neigbhor_sampling}]{\includegraphics[height=4cm]{figs/illustration/layer_sampling.pdf}}
+	\subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4cm]{figs/illustration/layer_sampling.pdf}}
 	%

### 2020-07-19 Manuscript/sec4-experiments.tex
update
update section 4.

--- 2020-07-19 Manuscript/sec4-experiments.tex
@@
 
-In this section, we answers the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
-Without otherwise mentioned, when we report the training time per epoch of a GNN, we measure the training time of 50 epoches, exclude the epoches with abnormal training time \footnote{During the training of some epoches, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
+We answer the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
+Without otherwise mentioned, the reported training time per epoch is the average wall-clock training time of 50 epoches, excluding abnormal epoches \footnote{During the training of some epoches, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
 Assume Q1 and Q3 are the 25\% and 75\% quantiles of the training time of 50 epoches, respectively.
-We regard the epoches with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epoches.} and report the average time of the remaining epoches.
+We regard the epoches with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epoches.}.
 
@@
 
-Fixing other hyper-parameters, the time complexity of $\phi$/$\gamma$ is linear to each hyper-parameter separately, according to the analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
+Fixing other hyper-parameters, the time complexities of $\phi$ and $\gamma$ are linear to each hyper-parameter separately, according to the analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
 If we increase one of the hyper-parameters, the training time should also increase linearly.
@@
     \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}
-
-    \subfloat[GAT]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}}
-
-    \subfloat[GaAN]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}}
+    \\
+    \subfloat[GAT\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}}
+    \\
+    \subfloat[GaAN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}}
 
@@
 
-For GCN (\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}) and GGNN (\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}), the only modifiable hyper-parameter is the hidden dimension $dim(\boldsymbol{h}^1)$, as $dim(\boldsymbol{h}^0)$ and $dim(\boldsymbol{h}^2)$ is determined by the dataset with $dim(\boldsymbol{h}^0)=dim(\boldsymbol{x})$ and $dim(\boldsymbol{h}^2)=$\#Classes.
-$dim(\boldsymbol{h}^1)$ affects the dimensions of the output hidden feature vector of Layer 0 $d^{0}_{out}$ and the input hidden feature vector of Layer 1 $d^1_{in}$ simultaneously, i.e., $dim(\boldsymbol{h}^1) = d^0_{out} = d^1_{in}$.
-The training time of GCN and GGNN increased linearly under big $dim(\boldsymbol{h}^1)$, consistent with the time complexity analysis.
+For GCN and GGNN, the only modifiable hyper-parameter is the hidden dimension $dim(\boldsymbol{h}^1)$ with $dim(\boldsymbol{h}^1) = d^0_{out} = d^1_{in}$.
+$dim(\boldsymbol{h}^0)$ and $dim(\boldsymbol{h}^2)$ is determined by the dataset with $dim(\boldsymbol{h}^0)=dim(\boldsymbol{x})$ and $dim(\boldsymbol{h}^2)=$\#Classes.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn} show that the training time of GCN and GGNN increased linearly under big $dim(\boldsymbol{h}^1)$, consistent with the time complexity analysis.
 
-For GAT (\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}), it uses the multi-head mechanism.
-Each head outputs a hidden feature vector of dimension $d_{out}$.
-Its time complexity is affected by the dimensions of the input/output hidden vectors $d_{in}$/$d_{out}$ and the number of heads $K$.
-The output hidden vector dimension of each layer is $d_{out}=K d_{head}$.
-Because of GAT model structure $d^1_{in}=d^0_{out}$, adjusting $d_{head}$ and $K$ is equivalent to adjusting Layer1’s $d^1_{in}$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time increases linearly with $d_{head}$ and $K$, two.
-For GaAN, which also has a multi-head mechanism, its computational complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} demonstrates that GaAN training time is linearly affected by hyperparameters.
+For GAT, we modified the number of heads $K$ and the dimension of each head $d_{head}$ in the GAT layer 0.
+The dimenstion of the hidden feature vector was determined correspondingly as $d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1) = K h_{head}$.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time increases linearly under big $d_{head}$ and $K$.
+
+For GaAN, it also adopts the multi-head mechanism.
+Its time complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time of GaAN is linearly affected by hyperparameters.
 These experiments prove the complexity analysis results given in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}.
@@
 When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.
-
-\begin{figure}
-    \centering
-    \includegraphics[height=8cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.png}
-    \caption{The influence of hyperparameters on GAT vertex/edge calculation time}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[height=8cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.png}
-    \caption{The influence of hyperparameters on GaAN vertex/edge calculation time}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
-\end{figure}
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.png}
+    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.pdf}
     \caption{The change of the memory expansion ratio with the dimension of the input feature vector. dataset: cam, other datasets are similar}

### 2020-07-19 Manuscript/sec4-experiments.tex

@@
     \caption{The change of memory usage with the average degree of the graph (R-MAT random graph, the number of vertices is fixed at 10k, and the input feature vector dimension is 32}
-    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
+    \label{fig:exp_memory_expansion_ratio_input_graph_number_of_edges}
 \end{figure}

### 2020-07-19 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 4.

@@
 $v_i$'s aggregated vector $\boldsymbol{s}^l_i$ and its hidden vector $\boldsymbol{h}^l_i$ from the previous GNN layer are fed into the \emph{vertex update} function $\gamma^l$ to calculate the output hidden vector $\boldsymbol{h}^{l+1}_i$ of the current layer $l$, i.e., $\boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \boldsymbol{s}^l_i)$
-The end-to-end training requires $\phi^l$ and $\gamma^l$ (like multi layer perceptrons and GRU) and $\Sigma_l$ (like mean, sum, element-wise min/max) are \emph{differentiable} to make the whole GNN differentialble.
+The end-to-end training requires $\phi^l$ and $\gamma^l$ (like multi-layer perceptrons and GRU) and $\Sigma_l$ (like mean, sum, element-wise min/max) are \emph{differentiable} to make the whole GNN differentialble.
 

### 2020-07-19 Manuscript/sec4-experiments.tex
Update section 4.

@@
 \label{sec:effects_of_hyper-parameters_on_performance}
+
+Theoretically, the hyper-parameters should affect the training time in a \emph{linear} way.
+According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexities of $\phi$ and $\gamma$ are linear to each hyper-parameter separately.
+If we increase one of the hyper-parameters and fix the others, the training time should increase linearly.
 
@@
 
-Fixing other hyper-parameters, the time complexities of $\phi$ and $\gamma$ are linear to each hyper-parameter separately, according to the analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
-If we increase one of the hyper-parameters, the training time should also increase linearly.
-In order to verify the linearity, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.
+To further evaluate the effects of hyper-parameters, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.
 
@@
 
-    \caption{Effects of hyper-parameters on vertex/edge calculation time.}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time.}
     \label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
@@
 
-For GaAN, it also adopts the multi-head mechanism.
+For GaAN, it is also based on the multi-head mechanism.
 Its time complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time of GaAN is linearly affected by hyperparameters.
-These experiments prove the complexity analysis results given in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex}.
-The training time of each GNN model increases linearly with the increase of hyperparameters.
-When the hidden vector dimension $d_{in}$ is too low, the calculations involving hidden vectors account for a very low proportion of the total calculation time,
-resulting in an insignificant change in the total training time.
-When the hidden vector dimension is large enough, the total training time increases linearly with $d_{in}$.
-
-\paragraph{The effects of hyper-parameters on memory usage}
-\figurename~\ref{fig:exp_hyperparameter_memory_usage} shows how each GNN model's memory usage varies with the algorithm's hyperparameters.
-With the increase of hyperparameters, GNN's memory usage also increases linearly.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time increased linearly with the hyper-parameters, except for $dim(\boldsymbol{h}^1)$.
+As $dim(\boldsymbol{h}^1)$ increased, the training time increased first slightly and then linearly.
+We could observe similar phenomena in GCN, GGNN and GAT with low hyper-parameters.
+When the hyper-parameter was too low, the GNN training could not make use of the full computing power of the GPU.
+When it became high enough, the training time increased linearly.
 
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.png}}
-    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.png}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.png}}\\
-    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
-    \caption{The effect of hyperparameters on GPU memory usage during the training phase (excluding the dataset memory)}
+    \subfloat[GCN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.png}}
+    \subfloat[GGNN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.png}}\\
+    \subfloat[GAT]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.png}}\\
+    \subfloat[GaAN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
+    \caption{Effects of hyper-parameters on the peak GPU memory usage during the training, excluding the memory used by the dataset and the model parameters.}
     \label{fig:exp_hyperparameter_memory_usage}
@@
 
+The experimental results support the time complexity analysis.
+We further measured the effects of the hyper-parameters on the peak GPU memory usage in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
+The memory usage also increased linearly as the hyper-parameters increased for all GNNs, except for GaAN on $dim(\boldsymbol{h}^1)$.
+As the hidden feature vectors $\boldsymbol{h}^1$ consumed a small proportion of memory in GaAN, the growth in the memory usage was not noticable until $dim(\boldsymbol{h}^1)$ was large enough.
+
 \paragraph{Summary}
 
-We can answer the question Q1 in \ref{sec:experimental_env}: the complexity analysis in \tablename~\ref{tab:gnn_overview_edge}, \tablename~\ref{tab:gnn_overview_vertex} is valid.
-\textbf{GNN training time and memory usage are linearly related to hyperparameters}.
-This allows algorithm engineers to use larger hyperparameters to increase the complexity of GNN without worrying about the time-consuming training and the explosive growth of memory usage.
+The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} is valid.
+The hyper-parameters affect the training time and the memory usage of the GNN training \textbf{in a linear way}.
+Algorithm enginners can use larger hyper-parameters to increase the expressive power of a GNN model without worrying the explosive growth in the training time and memory usage.
 
@@
 
-In this subsection, we aims to find what stage is the most time-consuming stage in GNN training by decomposing the time-consuming training.
+To find out which stage dominates the training time, we breakdown the training time and analyze the performance bottleneck level by level.
 
-\paragraph{Vertex/edge calculation time-consuming proportion analysis}
-
-\figurename~\ref{fig:exp_vertex_edge_cal_proportion} shows the ratio of the vertex/edge calculation time of different GNN layers
-to the total training time (including forward, backward and evaluation). GCN spends most of time on edge calculation in most datasets. A special case is  \textit{cph} dataset because of
-the dimension of the input feature vector of this dataset is very high, resulting in the high vertex calculation of Layer0.
-High vertex calculation makes GGNN's vertex calculation time-consuming ratio significantly higher than other algorithms.
-But in most datasets, for GGNN, edge calculation still occupies the majority of total time.
-In \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close for GGNN
-because the average degree of the two datasets is low (only 4.5 and 2.8).
-For the GAT and GaAN algorithms, due to their high edge calculation complexity, their edge calculation cost time is absolutely dominant.
-In summary, \textbf{edge calculation is the main time-consuming factor of GNN training}, especially in the case of more complicated edge calculation.
-
-Experiments also show that \textbf{the average degree of the dataset affects the time-consuming proportion of vertex/edge calculation}.
-We use the R-MAT generator to generate random graphs with an average degree between 10 and 100. The number of nodes of these graphs is fixed at 50k.
-Then we measure the change of the time-consuming proportion of the vertex/edge calculation in each GNN model varies with the average degree of the graph,
-as shown in \figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}. The edge calculation time increases linearly with the increase of the average degree,
-\textbf{The edge calculation time dominates the entire calculation time in most cases}.
-Only when the vertex calculation complexity is very high and the average degree is very low, the vertex calculation time can overtake the edge calculation time.
-Therefore, \textbf{the focus of GNN training optimization should improve the efficiency of edge calculation}.
+\subsubsection{Layer Level}
 
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_gaan.pdf}}
-    \caption{Vertex/edge calculation time-consuming ratio.}
+    \caption{Training time breakdown on the layer level, including the time spent on the forward, backward and evaluation phase.
+Each layer is further decomposed into the vertex and the edge calculation stages.}
     \label{fig:exp_vertex_edge_cal_proportion}
 \end{figure}
+
+\figurename~\ref{fig:exp_vertex_edge_cal_proportion} decomposes the training time of a GNN on the layer level.
+The training time of each layer is the summation of the time in the forward, backward and evaluation phases.
+In GCN, GAT and GaAN, the time spent on the layer 0 was much larger than the layer 1.
+In those GNNs, the dimensions of the input/output feature vectors in the layer 0 were much larger than the dimensions in the layer 1.
+$d^0_{in}=dim(\boldsymbol{x})$, $d^0_{out}=d^1_{in}=64$ and $d^1_{out}=\#Class$ and $dim(\boldsymbol{x}) \gg \#Class$.
+For GaAN, since it required the dimensions of the input/output feature vectors must be same, $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers were close.
+
+Each GNN layer can be further divided in the vertex and the edge calculation stages.
+In \figurename~\ref{fig:exp_vertex_edge_cal_proportion}, GCN spent most of the training time on the edge calculation in most datasets.
+A special case is \texttt{cph} dataset.
+The dimension of the input feature vectors was very high in \texttt{cph}, making the vertex calculation stage of the GCN Layer 0 spend considerable time.
+GGNN also spent the majority of its training time on the edge calculation.
+But the high time complexity of its vertex update function $\gamma$ made the ratio of the vertex calculation in the total training time much higher than other GNNs.
+%In \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close for GGNN
+%because the average degree of the two datasets is low (only 4.5 and 2.8).
+For GAT and GaAN, due to their high edge calculation complexity, the edge calculation is the absolutely dominant stage.
+In summary, \emph{the edge calculation is the most time-consuming stage in the GNN training}.
 
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.png}}
-    \caption{The effect of the average vertex degree on the time-consuming proportion of vertex/edge calculation.}
+    \caption{Effects of the average degree on the time proportion of the vertex/edge calculation. Graphs were generated with the R-MAT generator by fixing the number of vertices as 50,000. }
     \label{fig:exp_avg_degree_on_vertex_edge_cal_time}
@@
 
-\paragraph{Time-consuming decomposition analysis of edge calculation}
+The experimental results also indicate that the average degree of the dataset affects the time-consuming proportion of the vertex/edge calculation.
+For GaAN, the time spent on the vertex calculation exceeded the edge calculation on the \texttt{pub} and \texttt{cam} datasets, because the avaerage degrees of the two datasets were low, making $|\mathcal{E}|$ and $|\mathcal{V}|$ much closer.
+To evaluate the effects of the average degree, we used the R-MAT model to generate random graphs with 50k vertices and the average degrees ranging from 2 to 100.
+\figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time} shows the training time of the four GNNs under different average degrees.
+As the average degree increased, the training time of the edge calculation grew \emph{linearly}.
+For GCN, GAT and GaAN, the edge calculation dominated the entire training time even under small average degrees.
+Only for GGNN that had high vertex and low edge calculation complexities, the training time of the vertex calculation could exceed the edge calculation under low average degrees ($<5$).
+Therefore, \emph{to reduce the GNN training time, one should focus on improving the efficiency of the edge calculation}.
+
+\subsubsection{Step Level in Edge Calculation}
 
@@
     \centering
-    \includegraphics[width=1\columnwidth]{figs/illustration/steps_in_edge_calculation.png}
-    \caption{Step decomposition of edge calculation}
+    \includegraphics[width=1\columnwidth]{figs/illustration/steps_in_edge_calculation.pdf}
+    \caption{Step decomposition of the edge calculation in the GNN layer $l$.}
     \label{fig:steps_in_edge_calculation}
@@
 
-The edge calculation phase can be further decomposed into four steps of collect, message, aggregate and update,
-as shown in \figurename~\ref{fig:steps_in_edge_calculation}. The figure shows the edge calculation process of GNN layer $l$,
-edge index is a matrix that holds the edge sets of the graph with shape $M*2$, where $M$ is the number of edges,
-and two columns of the matrix respectively store the source vertex and the target vertex of each edge.
-Edge index remains unchanged throughout the calculation process.
-The collect step is used to prepare data structure required for edge calculation and will use the vertex hidden vector of the GNN layer $\boldsymbol{h}_i^l (1 \leq i \leq N)$
-as input, which is copied to the two layers of each edge according to the edge index, forming the input parameter tensor of the edge calculation function $\phi$
-(including $\boldsymbol{h}_i^l$,$\boldsymbol{h}_j^ l$ and $\boldsymbol{e}_{j, i}^l$).
-There is no calculation in this step, only data access is involved.
-The message step calls the function given by the user $\phi$ to complete the edge calculation process, and get message vector of each edge $\boldsymbol{m}_{j, i}^l (\boldsymbol{e}_{j, i}^l \in E(G))$.
-The aggregate step is based on the target of each edge, the message vector with the same target vertex is aggregated by the aggregation operator $\Sigma$,
-and then each vertex aggregation vector $\boldsymbol{a}_i^l (1 \leq i \leq N)$ is obtained.
-The last update step is optional, and it can perform additional correction processing on the aggregated vector (for example, adding bias to GCN).
-The aggregated vector $a_i^l$ after the update process will be input into the vertex calculation function $\gamma$ as an input parameter.
+In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collect, message, aggregate and update, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
+The edge index is a matrix with $M$ rows and 2 columns that holds the edge set of the graph, where $M=|\mathcal{E}|$.
+The two columns of the matrix store the source vertex and the target vertex of each edge, respectively.
+The collect step copies the vertex feature vectors from the previous layer $\boldsymbol{h}_i^l$ to the ends of each edge 
+in the edge index, to form the parameters $[\boldsymbol{h}^l_i, \boldsymbol{h}^l_{j}, \boldsymbol{e}^l_{i,j}]$ of the message function $\phi$.
+This step only involves the data movement.
+The message step calls the message function $\phi$ to get message vectors of all edges $\boldsymbol{m}_{i, j}^l$.
+The aggregate step aggregates the message vectors with the same target vertex into a single aggregated vector $\boldsymbol{s}^l_i$ with the aggregation operation $\Sigma$.
+The update step \emph{optinally} performs additional transformation on the aggregated vectors (for example, adding bias to GCN).
+The aggregated vectors $\emph{s}^l_i$ (after the update step) will be fed into the vertex update function $\gamma$ as an input parameter.
 

### 2020-07-20 Manuscript/sec2-review-of-graph-neural-network.tex
更新Section 4

@@
 According to the associative law of the matrix multiplication, $\boldsymbol{h}^{l+1}_i = \sum_{v_j \in \mathcal{N}(v_i)}{e_{j,i}\boldsymbol{W}^l\boldsymbol{h}^l_j}$.
-Since the dimension of $\boldsymbol{h}^{l+1}_i$ is usually smaller than $\boldsymbol{h}^l_i$ in practical GCNs, the implementation of GCN in PyTorch Geometric chooses to first conduct the vertex calculation $\hat{\boldsymbol{h}}^l_j = \boldsymbol{W}^l\boldsymbol{h}^l_j$ for each vertex $v_j$ and then conduct the edge calculation $\boldsymbol{h}^{l+1}_i=\sum_{v_j\in\mathcal{N}(v_i)}{\hat{\boldsymbol{h}}^l_j}$.
+Since the dimension of $\boldsymbol{h}^{l+1}_i$ is usually smaller than $\boldsymbol{h}^l_i$ in practical GCNs, the implementation of GCN in PyTorch Geometric chooses to first conduct the vertex calculation $\hat{\boldsymbol{h}}^l_j = \boldsymbol{W}^l\boldsymbol{h}^l_j$ for each vertex $v_j$ and then conduct the edge calculation $\boldsymbol{h}^{l+1}_i=\sum_{v_j\in\mathcal{N}(v_i)}{e_{j,i}\hat{\boldsymbol{h}}^l_j}$.
 As $\hat{\boldsymbol{h}}^l_j$ has the same dimension as $\boldsymbol{h}^{l+1}_i$, the implementation significantly reduces the  computation cost of the edge calculation.
@@
 GGNN further requires the dimension of $\boldsymbol{h}^{l+1}$ is equal to the dimension of $\boldsymbol{h}^l$.
+Since the message function $\phi$ only uses the hidden feature vector $\boldsymbol{h}^l_j$ of the source vertex $v_j$ of an edge $(v_j, v_i)$, in the implementation, GGNN conducts the pre-processing vertex calculation $\hat{\boldsymbol{h}}^l_i=\boldsymbol{W}\boldsymbol{h}^l_i$ for every vertex $v_i$ before the message-passing.
+The message function $\phi$ directly uses $\hat{\boldsymbol{h}}^l_j$ as the message vector for the edge $(v_j, v_i)$. 
+By this way, GGNN further reduces the time complexity of the edge calculation to $O(1)$ without increasing the time complexity of the vertex calculation.
 

### 2020-07-20 Manuscript/sec4-experiments.tex
更新Section 4

@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_gaan.pdf}}
-    \caption{Training time breakdown on the layer level, including the time spent on the forward, backward and evaluation phase.
+    \caption{Training time breakdown on the layer level.
+The training time of each layer includes the time spent on the forward, backward and evaluation phases.
 Each layer is further decomposed into the vertex and the edge calculation stages.}
@@
 Only for GGNN that had high vertex and low edge calculation complexities, the training time of the vertex calculation could exceed the edge calculation under low average degrees ($<5$).
-Therefore, \emph{to reduce the GNN training time, one should focus on improving the efficiency of the edge calculation}.
+Therefore, \emph{improving the efficiency of the edge calculation is the key to reduce the GNN training time}.
 
@@
 The message step calls the message function $\phi$ to get message vectors of all edges $\boldsymbol{m}_{i, j}^l$.
-The aggregate step aggregates the message vectors with the same target vertex into a single aggregated vector $\boldsymbol{s}^l_i$ with the aggregation operation $\Sigma$.
-The update step \emph{optinally} performs additional transformation on the aggregated vectors (for example, adding bias to GCN).
-The aggregated vectors $\emph{s}^l_i$ (after the update step) will be fed into the vertex update function $\gamma$ as an input parameter.
-
-We performed the execution time decomposition of the edge calculation process of each GNN algorithm on different datasets,
-and the results are shown in \figurename~\ref{fig:exp_edge_calc_decomposition}.
-The time-consuming decomposition of the edge calculation of each GNN is relatively stable and rarely affected by dataset.
-Although the collect step only performs data preparation, it occupies a lot of execution time in all GNNs.
-The message step in the GNN (GAT and GaAN) with high edge calculation complexity occupies the absolute dominant.
-Although its edge calculation in GCN only has a simple multiplication operation, it still takes more than 20\% of the time;
-In GGNN, because its edge calculation function $\boldsymbol{m}_{j,i }^l=\boldsymbol{W}^l\boldsymbol{h}_{j}^l$ is only related to the source vertex,
-so in the implementation of PyG will be $\boldsymbol{W}^l\boldsymbol{h}_j The calculation of ^l$ is carried out before the edge calculation starts
-(because this part of the calculation is only related to vertices, so we count the calculation into the vertex calculation phase).
-The calculated result is cached, and it is directly read when the message step is performed. As a result, the message step of GGNN gets 0.
-For the aggregate step, it occupies at least 35\% of training time of GNN (GCN and GGNN) with low edge computational complexity,
-while the GNN with high edge computational complexity (GAT and GaAN), whose time consumption is close to the collect step,
-and both are much lower than the message step. Experiments show that \textbf{for an algorithm with high edge calculation complexity,
-    the message step is the bottleneck of its performance, and it should be optimized}; and \textbf{For algorithms with low computational complexity,
-    optimizing the collect and aggregate steps can significantly reduce training time}.
+The aggregate step aggregates the message vectors with the same target vertex into a aggregated vector $\boldsymbol{s}^l_i$ with the aggregation operation $\Sigma$.
+The update step is optinal.
+It performs additional transformation on the aggregated vectors (for example, adding bias in GCN).
+The aggregated vectors $\boldsymbol{s}^l_i$ (after the update step) will be fed into the vertex update function $\gamma$ as one of the input parameters.
 
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.png}}
-    \caption{Time-consuming decomposition of edge calculations (including Layer0 and Layer1).}
+    \caption{Training time breakdown of the edge calculation stage (including both GNN layers).}
     \label{fig:exp_edge_calc_decomposition}
@@
 
-\paragraph{Hot-spot operator analysis}
-Various functions for vertex/edge calculation $\phi, \Sigma,\gamma$ consist of a series of basic operators,
-which are mapped to specific basic operators on the GPU (matrix multiplication mm, elementwise multiplication mul and index by tensor index\_select)
+We decomposed the execution time of the edge calculation step in \figurename~\ref{fig:exp_edge_calc_decomposition}.
+In each GNN, the proportion of the four steps were rather stable, rarely affected by datasets.
+For GAT and GaAN with the high edge calculation complexity, the message step consumed most of the execution time.
+For GCN and GGNN with the low complexity, the proportions of the steps were close.
+Since the message function $\phi$ of GGNN used the pre-computed $\hat{\boldsymbol{h}}^l_i$ as the message vector directly in the implementation, the time spent on the message step of GGNN was negligible.
+Although the collect step did not conduct any computation and only involved data movement, it occupied noticeable execution time in all the GNNs.
+The experiments show that \emph{the performance bottleneck on the step level depends on the complexity of the edge calculation}.
+For GNNs with the high edge calculation complexity, the message function $\phi$ is the performance bottleneck.
+Optimizing its implementation can significantly reduce the training time.
+For the other GNNs, optimization should focus on reducing the costs of the collect and the aggregation steps.
+Addtionally, improving the efficiency of the collect step can benefit all GNNs.
 
-Figure~\ref{fig:exp_top_basic_ops} shows the five operators with the highest time-consuming proportion in each GNN,
-the operator in the legend The order is determined by the average time-consuming ratio.
+\subsubsection{Operator Level}
+
+The functions $\phi$, $\Sigma$ and $\gamma$ in the vertex and edge calculation are made up of a series of basic operators implemented on GPU, like the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
+\figurename~\ref{fig:exp_top_basic_ops} shows the five most time-consuming basic operators in each GNN, averaged over all the real-world graphs in \tablename~\ref{tab:dataset_overview}.
 
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gcn.png}}
-    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_ggnn.png}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gat.png}}
-    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gaan.png}}
-    \caption{The time-consuming ratio of basic operators (including the forward, backward and evaluation stages)}
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gat.pdf}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gaan.pdf}}
+    \caption{Top 5 time-consuming basic operators of typical GNNs. The time proportion of each basic operator is averaged over all graphs with the error bar indicating the maximal and the minimal.}
     \label{fig:exp_top_basic_ops}
@@
 
-The analysis of the time-consuming operators of each algorithm is as follows:
+\paragraph{GCN}
+The most time-consuming basic operator was the matrix multiplication \texttt{mm} used in the vertex update function $\gamma$.
+The elementwise multiplication \texttt{mul} used in the message function $\phi$ was also time-consuming.
+The other three operators were used in the edge calculation: \texttt{scatter\_add\_} for the aggregation step in the forward phase, \texttt{gather} for the aggregation step in the backward phase, and \texttt{index\_select} for the collect step.
+For GCN, the basic operators related to the edge calculation consumed the majority of the training time.
 
-\begin{enumerate}
-    \item The matrix multiplication operator mm in GCN is mainly used for vertex calculation $\gamma$,
-          this operator is particularly time-consuming on the \textit{cph} dataset,
-          because the dimensionality of the vertex feature vector input by \textit{cph} is very high,
-          making the matrix multiplication in the vertex calculation of Layer0 The calculation is very high.
-          Mul is the multiplication operation in the edge calculation function $\phi$.
-          Both scatter\_add and gather are used to implement the aggregation step $\Sigma$ in the edge calculation,
-          where the former is used in the forward stage and the latter is used in backward Phase.
-          The index\_select operator is used in the collect step of the edge calculation.
-          For the GCN algorithm, the edge calculation related operators occupy the main time-consuming.
-          The time-consuming among the operators is relatively average, and there is no particularly outstanding performance bottleneck.
-    \item The most time consuming in GGNN is also the matrix multiplication mm operator,
-          which is mainly used for the vertex calculation function $\gamma$. The scatter\_add, index\_select and gather operators
-          are used for edge calculations. And the \_thnn\_fused\_gru\_cell is used in the backward calculation of GRU.
-          GGNN because of vertices With the increase in calculation complexity, the time-consuming time of the mm operator has increased significantly.
-    \item The four most time-consuming operators in GAT are all related to the edge calculation.
-          Mul, \_index\_put\_impl and sum are used to implement the edge calculation function $\phi$.
-          The index\_select operator is used in the collect phase of the edge calculation.
-          The mm operator is used vertex calculation function $\gamma$.
-    \item The most time-consuming matrix multiplication operator mm in GaAN is used for both edge calculation and vertex calculation,
-          where edge calculation is dominant. Mul and cat are used for the $\phi$ function in edge calculation.
-\end{enumerate}
+\paragraph{GGNN}
+The top basic operator was \texttt{mm} used in the vertex calculation.
+Due to the high time complexity in $\gamma$, the proportion of the \texttt{mm} operator were much higher than the other operators.
+The \texttt{thnn\_fused\_gru\_cell} operator that was used in the backward phase of $\gamma$ was also noticeable.
+The other three operators were used in the edge calculation.
 
-In terms of commonality,
-\textbf{The main time-consuming of GNN calculation is still matrix multiplication mm, elementwise multiplication mul},
-so it is very suitable for calculation with GPU. Although the calculation of the aggregate step in edge calculation is relatively simple,
-but it involves data synchronization and non-regular calculations (the degree of different vertices is very different),
-the related operators scatter\_add and gather still occupy a certain amount of time.
-Although the collection step in the edge calculation does not have any calculationss,
-but the related calculations index\_select operator still accounts for about 10\% of the time-consuming.
-\textbf{aggregate step and collect step are one of the computational performance bottlenecks of all GNN training},
-optimizing the corresponding operator will improve the training efficiency of all GNNs.
+\paragraph{GAT}
+All the top basic operators except for \texttt{mm} were related to the edge calculation.
+The \texttt{mm} operator was used in the vertex update function $\gamma$.
 
-\paragraph{Summary of performance bottlenecks}
+\paragraph{GaAN}
+The top basic operator was \texttt{mm}.
+It was used in both the vertex and the edge calculation, where the edge calculation is dominant.
+The scalar multiplication \texttt{mul} and the concatenation \texttt{cat} operators were used in the message function $\phi$.
 
+In general, the most time-consuming operator in GNN calculation is still the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul}, \emph{making GNN training suitable for GPU}.
+Although the aggregate step in the edge calculation is relatively simple (like sum and mean), the related operators \texttt{scatter\_add} and \texttt{gather} still consumed a certain amount of the time.
+They have to synchronize between hardware threads to avoid updating the same aggregated vector at the same time and they conducted non-regular memory access with the access pattern determined by the edge set dynamically.
+For GPU, they were less efficient than \texttt{mm}.
+The index-based selection \texttt{index\_select} operator from the collection step consumed around 10\% of time in all GNNs.
+Though GPUs have high on-chip memory bandwidth, improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} (like overlapping them with $\phi$) can benifit the training of all kinds of GNNs.
+
+\paragraph{Summary}
+The GNN training is suitable for GPU.
+The \textbf{edge calculation is the main performance bottleneck}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
+The performance bottleneck in the edge calculation depends on the time complexity of the message function $\phi$.
 \begin{itemize}
-    \item \textbf{The performance bottleneck of GNN training is affected by the average degree of the dataset}.
-          Because the average degree of most real-world graphs is above 10 degrees \cite{network-repository},
-          the performance bottleneck of GNN training will be concentrated on the edges calculation section.
-    \item \textbf{According to the calculation complexity of the edge calculation function $\phi$, the performance bottleneck of GNN in edge calculation is different}:
-          \begin{itemize}
-              \item If the computational complexity of $\phi$ is high, the performance bottleneck is concentrated on the basic operators used to implement $\phi$.
-                    Optimizing the implementation of the corresponding basic operators will improve the training performance of this type of GNN.
-                    Taking GAT as an example, The most time-consuming operator \_index\_put\_impl in GAT is mainly used in the backward stage of the softmax calculation ($\alpha^k_{ij}$) in $\phi$,
-                    which only involves data movement.
-                    The optimized softmax implementation on the GPU can significantly reduce GAT training time.
-              \item If the computational complexity of $\phi$ is low, the collect and aggregate steps in its edge calculation are bottlenecks in computational performance.
-The collect step only involves a large amount of data movement.
-The aggregate step calculation is relatively simple (such as sum/average/maximum) Value, etc.), but because it involves data synchronization and irregular calculation, its time-consuming is still significant.
-                    Optimizing the implementation of these two steps on the GPU will improve the training performance of this type of GNN.
-          \end{itemize}
+    \item If the time complexity of $\phi$ is \textbf{high}, the \textbf{efficiency of $\phi$} limits the performance.
+Reducing its computation cost (via optimizing its implementation or modifying the algorithm) can significantly reduce the training time.
+    \item If the time complexity of $\phi$ is \textbf{low}, the \textbf{collect step} and the \textbf{aggregation step} limit the performance.
+The collect step involves lots of data movement.
+The aggregation step suffers from the data synchronization and non-regular data access.
+Optimizing their implementations can significantly reduce the training time.
 \end{itemize}

### 2020-07-20 Manuscript/sec2-review-of-graph-neural-network.tex
修正gaan公式

--- 2020-07-19 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
-For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\sum_{k \in \mathcal{N}(j)}\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}}  \boldsymbol{h}_k^l] )$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
+For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
 
@@
                          & \text{Sub-layer 1:}\\
-						 & \alpha_{j, i, (k)} = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j,(k)}] ))} {\hat{\boldsymbol{a}}^{l,0}_{i,(k)}} \\
-						 & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^{l,1} = \parallel_{k=1}^K \delta(\alpha_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)})                                                                                                                                             \\
-						 & \text{Multi-head average}: \boldsymbol{m}_{j, i}^{l,1} = \frac{1}{K} \sum_{k=1}^K \delta(\alpha_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)})
+						 & \alpha^l_{j, i, (k)} = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j,(k)}] ))} {\hat{\boldsymbol{a}}^{l,0}_{i,(k)}} \\
+						 & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^{l,1} = \parallel_{k=1}^K \delta(\alpha^l_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)})                                                                                                                                             \\
+						 & \text{Multi-head average}: \boldsymbol{m}_{j, i}^{l,1} = \frac{1}{K} \sum_{k=1}^K \delta(\alpha^l_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)})
 					\end{aligned}$
@@
 				$\begin{aligned}[t]
-						 & \alpha_{j, i}^k = \frac {\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l, k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}} \boldsymbol{h}_i^l] )} {\sum_{k \in \mathcal{N}(j)}\exp(\textcolor{blue}{\boldsymbol{a}^T} [ \textcolor{blue}{\boldsymbol{W}^{l,k}_{xa}} \boldsymbol{h}_j^l \parallel \textcolor{blue}{\boldsymbol{W}^{l,k}_{ya}}  \boldsymbol{h}_k^l] )} \\
-						 & \boldsymbol{m}_{j, i, 1}^l = \parallel_{k=1}^K \delta(\alpha_{j, i}^k \textcolor{blue}{\boldsymbol{W}^{l,k}_v} \boldsymbol{h}_j^{l})                                                                                                                                                                                                                                                                                               \\
-						 & \boldsymbol{m}_{j, i, 2}^l = \textcolor{blue}{\boldsymbol{W}^l_m} \boldsymbol{h}_j^{l}                                                                                                                                                                                                                                                                                                                                             \\
-						 & \boldsymbol{m}_{j, i, 3}^l = \boldsymbol{h}_j^l
+						 & \text{Sub-layer 0:} \\
+						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)) \\
+						 & \text{Sub-layer 1:} \\
+						 & \alpha^l_{j, i, (k)} = \frac {\exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\
+						 & \boldsymbol{m}_{j, i}^{l, 1} = \parallel_{k=1}^K \alpha_{j, i, (k)} \textcolor{blue}{\boldsymbol{FC}^h_{\theta^l_v}} \hat{\boldsymbol{h}}_{j, (k)}^l \\
+						 & \text{Sub-layer 2:} \\
+						 & \boldsymbol{m}_{j, i}^{l, 2} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_m}} \boldsymbol{h}_j^{l}  \\
+						 & \text{Sub-layer 3:} \\
+						 & \boldsymbol{m}_{j, i}^{l, 3} = \boldsymbol{h}_j^l
 					\end{aligned}$
@@
 		$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
-		Blue variables are model parameters to learn.
+		Blue variables are model parameters to learn. In GaAN, $FC^{\alpha}_{\theta}(x) = \alpha(\boldsymbol{W}\boldsymbol{x} + \boldsymbol{b})$, 
+		where $\theta=\{\boldsymbol{W}, \boldsymbol{b}\}$, $\theta$ with different subscripts mean different transformation parameters, we denote $h(\cdot)$
+		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.
 	}
@@
 				$\begin{aligned}[t]
-						 & \boldsymbol{g}_i = \textcolor{blue}{\boldsymbol{W}}^l_g  [\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i, 2}^l \parallel \boldsymbol{s}_{i, 3}^l] \\
-						 & \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l_o [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i, 1}^l) ]
+						& \text{Sub-layer 0:}\\
+						& \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}\\
+						& \text{Sub-layer 1,2,3:}\\
+						& \boldsymbol{g}_i = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_g}}(\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}) \\
+						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_o}} (\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i}^{l, 1}))
 					\end{aligned}$
@@
 		Blue variables are model parameters to learn.
-		For Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for nodes with degree $|\mathcal{N}(i)|$ at layer $l$.}
+		For Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for vertices with degree $|\mathcal{N}(i)|$ at layer $l$. 
+		In GaAN, $FC^{\alpha}_{\theta}(x) = \alpha(\boldsymbol{W}\boldsymbol{x} + \boldsymbol{b})$, 
+		where $\theta=\{\boldsymbol{W}, \boldsymbol{b}\}$, $\theta$ with different subscripts mean different transformation parameters, we denote $h(\cdot)$
+		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.}
 	\label{tab:gnn_overview_vertex}
@@
 Based on the multi-head machanism, GaAN introduces a convolutional subnetwork to control the weight of each head.
-Thus, it introduces more edge-related parameters to train.
-Moreover, GaAN aggregates three messages simutaneously, further increasing the edge calculational complexity.
+Different to multi-head machanism in GAT, GaAN project the center vertex feature to the query vector (dimension is $d_v$) and
+the neighboring vertex features are projected to get key and value vectors (dimensions are $d_{xa}$ and $d_{ya}$, because they are set to the same value in the original paper experiment, we use $d_a$ to represent $d_{xa}$ and $d_{ya}$ in the description that follows).
+$K$ is the number of attention heads.
+The weight of each head is calculated by a convolutional network, which takes the feature of each vertex and its neighbors as input to get the gated values with number of $K$.
+The convolutional network is built by combining average pooling and max pooling.
+Moreover, the max pooling needs to project the vertex feature to a transformed vector with dimension of $d_m$, costing an additional computational overhead.
+Each GaAN layer consists of four sub-layers. The first sub-layer aims to get the summation of attention weights of every vertex in each head.
+The second sub-layer uses to aggreate neighboring vertices's query vector with the normalized attention weights $\alpha_{j, i, (k)}$ for every head. 
+And the third sub-layer is used in max-pooling and it gets the element-wise max vector of neighboring vertices' transformed vectors by message-passing.
+The last sub-layer gets element-wise mean vector of neighboring vertices' vectors by message-passing.
+The gate values $\boldsymbol{g}^l_i$ is obtained by using a fully-connected layer with vector concatenating $\boldsymbol{h}^{l}_i$, $\boldsymbol{s}^{l, 2}_i$ and $\boldsymbol{s}^{l, 3}_i$.
+At last, GaAN uses a fully-connected layer with concatenating $\boldsymbol{h}^{l}_i$ and the result of element-wise multiplying $\boldsymbol{g}^{l}_i$ and $\boldsymbol{s}^{l, 0}_i$ to get the output hidden vector.
 

### 2020-07-20 Manuscript/sec3-experiment-design.tex
更新Section 4
Update section 4.

@@
 			We can decompose the training time on different levels: layer level, vertex/edge computation level and the basic operator level.
-			On each level, we breakdown the training time of an epoch into several stages. The most time-consuming stage is the performance bottleneck in time.
+			On each level, we breakdown the training time of an epoch into several stages. The most time-consuming stage is the performance bottleneck.
 			Optimizing its implementation can significantly reduce the training time.
@@
 			The limited memory capacity of a GPU card is the main factor preventing us training GNNs on big graphs.
-			We measured the peak memory usage in the GNN training under different graph scales, input feature dims and average vertex degrees.
+			We measured the peak memory usage in the GNN training under different graph scales, input feature dimensions and average vertex degrees.
 			Based on the results, we analyze which is the most memory-consuming component.

### 2020-07-20 Manuscript/sec4-experiments.tex
Update section 4.

@@
 
-To find out which stage dominates the training time, we breakdown the training time and analyze the performance bottleneck level by level.
+To find out which stage/step dominates the training time, we breakdown the training time and analyze the performance bottleneck level by level.
 
@@
 
-At present, all data (including datasets and intermediate calculation results) of PyG in the process of training GNN with GPU
-are stored in GPU memory. Compared with the main memory of the system, the memory capacity on GPU is very limited.
-\textbf{GPU memory capacity is limited to Determinants of the size of the training dataset}.
-GaAN was unable to complete the training due to memory overflow during the training of the `\textit{cph}` dataset.
+During the GNN training, all data (including datasets and intermediate results) are stored in the on-chip memory of GPU. 
+Compared with the main memory on the host side, the capacity of the GPU memory is very limited.
+\emph{The GPU memory capacity limits the scale of graphs that a GPU can train GNNs on}.
+For example, GaAN was unable to complete the training due to memory overflow exception on \texttt{cph} dataset.
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_usage_stage_amp.png}
-    \caption{Maximum memory usage in each stage. Data Load refers to memory usage after data is loaded. dataset: amp. Other datasets are similar}
+    \includegraphics[height=5cm]{figs/experiments/exp_memory_usage_stage_amp.pdf}
+    \caption{Memory usage of each phase. Dataset: \texttt{amp}.}
     \label{fig:exp_memory_usage_stage_amp}
@@
 
-\figurename~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each stage when each GNN is trained on the cam dataset, the situation is similar on other datasets.
-\textbf{The memory usage in GNN training is forward The peak in the phase and the backward phase},
-because a large number of temporary calculation results will be generated in the forward phase,
-and the key intermediate calculation results will be cached.
-The cached intermediate results will be used in the gradient calculation of the backward phase.
-\figurename~\ref{fig:ggnn_vertex_func_computation_graph} shows the calculation graph of GGNN's vertex calculation function $\gamma$.
-It can be seen that a large number of operators are involved in GGNN vertex calculation and a large number of intermediate calculation results are generated.The key calculation results will also be cached,
-which is exacerbated Memory usage. Most of the peak memory usage in the loss phase comes from the intermediate calculation results of the cache.
-With the end of the backward phase, the memory of the intermediate calculation results is released.
-In the evaluation phase, there is no need to cache intermediate results for gradient calculations, Peak memory usage dropped significantly.
+\begin{figure}
+    \centering
+    \includegraphics[height=4.5cm]{figs/illustration/ggnn_vertex_func_computation_graph.pdf}
+    \caption{Computation graph of the vertex update function $\gamma$ of GGNN.}
+    \label{fig:ggnn_vertex_func_computation_graph}
+\end{figure}
+
+\figurename~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each phase in the GNN training on the \texttt{amp} dataset.
+The trend was similar on other datasets.
+\emph{The GNN training achieved its peak memory usage in the forward and the backward phases}.
+The forward phase generated a large number of intermediate results.
+Some key intermediate results were cached, increasing the memory usage.
+The cached results were used in the gradient calculation in the backward phase.
+\figurename~\ref{fig:ggnn_vertex_func_computation_graph} shows the computation graph of the vertex update function $\gamma$ of GGNN.
+The computation graph had a large number of operators, each operator generating an intermediate matrix.
+Some key intermediate matrices were cached.
+The cached matrices were the main source of memory usage in the loss phase.
+By the end of the backward phase, the cached results were released.
+Since the evaluation phase did not need to calculate the gradients, it did not cache intermediate results.
+Its memory usage declined sharply.
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{figs/illustration/ggnn_vertex_func_computation_graph.png}
-    \caption{The calculation graph of the GGNN vertex calculation function $\gamma$. The output of the Cached Operator will be cached for gradient calculation in the backward process}
-    \label{fig:ggnn_vertex_func_computation_graph}
+    \includegraphics[height=5cm]{figs/experiments/exp_memory_expansion_ratio.pdf}
+    \caption{Memory expansion ratios of typical GNNs.}
+    \label{fig:exp_memory_expansion_ratio}
 \end{figure}
 
-It is worth noting that \textbf{the peak memory during GNN training far exceeds the memory usage of the dataset itself}.
-The ratio of the highest peak memory usage during our training compared to the memory usage after data Load is
-defined as the memory expansion ratio. \figurename~\ref{fig:exp_memory_expansion_ratio} compares the memory expansion ratios
-of different GNNs on different datasets. The expansion ratio of GCN is the lowest, between 5-14 times,
-and the expansion ratio of GaAN is the highest, up to 101 times.
-\textbf{Very high expansion ratio severely limits the data scalability of GNN, making GPU unable to process large-scale graph datasets},
-especially restricting GNN with high edge calculation complexity.
+The peak memory usage during the GNN training far exceeds the size of the dataset itself.
+We define the \emph{memory expansion ratio} (MER) as the ratio of the peak memory usage during the training to the memory usage after loading the dataset.
+\figurename~\ref{fig:exp_memory_expansion_ratio} compares MER of different GNNs.
+GCN had the lowest MER (up to 14) while GaAN had the highest MER (up to 101).
+\emph{The high MER limits the data scalability of GNNs}, making GPU unable to handle big graphs.
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio.png}
-    \caption{The proportion of memory expansion of each GNN on different datasets.}
-    \label{fig:exp_memory_expansion_ratio}
+    \includegraphics[height=5cm]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.pdf}
+    \caption{Memory expansion ratio under different dimensions of the input feature vectors. Dataset: \texttt{cam}.}
+    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
 \end{figure}
 
-\figurename~\ref{fig:exp_memory_expansion_ratio} also shows that the expansion ratio of the same GNN under the same hyperparameters changes with different datasets.
-Because the input feature dimension of the \textit{cph} dataset is much higher than the hidden vector of the GNN layer The dimension of the input feature vector matrix
-of the graph is much higher than the matrix size of the intermediate calculation result of the cache,
-so its expansion ratio is particularly low, and the cam dataset is the opposite. In order to measure the effect of the input feature vector dimension on the memory
-expansion ratio , We randomly generated feature vectors of specific dimensions for different datasets.
-\figurename~\ref{fig:exp_memory_expension_ratio_input_feature_dimension} shows the change in the expansion ratio under different input feature vector dimensions.
-\textbf{In the same GNN structure and hyperparameter settings, using a higher-dimensional input feature vector can reduce memory expansion ratio} .
+\figurename~\ref{fig:exp_memory_expansion_ratio} also indicates that the same GNN had different MERs for different datasets.
+Two characteristics of the dataset affects the MER: the dimension of the input feature vector and the average degree.
+
+Given the same graph, the scales of the intermediate results are mainly affected by the hyper-parameters of the GNN.
+If the dimension of the input feature vectors is high (like the \texttt{cph} dataset), the size of the dataset is large.
+The size becomes comparable to the scales of the intermediate results,  making the MER low.
+To find out how the dimension affects the MER, we generated random input feature vectors with different dimensions for the \texttt{cam} dataset and measured the MER in \figurename~\ref{fig:exp_memory_expension_ratio_input_feature_dimension}.
+For a GNN under the same hyper-parameters, \emph{the MER decreased as the dimension of the input feature vectors increased}.
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.pdf}
-    \caption{The change of the memory expansion ratio with the dimension of the input feature vector. dataset: cam, other datasets are similar}
-    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
+    \subfloat[Peak memory usage]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_peak_memory.pdf}}
+    \subfloat[Memory expansion ratio]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_expansion_ratio.pdf}}
+    \caption{Memory usage under different average degrees of the graph.
+The graph was generated with the R-MAT generator fixing the number of vertices at 10K and the dimension of the input feature vectors at 32.}
+    \label{fig:exp_memory_expansion_ratio_input_graph_number_of_edges}
 \end{figure}
 
-Different GNNs have different vertex/edge calculation complexity, and the scale of the generated intermediate results has different sensitivity
-to the number of vertices/edges in the graph, resulting in the memory expansion ratio being affected by the average degree of the graph.
-We measured the GPU peak memory The usage and expansion ratios are affected by the scale of the graph.
-
-In the case of a fixed number of vertices in the graph, we use the R-MAT generator to generate random graphs with different average degrees (number of edges).
-The \figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage during training varies with the average degree.
-\textbf{As the average degree increases, the peak memory usage increases linearly.
-    The intermediate results generated by the edge calculation gradually dominate, and the memory expansion ratio of each GNN gradually stabilizes}.
-The expansion ratio is affected by the complexity of the edge calculation.
-Except for GGNN, the memory expansion ratio of other GNNs increases with the increase of degree. GGNN has a high vertex calculation complexity.
-When the average degree is low, its memory expansion ratio is mainly affected by the intermediate results of vertex calculation;
-when the average When the degree is increased, the memory expansion ratio is gradually determined by the edge calculation complexity.
-Because GGNN has the lowest edge calculation complexity, its stable expansion ratio is the lowest.
+The average degree of the graph also affects MER by influencing the relative scale of the intermediate results from vertex/edge calculation.
+Fixing the number of vertices $|\mathcal{V}|$, we used the R-MAT generator to generate random graphs with different average degrees.
+\figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage changes according to the average degrees.
+As the average degree $\bar{d}$ increased, the number of edges $|\mathcal{E}|$ increased and the peak memory usage increased \emph{linearly} with $\bar{d}$.
+The edge calculation gradually dominated the memory usage and \emph{the MER converged to a stable value}.
+The stable value was determined by the complexity of the edge calculation.
+Except for GGNN, the MERs of the other GNNs increased as $\bar{d}$ increased.
+As GGNN had high vertex calculation complexity, the MER related to the vertex calculation was much larger than the edge calculation.
+When the edge calculation dominated the memory usage, its MER became smaller.
 
@@
     \centering
-    \subfloat[]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_peak_memory.png}}
-    \subfloat[]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_expansion_ratio.png}}
-    \caption{The change of memory usage with the average degree of the graph (R-MAT random graph, the number of vertices is fixed at 10k, and the input feature vector dimension is 32}
-    \label{fig:exp_memory_expansion_ratio_input_graph_number_of_edges}
-\end{figure}
-
-In the case of a fixed number of edges in the graph, we use the R-MAT generator to generate random graphs with different numbers of vertices
-\figurename~\ref{@fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows the change of memory usage with the number of vertices during training.
-Except for GGNN, the number of vertices increases, the number of vertices increases, the number of vertices increases,
-and the number of vertices increases. The size of the eigenvector matrix of the vertex input becomes larger,
-but the peak memory usage only increases slightly, which makes the proportion of memory expansion decrease to a certain extent.
-Only GGNN has a large number of intermediate calculation results during the vertex calculation process because of the high vertex calculation complexity.
-The memory expansion factor has a small increase. The experimental data shows that \textbf{the intermediate result produced by the edge calculation is the dominant factor
-    in memory usage, and the peak memory usage of each GNN increases linearly with the increase in the number of edges}.
-
-\begin{figure}
-    \centering
-    \subfloat[]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_peak_memory.png}}
-    \subfloat[]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_expansion_ratio.png}}
-    \caption{Memory usage changes with the number of graph vertices (R-MAT random graph, the number of edges is fixed at 500k, and the input feature vector dimension is 32)}
+    \subfloat[Peak memory usage]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_peak_memory.pdf}}
+    \subfloat[Memory expansion ratio]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_expansion_ratio.pdf}}
+    \caption{Memory usage under different numbers of vertices of the graph.
+The graph was generated with the R-MAT generator fixing the number of edges at 500K and the dimension of the input feature vectors at 32.}
     \label{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge}
@@
 
-\paragraph{Bottleneck restricting data scalability}
-\begin{itemize}
-    \item \textbf{GPU memory capacity is the decisive factor limiting the scalability of the training dataset}.
-    \item \textbf{GPU memory usage mainly comes from the intermediate calculation results generated during the calculation process,
-              especially the intermediate calculation results of the edge calculation. Because part of the intermediate calculation results
-              will be cached to participate in backward calculation, high GPU memory usage runs through the forward and backward stages.}
-    \item \textbf{GNN's peak memory usage during training can reach tens or even hundreds of times the size of the input data.
-The limited memory capacity of the GPU severely limits the size of the input data that can be trained}.
-    \item \textbf{In the case of a fixed number of vertices, The peak memory usage of GNN increases linearly with the increase of the number of edges of the graph, The proportion of memory expansion will gradually stabilize to a fixed value determined by the complexity of the edge calculation}.
-    \item \textbf{In the case where the network structure and various hyperparameters are fixed, using a higher-dimensional input feature vector can reduce the expansion ratio of GPU memory usage}.
-\end{itemize}
+We also fixed the number of edges $|\mathcal{E}|$ in the graph and generated random graphs with different $|\mathcal{V}|$.
+\figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows how the memory usage changed according to $|\mathcal{V}|$.
+All GNNs were much more insensitive to the changes in $|\mathcal{V}|$ compared to $|\mathcal{E}|$.
+Except for GGNN, the MERs of the other GNNs declined as $|\mathcal{V}|$ increased because the scale of the dataset increased quicklier than the scales of the intermediate results.
+As GGNN had high vertex calculation complexity, the scales of the intermediate results were much more sensitive to $|\mathcal{V}|$.
+It indicates that \emph{the intermediate results of the edge calculation dominated the memory usage during the GNN training}.
 
-\label{sec:memory_usage_analysis}
+\paragraph{Summary}
+The \emph{high} memory expansion ratio severely restricted the data scalability of the GNN training.
+The memory usage mainly came from the intermediate results of the \emph{edge calculation}.
+Fixing the number of vertices, the memory usage increased \emph{linearly} along with the number of edges.
+Optimizing the memory usage of the edge calculation could significantly reduce the memory expansion ratio.
+Fixing the GNN structure and the hyper-parameters, increasing the dimension of the input feature vectors could also reduce the memory expansion ratio.
+
 \subsection{Effects of Sampling Techniques on Performance}
 
-Before the sampling technique, GNN training is full batch, that is, all the vertices and edges in the training set participate in the training and calculate the gradient at the same time.
-Full batch training can ensure convergence, but the training overhead is large each time, resulting in slow convergence.
-Inspired by the minibatch training method in stochastic gradient descent, a series of GNN sampling techniques are proposed.
+Without the sampling technique, GNNs are trained in a full batch manner.
+All the vertices and edges in the training set participate in the training.
+The full-batch training ensures the convergence, but the training time per epoch is long, showing the wall-clock convergence speed.
+Inspired by the mini-batch training in stochastic gradient descent, a series of GNN sampling techniques are proposed.
 The sampling technique decomposes the training of the full graph (i.e. epoch) into several batches, and

### 2020-07-20 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 4.
修正了gaan的错误

@@
 						& \text{Sub-layer 1,2,3:}\\
-						& \boldsymbol{g}_i = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_g}}(\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}) \\
-						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_o}} (\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i}^{l, 1}))
+						& \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_g}}(\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}) \\
+						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_o}} (\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i}^l \odot \boldsymbol{s}_{i}^{l, 1}))
 					\end{aligned}$
@@
 		Blue variables are model parameters to learn.
-		For Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for vertices with degree $|\mathcal{N}(i)|$ at layer $l$. 
+		In Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for vertices with degree $|\mathcal{N}(i)|$ at layer $l$. 
 		In GaAN, $FC^{\alpha}_{\theta}(x) = \alpha(\boldsymbol{W}\boldsymbol{x} + \boldsymbol{b})$, 

### 2020-07-20 Manuscript/sec4-experiments.tex
修改了gaan的一些说明

--- 2020-07-20 Manuscript/sec4-experiments.tex
@@
 \paragraph{GaAN}
-The top basic operator was \texttt{mm}.
-It was used in both the vertex and the edge calculation, where the edge calculation is dominant.
-The scalar multiplication \texttt{mul} and the concatenation \texttt{cat} operators were used in the message function $\phi$.
+The top basic operator was \texttt{addmm}. 
+The \texttt{addmm}, the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul} were used in both the vertex and the edge calculation, where the edge calculation is dominant.
 

### 2020-07-20 Manuscript/sec2-review-of-graph-neural-network.tex
update

@@
 Different to multi-head machanism in GAT, GaAN project the center vertex feature to the query vector (dimension is $d_v$) and
-the neighboring vertex features are projected to get key and value vectors (dimensions are $d_{xa}$ and $d_{ya}$, because they are set to the same value in the original paper experiment, we use $d_a$ to represent $d_{xa}$ and $d_{ya}$ in the description that follows).
+the neighboring vertex features are projected to get key and value vectors. The dimension of key and values vectors are the same, we set to $d_a$.
 $K$ is the number of attention heads.
@@
 
-To train GNNs in a mini-batch way, several sampling techniques \cite{chiang2019_cluster_gcn} are proposed.
+To train GNNs in a mini-batch way, several sampling techniques are proposed.
 In each mini-batch, they sample a small subgraph from the whole graph $\mathcal{G}$ and uses the subgraph to update the model parameters.

### 2020-07-21 Manuscript/sec2-review-of-graph-neural-network.tex
修正sec2中gaan的错误

@@
 For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
-For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
+For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(<\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) , \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)>)$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
 
@@
 						 & \text{Sub-layer 0:} \\
-						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)) \\
+						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(<\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l), \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)>) \\
 						 & \text{Sub-layer 1:} \\
-						 & \alpha^l_{j, i, (k)} = \frac {\exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\
+						 & \alpha^l_{j, i, (k)} = \frac {\exp(<\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l), \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)>)} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\
 						 & \boldsymbol{m}_{j, i}^{l, 1} = \parallel_{k=1}^K \alpha_{j, i, (k)} \textcolor{blue}{\boldsymbol{FC}^h_{\theta^l_v}} \hat{\boldsymbol{h}}_{j, (k)}^l \\
@@
 		where $\theta=\{\boldsymbol{W}, \boldsymbol{b}\}$, $\theta$ with different subscripts mean different transformation parameters, we denote $h(\cdot)$
-		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.
+		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.$<\cdot,\cdot>$ means the dot
+		product between two vectors.
 	}

### 2020-07-21 Manuscript/sec3-experiment-design.tex
Update section 4.

@@
 
+\paragraph{Sampling Techniques}
+
+We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical neighbor sampling and graph sampling techniques, respectively.
+For the neigbhor sampler, we used the neighborhood sample sizes (25 for GNN Layer 1, and 10 for GNN Layer 0) and the default batch size (512) from \cite{hamilton2017_graphsage}.
+For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to \cite{chiang2019_cluster_gcn}.
+
 \subsection{Experimental Scheme}

### 2020-07-21 Manuscript/sec4-experiments.tex
Update section 4.

@@
 \subsection{Memory Usage Analysis}
+\label{sec:memory_usage_analysis}
 
@@
 \subsection{Effects of Sampling Techniques on Performance}
+\label{sec:effects_of_sampling_techniques_on_performance}
 
-Without the sampling technique, GNNs are trained in a full batch manner.
-All the vertices and edges in the training set participate in the training.
-The full-batch training ensures the convergence, but the training time per epoch is long, showing the wall-clock convergence speed.
-Inspired by the mini-batch training in stochastic gradient descent, a series of GNN sampling techniques are proposed.
-The sampling technique decomposes the training of the full graph (i.e. epoch) into several batches, and
-each batch uses only part of the graph vertices and edges to participate training and performing gradient
-updates greatly reduces the training time of each batch, allowing multiple rounds of gradient descent to
-be performed within a fixed time, thereby accelerating convergence. The experiments in this section mainly
-analyze the impact of sampling techniques on training performance.
+With the sampling techniques, GNNs can be trained in a mini-batch manner.
+Each mini-batch updates the model parameters based on a small subgraph sampled from the original input graph.
+Thus, the training time per batch and the peak memory usage during the training should both decline significantly.
 
-In the current implementation of PyG, the GNN model parameters always reside on the GPU,
-and the dataset resides in the main memory. When processing each epoch, the CPU samples
-the graph dataset in the main memory and generates several batches,
-Each batch is a small-scale subgraph of the dataset. When training each batch,
-PyG copies the subgraph data corresponding to the batch to the GPU's memory,
-trains based on the subgraph and updates the model parameters according to the gradient.
-Based on the sampling technology and SGD optimization technology,
-the evaluation of the model parameters is performed every several epochs.
-The evaluation can be carried out on the CPU or on the GPU.
-Therefore, the statistical data in the experiments in this section does not include the evaluation phase.
-Neighbor Sampler and Cluster Sampler is selected in this section as they are two typical graph sampling techniques for analysis.
-
-\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the subgraph sampled in the two sampling techniques varies with the batch size.
-For Neighbor Sampler, the relative batch size is equal to the number of vertices sampled in the last layer of GNN relative to the top of the full graph the proportion of vertices.
-For Cluster Sampler, the batch size is equal to the number of partitions sampled compared to the number of all partitions in the whole graph.
-\textbf{Neighbor Sampler is very sensitive to the increase in batch size. As the batch size increases,
-    the sampling subgraph The number of vertices/edges and the average degree both increase rapidly and tend to stabilize}.
-\textbf{Cluster Sampler is less sensitive to the increase in batch size, the number of vertices/average degree increases
-    linearly with the increase in batch size, and the number of edges is in the batch When the size is relatively small,
-    it also increases linearly.}
-
-It is worth noting that \textbf{the average degree of the subgraph sampled is much lower than the average degree of the whole graph,
-    especially when the relative batch size is low}. Taking Neighbor Sampler at a relative batch size of 6\% as an example,
-The average degree of the \textit{amp} dataset is 31.1, but the average degree of the sampled subgraph is only 5.8,
-which is much lower than the average degree of the full graph.
-The average degree of the subgraph sampled by the Cluster Sampler is lower, only 3.0.
-\figurename~\ref{fig:exp_sampling_minibatch_degrees_distribution} shows the comparison of the distribution of the sampled subgraph with the original graph.
-The vertex dregree distribution of subgraphs sampled by the two sampling techniques is lower than that of the original graph.
-The reason is that the degree distribution of vertex in the actual graph dataset follows a power-rate distribution and only a small number of vertices is very high,
-which improves the average degree. In the sampling process, because the sampling method will limit the neighborhood size of the vertex, thereby reducing the upper limit of the vertex degree,
-so that the average degree drops significantly. Combined with the experimental results in section 4.2, the decrease in the average degree of sampled subgraph will increase the time-consuming
-proportion of vertex calculation. For GGNN with high vertex calculation complexity, vertex calculation will replace edge calculation and become a performance bottleneck.
+In the implementation in PyG, the GNN model and the dataset resided on the GPU side.
+To process each epoch, PyG sampled the original dataset in the main memory and generated several batches.
+Each batch was a small subgraph of the dataset.
+To train on each batch, PyG sent the sampled subgraph to GPU, calculated the gradients in the subgraph and updated the model parameters directly on GPU.
+With the sampling techniques, the model parameters were updated by a stochastic gradient descent optimizer.
+It conducted the evaluation phase every several epoches (either on the CPU side or the GPU side) to determine whether to stop the training.
+The experiments focused on the training phase of each batch.
 
@@
     \centering
-    \subfloat[Neighbor Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_graphsage_gcn.png}} \\
-    \subfloat[Cluster Sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_cluster_gcn.png}}
-    \caption{The size of the sampled subgraph changes with the batch size.
-Each batch size is sampled 50 times, and the error bar represents the standard deviation.
-The relative batch size is the ratio relative to the full graph.)}
+    \subfloat[Neighbor sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_graphsage_gcn.pdf}} \\
+    \subfloat[Cluster sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_cluster_gcn.pdf}}
+    \caption{Sizes of the sampled subgraphs under different batch sizes.
+Each batch size was sampled 50 times and the average value was reported.
+The error bar indicates the standard deviation.
+The batch size is relative to the full graph.}
     \label{fig:exp_sampling_minibatch_graph_info}
@@
 
+\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changed with the batch size.
+For the neighbor sampler, the relative batch size is the porportion of the sampled vertices of the last GNN layer in all vertices of the graph.
+For the cluster sampler, the relative batch size is the proportion of the sampled partitions to all partitions of the graph.
+The neighbor sampler was very sensitive to the batch size.
+As the batch size increased, the size of the sampled subgraph increased quickly and then stabalized.
+The cluster sampler was much less sensitive compared to the neighbor sampler.
+The number of vertices and the average degree of the sampled subgraphs increased linearly with the batch size.
+
 \begin{figure}
     \centering
-    \includegraphics[width=0.7\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.png}
-    \caption{Comparison of the vertex degree distribution of the sampled subgraph and the original graph. dataset: amp. Batch size = 512 (Neighbor Sampler) / 20 (Cluster Sampler)}
+    \includegraphics[width=0.4\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.pdf}
+    \caption{Vertex degree distribution of the sampled subgraph (relative batch size: 6\%) and the original graph. Dataset:\texttt{amp}.}
     \label{fig:exp_sampling_minibatch_degrees_distribution}
@@
 
-\figurename~\ref{fig:exp_sampling_batch_train_time} shows the change of the training time of each batch on the \textit{amc} and \textit{fli} datasets with the batch size after using the sampling technique.
-For the Neighbor Sampler, the time spent in the training phase is significantly reduced compared to full-batch training only when the batch size is very small.
-When the batch size is particularly small, the training time is significantly reduced. However, because the sampling itself has additional overhead,
-and there is also an overhead in transferring the sampled subgraph to the GPU, the training time of the entire batch may exceed the full graph.
-training is time-consuming. For Cluster Sampler, the sampled subgraph is smaller than Neighbor Sampler under the same relative batch size,
-which makes the effect of sampling technology more obvious. But when the relative batch size increases,
-the increment by additional cost of sampling technology is very obvious. When the relative batch size $\geq$ 25\%,
-the total time of each batch of the sampling technique even exceeds the time of the full graph training.
-Experiments show that \textbf{the implementation of sampling technology in PyG at this stage is very inefficient and the extra overhead is high}.
-When the batch size is slightly larger, the additional cost of sampling technology accounts for more than 50\% of the total training cost of the entire batch.
-\textbf{Sampling technology can reduce training time only on very small batches}.
+It is worth noting that the average degree of the sampled subgraph was \emph{much lower} than the average degree of the whole graph, especially when the relative batch size is low.
+Taking the neighbor sampler with the relative batch size of 6\% as an example, the average degree of the \texttt{amp} dataset was 31.1, but the average degree of the sampled subgraph was only 5.8.
+For the cluster sampler, it was even lower to 3.0.
+\figurename~\ref{fig:exp_sampling_minibatch_degrees_distribution} compares the degree distribution of the sampled subgraph with the original graph.
+The slopes of the curves were similar.
+It indicates that the sampled subgraphs still followed the power-law degree distribution.
+However, the numbers of vertices in the sampled subgraphs were much smaller than the original graph, significantly lowering the average degrees.
+According to the experimental results in Section~\ref{sec:training_time_breakdown}, if the average degree becomes lower, the proportion of the training time spent on vertex calculation will become higher, especially for GGNN.
 
@@
     \centering
-    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_amazon-computers.png}}
-    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.png}} \\
-    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_amazon-computers.png}}
-    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_flickr.png}}
-    \caption{The training time of each batch changes with the batch size. FULL means that the full graph participates in the training phase (excluding evaluation).}
+    \subfloat[Neighbor sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_amazon-computers.pdf}}
+    \subfloat[Neighbor sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_graphsage_flickr.pdf}} \\
+    \subfloat[Cluster sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_amazon-computers.pdf}}
+    \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_sampling_relative_batch_size_train_time_stack_cluster_flickr.pdf}}
+    \caption{Training time per batch breakdown. FULL means that the full graph participates in the training.}
     \label{fig:exp_sampling_batch_train_time}
@@
 
-However, \textbf{the advantage of the sampling technique is that it can greatly reduce the peak memory usage overhead,
-    making large-scale graph neural network training possible}.
-\figurename~\ref{fig:exp_sampling_memory_usage} shows how the peak memory usage changes with the relative batch size during the training process after sampling technology is used.
-After sampling sampling technology, peak memory usage is greatly reduced and the decrease of Cluster Sampler is greater than that of Neighbor Sampler.
+To find out the performance bottleneck with the sampling techniques, we decomposed the training time per batch into three phases: \emph{sampling} on CPU, \emph{transfering} sampled subgraphs from CPU to GPU and \emph{training} with the subgraphs on GPU.
+\figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.
+For the neighbor sampler, the sampling technique reduced the training time per batch only when the batch size was very small.
+When the batch became bigger, the sampling and the data transfering phases introduced noticeable overheads, even making the training time exceed the full-batch training.
+For the clustering sampler, the sampled subgraph was smaller than the neighbor sampler under the same relative batch size.
+The reduction in the training time was more obvious than the neighbor sampler.
+However, the overheads increased quickly as the relative batch size increased.
+The training time under the 25\% relative batch size already exceeded the time of full-batch training.
+The experimental results indicate that the implementation of the sampling techniques in PyG is inefficient.
+When the batch size was slightly big, more than 50\% of the time had been spent on sampling and data transfering.
+\emph{The sampling techniques are only efficient under small batch sizes.}
 
@@
     \centering
-    \subfloat[Neighbor Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_amazon-computers_peak_memory.png}}
-    \subfloat[Neighbor Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.png}} \\
-    \subfloat[Cluster Sampler on amc]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_amazon-computers_peak_memory.png}}
-    \subfloat[Cluster Sampler on fli]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_flickr_peak_memory.png}}
-    \caption{Change in peak memory usage with batch size. FULL indicates the case when the sampling technique is not used (excluding the evaluation stage).}
+    \subfloat[Neighbor sampler on \texttt{amc}]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_amazon-computers_peak_memory.pdf}}
+    \subfloat[Neighbor sampler on \texttt{fli}]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_graphsage_flickr_peak_memory.pdf}} \\
+    \subfloat[Cluster sampler on \texttt{amc}]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_amazon-computers_peak_memory.pdf}}
+    \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_flickr_peak_memory.pdf}}
+    \caption{Peak memory usage under different batch sizes. FULL means the full graph participates in the training.}
     \label{fig:exp_sampling_memory_usage}
 \end{figure}
-\label{sec:effects_of_sampling_techniques_on_performance}
+
+The main advantage of the sampling technique is \emph{reducing the peak memory usage} during the training.
+\figurename~\ref{fig:exp_sampling_memory_usage} shows the memory usage under different batch sizes.
+The peak memory usage declined significantly even under big batch sizes.
+The sampling techniques make training GNNs on big graphs possible for GPU.
+
+\paragraph{Summary}
+With small batch size, the sampling techniques could significantly reduce the training time per batch and the peak memory usage during the training.
+The sampled subgraphs had lower average degrees than the whole graph.
+However, the current implementation of the sampling techniques was every inefficient under big batch sizes.
+The time spent on the sampling phase and the data transfering phase could even exceeded the training phase.

### 2020-07-22 Manuscript/sec4-experiments.tex
update GaAN

--- 2020-07-20 Manuscript/sec4-experiments.tex
@@
 \paragraph{GaAN}
-The top basic operator was \texttt{addmm}. 
-The \texttt{addmm}, the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul} were used in both the vertex and the edge calculation, where the edge calculation is dominant.
+The top basic operator was \texttt{bmm} used in the message function $\phi$. 
+The \texttt{addmm} operator and the \texttt{mm} operator were used in both the vertex and the edge calculation, where the edge calculation is dominant.
 

### 2020-07-22 Manuscript/sec2-review-of-graph-neural-network.tex
update GaAN

--- 2020-07-20 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
-For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
+For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
 
@@
 						 & \text{Sub-layer 0:} \\
-						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l)) \\
+						 & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}})) \\
 						 & \text{Sub-layer 1:} \\
-						 & \alpha^l_{j, i, (k)} = \frac {\exp(\textcolor{blue}{FC_{\theta^{l, k}_{xa}}} (\boldsymbol{h}_j^l) \odot \textcolor{blue}{\boldsymbol{FC}_{\theta^{l,k}_{ya}}} (\boldsymbol{h}_i^l))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\
-						 & \boldsymbol{m}_{j, i}^{l, 1} = \parallel_{k=1}^K \alpha_{j, i, (k)} \textcolor{blue}{\boldsymbol{FC}^h_{\theta^l_v}} \hat{\boldsymbol{h}}_{j, (k)}^l \\
+						 & \alpha^l_{j, i, (k)} = \frac {\exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\
+						 & \boldsymbol{m}_{j, i}^{l, 1} = \parallel_{k=1}^K \alpha_{j, i, (k)} LeakyReLU(\textcolor{blue}{\boldsymbol{W}^{l, k}_v} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_v}) \\
 						 & \text{Sub-layer 2:} \\
-						 & \boldsymbol{m}_{j, i}^{l, 2} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_m}} \boldsymbol{h}_j^{l}  \\
+						 & \boldsymbol{m}_{j, i}^{l, 2} = \textcolor{blue}{\boldsymbol{W}^l_m} \boldsymbol{h}_j^{l} + \textcolor{blue}{\boldsymbol{b}^l_m} \\
 						 & \text{Sub-layer 3:} \\
@@
 		$d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
-		Blue variables are model parameters to learn. In GaAN, $FC^{\alpha}_{\theta}(x) = \alpha(\boldsymbol{W}\boldsymbol{x} + \boldsymbol{b})$, 
-		where $\theta=\{\boldsymbol{W}, \boldsymbol{b}\}$, $\theta$ with different subscripts mean different transformation parameters, we denote $h(\cdot)$
-		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.
+		Blue variables are model parameters to learn. 
 	}
@@
 						& \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}\\
-						& \text{Sub-layer 1,2,3:}\\
-						& \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_g}}(\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}) \\
-						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_o}} (\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i}^l \odot \boldsymbol{s}_{i}^{l, 1}))
+						& \text{Sub-layer 1:}\\
+						& \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{W}^l_g}[\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}] + \textcolor{blue}{\boldsymbol{b}^l_g} \\
+						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}^l_o} [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i}^l \odot \boldsymbol{s}_{i}^{l, 1})] + \textcolor{blue}{\boldsymbol{b}^l_o}
 					\end{aligned}$
@@
 		In Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for vertices with degree $|\mathcal{N}(i)|$ at layer $l$. 
-		In GaAN, $FC^{\alpha}_{\theta}(x) = \alpha(\boldsymbol{W}\boldsymbol{x} + \boldsymbol{b})$, 
-		where $\theta=\{\boldsymbol{W}, \boldsymbol{b}\}$, $\theta$ with different subscripts mean different transformation parameters, we denote $h(\cdot)$
-		to be the $LeakyReLU$ for activation functions and $FC_{\theta}(x)$ means applying no activation function after the linear transform.}
+		}
 	\label{tab:gnn_overview_vertex}

### 2020-07-22 Manuscript/sec4-experiments.tex

--- 2020-07-21 Manuscript/sec4-experiments.tex
@@
 \paragraph{GaAN}
-The top basic operator was \texttt{addmm}.
-The \texttt{addmm}, the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul} were used in both the vertex and the edge calculation, where the edge calculation is dominant.
+The top basic operator was \texttt{bmm} used in the message function $\phi$. 
+The \texttt{addmm} operator and the \texttt{mm} operator were used in both the vertex and the edge calculation, where the edge calculation is dominant.
 

### 2020-07-22 Manuscript/sec4-experiments.tex
Update the section of insight.

--- 2020-07-21 Manuscript/sec4-experiments.tex
@@
 The hyper-parameters affect the training time and the memory usage of the GNN training \textbf{in a linear way}.
-Algorithm enginners can use larger hyper-parameters to increase the expressive power of a GNN model without worrying the explosive growth in the training time and memory usage.
+Algorithm engineers can use larger hyper-parameters to increase the expressive power of a GNN model without worrying the explosive growth in the training time and memory usage.
 

### 2020-07-22 Manuscript/sec5-insights.tex
Update the section of insight.

@@
 
-Through our experiments, we prove the existing graph neural network system's performance optimization
-technologies. For exampling, \ref{sec:effects_of_sampling_techniques_on_performance} finds that the advantage of 
-sampling techniques can greatly reduce the peak memory usage, which clearly explains that when scaling up to large-scale
-graph sampling layer is an essential part of AliGraph \cite{zhu2019_aligraph}. \ref{sec:training_time_breakdown} shows that in real graph datasets
-(average degress over than 10), collect step of edge calculation is performance bottleneck. DGL \cite{DGL}'s key optimization
-methods kernel fusion operation that combines message function with update funsion and requires message function withour parameters.
+Through the extensive experiments, we propose the following key findings/suggestions for how to optimize the performance of GNN training.
 
-Compared to \cite{zhang2020_analysis_neugraph}, the autor thinks that computation-intensive GEMM kernel is not the bottleneck of GNN training. This
-is not consistent with the hotspot analysis in \ref{sec:training_time_breakdown}. This is because the standard of selecting algorithms of the paper is to cover the varieties for GNN workloads 
-while ignoring the complexity of GNN, which is mainly brought by matrix multiplication. In addition, the author's conclusion that kernel fusion can imporove performance
-that is similar to our findings.
+\begin{enumerate}
+    \item \emph{The time complexity in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} points out the performance bottleneck theoretically.}
+          The experimental results validate the time complexity analysis.
+          The time complexity points out where the bottleneck comes from.
+          Optimization should focus on complex operations in $\phi$ and $\gamma$.
 
-According to our experiments, we propose the following key findings:
+    \item \emph{The computational cost of a GNN layer is mainly affected by the dimensions of the input and the output hidden feature vectors.}
+          Theoretically and empirically, the training time and the memory usage both increase \emph{linearly} with the dimensions of the hidden feature vectors.
+          GNNs are friendly to high-dimensional scenarios.
+          Algorithm engineers can use high-dimensional feature vectors to improve the expressive power of a GNN without worrying explosive growth in the training time and memory usage.
 
+    \item \emph{Performance optimizations should focus on improving the efficiency of the edge calculation.}
+          The edge calculation is the most time-consuming phase in most GNNs.
           \begin{itemize}
-    \item The edge/vertex complexity analysis can be used to theoretically analyze performance bottleneck. And it allows algorithm engineers to use larger hyperparameters to
-    increase the complexity of GNN without worrying about the time-consuming training and the explosive growth of memory usage.
-    \item Edge computation is performance bottleneck of GNN training for real-world graphs. When the complexity of edge calculation is high, 
-    optimization on collect step is most important. When the complexity of edge calculation is low, the collect and aggregate step is the main performance bottleneck.
-    \item GPU memory expansion is the most significant fator restricting the scalabiltiy of the GNN algorithm. When dealing with larger-scale graphs, how to effectively save memory is always
-    a priority
-    \item The advantage of sampling technology is that it greatly reduces the overhead of peak memory usage, making large-scale graph neural network training possible.
-    And the time-consuming optimization of sampling technology will also bring great gains to the entire training.
+              \item If the complexity of the message function $\phi$ is high, the implementation of $\phi$ is critical to performance.
+                    Improving its efficiency can significantly reduce the training time.
+                    For example, the attention mechanism in GNNs (like GAT and GaAN) requires an extra sub-layer to calculate the attention weight of each edge.
+                    Implementing it with the specially optimized basic operators on GPU is a potential optimization.
+              \item If the complexity of $\phi$ is low, the efficiency of the collect step and the aggregation step becomes critical.
+                    The existing GNN libraries \cite{DGL, PyG, ma2019_neugraph} already introduce the \emph{fused} operator to improve their efficiency.
+                    When the message function $\phi$ is an assignment or a scalar multiplication of the hidden feature vector of the source vertex, the libraries replace the collect, message and aggregate steps with a single fused operator.
+                    The fused operator calculates the aggregated vectors directly from the input hidden feature vectors, minimizing the memory footprints and overlapping the memory accessing with calculation.
+                    By this way, it significantly reduces the training time of GNNs with low edge calculation complexity (like GCN) \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph}.
+                    However, the applicable condition of the fused operator is very restrict.
+                    It does not work for $\phi$ with more complex operations like matrix multiplication.
+                    A potial optimization is proposing an implementation of the edge calculation that generates the aggregated vectors directly from the input hidden feature vectors on the fly, without materializing the parameter vectors and the message vectors.
           \end{itemize}
+    \item \emph{The high memory usage caused by the intermediate results of the edge calculation limits the data scalability of the GNN training.}
+          The memory expansion ratios of the typical GNNs are very high, making GPU unable to handle big graphs.
+          To train GNNs with big datasets, one solution is to distribute the dataset among severl GPUs and frequently swap parts of the dataset between GPUs and the main memory \cite{ma2019_neugraph}.
+          Another possible solution \cite{chen2016_training_deep} comes from the DNN training.
+          It only checkpoints key intermediate results during the forward propagation and recalculates the missing results on demand during the backproporgation.
+          Implementing the checkpoint mechanism in the GNN training is another potential optimization.
+
+    \item \emph{Sampling techniques can significantly reduce the training time and the memory usage, but its implementation is still inefficient}.
+          The sampling techniques are effective under small batch sizes.
+          Its current implementation brings considerable overheads when the batch size becomes large.
+          Improving the efficiency of the sampling is a potentil optimization.
+          The subgraphs sampled with small batch sizes are small.
+          They cannot make fully use of the computing power of a GPU.
+          How to improve the GPU utilization under small batch sizes is another problem to solve.
+          One possible solution is to train multiple batches asynchronously on the same GPU and use the asynchronous stochastic gradient descent to speed up the converge.
+
+\end{enumerate}

### 2020-07-22 Manuscript/sec4-experiments.tex
Update section 6.

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[height=4cm]{figs/experiments/exp_small_graph_train_time.png}
+    \caption{Training time on small random graphs. Graphs were generated with the R-MAT generator with the average degree as X.}
+    \label{fig:exp_small_graph_train_time}
+\end{figure}
+
+The disadvantage of the sampling technique is wasting the GPU resources.
+As the sampling techniques are only effective under small batch sizes, the sampled subgraphs will be very small in those cases.
+They cannot make full use of the computing power of a GPU.
+To simulate the cases of training GNNs with small sampled subgraphs, we generated random graphs with few vertices and measured the training time per epoch in \figurename~\ref{fig:exp_small_graph_train_time}.
+As the number of vertices increased, the training time was nearly unchanged except for GaAN.
+The training time of GaAN only became larger then $|\mathcal{V}| \geq 8000$.
+
 \paragraph{Summary}
 With small batch size, the sampling techniques could significantly reduce the training time per batch and the peak memory usage during the training.
+However, small batch sizes could not make full use of the computing power of a GPU.
 The sampled subgraphs had lower average degrees than the whole graph.

### 2020-07-22 Manuscript/sec6-related-work.tex
Update section 6.

@@
 
-In this section, we brefily review the graph neural network models survey (GNNs survey), 
-graph neural network system(GNN system) and GNNs performance bottleneck analysis work.
+\paragraph{Survey of GNNs}
+\cite{zhou2018_gnn_review,zhang2018_gnn_survey,comprehensive-survey-wu-2020} survey the existing graph neural network models and classify them from an algorithmic view.
+They summarize the parallels and differences between the architecture of different GNN models.
+The typical applications of GNNs are also briefly introduced.
+Those surveys focus on comparying the existing GNNs theoretically not empirically.
 
-\subsection{GNNs survey}
-Zhou et al \cite{zhou2018_gnn_review}, Zhang et al \cite{zhang2018_gnn_survey} and Wu et al \cite{comprehensive-survey-wu-2020} 
-surveyed existing graph neural works models in different categorizations and viewpoints and provided a comprehensive review about GNNs' model 
-architecture, principle and application. Dwived et al \cite{dwivedi2020_benchmark_of_gnn} discussed the performance of different GNN algorithms 
-under the graph dataset of different scenes, and gived the key operators of designing effective GNNs in different scenarios. 
-However, these efforts are focused on the GNN algorithm itself and accuracy, without a detailed analysis of memory usage and running time.
+\paragraph{Evaluation of GNNs}
+Shchur et al. \cite{shchur2018_pitfall_of_gnn} evaluate the accuracy of popular GNN models on the node classification task.
+Dwived et al. \cite{dwivedi2020_benchmark_of_gnn} further compare the accuracy of popular GNNs fairly in a controlled environment.
+Hu et al. \cite{hu2020_open_graph_benchmark} propose the open grpah benchmark that provides a group of datasets and a standard evaluation workflow.
+The benchmark makes the comparison between GNNs easily and fairly.
+Those model evaluation efforts focus on evaluating the accuracy of different GNNs.
+They provide insightful suggestions to improve the accuracy.
 
-\subsection{GNN system}
+From the efficiency aspect, Yan et al.
+\cite{yan2020_characterizing_gcn} compare the performance characteristics of graph convolutional networks, typical graph processing (like PageRank) and MLP-based neural network on GPU.
+They provide optimization guidelines for the software and the hardware sides.
+Zhang et al. \cite{zhang2020_analysis_neugraph} compare the architectural characteristics of the GNN inference on GPU under the unified SAGA-NN \cite{ma2019_neugraph} programming model,
+They find that GNN inference has no fixed performance bottleneck and all components deserves to optimize.
+These two efforts focus on the \emph{inference} phase of GNNs and they investigate the potential optimizations from an architectural view.
+In this work, our target is to find out the performance bottleneck in the training phase from a system view.
+We consider the performance bottleneck in both time and memory usage.
+We also evaluate the effects of the sampling techniques.
+Our work and \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph} form a complementary study on the efficiency issue of GNNs.
+
+\paragraph{Libraries/Systems of GNNs}
+
 PyG \cite{PyG}, DGL \cite{DGL} designed the graph neural network system based on the message-passing model.
@@
 worth studying.
-
-\subsection{GNNs performance bottleneck analysis work}
-Yan et al \cite{yan2020_analysis_gcns_gpu} compared the performance characteristics of GNN algorithms, Graph Processing and MLP-based Neural Network, provided guidelines in software optimizaton and hardware optimization.
-Zhang et \cite{zhang2020_analysis_neugraph} characterized the GNN computation at the inference stage based on SAGA-NN (Scatter-ApplyEdge-Gather-ApplyVertex with Neural Networks) programming model, 
-and found that GNN computation has no fixed performance bottlenecks, and believed that each part has the value of optimization. 
-Compared to their works, the classification angle of our work is unique, and neither of their works consider the graph scalabilty and the access of sampling technology,
-which coverred in this paper.

### 2020-07-23 Manuscript/ms.tex
Update section 2.
更新GAT的公式.
Update related work.

@@
 \usepackage{booktabs}
+\usepackage{makecell}
 \usepackage{lscape}
@@
 	\title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
-\author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Yihua Huang\corref{correspondingauthor}}
-\cortext[correspondingauthor]{Corresponding author}
-\ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, yhuang\}@nju.edu.cn}
-\address{State Key Laboratory for Novel Software Technology, Department of Computer Science and Technology, Nanjing University, Nanjing 210023, China}
+	\author{Zhaokang Wang, Yunpan Wang}%, Chunfeng Yuan, Yihua Huang\corref{correspondingauthor}}
+	%	\cortext[correspondingauthor]{Corresponding author}
+	\ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn}%}, \{cfyuan, yhuang\}@nju.edu.cn}
+	\address{State Key Laboratory for Novel Software Technology, \\Department of Computer Science and Technology, Nanjing University, \\Nanjing 210023, China}
 

### 2020-07-23 Manuscript/sec6-related-work.tex
Update related work.

@@
 
-PyG \cite{PyG}, DGL \cite{DGL} designed the graph neural network system based on the message-passing model.
-PyG \cite{PyG} built upon PyTorch and obtained high data throught with sparse GPU accleration by providing dedicated CUDA kernels
-and mini-batch technologies. DGL \cite{DGL} supported a variety of computing backends (Tensorflow, MXNet, PyTorch) and leveraged
-fusion kernel techniques, which combine message function with update function to provide further performance improvements compared to PyG \cite{PyG}.
-NeuGraph \cite{ma2019_neugraph} proposed a new programming model, SAGA-NN(Scatter-ApplyEdge-Gather-ApplyVertex with Neural Networks), and achieved excellent
-performance in a single machine with mutliple GPUs by using graph computation optimization such as data partitioning management, scheduling and parall mutli-gpu processing.
-AliGraph \cite{zhu2019_aligraph} targetd at Attributed Heterogeneous Graph data model, disassembed each layer of GNN into there basic operations: Sampling, Aggregate and Combine,
-and leveraged graph parition, spearate storage of attributes and the importance-base vertex caching strategy in storage layer.
-In general, various optimization techniques are used in these GNN systems' design, but whether these optimization techniques match the bottlenecks of GNN performance is a question
-worth studying.
+PyG \cite{PyG} and DGL \cite{DGL} both adopt the message-passing model as the underlying programming model for GNNs and support training big datasets with the sampling techniques.
+PyG \cite{PyG} is built upon PyTorch and it uses optimized CUDA kernels for GNNs to achieve high performance.
+DGL \cite{DGL} provides a group of high level user APIs and supports training GNNs with a variety of backends (Tensorflow, MXNet and PyTorch) transparently.
+It also supports LSTM as the aggregation functions.
+NeuGraph \cite{ma2019_neugraph} proposes a new programming model \emph{SAGA-NN} for GNNs.
+It focuses on training big datasets efficiently without sampling.
+It partitions the dataset sophisticatedly, schedules the training tasks among multiple GPUs and swaps the data among GPUs and the host asynchronously.
+AliGraph \cite{zhu2019_aligraph} targets at training GNNs on big attributed heterogeneous graphs that are common in e-commerce platforms.
+The graphs are partitioned among multiple nodes in a cluster and AliGraph trains GNNs on the graphs in a distributed way with system optimizations.
+PGL \cite{pgl} is another graph learning framework from Baidu based on the PaddlePaddle platform.

### 2020-07-23 Manuscript/sec7-conclusion.tex
Update section 7.

@@
-\section{Conclusion and Future Work}
+\section{Conclusion}
 
-We systematically study the performance bottleneck of graph neural networks. We first analyze the GNN training
-from the perspective of edge/vertex time complexity and prove the validity of computation analysis on training
-time and memory usage. We then decompose the training time from top to bottom and analyze factors that affected GPU memory and
-the impact of sampling technology. Our analysis suggests that the edge calculation is the performance bottleneck of GNN model
-and optimizing the collection stage and aggregation stage is always worth doing, but when the complexity of computing is high, the message stage is
-the most stage that should be optimized. In addition, the huge memory usage is a big problem of GNN training and is linearly related of the number for edges.
-Sampling technology is one of ways to greatly reduce the peak memory usage overhead.
-
-In our work, the aggregator required by the selected algorithm is generally min, max, and mean.
-When the aggregate becomes complicated, whether the performance brings further changes can be used as future research work.
+In this work, we systematically study the performance bottleneck in graph neural network training.
+We model the existing GNNs with the message-passing framework.
+We classify the GNNs according to their edge and vertex calculation complexities to pick four typical GNNs to evaluate.
+The experimental results validate our complexity analysis.
+The training time and the memory usage increase linearly with the hyper-parameters of a GNN.
+To find out the performance bottleneck in time, we decompose the training time per epoch on different levels.
+The training time breakdown indicates that the edge calculation and its related basic operators are the performance bottleneck for most GNNs.
+Moreover, the intermediate results produced during the edge calculation cause high memory usage, limiting the data scalability.
+Adopting sampling techniques can reduce training time and memory usage significantly.
+However, the current implementation brings considerable sampling overheads.
+The small sampled graphs cannot make full use of the computing power of a GPU either.
+Our analysis indicates that the edge calculation should be the main target of optimizations.
+Reducing its memory usage and improving its efficiency can significantly improve the performance of GNN training.
+Based on the analysis, we propose several potential optimizations for the GNN learning frameworks.
+We believe that our analysis can help developers to improving the implementation of the frameworks.

### 2020-07-23 Manuscript/sec1-introduction.tex
Update section 1.

--- 2020-07-11 Manuscript/sec1-introduction.tex
@@
 
-This is a survey \cite{zhou2018_gnn_review}.
+In recent years, the graph neural network (GNN) is a hot research topic in the field of artificial intelligence.
+Many GNNs \cite{kipf2017_gcn, defferrad2016_chebnet, li2018_agcn,li2015_ggnn, hamilton2017_graphsage, huang2018_gat, zhang2018_gaan} are proposed.
+GNNs can learn the representation of vertices/edges in a graph from its topology and original feature vectors in an \emph{end-to-end} manner.
+The strong expressive power makes GNNs achieve impressive accuracy in node classification, link prediction and graph classification \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020}.
+
+To train GNNs easily, a series of graph neural network learning libraries/systems \cite{PyG, DGL, ma2019_neugraph, zhu2019_aligraph, PGL} are proposed.
+PyG \cite{PyG}, NeuGraph \cite{ma2019_neugraph}, PGL \cite{PGL} and DGL \cite{DGL} build upon the existing deep learning frameworks (PyG on PyTorch, NeuGraph on Tensorflow, PGL on PaddlePaddle, DGL on multiple backends).
+They provide users with a high-level programming model (message-passing for PyG/PGL/DGL and SAGA-NN for NeuGraph) to describe the structure of a GNN.
+They take advantage of the common tools provided by the frameworks like the automatic differentiation to simplify the development.
+The GNN learning libraries/systems utilize specially optimized CUDA kernels (like kernel fusion \cite{DGL} \cite{ma2019_neugraph}) and other implementation techniques (like 2D graph partitioning \cite{ma2019_neugraph}) to improve the speed of GNN training.
+
+However, whether these optimizations solve the real performance bottleneck is still in doubt.
+Yan et al. \cite{yan2020_characterizing_gcn} and Zhang et al. \cite{zhang2020_analysis_neugraph} analyze the performance characteristics of the GNN \emph{inference} from the architectural view.
+They find that the GNN inference is more cache-friendly than the traditional graph analysis (like PageRank) and is suitable for GPU.
+They verify the effectiveness of the kernel fusion optimization in reducing the inference time.
+Nevertheless, \cite{yan2020_characterizing_gcn} and \cite{zhang2020_analysis_neugraph} focus on the inference phase and does not discuss the performance bottleneck in the training phase.
+
+To find out the performance bottleneck in the GNN training, we conduct experimental analysis in this work.
+We model the typical GNNs with the message-passing framework.
+Since we focus on the efficiency issue of GNN training instead of accuracy, we classify the typical GNNs into four quadrants according to their vertex and edge calculation time complexity.
+We pick GCN \cite{kipf2017_gcn}, GGNN \cite{li2015_ggnn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan} as representative GNNs with different vertex/edge calculation complexities.
+We implement them with PyG and evaluate their efficiency with six real-world datasets on GPU.
+We verify the correctness of the complexity analysis by measuring the effects of the hyper-parameters on the training time and memory usage.
+We find out the most time-consuming stage in GNN training by decomposing the training time per epoch from the layer level to the operator level.
+We analyze the memory usage during the training to discover the main factor that limits the data scalability of GNN training on GPU.
+Finally, we evaluate whether the sampling techniques affect the performance bottleneck.
+Our key findings and insights are summarized below.
+
+\begin{itemize}
+    \item The training time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.
+          The training time and memory usage increase \emph{linearly} with hyper-parameters.
+    \item The edge-related calculation is the performance bottleneck for most GNNs.
+          The majority of the training time is spent on it.
+          For GNNs with high edge calculation complexity, optimizations should focus on the implementation of the message function that is conducted on every edge during the edge calculation.
+          For GNNs with low edge calculation complexity, optimizations should focus on the collect step and the aggregation step of the edge calculation.
+          Overlapping the data accessing with the computation is a potential optimizing direction.
+    \item The high memory usage caused by the intermediate results of the edge calculation is the main factor that prevents us training big graphs on GPU.
+    \item The sampling techniques can significantly reduce the training time and memory usage, but the implementation is still inefficient.
+The time spent on the sampling may exceed the time spent on the training under big batch sizes.
+How to make full use of the computing power of GPUs with the sampling techniques is another question to solve.
+\end{itemize}
+
+Based on the insights, we provide several potential optimization directions.
+We believe that our analysis can help the developers of the GNN libraries/systems have a better understanding of the characteristics of GNN training and propose more targeted optimizations.
+
+\paragraph{Outline}
+We briefly survey the typical GNNs in Section~\ref{sec:review_of_gnns}.
+We introduce our experimental setting and targets in Section~\ref{sec:experimental_design}.
+The experimental results are presented and analyzed in Section~\ref{sec:experiment_results}.
+We summarize the key findings and give out potential optimization directions in Section~\ref{sec:insights}.
+We introduce the related work in Section~\ref{sec:related_work} and finally conclude our work in Section~\ref{sec:conclusion}.

### 2020-07-23 Manuscript/sec4-experiments.tex
Update section 1.

@@
     \centering
-    \includegraphics[height=4cm]{figs/experiments/exp_small_graph_train_time.png}
-    \caption{Training time on small random graphs. Graphs were generated with the R-MAT generator with the average degree as X.}
+    \includegraphics[height=5cm]{figs/experiments/exp_small_graph_train_time.pdf}
+    \caption{Training time per epoch on small random graphs.
+For each number of vertices, we generated 50 random R-MAT graphs with the average degree of 4.0 and reported the average training time per epoch (without the evaluation phase).
+The error bar indicates the standard deviation.}
     \label{fig:exp_small_graph_train_time}
@@
 To simulate the cases of training GNNs with small sampled subgraphs, we generated random graphs with few vertices and measured the training time per epoch in \figurename~\ref{fig:exp_small_graph_train_time}.
-As the number of vertices increased, the training time was nearly unchanged except for GaAN.
-The training time of GaAN only became larger then $|\mathcal{V}| \geq 8000$.
+As the number of vertices increased, the training time was almost unchanged except for GaAN.
+The training time of GaAN increased only with $|\mathcal{V}| \geq 4000$.
 

### 2020-07-23 Manuscript/sec6-related-work.tex
Update section 1.

@@
 \section{Related Work}
+\label{sec:related_work}
 
@@
 The typical applications of GNNs are also briefly introduced.
-Those surveys focus on comparying the existing GNNs theoretically not empirically.
+Those surveys focus on comparing the existing GNNs theoretically not empirically.
 
@@
 Dwived et al. \cite{dwivedi2020_benchmark_of_gnn} further compare the accuracy of popular GNNs fairly in a controlled environment.
-Hu et al. \cite{hu2020_open_graph_benchmark} propose the open grpah benchmark that provides a group of datasets and a standard evaluation workflow.
-The benchmark makes the comparison between GNNs easily and fairly.
+Hu et al. \cite{hu2020_open_graph_benchmark} propose the open graph benchmark that provides a group of datasets and a standard evaluation workflow.
+The benchmark makes comparisons between GNNs easily and fairly.
 Those model evaluation efforts focus on evaluating the accuracy of different GNNs.
-They provide insightful suggestions to improve the accuracy.
+They provide insightful suggestions to improve accuracy.
 
@@
 PyG \cite{PyG} is built upon PyTorch and it uses optimized CUDA kernels for GNNs to achieve high performance.
-DGL \cite{DGL} provides a group of high level user APIs and supports training GNNs with a variety of backends (Tensorflow, MXNet and PyTorch) transparently.
+DGL \cite{DGL} provides a group of high-level user APIs and supports training GNNs with a variety of backends (Tensorflow, MXNet and PyTorch) transparently.
 It also supports LSTM as the aggregation functions.
@@
 The graphs are partitioned among multiple nodes in a cluster and AliGraph trains GNNs on the graphs in a distributed way with system optimizations.
-PGL \cite{pgl} is another graph learning framework from Baidu based on the PaddlePaddle platform.
+PGL \cite{PGL} is another graph learning framework from Baidu based on the PaddlePaddle platform.

### 2020-07-23 Manuscript/ms.tex
更新完成初稿.

@@
 		Graph neural network has become a research hotspot in the field of artificial intelligence due to state-of-the-art of performance
-		achieved in many grpah-related tasks. At the same time, various of graph neural network system has emrged one after another.
+		achieved in many graph-related tasks. At the same time, various of graph neural network systems have emerged one after another.
 		These systems have used their own skills in implementation, but there are very few works to study the performance bottleneck
 		on graph neural network training. In contrast to prior works that present characterization of GCNs and select GNNs cover GNN workloads,
-		we select typical algorithms by complexity of edge/vertex calculation. We analyze the performance bottleneck by breaking down training
+		we select typical algorithms by complexities of edge/vertex calculation. We analyze the performance bottleneck by breaking down training
 		time, study the affects of hyper-parameters and sampling technologies and find factors of memory usage. We finally put forward some key

### 2020-07-23 Manuscript/sec2-review-of-graph-neural-network.tex
update
Update section 1.
更新完成初稿.

@@
 \section{Review of Graph Neural Networks}
+\label{sec:review_of_gnns}
 
@@
 	\centering
-	\includegraphics[width=1\columnwidth]{figs/illustration/GNN_common_architecture.png}
+	\includegraphics[width=1\columnwidth]{figs/illustration/GNN_common_architecture.pdf}
 	\caption{Structure of a typical graph neural network. (a) Demo GNN, (b) Demo graph. The target application is the node classification. The demo GNN has two GNN layers.}
@@
 	\centering
-	\includegraphics[width=0.5\columnwidth]{figs/illustration/GNN_Unit.png}
+	\includegraphics[width=0.5\columnwidth]{figs/illustration/GNN_Unit.pdf}
 	\caption{Graph neuron of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}(b).
@@
 			$O(d_{in})$                                                                                                                 \\
-			AGCN                                                                                                                      &
+			AGCN \cite{li2018_agcn}                                                                                                   &
 			Spectral                                                                                                                  &
@@
 			$O(d_{in})$                                                                                                                 \\
-			GraphSAGE                                                                                                                 &
+			GraphSAGE \cite{hamilton2017_graphsage}                                                                                   &
 			Non-spectral                                                                                                              &
@@
 			$O(1)$                                                                                                                      \\
-			GraphSAGE-pool                                                                                                            &
+			GraphSAGE-pool \cite{hamilton2017_graphsage}                                                                              &
 			Non-spectral                                                                                                              &
@@
 			$O(d_{in} * d_{out})$                                                                                                       \\
-			Neural FPs                                                                                                                &
+			Neural FPs  \cite{duvenaud2015_neural_fps}                                                                                &
 			Non-spectral                                                                                                              &
@@
 			$O(1)$                                                                                                                      \\
-			SSE                                                                                                                       &
+			SSE \cite{han2018_sse}                                                                                                    &
 			Recurrent                                                                                                                 &
@@
 			$O(f+d_{in})$                                                                                                               \\
-			\textbf{GGNN}                                                                                                             &
+			\textbf{GGNN}  \cite{li2015_ggnn}                                                                                         &
 			Gated                                                                                                                     &
@@
 			$O(d_{in} * d_{out})$                                                                                                       \\
-			\textbf{GAT}                                                                                                              &
+			\textbf{GAT}   \cite{huang2018_gat}                                                                                       &
 			Attention                                                                                                                 &
@@
 				$\begin{aligned}[t]
-                         & \text{Sub-layer 0:}\\
-                         & \boldsymbol{m}^{l,0}_{j,i,(k)} = \exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j, (k)}]))\\
-                         & \text{Sub-layer 1:}\\
+						 & \text{Sub-layer 0:}                                                                                                                                                                                    \\
+						 & \boldsymbol{m}^{l,0}_{j,i,(k)} = \exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j, (k)}]))                                    \\
+						 & \text{Sub-layer 1:}                                                                                                                                                                                    \\
 						 & \alpha^l_{j, i, (k)} = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j,(k)}] ))} {\hat{\boldsymbol{a}}^{l,0}_{i,(k)}} \\
@@
 				\begin{aligned}[t]
-                \text{concat: } O(d_{out}) &\\
-                \text{average: } O(K * d_{out}) &\\
+					\text{concat: } O(d_{out})      & \\
+					\text{average: } O(K * d_{out}) & \\
 					\text{Two sub-layers}           &
@@
 			\\
-			\textbf{GaAN}                                                                                                             &
+			\textbf{GaAN}     \cite{zhang2018_gaan}                                                                                   &
 			Attention                                                                                                                 &
@@
 						 & \text{Sub-layer 1:}                                                                                                                                                                                                                                                                  \\
-						 & \alpha^l_{j, i, (k)} = \frac {\exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}}\\
+						 & \alpha^l_{j, i, (k)} = \frac {\exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}} \\
 						 & \boldsymbol{m}_{j, i}^{l, 1} = \parallel_{k=1}^K \alpha_{j, i, (k)} LeakyReLU(\textcolor{blue}{\boldsymbol{W}^{l, k}_v} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_v})                                                                                                           \\
@@
 			\makecell[r]{$O(max(d_a, d_m, d_v) * K * d_{in})$                                                                           \\
-                        Four sub-layers}\\
+			Four sub-layers}                                                                                                            \\
 			\bottomrule
@@
 			$O(d_{in} * d_{out})$                                                                                                                                                                                              \\
-			AGCN                                                                                                                                                                                                             &
+			AGCN   \cite{li2018_agcn}                                                                                                                                                                                        &
 			$\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l  \boldsymbol{s}_i^{l}$                                                                                                                              &
 			$O(d_{in} * d_{out})$                                                                                                                                                                                              \\
-			GraphSAGE                                                                                                                                                                                                        &
+			GraphSAGE  \cite{hamilton2017_graphsage}                                                                                                                                                                         &
 			$\boldsymbol{h}_i^{l+1} =   \delta(\textcolor{blue}{\boldsymbol{W}}^l  [\boldsymbol{s}_i^{l} \parallel \boldsymbol{h}_i^l])$                                                                                     &
 			$O(d_{in} * d_{out})$                                                                                                                                                                                              \\
-			GraphSAGE-pool                                                                                                                                                                                                   &
+			GraphSAGE-pool   \cite{hamilton2017_graphsage}                                                                                                                                                                   &
 			$\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$                                                                                                                                                                    &
 			$O(1)$                                                                                                                                                                                                             \\
-			Neural FPs                                                                                                                                                                                                       &
+			Neural FPs        \cite{duvenaud2015_neural_fps}                                                                                                                                                                 &
 			$\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  (\boldsymbol{h}_i^l + \boldsymbol{s}_i^{l}))$                                                                           &
 			$O(d_{in} * d_{out})$                                                                                                                                                                                              \\
-			SSE                                                                                                                                                                                                              &
+			SSE             \cite{han2018_sse}                                                                                                                                                                               &
 			$\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 [\boldsymbol{x}_i \parallel \boldsymbol{s}_i^l]))$ &
 			$O((f + d_{in}) * d_{out})$                                                                                                                                                                                        \\
-			\textbf{GGNN}                                                                                                                                                                                                    &
+			\textbf{GGNN}    \cite{li2015_ggnn}                                                                                                                                                                              &
 			\begin{scriptsize}
@@
 			$O(d_{in} * d_{out})$                                                                                                                                                                                              \\
-			\textbf{GAT} &
+			\textbf{GAT} \cite{huang2018_gat}                                                                                                                                                                                &
 			\begin{scriptsize}
 				$\begin{aligned}[t]
-                & \text{Preprocessing:}\\
-                & \hat{\boldsymbol{h}}^{l}_{i,(k)} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l}\\
-                & \text{Sub-layer 0:}\\
-                & \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}\\
-                & \text{Sub-layer 1:}\\
+						 & \text{Preprocessing:}                                                                          \\
+						 & \hat{\boldsymbol{h}}^{l}_{i,(k)} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l} \\
+						 & \text{Sub-layer 0:}                                                                            \\
+						 & \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}                              \\
+						 & \text{Sub-layer 1:}                                                                            \\
 						 & \boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^{l,1}
@@
 				\begin{aligned}[t]
-             \text{concat:} O(d_{in}*d_{out}) &\\
-             \text{average:} O(K*d_{in}*d_{out}) &\\
-             \text{Two sub-layers}&
+					\text{concat:} O(d_{in}*d_{out})    & \\
+					\text{average:} O(K*d_{in}*d_{out}) & \\
+					\text{Two sub-layers}               &
 				\end{aligned}
@@
 			\\
-			\textbf{GaAN}                                                                                                                                                                                                    &
+			\textbf{GaAN}  \cite{zhang2018_gaan}                                                                                                                                                                             &
 			\begin{scriptsize}
 				$\begin{aligned}[t]
-						& \text{Sub-layer 0:}\\
-						& \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}\\
-						& \text{Sub-layer 1:}\\
+						 & \text{Sub-layer 0:}                                                                                                                                                                            \\
+						 & \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}                                                                                                                              \\
+						 & \text{Sub-layer 1, 2, 3:}                                                                                                                                                                      \\
 						 & \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{W}^l_g}[\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}] + \textcolor{blue}{\boldsymbol{b}^l_g} \\
@@
 			\end{scriptsize}                                                                                                                                                                                   &
-			\makecell[r]{$O(max(K * d_v + d_{in}, 2 * d_{in} + d_m) * d_{out})$\\
+			\makecell[r]{$O(max(K * d_v + d_{in}, 2 * d_{in} + d_m) * d_{out})$                                                                                                                                                \\
 				Four sub-layers}

### 2020-07-23 Manuscript/sec4-experiments.tex
更新完成初稿.

@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.png}}
-    \subfloat[GGNN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.png}}\\
-    \subfloat[GAT]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.png}}\\
-    \subfloat[GaAN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.png}}
+    \subfloat[GCN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
+    \subfloat[GaAN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.pdf}}
     \caption{Effects of hyper-parameters on the peak GPU memory usage during the training, excluding the memory used by the dataset and the model parameters.}
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.png}}
-    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_ggnn.png}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gat.png}}
-    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.png}}
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gat.pdf}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.pdf}}
     \caption{Effects of the average degree on the time proportion of the vertex/edge calculation. Graphs were generated with the R-MAT generator by fixing the number of vertices as 50,000. }
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gcn.png}}
-    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_ggnn.png}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gat.png}}
-    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.png}}
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gat.pdf}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.pdf}}
     \caption{Training time breakdown of the edge calculation stage (including both GNN layers).}

### 2020-07-23 Manuscript/sec1-introduction.tex
update by www.grammarly.com

@@
 Many GNNs \cite{kipf2017_gcn, defferrad2016_chebnet, li2018_agcn,li2015_ggnn, hamilton2017_graphsage, huang2018_gat, zhang2018_gaan} are proposed.
-GNNs can learn the representation of vertices/edges in a graph from its topology and original feature vectors in an \emph{end-to-end} manner.
-The strong expressive power makes GNNs achieve impressive accuracy in node classification, link prediction and graph classification \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020}.
+GNN can learn the representation of vertices/edges in a graph from its topology and original feature vectors in an \emph{end-to-end} manner.
+The strong expressive power makes GNN achieve impressive accuracy in node classification, link prediction, and graph classification \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020}.
 
-To train GNNs easily, a series of graph neural network learning libraries/systems \cite{PyG, DGL, ma2019_neugraph, zhu2019_aligraph, PGL} are proposed.
+To train GNN easily, a series of graph neural network learning libraries/systems \cite{PyG, DGL, ma2019_neugraph, zhu2019_aligraph, PGL} are proposed.
 PyG \cite{PyG}, NeuGraph \cite{ma2019_neugraph}, PGL \cite{PGL} and DGL \cite{DGL} build upon the existing deep learning frameworks (PyG on PyTorch, NeuGraph on Tensorflow, PGL on PaddlePaddle, DGL on multiple backends).
@@
           Overlapping the data accessing with the computation is a potential optimizing direction.
-    \item The high memory usage caused by the intermediate results of the edge calculation is the main factor that prevents us training big graphs on GPU.
+    \item The high memory usage caused by the intermediate results of the edge calculation is the main factor that prevents us from training big graphs on GPU.
     \item The sampling techniques can significantly reduce the training time and memory usage, but the implementation is still inefficient.

### 2020-07-23 Manuscript/sec2-review-of-graph-neural-network.tex
update by www.grammarly.com

@@
 
-In this section, we formally define the graph neural network (GNN, for short) and breifly survey typical graph neural networks.
+In this section, we formally define the graph neural network (GNN, for short) and briefly survey typical graph neural networks.
 We denote a simple graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
@@
 In the first GNN layer (Layer 0), the graph neuron of the vertex $v_i$ collects input feature vectors of itself and the vertices $\boldsymbol{x}_j$ that are adjacent to $v_i$ in $\mathcal{G}$ (i.e., $v_j \in \mathcal{N}(v_i)$) from the input layer.
-After aggregating input feature vectors and applying non-linear transformation, the graph neuron outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
+After aggregating input feature vectors and applying the non-linear transformation, the graph neuron outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
 Take the demo DNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as the example.
@@
 Based on the collected hidden vectors, the graph neuron in Layer 1 outputs a new hidden feature vector $\boldsymbol{h}^2_i$ for $v_i$.
-Though there are only two GNN layers in \figurename~\ref{fig:general_structure_of_gnn}, a GNN allows to stack more GNN layers to support deeper graph analysis.
+Though there are only two GNN layers in \figurename~\ref{fig:general_structure_of_gnn}, a GNN allows us to stack more GNN layers to support deeper graph analysis.
 %In \figurename~\ref{fig:general_structure_of_gnn}, we shows a GNN with two layers.
@@
 The last GNN layer (Layer $L-1$) outputs a hidden feature vector $\boldsymbol{h}^{L}_i$ for every vertex $v_i$.
-As an embedding vector, $\boldsymbol{h}^L_i$ encodoes the knowledge learned from the input layer and all the previous GNN layers.
+As an embedding vector, $\boldsymbol{h}^L_i$ encodes the knowledge learned from the input layer and all the previous GNN layers.
 Since $\boldsymbol{h}^L_i$ is affected by $v_i$ and the vertices in the $L$-hop neighborhood of $v_i$, analyzing a graph with a \emph{deeper} GNN means analyzing each vertex with a \emph{wider} scope.
@@
 The hidden feature vectors $\boldsymbol{h}^L_i$ of the last GNN layer are fed to the prediction layer to generate the output of the whole GNN.
-The prediction layer is a standard nerual network.
+The prediction layer is a standard neural network.
 The structure of the prediction layer depends on the prediction task of the GNN.
@@
 We can calculate the gradients of the loss function on the model parameters from the prediction layer directly.
-With the help of the back proporgation technique, the gradient is propogated from the prediction layer back to the previous GNN layers layer by layer.
+With the help of the backpropagation technique, the gradient is propagated from the prediction layer back to the previous GNN layers layer by layer.
 The model parameters are updated with a gradient descent optimizer like Adam.
@@
 In \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we list the edge and vertex calculation complexity, respectively.
-The time complexity of a graph neuron are affected by the dimensions of the input/output hidden vectors $d_{in}$ and $d_{out}$ and the dimensions of the model parameters (like the number of heads $K$ in GAT and the dimensions of the view vectors $d_a$/$d_v$ in GaAN).
+The time complexity of a graph neuron is affected by the dimensions of the input/output hidden vectors $d_{in}$ and $d_{out}$ and the dimensions of the model parameters (like the number of heads $K$ in GAT and the dimensions of the view vectors $d_a$/$d_v$ in GaAN).
 
 We classify the typical GNNs into four quadrants based on their edge/vertex complexity as shown in \figurename~\ref{fig:gnn_complexity_quadrant}.
-We pick GCN, GGNN, GAT and GaAN as the \emph{representative GNNs} of the four quadrants.
+We pick GCN, GGNN, GAT, and GaAN as the \emph{representative GNNs} of the four quadrants.
 
@@
 The message function $\phi$ directly uses $\hat{\boldsymbol{h}}^l_j$ as the message vector for the edge $(v_j, v_i)$.
-By this way, GGNN further reduces the time complexity of the edge calculation to $O(1)$ without increasing the time complexity of the vertex calculation.
+In this way, GGNN further reduces the time complexity of the edge calculation to $O(1)$ without increasing the time complexity of the vertex calculation.
 
@@
 The second sub-layer gets the normalized attention weights $\alpha_{j, i, (k)}$ for every edge in every head and aggregates the hidden feature vectors with the normalized weights in the message-passing.
-GAT uses the aggreated vector $\boldsymbol{s}^{l,1}_i$ of the second sub-layer as the output hidden vector directly.
+GAT uses the aggregated vector $\boldsymbol{s}^{l,1}_i$ of the second sub-layer as the output hidden vector directly.
 
 \textbf{GaAN} (high vertex \& edge calculation complexity):
-Based on the multi-head machanism, GaAN introduces a convolutional subnetwork to control the weight of each head.
-Different to multi-head machanism in GAT, GaAN project the center vertex feature to the query vector (dimension is $d_v$) and
+Based on the multi-head mechanism, GaAN introduces a convolutional subnetwork to control the weight of each head.
+Different from to multi-head mechanism in GAT, GaAN project the center vertex feature to the query vector (dimension is $d_v$), and
 the neighboring vertex features are projected to get key and value vectors. The dimension of key and values vectors are the same, we set to $d_a$.
 $K$ is the number of attention heads.
-The weight of each head is calculated by a convolutional network, which takes the feature of each vertex and its neighbors as input to get the gated values with number of $K$.
+The weight of each head is calculated by a convolutional network, which takes the feature of each vertex and its neighbors as input to get the gated values with a dimension of $K$.
 The convolutional network is built by combining average pooling and max pooling.
-Moreover, the max pooling needs to project the vertex feature to a transformed vector with dimension of $d_m$, costing an additional computational overhead.
+Moreover, the max-pooling needs to project the vertex feature to a transformed vector with a dimension of $d_m$, costing an additional computational overhead.
 Each GaAN layer consists of four sub-layers. The first sub-layer aims to get the summation of attention weights of every vertex in each head.
-The second sub-layer uses to aggreate neighboring vertices's query vector with the normalized attention weights $\alpha_{j, i, (k)}$ for every head.
+The second sub-layer uses to aggregate neighboring vertices' query vector with the normalized attention weights $\alpha_{j, i, (k)}$ for every head.
 And the third sub-layer is used in max-pooling and it gets the element-wise max vector of neighboring vertices' transformed vectors by message-passing.
@@
 In other words, the sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:gnn_sampling}.
-Inactive graph neurons and connetions do not participate in the training of this mini-batch, saving lots of computation and storage costs.
+Inactive graph neurons and connections do not participate in the training of this mini-batch, saving lots of computation and storage costs.
 Moreover, it may reduce the risk of overfitting the training graph.
-Based on whether different GNN layers sample different subgraphs, the existing sampling techniques can be devided into two groups \cite{zeng2020_graphsaint}: the neighbor sampling and the graph sampling.
+Based on whether different GNN layers sample different subgraphs, the existing sampling techniques can be divided into two groups \cite{zeng2020_graphsaint}: the neighbor sampling and the graph sampling.
 
 The neighbor sampling techniques \cite{hamilton2017_graphsage, ying2018_pinsage, chen2018_fastgcn, chen2018_sgcn, huang2018_adap} sample the subgraphs layer by layer.
-They first sample several vertices from $\mathcal{V}$ in the last GNN layer.
+The first sample several vertices from $\mathcal{V}$ in the last GNN layer.
 Then they repeatedly sample the neighbors of those vertices in the previous layer until the input layer.
@@
 $S^l$ is the hyperparameter that is usually much smaller than $|\mathcal{V}|$.
-By this way, GraphSAGE limits the neighborhood sizes of the vertices in the sampled subgraph, especially high-degree vertices.
+In this way, GraphSAGE limits the neighborhood sizes of the vertices in the sampled subgraph, especially high-degree vertices.
 

### 2020-07-23 Manuscript/sec3-experiment-design.tex
Update section 1.
update by www.grammarly.com

@@
 \section{Experiment Design}
+\label{sec:experimental_design}
 
@@
 \paragraph{Experimental Environment}
-All the experiments were conducted in a CentOS 7 Linux server with the kernel version 3.10.0.
-The server had 40 cores and 90 GB main meory.
-The server was equipped with a NVIDIA Tesla T4 GPU card with 16GB GDDR6 memory.
-For the software environment, we adopted Python 3.7.7, PyTorch 1.5.0 and CUDA 10.1.
+All the experiments were conducted in a CentOS 7 Linux server with kernel version 3.10.0.
+The server had 40 cores and 90 GB main memory.
+The server was equipped with an NVIDIA Tesla T4 GPU card with 16GB GDDR6 memory.
+For the software environment, we adopted Python 3.7.7, PyTorch 1.5.0, and CUDA 10.1.
 We implemented all the GNNs with PyTorch Geometric 1.5.0.
@@
 To evaluate the effects of graph topological characteristics (like the average degree) on the performance bottleneck uniformly, we used the R-MAT graph generator \cite{rmat-generator}.
-Input feature vectors of the random graphs were random dense vectors with the dimension of 32.
+Input feature vectors of the random graphs were random dense vectors with a dimension of 32.
 Vertices were divided into 10 classes randomly.
@@
 We trained GNNs with the semi-supervised learning setting.
-All veritces and their input feature vectors were used used, but only parts of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
-The vertices with unseed labels were used in the evaluation phsae to check the accuracy of the current parameters.
+All vertices and their input feature vectors were used, but only parts of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
+The vertices with unseen labels were used in the evaluation phase to check the accuracy of the current parameters.
 %Since model parameters of GNNs were not restricted by the topological structure of $\mathcal{G}$, the model learned from the semi-supervised learning can directly extrapolate to unseen vertices.
@@
 As GNNs used different hyper-parameters for different datasets, we picked the most popular hyper-parameters and used the same set of hyper-parameters for all the datasets in our experiments.
-Some hyper-parameters like the dimensions of hidden feature vectors were common hyper-parameters.
+Some hyper-parameters like the dimensions of hidden feature vectors were common.
 We set them to the same values in the four GNNs.
@@
 We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical neighbor sampling and graph sampling techniques, respectively.
-For the neigbhor sampler, we used the neighborhood sample sizes (25 for GNN Layer 1, and 10 for GNN Layer 0) and the default batch size (512) from \cite{hamilton2017_graphsage}.
+For the neighbor sampler, we used the neighborhood sample sizes (25 for GNN Layer 1, and 10 for GNN Layer 0) and the default batch size (512) from \cite{hamilton2017_graphsage}.
 For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to \cite{chiang2019_cluster_gcn}.
@@
 
-To find out performance bottleneck in GNN training, we conduct the bottleneck analysis with four questions.
-The answers to those questions will give us a more comprehensive view on the performance characteristics of GNN training.
-We design extensive experiments to find the answers emperically.
+To find out the performance bottleneck in GNN training, we conduct the bottleneck analysis with four questions.
+The answers to those questions will give us a more comprehensive view of the performance characteristics of GNN training.
+We design extensive experiments to find the answers empirically.
 \begin{itemize}
@@
 
-	      Every GNN has a group of hyper-parameters like the number of GNN layers and the dimision of hidden feature vectors.
+          Every GNN has a group of hyper-parameters like the number of GNN layers and the dimension of hidden feature vectors.
 The hyper-parameters affect the training time per epoch and the peak memory usage during the training.
@@
 
-	      We can decompose the training time on different levels: layer level, vertex/edge computation level and the basic operator level.
+          We can decompose the training time on different levels: layer level, vertex/edge computation level, and the basic operator level.
           On each level, we breakdown the training time of an epoch into several stages. The most time-consuming stage is the performance bottleneck.
@@
 
-	      The limited memory capacity of a GPU card is the main factor preventing us training GNNs on big graphs.
-	      We measured the peak memory usage in the GNN training under different graph scales, input feature dimensions and average vertex degrees.
+          The limited memory capacity of a GPU card is the main factor preventing us from training GNNs on big graphs.
+          We measured the peak memory usage in the GNN training under different graph scales, input feature dimensions, and average vertex degrees.
           Based on the results, we analyze which is the most memory-consuming component.
-	      Reducing its memory usage will enable us training bigger GNNs under the same memory capacity.
+          Reducing its memory usage will enable us to train bigger GNNs under the same memory capacity.
 

### 2020-07-23 Manuscript/sec4-experiments.tex
update by www.grammarly.com

@@
 We answer the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
-Without otherwise mentioned, the reported training time per epoch is the average wall-clock training time of 50 epoches, excluding abnormal epoches \footnote{During the training of some epoches, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
-Assume Q1 and Q3 are the 25\% and 75\% quantiles of the training time of 50 epoches, respectively.
-We regard the epoches with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epoches.}.
+Without otherwise mentioned, the reported training time per epoch is the average wall-clock training time of 50 epochs, excluding abnormal epochs \footnote{During the training of some epochs, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
+Assume Q1 and Q3 are the 25\% and 75\% quantiles of the training time of 50 epochs, respectively.
+We regard the epochs with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epochs.}.
 
@@
 As $dim(\boldsymbol{h}^1)$ increased, the training time increased first slightly and then linearly.
-We could observe similar phenomena in GCN, GGNN and GAT with low hyper-parameters.
+We could observe similar phenomena in GCN, GGNN, and GAT with low hyper-parameters.
 When the hyper-parameter was too low, the GNN training could not make use of the full computing power of the GPU.
@@
 The memory usage also increased linearly as the hyper-parameters increased for all GNNs, except for GaAN on $dim(\boldsymbol{h}^1)$.
-As the hidden feature vectors $\boldsymbol{h}^1$ consumed a small proportion of memory in GaAN, the growth in the memory usage was not noticable until $dim(\boldsymbol{h}^1)$ was large enough.
+As the hidden feature vectors $\boldsymbol{h}^1$ consumed a small proportion of memory in GaAN, the growth in the memory usage was not noticeable until $dim(\boldsymbol{h}^1)$ was large enough.
 
@@
 The hyper-parameters affect the training time and the memory usage of the GNN training \textbf{in a linear way}.
-Algorithm engineers can use larger hyper-parameters to increase the expressive power of a GNN model without worrying the explosive growth in the training time and memory usage.
+Algorithm engineers can use larger hyper-parameters to increase the expressive power of a GNN model without worrying about the explosive growth in the training time and memory usage.
 
@@
 \figurename~\ref{fig:exp_vertex_edge_cal_proportion} decomposes the training time of a GNN on the layer level.
-The training time of each layer is the summation of the time in the forward, backward and evaluation phases.
-In GCN, GAT and GaAN, the time spent on the layer 0 was much larger than the layer 1.
+The training time of each layer is the summation of the time in the forward, backward, and evaluation phases.
+In GCN, GAT, and GaAN, the time spent on layer 0 was much larger than layer 1.
 In those GNNs, the dimensions of the input/output feature vectors in the layer 0 were much larger than the dimensions in the layer 1.
 $d^0_{in}=dim(\boldsymbol{x})$, $d^0_{out}=d^1_{in}=64$ and $d^1_{out}=\#Class$ and $dim(\boldsymbol{x}) \gg \#Class$.
-For GaAN, since it required the dimensions of the input/output feature vectors must be same, $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers were close.
+For GaAN, since it required the dimensions of the input/output feature vectors must be the same, $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers were close.
 
-Each GNN layer can be further divided in the vertex and the edge calculation stages.
+Each GNN layer can be further divided into the vertex and the edge calculation stages.
 In \figurename~\ref{fig:exp_vertex_edge_cal_proportion}, GCN spent most of the training time on the edge calculation in most datasets.
@@
 But the high time complexity of its vertex update function $\gamma$ made the ratio of the vertex calculation in the total training time much higher than other GNNs.
-%In \textit{pub} and cam dataset, the edge calculation cost and the vertex calculation cost are close for GGNN
+%In \textit{pub} and cam dataset, the edge calculation cost, and the vertex calculation cost are close for GGNN
 %because the average degree of the two datasets is low (only 4.5 and 2.8).
@@
 The experimental results also indicate that the average degree of the dataset affects the time-consuming proportion of the vertex/edge calculation.
-For GaAN, the time spent on the vertex calculation exceeded the edge calculation on the \texttt{pub} and \texttt{cam} datasets, because the avaerage degrees of the two datasets were low, making $|\mathcal{E}|$ and $|\mathcal{V}|$ much closer.
+For GaAN, the time spent on the vertex calculation exceeded the edge calculation on the \texttt{pub} and \texttt{cam} datasets, because the average degrees of the two datasets were low, making $|\mathcal{E}|$ and $|\mathcal{V}|$ much closer.
 To evaluate the effects of the average degree, we used the R-MAT model to generate random graphs with 50k vertices and the average degrees ranging from 2 to 100.
@@
 As the average degree increased, the training time of the edge calculation grew \emph{linearly}.
-For GCN, GAT and GaAN, the edge calculation dominated the entire training time even under small average degrees.
+For GCN, GAT, and GaAN, the edge calculation dominated the entire training time even under small average degrees.
 Only for GGNN that had high vertex and low edge calculation complexities, the training time of the vertex calculation could exceed the edge calculation under low average degrees ($<5$).
@@
 
-In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collect, message, aggregate and update, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
+In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collect, message, aggregate, and update, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
 The edge index is a matrix with $M$ rows and 2 columns that holds the edge set of the graph, where $M=|\mathcal{E}|$.
@@
 The message step calls the message function $\phi$ to get message vectors of all edges $\boldsymbol{m}_{i, j}^l$.
-The aggregate step aggregates the message vectors with the same target vertex into a aggregated vector $\boldsymbol{s}^l_i$ with the aggregation operation $\Sigma$.
-The update step is optinal.
-It performs additional transformation on the aggregated vectors (for example, adding bias in GCN).
+The aggregate step aggregates the message vectors with the same target vertex into an aggregated vector $\boldsymbol{s}^l_i$ with the aggregation operation $\Sigma$.
+The update step is optional.
+It performs an additional transformation on the aggregated vectors (for example, adding bias in GCN).
 The aggregated vectors $\boldsymbol{s}^l_i$ (after the update step) will be fed into the vertex update function $\gamma$ as one of the input parameters.
@@
 For the other GNNs, optimization should focus on reducing the costs of the collect and the aggregation steps.
-Addtionally, improving the efficiency of the collect step can benefit all GNNs.
+Additionally, improving the efficiency of the collect step can benefit all GNNs.
 
@@
 The top basic operator was \texttt{mm} used in the vertex calculation.
-Due to the high time complexity in $\gamma$, the proportion of the \texttt{mm} operator were much higher than the other operators.
+Due to the high time complexity in $\gamma$, the proportion of the \texttt{mm} operator was much higher than the other operators.
 The \texttt{thnn\_fused\_gru\_cell} operator that was used in the backward phase of $\gamma$ was also noticeable.
@@
 The collect step involves lots of data movement.
-The aggregation step suffers from the data synchronization and non-regular data access.
+The aggregation step suffers from data synchronization and non-regular data access.
 Optimizing their implementations can significantly reduce the training time.
@@
 \figurename~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each phase in the GNN training on the \texttt{amp} dataset.
-The trend was similar on other datasets.
+The trend was similar to other datasets.
 \emph{The GNN training achieved its peak memory usage in the forward and the backward phases}.
 The forward phase generated a large number of intermediate results.
-Some key intermediate results were cached, increasing the memory usage.
+Some key intermediate results were cached, increasing memory usage.
 The cached results were used in the gradient calculation in the backward phase.
@@
 \figurename~\ref{fig:exp_memory_expansion_ratio} also indicates that the same GNN had different MERs for different datasets.
-Two characteristics of the dataset affects the MER: the dimension of the input feature vector and the average degree.
+Two characteristics of the dataset affect the MER: the dimension of the input feature vector and the average degree.
 
@@
 
-The average degree of the graph also affects MER by influencing the relative scale of the intermediate results from vertex/edge calculation.
+The average degree of the graph also affects MER by influencing the relative scale of the intermediate results from the vertex/edge calculation.
 Fixing the number of vertices $|\mathcal{V}|$, we used the R-MAT generator to generate random graphs with different average degrees.
@@
 The stable value was determined by the complexity of the edge calculation.
-Except for GGNN, the MERs of the other GNNs increased as $\bar{d}$ increased.
+Except for GGNN, the MER of the other GNNs increased as $\bar{d}$ increased.
 As GGNN had high vertex calculation complexity, the MER related to the vertex calculation was much larger than the edge calculation.
@@
 All GNNs were much more insensitive to the changes in $|\mathcal{V}|$ compared to $|\mathcal{E}|$.
-Except for GGNN, the MERs of the other GNNs declined as $|\mathcal{V}|$ increased because the scale of the dataset increased quicklier than the scales of the intermediate results.
+Except for GGNN, the MER of the other GNNs declined as $|\mathcal{V}|$ increased because the scale of the dataset increased more quickly than the scales of the intermediate results.
 As GGNN had high vertex calculation complexity, the scales of the intermediate results were much more sensitive to $|\mathcal{V}|$.
@@
 Each batch was a small subgraph of the dataset.
-To train on each batch, PyG sent the sampled subgraph to GPU, calculated the gradients in the subgraph and updated the model parameters directly on GPU.
+To train on each batch, PyG sent the sampled subgraph to GPU, calculated the gradients in the subgraph, and updated the model parameters directly on GPU.
 With the sampling techniques, the model parameters were updated by a stochastic gradient descent optimizer.
-It conducted the evaluation phase every several epoches (either on the CPU side or the GPU side) to determine whether to stop the training.
+It conducted the evaluation phase every several epochs (either on the CPU side or the GPU side) to determine whether to stop the training.
 The experiments focused on the training phase of each batch.
@@
 \figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changed with the batch size.
-For the neighbor sampler, the relative batch size is the porportion of the sampled vertices of the last GNN layer in all vertices of the graph.
+For the neighbor sampler, the relative batch size is the proportion of the sampled vertices of the last GNN layer in all vertices of the graph.
 For the cluster sampler, the relative batch size is the proportion of the sampled partitions to all partitions of the graph.
 The neighbor sampler was very sensitive to the batch size.
-As the batch size increased, the size of the sampled subgraph increased quickly and then stabalized.
+As the batch size increased, the size of the sampled subgraph increased quickly and then stabilized.
 The cluster sampler was much less sensitive compared to the neighbor sampler.
@@
 For the neighbor sampler, the sampling technique reduced the training time per batch only when the batch size was very small.
-When the batch became bigger, the sampling and the data transfering phases introduced noticeable overheads, even making the training time exceed the full-batch training.
+When the batch became bigger, the sampling and the data transferring phases introduced noticeable overheads, even making the training time exceed the full-batch training.
 For the clustering sampler, the sampled subgraph was smaller than the neighbor sampler under the same relative batch size.
@@
 The experimental results indicate that the implementation of the sampling techniques in PyG is inefficient.
-When the batch size was slightly big, more than 50\% of the time had been spent on sampling and data transfering.
+When the batch size was slightly big, more than 50\% of the time had been spent on sampling and data transferring.
 \emph{The sampling techniques are only efficient under small batch sizes.}
@@
 
-The disadvantage of the sampling technique is wasting the GPU resources.
+The disadvantage of the sampling technique is wasting GPU resources.
 As the sampling techniques are only effective under small batch sizes, the sampled subgraphs will be very small in those cases.
@@
 However, the current implementation of the sampling techniques was every inefficient under big batch sizes.
-The time spent on the sampling phase and the data transfering phase could even exceeded the training phase.
+The time spent on the sampling phase and the data transferring phase could even exceed the training phase.

### 2020-07-23 Manuscript/sec5-insights.tex
Update section 1.
update by www.grammarly.com

@@
 \section{Insights}
+\label{sec:insights}
 
@@
               \item If the complexity of the message function $\phi$ is high, the implementation of $\phi$ is critical to performance.
-                    Improving its efficiency can significantly reduce the training time.
+                    Improving its efficiency can significantly reduce training time.
                     For example, the attention mechanism in GNNs (like GAT and GaAN) requires an extra sub-layer to calculate the attention weight of each edge.
@@
                     The existing GNN libraries \cite{DGL, PyG, ma2019_neugraph} already introduce the \emph{fused} operator to improve their efficiency.
-                    When the message function $\phi$ is an assignment or a scalar multiplication of the hidden feature vector of the source vertex, the libraries replace the collect, message and aggregate steps with a single fused operator.
+                    When the message function $\phi$ is an assignment or a scalar multiplication of the hidden feature vector of the source vertex, the libraries replace the collect, message, and aggregate steps with a single fused operator.
                     The fused operator calculates the aggregated vectors directly from the input hidden feature vectors, minimizing the memory footprints and overlapping the memory accessing with calculation.
-                    By this way, it significantly reduces the training time of GNNs with low edge calculation complexity (like GCN) \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph}.
-                    However, the applicable condition of the fused operator is very restrict.
+                    In this way, it significantly reduces the training time of GNNs with low edge calculation complexity (like GCN) \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph}.
+                    However, the applicable condition of the fused operator is very restricted.
                     It does not work for $\phi$ with more complex operations like matrix multiplication.
-                    A potial optimization is proposing an implementation of the edge calculation that generates the aggregated vectors directly from the input hidden feature vectors on the fly, without materializing the parameter vectors and the message vectors.
+                    A potential optimization is proposing an implementation of the edge calculation that generates the aggregated vectors directly from the input hidden feature vectors on the fly, without materializing the parameter vectors and the message vectors.
           \end{itemize}
@@
           The memory expansion ratios of the typical GNNs are very high, making GPU unable to handle big graphs.
-          To train GNNs with big datasets, one solution is to distribute the dataset among severl GPUs and frequently swap parts of the dataset between GPUs and the main memory \cite{ma2019_neugraph}.
-          Another possible solution \cite{chen2016_training_deep} comes from the DNN training.
-          It only checkpoints key intermediate results during the forward propagation and recalculates the missing results on demand during the backproporgation.
-          Implementing the checkpoint mechanism in the GNN training is another potential optimization.
+          To train GNNs with big datasets, one solution is to distribute the dataset among several GPUs and frequently swap parts of the dataset between GPUs and the main memory \cite{ma2019_neugraph}.
+          Another possible solution \cite{chen2016_training_deep} comes from DNN training.
+          It only checkpoints key intermediate results during the forward propagation and recalculates the missing results on demand during the backpropagation.
+          Implementing the checkpoint mechanism in GNN training is another potential optimization.
 
-    \item \emph{Sampling techniques can significantly reduce the training time and the memory usage, but its implementation is still inefficient}.
+    \item \emph{Sampling techniques can significantly reduce the training time and memory usage, but its implementation is still inefficient}.
           The sampling techniques are effective under small batch sizes.
           Its current implementation brings considerable overheads when the batch size becomes large.
-          Improving the efficiency of the sampling is a potentil optimization.
+          Improving the efficiency of the sampling is a potential optimization.
           The subgraphs sampled with small batch sizes are small.
-          They cannot make fully use of the computing power of a GPU.
+          They cannot make full use of the computing power of a GPU.
           How to improve the GPU utilization under small batch sizes is another problem to solve.

### 2020-07-23 Manuscript/sec6-related-work.tex
update by www.grammarly.com

@@
 From the efficiency aspect, Yan et al.
-\cite{yan2020_characterizing_gcn} compare the performance characteristics of graph convolutional networks, typical graph processing (like PageRank) and MLP-based neural network on GPU.
+\cite{yan2020_characterizing_gcn} compare the performance characteristics of graph convolutional networks, typical graph processing (like PageRank), and MLP-based neural network on GPU.
 They provide optimization guidelines for the software and the hardware sides.
 Zhang et al. \cite{zhang2020_analysis_neugraph} compare the architectural characteristics of the GNN inference on GPU under the unified SAGA-NN \cite{ma2019_neugraph} programming model,
-They find that GNN inference has no fixed performance bottleneck and all components deserves to optimize.
+They find that GNN inference has no fixed performance bottleneck and all components deserve to optimize.
 These two efforts focus on the \emph{inference} phase of GNNs and they investigate the potential optimizations from an architectural view.
@@
 PyG \cite{PyG} is built upon PyTorch and it uses optimized CUDA kernels for GNNs to achieve high performance.
-DGL \cite{DGL} provides a group of high-level user APIs and supports training GNNs with a variety of backends (Tensorflow, MXNet and PyTorch) transparently.
+DGL \cite{DGL} provides a group of high-level user APIs and supports training GNNs with a variety of backends (Tensorflow, MXNet, and PyTorch) transparently.
 It also supports LSTM as the aggregation functions.
@@
 It focuses on training big datasets efficiently without sampling.
-It partitions the dataset sophisticatedly, schedules the training tasks among multiple GPUs and swaps the data among GPUs and the host asynchronously.
+It partitions the dataset sophisticatedly, schedules the training tasks among multiple GPUs, and swaps the data among GPUs and the host asynchronously.
 AliGraph \cite{zhu2019_aligraph} targets at training GNNs on big attributed heterogeneous graphs that are common in e-commerce platforms.

### 2020-07-23 Manuscript/sec1-introduction.tex
统一为edge/vertex表达

@@
 Since we focus on the efficiency issue of GNN training instead of accuracy, we classify the typical GNNs into four quadrants according to their vertex and edge calculation time complexity.
-We pick GCN \cite{kipf2017_gcn}, GGNN \cite{li2015_ggnn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan} as representative GNNs with different vertex/edge calculation complexities.
+We pick GCN \cite{kipf2017_gcn}, GGNN \cite{li2015_ggnn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan} as representative GNNs with different edge/vertex calculation complexities.
 We implement them with PyG and evaluate their efficiency with six real-world datasets on GPU.

### 2020-07-23 Manuscript/sec4-experiments.tex
统一为edge/vertex表达

@@
 
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time.}
+    \caption{Effects of hyper-parameters on the edge/vertex calculation time.}
     \label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.pdf}}
-    \caption{Effects of the average degree on the time proportion of the vertex/edge calculation. Graphs were generated with the R-MAT generator by fixing the number of vertices as 50,000. }
+    \caption{Effects of the average degree on the time proportion of the edge/vertex calculation. Graphs were generated with the R-MAT generator by fixing the number of vertices as 50,000. }
     \label{fig:exp_avg_degree_on_vertex_edge_cal_time}
@@
 
-The experimental results also indicate that the average degree of the dataset affects the time-consuming proportion of the vertex/edge calculation.
+The experimental results also indicate that the average degree of the dataset affects the time-consuming proportion of the edge/vertex calculation.
 For GaAN, the time spent on the vertex calculation exceeded the edge calculation on the \texttt{pub} and \texttt{cam} datasets, because the average degrees of the two datasets were low, making $|\mathcal{E}|$ and $|\mathcal{V}|$ much closer.
@@
 
-The average degree of the graph also affects MER by influencing the relative scale of the intermediate results from the vertex/edge calculation.
+The average degree of the graph also affects MER by influencing the relative scale of the intermediate results from the edge/vertex calculation.
 Fixing the number of vertices $|\mathcal{V}|$, we used the R-MAT generator to generate random graphs with different average degrees.

### 2020-07-24 Manuscript/sec1-introduction.tex
update Tensorflow to TensorFlow

@@
 To train GNN easily, a series of graph neural network learning libraries/systems \cite{PyG, DGL, ma2019_neugraph, zhu2019_aligraph, PGL} are proposed.
-PyG \cite{PyG}, NeuGraph \cite{ma2019_neugraph}, PGL \cite{PGL} and DGL \cite{DGL} build upon the existing deep learning frameworks (PyG on PyTorch, NeuGraph on Tensorflow, PGL on PaddlePaddle, DGL on multiple backends).
+PyG \cite{PyG}, NeuGraph \cite{ma2019_neugraph}, PGL \cite{PGL} and DGL \cite{DGL} build upon the existing deep learning frameworks (PyG on PyTorch, NeuGraph on TensorFlow, PGL on PaddlePaddle, DGL on multiple backends).
 They provide users with a high-level programming model (message-passing for PyG/PGL/DGL and SAGA-NN for NeuGraph) to describe the structure of a GNN.

### 2020-07-24 Manuscript/sec6-related-work.tex
update Tensorflow to TensorFlow

@@
 PyG \cite{PyG} is built upon PyTorch and it uses optimized CUDA kernels for GNNs to achieve high performance.
-DGL \cite{DGL} provides a group of high-level user APIs and supports training GNNs with a variety of backends (Tensorflow, MXNet, and PyTorch) transparently.
+DGL \cite{DGL} provides a group of high-level user APIs and supports training GNNs with a variety of backends (TensorFlow, MXNet, and PyTorch) transparently.
 It also supports LSTM as the aggregation functions.

### 2020-07-24 Manuscript/sec2-review-of-graph-neural-network.tex
按照GAT实际的实现修改了\delta的位置
fix illustrated拼写错误

@@
 
-As illustracted in \figurename~\ref{fig:general_structure_of_gnn}, a typical GNN can be decomposed into three parts: an input layer + several GNN layers + a prediction layer.
+As illustrated in \figurename~\ref{fig:general_structure_of_gnn}, a typical GNN can be decomposed into three parts: an input layer + several GNN layers + a prediction layer.
 
@@
 After aggregating input feature vectors and applying the non-linear transformation, the graph neuron outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
-Take the demo DNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as the example.
+Take the demo GNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as the example.
 Since $\mathcal{N}(v_3) = \{v_1, v_2, v_4, v_5, v_6\}$, the graph neuron of $v_1$ at layer 0 collects the feature vectors \{$\boldsymbol{x}_1$, $\boldsymbol{x}_2$, $\boldsymbol{x}_3$, $\boldsymbol{x}_4$, $\boldsymbol{x}_5$, $\boldsymbol{x}_6$\} from the input layer and outputs $\boldsymbol{h}^1_1$.
@@
                          & \alpha^l_{j, i, (k)} = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j,(k)}] ))} {\hat{\boldsymbol{a}}^{l,0}_{i,(k)}} \\
-                         & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^{l,1} = \parallel_{k=1}^K \delta(\alpha^l_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)})                                                         \\
-                         & \text{Multi-head average}: \boldsymbol{m}_{j, i}^{l,1} = \frac{1}{K} \sum_{k=1}^K \delta(\alpha^l_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)})
+                         & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^{l,1} = \parallel_{k=1}^K \alpha^l_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)}                                                         \\
+                         & \text{Multi-head average}: \boldsymbol{m}_{j, i}^{l,1} = \frac{1}{K} \sum_{k=1}^K \alpha^l_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)}
                     \end{aligned}$
@@
                          & \text{Sub-layer 1:}                                                                            \\
-                         & \boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^{l,1}
+                         & \boldsymbol{h}_i^{l+1} = \delta(\boldsymbol{s}_i^{l,1})
                     \end{aligned}

### 2020-07-24 Manuscript/sec4-experiments.tex
fix transferring

@@
 
-To find out the performance bottleneck with the sampling techniques, we decomposed the training time per batch into three phases: \emph{sampling} on CPU, \emph{transfering} sampled subgraphs from CPU to GPU and \emph{training} with the subgraphs on GPU.
+To find out the performance bottleneck with the sampling techniques, we decomposed the training time per batch into three phases: \emph{sampling} on CPU, \emph{transferring} sampled subgraphs from CPU to GPU and \emph{training} with the subgraphs on GPU.
 \figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.

### 2020-08-21 Manuscript/ms.tex

@@
 	\begin{abstract}
-		Graph neural network has become a research hotspot in the field of artificial intelligence due to state-of-the-art of performance
-		achieved in many graph-related tasks. At the same time, various of graph neural network systems have emerged one after another.
-		These systems have used their own skills in implementation, but there are very few works to study the performance bottleneck
-		on graph neural network training. In contrast to prior works that present characterization of GCNs and select GNNs cover GNN workloads,
-		we select typical algorithms by complexities of edge/vertex calculation. We analyze the performance bottleneck by breaking down training
-		time, study the affects of hyper-parameters and sampling technologies and find factors of memory usage. We finally put forward some key
-		findings for GNN training and hope our work can help GNN system researchers.
+        Graph neural network(GNN) has become a research hotspot in the field of artificial intelligence due to state-of-the-art performance achieved in many graph-related tasks.
+At the same time, various graph neural network systems have emerged one after another.
+        These systems have used their skills in implementation, but there are very few works to study the performance bottleneck on graph neural network training.
+In contrast to prior works that present characterization of GCNs and select GNNs cover GNN workloads,
+		we select typical algorithms by complexities of edge/vertex calculation.
+We analyze the performance bottleneck by breaking down training time, study the effects of hyper-parameters and sampling technologies, and find factors of memory usage.
+		We finally put forward some key findings for GNN training and hope our work can help GNN system researchers.
 	\end{abstract}

### 2020-08-21 Manuscript/sec2-review-of-graph-neural-network.tex

@@
 $v_i$'s aggregated vector $\boldsymbol{s}^l_i$ and its hidden vector $\boldsymbol{h}^l_i$ from the previous GNN layer are fed into the \emph{vertex update} function $\gamma^l$ to calculate the output hidden vector $\boldsymbol{h}^{l+1}_i$ of the current layer $l$, i.e., $\boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \boldsymbol{s}^l_i)$
-The end-to-end training requires $\phi^l$ and $\gamma^l$ (like multi-layer perceptrons and GRU) and $\Sigma_l$ (like mean, sum, element-wise min/max) are \emph{differentiable} to make the whole GNN differentialble.
+The end-to-end training requires $\phi^l$ and $\gamma^l$ (like multi-layer perceptrons and GRU) and $\Sigma_l$ (like mean, sum, element-wise min/max) are \emph{differentiable} to make the whole GNN differentiable.
 

### 2020-08-21 Manuscript/sec4-experiments.tex

@@
 In GCN, GAT, and GaAN, the time spent on layer 0 was much larger than layer 1.
-In those GNNs, the dimensions of the input/output feature vectors in the layer 0 were much larger than the dimensions in the layer 1.
+In those GNNs, the dimensions of the input/output feature vectors in layer 0 were much larger than the dimensions in layer 1.
 $d^0_{in}=dim(\boldsymbol{x})$, $d^0_{out}=d^1_{in}=64$ and $d^1_{out}=\#Class$ and $dim(\boldsymbol{x}) \gg \#Class$.
@@
 For GPU, they were less efficient than \texttt{mm}.
-The index-based selection \texttt{index\_select} operator from the collection step consumed around 10\% of time in all GNNs.
-Though GPUs have high on-chip memory bandwidth, improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} (like overlapping them with $\phi$) can benifit the training of all kinds of GNNs.
+The index-based selection \texttt{index\_select} operator from the collection step consumed around 10\% of the time in all GNNs.
+Though GPUs have high on-chip memory bandwidth, improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} (like overlapping them with $\phi$) can benefit the training of all kinds of GNNs.
 

### 2020-08-21 Manuscript/sec6-related-work.tex

@@
 They provide optimization guidelines for the software and the hardware sides.
-Zhang et al. \cite{zhang2020_analysis_neugraph} compare the architectural characteristics of the GNN inference on GPU under the unified SAGA-NN \cite{ma2019_neugraph} programming model,
+Zhang et al. \cite{zhang2020_analysis_neugraph} compare the architectural characteristics of the GNN inference on GPU under the unified SAGA-NN \cite{ma2019_neugraph} programming model.
 They find that GNN inference has no fixed performance bottleneck and all components deserve to optimize.

### 2020-08-22 Manuscript/sec2-review-of-graph-neural-network.tex
更新论文稿。

@@
     \centering
-    \subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4cm]{figs/illustration/layer_sampling.pdf}}
+    \subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4.1cm]{figs/illustration/layer_sampling.pdf}}
     %
-    \subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4cm]{figs/illustration/graph_sampling.pdf}}
+    \subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4.1cm]{figs/illustration/graph_sampling.pdf}}
     \caption{Training a GNN with sampling techniques. The faded graph neurons and their connections are inactivated.}

### 2020-08-22 Manuscript/ms.tex
更新修改版的论文.

@@
 	\title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
-	\author{Zhaokang Wang, Yunpan Wang}%, Chunfeng Yuan, Yihua Huang\corref{correspondingauthor}}
-	%	\cortext[correspondingauthor]{Corresponding author}
-	\ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn}%}, \{cfyuan, yhuang\}@nju.edu.cn}
+    \author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu$^*$, Yihua Huang \corref{correspondingauthor}}
+    \cortext[correspondingauthor]{Corresponding authors with equal contribution}
+    \ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, gurong, yhuang\}@nju.edu.cn}
 	\address{State Key Laboratory for Novel Software Technology, \\Department of Computer Science and Technology, Nanjing University, \\Nanjing 210023, China}

### 2020-08-22 Manuscript/sec7-conclusion.tex
update section 7.
Update section 1.
更新修改版的论文.

@@
 \section{Conclusion}
+\label{sec:conclusion}
 
@@
 Based on the analysis, we propose several potential optimizations for the GNN learning frameworks.
-We believe that our analysis can help developers to improving the implementation of the frameworks.
+We believe that our analysis can help developers to have a better understanding of the characteristics of GNN computation.
+
+\section*{Acknowledgement}
+
+This work is funded in part by National Key R\&D Program of China [grant number 2019YFC1711000]; China NSF Grants [grant number U1811461]; Jiangsu Province Industry Support Program [grant number BE2017155]; Natural Science Foundation of Jiangsu Province [grant number BK20170651]; Collaborative Innovation Center of Novel Software Technology and Industrialization; and the program B for Outstanding PhD candidate of Nanjing University.

### 2020-08-22 Manuscript/ms.tex
update ms.tex

@@
 
-	\title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
+	\title{Empirical Exploration of the Performance Bottleneck in Graph Neural Network Training}
     \author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu$^*$, Yihua Huang \corref{correspondingauthor}}
@@
 	\begin{abstract}
-        Graph neural network(GNN) has become a research hotspot in the field of artificial intelligence due to state-of-the-art performance achieved in many graph-related tasks.
-At the same time, various graph neural network systems have emerged one after another.
-        These systems have used their skills in implementation, but there are very few works to study the performance bottleneck on graph neural network training.
-In contrast to prior works that present characterization of GCNs and select GNNs cover GNN workloads,
-		we select typical algorithms by complexities of edge/vertex calculation.
-We analyze the performance bottleneck by breaking down training time, study the effects of hyper-parameters and sampling technologies, and find factors of memory usage.
-		We finally put forward some key findings for GNN training and hope our work can help GNN system researchers.
+		The graph neural network (GNN) has become a research hotspot for its state-of-the-art performance in many graph analysis tasks.
+		Various graph neural network libraries have emerged.
+		They make the development of GNNs convenient, but their performance on large datasets is not satisfying.
+		In this work, we analyze the performance bottleneck in training GNN with GPUs empirically.
+		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
+		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN).
+		We breakdown their training time and memory usage, evaluate the effects of hyper-parameters, and assess the efficiency of the sampling techniques.  
+		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training time and memory usage.
+		Future optimization can focus on it. 
+		The sampling techniques are essential for training big graphs on GPU, but their current implementations still have room for improvement.
+		Improving its efficiency is another potential optimization direction.
 	\end{abstract}
@@
 	\begin{keyword}
-		graph neural network, performance bottleneck, deep learning, characterization
+		graph neural network, performance bottleneck analysis, empirical evaluation, machine learning system, GPU
 	\end{keyword}

### 2020-08-25 Manuscript/sec1-introduction.tex
update

@@
 
-In recent years, the graph neural network (GNN) is a hot research topic in the field of artificial intelligence.
+In recent years, the graph neural network (GNN) becomes a hot research topic in the field of artificial intelligence.
 Many GNNs \cite{kipf2017_gcn, defferrad2016_chebnet, li2018_agcn,li2015_ggnn, hamilton2017_graphsage, huang2018_gat, zhang2018_gaan} are proposed.
-GNN can learn the representation of vertices/edges in a graph from its topology and original feature vectors in an \emph{end-to-end} manner.
-The strong expressive power makes GNN achieve impressive accuracy in node classification, link prediction, and graph classification \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020}.
+They can learn the representation of vertices/edges in a graph from its topology and the original feature vectors in an \emph{end-to-end} manner.
+The powerful expression ability of GNNs makes them achieve good accuracy in many graph analysis tasks \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020}, like node classification, link prediction, and graph classification.
 
-To train GNN easily, a series of graph neural network learning libraries/systems \cite{PyG, DGL, ma2019_neugraph, zhu2019_aligraph, PGL} are proposed.
+To train GNNs easily, a series of GNN libraries/systems \cite{PyG, DGL, ma2019_neugraph, zhu2019_aligraph, PGL} are proposed.
 PyG \cite{PyG}, NeuGraph \cite{ma2019_neugraph}, PGL \cite{PGL} and DGL \cite{DGL} build upon the existing deep learning frameworks (PyG on PyTorch, NeuGraph on TensorFlow, PGL on PaddlePaddle, DGL on multiple backends).
-They provide users with a high-level programming model (message-passing for PyG/PGL/DGL and SAGA-NN for NeuGraph) to describe the structure of a GNN.
-They take advantage of the common tools provided by the frameworks like the automatic differentiation to simplify the development.
-The GNN learning libraries/systems utilize specially optimized CUDA kernels (like kernel fusion \cite{DGL} \cite{ma2019_neugraph}) and other implementation techniques (like 2D graph partitioning \cite{ma2019_neugraph}) to improve the speed of GNN training.
+They provide users with a high-level programming models (the message-passing model for PyG/PGL/DGL and the SAGA-NN model for NeuGraph) to describe the structure of a GNN.
+They take advantage of the common tools provided by the underlying frameworks like the automatic differentiation to simplify the development.
+They utilize specially optimized CUDA kernels (like kernel fusion \cite{DGL} \cite{ma2019_neugraph}) and other implementation techniques (like 2D graph partitioning \cite{ma2019_neugraph}) to improve the speed of GNN training on GPUs.
 
-However, whether these optimizations solve the real performance bottleneck is still in doubt.
-Yan et al. \cite{yan2020_characterizing_gcn} and Zhang et al. \cite{zhang2020_analysis_neugraph} analyze the performance characteristics of the GNN \emph{inference} from the architectural view.
-They find that the GNN inference is more cache-friendly than the traditional graph analysis (like PageRank) and is suitable for GPU.
-They verify the effectiveness of the kernel fusion optimization in reducing the inference time.
-Nevertheless, \cite{yan2020_characterizing_gcn} and \cite{zhang2020_analysis_neugraph} focus on the inference phase and does not discuss the performance bottleneck in the training phase.
+However, what is the real performance bottleneck in the GNN training is still in doubt.
+Yan et al. \cite{yan2020_characterizing_gcn} and Zhang et al. \cite{zhang2020_analysis_neugraph} experimentally analyze the architectural characteristics of the GNN \emph{inference}.
+They find that the GNN inference is more cache-friendly than the traditional graph analysis tasks(like PageRank) and is suitable for GPU.
+They verify the effectiveness of the kernel fusion optimization in reducing the time of inference.
+Nevertheless, they only analyze the inference stage, ignoring the effects of the backpropagation during the training.
 
-To find out the performance bottleneck in the GNN training, we conduct experimental analysis in this work.
-We model the typical GNNs with the message-passing framework.
-Since we focus on the efficiency issue of GNN training instead of accuracy, we classify the typical GNNs into four quadrants according to their vertex and edge calculation time complexity.
-We pick GCN \cite{kipf2017_gcn}, GGNN \cite{li2015_ggnn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan} as representative GNNs with different edge/vertex calculation complexities.
+To explore the essential performance bottleneck in the GNN training, we conduct a range of experimental analysis in deep in this work. 
+We focus on the efficiency bottleneck of GNN training instead of accuracy. 
+We model the GNNs with the message-passing framework that decomposes a GNN layer into two parts: the vertex calculation and the edge calculation.  
+According to the time complexity of the two parts, we classify the typical GNNs into four quadrants(\{high, low\} complexity $\times$ \{vertex, edge\} calculation).
+We choose GCN \cite{kipf2017_gcn}, GGNN \cite{li2015_ggnn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan} as representative GNNs of the four quadrants.
+
 We implement them with PyG and evaluate their efficiency with six real-world datasets on GPU.
-We verify the correctness of the complexity analysis by measuring the effects of the hyper-parameters on the training time and memory usage.
-We find out the most time-consuming stage in GNN training by decomposing the training time per epoch from the layer level to the operator level.
-We analyze the memory usage during the training to discover the main factor that limits the data scalability of GNN training on GPU.
-Finally, we evaluate whether the sampling techniques affect the performance bottleneck.
-Our key findings and insights are summarized below.
+We identify the most time-consuming stage in the GNN training by decomposing the training time per epoch from the layer level to the operator level.
+We also analyze the memory usage during the training to discover the main factor that limits the data scalability of GNN training on GPU. 
+Finally, we evaluate whether or not the sampling techniques affect the performance bottleneck. 
+The key findings and insights are summarized below.
 
 \begin{itemize}
-    \item The training time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.
-          The training time and memory usage increase \emph{linearly} with hyper-parameters.
-    \item The edge-related calculation is the performance bottleneck for most GNNs.
-          The majority of the training time is spent on it.
-          For GNNs with high edge calculation complexity, optimizations should focus on the implementation of the message function that is conducted on every edge during the edge calculation.
-          For GNNs with low edge calculation complexity, optimizations should focus on the collect step and the aggregation step of the edge calculation.
-          Overlapping the data accessing with the computation is a potential optimizing direction.
-    \item The high memory usage caused by the intermediate results of the edge calculation is the main factor that prevents us from training big graphs on GPU.
-    \item The sampling techniques can significantly reduce the training time and memory usage, but the implementation is still inefficient.
-The time spent on the sampling may exceed the time spent on the training under big batch sizes.
-How to make full use of the computing power of GPUs with the sampling techniques is another question to solve.
+    \item \textbf{The training time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.}
+    Fixing other hyper-parameters, the training time and the memory usage of a GNN layer increase linearly as the input/output dimensions.
+    \item \textbf{The edge-related calculation is the performance bottleneck for most GNNs.}
+    For GNNs with high edge calculation complexity, most of the training time is spent on conducting the messaging function for every edge. 
+    For GNNs with low edge calculation complexity, the message collection and aggregation consumes most of the training time.
+    \item \textbf{The high memory usage of the edge calculation is the main factor limiting the data scalability of GNN training.}
+    The edge calculation generates and caches many intermediate results. 
+    They are an order of magnitude larger than the dataset itself. 
+    As GPUs have limited on-chip memory, the high memory consumption prevents us from training big graphs on GNNs.
+    \item \textbf{The sampling techniques can significantly reduce training time and memory usage.}
+    They are essential for training big graphs on GPUs. 
+    However, the existing implementation is still inefficient. 
+    Under big batch sizes, the time spent on the sampling may exceed the time spent on the training. 
+    Under small batch sizes, the sampled graphs are also small, wasting the computing power of GPUs.
 \end{itemize}
 
-Based on the insights, we provide several potential optimization directions.
-We believe that our analysis can help the developers of the GNN libraries/systems have a better understanding of the characteristics of GNN training and propose more targeted optimizations.
+Based on the insights, we provide several potential optimization directions:
+\begin{itemize}
+      \item To reduce training time, optimizations should focus on improving the efficiency of the edge calculation. 
+      One may consider developing optimized operators for the messaging step that is the major source of computing costs in the edge calculation.
+       Fusing operators of the collection step, messaging function and the aggregation step together is another way to reduce the overheads in the edge calculation.
+      \item To reduce memory usage, optimizations should focus on reducing the intermediate results in the edge calculation. 
+      One may consider adopting the checkpoint mechanism to cache less intermediate results during the forward phase and re-calculate the needed data on the fly during the backpropagation.
+      \item To improve the efficiency of the sampling techniques, one may consider overlapping the sampling on the CPU side with the training on the GPU side. 
+      Choosing a proper batch size automatically is another potential optimization.
+\end{itemize}
+We hope that our analysis can help the developers of the GNN libraries/systems have a better understanding of the characteristics of GNN training and propose more targeted optimizations.
 

### 2020-08-25 Manuscript/sec2-review-of-graph-neural-network.tex
update

@@
 
-In this section, we formally define the graph neural network (GNN, for short) and briefly survey typical graph neural networks.
+In this section, we formally define the graph neural networks and briefly survey typical graph neural networks.
 We denote a simple graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
@@
 
-\subsection{General Structure of Graph Neural Networks}
+\subsection{Structure of Graph Neural Networks}
 
@@
 In the first GNN layer (Layer 0), the graph neuron of the vertex $v_i$ collects input feature vectors of itself and the vertices $\boldsymbol{x}_j$ that are adjacent to $v_i$ in $\mathcal{G}$ (i.e., $v_j \in \mathcal{N}(v_i)$) from the input layer.
-After aggregating input feature vectors and applying the non-linear transformation, the graph neuron outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
+The graph neuron aggregates input feature vectors, apply non-linear transformation, and outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
 Take the demo GNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as the example.
-Since $\mathcal{N}(v_3) = \{v_1, v_2, v_4, v_5, v_6\}$, the graph neuron of $v_1$ at layer 0 collects the feature vectors \{$\boldsymbol{x}_1$, $\boldsymbol{x}_2$, $\boldsymbol{x}_3$, $\boldsymbol{x}_4$, $\boldsymbol{x}_5$, $\boldsymbol{x}_6$\} from the input layer and outputs $\boldsymbol{h}^1_1$.
+Since $\mathcal{N}(v_3) = \{v_1, v_2, v_4, v_5, v_6\}$, the graph neuron of $v_3$ at the GNN layer 0 collects the feature vectors \{$\boldsymbol{x}_1$, $\boldsymbol{x}_2$, $\boldsymbol{x}_3$, $\boldsymbol{x}_4$, $\boldsymbol{x}_5$, $\boldsymbol{x}_6$\} from the input layer and outputs $\boldsymbol{h}^1_3$.
 Different GNNs mainly differ in the graph neurons that they use.
@@
 
+Different from the traditional neural networks that layers are fully connected, the layers are sparsely connected in GNNs. 
 The connection between the input layer and the first GNN layer is determined by the topology of $\mathcal{G}$.
-In the traditional neural networks, neurons of neighboring layers are fully connected.
-In GNNs, two graph neurons are connected only if their corresponding vertices have an edge between them in $\mathcal{G}$.
+Two graph neurons are connected only if their corresponding vertices have an edge between them in $\mathcal{G}$.
 Most real-world graphs are very \emph{sparse}, i.e. $|\mathcal{E}| \ll |\mathcal{V}|^2$.
 
-In the next GNN layer (Layer 1), the graph neuron of $v_i$ collects the hidden feature vectors of itself $\boldsymbol{h}^1_i$ and its neighbors ($\boldsymbol{h}^1_j$ with $v_j \in \mathcal{N}(v_i)$) from the \emph{previous} GNN layer.
+In the next GNN layer (GNN Layer 1), the graph neuron of $v_i$ collects the hidden feature vectors of itself $\boldsymbol{h}^1_i$ and its neighbors ($\boldsymbol{h}^1_j$ with $v_j \in \mathcal{N}(v_i)$) from the \emph{previous} GNN layer.
 Based on the collected hidden vectors, the graph neuron in Layer 1 outputs a new hidden feature vector $\boldsymbol{h}^2_i$ for $v_i$.
-Though there are only two GNN layers in \figurename~\ref{fig:general_structure_of_gnn}, a GNN allows us to stack more GNN layers to support deeper graph analysis.
-%In \figurename~\ref{fig:general_structure_of_gnn}, we shows a GNN with two layers.
-
-Assume there are $L$ GNN layers.
-The last GNN layer (Layer $L-1$) outputs a hidden feature vector $\boldsymbol{h}^{L}_i$ for every vertex $v_i$.
+A GNN allows stacking more GNN layers to support deeper graph analysis.
+Assume there are $L$ GNN layers in traditional.
+The last GNN layer (GNN Layer $L-1$) outputs a hidden feature vector $\boldsymbol{h}^{L}_i$ for every vertex $v_i$.
 As an embedding vector, $\boldsymbol{h}^L_i$ encodes the knowledge learned from the input layer and all the previous GNN layers.
@@
 The structure of the prediction layer depends on the prediction task of the GNN.
-Take the node classification task as the example, as shown in \figurename~\ref{fig:general_structure_of_gnn}.
+Take the node classification task in \figurename~\ref{fig:general_structure_of_gnn} as the example.
 The node classification predicts a label for every vertex in $\mathcal{G}$.
@@
 
-Supporting end-to-end training is a prominent advantage of GNN, compared with other graph-based machine learning methods.
-We can calculate the gradients of the loss function on the model parameters from the prediction layer directly.
-With the help of the backpropagation technique, the gradient is propagated from the prediction layer back to the previous GNN layers layer by layer.
-The model parameters are updated with a gradient descent optimizer like Adam.
-Except for the input feature vector, there is no need to conduct handworked feature extraction.
-In a fully parameterized way, the GNN automatically extracts an embedding vector for each vertex from its $L$-hop neighborhood.
-The parameters are tuned according to the specific prediction task, leading to high prediction accuracy.
+Supporting end-to-end training is a prominent advantage of GNN, compared with traditional graph-based machine learning methods.
+The traditional methods need to construct feature vectors manually or from the embedding methods like DeepWalk \cite{bryan2014_deepwalk} and node2vec \cite{aditya2016_node2vec}.
+The feature vector generation is independent from the downstream prediction task. 
+Thus, the vectors have to be adjusted for every prediction task individually.
+In GNNs, the gradients are propagated from the prediction layer back to the previous GNN layers layer by layer. 
+The model parameters in the GNN layers are updated based on the feedbacks from the downstream prediction task. 
+In a fully parameterized way, the GNN automatically extracts an embedding vector for each vertex from its $L$-hop neighborhood, tuned according to the specific prediction task.
 
@@
     \caption{Graph neuron of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}(b).
-$\phi$/$\Sigma$/$\gamma$ are the message/aggregation/vertex update functions in the message-passing model, respecitvely.}
+$\phi$/$\Sigma$/$\gamma$ are the messaging/aggregation/vertex updating functions in the message-passing model, respecitvely.}
     \label{fig:graph_neuron_structure}
@@
 We follow the message-passing model \cite{gilmer_messgae_passing} to formally define a graph neuron.
-The message-passing model is widely used in the cutting-edge GNN training systems like PyTorch Geometric (PyG) \cite{PyG} and Deep Graph Library (DGL) \cite{DGL}.
+The message-passing model is widely used in the cutting-edge GNN libraries like PyTorch Geometric (PyG) \cite{PyG} and Deep Graph Library (DGL) \cite{DGL}.
 \figurename~\ref{fig:graph_neuron_structure} shows the structure of a graph neuron in the message-passing model.
-A graph neuron collects messages from its neighbor graph neurons and outputs a hidden feature vector according to the aggregated messages.
 Graph neurons at layer $l$ are made of three \emph{differentiable} functions: $\phi^l$, $\Sigma^l$ and $\gamma^l$.
@@
 
-$\phi^l$ is the \emph{message} function.
-For every incident edge $(v_j, v_i)$ of $v_i$, $\phi$ receives the output hidden feature vectors $\boldsymbol{h}^l_i$ and $\boldsymbol{h}^l_j$ of the previous GNN layer and the edge feature vector $\boldsymbol{e}_{j,i}$ as the input.
+$\phi^l$ is the \emph{messaging} function.
+For every incident edge $(v_j, v_i)$ of $v_i$, $\phi$ receives the output hidden feature vectors $\boldsymbol{h}^l_i$ and $\boldsymbol{h}^l_j$ from the previous GNN layer and the edge feature vector $\boldsymbol{e}_{j,i}$ as the input.
 $\phi^l$ emits a message vector $\boldsymbol{m}^l_{j,i}$ for every edge $(v_j, v_i)$ at layer $l$, i.e., $\boldsymbol{m}^l_{j,i}=\phi^l(\boldsymbol{h}^l_i, \boldsymbol{h}^l_j, \boldsymbol{e}_{j,i})$.
-For $v_i$, the message vectors $\boldsymbol{m}^l_{x,j}$ of its adjacent edges ($v_x \in \mathcal{N}(v_i)$) are aggregated by the \emph{aggregation} function $\Sigma^l$ to produce an aggregated vector $\boldsymbol{s}^l_i$, i.e., $\boldsymbol{s}^l_i=\mathlarger{\Sigma}^l_{v_j \in \mathcal{N}(v_i)}\boldsymbol{m}^l_{j,i}$.
-$v_i$'s aggregated vector $\boldsymbol{s}^l_i$ and its hidden vector $\boldsymbol{h}^l_i$ from the previous GNN layer are fed into the \emph{vertex update} function $\gamma^l$ to calculate the output hidden vector $\boldsymbol{h}^{l+1}_i$ of the current layer $l$, i.e., $\boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \boldsymbol{s}^l_i)$
+For every $v_i$, the message vectors $\boldsymbol{m}^l_{j,i}$ of its adjacent edges ($v_j \in \mathcal{N}(v_i)$) are aggregated by the \emph{aggregation} function $\Sigma^l$ to produce an aggregated vector $\boldsymbol{s}^l_i$, i.e., $\boldsymbol{s}^l_i=\mathlarger{\Sigma}^l_{v_j \in \mathcal{N}(v_i)}\boldsymbol{m}^l_{j,i}$.
+$v_i$'s aggregated vector $\boldsymbol{s}^l_i$ and its hidden vector $\boldsymbol{h}^l_i$ from the previous GNN layer are fed into the \emph{vertex updating} function $\gamma^l$ to calculate the output hidden vector $\boldsymbol{h}^{l+1}_i$ of the current layer $l$, i.e., $\boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \boldsymbol{s}^l_i)$
 The end-to-end training requires $\phi^l$ and $\gamma^l$ (like multi-layer perceptrons and GRU) and $\Sigma_l$ (like mean, sum, element-wise min/max) are \emph{differentiable} to make the whole GNN differentiable.
 
-Different GNNs adopt different kinds of graph neurons and have different definitions of the three functions.
-$\phi$ and $\Sigma$ are the \emph{edge calculation} functions.
-They are conducted over every edge in $\mathcal{G}$.
-$\gamma$ is the \emph{vertex calculation} function.
-It is conducted over every vertex in $\mathcal{G}$.
+Different GNNs have different definitions of the three functions.
+We regard $\phi$ and $\Sigma$ as the \emph{edge calculation} functions, since they are conducted over every edge in $\mathcal{G}$.
+We regard $\gamma$ as the \emph{vertex calculation} function, as it is conducted over every vertex in $\mathcal{G}$.
 \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
@@
 For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
-For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))$, and the other three layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
+For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))$, and the other three sub-layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
 
@@
             max                                                                                                                       &
-            $\boldsymbol{m}_{j, i}^l =  \delta(\textcolor{blue}{\boldsymbol{W}^l_{pool}} \boldsymbol{h}_j^l + \textcolor{blue}{b}^l)$ &
+            $\boldsymbol{m}_{j, i}^l =  \delta(\textcolor{blue}{\boldsymbol{W}^l_{pool}} \boldsymbol{h}_j^l + \textcolor{blue}{b^l})$ &
             $O(d_{in} * d_{out})$                                                                                                       \\
@@
                 $\begin{aligned}[t]
-                         & {\boldsymbol{z}}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^z \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^{sz} + \textcolor{blue}{\boldsymbol{U}}^z \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hz})                    \\
-                         & \boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}}^r \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}}^{sr} +\textcolor{blue}{\boldsymbol{U}}^r \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}}^{hr})                        \\
-                         & \boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}}^s + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}}^h)) \\
+                         & {\boldsymbol{z}}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}^z} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}^{sz}} + \textcolor{blue}{\boldsymbol{U}^z} \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}^{hz}})                    \\
+                         & \boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}^r} \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}^{sr}} +\textcolor{blue}{\boldsymbol{U}^r} \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}^{hr}})                        \\
+                         & \boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}^s} + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}^h})) \\
                          & \boldsymbol{h}_i^{l+1} = (1 - {\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l + {\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
@@
                          & \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}                                                                                                                              \\
-                         & \text{Sub-layer 1, 2, 3:}                                                                                                                                                                      \\
+                         & \text{After sub-layer 0,1,2,3:}                                                                                                                                                                      \\
                          & \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{W}^l_g}[\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}] + \textcolor{blue}{\boldsymbol{b}^l_g} \\
@@
 In \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we list the edge and vertex calculation complexity, respectively.
-The time complexity of a graph neuron is affected by the dimensions of the input/output hidden vectors $d_{in}$ and $d_{out}$ and the dimensions of the model parameters (like the number of heads $K$ in GAT and the dimensions of the view vectors $d_a$/$d_v$ in GaAN).
+The time complexity of a graph neuron is affected by the dimensions of the input/output hidden vectors $d_{in}$ and $d_{out}$ and the dimensions of the model parameters (like the number of heads $K$ in GAT and the dimensions of the view vectors $d_a$/$d_v$/$d_m$ in GaAN).
 
@@
 
-\textbf{GCN} \cite{kipf2017_gcn} (low vertex \& edge calculation complexity): Graph convolution network (GCN) is the first-order approximation of the spectral-based graph convolutions.
+\textbf{GCN} \cite{kipf2017_gcn} (low vertex \& edge calculation complexity): Graph convolution network (GCN \cite{kipf2017_gcn}) introduces the first-order approximation of the spectral-based graph convolutions.
 %By combining the advantages of both the spectral-based and the spatial-based convolution, it can learn the representation of the local topological structure and vertex features efficiently.
@@
 \textbf{GGNN} (high vertex \& low edge calculation complexity):
-GGNN introduces the gated recurrent unit (GRU) into the graph neural networks.
-The vertex update function $\phi$ of GGNN is a modified GRU unit that has 12 model parameters to learn, having high computational complexity.
+GGNN \cite{li2015_ggnn} introduces the gated recurrent unit (GRU) into the graph neural networks.
+The vertex updating function $\phi$ of GGNN is a modified GRU unit that has 12 model parameters to learn, having high computational complexity.
 To lower the training cost, all GNN layers share the same group of parameters in GGNN.
 GGNN further requires the dimension of $\boldsymbol{h}^{l+1}$ is equal to the dimension of $\boldsymbol{h}^l$.
-Since the message function $\phi$ only uses the hidden feature vector $\boldsymbol{h}^l_j$ of the source vertex $v_j$ of an edge $(v_j, v_i)$, in the implementation, GGNN conducts the pre-processing vertex calculation $\hat{\boldsymbol{h}}^l_i=\boldsymbol{W}\boldsymbol{h}^l_i$ for every vertex $v_i$ before the message-passing.
-The message function $\phi$ directly uses $\hat{\boldsymbol{h}}^l_j$ as the message vector for the edge $(v_j, v_i)$.
+Since the messaging function $\phi$ only uses the hidden feature vector $\boldsymbol{h}^l_j$ of the source vertex $v_j$ of an edge $(v_j, v_i)$.
+In the implementation of PyG, GGNN conducts the pre-processing vertex calculation $\hat{\boldsymbol{h}}^l_i=\boldsymbol{W}\boldsymbol{h}^l_i$ for every vertex $v_i$ before the message-passing.
+The messaging function $\phi$ directly uses $\hat{\boldsymbol{h}}^l_j$ as the message vector for the edge $(v_j, v_i)$.
 In this way, GGNN further reduces the time complexity of the edge calculation to $O(1)$ without increasing the time complexity of the vertex calculation.
@@
 \textbf{GAT} (low vertex \& high edge calculation complexity):
-GAT introduces the attention and multi-head mechanism into the graph neural networks.
+GAT \cite{huang2018_gat} introduces the attention and multi-head mechanism into the graph neural networks.
 The $K$ heads generate $K$ independent views for an edge, where $K$ is a hyper-parameter.
@@
 The first sub-layer uses the attention vectors to calculate the attention weights of every edge in every head $\boldsymbol{m}^{l,0}_{j,i,(k)}$.
-After the message-passing, the first-layer gets the summation of attention weights of every vertex in every head $\hat{\boldsymbol{a}}^{l,0}_{i,(k)}$.
-The second sub-layer gets the normalized attention weights $\alpha_{j, i, (k)}$ for every edge in every head and aggregates the hidden feature vectors with the normalized weights in the message-passing.
+After aggregation, the first sub-layer gets the summation of attention weights of every vertex in every head $\hat{\boldsymbol{a}}^{l,0}_{i,(k)}$.
+The second sub-layer calculates the normalized attention weights $\alpha_{j, i, (k)}$ for every edge in every head and aggregates the hidden feature vectors with the normalized weights in the message-passing.
 GAT uses the aggregated vector $\boldsymbol{s}^{l,1}_i$ of the second sub-layer as the output hidden vector directly.
@@
 \textbf{GaAN} (high vertex \& edge calculation complexity):
-Based on the multi-head mechanism, GaAN introduces a convolutional subnetwork to control the weight of each head.
-Different from to multi-head mechanism in GAT, GaAN project the center vertex feature to the query vector (dimension is $d_v$), and
-the neighboring vertex features are projected to get key and value vectors. The dimension of key and values vectors are the same, we set to $d_a$.
-$K$ is the number of attention heads.
-The weight of each head is calculated by a convolutional network, which takes the feature of each vertex and its neighbors as input to get the gated values with a dimension of $K$.
-The convolutional network is built by combining average pooling and max pooling.
-Moreover, the max-pooling needs to project the vertex feature to a transformed vector with a dimension of $d_m$, costing an additional computational overhead.
-Each GaAN layer consists of four sub-layers. The first sub-layer aims to get the summation of attention weights of every vertex in each head.
-The second sub-layer uses to aggregate neighboring vertices' query vector with the normalized attention weights $\alpha_{j, i, (k)}$ for every head.
-And the third sub-layer is used in max-pooling and it gets the element-wise max vector of neighboring vertices' transformed vectors by message-passing.
-The last sub-layer gets element-wise mean vector of neighboring vertices' vectors by message-passing.
-The gate values $\boldsymbol{g}^l_i$ is obtained by using a fully-connected layer with vector concatenating $\boldsymbol{h}^{l}_i$, $\boldsymbol{s}^{l, 2}_i$ and $\boldsymbol{s}^{l, 3}_i$.
-At last, GaAN uses a fully-connected layer with concatenating $\boldsymbol{h}^{l}_i$ and the result of element-wise multiplying $\boldsymbol{g}^{l}_i$ and $\boldsymbol{s}^{l, 0}_i$ to get the output hidden vector.
+Based on the multi-head mechanism, GaAN \cite{zhang2018_gaan} introduces a convolutional subnetwork to control the weight of each head.
+Each GaAN layer consists of four sub-layers. The first two sub-layers are similar to GAT, and the last two sub-layers build the convolutional subnetwork.
+The first sub-layer aims to get the summation of attention weights of every vertex in each head $\boldsymbol{\hat{a}}^{l,0}_{j, i, (k)}$.
+The second sub-layer aggregates the feature vectors with the normalized attention weights $\boldsymbol{\hat{a}}^{l,0}_{i,(k)}$.
+The third and fourth sub-layers aggregate feature vectors with element-wise max and element-wise mean operators separately.
+After the four sub-layers, the vertex updating funciton uses the aggregated vectors of last three sub-layers $\boldsymbol{s}^{l, 1}_i, \boldsymbol{s}^{l, 2}_i, \boldsymbol{s}^{l, 3}_i$ to generate the output hidden vector $\boldsymbol{h}^{l+1}_i$
 
@@
 
-To train GNNs in a mini-batch way, several sampling techniques are proposed.
+To train GNNs in a mini-batch way, the sampling techniques are proposed.
 In each mini-batch, they sample a small subgraph from the whole graph $\mathcal{G}$ and uses the subgraph to update the model parameters.
-In other words, the sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:gnn_sampling}.
-Inactive graph neurons and connections do not participate in the training of this mini-batch, saving lots of computation and storage costs.
+The sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:gnn_sampling}.
+In active graph neurons and connections do not participate in the training of this mini-batch, saving lots of computation and storage costs.
 Moreover, it may reduce the risk of overfitting the training graph.
-Based on whether different GNN layers sample different subgraphs, the existing sampling techniques can be divided into two groups \cite{zeng2020_graphsaint}: the neighbor sampling and the graph sampling.
+The existing sampling techniques can be classified into two groups \textbf{neighbor sampling and graph sampling} based on whether different GNN layers sample different subgraphs.
 
-The neighbor sampling techniques \cite{hamilton2017_graphsage, ying2018_pinsage, chen2018_fastgcn, chen2018_sgcn, huang2018_adap} sample the subgraphs layer by layer.
-The first sample several vertices from $\mathcal{V}$ in the last GNN layer.
-Then they repeatedly sample the neighbors of those vertices in the previous layer until the input layer.
+The neighbor sampling techniques \cite{hamilton2017_graphsage, ying2018_pinsage, chen2018_fastgcn, chen2018_sgcn, huang2018_adap} sample nodes or edges layer by layer.
 The sampled subgraphs of different GNN layers may be \emph{different}, as shown in \figurename~\ref{fig:gnn_sampling_neighbor_sampling}.
 GraphSAGE \cite{hamilton2017_graphsage} is the representative technique.
+The tecnnique first samples several vertices from $\mathcal{V}$ in the last GNN layer.
+Then it repeatedly samples the neighbors of those sampled vertices in the previous layer until the input layer.
 For every sampled vertex $v_i$ in the GNN layer $l$, GraphSAGE samples at most $S^l$ neighbors of $v_i$ in the previous GNN layer.
-$S^l$ is the hyperparameter that is usually much smaller than $|\mathcal{V}|$.
+$S^l$ is the hyper-parameter that is usually much smaller than $|\mathcal{V}|$.
 In this way, GraphSAGE limits the neighborhood sizes of the vertices in the sampled subgraph, especially high-degree vertices.
@@
 The cluster sampler technique \cite{chiang2019_cluster_gcn} is the representative technique.
-Given a training graph $\mathcal{G}$, it partitions $\mathcal{G}$ into closely connected clusters.
-For each mini-batch, it randomly picks $K$ clusters, where $K$ is the hyperparameter.
-The technique ignores the inter-cluster edges and only keeps the intra-cluster edges in the subgraph.
+Given a training graph $\mathcal{G}$, it partitions $\mathcal{G}$ into dense clusters.
+For each mini-batch, it randomly pick $K$ clusters to form the sampled subgraph, where $K$ is the hyper-parameter.

### 2020-08-25 Manuscript/sec4-experiments.tex
update

@@
-\section{Experiment Results and Analysis}
+\section{Evaluation Results and Analysis}
 \label{sec:experiment_results}
@@
 We answer the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
-Without otherwise mentioned, the reported training time per epoch is the average wall-clock training time of 50 epochs, excluding abnormal epochs \footnote{During the training of some epochs, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
+Without otherwise mentioned, the reported training time per epoch is the average wall-clock training time of 50 epochs, excluding abnormal epochs \footnote{During the training of some epochs, there are extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increase the training time.
 Assume Q1 and Q3 are the 25\% and 75\% quantiles of the training time of 50 epochs, respectively.
@@
 
-Theoretically, the hyper-parameters should affect the training time in a \emph{linear} way.
 According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexities of $\phi$ and $\gamma$ are linear to each hyper-parameter separately.
@@
 
-To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compare the training time of the four GNNs on the same dataset.
-\figurename~\ref{fig:exp_absolute_training_time} shows the wall-clock training time per epoch of the GNNs on the real-world datasets.
-The ranking of the training time was GaAN $\gg$ GAT $>$ GGNN $>$ GCN in all cases.
-Since the real-world graphs had more edges than edges ($m > n$), the time complexity of the edge computation affected more than the vertex computation.
-The ranking was consistent with the time complexity analysis.
+To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compare the training time of the four GNNs on the real-world datasets in \ref{tab:dataset_overview}.
+The ranking of the training time is GaAN $\gg$ GAT $>$ GGNN $>$ GCN in all cases.
+Since the real-world graphs have more edges than edges ($m > n$), the time complexity of the edge calculation stage affects more than the vertex calculation stage.
+The ranking is consistent with the time complexity analysis.
 
@@
 
-To further evaluate the effects of hyper-parameters, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.
+To further evaluate the effects of the hyper-parameters, we measure the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.
 
@@
 
-For GCN and GGNN, the only modifiable hyper-parameter is the hidden dimension $dim(\boldsymbol{h}^1)$ with $dim(\boldsymbol{h}^1) = d^0_{out} = d^1_{in}$.
-$dim(\boldsymbol{h}^0)$ and $dim(\boldsymbol{h}^2)$ is determined by the dataset with $dim(\boldsymbol{h}^0)=dim(\boldsymbol{x})$ and $dim(\boldsymbol{h}^2)=$\#Classes.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn} show that the training time of GCN and GGNN increased linearly under big $dim(\boldsymbol{h}^1)$, consistent with the time complexity analysis.
+Since $dim(\boldsymbol{h^0})$ and $dim{\boldsymbol{h^1}}$ are determined by the dataset with $dim(\boldsymbol{h}^0=dim(\boldsymbol{x}))$ and $dim(\boldsymbol{h}^2)=\#Classes$,
+for GCN and GGNN, the only modifiable hyper-parameter is the hidden dimension $dim(\boldsymbol{h}^1)$ with $dim(\boldsymbol{h}^1) = d^0_{out} = d^1_{in}$.
+According to the time complexity analysis, if we fix other hyper-parameters but only increase $dim(\boldsymbol{h}^1)$, the computing costs of the GNN layer 0 and the GNN layer 1 both increase linearly with $dim(\boldsymbol{h}^1)$, causing the training time of the whole GNN also increasing linearly.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn} show that the training time of GCN and GGNN increased linearly with $dim(\boldsymbol{h}^1)$ when $dim(\boldsymbol{h}^1)$ is big, consistent with the time complexity analysis.
 
-For GAT, we modified the number of heads $K$ and the dimension of each head $d_{head}$ in the GAT layer 0.
-The dimenstion of the hidden feature vector was determined correspondingly as $d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1) = K h_{head}$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} shows that the GAT training time increases linearly under big $d_{head}$ and $K$.
+For GAT, we modify the number of heads $K$ and the dimension of each head $d_{head}$ in the GAT layer 0.
+The dimension of the hidden feature vector is determined correspondingly as $d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1) = K d_{head}$.
+Thus, the computing costs of the GAT layer 0 and the GAT layer 1 increase linearly with K and $d_{head}$ separately. 
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} confirms the theoretical analysis.
 
 For GaAN, it is also based on the multi-head mechanism.
-Its time complexity is affected by $d_{in}$, $d_v$, $d_a$ and the number of heads $K$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time increased linearly with the hyper-parameters, except for $dim(\boldsymbol{h}^1)$.
-As $dim(\boldsymbol{h}^1)$ increased, the training time increased first slightly and then linearly.
-We could observe similar phenomena in GCN, GGNN, and GAT with low hyper-parameters.
-When the hyper-parameter was too low, the GNN training could not make use of the full computing power of the GPU.
-When it became high enough, the training time increased linearly.
+Its time complexity is affected by $dim(\boldsymbol{h}^1)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1)$), $d_a$, $d_v$, $d_m$and the number of heads $K$.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time increases linearly with the hyper-parameters, except for $dim(\boldsymbol{h}^1)$.
+As $dim(\boldsymbol{h}^1)$ increases, the training time increases first slightly and then linearly.
+We observe similar phenomena in GCN, GGNN, and GAT with low hyper-parameters.
+When the hyper-parameters is too low, the GNN training cannot make full use of the computing power of the GPU.
+When the hyper-parameter becomes high enough, the training time increases linearly, supporting the time complexity analysis.
 
@@
 
-The experimental results support the time complexity analysis.
 We further measured the effects of the hyper-parameters on the peak GPU memory usage in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
-The memory usage also increased linearly as the hyper-parameters increased for all GNNs, except for GaAN on $dim(\boldsymbol{h}^1)$.
-As the hidden feature vectors $\boldsymbol{h}^1$ consumed a small proportion of memory in GaAN, the growth in the memory usage was not noticeable until $dim(\boldsymbol{h}^1)$ was large enough.
+The memory usage also increases linearly as the hyper-parameters increase for all GNNs, except for GaAN on $dim(\boldsymbol{h}^1)$.
+As the hidden feature vectors $\boldsymbol{h}^1$ consume a small proportion of memory in GaAN, the growth in the memory usage is not noticeable until $dim(\boldsymbol{h}^1)$ is large enough.
 
@@
 The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} is valid.
-The hyper-parameters affect the training time and the memory usage of the GNN training \textbf{in a linear way}.
-Algorithm engineers can use larger hyper-parameters to increase the expressive power of a GNN model without worrying about the explosive growth in the training time and memory usage.
+Fixing other hyper-parameters, each hyper-parameter, itself affects the training time and the memory usage of a GNN Layer \textbf{in a linear way}.
+Algorithm engineers can adjust hyper-parameters according to the time complexity to avoid explosive growth in the training time and memory usage.
 
@@
 
-To find out which stage/step dominates the training time, we breakdown the training time and analyze the performance bottleneck level by level.
+To find out which stage/step dominates the training time, we decompose the training time and analyze the performance bottleneck level by level.
 
@@
 The training time of each layer is the summation of the time in the forward, backward, and evaluation phases.
-In GCN, GAT, and GaAN, the time spent on layer 0 was much larger than layer 1.
-In those GNNs, the dimensions of the input/output feature vectors in layer 0 were much larger than the dimensions in layer 1.
+In GCN, GAT, and GaAN, the time spent on the layer 0 is much larger than the layer 1.
+In those GNNs, the dimensions of the input/output feature vectors in the layer 0 are much larger than the dimensions in the layer 1.
 $d^0_{in}=dim(\boldsymbol{x})$, $d^0_{out}=d^1_{in}=64$ and $d^1_{out}=\#Class$ and $dim(\boldsymbol{x}) \gg \#Class$.
-For GaAN, since it required the dimensions of the input/output feature vectors must be the same, $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers were close.
+For GaAN, since it requires the dimensions of the input/output feature vectors must be the same, the hyper-parameter are $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers is close.
 
 Each GNN layer can be further divided into the vertex and the edge calculation stages.
-In \figurename~\ref{fig:exp_vertex_edge_cal_proportion}, GCN spent most of the training time on the edge calculation in most datasets.
+In \figurename~\ref{fig:exp_vertex_edge_cal_proportion}, GCN spends most of the training time on the edge calculation stage in most datasets.
 A special case is \texttt{cph} dataset.
-The dimension of the input feature vectors was very high in \texttt{cph}, making the vertex calculation stage of the GCN Layer 0 spend considerable time.
-GGNN also spent the majority of its training time on the edge calculation.
-But the high time complexity of its vertex update function $\gamma$ made the ratio of the vertex calculation in the total training time much higher than other GNNs.
+The dimension of the input feature vectors is very high in \texttt{cph}, making the vertex calculation stage of the GCN Layer 0 spend considerable time.
+GGNN also spends the majority of its training time on the edge calculation stage.
+But the high time complexity of its vertex updating function $\gamma$ makes the ratio of the vertex calculation in the total training time much higher than the other GNNs.
 %In \textit{pub} and cam dataset, the edge calculation cost, and the vertex calculation cost are close for GGNN
 %because the average degree of the two datasets is low (only 4.5 and 2.8).
-For GAT and GaAN, due to their high edge calculation complexity, the edge calculation is the absolutely dominant stage.
-In summary, \emph{the edge calculation is the most time-consuming stage in the GNN training}.
+For GAT and GaAN, due to their high edge calculation complexity, the edge calculation stage is the absolutely dominant stage.
+In summary, \emph{the edge calculation stage is the most time-consuming stage in the GNN training}.
 
@@
 
-The experimental results also indicate that the average degree of the dataset affects the time-consuming proportion of the edge/vertex calculation.
-For GaAN, the time spent on the vertex calculation exceeded the edge calculation on the \texttt{pub} and \texttt{cam} datasets, because the average degrees of the two datasets were low, making $|\mathcal{E}|$ and $|\mathcal{V}|$ much closer.
-To evaluate the effects of the average degree, we used the R-MAT model to generate random graphs with 50k vertices and the average degrees ranging from 2 to 100.
+The experimental results also indicate that the average degree of the dataset affects the time-consuming proportion of the edge/vertex calculation time.
+For GaAN, the time spent on the vertex calculation stage exceeds the edge calculation stage on the \texttt{pub} and \texttt{cam} datasets, because the average degrees of the two datasets are low, making $|\mathcal{E}|$ and $|\mathcal{V}|$ much closer.
+To evaluate the effects of the average degree, we used the R-MAT generator to generate random graphs with 50k vertices and the average degrees ranging from 2 to 100.
 \figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time} shows the training time of the four GNNs under different average degrees.
-As the average degree increased, the training time of the edge calculation grew \emph{linearly}.
-For GCN, GAT, and GaAN, the edge calculation dominated the entire training time even under small average degrees.
-Only for GGNN that had high vertex and low edge calculation complexities, the training time of the vertex calculation could exceed the edge calculation under low average degrees ($<5$).
-Therefore, \emph{improving the efficiency of the edge calculation is the key to reduce the GNN training time}.
+As the average degree increases, the training time of the edge calculation stage grows \emph{linearly}.
+For GCN, GAT, and GaAN, the edge calculation stage dominates the entire training time even under small average degrees.
+Only for GGNN that has high vertex and low edge calculation complexities, the training time of the vertex calculation stage exceeds the edge calculation stage under low average degrees ($<5$).
+Therefore, \emph{improving the efficiency of the edge calculation stage is the key to reduce the GNN training time}.
 
@@
 
-In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collect, message, aggregate, and update, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
+In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collection, messaging, aggregation, and updating, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
 The edge index is a matrix with $M$ rows and 2 columns that holds the edge set of the graph, where $M=|\mathcal{E}|$.
 The two columns of the matrix store the source vertex and the target vertex of each edge, respectively.
-The collect step copies the vertex feature vectors from the previous layer $\boldsymbol{h}_i^l$ to the ends of each edge
-in the edge index, to form the parameters $[\boldsymbol{h}^l_i, \boldsymbol{h}^l_{j}, \boldsymbol{e}^l_{i,j}]$ of the message function $\phi$.
+The collection step copies the vertex feature vectors from the previous layer $\boldsymbol{h}_i^l$ to the ends of each edge
+in the edge index, to form the parameters tensor $[\boldsymbol{h}^l_i, \boldsymbol{h}^l_{j}, \boldsymbol{e}^l_{i,j}]$ of the messaging function $\phi$.
 This step only involves the data movement.
-The message step calls the message function $\phi$ to get message vectors of all edges $\boldsymbol{m}_{i, j}^l$.
-The aggregate step aggregates the message vectors with the same target vertex into an aggregated vector $\boldsymbol{s}^l_i$ with the aggregation operation $\Sigma$.
-The update step is optional.
+The messaging step calls the messaging function $\phi$ to get message vectors of all edges $\boldsymbol{m}_{i, j}^l$.
+The aggregation step aggregates the message vectors with the same target vertex into an aggregated vector $\boldsymbol{s}^l_i$ with the aggregation operation $\Sigma$.
+The updating step is optional.
 It performs an additional transformation on the aggregated vectors (for example, adding bias in GCN).
-The aggregated vectors $\boldsymbol{s}^l_i$ (after the update step) will be fed into the vertex update function $\gamma$ as one of the input parameters.
+The aggregated vectors $\boldsymbol{s}^l_i$ (after the updating step) will be fed into the vertex updating function $\gamma$ as one of the input parameters.
 
@@
 
-We decomposed the execution time of the edge calculation step in \figurename~\ref{fig:exp_edge_calc_decomposition}.
-In each GNN, the proportion of the four steps were rather stable, rarely affected by datasets.
-For GAT and GaAN with the high edge calculation complexity, the message step consumed most of the execution time.
-For GCN and GGNN with the low complexity, the proportions of the steps were close.
-Since the message function $\phi$ of GGNN used the pre-computed $\hat{\boldsymbol{h}}^l_i$ as the message vector directly in the implementation, the time spent on the message step of GGNN was negligible.
-Although the collect step did not conduct any computation and only involved data movement, it occupied noticeable execution time in all the GNNs.
-The experiments show that \emph{the performance bottleneck on the step level depends on the complexity of the edge calculation}.
-For GNNs with the high edge calculation complexity, the message function $\phi$ is the performance bottleneck.
-Optimizing its implementation can significantly reduce the training time.
-For the other GNNs, optimization should focus on reducing the costs of the collect and the aggregation steps.
-Additionally, improving the efficiency of the collect step can benefit all GNNs.
+We decompose the execution time of the edge calculation stage in \figurename~\ref{fig:exp_edge_calc_decomposition}.
+In each GNN, the proportions of the four steps are rather stable, rarely affected by datasets. 
+For GAT and GaAN with the high edge calculation complexity, the messaging step consumes most of the training time. 
+For GCN and GGNN with the low edge complexity, the proportions of the steps are close. 
+Since the messaging function $\phi$ of GGNN uses the pre-computed $\hat{\boldsymbol{h}}^l_i$ as the message vector directly, the time spent on the messaging step of GGNN is negligible.
+Although the collecting step does not conduct any computation and only involves data movement, it occupies noticeable execution time in all the GNNs.
+The experiments show that \emph{the performance bottleneck on the step level depends on the complexity of the messaging function $\phi$}.
+For GNNs with the high complexity, the messaging function $\phi$ is the performance bottleneck.
+Optimizing the implementation of $\phi$ can significantly reduce the training time.
+For the other GNNs, optimization should focus on reducing the costs of the collection and the aggregation steps.
+Additionally, improving the efficiency of the collection step can benefit all GNNs.
 
@@
 \paragraph{GCN}
-The most time-consuming basic operator was the matrix multiplication \texttt{mm} used in the vertex update function $\gamma$.
-The elementwise multiplication \texttt{mul} used in the message function $\phi$ was also time-consuming.
-The other three operators were used in the edge calculation: \texttt{scatter\_add\_} for the aggregation step in the forward phase, \texttt{gather} for the aggregation step in the backward phase, and \texttt{index\_select} for the collect step.
-For GCN, the basic operators related to the edge calculation consumed the majority of the training time.
+The most time-consuming basic operator is the matrix multiplication \texttt{mm} used in the vertex updating function $\gamma$.
+The elementwise multiplication \texttt{mul} used in the messaging function $\phi$ is also time-consuming.
+The other three operators are used in the edge calculation stage: \texttt{scatter\_add\_} for the aggregation step in the forward phase, \texttt{gather} for the aggregation step in the backward phase, and \texttt{index\_select} for the collection step.
+For GCN, the basic operators related to the edge calculation stage consume the majority of the training time.
 
 \paragraph{GGNN}
-The top basic operator was \texttt{mm} used in the vertex calculation.
-Due to the high time complexity in $\gamma$, the proportion of the \texttt{mm} operator was much higher than the other operators.
-The \texttt{thnn\_fused\_gru\_cell} operator that was used in the backward phase of $\gamma$ was also noticeable.
-The other three operators were used in the edge calculation.
+The top basic operator is \texttt{mm} used in the vertex updating function $\gamma$.
+Due to its high time complexity, the proportion of the \texttt{mm} is much higher than the other operators.
+The \texttt{thnn\_fused\_gru\_cell} operator used in the backward phase of $\gamma$ is also noticeable.
+The other three operators are used in the edge calculation stage.
 
 \paragraph{GAT}
-All the top basic operators except for \texttt{mm} were related to the edge calculation.
-The \texttt{mm} operator was used in the vertex update function $\gamma$.
+All the top basic operators except for \texttt{mm} are related to the edge calculation stage.
+The \texttt{mm} operator is used in the vertex updating function $\gamma$.
 
 \paragraph{GaAN}
-The top basic operator was \texttt{bmm} used in the message function $\phi$.
-The \texttt{addmm} operator and the \texttt{mm} operator were used in both the vertex and the edge calculation, where the edge calculation is dominant.
+The top basic operator is \texttt{bmm} used in the messaging function $\phi$.
+The \texttt{addmm} operator and the \texttt{mm} operator are used in both the vertex and the edge calculation stages, where the edge calculation stage is dominant.
 
-In general, the most time-consuming operator in GNN calculation is still the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul}, \emph{making GNN training suitable for GPU}.
-Although the aggregate step in the edge calculation is relatively simple (like sum and mean), the related operators \texttt{scatter\_add} and \texttt{gather} still consumed a certain amount of the time.
-They have to synchronize between hardware threads to avoid updating the same aggregated vector at the same time and they conducted non-regular memory access with the access pattern determined by the edge set dynamically.
-For GPU, they were less efficient than \texttt{mm}.
-The index-based selection \texttt{index\_select} operator from the collection step consumed around 10\% of the time in all GNNs.
-Though GPUs have high on-chip memory bandwidth, improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} (like overlapping them with $\phi$) can benefit the training of all kinds of GNNs.
+In general, the most time-consuming operator in the four GNNs, is still the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul}, \emph{making GNN training suitable for GPU}.
+Although the aggregation step in the edge calculation stage is relatively simple (like sum and mean), the related operators \texttt{scatter\_add} and \texttt{gather} still consume a certain amount of the time.
+The operators have to synchronize between hardware threads to avoid updating the same aggregated vector at the same time.
+They also conduct non-regular memory access with the access pattern determined by the edge set dynamically.
+For GPUs, they are less efficient than \texttt{mm}.
+The index-based selection \texttt{index\_select} operator from the collection step consume around 10\% of the time in all GNNs.
+Though GPUs have high on-chip memory bandwidth, improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} can benefit the training of all kinds of GNNs.
 
@@
 The GNN training is suitable for GPU.
-The \textbf{edge calculation is the main performance bottleneck}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
-The performance bottleneck in the edge calculation depends on the time complexity of the message function $\phi$.
+\textbf{The edge calculation stage is the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
+The performance bottleneck in the edge calculation stage depends on the time complexity of the messaging function $\phi$.
 \begin{itemize}
@@
 Reducing its computation cost (via optimizing its implementation or modifying the algorithm) can significantly reduce the training time.
-    \item If the time complexity of $\phi$ is \textbf{low}, the \textbf{collect step} and the \textbf{aggregation step} limit the performance.
-The collect step involves lots of data movement.
+    \item If the time complexity of $\phi$ is \textbf{low}, the \textbf{collection step} and the \textbf{aggregation step} limit the performance.
+The collection step involves lots of data movement.
 The aggregation step suffers from data synchronization and non-regular data access.
@@
 Compared with the main memory on the host side, the capacity of the GPU memory is very limited.
-\emph{The GPU memory capacity limits the scale of graphs that a GPU can train GNNs on}.
-For example, GaAN was unable to complete the training due to memory overflow exception on \texttt{cph} dataset.
+\emph{The GPU memory capacity limits the scales of the graphs that a GPU can train GNNs on}.
+For example, GaAN is unable to train on \texttt{cph} dataset due to the out of memory exception.
 
@@
     \includegraphics[height=4.5cm]{figs/illustration/ggnn_vertex_func_computation_graph.pdf}
-    \caption{Computation graph of the vertex update function $\gamma$ of GGNN.}
+    \caption{Computation graph of the vertex updating function $\gamma$ of GGNN.}
     \label{fig:ggnn_vertex_func_computation_graph}
@@
 \figurename~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each phase in the GNN training on the \texttt{amp} dataset.
-The trend was similar to other datasets.
-\emph{The GNN training achieved its peak memory usage in the forward and the backward phases}.
-The forward phase generated a large number of intermediate results.
-Some key intermediate results were cached, increasing memory usage.
-The cached results were used in the gradient calculation in the backward phase.
-\figurename~\ref{fig:ggnn_vertex_func_computation_graph} shows the computation graph of the vertex update function $\gamma$ of GGNN.
-The computation graph had a large number of operators, each operator generating an intermediate matrix.
-Some key intermediate matrices were cached.
-The cached matrices were the main source of memory usage in the loss phase.
-By the end of the backward phase, the cached results were released.
-Since the evaluation phase did not need to calculate the gradients, it did not cache intermediate results.
-Its memory usage declined sharply.
+The trend is similar on the other datasets.
+\emph{The GNN training achieves its peak memory usage in the forward and the backward phases}.
+The forward phase generates lots of intermediate results.
+Some key intermediate results are cached, increasing memory usage.
+The cached results are used in the gradient calculation in the backward phase.
+\figurename~\ref{fig:ggnn_vertex_func_computation_graph} shows the computation graph of the vertex updating function $\gamma$ of GGNN.
+The computation graph has a large number of operators. Each operator generates an intermediate tensor.
+Some key intermediate tensors are cached.
+The cached tensors are the main source of memory usage in the loss phase.
+By the end of the backward phase, the cached tensors are released.
+Since the evaluation phase does not need to calculate the gradients, it does not cache intermediate tensors.
+Its memory usage declines sharply.
 
@@
 \figurename~\ref{fig:exp_memory_expansion_ratio} compares MER of different GNNs.
-GCN had the lowest MER (up to 14) while GaAN had the highest MER (up to 101).
-\emph{The high MER limits the data scalability of GNNs}, making GPU unable to handle big graphs.
+GCN has the lowest MER (up to 15) while GaAN has the highest MER (up to 104).
+\emph{The high MER limits the data scalability of GNNs}, making GPUs unable to handle big graphs.
 
@@
 
-\figurename~\ref{fig:exp_memory_expansion_ratio} also indicates that the same GNN had different MERs for different datasets.
-Two characteristics of the dataset affect the MER: the dimension of the input feature vector and the average degree.
+\figurename~\ref{fig:exp_memory_expansion_ratio} also indicates that the same GNN has different MERs for different datasets.
+Two characteristics of a dataset affect the MER: the dimension of the input feature vector and the average degree.
 
@@
 If the dimension of the input feature vectors is high (like the \texttt{cph} dataset), the size of the dataset is large.
-The size becomes comparable to the scales of the intermediate results,  making the MER low.
+The size may become comparable to the scales of the intermediate results,  making the MER low.
 To find out how the dimension affects the MER, we generated random input feature vectors with different dimensions for the \texttt{cam} dataset and measured the MER in \figurename~\ref{fig:exp_memory_expension_ratio_input_feature_dimension}.
-For a GNN under the same hyper-parameters, \emph{the MER decreased as the dimension of the input feature vectors increased}.
+For a GNN under the same hyper-parameters, \emph{the MER decreases as the dimension of the input feature vectors increases}.
 
@@
 
-The average degree of the graph also affects MER by influencing the relative scale of the intermediate results from the edge/vertex calculation.
+The average degree of the graph also affects MER by influencing the relative scales of the intermediate results from the edge/vertex calculation stages.
 Fixing the number of vertices $|\mathcal{V}|$, we used the R-MAT generator to generate random graphs with different average degrees.
 \figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage changes according to the average degrees.
-As the average degree $\bar{d}$ increased, the number of edges $|\mathcal{E}|$ increased and the peak memory usage increased \emph{linearly} with $\bar{d}$.
-The edge calculation gradually dominated the memory usage and \emph{the MER converged to a stable value}.
-The stable value was determined by the complexity of the edge calculation.
-Except for GGNN, the MER of the other GNNs increased as $\bar{d}$ increased.
-As GGNN had high vertex calculation complexity, the MER related to the vertex calculation was much larger than the edge calculation.
-When the edge calculation dominated the memory usage, its MER became smaller.
+As the average degree $\bar{d}$ increases, the number of edges $|\mathcal{E}|$ increases and the peak memory usage increases \emph{linearly} with $\bar{d}$.
+The edge calculation stage gradually dominates the memory usage and \emph{the MER converges to a stable value}.
+The stable value is determined by the complexity of the edge calculation stage.
+Except for GGNN, the MER of the other GNNs increases as $\bar{d}$ increases.
+As GGNN has high vertex calculation complexity, the MER related to the vertex calculation stage is much larger than the edge calculation stage.
+When the edge calculation stage dominates the memory usage, its MER becomes smaller.
 
@@
 
-We also fixed the number of edges $|\mathcal{E}|$ in the graph and generated random graphs with different $|\mathcal{V}|$.
-\figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows how the memory usage changed according to $|\mathcal{V}|$.
-All GNNs were much more insensitive to the changes in $|\mathcal{V}|$ compared to $|\mathcal{E}|$.
-Except for GGNN, the MER of the other GNNs declined as $|\mathcal{V}|$ increased because the scale of the dataset increased more quickly than the scales of the intermediate results.
-As GGNN had high vertex calculation complexity, the scales of the intermediate results were much more sensitive to $|\mathcal{V}|$.
-It indicates that \emph{the intermediate results of the edge calculation dominated the memory usage during the GNN training}.
+We also fixed the number of edges $|\mathcal{E}|$ in the graphs and generated random graphs with different $|\mathcal{V}|$.
+\figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows how the memory usage changes according to $|\mathcal{V}|$.
+All GNNs are insensitive to the changes in $|\mathcal{V}|$ compared to $|\mathcal{E}|$.
+Except for GGNN, the MERs of the other GNNs decline as $|\mathcal{V}|$ increases because the scales of the datasets increase more quickly than the scales of the intermediate results.
+As GGNN has high vertex calculation complexity, the scales of the intermediate results are much more sensitive to $|\mathcal{V}|$.
+It indicates that \emph{the intermediate results of the edge calculation stage dominated the memory usage during the GNN training}.
 
 \paragraph{Summary}
-The \emph{high} memory expansion ratio severely restricted the data scalability of the GNN training.
-The memory usage mainly came from the intermediate results of the \emph{edge calculation}.
-Fixing the number of vertices, the memory usage increased \emph{linearly} along with the number of edges.
-Optimizing the memory usage of the edge calculation could significantly reduce the memory expansion ratio.
-Fixing the GNN structure and the hyper-parameters, increasing the dimension of the input feature vectors could also reduce the memory expansion ratio.
+The \emph{high} memory expansion ratio severely restrictes the data scalability of the GNN training.
+The memory usage mainly comes from the intermediate results of the \emph{edge calculation stage}.
+Fixing the number of vertices, the memory usage increases \emph{linearly} along with the number of edges.
+Optimizing the memory usage of the edge calculation stage can significantly reduce the memory expansion ratio.
+Fixing the GNN structures and the hyper-parameters, increasing the dimension of the input feature vectors can also reduce the memory expansion ratio.
 
@@
 
-In the implementation in PyG, the GNN model and the dataset resided on the GPU side.
-To process each epoch, PyG sampled the original dataset in the main memory and generated several batches.
-Each batch was a small subgraph of the dataset.
-To train on each batch, PyG sent the sampled subgraph to GPU, calculated the gradients in the subgraph, and updated the model parameters directly on GPU.
-With the sampling techniques, the model parameters were updated by a stochastic gradient descent optimizer.
-It conducted the evaluation phase every several epochs (either on the CPU side or the GPU side) to determine whether to stop the training.
-The experiments focused on the training phase of each batch.
+In the implementation in PyG, the GNN model and the dataset resides on the GPU side.
+To process each epoch, PyG samples the original dataset in the main memory and generates several batches.
+Each batch is a small subgraph of the dataset.
+To train on each batch, PyG sends the sampled subgraph to GPU, calculates the gradients on the subgraph, and updates the model parameters directly on GPU.
+With the sampling techniques, the model parameters are updated by a stochastic gradient descent optimizer.
+PyG conducts the evaluation phase every several epochs (either on the CPU side or the GPU side) to determine whether to stop the training.
+In this section, the experiments focus on the training phase of each batch.
 
@@
 
-\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changed with the batch size.
-For the neighbor sampler, the relative batch size is the proportion of the sampled vertices of the last GNN layer in all vertices of the graph.
+\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changes with the batch size.
+For the neighbor sampler, the relative batch size is the proportion of the sampled vertices of the last GNN layer in $|\mathcal{V}|$.
 For the cluster sampler, the relative batch size is the proportion of the sampled partitions to all partitions of the graph.
-The neighbor sampler was very sensitive to the batch size.
-As the batch size increased, the size of the sampled subgraph increased quickly and then stabilized.
-The cluster sampler was much less sensitive compared to the neighbor sampler.
-The number of vertices and the average degree of the sampled subgraphs increased linearly with the batch size.
+The neighbor sampler is very sensitive to the batch size.
+As the batch size increases, the size of the sampled subgraph first increases quickly and then stabilizes.
+The cluster sampler is much less sensitive compared to the neighbor sampler.
+The number of vertices and the average degree of the sampled subgraphs increases linearly with the batch size.
 
@@
 
-It is worth noting that the average degree of the sampled subgraph was \emph{much lower} than the average degree of the whole graph, especially when the relative batch size is low.
-Taking the neighbor sampler with the relative batch size of 6\% as an example, the average degree of the \texttt{amp} dataset was 31.1, but the average degree of the sampled subgraph was only 5.8.
-For the cluster sampler, it was even lower to 3.0.
-\figurename~\ref{fig:exp_sampling_minibatch_degrees_distribution} compares the degree distribution of the sampled subgraph with the original graph.
-The slopes of the curves were similar.
-It indicates that the sampled subgraphs still followed the power-law degree distribution.
-However, the numbers of vertices in the sampled subgraphs were much smaller than the original graph, significantly lowering the average degrees.
-According to the experimental results in Section~\ref{sec:training_time_breakdown}, if the average degree becomes lower, the proportion of the training time spent on vertex calculation will become higher, especially for GGNN.
+It is worth noting that the average degree of the sampled subgraph is \emph{much lower} than the average degree of the whole graph, especially when the relative batch size is low.
+Taking the neighbor sampler with the relative batch size of 6\% as an example, the average degree of the \texttt{amp} dataset is 31.1, but the average degree of the sampled subgraph is only 5.8.
+For the cluster sampler, the average degree is 3.0.
+\figurename~\ref{fig:exp_sampling_minibatch_degrees_distribution} compares the degree distribution of the sampled subgraphs with the original graph.
+The slopes of the curves are similar.
+It indicates that the sampled subgraphs still follow the power-law degree distribution.
+However, there are much less vertices in the sampled subgraphs, significantly lowering the average degrees.
+According to the experimental results in Section~\ref{sec:training_time_breakdown}, if the average degree becomes lower, the proportion of the training time spent on the vertex calculation stage will become higher, especially for GGNN.
 
@@
 
-To find out the performance bottleneck with the sampling techniques, we decomposed the training time per batch into three phases: \emph{sampling} on CPU, \emph{transferring} sampled subgraphs from CPU to GPU and \emph{training} with the subgraphs on GPU.
+To find out the performance bottleneck with the sampling techniques, we decompose the training time per batch into three phases: \emph{sampling} on CPU, \emph{transferring} sampled subgraphs from CPU to GPU and \emph{training} with the subgraphs on GPU.
 \figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.
-For the neighbor sampler, the sampling technique reduced the training time per batch only when the batch size was very small.
-When the batch became bigger, the sampling and the data transferring phases introduced noticeable overheads, even making the training time exceed the full-batch training.
-For the clustering sampler, the sampled subgraph was smaller than the neighbor sampler under the same relative batch size.
-The reduction in the training time was more obvious than the neighbor sampler.
-However, the overheads increased quickly as the relative batch size increased.
-The training time under the 25\% relative batch size already exceeded the time of full-batch training.
-The experimental results indicate that the implementation of the sampling techniques in PyG is inefficient.
-When the batch size was slightly big, more than 50\% of the time had been spent on sampling and data transferring.
+For the neighbor sampler, the sampling technique reduces the training time per batch only when the batch size is very small.
+When the batch becomes bigger, the sampling and the data transferring phases introduce noticeable overheads, making the training time exceed the full-batch training.
+For the clustering sampler, the sampled subgraph is smaller than the neighbor sampler under the same relative batch size.
+The reduction in the training time is more obvious than the neighbor sampler.
+However, the overheads increase quickly as the relative batch size increase.
+The training time under the 25\% relative batch size already exceede the time of full-batch training.
+The experimental results indicate that the current implementation of the sampling techniques in PyG is inefficient.
+When the batch size is slightly big, more than 50\% of the time has been spent on sampling and data transferring.
 \emph{The sampling techniques are only efficient under small batch sizes.}
@@
 \figurename~\ref{fig:exp_sampling_memory_usage} shows the memory usage under different batch sizes.
-The peak memory usage declined significantly even under big batch sizes.
-The sampling techniques make training GNNs on big graphs possible for GPU.
+The peak memory usage declines significantly even under big batch sizes.
+The sampling techniques make training GNNs on big graphs possible for GPUs.
 
@@
 They cannot make full use of the computing power of a GPU.
-To simulate the cases of training GNNs with small sampled subgraphs, we generated random graphs with few vertices and measured the training time per epoch in \figurename~\ref{fig:exp_small_graph_train_time}.
-As the number of vertices increased, the training time was almost unchanged except for GaAN.
-The training time of GaAN increased only with $|\mathcal{V}| \geq 4000$.
+To simulate the situation, we generated random graphs with few vertices and measured the training time per epoch in \figurename~\ref{fig:exp_small_graph_train_time}.
+As the number of vertices increases, the training time is almost unchanged except for GaAN.
+The training time of GaAN increases only with $|\mathcal{V}| \geq 4000$.
 
 \paragraph{Summary}
-With small batch size, the sampling techniques could significantly reduce the training time per batch and the peak memory usage during the training.
-However, small batch sizes could not make full use of the computing power of a GPU.
-The sampled subgraphs had lower average degrees than the whole graph.
-However, the current implementation of the sampling techniques was every inefficient under big batch sizes.
-The time spent on the sampling phase and the data transferring phase could even exceed the training phase.
+The sampled subgraphs have lower average degrees than the whole graph.
+With small batch sizes, the sampling techniques can significantly reduce the training time per batch and the peak memory usage during the training.
+However, small batch sizes cannot make full use of the computing power of a GPU.
+With big batch sizes, the current implementation of the sampling techniques in PyG is inefficient.
+The time spent on the sampling phase and the data transferring phase even exceeds the training phase.

### 2020-08-25 Manuscript/sec7-conclusion.tex
Update acknowledgements.
update

@@
 
-In this work, we systematically study the performance bottleneck in graph neural network training.
+In this work, we systematically explore the performance bottleneck in graph neural network training. 
 We model the existing GNNs with the message-passing framework. 
-We classify the GNNs according to their edge and vertex calculation complexities to pick four typical GNNs to evaluate.
-The experimental results validate our complexity analysis.
-The training time and the memory usage increase linearly with the hyper-parameters of a GNN.
-To find out the performance bottleneck in time, we decompose the training time per epoch on different levels.
-The training time breakdown indicates that the edge calculation and its related basic operators are the performance bottleneck for most GNNs.
-Moreover, the intermediate results produced during the edge calculation cause high memory usage, limiting the data scalability.
-Adopting sampling techniques can reduce training time and memory usage significantly.
-However, the current implementation brings considerable sampling overheads.
-The small sampled graphs cannot make full use of the computing power of a GPU either.
-Our analysis indicates that the edge calculation should be the main target of optimizations.
-Reducing its memory usage and improving its efficiency can significantly improve the performance of GNN training.
-Based on the analysis, we propose several potential optimizations for the GNN learning frameworks.
-We believe that our analysis can help developers to have a better understanding of the characteristics of GNN computation.
+We classify the GNNs according to their edge and vertex calculation complexities to select four typical GNNs for evaluation. 
+The experimental results validate our complexity analysis. Fixing other hyper-parameters, the training time and the memory usage increase linearly with each hyper-parameter of the four GNNs. 
+To find out the performance bottleneck in the training time, we decompose the training time per epoch on different levels. 
+The training time breakdown analysis indicates that the edge calculation stage and its related basic operators are the performance bottleneck for most GNNs. 
+Moreover, the intermediate results produced by the edge calculation stage cause high memory usage, limiting the data scalability. 
+Adopting sampling techniques can reduce the training time and the memory usage significantly. 
+However, the current implementation of the sampling techniques in PyG brings considerable sampling overheads. 
+The small sampled subgraphs cannot make full use of the computing power of a GPU card either. 
+Our analysis indicates that the edge calculation stage should be the main target of optimizations. 
+Reducing its memory usage and improving its efficiency can significantly improve the performance of the GNN training. 
+Based on the analysis, we propose several potential optimizations for the GNN frameworks. 
+We believe that our analysis can help developers to have a better understanding of the characteristics of GNN training.
 

### 2020-08-26 Manuscript/ms.tex
更新正文的一些排版问题.
final_8_26

@@
 \usepackage{subfig}
+\usepackage{float}
 \modulolinenumbers[5]
@@
 
-	\title{Empirical Exploration of the Performance Bottleneck in Graph Neural Network Training}
-    \author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu$^*$, Yihua Huang \corref{correspondingauthor}}
+	\title{Empirical Analysis of the Performance Bottleneck in Graph Neural Network Training}
+    \author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu$^*$ \corref{correspondingauthor1}, Yihua Huang$^*$ \corref{correspondingauthor2}}
     \cortext[correspondingauthor]{Corresponding authors with equal contribution}
@@
 	\begin{abstract}
-		The graph neural network (GNN) has become a research hotspot for its state-of-the-art performance in many graph analysis tasks.
-		Various graph neural network libraries have emerged.
+		The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks.
+		Recently, various graph neural network libraries have emerged.
 		They make the development of GNNs convenient, but their performance on large datasets is not satisfying.
@@
 		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
-		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN).
+		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation.
 		We breakdown their training time and memory usage, evaluate the effects of hyper-parameters, and assess the efficiency of the sampling techniques.  
@@
 		The sampling techniques are essential for training big graphs on GPU, but their current implementations still have room for improvement.
-		Improving its efficiency is another potential optimization direction.
 	\end{abstract}

### 2020-08-26 Manuscript/sec4-experiments.tex
更新正文的一些排版问题.
新增提交文件。

@@
 
-\begin{figure}
+\begin{figure}[htb]
     \centering
@@
 
-\begin{figure}
+\begin{figure}[tbp]
     \centering
@@
 For GaAN, it is also based on the multi-head mechanism.
-Its time complexity is affected by $dim(\boldsymbol{h}^1)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1)$), $d_a$, $d_v$, $d_m$and the number of heads $K$.
+Its time complexity is affected by $dim(\boldsymbol{h}^1)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1)$), $d_a$, $d_v$, $d_m$ and the number of heads $K$.
 \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time increases linearly with the hyper-parameters, except for $dim(\boldsymbol{h}^1)$.

### 2020-08-29 CCPE/Mauscript/sec1-introduction.tex
update

--- 2020-08-25 Manuscript/sec1-introduction.tex
@@
 \section{Introduction}
-
 In recent years, the graph neural network (GNN) becomes a hot research topic in the field of artificial intelligence.
-Many GNNs \cite{kipf2017_gcn, defferrad2016_chebnet, li2018_agcn,li2015_ggnn, hamilton2017_graphsage, huang2018_gat, zhang2018_gaan} are proposed.
+Many GNNs~\cite{kipf2017_gcn, defferrad2016_chebnet, li2018_agcn,li2015_ggnn, hamilton2017_graphsage, huang2018_gat, zhang2018_gaan} are proposed.
 They can learn the representation of vertices/edges in a graph from its topology and the original feature vectors in an \emph{end-to-end} manner.
@@
 \begin{itemize}
-      \item To reduce training time, optimizations should focus on improving the efficiency of the edge calculation. 
+      \item To reduce training time, \textbf{optimizations should focus on improving the efficiency of the edge calculation}. 
       One may consider developing optimized operators for the messaging step that is the major source of computing costs in the edge calculation.
        Fusing operators of the collection step, messaging function and the aggregation step together is another way to reduce the overheads in the edge calculation.
-      \item To reduce memory usage, optimizations should focus on reducing the intermediate results in the edge calculation. 
+      \item To reduce memory usage, \textbf{optimizations should focus on reducing the intermediate results in the edge calculation}. 
       One may consider adopting the checkpoint mechanism to cache less intermediate results during the forward phase and re-calculate the needed data on the fly during the backpropagation.
-      \item To improve the efficiency of the sampling techniques, one may consider overlapping the sampling on the CPU side with the training on the GPU side. 
+      \item To improve the efficiency of the sampling techniques, \textbf{one may consider overlapping the sampling on the CPU side with the training on the GPU side.} 
       Choosing a proper batch size automatically is another potential optimization.

### 2020-08-29 CCPE/Mauscript/sec5-insights.tex
update

--- 2020-07-23 Manuscript/sec5-insights.tex
@@
 
-Through the extensive experiments, we propose the following key findings/suggestions for how to optimize the performance of GNN training.
+Through the extensive experiments, we propose the following key findings and suggestions for how to optimize the performance of the GNN training.
 
@@
           The time complexity points out where the bottleneck comes from.
-          Optimization should focus on complex operations in $\phi$ and $\gamma$.
+          Optimization should focus on complex operations in the messaging function $\phi$ and the vertex updating function $\gamma$.
 
     \item \emph{The computational cost of a GNN layer is mainly affected by the dimensions of the input and the output hidden feature vectors.}
-          Theoretically and empirically, the training time and the memory usage both increase \emph{linearly} with the dimensions of the hidden feature vectors.
+          Theoretically and empirically, the training time and the memory usage of a GNN layer both increase \emph{linearly} with the dimensions of the input/output hidden feature vectors separately.
           GNNs are friendly to high-dimensional scenarios. 
-          Algorithm engineers can use high-dimensional feature vectors to improve the expressive power of a GNN without worrying explosive growth in the training time and memory usage.
-
-    \item \emph{Performance optimizations should focus on improving the efficiency of the edge calculation.}
-          The edge calculation is the most time-consuming phase in most GNNs.
+          Algorithm engineers can use high-dimensional feature vectors to improve the expressive power of a GNN without worrying exponential growth in the training time and memory usage
+    \item \emph{Performance optimizations should focus on improving the efficiency of the edge calculation stage.}
+          The edge calculation stage is the most time-consuming stage in most GNNs.
           \begin{itemize}
-              \item If the complexity of the message function $\phi$ is high, the implementation of $\phi$ is critical to performance.
-                    Improving its efficiency can significantly reduce training time.
+              \item If the complexity of the messaging function $\phi$ is high, the implementation of $\phi$ is critical to performance.
+                    Improving its efficiency can significantly reduce the training time.
                     For example, the attention mechanism in GNNs (like GAT and GaAN) requires an extra sub-layer to calculate the attention weight of each edge.
                     Implementing it with the specially optimized basic operators on GPU is a potential optimization.
-              \item If the complexity of $\phi$ is low, the efficiency of the collect step and the aggregation step becomes critical.
+              \item If the complexity of $\phi$ is low, the efficiency of the collection step and the aggregation step becomes critical.
                     The existing GNN libraries \cite{DGL, PyG, ma2019_neugraph} already introduce the \emph{fused} operator to improve their efficiency.
-                    When the message function $\phi$ is an assignment or a scalar multiplication of the hidden feature vector of the source vertex, the libraries replace the collect, message, and aggregate steps with a single fused operator.
-                    The fused operator calculates the aggregated vectors directly from the input hidden feature vectors, minimizing the memory footprints and overlapping the memory accessing with calculation.
+                    When the messaging function $\phi$ is an assignment or a scalar multiplication of the hidden feature vector of the source vertex, the libraries replace the collection, messaging, and aggregation steps with a single fused operator.
+                    The fused operator calculates the aggregated vectors directly from the input hidden feature vectors, minimizing the memory footprints and overlapping the memory accessing with computation.
                     In this way, it significantly reduces the training time of GNNs with low edge calculation complexity (like GCN) \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph}.
@@
                     It does not work for $\phi$ with more complex operations like matrix multiplication.
-                    A potential optimization is proposing an implementation of the edge calculation that generates the aggregated vectors directly from the input hidden feature vectors on the fly, without materializing the parameter vectors and the message vectors.
+                    A potential optimization is to develop composite CUDA kernels that can read the input hidden feature vectors and aggregate message vectors on the fly, without materializing the parameter vectors and the message vectors.
 \end{itemize}
-    \item \emph{The high memory usage caused by the intermediate results of the edge calculation limits the data scalability of the GNN training.}
-          The memory expansion ratios of the typical GNNs are very high, making GPU unable to handle big graphs.
-          To train GNNs with big datasets, one solution is to distribute the dataset among several GPUs and frequently swap parts of the dataset between GPUs and the main memory \cite{ma2019_neugraph}.
-          Another possible solution \cite{chen2016_training_deep} comes from DNN training.
-          It only checkpoints key intermediate results during the forward propagation and recalculates the missing results on demand during the backpropagation.
-          Implementing the checkpoint mechanism in GNN training is another potential optimization.
+    \item \emph{The high memory usage caused by the intermediate results of the edge calculation stage limits the data scalability of the GNN training.}
+          The memory expansion ratios of the typical GNNs are very high, making GPUs unable to handle big graphs.
+          One solution is to distribute the dataset among several GPUs and frequently swap parts of the dataset between GPUs and the main memory \cite{ma2019_neugraph}.
+          Another possible solution \cite{chen2016_training_deep} comes from the deep neural network training.
+          It only checkpoints key intermediate results during the forward propagation and re-calculates the missing results on demand during the backpropagation.
+          Implementing the checkpoint mechanism in the GNN training is another potential optimization.
 
@@
           Improving the efficiency of the sampling is a potential optimization.
-          The subgraphs sampled with small batch sizes are small.
+          The sampled subgraphs are usually small.
           They cannot make full use of the computing power of a GPU.

### 2020-08-29 CCPE/Mauscript/wileyNJD-AMA.tex
update

\documentclass[AMA,STIX1COL]{WileyNJD-v2}
\usepackage{lineno,hyperref}
\usepackage{amsmath, amsthm}
\usepackage{relsize}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{lscape}
\usepackage{xcolor}
\usepackage{subfig}
\usepackage{float}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\articletype{Article Type}%

\received{}
\revised{}
\accepted{}

\raggedbottom

\begin{document}

\title{This is the sample article title}

\author[1]{Author One*}
\author[2,3]{Author Two}
\author[3]{Author Three}

\authormark{AUTHOR ONE \textsc{et al}}

\address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
\address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
\address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}

\presentaddress{This is sample for present address text this is sample for present address text}

\abstract[Summary]{The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks.
Recently, various graph neural network libraries have emerged.
They make the development of GNNs convenient, but their performance on large datasets is not satisfying.
In this work, we analyze the performance bottleneck in training GNN with GPUs empirically.
A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation.
We breakdown their training time and memory usage, evaluate the effects of hyper-parameters, and assess the efficiency of the sampling techniques.  
The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training time and memory usage.
Future optimization can focus on it. 
The sampling techniques are essential for training big graphs on GPU, but their current implementations still have room for improvement.}

\keywords{graph neural network, performance bottleneck analysis, empirical evaluation, machine learning system, GPU}

\maketitle

\section{Macros}

This URL contains the LaTeX Class file for Software: Practice and Experience (SP\&E):
\begin{verbatim}
\url{https://onlinelibrary.wiley.com/page/journal/1097024x/homepage/la_tex_class_file.htm}
\end{verbatim}
Clicking on ``AMA-stix.zip'' downloads the file AMA-stix-1510051231000.zip from this URL:
\begin{verbatim}
\url{https://wol-prod-cdn.literatumonline.com/pb-assets/assets/1097024X/AMA-stix-1510051231000.zip}
\end{verbatim}
In file AMA-stix/ama/wileyNJD-AMA.tex, there is an example latex document for authors.
I have edited this file to demonstrate problems with the latex macros in files WileyNJD-v2.cls and WileyNJD-AMA.bst, and used the following command to generate a PDF file.
\begin{verbatim}
pdflatex wileyNJD-AMA; bibtex wileyNJD-AMA; pdflatex wileyNJD-AMA; pdflatex wileyNJD-AMA;
\end{verbatim}

\section{First Problem}

The header on this page is:
\begin{quote}
Received {\color{red}26 April 2016} | Revised {\color{red}6 June 2016} | Accepted {\color{red}6 June 2016}
\end{quote}
Authors do not know these dates, so they are likely to just leave the dates unchanged.
It would be better to have a placeholder:
\begin{quote}
Received {\color{red}Added at production} | Revised {\color{red}Added at production} | Accepted {\color{red}Added at production}
\end{quote}

\section{Second Problem}

SP\&E style use symbols for footnotes and numbers for bibliography citations.
However, the latex macros generate numbers for footnotes rather than symbols number, which makes it impossible to tell the difference between a footnote and a citation.
This is a footnote\footnote{Footnote} and this is a citation~\cite{book01}, and they both are numbered $^1$.
Attempting to fix the problem by adding the following latex command results in an error.
\begin{verbatim}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\end{verbatim}

\section{Third Problem}\label{section}

The ``ref'' macro used to print label for section, figures and tables leaves an extra space after the label number for figures and tables but not sections.
Figure~\ref{figure} has an extra space after the number, as does Table~\ref{table}, but Section~\ref{section} does not have an extra space.

\begin{figure}
\centering
I'm a figure above the caption
\caption{This is the sample figure caption}
\label{figure}
\end{figure}

\begin{table}
\caption{This is the sample table caption}
\label{table}
\centering
I'm a table below the caption
\end{table}

\section{Fourth Problem}

There are multiple problems in the WileyNJD-AMA.bst macros for formatting bibliographic entries.
Specifically, fields within entries are missing, as is space between fields, possibly in an attempt to shorten the length of the bibliographic entries.

Here is an exhaustive list of all fields for all bibliography entries.
\begin{quote}
article~\cite{article01}, book~\cite{book01}, booklet~\cite{booklet01}, inbook~\cite{inbook01}, incollection~\cite{incollection01}, inproceedings~\cite{inproceedings01}, manual~\cite{manual01}, mastersthesis~\cite{mastersthesis01}, misc~\cite{misc01}, phdthesis~\cite{phdthesis01}, proceedings~\cite{proceedings01}, techreport~\cite{techreport01}, unpublished~\cite{unpublished01}
\end{quote}
Looking at the references below, there are multiple fields missing from the bibliographic entries, there are spaces before periods, and there are fields run together, etc.

\input{sec1-introduction.tex}
\input{sec2-review-of-graph-neural-network.tex}
\input{sec3-experiment-design.tex}
\input{sec4-experiments.tex}
\input{sec5-insights.tex}
\input{sec6-related-work.tex}
\input{sec7-conclusion.tex}

\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
\bibliography{wileyNJD-AMA}%

\end{document}

### 2020-08-29 CCPE/Mauscript/sec2-review-of-graph-neural-network.tex
update

--- 2020-08-25 Manuscript/sec2-review-of-graph-neural-network.tex
@@
 \begin{table}
-    \hspace{-5em}
+    \centering
     \begin{footnotesize}
@@
 \begin{table}
+    \centering
     \begin{footnotesize}
@@
 
-\textbf{GCN} \cite{kipf2017_gcn} (low vertex \& edge calculation complexity): Graph convolution network (GCN \cite{kipf2017_gcn}) introduces the first-order approximation of the spectral-based graph convolutions.
+\textbf{GCN} (low vertex \& edge calculation complexity): Graph convolution network (GCN \cite{kipf2017_gcn}) introduces the first-order approximation of the spectral-based graph convolutions.
 %By combining the advantages of both the spectral-based and the spatial-based convolution, it can learn the representation of the local topological structure and vertex features efficiently.

### 2020-08-29 CCPE/Mauscript/sec3-experiment-design.tex
update

--- 2020-07-23 Manuscript/sec3-experiment-design.tex
@@
-\section{Experiment Design}
+\section{Evaluation Design}
 \label{sec:experimental_design}
 
-We design a series of experiments to find out the performance bottleneck in training graph neural networks.
+We design a series of experiments to explore the performance bottleneck in training graph neural networks.
 We first introduce the experimental setting in Section~\ref{sec:experimental_env} and then give out our experimental scheme in Section~\ref{sec:experimental_scheme}.
-The experiment results are presented and analyzed later in Section~\ref{sec:experiment_results}.
+The evaluation results are presented and analyzed later in Section~\ref{sec:experiment_results}.
 
@@
 The server had 40 cores and 90 GB main memory.
-The server was equipped with an NVIDIA Tesla T4 GPU card with 16GB GDDR6 memory.
+The server was equipped with an NVIDIA Tesla T4 GPU with 16GB GDDR6 memory.
 For the software environment, we adopted Python 3.7.7, PyTorch 1.5.0, and CUDA 10.1.
@@
 For the \texttt{cam} dataset, we generated random dense feature vectors.
-Since we mainly focus on the training efficiency of GNNs instead of accuracies, we also used random graphs in the experiments.
-To evaluate the effects of graph topological characteristics (like the average degree) on the performance bottleneck uniformly, we used the R-MAT graph generator \cite{rmat-generator}.
-Input feature vectors of the random graphs were random dense vectors with a dimension of 32.
-Vertices were divided into 10 classes randomly.
+We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in the experiments, to explore the effects of graph topological characteristics (like the average degree) on the performance bottleneck.
+Input feature vectors of random graphs were random dense vectors with a dimension of 32.
+Vertices of random graphs were classified into 10 classes randomly.
 
@@
     \centering
-    \small
     \begin{tabular}{cccccccc}
         \toprule
-        Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $dim(\boldsymbol{x})$ & Sparsity & \#Class & Directed \\
+        Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $dim(\boldsymbol{x})$ & \#Class & Directed \\
         \midrule
-        pubmed (pub) \cite{yang2016_revisiting_semisupervised}  & 19,717          & 44,324          & 4.5       & 500                   & 0.90     & 3       & Yes      \\
-        amazon-photo (amp) \cite{shchur2018_pitfall_of_gnn}     & 7,650           & 119,081         & 31.1      & 745                   & 0.65     & 8       & Yes      \\
-        amazon-computers (amc) \cite{shchur2018_pitfall_of_gnn} & 13,752          & 245,861         & 35.8      & 767                   & 0.65     & 10      & Yes      \\
-        coauthor-physics (cph) \cite{shchur2018_pitfall_of_gnn} & 34,493          & 247,962         & 14.4      & 8415                  & 0.996    & 5       & Yes      \\
-        flickr (fli) \cite{zeng2020_graphsaint}                 & 89,250          & 899,756         & 10.1      & 500                   & 0.54     & 7       & No       \\
-        com-amazon (cam) \cite{yang2012_defining}               & 334,863         & 925,872         & 2.8       & 32                    & 0.0      & 10      & No       \\
+        pubmed (pub) \cite{yang2016_revisiting_semisupervised}  & 19,717          & 44,324          & 4.5       & 500                   & 3       & Yes      \\
+        amazon-photo (amp) \cite{shchur2018_pitfall_of_gnn}     & 7,650           & 119,081         & 31.1      & 745                   & 8       & Yes      \\
+        amazon-computers (amc) \cite{shchur2018_pitfall_of_gnn} & 13,752          & 245,861         & 35.8      & 767                   & 10      & Yes      \\
+        coauthor-physics (cph) \cite{shchur2018_pitfall_of_gnn} & 34,493          & 247,962         & 14.4      & 8415                  & 5       & Yes      \\
+        flickr (fli) \cite{zeng2020_graphsaint}                 & 89,250          & 899,756         & 10.1      & 500                   & 7       & No       \\
+        com-amazon (cam) \cite{yang2012_defining}               & 334,863         & 925,872         & 2.8       & 32                    & 10      & No       \\
         \bottomrule
     \end{tabular}
-    \caption{Dataset overview.
-$\bar{d}$ represents the average vertex degree.
-$dim(\boldsymbol{x})$ is the dimension of the input feature vector.
-The sparsity is the proportion of zero elements in the input feature vectors.}
+    \caption{Dataset overview. $\bar{d}$ represents the average vertex degree. $dim(\boldsymbol{x})$ is the dimension of the input feature vector.}
     \label{tab:dataset_overview}
@@
 All vertices and their input feature vectors were used, but only parts of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
-The vertices with unseen labels were used in the evaluation phase to check the accuracy of the current parameters.
+The vertices with unseen labels were used in the evaluation phase to evaluate the accuracy of the current parameters.
 %Since model parameters of GNNs were not restricted by the topological structure of $\mathcal{G}$, the model learned from the semi-supervised learning can directly extrapolate to unseen vertices.
@@
 The structure was popular in the experimental evaluation of GCN \cite{kipf2017_gcn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan}.
-Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, we added two MLP layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
-We stored the dataset and the model parameters in the memory of GPU.
+Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, we added two multi-layer perceptron(MLP) layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
+We stored the dataset and the model parameters on the GPU side.
 All the training was conducted on GPU.
@@
 We use $dim(\boldsymbol{v})$ to denote the dimension of a vector $\boldsymbol{v}$.
-We picked the hyper-parameters of GNNs according to their original papers.
-As GNNs used different hyper-parameters for different datasets, we picked the most popular hyper-parameters and used the same set of hyper-parameters for all the datasets in our experiments.
-Some hyper-parameters like the dimensions of hidden feature vectors were common.
-We set them to the same values in the four GNNs.
+We picked the hyper-parameters of GNNs according to their popularity in the original papers.
+We used the same set of hyper-parameters for all the datasets. 
+Some hyper-parameters like the dimensions of hidden feature vectors were common in the four GNNs and we set them to the same values.
 For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, $dim(\boldsymbol{h}^1_i)=64$, and $dim(\boldsymbol{h}^2_i)=\#Classes$.
 For GAT, we set the hyper-parameters according to \cite{huang2018_gat}.
-The first GAT layer had 8 heads with $d^0_{head}=8$ and merged the heads by concatenating.
-The second GAT layer used a single head with $d^1_{head}=d^1_{out}=\#Classes$.
+The first GAT layer had 8 heads with the dimension of each head $d^0_{head}=8$. The first GAT layer merged the heads by concatenating.
+The second GAT layer used a single head with the dimension $d^1_{head}=d^1_{out}=\#Classes$.
 For GGNN, since it uses extra MLP layers to transform the dimensions of the input/output feature vectors, we set $dim(\boldsymbol{h}^0_i) = dim(\boldsymbol{h}^1_i) = dim(\boldsymbol{h}^2_i) = 64$.
@@
 
-We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical neighbor sampling and graph sampling techniques, respectively.
-For the neighbor sampler, we used the neighborhood sample sizes (25 for GNN Layer 1, and 10 for GNN Layer 0) and the default batch size (512) from \cite{hamilton2017_graphsage}.
+We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical sampling techniques respectively.
+For the neighbor sampler, we set the neighborhood sample sizes as 25 for GNN Layer 1, and 10 for GNN Layer 0 and set the default batch size as 512 from \cite{hamilton2017_graphsage}.
 For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to \cite{chiang2019_cluster_gcn}.
@@
 
-To find out the performance bottleneck in GNN training, we conduct the bottleneck analysis with four questions.
+To find out the performance bottleneck in GNN training, we conducted the experimental analysis with four questions.
 The answers to those questions will give us a more comprehensive view of the performance characteristics of GNN training.
-We design extensive experiments to find the answers empirically.
+
 \begin{itemize}
@@
 
-          Every GNN has a group of hyper-parameters like the number of GNN layers and the dimension of hidden feature vectors.
+          Every GNN has a group of hyper-parameters like the number of GNN layers and the dimensions of hidden feature vectors.
 The hyper-parameters affect the training time per epoch and the peak memory usage during the training.
@@
 
-          We can decompose the training time on different levels: layer level, vertex/edge computation level, and the basic operator level.
-          On each level, we breakdown the training time of an epoch into several stages. The most time-consuming stage is the performance bottleneck.
+          We can decompose the training time on different levels: layer level, edge/vertex calculation level, and the basic operator level.
+          On each level, we decomposed the training time of an epoch into several stages. The most time-consuming stage is the performance bottleneck.
           Optimizing its implementation can significantly reduce the training time.
@@
 
-          The limited memory capacity of a GPU card is the main factor preventing us from training GNNs on big graphs.
-          We measured the peak memory usage in the GNN training under different graph scales, input feature dimensions, and average vertex degrees.
-          Based on the results, we analyze which is the most memory-consuming component.
-          Reducing its memory usage will enable us to train bigger GNNs under the same memory capacity.
+          The limited memory capacity of a GPU is the main factor preventing us from training GNNs on big graphs.
+          We measured the peak memory usage of GNN training under different graph scales, input feature dimensions, and average vertex degrees.
+          Based on the results, we analyzed which is the most memory-consuming component in a GNN.
+          Reducing its memory usage will enable us to train GNNs on bigger graphs under the same memory capacity.
 
@@
 
-          In theory, the sampling techniques can significantly reduce the graph neurons that participate in the training of a batch.
+          Theoretically, the sampling techniques can significantly reduce the number of graph neurons that participate in the training of a batch.
           Consequently, the training time and the memory usage should also decrease.

### 2020-08-29 CCPE/Mauscript/wileyNJD-AMA.tex
update

@@
 
-\author[1]{Author One*}
-\author[2,3]{Author Two}
-\author[3]{Author Three}
+\author[1]{Zhaokang Wang*}
+\author[2,3]{Yunpan Wang, Chunfeng Yuan}
+\author[3]{Rong Gu, Yihua Huang}
 
@@
 
-\address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
-\address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
-\address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
+\address[1]{\orgdiv{Pasa Lab}, \orgname{Nanjing University}, \orgaddress{\state{JiangSu}, \country{China}}}
+\address[2]{\orgdiv{Pasa Lab}, \orgname{Nanjing University}, \orgaddress{\state{JiangSu}, \country{China}}}
+\address[3]{\orgdiv{Pasa Lab}, \orgname{Nanjing University}, \orgaddress{\state{JiangSu}, \country{China}}}
 
-\corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}
+\corres{*Rong Gu, *Yihua Huang. \email{\{gurong, yhuang\}@nju.edu.cn}}
 
-\presentaddress{This is sample for present address text this is sample for present address text}
+\presentaddress{No.163, Xianlin Road, Qixia District, Nanjing City, Jiangsu Province, China}
 
@@
 
-\section{Macros}
-
-This URL contains the LaTeX Class file for Software: Practice and Experience (SP\&E):
-\begin{verbatim}
-\url{https://onlinelibrary.wiley.com/page/journal/1097024x/homepage/la_tex_class_file.htm}
-\end{verbatim}
-Clicking on ``AMA-stix.zip'' downloads the file AMA-stix-1510051231000.zip from this URL:
-\begin{verbatim}
-\url{https://wol-prod-cdn.literatumonline.com/pb-assets/assets/1097024X/AMA-stix-1510051231000.zip}
-\end{verbatim}
-In file AMA-stix/ama/wileyNJD-AMA.tex, there is an example latex document for authors.
-I have edited this file to demonstrate problems with the latex macros in files WileyNJD-v2.cls and WileyNJD-AMA.bst, and used the following command to generate a PDF file.
-\begin{verbatim}
-pdflatex wileyNJD-AMA; bibtex wileyNJD-AMA; pdflatex wileyNJD-AMA; pdflatex wileyNJD-AMA;
-\end{verbatim}
-
-\section{First Problem}
-
-The header on this page is:
-\begin{quote}
-Received {\color{red}26 April 2016} | Revised {\color{red}6 June 2016} | Accepted {\color{red}6 June 2016}
-\end{quote}
-Authors do not know these dates, so they are likely to just leave the dates unchanged.
-It would be better to have a placeholder:
-\begin{quote}
-Received {\color{red}Added at production} | Revised {\color{red}Added at production} | Accepted {\color{red}Added at production}
-\end{quote}
-
-\section{Second Problem}
-
-SP\&E style use symbols for footnotes and numbers for bibliography citations.
-However, the latex macros generate numbers for footnotes rather than symbols number, which makes it impossible to tell the difference between a footnote and a citation.
-This is a footnote\footnote{Footnote} and this is a citation~\cite{book01}, and they both are numbered $^1$.
-Attempting to fix the problem by adding the following latex command results in an error.
-\begin{verbatim}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\end{verbatim}
-
-\section{Third Problem}\label{section}
-
-The ``ref'' macro used to print label for section, figures and tables leaves an extra space after the label number for figures and tables but not sections.
-Figure~\ref{figure} has an extra space after the number, as does Table~\ref{table}, but Section~\ref{section} does not have an extra space.
-
-\begin{figure}
-\centering
-I'm a figure above the caption
-\caption{This is the sample figure caption}
-\label{figure}
-\end{figure}
-
-\begin{table}
-\caption{This is the sample table caption}
-\label{table}
-\centering
-I'm a table below the caption
-\end{table}
-
-\section{Fourth Problem}
-
-There are multiple problems in the WileyNJD-AMA.bst macros for formatting bibliographic entries.
-Specifically, fields within entries are missing, as is space between fields, possibly in an attempt to shorten the length of the bibliographic entries.
-
-Here is an exhaustive list of all fields for all bibliography entries.
-\begin{quote}
-article~\cite{article01}, book~\cite{book01}, booklet~\cite{booklet01}, inbook~\cite{inbook01}, incollection~\cite{incollection01}, inproceedings~\cite{inproceedings01}, manual~\cite{manual01}, mastersthesis~\cite{mastersthesis01}, misc~\cite{misc01}, phdthesis~\cite{phdthesis01}, proceedings~\cite{proceedings01}, techreport~\cite{techreport01}, unpublished~\cite{unpublished01}
-\end{quote}
-Looking at the references below, there are multiple fields missing from the bibliographic entries, there are spaces before periods, and there are fields run together, etc.
-
 \input{sec1-introduction.tex}

### 2020-08-29 CCPE/Mauscript/wileyNJD-AMA.tex
更新CCPE版本的前言，同时重命名了FGCS.

@@
 
-\author[1]{Zhaokang Wang*}
-\author[2,3]{Yunpan Wang, Chunfeng Yuan}
-\author[3]{Rong Gu, Yihua Huang}
+\author[1]{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu*, Yihua Huang*}
 
-\authormark{AUTHOR ONE \textsc{et al}}
+\authormark{Wang \textsc{et al}}
 
-\address[1]{\orgdiv{Pasa Lab}, \orgname{Nanjing University}, \orgaddress{\state{JiangSu}, \country{China}}}
-\address[2]{\orgdiv{Pasa Lab}, \orgname{Nanjing University}, \orgaddress{\state{JiangSu}, \country{China}}}
-\address[3]{\orgdiv{Pasa Lab}, \orgname{Nanjing University}, \orgaddress{\state{JiangSu}, \country{China}}}
+\address{\orgdiv{State Key Laboratory for Novel Software Technology}, \orgdiv{Department of Computer Science and Technology}, \orgname{Nanjing University}, \orgaddress{\state{Jiangsu}, \country{China}}}
 
-\corres{*Rong Gu, *Yihua Huang. \email{\{gurong, yhuang\}@nju.edu.cn}}
+\corres{Rong Gu* and Yihua Huang* with equal contribution. \\ \email{\{gurong, yhuang\}@nju.edu.cn}}
 
-\presentaddress{No.163, Xianlin Road, Qixia District, Nanjing City, Jiangsu Province, China}
+\presentaddress{No.163 Xianlin Avenue,  Nanjing 210023, Jiangsu, China}
 

### 2020-08-29 FGCS/sec1-introduction.tex
更新CCPE版本的前言，同时重命名了FGCS.

--- 2020-08-29 CCPE/Mauscript/sec1-introduction.tex
@@
 \section{Introduction}
+
 In recent years, the graph neural network (GNN) becomes a hot research topic in the field of artificial intelligence.
-Many GNNs~\cite{kipf2017_gcn, defferrad2016_chebnet, li2018_agcn,li2015_ggnn, hamilton2017_graphsage, huang2018_gat, zhang2018_gaan} are proposed.
+Many GNNs \cite{kipf2017_gcn, defferrad2016_chebnet, li2018_agcn,li2015_ggnn, hamilton2017_graphsage, huang2018_gat, zhang2018_gaan} are proposed.
 They can learn the representation of vertices/edges in a graph from its topology and the original feature vectors in an \emph{end-to-end} manner.

### 2020-08-29 FGCS/sec6-related-work.tex
更新CCPE版本的前言，同时重命名了FGCS.

--- 2020-08-21 Manuscript/sec6-related-work.tex
@@
 \paragraph{Survey of GNNs}
-\cite{zhou2018_gnn_review,zhang2018_gnn_survey,comprehensive-survey-wu-2020} survey the existing graph neural network models and classify them from an algorithmic view.
-They summarize the parallels and differences between the architecture of different GNN models.
+Zhou et al.\cite{zhou2018_gnn_review}, Zhang et al.\cite{zhang2018_gnn_survey} and Wu et al.\cite{comprehensive-survey-wu-2020} survey the existing graph neural networks and classify them from an algorithmic view.
+They summarize the similarities and differences between the architectures of different GNNs.
 The typical applications of GNNs are also briefly introduced.
-Those surveys focus on comparing the existing GNNs theoretically not empirically.
+Those surveys focus on comparing the existing GNNs theoretically, not empirically.
 
 \paragraph{Evaluation of GNNs}
-Shchur et al. \cite{shchur2018_pitfall_of_gnn} evaluate the accuracy of popular GNN models on the node classification task.
+Shchur et al. \cite{shchur2018_pitfall_of_gnn} evaluate the accuracy of popular GNNs on the node classification task.
 Dwived et al. \cite{dwivedi2020_benchmark_of_gnn} further compare the accuracy of popular GNNs fairly in a controlled environment.
-Hu et al. \cite{hu2020_open_graph_benchmark} propose the open graph benchmark that provides a group of datasets and a standard evaluation workflow.
+Hu et al. \cite{hu2020_open_graph_benchmark} propose the open graph benchmark that provides a standard datasets and a standard evaluation workflow.
 The benchmark makes comparisons between GNNs easily and fairly.
@@
 From the efficiency aspect, Yan et al.
-\cite{yan2020_characterizing_gcn} compare the performance characteristics of graph convolutional networks, typical graph processing (like PageRank), and MLP-based neural network on GPU.
-They provide optimization guidelines for the software and the hardware sides.
-Zhang et al. \cite{zhang2020_analysis_neugraph} compare the architectural characteristics of the GNN inference on GPU under the unified SAGA-NN \cite{ma2019_neugraph} programming model.
-They find that GNN inference has no fixed performance bottleneck and all components deserve to optimize.
-These two efforts focus on the \emph{inference} phase of GNNs and they investigate the potential optimizations from an architectural view.
+\cite{yan2020_characterizing_gcn} compare the performance characteristics of graph convolutional networks, typical graph processing kernels(like PageRank), and the MLP-based neural networks on GPU.
+They provide optimization guidelines for both the software and the hardware developers.
+Zhang et al. \cite{zhang2020_analysis_neugraph} analyze the architectural characteristics of the GNN inference on GPU under SAGA-NN \cite{ma2019_neugraph} model.
+They find that the GNN inference has no fixed performance bottleneck and all components deserve to optimize.
+These two efforts focus on the \emph{inference} phase of GNNs and they investigate the potential optimizations mainly from an architectural view.
 In this work, our target is to find out the performance bottleneck in the training phase from a system view.

### 2020-08-29 CCPE/template/ama/wileyNJD-AMA.tex
update

\documentclass[AMA,STIX1COL]{WileyNJD-v2}
\usepackage{lineno,hyperref}
\usepackage{amsmath, amsthm}
\usepackage{relsize}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{lscape}
\usepackage{xcolor}
\usepackage{subfig}
\usepackage{float}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\articletype{Article Type}%

\received{}
\revised{}
\accepted{}

\raggedbottom

\begin{document}

\title{This is the sample article title}

\author[1]{Author One*}
\author[2,3]{Author Two}
\author[3]{Author Three}

\authormark{AUTHOR ONE \textsc{et al}}

\address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
\address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
\address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}

\presentaddress{This is sample for present address text this is sample for present address text}

\abstract[Summary]{The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks.
Recently, various graph neural network libraries have emerged.
They make the development of GNNs convenient, but their performance on large datasets is not satisfying.
In this work, we analyze the performance bottleneck in training GNN with GPUs empirically.
A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation.
We breakdown their training time and memory usage, evaluate the effects of hyper-parameters, and assess the efficiency of the sampling techniques.  
The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training time and memory usage.
Future optimization can focus on it. 
The sampling techniques are essential for training big graphs on GPU, but their current implementations still have room for improvement.}

\keywords{graph neural network, performance bottleneck analysis, empirical evaluation, machine learning system, GPU}

\maketitle

\section{Macros}

This URL contains the LaTeX Class file for Software: Practice and Experience (SP\&E):
\begin{verbatim}
\url{https://onlinelibrary.wiley.com/page/journal/1097024x/homepage/la_tex_class_file.htm}
\end{verbatim}
Clicking on ``AMA-stix.zip'' downloads the file AMA-stix-1510051231000.zip from this URL:
\begin{verbatim}
\url{https://wol-prod-cdn.literatumonline.com/pb-assets/assets/1097024X/AMA-stix-1510051231000.zip}
\end{verbatim}
In file AMA-stix/ama/wileyNJD-AMA.tex, there is an example latex document for authors.
I have edited this file to demonstrate problems with the latex macros in files WileyNJD-v2.cls and WileyNJD-AMA.bst, and used the following command to generate a PDF file.
\begin{verbatim}
pdflatex wileyNJD-AMA; bibtex wileyNJD-AMA; pdflatex wileyNJD-AMA; pdflatex wileyNJD-AMA;
\end{verbatim}

\section{First Problem}

The header on this page is:
\begin{quote}
Received {\color{red}26 April 2016} | Revised {\color{red}6 June 2016} | Accepted {\color{red}6 June 2016}
\end{quote}
Authors do not know these dates, so they are likely to just leave the dates unchanged.
It would be better to have a placeholder:
\begin{quote}
Received {\color{red}Added at production} | Revised {\color{red}Added at production} | Accepted {\color{red}Added at production}
\end{quote}

\section{Second Problem}

SP\&E style use symbols for footnotes and numbers for bibliography citations.
However, the latex macros generate numbers for footnotes rather than symbols number, which makes it impossible to tell the difference between a footnote and a citation.
This is a footnote\footnote{Footnote} and this is a citation~\cite{book01}, and they both are numbered $^1$.
Attempting to fix the problem by adding the following latex command results in an error.
\begin{verbatim}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\end{verbatim}

\section{Third Problem}\label{section}

The ``ref'' macro used to print label for section, figures and tables leaves an extra space after the label number for figures and tables but not sections.
Figure~\ref{figure} has an extra space after the number, as does Table~\ref{table}, but Section~\ref{section} does not have an extra space.

\begin{figure}
\centering
I'm a figure above the caption
\caption{This is the sample figure caption}
\label{figure}
\end{figure}

\begin{table}
\caption{This is the sample table caption}
\label{table}
\centering
I'm a table below the caption
\end{table}

\section{Fourth Problem}

There are multiple problems in the WileyNJD-AMA.bst macros for formatting bibliographic entries.
Specifically, fields within entries are missing, as is space between fields, possibly in an attempt to shorten the length of the bibliographic entries.

Here is an exhaustive list of all fields for all bibliography entries.
\begin{quote}
article~\cite{article01}, book~\cite{book01}, booklet~\cite{booklet01}, inbook~\cite{inbook01}, incollection~\cite{incollection01}, inproceedings~\cite{inproceedings01}, manual~\cite{manual01}, mastersthesis~\cite{mastersthesis01}, misc~\cite{misc01}, phdthesis~\cite{phdthesis01}, proceedings~\cite{proceedings01}, techreport~\cite{techreport01}, unpublished~\cite{unpublished01}
\end{quote}
Looking at the references below, there are multiple fields missing from the bibliographic entries, there are spaces before periods, and there are fields run together, etc.

\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
\bibliography{wileyNJD-AMA}%

\end{document}

### 2020-08-29 CCPE/Mauscript/sec2-review-of-graph-neural-network.tex
更新草稿的排版.

@@
     \centering
-    \subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4.1cm]{figs/illustration/layer_sampling.pdf}}
+    \subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4.5cm]{figs/illustration/layer_sampling.pdf}}
     %
-    \subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4.1cm]{figs/illustration/graph_sampling.pdf}}
+    \subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4.5cm]{figs/illustration/graph_sampling.pdf}}
     \caption{Training a GNN with sampling techniques. The faded graph neurons and their connections are inactivated.}

### 2020-08-30 CCPE/Mauscript/wileyNJD-AMA.tex
update
更新草稿的排版.

@@
 \usepackage{lineno,hyperref}
+\hypersetup{colorlinks=true,citecolor=blue}
 \usepackage{amsmath, amsthm}
@@
 
-\title{This is the sample article title}
+\title{Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs}
 
@@
 \abstract[Summary]{The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks. 
-Recently, various graph neural network libraries have emerged.
-They make the development of GNNs convenient, but their performance on large datasets is not satisfying.
+Recently, various graph neural network libraries have emerged.They make the development of GNNs convenient, but their performance on large datasets is not satisfying. 
 In this work, we analyze the performance bottleneck in training GNN with GPUs empirically. 
@@
 The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training time and memory usage.
-Future optimization can focus on it. 
-The sampling techniques are essential for training big graphs on GPU, but their current implementations still have room for improvement.}
+Future optimization can focus on it. The sampling techniques are essential for training big graphs on GPUs, but their current implementations still have room for improvement.}
 

### 2020-08-30 CCPE/Mauscript/sec1-introduction.tex
update

@@
 Yan et al. \cite{yan2020_characterizing_gcn} and Zhang et al. \cite{zhang2020_analysis_neugraph} experimentally analyze the architectural characteristics of the GNN \emph{inference}.
-They find that the GNN inference is more cache-friendly than the traditional graph analysis tasks(like PageRank) and is suitable for GPU.
+They find that the GNN inference is more cache-friendly than the traditional graph analysis tasks(like PageRank) and is suitable for GPUs.
 They verify the effectiveness of the kernel fusion optimization in reducing the time of inference.
@@
 
-We implement them with PyG and evaluate their efficiency with six real-world datasets on GPU.
+We implement them with PyG and evaluate their efficiency with six real-world datasets on a GPU.
 We identify the most time-consuming stage in the GNN training by decomposing the training time per epoch from the layer level to the operator level.
-We also analyze the memory usage during the training to discover the main factor that limits the data scalability of GNN training on GPU. 
+We also analyze the memory usage during the training to discover the main factor that limits the data scalability of GNN training on GPUs. 
 Finally, we evaluate whether or not the sampling techniques affect the performance bottleneck. 

### 2020-08-30 CCPE/Mauscript/sec4-experiments.tex
update

--- 2020-08-26 Manuscript/sec4-experiments.tex
@@
 
-The functions $\phi$, $\Sigma$ and $\gamma$ in the vertex and edge calculation are made up of a series of basic operators implemented on GPU, like the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
+The functions $\phi$, $\Sigma$ and $\gamma$ in the vertex and edge calculation are made up of a series of basic operators implemented on the GPU, like the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
 \figurename~\ref{fig:exp_top_basic_ops} shows the five most time-consuming basic operators in each GNN, averaged over all the real-world graphs in \tablename~\ref{tab:dataset_overview}.
@@
 
-In general, the most time-consuming operator in the four GNNs, is still the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul}, \emph{making GNN training suitable for GPU}.
+In general, the most time-consuming operator in the four GNNs, is still the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul}, \emph{making GNN training suitable for GPUs}.
 Although the aggregation step in the edge calculation stage is relatively simple (like sum and mean), the related operators \texttt{scatter\_add} and \texttt{gather} still consume a certain amount of the time.
@@
 \paragraph{Summary}
-The GNN training is suitable for GPU.
+The GNN training is suitable for GPUs.
 \textbf{The edge calculation stage is the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
@@
 
-During the GNN training, all data (including datasets and intermediate results) are stored in the on-chip memory of GPU.
+During the GNN training, all data (including datasets and intermediate results) are stored in the on-chip memory of the GPU.
 Compared with the main memory on the host side, the capacity of the GPU memory is very limited.
@@
 Each batch is a small subgraph of the dataset.
-To train on each batch, PyG sends the sampled subgraph to GPU, calculates the gradients on the subgraph, and updates the model parameters directly on GPU.
+To train on each batch, PyG sends the sampled subgraph to the GPU, calculates the gradients on the subgraph, and updates the model parameters directly on GPU.
 With the sampling techniques, the model parameters are updated by a stochastic gradient descent optimizer.
@@
 
-To find out the performance bottleneck with the sampling techniques, we decompose the training time per batch into three phases: \emph{sampling} on CPU, \emph{transferring} sampled subgraphs from CPU to GPU and \emph{training} with the subgraphs on GPU.
+To find out the performance bottleneck with the sampling techniques, we decompose the training time per batch into three phases: \emph{sampling} on the CPU, \emph{transferring} sampled subgraphs from the CPU to the GPU and \emph{training} with the subgraphs on GPU.
 \figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.

### 2020-08-30 CCPE/Mauscript/sec6-related-work.tex
update

--- 2020-08-29 FGCS/sec6-related-work.tex
@@
 From the efficiency aspect, Yan et al.
-\cite{yan2020_characterizing_gcn} compare the performance characteristics of graph convolutional networks, typical graph processing kernels(like PageRank), and the MLP-based neural networks on GPU.
+\cite{yan2020_characterizing_gcn} compare the performance characteristics of graph convolutional networks, typical graph processing kernels(like PageRank), and the MLP-based neural networks on GPUs.
 They provide optimization guidelines for both the software and the hardware developers.
-Zhang et al. \cite{zhang2020_analysis_neugraph} analyze the architectural characteristics of the GNN inference on GPU under SAGA-NN \cite{ma2019_neugraph} model.
+Zhang et al. \cite{zhang2020_analysis_neugraph} analyze the architectural characteristics of the GNN inference on GPUs under SAGA-NN \cite{ma2019_neugraph} model.
 They find that the GNN inference has no fixed performance bottleneck and all components deserve to optimize.

### 2020-08-30 CCPE/Mauscript/sec3-experiment-design.tex
update

@@
 We stored the dataset and the model parameters on the GPU side.
-All the training was conducted on GPU.
+All the training was conducted on the GPU.
 
@@
 The hyper-parameters affect the training time per epoch and the peak memory usage during the training.
-          To evaluate their effects, we measured how the training time per epoch and the peak memory usage (of GPU) changed as we increased the values of the hyper-parameters.
+          To evaluate their effects, we measured how the training time per epoch and the peak memory usage (of the GPU) changed as we increased the values of the hyper-parameters.
           Through the experiments, we want to verify the validity of the computational complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.

### 2020-08-30 CCPE/Mauscript/sec4-experiments.tex
update

@@
 Each batch is a small subgraph of the dataset.
-To train on each batch, PyG sends the sampled subgraph to the GPU, calculates the gradients on the subgraph, and updates the model parameters directly on GPU.
+To train on each batch, PyG sends the sampled subgraph to the GPU, calculates the gradients on the subgraph, and updates the model parameters directly on the GPU.
 With the sampling techniques, the model parameters are updated by a stochastic gradient descent optimizer.
@@
 
-To find out the performance bottleneck with the sampling techniques, we decompose the training time per batch into three phases: \emph{sampling} on the CPU, \emph{transferring} sampled subgraphs from the CPU to the GPU and \emph{training} with the subgraphs on GPU.
+To find out the performance bottleneck with the sampling techniques, we decompose the training time per batch into three phases: \emph{sampling} on the CPU, \emph{transferring} sampled subgraphs from the CPU to the GPU and \emph{training} with the subgraphs on the GPU.
 \figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.

### 2020-09-07 CCPE/Mauscript/sec3-experiment-design.tex
update

@@
 For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, $dim(\boldsymbol{h}^1_i)=64$, and $dim(\boldsymbol{h}^2_i)=\#Classes$.
-For GAT, we set the hyper-parameters according to \cite{huang2018_gat}.
+For GAT, we set the hyper-parameters according to its paper\cite{huang2018_gat}.
 The first GAT layer had 8 heads with the dimension of each head $d^0_{head}=8$. The first GAT layer merged the heads by concatenating.
@@
 We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical sampling techniques respectively.
-For the neighbor sampler, we set the neighborhood sample sizes as 25 for GNN Layer 1, and 10 for GNN Layer 0 and set the default batch size as 512 from \cite{hamilton2017_graphsage}.
-For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to \cite{chiang2019_cluster_gcn}.
+For the neighbor sampler, we set the neighborhood sample sizes as 25 for GNN Layer 1, and 10 for GNN Layer 0 and set the default batch size as 512 from its paper\cite{hamilton2017_graphsage}.
+For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to the parameters used in its paper\cite{chiang2019_cluster_gcn}.
 

### 2020-09-07 NEUROC/matrials/2.OSP_Latex/OSP_Latex_template.tex
update

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

\journal{Name of journal}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Title/Name of your software}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{A. Author}

\address{Your institute, some address}

\begin{abstract}
%% Text of abstract 
Ca. 100 words

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
keyword 1 \sep keyword 2 \sep keyword 3

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\linenumbers

%% main text

Description of your software in maximum 5 pages for first Original Software Publication –- see suggested format;

\section{Introduction}
\label{}

Introduce the motivation of developing the software, and explain why it is important.

\section{Problems and Background}
\label{}

Give the formulations of problems to be solved by the software/toolbox.

Introduce the background and related work in literature (cite or list algorithms used, other software etc.).

\section{Software Framework }
\label{}

\subsection{Software Architecture}
\label{}

Give a short overview of the overall software architecture.

\subsection{Software Functionalities}
\label{}

Present the major functionalities of the software.

\subsection{Sample code snippets analysis (optional)}
\label{}

\section{Implementation and Empirical Results}
\label{}

Implementation details.

Empirical results.

Conduct empirical studies and provide results.

Compare with state-of-the-art software if any, kindly cite relevant work.

\section{Illustrative Examples}
\label{}

Provide at least one illustrative example to demonstrate the major functions.

Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel. (Please upload any video as a single supplementary file with your article. Only one MP4 formatted, with 50MB maximum size, video is possible per article. Recommended video dimensions are 640 $\times$ 480 at a maximum of 30 frames/second. Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$. This tool will display your video exactly in the same way as it will appear on ScienceDirect.).

\section{Conclusions}
\label{}

Set out the conclusion of this original software publication.

\section*{Acknowledgements}
\label{}

Optionally thank people and institutes you need to acknowledge.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References: At least 5 are required 
%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

\bibitem{}

\end{thebibliography}

\clearpage
\section*{Required Metadata}
\label{}

\section*{Current executable software version}
\label{}

Ancillary data table required for sub version of the executable software: (x.1, x.2 etc.) kindly replace examples in right column with the correct information about your executables, and leave the left column as it is.

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{(executable) Software metadata description} & \textbf{Please fill in this column} \\
\hline
S1 & Current software version & for example 1.1, 2.4 etc. \\
\hline
S2 & Permanent link to executables of this version  & example: $https://github.com/combogenomics/$ $DuctApe/releases/tag/DuctApe-0.16.4$ \\
\hline
S3 & Legal Software License & List one of the approved licenses \\
\hline
S4 & Computing platform/Operating System & for example Android, BSD, iOS, Linux, OS X, Microsoft Windows, Unix-like , IBM z/OS, distributed/web based etc. \\
\hline
S5 & Installation requirements \& dependencies & \\
\hline
S6 & If available, link to user manual - if formally published include a reference to the publication in the reference list & Example: $http://mozart.github.io/documentation/$ \\
\hline
S7 & Support email for questions & \\
\hline
\end{tabular}
\caption{Software metadata (optional)}
\label{} 
\end{table}

\section*{Current code version}
\label{}

Ancillary data table required for subversion of the codebase. Kindly replace examples in right column with the correct information about your current code, and leave the left column as it is.

\begin{table}[!h]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version & For example v42 \\
\hline
C2 & Permanent link to code/repository used of this code version & For example: $https://github.com/mozart/mozart2$ \\
\hline
C3 & Legal Code License   & List one of the approved licenses \\
\hline
C4 & Code versioning system used & For example svn, git, mercurial, etc. put none if none \\
\hline
C5 & Software code languages, tools, and services used & For example c++, python, r,  etc. \\
\hline
C6 & Compilation requirements, operating environments \& dependencies & \\
\hline
C7 & If available Link to developer documentation/manual & For example: $http://mozart.github.io/documentation/$ \\
\hline
C8 & Support email for questions & \\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

\end{document}
\endinput
%%
%% End of file `OSP_Latex_template.tex'.

### 2020-09-08 NEUROC/ms.tex
neuroc_final

--- 2020-08-26 Manuscript/ms.tex
@@
 
-	\title{Empirical Analysis of the Performance Bottleneck in Graph Neural Network Training}
+	\title{Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs}
     \author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu$^*$ \corref{correspondingauthor1}, Yihua Huang$^*$ \corref{correspondingauthor2}}
@@
 		The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks. 
-		Recently, various graph neural network libraries have emerged.
-		They make the development of GNNs convenient, but their performance on large datasets is not satisfying.
+		Recently, various graph neural network libraries have emerged.They make the development of GNNs convenient, but their performance on large datasets is not satisfying. 
 		In this work, we analyze the performance bottleneck in training GNN with GPUs empirically. 
@@
 		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training time and memory usage.
-		Future optimization can focus on it. 
-		The sampling techniques are essential for training big graphs on GPU, but their current implementations still have room for improvement.
+		Future optimization can focus on it. The sampling techniques are essential for training big graphs on GPUs, but their current implementations still have room for improvement.
 	\end{abstract}
@@
 
+\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
 \bibliography{gnnref.bib}

### 2020-09-08 NEUROC/sec4-experiments.tex
neuroc_final

--- 2020-08-30 CCPE/Mauscript/sec4-experiments.tex
@@
 The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} is valid.
-Fixing other hyper-parameters, each hyper-parameter, itself affects the training time and the memory usage of a GNN Layer \textbf{in a linear way}.
+Fixing other hyper-parameters, each hyper-parameter itself affects the training time and the memory usage of a GNN Layer \textbf{in a linear way}.
 Algorithm engineers can adjust hyper-parameters according to the time complexity to avoid explosive growth in the training time and memory usage.
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_gcn.pdf}}
-    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_gat.pdf}}
-    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_layer_time_proportion_gaan.pdf}}
+    \subfloat[GCN]{\includegraphics[height=4.6cm]{figs/experiments/exp_layer_time_proportion_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=4.6cm]{figs/experiments/exp_layer_time_proportion_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=4.6cm]{figs/experiments/exp_layer_time_proportion_gat.pdf}}
+    \subfloat[GaAN]{\includegraphics[height=4.6cm]{figs/experiments/exp_layer_time_proportion_gaan.pdf}}
     \caption{Training time breakdown on the layer level.

### 2020-09-09 FGCS/sec4-experiments.tex
update

--- 2020-08-26 Manuscript/sec4-experiments.tex
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.pdf}}
-    \subfloat[GGNN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
-    \subfloat[GaAN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.pdf}}
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.pdf}}
     \caption{Effects of hyper-parameters on the peak GPU memory usage during the training, excluding the memory used by the dataset and the model parameters.}

### 2020-10-13 CCPE/template/Documents/wileyNJD-Doc.tex
增加了Motivation各个数据集的代码

\documentclass[AMA,LATO1COL]{WileyNJD-v2}
\usepackage{moreverb}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\articletype{Article Type}%

\received{<day> <Month>, <year>}
\revised{<day> <Month>, <year>}
\accepted{<day> <Month>, <year>}

%\raggedbottom

\begin{document}

\title{A demonstration of the \LaTeX\ class file for Wiley NJD Journals\protect\thanks{This is an example for title footnote.}}

\author[1]{Author One*}

\author[2,3]{Author Two}

\author[3]{Author Three}

\authormark{AUTHOR ONE \textsc{et al}}

\address[1]{\orgdiv{Org Division}, \orgname{Org name}, \orgaddress{\state{State name}, \country{Country name}}}

\address[2]{\orgdiv{Org Division}, \orgname{Org name}, \orgaddress{\state{State name}, \country{Country name}}}

\address[3]{\orgdiv{Org Division}, \orgname{Org name}, \orgaddress{\state{State name}, \country{Country name}}}

\corres{*Corresponding author name, Corresponding address. \email{authorone@Email.com}}

\presentaddress{Present address}

\abstract[Abstract]{This paper describes the use of the \LaTeXe\ \textsf{WileyNJD-v2.cls}
class file for setting papers for \emph{Mathematical Methods in the Applied Sciences}.}

\keywords{Class file; \LaTeXe; \emph{Wiley NJD}}

\jnlcitation{\cname{%
\author{Williams K.}, 
\author{B. Hoskins}, 
\author{R. Lee}, 
\author{G. Masato}, and 
\author{T. Woollings}} (\cyear{2016}), 
\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}

\maketitle

\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

\section{Introduction}\label{sec1}

Many authors submitting \( \sin \cos \tan \inf_{x} \) to NJD journals use \LaTeXe\ to
prepare their papers. This paper describes the
\textsf{WileyNJD-v2.cls} class file which can be used to convert
articles produced with other \LaTeXe\ class files into the correct
form for publication in \emph{Wiley NJD Journals}.

The \textsf{WileyNJD-v2.cls} class file preserves much of the standard
\LaTeXe\ interface so that any document which was produced using
the standard \LaTeXe\ \textsf{article} style can easily be
converted to work with the \textsf{WileyNJD-v2} style. However, the
width of text and typesize will vary from that of
\textsf{article.cls}; therefore, \emph{line breaks will change}
and it is likely that displayed mathematics and tabular material
will need re-setting.

In the following sections we describe how to lay out your code to
use \textsf{WileyNJD-v2.cls} to reproduce the typographical look of
\emph{Wiley NJD Journals}.

\subsection{Procedure to install fonts}

\begin{enumerate}
\item All font files are available under the Lato-fonts folder 
\item Font installer is available under the same folder Windows-Lato-fontinstaller.exe
\item Execute (double click the EXE file) the EXE file that will install all fonts/map files to your local drive.
\end{enumerate}

\subsection{The Three Golden Rules}

Before we proceed, we would like to
stress \emph{three golden rules} that need to be followed to
enable the most efficient use of your code at the typesetting
stage:
\begin{enumerate}
\item[(i)] keep your own macros to an absolute minimum;

\item[(ii)] as \TeX\ is designed to make sensible spacing
decisions by itself, do \emph{not} use explicit horizontal or
vertical spacing commands, except in a few accepted (mostly
mathematical) situations, such as \verb"\," before a
differential~d, or \verb"\quad" to separate an equation from its
qualifier;

\item[(iii)] follow the \emph{NJD} reference style.
\begin{enumerate}[a.]
\item Chemistry --- Use the ``AMA'' option as \verb"\documentclass[AMA]{WileyNJD-v2.cls}"

\end{enumerate}
\end{enumerate}

\section{Getting Started} The \textsf{WileyNJD-v2.cls} class file should run
on any standard \LaTeXe\ installation. If any of the fonts, class
files or packages it requires are missing from your installation,
they can be found on the \emph{\TeX\ Live} CD-ROMs or from CTAN.

LaTeX document class options

\begin{flushleft}
\begin{enumerate}[a.]
\item LATO1COL--- For LATO font large one column layout use the ``LATO1COL'' option as \verb"\documentclass[AMA,LATO1COL]{WileyNJD-v2}"
\item LATO2COL--- For LATO font large two column layout use the ``LATO2COL'' option as \verb"\documentclass[AMA,LATO2COL]{WileyNJD-v2}"
\item LATOSMALL--- For LATO font small layout use the ``LATOSMALL'' option as \verb"\documentclass[AMA,LATOSMALL]{WileyNJD-v2}"
\end{enumerate}
\end{flushleft}

\section{The Article Header Information}
The heading for any file using \textsf{WileyNJD-v2.cls} is shown in
Figure~\ref{F1}.

\subsection{Remarks}

\begin{enumerate}[(I).]

\item Use \verb"\title{<title> \protect\thanks{<title footnotes}}" for article title and title footnote.
\item Use \verb"\authormark{}" for running heads.

\item Note the use of \verb"\author[<link>]{<name>}" and \verb"\address[<link>]{<name>}" to
link names and addresses. The author for correspondence is marked
by ``*'' and \verb"\corres{}" is used to give that
author's address, which will be printed besides abstract, prefaced by
`Correspondence to:'.

\item For submitting a double-spaced manuscript, add
\verb"doublespace" as an option to the documentclass line. \verb"\documentclass[doublespace]{WileyNJD-v2}"

\item Use \verb"\presentaddress{}" for present address.

\item In abstract \verb"\abstract[<title>]{abstract paragraph}" use optional parameter for title followed by abstract paragraph.

\item For Key words use \verb"\keywords{}".

\item For how to site use \verb"\jnlcitation{\cname{\author{<author name>},"

\verb"\ctitle{<title>}, \cjournal{<Journal name>}, \cvol{<vol>}.}}".

\item For title page abbreviations use \verb"\footnotetext{<\textbf{Abbreviation title:} Abreviations>}"

\item Use \verb"\articletype{<article category}" for article header information

\item Use \verb"\received{<received date>} \revised{<revised date>} \accepted{<accepted date>}" for history dates.

\end{enumerate}

\begin{figure}[p]
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}

\documentclass[AMA,LATO1COL]{WileyNJD-v2}

\articletype{Article Type}%

\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}

\begin{document}

\title{<Initial cap, lower case>\protect\thanks{<title footnote.>}}

\author[<address link>]{<Author name><corresponding author*>}

\author[<address link>,<address link>]{Author Name}

\authormark{AUTHOR ONE \textsc{et al}}

\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>}, 
\orgaddress{\state{<State name>}, \country{<Country name>}}}
\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>},
 \orgaddress{\state{<State name>}, \country{<Country name>}}}

\corres{<corresponding author link*> <author name, address.
 \email{<authorone@email.com>}}

\presentaddress{<Present address>}

\abstract[<Abstract heading>]{<Abstract paragraph>}

\keywords{<keyword1>, <keyword2>,...}

\jnlcitation{\cname{%
\author{<aurhor name>}, 
\author{<aurhor name>}, 
\author{<aurhor name>}, 
\author{<aurhor name>},  and 
\author{<aurhor name>}} (\cyear{<year>}), 
\ctitle{<journal title>}, \cjournal{<journal name>} <year> <vol> Page <xxx>-<xxx>}

\footnotetext{\textbf{<abbreviation head:>} <abbreviations> ..}

\maketitle

\section{Introduction}
.
.
.
\end{boxedverbatim}
\end{center}
\caption{Example for title page.\label{F1}}
\end{figure}

\section{The Body of the Article}

\subsection{Section headings}

\begin{enumerate}[(H1)]
\item Section --- use \verb"\section{}"
\item SubSection--- use \verb"\subsection{}"
\item SubSubSectioin--- use \verb"\subsubsection{}"
\item Paragraph--- use \verb"\paragraph{}"
\item Subparagraph--- use \verb"\subparagraph{}"
\end{enumerate}

\subsection{Mathematics} \textsf{WileyNJD-v2.cls} makes the full
functionality of \AmS\/\TeX\ available. We encourage the use of
the \verb"align", \verb"gather" and \verb"multline" environments
for displayed mathematics.

\subsection{Figures and Tables}

\textsf{WileyNJD-v2.cls} uses the
\textsf{graphicx} package for handling figures.

Figures are called in as follows:
\begin{verbatim}
\begin{figure}
\centering
\includegraphics{<figure name>}
\caption{<Figure caption>}
\end{figure}
\end{verbatim}

The standard coding for a table is shown in Figure~\ref{F2}.

\begin{figure}[h]
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}
\begin{table}
\caption{<Table caption>}
\centering
\begin{tabular}{<table alignment>}
\toprule
<column headings>\\
\midrule
<table entries
(separated by & as usual)>\\
<table entries>\\
.
.
.\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Source: xxx.
\item[1] xxx.
\item[2] xxx.
\end{tablenotes}
\end{table}
\end{boxedverbatim}
\end{center}
\caption{Example for table layout.\label{F2}}
\end{figure}

\subsection{Cross-referencing}
The use of the \LaTeX\ cross-reference system
for figures, tables, equations, etc., is encouraged
(using \verb"\ref{<name>}" and \verb"\label{<name>}").

\subsection{Box text}

\begin{verbatim}
\begin{boxtext}
\section*{<title>}%
Paragraph
\end{boxtext}
\end{verbatim}

\subsection{List items}

\subsubsection{Enumerate list styles}
\begin{verbatim}
\begin{enumerate}[1]
\item 
\end{enumerate}

\begin{enumerate}[1.]
\item 
\end{enumerate}

\begin{enumerate}[(1)]
\item 
\end{enumerate}

\begin{enumerate}[I]
\item 
\end{enumerate}

\begin{enumerate}[i]
\item 
\end{enumerate}

\begin{enumerate}[a]
\item 
\end{enumerate}

\end{verbatim}

\subsubsection{Bullet list styles}

\begin{verbatim}
\begin{itemize}
\item 
\end{itemize}
\end{verbatim}

\subsubsection{Description list}

\begin{verbatim}
\begin{description}
\item[<entry>] description text.
\end{description}
\end{verbatim}

\subsection{Enunciations}

\begin{verbatim}
\begin{theorem}[<Theorem subhead>]\label{thm1}
<theorem text>. 
\end{theorem}

\begin{proposition}[<proposition subhead>]\label{pro1}
<proposition text>. 
\end{proposition}

\begin{definition}[<definition subhead>]\label{dfn1}
<definition text>. 
\end{definition}

\begin{proof}
<proof text>. 
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm1}]
<proof text>.
\end{proof}

\end{verbatim}

\subsection{Program codes}

Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math. Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math. Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated. Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.  All other code environments are set with normal text font. Refer below example:

\begin{verbatim}
\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
for i:=maxint to 0 do
begin
{ do nothing }
end;
Write('Case insensitive ');
WritE('Pascal keywords.');
\end{lstlisting}
\end{verbatim}

\subsection{Acknowledgements} An Acknowledgements section is started with \verb"\ack" or
\verb"\acks" for \textit{Acknowledgement} or
\textit{Acknowledgements}, respectively. It must be placed just
before the References.

\subsection{Bibliography}

\begin{enumerate}[1]
\item Use \verb"\bibliography{wileyNJD-AMA}" BST file for AMA reference style
\item Use \verb"\bibliography{wileyNJD-APA}" BST file for APA reference style
\item Use \verb"\bibliography{wileyNJD-AMS}" BST file for AMS reference style
\item Use \verb"\bibliography{wileyNJD-VANCOUVER}" BST file for Vancouver reference style
\item Use \verb"\bibliography{wileyNJD-ACS}" BST file for Chemistry reference style
\end{enumerate}

The normal commands for producing the reference list are:

\begin{verbatim}
\begin{thebibliography}{99}
\bibitem{<x-ref label>}
         <Reference details>
.
.
.
\end{thebibliography}
\end{verbatim}

\subsection{Appendix Section}

\begin{verbatim}
\appendix

\section{Section title of first appendix\label{app1}}
.
.
.

\end{verbatim}

\end{document}

### 2020-10-13 Technical-report/sample-technique-motivation/code/ogbl-citation/cluster_gcn.py

@@ -1,0 +1,241 @@
+import argparse
+
+import torch
+import numpy as np
+import torch.nn.functional as F
+from torch.utils.data import DataLoader
+
+from torch_sparse import SparseTensor
+from torch_geometric.data import ClusterData, ClusterLoader
+from torch_geometric.nn import GCNConv
+from torch_geometric.utils import to_undirected
+
+from ogb.linkproppred import PygLinkPropPredDataset, Evaluator
+
+from logger import Logger
+
+
+class GCN(torch.nn.Module):
+    def __init__(self, in_channels, hidden_channels, out_channels, num_layers,
+                 dropout):
+        super(GCN, self).__init__()
+
+        self.convs = torch.nn.ModuleList()
+        self.convs.append(GCNConv(in_channels, hidden_channels))
+        for _ in range(num_layers - 2):
+            self.convs.append(GCNConv(hidden_channels, hidden_channels))
+        self.convs.append(GCNConv(hidden_channels, out_channels))
+
+        self.dropout = dropout
+
+    def reset_parameters(self):
+        for conv in self.convs:
+            conv.reset_parameters()
+
+    def forward(self, x, edge_index):
+        for conv in self.convs[:-1]:
+            x = conv(x, edge_index)
+            x = F.relu(x)
+            x = F.dropout(x, p=self.dropout, training=self.training)
+        x = self.convs[-1](x, edge_index)
+        return x
+
+
+class GCNInference(torch.nn.Module):
+    def __init__(self, weights):
+        super(GCNInference, self).__init__()
+        self.weights = weights
+
+    def forward(self, x, adj):
+        for i, (weight, bias) in enumerate(self.weights):
+            x = adj @ x @ weight + bias
+            x = np.clip(x, 0, None) if i < len(self.weights) - 1 else x
+        return x
+
+
+class LinkPredictor(torch.nn.Module):
+    def __init__(self, in_channels, hidden_channels, out_channels, num_layers,
+                 dropout):
+        super(LinkPredictor, self).__init__()
+
+        self.lins = torch.nn.ModuleList()
+        self.lins.append(torch.nn.Linear(in_channels, hidden_channels))
+        for _ in range(num_layers - 2):
+            self.lins.append(torch.nn.Linear(hidden_channels, hidden_channels))
+        self.lins.append(torch.nn.Linear(hidden_channels, out_channels))
+
+        self.dropout = dropout
+
[…]

### 2020-10-13 Technical-report/sample-technique-motivation/code/ogbl-citation/gcn.py

@@ -1,0 +1,262 @@
+import argparse
+
+import torch
+from torch.nn import Parameter
+import torch.nn.functional as F
+from torch.utils.data import DataLoader
+
+import torch_geometric.transforms as T
+from torch_geometric.nn import GCNConv, SAGEConv
+
+from ogb.linkproppred import PygLinkPropPredDataset, Evaluator
+
+from logger import Logger
+
+
+class GCN(torch.nn.Module):
+    def __init__(self, in_channels, hidden_channels, out_channels, num_layers,
+                 dropout):
+        super(GCN, self).__init__()
+
+        self.convs = torch.nn.ModuleList()
+        self.convs.append(
+            GCNConv(in_channels, hidden_channels, normalize=False))
+        for _ in range(num_layers - 2):
+            self.convs.append(
+                GCNConv(hidden_channels, hidden_channels, normalize=False))
+        self.convs.append(
+            GCNConv(hidden_channels, out_channels, normalize=False))
+
+        self.dropout = dropout
+
+    def reset_parameters(self):
+        for conv in self.convs:
+            conv.reset_parameters()
+
+    def forward(self, x, adj_t):
+        for conv in self.convs[:-1]:
+            x = conv(x, adj_t)
+            x = F.relu(x)
+            x = F.dropout(x, p=self.dropout, training=self.training)
+        x = self.convs[-1](x, adj_t)
+        return x
+
+
+class SAGE(torch.nn.Module):
+    def __init__(self, in_channels, hidden_channels, out_channels, num_layers,
+                 dropout):
+        super(SAGE, self).__init__()
+
+        self.convs = torch.nn.ModuleList()
+        self.convs.append(SAGEConv(in_channels, hidden_channels))
+        for _ in range(num_layers - 2):
+            self.convs.append(SAGEConv(hidden_channels, hidden_channels))
+        self.convs.append(SAGEConv(hidden_channels, out_channels))
+
+        self.dropout = dropout
+
+    def reset_parameters(self):
+        for conv in self.convs:
+            conv.reset_parameters()
+
+    def forward(self, x, adj_t):
+        for conv in self.convs[:-1]:
+            x = conv(x, adj_t)
+            x = F.relu(x)
+            x = F.dropout(x, p=self.dropout, training=self.training)
+        x = self.convs[-1](x, adj_t)
+        return x
+
+
+class LinkPredictor(torch.nn.Module):
[…]

### 2020-10-13 Technical-report/sample-technique-motivation/code/ogbl-citation/graph_saint.py

@@ -1,0 +1,241 @@
+import argparse
+
+import torch
+import numpy as np
+import torch.nn.functional as F
+from torch.utils.data import DataLoader
+
+from torch_sparse import SparseTensor
+from torch_geometric.data import GraphSAINTRandomWalkSampler
+from torch_geometric.nn import GCNConv
+from torch_geometric.utils import to_undirected
+
+from ogb.linkproppred import PygLinkPropPredDataset, Evaluator
+
+from logger import Logger
+
+
+class GCN(torch.nn.Module):
+    def __init__(self, in_channels, hidden_channels, out_channels, num_layers,
+                 dropout):
+        super(GCN, self).__init__()
+
+        self.convs = torch.nn.ModuleList()
+        self.convs.append(GCNConv(in_channels, hidden_channels))
+        for _ in range(num_layers - 2):
+            self.convs.append(GCNConv(hidden_channels, hidden_channels))
+        self.convs.append(GCNConv(hidden_channels, out_channels))
+
+        self.dropout = dropout
+
+    def reset_parameters(self):
+        for conv in self.convs:
+            conv.reset_parameters()
+
+    def forward(self, x, edge_index):
+        for conv in self.convs[:-1]:
+            x = conv(x, edge_index)
+            x = F.relu(x)
+            x = F.dropout(x, p=self.dropout, training=self.training)
+        x = self.convs[-1](x, edge_index)
+        return x
+
+
+class GCNInference(torch.nn.Module):
+    def __init__(self, weights):
+        super(GCNInference, self).__init__()
+        self.weights = weights
+
+    def forward(self, x, adj):
+        for i, (weight, bias) in enumerate(self.weights):
+            x = adj @ x @ weight + bias
+            x = np.clip(x, 0, None) if i < len(self.weights) - 1 else x
+        return x
+
+
+class LinkPredictor(torch.nn.Module):
+    def __init__(self, in_channels, hidden_channels, out_channels, num_layers,
+                 dropout):
+        super(LinkPredictor, self).__init__()
+
+        self.lins = torch.nn.ModuleList()
+        self.lins.append(torch.nn.Linear(in_channels, hidden_channels))
+        for _ in range(num_layers - 2):
+            self.lins.append(torch.nn.Linear(hidden_channels, hidden_channels))
+        self.lins.append(torch.nn.Linear(hidden_channels, out_channels))
+
+        self.dropout = dropout
+
[…]

### 2020-10-13 Technical-report/sample-technique-motivation/code/ogbn-products/graphsage.py

@@ -1,0 +1,129 @@
+import argparse
+
+import torch
+import torch.nn.functional as F
+
+import torch_geometric.transforms as T
+from torch_geometric.nn import SAGEConv
+
+from ogb.nodeproppred import PygNodePropPredDataset, Evaluator
+
+from logger import Logger
+
+
+class SAGE(torch.nn.Module):
+    def __init__(self, in_channels, hidden_channels, out_channels, num_layers,
+                 dropout):
+        super(SAGE, self).__init__()
+
+        self.convs = torch.nn.ModuleList()
+        self.convs.append(SAGEConv(in_channels, hidden_channels))
+        for _ in range(num_layers - 2):
+            self.convs.append(SAGEConv(hidden_channels, hidden_channels))
+        self.convs.append(SAGEConv(hidden_channels, out_channels))
+
+        self.dropout = dropout
+
+    def reset_parameters(self):
+        for conv in self.convs:
+            conv.reset_parameters()
+
+    def forward(self, x, adj_t):
+        for conv in self.convs[:-1]:
+            x = conv(x, adj_t)
+            x = F.relu(x)
+            x = F.dropout(x, p=self.dropout, training=self.training)
+        x = self.convs[-1](x, adj_t)
+        return torch.log_softmax(x, dim=-1)
+
+
+def train(model, data, train_idx, optimizer):
+    model.train()
+
+    optimizer.zero_grad()
+    out = model(data.x, data.adj_t)[train_idx]
+    loss = F.nll_loss(out, data.y.squeeze(1)[train_idx])
+    loss.backward()
+    optimizer.step()
+
+    return loss.item()
+
+
+@torch.no_grad()
+def test(model, data, split_idx, evaluator):
+    model.eval()
+
+    out = model(data.x, data.adj_t)
+    y_pred = out.argmax(dim=-1, keepdim=True)
+
+    train_acc = evaluator.eval({
+        'y_true': data.y[split_idx['train']],
+        'y_pred': y_pred[split_idx['train']],
+    })['acc']
+    valid_acc = evaluator.eval({
+        'y_true': data.y[split_idx['valid']],
+        'y_pred': y_pred[split_idx['valid']],
+    })['acc']
+    test_acc = evaluator.eval({
+        'y_true': data.y[split_idx['test']],
+        'y_pred': y_pred[split_idx['test']],
+    })['acc']
+
+    return train_acc, valid_acc, test_acc
+
+
+def main():
[…]

### 2020-10-13 Technical-report/sample-technique-motivation/code/ogbn-products/neigbor_sampling.py
增加了执行计划和测试

@@ -9,8 +9,8 @@ from ogb.nodeproppred import PygNodePropPredDataset, Evaluator
 from torch_geometric.data import NeighborSampler
 from torch_geometric.nn import SAGEConv
 
-root = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'data', 'products')
-dataset = PygNodePropPredDataset('ogbn-products', root)
+# root = osp.join(osp.dirname(osp.realpath(__file__)), '..', 'data', 'products')
+dataset = PygNodePropPredDataset('ogbn-products')
 split_idx = dataset.get_idx_split()
 evaluator = Evaluator(name='ogbn-products')
 data = dataset[0]

### 2020-10-13 Technical-report/sample-technique-motivation/code/run_base.sh

@@ -1,0 +1,46 @@
+base_path="/home/wangzhaokang/wangyunpan/pyg-gnns/Technical-report/sample-technique-motivation/code"
+
+cd "${base_path}/ogbn-products"
+echo "ogbn-products test..."
+echo "cluster_gcn test..."
+date
+python cluster_gcn.py 1>>run_base.log 2>&1
+date
+echo "graph_saint test..."
+date
+python graph_saint.py 1>>run_base.log 2>&1
+date
+echo "neighbor_sampling test..."
+date
+python neighbor_sampling.py 1>>run_base.log 2>&1
+date
+
+cd "${base_path}/ogbn-mag"
+echo "ogbn-mag test..."
+echo "cluster_gcn test..."
+date
+python cluster_gcn.py 1>>run_base.log 2>&1
+date
+echo "graph_saint test..."
+date
+python graph_saint.py 1>>run_base.log 2>&1
+date
+echo "neighbor_sampling test..."
+date
+python neighbor_sampling.py 1>>run_base.log 2>&1
+date
+echo "rgcn test..."
+date
+python neighbor_sampling.py 1>>run_base.log 2>&1
+date
+
+cd "${base_path}/ogbl-citation"
+echo "ogbn-citation test..."
+echo "cluster_gcn test..."
+date
+python cluster_gcn.py 1>>run_base.log 2>&1
+date
+echo "graph_saint test..."
+date
+python graph_saint.py 1>>run_base.log 2>&1
+date

### 2020-12-14 ggnn/layers.py
完成了大部分的代码开发

@@ -114,7 +114,7 @@ class GatedGraphConv(MessagePassing):
         device = torch.device(self.device if self.gpu else 'cpu')
         flag = self.infer_flag
         
-        sampling_time, to_time, train_time, cat_time = 0.0, 0.0, 0.0, 0.0
+        sampling_time, to_time, train_time = 0.0, 0.0, 0.0
         total_batches = len(subgraph_loader)
         
         for i in range(self.num_layers):
@@ -149,13 +149,14 @@ class GatedGraphConv(MessagePassing):
                     train_time += time.time() - et2
                 except StopIteration:
                     break
-            
-            t0 = time.time()
             x_all = torch.cat(xs, dim=0)
-            cat_time += time.time() - t0
 
+        sampling_time /= total_batches
+        to_time /= total_batches
+        train_time /= total_batches
+        
         log_memory(flag, device, 'inference end') 
-        print(f"Evaluation: batches: {total_batches}, sampling time: {sampling_time}, to_time: {to_time}, train_time: {train_time}, cat_time: {cat_time}")
+        print(f"avg_batch_train_time: {train_time}, avg_batch_sampling_time:{sampling_time}, avg_batch_to_time: {to_time}")
         return x_all
     
     

### 2020-12-14 paper_exp5_paras_acc/convergence_validation.py

@@ -1,0 +1,218 @@
+import os, re, sys
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+plt.style.use("ggplot")
+plt.rcParams["font.size"] = 12
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+models = ["gcn", "ggnn", "gat", "gaan"]
+datasets = ["amazon-photo", "pubmed", "amazon-computers", "coauthor-physics", "flickr"]
+gcn_ggnn_hds = ["1", "2", "4", "8", "16", "32", "64", "128", "256", "512", "1024", "2048"]
+gat_hds = ["1", "2", "4", "8", "16", "32", "64", "128", "256"]
+gat_heads = ["1", "2", "4", "8", "16"]
+gaan_hds = ["1", "2", "4", "8", "16", "32", "64", "128", "256", "512", "1024", "2048"]
+gaan_ds = ["1", "2", "4", "8", "16", "32", "64", "128", "256"]
+gaan_heads = ["1", "2", "4", "8", "16"]
+
+os.chdir("early_stopping1")
+for model in models:
+    for data in datasets:
+        if not os.path.exists(f"acc_fig/{model}/{data}"):
+            os.makedirs(f"acc_fig/{model}/{data}")
+        print(model, data)
+        if model in ["gcn", "ggnn"]:
+            dir_config = "dir_gcn_ggnn_acc"
+            for hd in gcn_ggnn_hds:
+                file_name = f"{dir_config}/config0_{model}_{data}_{hd}.log"
+                if not os.path.exists(file_name):
+                    continue   
+                print(file_name)
+                train_acc, val_acc, test_acc = [], [], []
+                acc = None
+                cnt = 0
+                with open(file_name) as f:
+                    for line in f:
+                        match_line = re.match(r"Epoch: .*, Train: (.*), Val: (.*), Test: (.*)", line)
+                        match_final_line = re.match("   Final Test: (.*) ± .*", line)
+                        if match_line and cnt < 1000:
+                            train_acc.append(float(match_line.group(1)))
+                            val_acc.append(float(match_line.group(2)))
+                            test_acc.append(float(match_line.group(3)))
+                            cnt += 1
+                        if match_final_line:
+                            acc = int(float(match_final_line.group(1)) * 100) / 10000
+                print("Final Test", acc)
+                fig, ax = plt.subplots()
+                x = range(len(train_acc))
[…]

### 2020-12-14 paper_exp5_paras_acc/handle_paras_acc.py

@@ -1,0 +1,278 @@
+import os, re, sys
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+plt.style.use("ggplot")
+plt.rcParams["font.size"] = 12
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+datasets = ["amazon-photo", "pubmed", "amazon-computers", "coauthor-physics", "flickr", "com-amazon"]
+datasets_map = ['amp', 'pub', 'amc', 'cph', 'fli', 'cam']
+
+models = ["gcn", "ggnn", "gat", "gaan"]
+gcn_ggnn_hds = ["1", "2", "4", "8", "16", "32", "64", "128", "256", "512", "1024", "2048"]
+gat_hds = ["1", "2", "4", "8", "16", "32", "64", "128", "256"]
+gat_heads = ["1", "2", "4", "8", "16"]
+gaan_hds = ["1", "2", "4", "8", "16", "32", "64", "128", "256", "512", "1024", "2048"]
+gaan_ds = ["1", "2", "4", "8", "16", "32", "64", "128", "256"]
+gaan_heads = ["1", "2", "4", "8", "16"]
+
+def save_acc_to_csv(dir_work="early_stopping2"): # 将统计得到的acc结果保存在csv文件中 
+    os.chdir(dir_work)
+    if not os.path.exists("acc_res"):
+        os.makedirs("acc_res")
+    for model in models:
+        if model == "gcn" or model == "ggnn":
+            dir_config = "dir_gcn_ggnn_acc"
+            # hds
+            df_hds = {}
+            for data in datasets:
+                df_hds[data] = []
+                for hd in gcn_ggnn_hds:
+                    file_name = f"{dir_config}/config0_{model}_{data}_{hd}.log"
+                    if not os.path.exists(file_name):
+                        df_hds[data].append(None)
+                        continue
+                    print(file_name)
+                    acc = None                    
+                    with open(file_name) as f:
+                        for line in f:
+                            match_line = re.match("   Final Test: (.*) ± .*", line)
+                            if match_line:
+                                acc = int(float(match_line.group(1)) * 100) / 10000
+                                break
+                    df_hds[data].append(acc)
+            df = pd.DataFrame(df_hds, index=gcn_ggnn_hds)
+            df.columns = datasets_map
+            df.to_csv(f"acc_res/{model}_hds.csv")
+        elif model == "gat":
+            dir_config = "dir_gat_acc"
+            # hds
+            df_hds = {}
[…]

### 2020-12-14 paper_exp6_sampling_acc/batch_acc_cum_cluster_fix_batch.sh

@@ -1,0 +1,7 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_batch.py --epochs 10000 --mode cluster --model gaan --data coauthor-physics --device cuda:0 --batch_partitions 15 --heads 4 --d_v 32 --d_a 32 --d_m 32 --hidden_dims 1 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp4_relative_sampling/batch_acc_cum_fix_batch/cluster_gaan_coauthor-physics_15.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_batch.py --epochs 10000 --mode cluster --model gaan --data coauthor-physics --device cuda:0 --batch_partitions 45 --heads 4 --d_v 32 --d_a 32 --d_m 32 --hidden_dims 1 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp4_relative_sampling/batch_acc_cum_fix_batch/cluster_gaan_coauthor-physics_45.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_batch.py --epochs 10000 --mode cluster --model gaan --data coauthor-physics --device cuda:0 --batch_partitions 90 --heads 4 --d_v 32 --d_a 32 --d_m 32 --hidden_dims 1 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp4_relative_sampling/batch_acc_cum_fix_batch/cluster_gaan_coauthor-physics_90.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_batch.py --epochs 10000 --mode cluster --model gaan --data coauthor-physics --device cuda:0 --batch_partitions 150 --heads 4 --d_v 32 --d_a 32 --d_m 32 --hidden_dims 1 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp4_relative_sampling/batch_acc_cum_fix_batch/cluster_gaan_coauthor-physics_150.log 2>&1
[…]

### 2020-12-14 paper_exp6_sampling_acc/batch_acc_cum_cluster_fix_time.sh

@@ -1,0 +1,82 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode cluster --model gcn --data amazon-computers --device cuda:0 --batch_partitions 150 --hidden_dims 256 --fix_time 1400 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/batch_acc_cum_fix_time/cluster_gcn_amazon-computers_150.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode cluster --model gcn --data amazon-computers --device cuda:0 --batch_partitions 375 --hidden_dims 256 --fix_time 1400 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/batch_acc_cum_fix_time/cluster_gcn_amazon-computers_375.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode cluster --model gcn --data coauthor-physics --device cuda:0 --batch_partitions 15 --hidden_dims 128 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/batch_acc_cum_fix_time/cluster_gcn_coauthor-physics_15.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode cluster --model gcn --data coauthor-physics --device cuda:0 --batch_partitions 45 --hidden_dims 128 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/batch_acc_cum_fix_time/cluster_gcn_coauthor-physics_45.log 2>&1
[…]

### 2020-12-14 paper_exp6_sampling_acc/convergence_validation.py

@@ -1,0 +1,98 @@
+import os, re, sys
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+plt.style.use("ggplot")
+plt.rcParams["font.size"] = 12
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+datasets = ["amazon-photo", "pubmed", "amazon-computers", "coauthor-physics", "flickr"]
+models = ["gcn", "ggnn", "gat", "gaan"]
+modes = ["cluster", "graphsage"]
+
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625],
+    'com-amazon': [3349, 10046, 20092, 33487, 83716, 167432]
+}
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+    'com-amazon': 'cam'
+}
+
+xticklabels = ['1%', '3%', '6%', '10%', '25%', '50%', 'FULL']
+
+dir_in = "batch_acc_cum_fix_time"
+
+for data in datasets:
+    for model in models:
+        if not os.path.exists(f"acc_fig/{model}/{data}"):
+            os.makedirs(f"acc_fig/{model}/{data}")
+        for mode in modes:
+            print(data, model, mode)
+            # 将数据存储到csv文件
+            if mode == "cluster":
+                for i, cs in enumerate(cluster_batchs):
+                    file_path = os.path.join(dir_in, '_'.join([mode, model, data, str(cs)]) + ".log")
+                    if not os.path.exists(file_path):
+                        continue
+                    print(file_path)
+                    train_acc, val_acc = [], []
+                    # 读取日志文件，获取bs_times, bs_accs: dims=100
+                    with open(file_path) as f:
+                        for line in f:
+                            match_line = re.match(r"Batch: .*, train_acc: (.*), val_acc: (.*), best_val_acc:.*", line)
+                            if match_line:
[…]

### 2020-12-14 paper_exp6_sampling_acc/sampling_batch_acc_cum_fix_epoch.py

@@ -1,0 +1,73 @@
+"""
+sampling_batch_acc_cum:
+采样的对比实验代码
+"""
+import os
+import time
+import numpy as np
+import pandas as pd
+
+config_paras = pd.read_csv("/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp5_paras_acc/early_stopping2/acc_res/max_acc.csv", index_col=0)
+
+small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr']
+algs = ['gcn', 'ggnn', 'gat', 'gaan']
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+    'com-amazon': 'cam'
+}
+
+dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "batch_acc_cum_fix_epoch")
+if not os.path.exists(dir_path):
+    os.makedirs(dir_path)
+
+for i, mode in enumerate(['cluster', 'graphsage']):
+    sh_commands = []
+    for alg in algs:
+        for data in small_datasets:
+            paras = str(config_paras.loc[datasets_maps[data], alg]).split('_')
+            if alg in ["gcn", "ggnn"]:
+                config_str = f"--hidden_dims {paras[0]}"
+            elif alg == "gat":
+                config_str = f"--heads {paras[0]} --head_dims {paras[1]}"
+            elif alg == "gaan":
+                config_str = f"--heads {paras[0]} --d_v {paras[1]} --d_a {paras[1]} --d_m {paras[1]} --hidden_dims {paras[2]}"
+            if mode == 'cluster':
[…]

### 2020-12-14 paper_exp6_sampling_acc/sampling_batch_acc_cum_fix_time.py

@@ -1,0 +1,80 @@
+"""
+sampling_batch_acc_cum_fix_time:
+采样的对比实验代码
+"""
+import os
+import time
+import numpy as np
+import pandas as pd
+
+config_paras = pd.read_csv("/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp5_paras_acc/early_stopping2/acc_res/max_acc.csv", index_col=0)
+
+small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr']
+algs = ['gcn', 'ggnn', 'gat', 'gaan']
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+    'com-amazon': 'cam'
+}
+
+fix_times = {
+    'pubmed': 1000,
+    'coauthor-physics': 1000,
+    'flickr': 1750,
+    'amazon-photo': 1000,
+    'amazon-computers': 1400
+}
+
+dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "batch_acc_cum_fix_time")
+if not os.path.exists(dir_path):
+    os.makedirs(dir_path)
+
+for i, mode in enumerate(['cluster', 'graphsage']):
+    sh_commands = []
+    for alg in algs:
+        for data in small_datasets:
+            paras = str(config_paras.loc[datasets_maps[data], alg]).split('_')
+            if alg in ["gcn", "ggnn"]:
+                config_str = f"--hidden_dims {paras[0]}"
+            elif alg == "gat":
+                config_str = f"--heads {paras[0]} --head_dims {paras[1]}"
+            elif alg == "gaan":
+                config_str = f"--heads {paras[0]} --d_v {paras[1]} --d_a {paras[1]} --d_m {paras[1]} --hidden_dims {paras[2]}"
+            if mode == 'cluster':
[…]

### 2020-12-14 paper_exp7_inference_sampling/inference_sampling_graphsage_memory.sh

@@ -1,0 +1,133 @@
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --mode graphsage --model ggnn --data amazon-photo --epochs 20 --batch_size 3825 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/graphsage_ggnn_amazon-photo_3825.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --mode graphsage --model gat --data amazon-photo --epochs 20 --batch_size 77 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/graphsage_gat_amazon-photo_77.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --mode graphsage --model gat --data amazon-photo --epochs 20 --batch_size 230 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/graphsage_gat_amazon-photo_230.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --mode graphsage --model gat --data amazon-photo --epochs 20 --batch_size 459 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/graphsage_gat_amazon-photo_459.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --mode graphsage --model gat --data amazon-photo --epochs 20 --batch_size 765 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/graphsage_gat_amazon-photo_765.json
[…]

### 2020-12-14 paper_exp7_inference_sampling/inference_sampling_time.py

@@ -1,0 +1,47 @@
+import os
+import time
+
+small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr', 'com-amazon']
+
+algs = ['gcn', 'ggnn', 'gat', 'gaan']
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625],
+    'com-amazon': [3349, 10046, 20092, 33487, 83716, 167432]
+}
+
+dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "inference_sampling_time")
+if not os.path.exists(dir_path):
+    os.makedirs(dir_path)
+
+for i, mode in enumerate(['cluster', 'graphsage']):
+    sh_commands = []
+    for data in small_datasets:
+        for alg in algs:
+            if mode == 'cluster':
+                cmd = "python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:{} --mode {} --model {} --data {} --epochs 20 --batch_partitions {} >{} 2>&1"
+                for cs in cluster_batchs:
+                    file_path = os.path.join(dir_path, '_'.join([mode, alg, data, str(cs)]) + '.log')
+                    if os.path.exists(file_path):
+                        continue
+                    print(file_path)
+                    sh_commands.append(cmd.format(str(i), mode, alg, data, str(cs), file_path))
+                    print(time.strftime('%Y-%m-%d %H:%M:%S', time.localtime(time.time())))
+            else:
+                cmd = "python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:{} --mode {} --model {} --data {} --epochs 20 --batch_size {} >{} 2>&1"
+                for gs in graphsage_batchs[data]:
+                    file_path = os.path.join(dir_path, '_'.join([mode, alg, data, str(gs)]) + '.log')
+                    if os.path.exists(file_path):
+                        continue
+                    print(file_path)
[…]

### 2020-12-14 paper_exp8_inference_full/feat_dims_memory.sh

@@ -1,0 +1,30 @@
+#!/usr/bin/env bash
+dir_config="dir_feat_dims_json"
+
+if [ ! -d ${dir_config} ]
+then
+    mkdir -p $dir_config
+fi
+
+
+# datasets=(amazon-photo pubmed amazon-computers coauthor-physics flickr com-amazon)
+datasets=(com-amazon)
+models=(gcn ggnn gat gaan)
+fds=(16 32 64 128 256 512)
+
+for model in ${models[@]}
+do
+    for data in ${datasets[@]}
+    do
+        for fd in ${fds[@]}
+        do
+            json_path="${dir_config}/config0_${model}_${data}_${fd}.json"
+            if [ -f $json_path ]; then # 断点续传
+                continue
+            fi
+            val="configuration=0, model=${model}, dataset=${data}, dense_feat_dims=${fd}"
+            echo ${val}
+            python -u ../main_inference_memory.py --dataset "${data}_${fd}" --model ${model} --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_${fd}.json"
+        done
+    done
+done

### 2020-12-15 NEUROC/Response-MajRev/response_letter.tex
回复R1Q2.

% LaTeX rebuttal letter example. 
% 
% Copyright 2019 Friedemann Zenke, fzenke.net
%
% Based on examples by Dirk Eddelbuettel, Fran and others from 
% https://tex.stackexchange.com/questions/2317/latex-style-or-macro-for-detailed-response-to-referee-report
% 
% Licensed under cc by-sa 3.0 with attribution required.

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lipsum} % to generate some filler text
\usepackage{fullpage}
\usepackage{times}

% import Eq and Section references from the main manuscript where needed
% \usepackage{xr}
% \externaldocument{manuscript}

% package needed for optional arguments
\usepackage{xifthen}
% define counters for reviewers and their points
\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}

% This refines the format of how the reviewer/point reference will appear.
\renewcommand{\thepoint}{P\,\thereviewer.\arabic{point}}

% command declarations for reviewer points and our responses
\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
                  \section*{Reviewer \thereviewer}}

\newenvironment{point}
   {\refstepcounter{point} \bigskip \noindent {\textbf{Reviewer~Point~\thepoint} } ---\ \begin{sf}}
   {\end{sf} \par}

\newcommand{\shortpoint}[1]{\refstepcounter{point}  \bigskip \noindent 
	{\textbf{Reviewer~Point~\thepoint} } ---\begin{sf} ~#1 \end{sf}\par}

\newenvironment{reply}
   {\medskip \noindent \textbf{Reply}:\  }
   {\medskip}

\newcommand{\shortreply}[2][]{\medskip \noindent \textbf{Reply}:\  #2
	\ifthenelse{\equal{#1}{}}{}{ \hfill \footnotesize (#1)}%
	\medskip}

\begin{document}

\section*{Response to the reviewers}
% General intro text goes here
We thank the reviewers for their critical assessment of our work. 
In the following we address their concerns point by point.

% Let's start point-by-point with Reviewer 1
\reviewersection

% Point one description 
\begin{point}
	There are lots of symbols in this paper. Some symbols are reused and confusing, such as s denotes sub-layers or edge features.
\end{point}

% Our reply
\begin{reply}
	TODO
\end{reply}

\begin{point}
    Some typical applications of GNNs should be included, such as video object segmentation [ref1], human-object interaction [ref2] and human-parsing [ref3].[1] Zero-shot video object segmentation via attentive graph neural networks,iccv 2019 [2] Learning human-object interactions by graph parsing neural networks, eccv 2018. [3] Hierarchical human parsing with typed part-relation reasoning, cvpr 2020.
\end{point}

\begin{reply}
	Thank you for pointing out our shortcomings. Computer vision is indeed another important application area of graph neural networks. We have added the mentioned references in the INTRODUCTION section in the revised manuscript. We quote the related sentence below:
    \begin{quote}
         The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks [8, 9, 10] (like node classification and link prediction) but also computer vision tasks (like human-object interaction [11], human parsing [12], and video object segmentation [13]).

    \end{quote}
\end{reply}

\subsection*{Minor}

% Use the short-hand macros for one-liners.
\shortpoint{ Typo in line xy. }
\shortreply{ Fixed.}

% Begin a new reviewer section
\reviewersection

\begin{point}
	This is the first point of Reviewer \thereviewer. With some more words foo
	bar foo bar ...
\end{point}

\begin{reply}
	Our reply to it with reference to one of our points above using the \LaTeX's 
	label/ref system (see also \ref{pt:foo}).
\end{reply}

\end{document}

### 2020-12-15 NEUROC/sec1-introduction.tex
增加了Motivation各个数据集的代码
回复R1Q2.

--- 2020-08-30 CCPE/Mauscript/sec1-introduction.tex
@@
 \section{Introduction}
+
 In recent years, the graph neural network (GNN) becomes a hot research topic in the field of artificial intelligence.
@@
 They can learn the representation of vertices/edges in a graph from its topology and the original feature vectors in an \emph{end-to-end} manner.
-The powerful expression ability of GNNs makes them achieve good accuracy in many graph analysis tasks \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020}, like node classification, link prediction, and graph classification.
+The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020} (like node classification and link prediction) but also computer vision tasks (like human-object interaction \cite{qi2018_learning_humanobject}, human parsing \cite{wang2020_hierarchical_human_parsing}, and video object segmentation \cite{wang2019_zeroshot_video}).
 

### 2020-12-16 NEUROC/Response-MajRev/response_letter.tex
更新R1P1

@@
+% !TEX program=pdflatex
 % LaTeX rebuttal letter example. 
@@
 
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{times}
+\usepackage{amsmath, amsthm}
 
@@
 \begin{reply}
-	TODO
+    We apologize for the confusing use of symbols.
+    %
+    To clarify the symbol usage, we have checked the full text of the manuscript and unified the usage of symbols.
+    %
+    We have avoided the problem of repeated use of symbols, so that each symbol only represents one meaning after the revision.
+    %
+    We summarize the frequently-used symbols in Table 1 in the revised manuscript.
+    %
+    We quote the table below:
+    %%%%% TODO, Paste Table 1 %%%%.
+
+    In the revised manuscript, $\boldsymbol{e}_{i,j}$ represents the input feature vector of the edge $e_{i,j}$.
+    %
+    It is the same for all GNN layers.
+    %
+    $\boldsymbol{s}$ represents aggregated vectors outputted by the aggregation function $\Sigma$ in graph neurons.
+    %
+    $\boldsymbol{s}^l_i$ represents the aggregated vector of the graph neuron corresponding to the vertex $v_i$ in the GNN layer $l$.
+    %
+    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,k}_i$ represents the aggregated vector corresponding to $v_i$ in the $k$-th sub-layer.
+
+    To clarify the concept of sub-layers in a GNN layer, we have added the following description in Section 2.2 ``Graph Neuron and Message-passing Model'' in the revised manuscript:
+    %%%%% TODO %%%%%%%%
+
 \end{reply}

### 2020-12-16 NEUROC/sec2-review-of-graph-neural-network.tex
update
增加了Motivation各个数据集的代码
更新R1P1

--- 2020-08-29 CCPE/Mauscript/sec2-review-of-graph-neural-network.tex
@@
+% !TEX root=ms.tex
 \section{Review of Graph Neural Networks}
@@
 In this section, we formally define the graph neural networks and briefly survey typical graph neural networks.
-We denote a simple graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
-Let $n=|\mathcal{V}|$ and $m=|\mathcal{E}|$ as the number of vertices/edges.
-We use $v_i$ $(0 \leq i < n)$ to denote a vertex and $e_{i,j}=(v_i, v_j)$ to denote the edge pointing from $v_i$ to $v_j$.
+We denote a simple \emph{undirected} graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
+%Let $n=|\mathcal{V}|$ and $m=|\mathcal{E}|$ as the number of vertices/edges.
+We use $v_i$ $(0 \leq i < |\mathcal{V}|)$ to denote a vertex and $e_{i,j}=(v_i, v_j)$ to denote the edge pointing from $v_i$ to $v_j$.
 The adjacency set of $v_i$ is $\mathcal{N}(v_i)=\{v|(v_i, v) \in \mathcal{E}\}$.
 We denote a \emph{vector} with a bold lower case letter like $\boldsymbol{x}$ and a \emph{matri}x with a bold upper case letter like $\boldsymbol{X}$.
+Table~\ref{tab:notations} summarizes the common symbols used throughout this work.
+
+\begin{table}[h]
+    \caption{Notations}
+    \label{tab:notations}
+    \centering
+    \small
+    \begin{tabular}{p{3em}lp{35em}}
+        \toprule
+       Category & Symbol & Meaning \\
+        \midrule
+        \multirow[c]{4}{3em}{Graph Structure}& $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ & The simple undirected input graph with the vertex set $\mathcal{V}$ and the edge set $\mathcal{E}$. \\
+        & $v_i$ & The $i$-th vertex of the input graph. \\
+        & $e_{i,j}$ & The edge pointing from $v_i$ to $v_j$ of the input graph. \\
+        & $\mathcal{N}(v_i)$ & The adjacency set of $v_i$ in the input graph. \\ \midrule
+        \multirow[c]{6}{3em}{GNN Definition}& $L$ & The number of GNN layers. \\
+        & $\phi^l$ & The messaging function of the GNN layer $l$. \\
+        & $\Sigma^l$ & The aggregation function of the GNN layer $l$. \\
+        & $\gamma^l$ & The vertex updating function of the GNN layer $l$. \\ 
+        & $\phi^{l,k}$/$\Sigma^{l,k}$/$\gamma^{l,k}$ & The messaging/aggregation/updating function of the $k$-th sub-layer of the GNN layer  $l$.\\
+        & $\textcolor{blue}{\boldsymbol{W}^l, \boldsymbol{W}^{(k)}/\boldsymbol{b}, \boldsymbol{a}}$ & The matrices/vectors represented by the blue characters are the weight matrices/vectors that need to be learned in the GNN.
+\\  \midrule
+        \multirow[c]{8}{3em}{Vectors}& $\boldsymbol{v}_i$ & The input feature vector of the vertex $v_i$. \\
+        & $\boldsymbol{e}_{i,j}$ & The input feature vector of the edge $e_{i,j}$.  \\
+        & $\boldsymbol{h}_i^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_i$ in the GNN layer $l$. \\
+        & $\boldsymbol{h}_i^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_i$ in the GNN layer $l$.\\
+        & $\boldsymbol{m}_{i,j}^l$ & The message vector of the edge $e_{i,j}$ outputted by $\phi^l$ of the GNN layer $l$. \\
+        & $\boldsymbol{s}_{i}^l$ & The aggregated vector of the vertex $v_i$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
+        & $\boldsymbol{m}_{i,j}^{l,k}$/$\boldsymbol{s}_{i}^{l,k}$ & The message/aggregated vector of the vertex $v_i$ outputted by $\phi^{l,k}$/$\Sigma^{l,k}$ of the $k$-th sub-layer of the GNN layer $l$.
+\\
+        & $d_{in}$, $d_{out}$ &  The dimensions of the input/output hidden vectors of a graph neuron. \\
+        \bottomrule
+
+    \end{tabular}
+\end{table}
 
@@
     \includegraphics[width=0.5\columnwidth]{figs/illustration/GNN_Unit.pdf}
-    \caption{Graph neuron of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}(b).
+    \caption{Graph neuron of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}b.
 $\phi$/$\Sigma$/$\gamma$ are the messaging/aggregation/vertex updating functions in the message-passing model, respecitvely.}
@@
 \begin{table}
-    \centering
+    \hspace{-5em}
     \begin{footnotesize}

### 2020-12-16 exp_graphsage_hop.py
update

@@ -1,0 +1,82 @@
+import sys
+import time
+import os
+import numpy as np
+import os.path as osp
+import matplotlib.pyplot as plt
+
+from torch_geometric.data import NeighborSampler
+from utils import small_datasets, get_dataset, get_split_by_file
+
+plt.style.use("ggplot")
+plt.rcParams["font.size"] = 12
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+dir_out = "/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/exp_graphsage_hop"
+file_out = "exp_inference_sampling_degrees_distribution_"
+colors = plt.get_cmap('Dark2')(np.linspace(0.15, 0.85, 5))
+markers = 'oD^sdp'
+
+def helper(edge_index, degrees):
+    d_v = {}
+    for e in edge_index.T.numpy():
+        # 统计入度
+        if e[0] not in d_v.keys():
+            d_v[e[0]] = 1
+        else:
+            d_v[e[0]] += 1
+        # 统计出度
+        if e[1] not in d_v.keys():
+            d_v[e[1]] = 1
+        else:
+            d_v[e[1]] += 1
+    
+    for k in d_v.keys():
+        if d_v[k] not in degrees.keys():
+            degrees[d_v[k]] = 1
+        else:
+            degrees[d_v[k]] += 1
+    return degrees
+    
+for data_name in small_datasets:
+    data = get_dataset(data_name, normalize_features=True)[0]
+
+    # add train, val, test split
+    if data_name in ['amazon-computers', 'amazon-photo', 'coauthor-physics']:
+        file_path = osp.join('/home/wangzhaokang/wangyunpan/gnns-project/datasets', data_name + "/raw/role.json")
+        data.train_mask, data.val_mask, data.test_mask = get_split_by_file(file_path, data.num_nodes)
+    
+    subgraph_loader = NeighborSampler(data.edge_index, sizes=[-1] * 5, batch_size=1024,
+                                    shuffle=False, num_workers=40)
+    
+    total_batches = len(subgraph_loader)
+    total_degrees = {}
+    for i in range(5):
+        total_degrees[i] = {}
+        
+    for batch in subgraph_loader:
+        batch_size, n_id, adjs = batch
+        for i, (edge_index, e_id, size) in enumerate(adjs):
[…]

### 2020-12-16 main_full_batch_acc_cum.py

@@ -158,6 +158,7 @@ for run in range(args.runs):
 
     es_count = best_val_acc = test_acc = 0
     t0 = time.time()
+    patient_step = 0
     for epoch in range(args.epochs):
         train(epoch)
         es_count += 1
@@ -165,6 +166,11 @@ for run in range(args.runs):
             accs = test()
             if accs[1] > best_val_acc:
                 best_val_acc = accs[1]
-                test_acc = max(test_acc, accs[2])
+                test_acc = accs[2]
+                patient_step = 0
+            else:
+                patient_step += 1
             print(f"Batch: {es_count:03d}, train_acc: {accs[0]:.8f}, val_acc: {accs[1]:.8f}, best_val_acc: {best_val_acc: .8f}, best_test_acc: {test_acc:.8f}, cur_use_time: {(time.time() - t0):.4f}s")
+        if patient_step >= 50:
+            break
   

### 2020-12-16 main_kdd_criterion.py

@@ -22,8 +22,8 @@ parser = argparse.ArgumentParser()
 parser.add_argument('--dataset', type=str, default='cora', help="dataset: [cora, flickr, com-amazon, reddit, com-lj,"
                                                                     "amazon-computers, amazon-photo, coauthor-physics, pubmed]")
 parser.add_argument('--model', type=str, default='gcn', help="gnn models: [gcn, ggnn, gat, gaan]")
-parser.add_argument('--epochs', type=int, default=100000, help="epochs for training")
-parser.add_argument('--patience_step', type=int, default=50, help="for KDDCriterion")
+parser.add_argument('--epochs', type=int, default=100000, help="epochs for training: KDDCriterion default")
+parser.add_argument('--patience_step', type=int, default=50, help="KDDCriterion default")
 parser.add_argument('--layers', type=int, default=2, help="layers for hidden layer")
 parser.add_argument('--hidden_dims', type=int, default=64, help="hidden layer output dims")
 parser.add_argument('--heads', type=int, default=8, help="gat or gaan model: heads")

### 2020-12-16 main_sampling_kdd_criterion.py

@@ -1,6 +1,3 @@
-"""
-Sample-based Inference阶段的时间性能瓶颈和空间性能瓶颈测量文件
-"""
 import torch
 import torch.nn.functional as F
 from torch.nn import ModuleList
@@ -18,7 +15,6 @@ from gaan.models import GaAN
 from ggnn.models import GGNN
 from gat.models import GAT
 from gcn.models import GCN
-from logger import Logger
 
 from utils import get_dataset, gcn_norm, normalize, get_split_by_file, nvtx_push, nvtx_pop, log_memory, small_datasets
 
@@ -27,7 +23,8 @@ parser.add_argument('--dataset', type=str, default='cora', help="dataset: [cora,
                                                                     "amazon-computers, amazon-photo, coauthor-physics, pubmed]")
 
 parser.add_argument('--model', type=str, default='gcn', help="gnn models: [gcn, ggnn, gat, gaan]")
-parser.add_argument('--epochs', type=int, default=11, help="epochs for training")
+parser.add_argument('--epochs', type=int, default=100000, help="epochs for training")
+parser.add_argument('--patience_step', type=int, default=50, help="patience_step for training")
 parser.add_argument('--layers', type=int, default=2, help="layers for hidden layer")
 parser.add_argument('--hidden_dims', type=int, default=64, help="hidden layer output dims")
 parser.add_argument('--heads', type=int, default=8, help="gat or gaan model: heads")
@@ -44,7 +41,6 @@ parser.add_argument('--lr', type=float, default=0.01, help="adam's learning rate
 parser.add_argument('--weight_decay', type=float, default=0.0005, help="adam's weight decay")
 parser.add_argument('--no_record_shapes', action='store_false', default=True, help="nvtx or autograd's profile to record shape")
 parser.add_argument('--json_path', type=str, default='', help="json file path for memory")
-parser.add_argument('--infer_json_path', type=str, default='', help="inference stage: json file path for memory")
 parser.add_argument('--mode', type=str, default='cluster', help='sampling: [cluster, graphsage]')
 parser.add_argument('--batch_size', type=int, default=512, help='batch size')
 parser.add_argument('--batch_partitions', type=int, default=20, help='number of cluster partitions per batch')
@@ -53,10 +49,7 @@ parser.add_argument('--num_workers', type=int, default=40, help='number of Data 
[…]

### 2020-12-16 main_sampling_kdd_criterion_batch.py

@@ -1,6 +1,3 @@
-"""
-Sample-based Inference阶段的时间性能瓶颈和空间性能瓶颈测量文件
-"""
 import torch
 import torch.nn.functional as F
 from torch.nn import ModuleList
@@ -18,7 +15,6 @@ from gaan.models import GaAN
 from ggnn.models import GGNN
 from gat.models import GAT
 from gcn.models import GCN
-from logger import Logger
 
 from utils import get_dataset, gcn_norm, normalize, get_split_by_file, nvtx_push, nvtx_pop, log_memory, small_datasets
 
@@ -27,7 +23,8 @@ parser.add_argument('--dataset', type=str, default='cora', help="dataset: [cora,
                                                                     "amazon-computers, amazon-photo, coauthor-physics, pubmed]")
 
 parser.add_argument('--model', type=str, default='gcn', help="gnn models: [gcn, ggnn, gat, gaan]")
-parser.add_argument('--epochs', type=int, default=11, help="epochs for training")
+parser.add_argument('--epochs', type=int, default=100000, help="epochs for training")
+parser.add_argument('--patience_step', type=int, default=50, help="patience_step for training")
 parser.add_argument('--layers', type=int, default=2, help="layers for hidden layer")
 parser.add_argument('--hidden_dims', type=int, default=64, help="hidden layer output dims")
 parser.add_argument('--heads', type=int, default=8, help="gat or gaan model: heads")
@@ -44,7 +41,6 @@ parser.add_argument('--lr', type=float, default=0.01, help="adam's learning rate
 parser.add_argument('--weight_decay', type=float, default=0.0005, help="adam's weight decay")
 parser.add_argument('--no_record_shapes', action='store_false', default=True, help="nvtx or autograd's profile to record shape")
 parser.add_argument('--json_path', type=str, default='', help="json file path for memory")
-parser.add_argument('--infer_json_path', type=str, default='', help="inference stage: json file path for memory")
 parser.add_argument('--mode', type=str, default='cluster', help='sampling: [cluster, graphsage]')
 parser.add_argument('--batch_size', type=int, default=512, help='batch size')
 parser.add_argument('--batch_partitions', type=int, default=20, help='number of cluster partitions per batch')
[…]

### 2020-12-16 paper_exp5_paras_acc/convergence_validation.py

@@ -15,7 +15,7 @@ gaan_hds = ["1", "2", "4", "8", "16", "32", "64", "128", "256", "512", "1024", "
 gaan_ds = ["1", "2", "4", "8", "16", "32", "64", "128", "256"]
 gaan_heads = ["1", "2", "4", "8", "16"]
 
-os.chdir("early_stopping1")
+# os.chdir("early_stopping1")
 for model in models:
     for data in datasets:
         if not os.path.exists(f"acc_fig/{model}/{data}"):
@@ -28,97 +28,90 @@ for model in models:
                 if not os.path.exists(file_name):
                     continue   
                 print(file_name)
-                train_acc, val_acc, test_acc = [], [], []
+                val_loss, train_acc, val_acc, test_acc = [], [], [], []
                 acc = None
                 cnt = 0
                 with open(file_name) as f:
                     for line in f:
-                        match_line = re.match(r"Epoch: .*, Train: (.*), Val: (.*), Test: (.*)", line)
-                        match_final_line = re.match("   Final Test: (.*) ± .*", line)
+                        match_line = re.match(r".*val_loss: (.*), Train: (.*), Val: (.*), Test: (.*)", line)
                         if match_line and cnt < 1000:
-                            train_acc.append(float(match_line.group(1)))
-                            val_acc.append(float(match_line.group(2)))
-                            test_acc.append(float(match_line.group(3)))
+                            val_loss.append(float(match_line.group(1)))
+                            train_acc.append(float(match_line.group(2)))
+                            val_acc.append(float(match_line.group(3)))
+                            test_acc.append(float(match_line.group(4)))
                             cnt += 1
-                        if match_final_line:
-                            acc = int(float(match_final_line.group(1)) * 100) / 10000
-                print("Final Test", acc)
                 fig, ax = plt.subplots()
                 x = range(len(train_acc))
                 category_colors = plt.get_cmap('RdYlGn')(
-                np.linspace(0.15, 0.85, 3))
-                labels = ["train_acc", "val_acc", "test_acc"]
-                accs = [train_acc, val_acc, test_acc]
+                np.linspace(0.15, 0.85, 4))
+                labels = ["val_loss", "train_acc", "val_acc", "test_acc"]
+                accs = [val_loss, train_acc, val_acc, test_acc]
                 for i, c in enumerate(category_colors):
                     ax.plot(x, accs[i], color=c, label=labels[i])
                 ax.legend()
[…]

### 2020-12-16 paper_exp5_paras_acc/gaan_exp_acc.sh

@@ -10,8 +10,9 @@ fi
 datasets=(amazon-photo pubmed amazon-computers coauthor-physics flickr)
 models=(gaan)
 ds=(8 16 32 64 128 256)
-heads=(1 2 4 8 16)
-hds=(1 2 4 8 16 32 64 128 256 512 1024 2048)
+# heads=(1 2 4 8 16)
+# hds=(1 2 4 8 16 32 64 128 256 512 1024 2048)
+# ds=(1 2 4)
 
 for data in ${datasets[@]}
 do
@@ -29,25 +30,25 @@ do
         done
 
         # hidden_dims
-        for hd in ${hds[@]}
-        do
-            val="model=${model}, dataset=${data}, heads=4, d_a, d_v, d_m=32, hidden_dims=${hd}"
-            echo ${val}
-            if [ -f "${dir_config}/config0_${model}_${data}_4_32_${hd}.log" ]; then # 断点续传
-                continue
-            fi
-            python ../main_kdd_criterion.py --device cuda:0 --dataset ${data} --model ${model} --hidden_dims ${hd} --heads 4 --d_v 32 --d_a 32 --d_m 32 1>"${dir_config}/config0_${model}_${data}_4_32_${hd}.log" 2>&1
-        done
+        # for hd in ${hds[@]}
+        # do
+        #     val="model=${model}, dataset=${data}, heads=4, d_a, d_v, d_m=32, hidden_dims=${hd}"
+        #     echo ${val}
+        #     if [ -f "${dir_config}/config0_${model}_${data}_4_32_${hd}.log" ]; then # 断点续传
+        #         continue
+        #     fi
+        #     python ../main_kdd_criterion.py --device cuda:0 --dataset ${data} --model ${model} --hidden_dims ${hd} --heads 4 --d_v 32 --d_a 32 --d_m 32 1>"${dir_config}/config0_${model}_${data}_4_32_${hd}.log" 2>&1
+        # done
         
         # heads
-        for h in ${heads[@]}
-        do
-            val="model=${model}, dataset=${data}, heads=${h}, d_a, d_v, d_m=32, hidden_dims=64"
-            echo ${val}
-            if [ -f "${dir_config}/config0_${model}_${data}_${h}_32_64.log" ]; then # 断点续传
-                continue
-            fi
[…]

### 2020-12-16 paper_exp5_paras_acc/gat_exp_acc.sh

@@ -14,27 +14,25 @@ heads=(1 2 4 8 16)
 
 for data in ${datasets[@]}
 do
-    # for model in ${models[@]}
-    model="gat"
-    for hd in ${hds[@]}
+    for model in ${models[@]}
     do
-        for hd in ${hds[@]}
-        do
-            val="model=${model}, dataset=${data}, head_dims=${hd}, heads=4"
-            echo ${val}
-            if [ -f "${dir_config}/config0_${model}_${data}_4_${hd}.log" ]; then # 断点续传
-                continue
-            fi
-            python ../main_kdd_criterion.py --device cuda:1 --dataset ${data} --model ${model} --head_dims ${hd} --d_v ${hd} --d_a ${hd} --heads 4 1>"${dir_config}/config0_${model}_${data}_4_${hd}.log" 2>&1
-        done
+        # for hd in ${hds[@]}
+        # do
+        #     val="model=${model}, dataset=${data}, head_dims=${hd}, heads=4"
+        #     echo ${val}
+        #     if [ -f "${dir_config}/config0_${model}_${data}_4_${hd}.log" ]; then # 断点续传
+        #         continue
+        #     fi
+        #     python ../main_kdd_criterion.py --device cuda:1 --dataset ${data} --model ${model} --head_dims ${hd} --d_v ${hd} --d_a ${hd} --heads 4 1>"${dir_config}/config0_${model}_${data}_4_${hd}.log" 2>&1
+        # done
         for h in ${heads[@]}
         do
-            val="model=${model}, dataset=${data}, head_dims=4, heads=${h}"
+            val="model=${model}, dataset=${data}, head_dims=32, heads=${h}"
             echo ${val}
-            if [ -f "${dir_config}/config0_${model}_${data}_${h}_${hd}.log" ]; then # 断点续传
+            if [ -f "${dir_config}/config0_${model}_${data}_${h}_32.log" ]; then # 断点续传
                 continue
             fi
-            python ../main_kdd_criterion.py --device cuda:1 --dataset ${data} --model ${model} --head_dims ${hd} --heads ${h} 1>"${dir_config}/config0_${model}_${data}_${h}_${hd}.log" 2>&1
+            python ../main_kdd_criterion.py --device cuda:1 --dataset ${data} --model ${model} --head_dims 32 --heads ${h} 1>"${dir_config}/config0_${model}_${data}_${h}_32.log" 2>&1
         done
     done
 done

### 2020-12-16 paper_exp5_paras_acc/handle_paras_acc_heads.py

@@ -13,10 +13,10 @@ models = ["gcn", "ggnn", "gat", "gaan"]
 gat_heads = ["1", "2", "4", "8", "16"]
 
 def save_acc_to_csv(): # 将统计得到的acc结果保存在csv文件中 
-    if not os.path.exists("acc_res"):
-        os.makedirs("acc_res")
+    dir_config = "dir_gat_heads_exp"
+    if not os.path.exists(dir_config):
+        os.makedirs(dir_config)
     model = "gat"
-    dir_config = "dir_gat_acc"
     
     for hd in ["1", "2", "4"]:
         # heads

### 2020-12-16 paper_exp6_sampling_acc/convergence_validation.py

@@ -32,12 +32,13 @@ datasets_maps = {
 
 xticklabels = ['1%', '3%', '6%', '10%', '25%', '50%', 'FULL']
 
-dir_in = "batch_acc_cum_fix_time"
+dir_in = "log_fix_time"
+dir_out = "res_convergence_validation"
 
 for data in datasets:
     for model in models:
-        if not os.path.exists(f"acc_fig/{model}/{data}"):
-            os.makedirs(f"acc_fig/{model}/{data}")
+        if not os.path.exists(f"{dir_out}/{model}/{data}"):
+            os.makedirs(f"{dir_out}/{model}/{data}")
         for mode in modes:
             print(data, model, mode)
             # 将数据存储到csv文件
@@ -95,4 +96,4 @@ for data in datasets:
                     ax.legend()
                     fig.tight_layout() 
                     fig_path = '_'.join([mode, model, data, str(cs)]) + '_graphsage.png'
-                    fig.savefig(f"acc_fig/{model}/{data}/{fig_path}")
+                    fig.savefig(f"{dir_out}/{model}/{data}/{fig_path}")

### 2020-12-16 paper_exp6_sampling_acc/handle_sampling_acc_fix_epoch.py

@@ -1,0 +1,117 @@
+import os, re, sys
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+plt.style.use("ggplot")
+plt.rcParams["font.size"] = 12
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+datasets = ["amazon-photo", "pubmed", "amazon-computers", "coauthor-physics", "flickr"]
+# datasets = ["amazon-computers"]
+modes = ["cluster", "graphsage"]
+algs = ["gcn", "ggnn", "gat", "gaan"]
+# algs = ["gat"]
+
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+xticklabels = ['1%', '3%', '6%', '10%', '25%', '50%', 'FULL']
+
+dir_in = "log_fix_epoch"
+dir_out = "res_fix_epoch"
+
+for data in datasets:
+    if not os.path.exists(dir_out + "/" + data):
+        os.makedirs(dir_out + "/" + data)
+        
+"""
+目标：绘制不同BatchSize下，精度随Batch Nums的变化结果
+
+数据收集：
+算法, 采样方法，数据集，time/acc
+
+绘制图像：
+算法+采样方法+time/acc
+df.index: 图像的横坐标
+df.columns: 图像中的不同的线(不同的BatchSize)
+"""
+for data in datasets:
+    for alg in algs:
+        for mode in modes:
+            print(data, alg, mode)
+            flag = False
+            # 将数据存储到csv文件
+            df_times, df_accs = {}, {}
+            if mode == "cluster":
+                for i, cs in enumerate(cluster_batchs):
+                    file_path = os.path.join(dir_in, '_'.join([mode, alg, data, str(cs)]) + ".log")
+                    if not os.path.exists(file_path):
+                        flag = True
+                        break
+                    df_times[xticklabels[i]], df_accs[xticklabels[i]] = [], []
+                    # 读取日志文件，获取bs_times, bs_accs: dims=100
+                    with open(file_path) as f:
+                        for line in f:
[…]

### 2020-12-16 paper_exp6_sampling_acc/handle_sampling_acc_fix_time.py

@@ -1,0 +1,114 @@
+import os, re, sys
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+plt.style.use("ggplot")
+plt.rcParams["font.size"] = 12
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+datasets = ["amazon-photo", "pubmed", "amazon-computers", "coauthor-physics", "flickr"]
+modes = ["cluster", "graphsage"]
+algs = ["gcn", "ggnn", "gat", "gaan"]
+
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+    'com-amazon': 'cam'
+}
+
+xticklabels = ['1%', '3%', '6%', '10%', '25%', '50%']
+
+dir_in = "log_fix_time"
+dir_out = "res_fix_time"
+
+for data in datasets:
+    if not os.path.exists(dir_out + "/" + data):
+        os.makedirs(dir_out + "/" + data)
+        
+"""
+目标：绘制不同BatchSize下，精度随Batch Nums的变化结果
+
+数据收集：
+算法, 采样方法，数据集，time/acc
+
+绘制图像：
+算法+采样方法+time/acc
+df.index: 图像的横坐标
+df.columns: 图像中的不同的线(不同的BatchSize)
+"""
+
+max_accs = pd.read_csv("/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp5_paras_acc/acc_res/alg_acc.csv", index_col=0)
+
+for data in datasets:
+    for alg in algs:
+        for mode in modes:
+            flag = False
+            # 将数据存储到csv文件
+            df_times, df_accs = {}, {}
+            if mode == "cluster":
+                for i, cs in enumerate(cluster_batchs):
[…]

### 2020-12-16 paper_exp6_sampling_acc/sampling_acc_fix_batch.py

@@ -1,0 +1,77 @@
+"""
+sampling_batch_acc_cum:
+采样的对比实验代码
+"""
+import os
+import time
+import numpy as np
+import pandas as pd
+
+config_paras = pd.read_csv("/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp5_paras_acc/early_stopping2/acc_res/max_acc.csv", index_col=0)
+
+small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr']
+algs = ['gcn', 'ggnn', 'gat', 'gaan']
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+    'com-amazon': 'cam'
+}
+
+dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "log_fix_batch")
+if not os.path.exists(dir_path):
+    os.makedirs(dir_path)
+
+for i, mode in enumerate(['cluster', 'graphsage']):
+    sh_commands = []
+    for alg in algs:
+        for data in small_datasets:
+            paras = str(config_paras.loc[datasets_maps[data], alg]).split('_')
+            if alg in ["gcn", "ggnn"]:
+                config_str = f"--hidden_dims {paras[0]}"
+            elif alg == "gat":
+                config_str = f"--heads {paras[0]} --head_dims {paras[1]}"
+            elif alg == "gaan":
+                config_str = f"--heads {paras[0]} --d_v {paras[1]} --d_a {paras[1]} --d_m {paras[1]} --hidden_dims {paras[2]}"
+            if mode == 'cluster':
[…]

### 2020-12-16 paper_exp6_sampling_acc/sampling_acc_fix_time.py

@@ -1,0 +1,80 @@
+"""
+sampling_batch_acc_cum_fix_time:
+采样的对比实验代码
+"""
+import os
+import time
+import numpy as np
+import pandas as pd
+
+config_paras = pd.read_csv("/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp5_paras_acc/acc_res/max_acc.csv", index_col=0)
+
+small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr']
+algs = ['gcn', 'ggnn', 'gat', 'gaan']
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+    'com-amazon': 'cam'
+}
+
+fix_times = {
+    'pubmed': 1000,
+    'coauthor-physics': 1000,
+    'flickr': 1750,
+    'amazon-photo': 1000,
+    'amazon-computers': 1400
+}
+
+dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "log_fix_time")
+if not os.path.exists(dir_path):
+    os.makedirs(dir_path)
+
+for i, mode in enumerate(['cluster', 'graphsage']):
+    sh_commands = []
+    for alg in algs:
+        for data in small_datasets:
+            paras = str(config_paras.loc[datasets_maps[data], alg]).split('_')
+            if alg in ["gcn", "ggnn"]:
+                config_str = f"--hidden_dims {paras[0]}"
+            elif alg == "gat":
+                config_str = f"--heads {paras[0]} --head_dims {paras[1]}"
+            elif alg == "gaan":
+                config_str = f"--heads {paras[0]} --d_v {paras[1]} --d_a {paras[1]} --d_m {paras[1]} --hidden_dims {paras[2]}"
+            if mode == 'cluster':
[…]

### 2020-12-16 paper_exp6_sampling_acc/sampling_acc_kdd_criterion.py

@@ -1,0 +1,62 @@
+import os
+import time
+import numpy as np
+import pandas as pd
+
+config_paras = pd.read_csv("/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp5_paras_acc/acc_res/max_acc.csv", index_col=0)
+
+small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr']
+algs = ['gcn', 'ggnn', 'gat', 'gaan']
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+    'com-amazon': 'cam'
+}
+
+dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "kdd_criterion")
+if not os.path.exists(dir_path):
+    os.makedirs(dir_path)
+
+for i, mode in enumerate(['cluster', 'graphsage']):
+    sh_commands = []
+    for alg in algs:
+        for data in small_datasets:
+            paras = str(config_paras.loc[datasets_maps[data], alg]).split('_')
+            if alg in ["gcn", "ggnn"]:
+                config_str = f"--hidden_dims {paras[0]}"
+            elif alg == "gat":
+                config_str = f"--heads {paras[0]} --head_dims {paras[1]}"
+            elif alg == "gaan":
+                config_str = f"--heads {paras[0]} --d_v {paras[1]} --d_a {paras[1]} --d_m {paras[1]} --hidden_dims {paras[2]}"
+            if mode == 'cluster':
+                cmd = "python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode {} --model {} --data {} --device cuda:{} --batch_partitions {} {} >>{} 2>&1"
[…]

### 2020-12-16 paper_exp6_sampling_acc/sh_cluster_kdd_criterion.sh

@@ -1,0 +1,120 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 15 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/cluster_gcn_amazon-photo_15.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 45 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/cluster_gcn_amazon-photo_45.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 90 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/cluster_gcn_amazon-photo_90.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 150 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/cluster_gcn_amazon-photo_150.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 375 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/cluster_gcn_amazon-photo_375.log 2>&1
[…]

### 2020-12-16 paper_exp6_sampling_acc/sh_cluster_kdd_criterion_batch.sh

@@ -1,0 +1,120 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 15 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/cluster_gcn_amazon-photo_15.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 45 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/cluster_gcn_amazon-photo_45.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 90 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/cluster_gcn_amazon-photo_90.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 150 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/cluster_gcn_amazon-photo_150.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 375 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/cluster_gcn_amazon-photo_375.log 2>&1
[…]

### 2020-12-16 paper_exp6_sampling_acc/sh_graphsage_kdd_criterion.sh

@@ -1,0 +1,120 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 77 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/graphsage_gcn_amazon-photo_77.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 230 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/graphsage_gcn_amazon-photo_230.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 459 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/graphsage_gcn_amazon-photo_459.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 765 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/graphsage_gcn_amazon-photo_765.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 1913 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion/graphsage_gcn_amazon-photo_1913.log 2>&1
[…]

### 2020-12-16 paper_exp6_sampling_acc/sh_graphsage_kdd_criterion_batch.sh

@@ -1,0 +1,120 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 77 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/graphsage_gcn_amazon-photo_77.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 230 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/graphsage_gcn_amazon-photo_230.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 459 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/graphsage_gcn_amazon-photo_459.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 765 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/graphsage_gcn_amazon-photo_765.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_kdd_criterion_batch.py --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 1913 --hidden_dims 64 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/kdd_criterion_batch/graphsage_gcn_amazon-photo_1913.log 2>&1
[…]

### 2020-12-16 paper_exp7_inference_sampling/inference_sampling_memory.py

@@ -2,46 +2,22 @@ import os
 import time
 
 small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr', 'com-amazon']
-
 algs = ['gcn', 'ggnn', 'gat', 'gaan']
-cluster_batchs = [15, 45, 90, 150, 375, 750]
-
-graphsage_batchs = {
-    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
-    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
-    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
-    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
-    'flickr': [893, 2678, 5355, 8925, 22313, 44625],
-    'com-amazon': [3349, 10046, 20092, 33487, 83716, 167432]
-}
 
 dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "inference_sampling_memory")
 if not os.path.exists(dir_path):
     os.makedirs(dir_path)
 
-for i, mode in enumerate(['cluster', 'graphsage']):
-    sh_commands = []
+sh_commands = []
+for alg in algs:
     for data in small_datasets:
-        for alg in algs:
-            if mode == 'cluster':
-                cmd = "python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:{} --mode {} --model {} --data {} --epochs 20 --batch_partitions {} --infer_json_path {}"
-                for cs in cluster_batchs:
-                    file_path = os.path.join(dir_path, '_'.join([mode, alg, data, str(cs)]) + '.json')
-                    if os.path.exists(file_path):
-                        continue
-                    print(file_path)
-                    sh_commands.append(cmd.format(str(i), mode, alg, data, str(cs), file_path))
-                    print(time.strftime('%Y-%m-%d %H:%M:%S', time.localtime(time.time())))
-            else:
-                cmd = "python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:{} --mode {} --model {} --data {} --epochs 20 --batch_size {} --infer_json_path {}"
-                for gs in graphsage_batchs[data]:
-                    file_path = os.path.join(dir_path, '_'.join([mode, alg, data, str(gs)]) + '.json')
-                    if os.path.exists(file_path):
-                        continue
[…]

### 2020-12-16 paper_exp7_inference_sampling/inference_sampling_memory.sh

@@ -1,0 +1,4 @@
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model gcn --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gcn_com-amazon.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model ggnn --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/ggnn_com-amazon.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model gat --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gat_com-amazon.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model gaan --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gaan_com-amazon.json

### 2020-12-16 paper_exp7_inference_sampling/inference_sampling_time.py

@@ -2,46 +2,22 @@ import os
 import time
 
 small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr', 'com-amazon']
-
 algs = ['gcn', 'ggnn', 'gat', 'gaan']
-cluster_batchs = [15, 45, 90, 150, 375, 750]
-
-graphsage_batchs = {
-    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
-    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
-    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
-    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
-    'flickr': [893, 2678, 5355, 8925, 22313, 44625],
-    'com-amazon': [3349, 10046, 20092, 33487, 83716, 167432]
-}
 
 dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "inference_sampling_time")
 if not os.path.exists(dir_path):
     os.makedirs(dir_path)
 
-for i, mode in enumerate(['cluster', 'graphsage']):
-    sh_commands = []
+sh_commands = []
+for alg in algs:
     for data in small_datasets:
-        for alg in algs:
-            if mode == 'cluster':
-                cmd = "python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:{} --mode {} --model {} --data {} --epochs 20 --batch_partitions {} >{} 2>&1"
-                for cs in cluster_batchs:
-                    file_path = os.path.join(dir_path, '_'.join([mode, alg, data, str(cs)]) + '.log')
-                    if os.path.exists(file_path):
-                        continue
-                    print(file_path)
-                    sh_commands.append(cmd.format(str(i), mode, alg, data, str(cs), file_path))
-                    print(time.strftime('%Y-%m-%d %H:%M:%S', time.localtime(time.time())))
-            else:
-                cmd = "python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:{} --mode {} --model {} --data {} --epochs 20 --batch_size {} >{} 2>&1"
-                for gs in graphsage_batchs[data]:
-                    file_path = os.path.join(dir_path, '_'.join([mode, alg, data, str(gs)]) + '.log')
-                    if os.path.exists(file_path):
-                        continue
[…]

### 2020-12-16 paper_exp7_inference_sampling/run.sh

@@ -1,0 +1,2 @@
+bash inference_sampling_time.sh >inference_sampling_time.log 2>&1
+bash inference_sampling_memory.sh >inference_sampling_memory.log 2>&1

### 2020-12-16 paper_exp8_inference_full/config_memory.sh

@@ -19,6 +19,6 @@ do
             continue
         fi
         echo ${val}
-        python ../main_inference.py --dataset ${data} --model ${model} --json_path "${dir_config}/config0_${model}_${data}.json"
+        python ../main_inference_memory.py --device cuda:0 --dataset ${data} --model ${model} --json_path "${dir_config}/config0_${model}_${data}.json"
     done
 done

### 2020-12-16 paper_exp8_inference_full/degrees_memory.sh

@@ -19,6 +19,6 @@ do
         fi
         val="configuration=0, model=${model}, dataset=graph_10k_${ds}"
         echo ${val}
-        python ../main_inference_memory.py --dataset "graph_10k_${ds}" --model ${model} --json_path "${dir_config}/config0_${model}_graph_10k_${ds}.json"
+        python ../main_inference_memory.py --device cuda:0 --dataset "graph_10k_${ds}" --model ${model} --json_path "${dir_config}/config0_${model}_graph_10k_${ds}.json"
     done
 done

### 2020-12-16 paper_exp8_inference_full/feat_dims_memory.sh

@@ -7,7 +7,6 @@ then
 fi
 
 
-# datasets=(amazon-photo pubmed amazon-computers coauthor-physics flickr com-amazon)
 datasets=(com-amazon)
 models=(gcn ggnn gat gaan)
 fds=(16 32 64 128 256 512)

### 2020-12-16 paper_exp8_inference_full/run.sh

@@ -3,4 +3,4 @@ date
 bash config_exp.sh >config_exp.log 2>&1
 date
 echo "begin degree exp"
-bash degree_exp.sh >degree_exp.log 2>&1
+bash degrees_exp.sh >degrees_exp.log 2>&1

### 2020-12-16 run_0.sh

@@ -1,15 +1,13 @@
 export LD_LIBRARY_PATH=/home/wangzhaokang/anaconda3/envs/pyg1.5/lib/python3.7/site-packages/torch/lib:${LD_LIBRARY_PATH}
 dir_path="/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns"
-
-# date
-# cd "${dir_path}/paper_exp7_inference_sampling"
-# echo "exp7: "
-# bash inference_sampling_cluster_time.sh >inference_sampling_cluster_time.log 2>&1
-# date
-# bash inference_sampling_cluster_memory.sh >inference_sampling_cluster_memory.log 2>&1
-
 date
-cd "${dir_path}/paper_exp6_sampling_acc"
-echo "exp6: "
-bash batch_acc_cum_cluster_fix_time.sh >batch_acc_cum_cluster_fix_time.log 2>&1
 
+cd "${dir_path}/paper_exp7_inference_sampling"
+echo "begin inference sampling memory"
+bash inference_sampling_memory.sh > inference_sampling_memory.log 2>&1
+date
+
+cd "${dir_path}/paper_exp6_sampling_acc"
+echo "cluster fix time"
+bash sh_cluster_fix_time_new.sh >sh_cluster_fix_time_new.log 2>&1
+date

### 2020-12-16 run_1.sh

@@ -1,15 +1,13 @@
 export LD_LIBRARY_PATH=/home/wangzhaokang/anaconda3/envs/pyg1.5/lib/python3.7/site-packages/torch/lib:${LD_LIBRARY_PATH}
 dir_path="/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns"
-
-# date
-# cd "${dir_path}/paper_exp7_inference_sampling"
-# echo "exp7: "
-# bash inference_sampling_graphsage_time.sh >inference_sampling_graphsage_time.log 2>&1
-# date
-# bash inference_sampling_graphsage_memory.sh >inference_sampling_graphsage_memory.log 2>&1
-
 date
-cd "${dir_path}/paper_exp6_sampling_acc"
-echo "exp6: "
-bash batch_acc_cum_graphsage_fix_time.sh >batch_acc_cum_graphsage_fix_time.log 2>&1
 
+# cd "${dir_path}/paper_exp5_paras_acc"
+# echo "gat heads acc"
+# bash gat_heads_exp.sh >gat_heads_exp.log 2>&1
+# date
+
+cd "${dir_path}/paper_exp6_sampling_acc"
+echo "graphsage fix time"
+bash sh_graphsage_fix_time_new.sh >sh_graphsage_fix_time_new.log 2>&1
+date

### 2020-12-18 NEUROC/Response-MajRev/response_letter.tex
更新R1P1

@@
 
-    In the revised manuscript, $\boldsymbol{e}_{i,j}$ represents the input feature vector of the edge $e_{i,j}$.
+    In the revised manuscript, $\boldsymbol{e}_{x,y}$ represents the input feature vector of the edge $e_{x,y}$.
     %
@@
     %
-    $\boldsymbol{s}^l_i$ represents the aggregated vector of the graph neuron corresponding to the vertex $v_i$ in the GNN layer $l$.
+    $\boldsymbol{s}^l_x$ represents the aggregated vector of the graph neuron corresponding to the vertex $v_x$ in the GNN layer $l$.
     %
-    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,k}_i$ represents the aggregated vector corresponding to $v_i$ in the $k$-th sub-layer.
+    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents the aggregated vector corresponding to $v_x$ in the $i$-th sub-layer.
 

### 2020-12-18 NEUROC/sec1-introduction.tex
更新R1P1

@@
 To train GNNs easily, a series of GNN libraries/systems \cite{PyG, DGL, ma2019_neugraph, zhu2019_aligraph, PGL} are proposed.
-PyG \cite{PyG}, NeuGraph \cite{ma2019_neugraph}, PGL \cite{PGL} and DGL \cite{DGL} build upon the existing deep learning frameworks (PyG on PyTorch, NeuGraph on TensorFlow, PGL on PaddlePaddle, DGL on multiple backends).
+PyTorch Geometric (PyG) \cite{PyG}, NeuGraph \cite{ma2019_neugraph}, PGL \cite{PGL} and Deep Graph Library (DGL) \cite{DGL} build upon the existing deep learning frameworks (PyG on PyTorch, NeuGraph on TensorFlow, PGL on PaddlePaddle, DGL on multiple backends).
 They provide users with a high-level programming models (the message-passing model for PyG/PGL/DGL and the SAGA-NN model for NeuGraph) to describe the structure of a GNN.

### 2020-12-18 NEUROC/sec2-review-of-graph-neural-network.tex
更新R1P1

--- 2020-08-29 CCPE/Mauscript/sec2-review-of-graph-neural-network.tex
@@
 In this section, we formally define the graph neural networks and briefly survey typical graph neural networks.
-We denote a simple graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
-Let $n=|\mathcal{V}|$ and $m=|\mathcal{E}|$ as the number of vertices/edges.
-We use $v_i$ $(0 \leq i < n)$ to denote a vertex and $e_{i,j}=(v_i, v_j)$ to denote the edge pointing from $v_i$ to $v_j$.
-The adjacency set of $v_i$ is $\mathcal{N}(v_i)=\{v|(v_i, v) \in \mathcal{E}\}$.
-We denote a \emph{vector} with a bold lower case letter like $\boldsymbol{x}$ and a \emph{matri}x with a bold upper case letter like $\boldsymbol{X}$.
+%
+We denote a simple \emph{undirected} graph $\mathcal{G}$ as $\mathcal{G}=(\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set of $\mathcal{G}$, respectively.
+%
+We use $v_x$ $(0 \leq x < |\mathcal{V}|)$ to denote a vertex and $e_{x,y}=(v_x, v_y)$ to denote the edge pointing from $v_x$ to $v_y$.
+%
+The adjacency set of $v_x$ is $\mathcal{N}(v_x)=\{v|(v_x, v) \in \mathcal{E}\}$.
+%
+We denote a \emph{vector} with a bold lower case letter like $\boldsymbol{h}$ and a \emph{matri}x with a bold upper case letter like $\boldsymbol{W}$.
+%
+Table~\ref{tab:notations} summarizes the common symbols used throughout this work.
+%
+We use blue characters $\Param{\MyVec{w}}$/$\Param{\MyMat{W}}$ to denote weight vectors/matrices that are model parameters to train in a GNN.
+
+\begin{table}[h]
+    \caption{Notations}
+    \label{tab:notations}
+    \centering
+    \small
+    \begin{tabular}{p{3em}lp{35em}}
+        \toprule
+       Category & Symbol & Meaning \\
+        \midrule
+        \multirow[c]{4}{3em}{Graph Structure}& $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ & The simple undirected input graph with the vertex set $\mathcal{V}$ and the edge set $\mathcal{E}$. \\
+        & $v_x$ & The $x$-th vertex of the input graph. \\
+        & $e_{x,y}$ & The edge pointing from $v_x$ to $v_y$ of the input graph. \\
+        & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ \midrule
+        \multirow[c]{6}{3em}{GNN Definition}& $L$ & The number of GNN layers. \\
+        & $K$ & The number of heads in a GNN layer. \\
+        & $\phi^l$ & The messaging function of the GNN layer $l$. \\
+        & $\Sigma^l$ & The aggregation function of the GNN layer $l$. \\
+        & $\gamma^l$ & The vertex updating function of the GNN layer $l$. \\ 
+        & $\phi^{l,i}$/$\Sigma^{l,i}$/$\gamma^{l,i}$ & The messaging/aggregation/updating function of the $i$-th sub-layer of the GNN layer  $l$.\\
+        & $\textcolor{blue}{\boldsymbol{W}^l, \boldsymbol{W}^{(k)}/\boldsymbol{b}, \boldsymbol{a}}$ & The matrices/vectors represented by the blue characters are the weight matrices/vectors that need to be learned in the GNN.
+\\  \midrule
+        \multirow[c]{8}{3em}{Vectors}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
+        & $\boldsymbol{e}_{x,y}$ & The feature vector of the edge $e_{x,y}$.  \\
+        & $\boldsymbol{h}_x^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$. \\
+        & $\boldsymbol{h}_x^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$.\\
+        & $\boldsymbol{m}_{x,y}^l$ & The message vector of the edge $e_{x,y}$ outputted by $\phi^l$ of the GNN layer $l$. \\
+        & $\boldsymbol{s}_{x}^l$ & The aggregated vector of the vertex $v_x$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
+        & $\boldsymbol{h}_{x}^{l,i}$/$\boldsymbol{m}_{x,y}^{l,i}$/$\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
+\\
+        & $d_{in}$, $d_{out}$ &  The dimensions of the input/output hidden vectors of a graph neuron. \\
+        \bottomrule
+
+    \end{tabular}
+\end{table}
 
@@
 
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \includegraphics[width=1\columnwidth]{figs/illustration/GNN_common_architecture.pdf}
+    \includegraphics[width=0.95\columnwidth]{figs/illustration/GNN_common_architecture.pdf}
     \caption{Structure of a typical graph neural network. (a) Demo GNN, (b) Demo graph. The target application is the node classification. The demo GNN has two GNN layers.}
@@
 
-A GNN receives a graph $\mathcal{G}$ as the input.
-Every vertex $v_i$ in $\mathcal{G}$ is attached with a feature vector $\boldsymbol{x}_i$ to describe the properties of the vertex.
-The edges of $\mathcal{G}$ may also be attached with feature vectors $\boldsymbol{e}_{i,j}$
-The input layer of a GNN receives feature vectors from all vertices and passes them to GNN layers.
+In the inpug layer, A GNN receives a graph $\mathcal{G}$ as the input.
+%
+Every vertex $v_x$ in $\mathcal{G}$ is attached with a feature vector $\boldsymbol{v}_x$ to describe the properties of the vertex.
+%
+Every edge $e_{x,y}$ of $\mathcal{G}$ may also be attached with a feature vector $\boldsymbol{e}_{x,y}$.
+%
+The input layer of a GNN receives feature vectors from all vertices and passes the feature vectors to the first GNN layer (i.e. GNN layer 0).
 
-A GNN layer consists of $n$ graph neurons, where $n$ is the number of vertices in $\mathcal{G}$.
+A GNN usually consists of more than one GNN layers.
+%
+Each GNN layer consists of $|\mathcal{V}|$ graph neurons, where $|\mathcal{V}|$ is the number of vertices in $\mathcal{G}$.
+%
 Each graph neuron corresponds to a vertex in $\mathcal{G}$.
-In the first GNN layer (Layer 0), the graph neuron of the vertex $v_i$ collects input feature vectors of itself and the vertices $\boldsymbol{x}_j$ that are adjacent to $v_i$ in $\mathcal{G}$ (i.e., $v_j \in \mathcal{N}(v_i)$) from the input layer.
-The graph neuron aggregates input feature vectors, apply non-linear transformation, and outputs a hidden feature vector $\boldsymbol{h}^1_i$ for $v_i$.
+%
+Different GNNs mainly differ in the graph neurons that they use.
+%
+We elaborate on details of graph neurons later.
+%
+GNN layers are \emph{sparsely} connected with the input layer and other GNN layers.
+%
+\begin{itemize}
+    \item In the first GNN layer (layer 0), a graph neuron collects feature vectors from the input layer.
+    %
+    For the graph neuron corresponding to the vertex $v_x$, it collects the feature vector $\boldsymbol{v}_x$ and the feature vectors $\boldsymbol{v}_y$ of the vertices $v_y$ that are adjacent to $v_x$ (i.e.
+$v_y \in \mathcal{N}(v_x)$).
+    %
+    The graph neuron aggregates input feature vectors, apply non-linear transformation, and outputs a hidden vector $\boldsymbol{h}^1_x$ for $v_x$.
+    %
     Take the demo GNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as the example.
-Since $\mathcal{N}(v_3) = \{v_1, v_2, v_4, v_5, v_6\}$, the graph neuron of $v_3$ at the GNN layer 0 collects the feature vectors \{$\boldsymbol{x}_1$, $\boldsymbol{x}_2$, $\boldsymbol{x}_3$, $\boldsymbol{x}_4$, $\boldsymbol{x}_5$, $\boldsymbol{x}_6$\} from the input layer and outputs $\boldsymbol{h}^1_3$.
-Different GNNs mainly differ in the graph neurons that they use.
-We elaborate on their details later.
+    %
+    Since $\mathcal{N}(v_3) = \{v_1, v_2, v_4, v_5, v_6\}$, the graph neuron of $v_3$ at the GNN layer 0 collects the input feature vectors \{$\boldsymbol{v}_1$, $\boldsymbol{v}_2$, $\boldsymbol{v}_3$, $\boldsymbol{v}_4$, $\boldsymbol{v}_5$, $\boldsymbol{v}_6$\} from the input layer and outputs $\boldsymbol{h}^1_3$.
+    %
+    The connections between the first GNN layer and the input layer  are determined by the topology of $\mathcal{G}$.
+    %
+    The graph neuron of $v_x$ in the first GNN layer is connected with the input unit of $v_y$  in the input layer only if there is an edge $e_{x,y}$ between $v_x$ and $v_y$ in $\mathcal{G}$.
+    %
+    Since most real-world graphs are very \emph{sparse} (i.e.
+$|\mathcal{E}| \ll |\mathcal{V}|^2$), the connections between the first GNN layer and the input layer are also sparse, different from the traditional neural networks.
 
-Different from the traditional neural networks that layers are fully connected, the layers are sparsely connected in GNNs. 
-The connection between the input layer and the first GNN layer is determined by the topology of $\mathcal{G}$.
-Two graph neurons are connected only if their corresponding vertices have an edge between them in $\mathcal{G}$.
-Most real-world graphs are very \emph{sparse}, i.e. $|\mathcal{E}| \ll |\mathcal{V}|^2$.
+    \item In the next GNN layer (layer 1), the graph neuron corresponding to $v_x$ collects the hidden vector of itself $\boldsymbol{h}^1_x$ and its adjacent vertices ($\boldsymbol{h}^1_y$ with $v_y \in \mathcal{N}(v_x)$) from the \emph{previous} GNN layer.
+    %
+    Thus, the connections between the first and the second GNN layers are also determined by the topology of $\mathcal{G}$.
+    %
+    Based on the collected hidden vectors, the graph neuron in the layer 1 outputs a new hidden vector $\boldsymbol{h}^2_x$ for $v_x$.
 
-In the next GNN layer (GNN Layer 1), the graph neuron of $v_i$ collects the hidden feature vectors of itself $\boldsymbol{h}^1_i$ and its neighbors ($\boldsymbol{h}^1_j$ with $v_j \in \mathcal{N}(v_i)$) from the \emph{previous} GNN layer.
-Based on the collected hidden vectors, the graph neuron in Layer 1 outputs a new hidden feature vector $\boldsymbol{h}^2_i$ for $v_i$.
-A GNN allows stacking more GNN layers to support deeper graph analysis.
-Assume there are $L$ GNN layers in traditional.
-The last GNN layer (GNN Layer $L-1$) outputs a hidden feature vector $\boldsymbol{h}^{L}_i$ for every vertex $v_i$.
-As an embedding vector, $\boldsymbol{h}^L_i$ encodes the knowledge learned from the input layer and all the previous GNN layers.
-Since $\boldsymbol{h}^L_i$ is affected by $v_i$ and the vertices in the $L$-hop neighborhood of $v_i$, analyzing a graph with a \emph{deeper} GNN means analyzing each vertex with a \emph{wider} scope.
+    \item   A GNN allows stacking more GNN layers to support deeper graph analysis.
+    %
+    Assume there are $L$ GNN layers in total.
+    %
+    The last GNN layer (layer $L-1$) outputs a hidden vector $\boldsymbol{h}^{L}_x$ for every vertex $v_x$.
+    %
+    $\boldsymbol{h}^L_x$ is an embedding vector that encodes the knowledge learned from the input layer and all the previous GNN layers.
+    %
+    Since $\boldsymbol{h}^L_x$ is affected by $v_x$ and the vertices in the $L$-hop neighborhood of $v_x$, analyzing a graph with more GNN layers means analyzing each vertex with a \emph{wider} scope.
+    %
+    The hidden vectors $\boldsymbol{h}^L_x$ of the last GNN layer are fed to the prediction layer to generate the output for the whole GNN.
+\end{itemize}
 
-The hidden feature vectors $\boldsymbol{h}^L_i$ of the last GNN layer are fed to the prediction layer to generate the output of the whole GNN.
 The prediction layer is a standard neural network.
+%
 The structure of the prediction layer depends on the prediction task of the GNN.
+%
 Take the node classification task in \figurename~\ref{fig:general_structure_of_gnn} as the example.
+%
 The node classification predicts a label for every vertex in $\mathcal{G}$.
-In this case, the prediction layer can be a simple softmax layer with $\boldsymbol{h}^L_i$ as the input and a vector of probabilities as the output.
-If the prediction task is edge prediction, the hidden feature vectors of two vertices are concatenated and fed into a softmax layer.
+%
+In this case, the prediction layer can be a simple softmax layer with $\boldsymbol{h}^L_x$ as the input and a vector of probabilities as the output.
+%
+If the prediction task is the edge prediction, the hidden vectors of two vertices are concatenated and fed into a softmax layer.
+%
 If we need to predict a label for the whole graph, a pooling (max/mean/...) layer is added to generate an embedding vector for the whole graph and the embedding vector is used to produce the final prediction.
 
-Supporting end-to-end training is a prominent advantage of GNN, compared with traditional graph-based machine learning methods.
-The traditional methods need to construct feature vectors manually or from the embedding methods like DeepWalk \cite{bryan2014_deepwalk} and node2vec \cite{aditya2016_node2vec}.
-The feature vector generation is independent from the downstream prediction task. 
-Thus, the vectors have to be adjusted for every prediction task individually.
-In GNNs, the gradients are propagated from the prediction layer back to the previous GNN layers layer by layer. 
+Supporting end-to-end training is a prominent advantage of GNNs, compared with traditional graph-based machine learning methods.
+The traditional methods need to construct input feature vectors for vertices and edges manually or use embedding methods like DeepWalk \cite{bryan2014_deepwalk} and node2vec \cite{aditya2016_node2vec}.
+The feature vector generation is independent from the model training.
+Therefore, generated feature vectors may not be suitable for downstream prediction tasks.
+In GNNs, gradients are propagated from the prediction layer back to GNN layers layer by layer. 
 The model parameters in the GNN layers are updated based on the feedbacks from the downstream prediction task. 
-In a fully parameterized way, the GNN automatically extracts an embedding vector for each vertex from its $L$-hop neighborhood, tuned according to the specific prediction task.
+In a fully parameterized way, a GNN can automatically extract an embedding vector for each vertex from its $L$-hop neighborhood, tuned according to the specific prediction task.
 
@@
 Graph neurons are building blocks of a GNN.
+%
 A GNN layer consists of $|\mathcal{V}|$ graph neurons.
+%
 Each vertex corresponds to a graph neuron.
-A graph neuron as shown in \figurename~\ref{fig:graph_neuron_structure} is a small neural network.
-The graph neuron of $v_i$ at layer $l$ receives hidden feature vectors $\boldsymbol{h}^l_j$ from the graph neurons of $v_i$ and its neighbors ($v_j \in \{v_i\} \cup \mathcal{N}(v_i)$) at the previous GNN layer \footnote{For the GNN layer 0, graph neurons receive input feature vectors, i.e., $\boldsymbol{h}^0_i=\boldsymbol{x}_i$}.
-The graph neuron aggregates the received hidden feature vectors, applies non-linear transformations, and outputs a new hidden feature vector $\boldsymbol{h}_i^{l+1}$.
+%
+A graph neuron is a small neural network.
+%
+For the graph neuron corresponding to $v_x$ at the layer $l$, it receives the hidden vector of itself $\boldsymbol{h}^l_x$ and the hidden vectors of its adjacent vertices $\boldsymbol{h}^l_y$ with $v_y \in \mathcal{N}(v_x)$ from the previous GNN layer\footnote{For the GNN layer 0, graph neurons receive input feature vectors, i.e., $\boldsymbol{h}^0_i=\boldsymbol{v}_i$}.
+%
+The graph neuron of $v_x$ aggregates the received hidden vectors, applies non-linear transformations, and outputs a new hidden vector $\boldsymbol{h}_x^{l+1}$.
 
-\begin{figure}
+We follow the message-passing model \cite{gilmer_messgae_passing} to formally define a graph neuron.
+%
+The message-passing model is widely used in the cutting-edge GNN libraries like PyG \cite{PyG} and DGL \cite{DGL}.
+%
+\figurename~\ref{fig:graph_neuron_structure} shows the internal structure of a graph neuron in the message-passing model.
+%
+A graph neuron at the layer $l$ are made of three \emph{differentiable} functions: the messaging function $\phi^l$, the aggregation function $\Sigma^l$, and the updating function $\gamma^l$.
+
+\begin{figure}[H]
     \centering
     \includegraphics[width=0.5\columnwidth]{figs/illustration/GNN_Unit.pdf}
-    \caption{Graph neuron of $v_3$ at the GNN layer $l$ with the graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}(b).
-$\phi$/$\Sigma$/$\gamma$ are the messaging/aggregation/vertex updating functions in the message-passing model, respecitvely.}
+    \caption{Graph neuron of $v_3$ in the GNN layer $l$ with the demo graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}b.
+$\phi^l$/$\Sigma^l$/$\gamma^l$ are the messaging/aggregation/updating functions in the message-passing model, respecitvely.}
     \label{fig:graph_neuron_structure}
@@
 
-We follow the message-passing model \cite{gilmer_messgae_passing} to formally define a graph neuron.
-The message-passing model is widely used in the cutting-edge GNN libraries like PyTorch Geometric (PyG) \cite{PyG} and Deep Graph Library (DGL) \cite{DGL}.
-\figurename~\ref{fig:graph_neuron_structure} shows the structure of a graph neuron in the message-passing model.
-Graph neurons at layer $l$ are made of three \emph{differentiable} functions: $\phi^l$, $\Sigma^l$ and $\gamma^l$.
-The graph neuron calculates the output hidden vector $\boldsymbol{h}^{l+1}_i$ by
-$$
-    \boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \mathlarger{\Sigma}^l_{v_j \in \mathcal{N}(v_i)}{\phi^l(\boldsymbol{h}^l_i, \boldsymbol{h}^l_j,   \boldsymbol{e}_{j,i})}).
-$$
+The graph neuron of $v_x$ calculates the output hidden vector $\boldsymbol{h}^{l+1}_x$ with the three functions in three steps:
+%
+\begin{enumerate}
+    %
+    \item  For every adjacent edge $(v_y, v_x)$ of $v_x$ ($v_y \in \mathcal{N}(v_x)$), the messaging function $\phi^l$ receives the output hidden vectors $\boldsymbol{h}^l_x$ and $\boldsymbol{h}^l_y$ from the previous GNN layer and the edge feature vector $\boldsymbol{e}_{y,x}$ (and other feature vectors associated with $v_x$/$v_y$ if necessary) as the input.
+    %
+    $\phi^l$ emits a \emph{message vector} $\boldsymbol{m}^l_{y,x}$ for every edge $(v_y, v_x)$ at the layer $l$, i.e.
+$\boldsymbol{m}^l_{y,x} = \phi^l(\boldsymbol{h}^l_y, \boldsymbol{h}^l_x, \boldsymbol{e}_{y,x}, \dots)$;
+    %
+    \item The aggregation function $\Sigma^l$ then aggregates the message vectors $\boldsymbol{m}^l_{y,x}$ of the adjacent edges ($v_y \in \mathcal{N}(v_x)$) to produce an \emph{aggregated vector} $\boldsymbol{s}^l_x$, i.e.
+$\boldsymbol{s}^l_{x} = \sum^l_{v_y \in \mathcal{N}(v_x)}{\boldsymbol{m}^l_{y,x}}$;
+    %
+    \item The updating function $\gamma^l$ calculates the {hidden vector} of this layer $\boldsymbol{h}^{l+1}_x$ based on the hidden vector from the previous layer $\MyVec{h}^l_x$ and the aggregated vector $\MyVec{s}^l_x$ (and other feature vectors associated with $v_x$ if necessary), i.e.
+$\boldsymbol{h}^{l+1}_x = \gamma^l(\boldsymbol{h}^l_x, \boldsymbol{s}^l_x, \dots)$.
+\end{enumerate}
 
-$\phi^l$ is the \emph{messaging} function.
-For every incident edge $(v_j, v_i)$ of $v_i$, $\phi$ receives the output hidden feature vectors $\boldsymbol{h}^l_i$ and $\boldsymbol{h}^l_j$ from the previous GNN layer and the edge feature vector $\boldsymbol{e}_{j,i}$ as the input.
-$\phi^l$ emits a message vector $\boldsymbol{m}^l_{j,i}$ for every edge $(v_j, v_i)$ at layer $l$, i.e., $\boldsymbol{m}^l_{j,i}=\phi^l(\boldsymbol{h}^l_i, \boldsymbol{h}^l_j, \boldsymbol{e}_{j,i})$.
-For every $v_i$, the message vectors $\boldsymbol{m}^l_{j,i}$ of its adjacent edges ($v_j \in \mathcal{N}(v_i)$) are aggregated by the \emph{aggregation} function $\Sigma^l$ to produce an aggregated vector $\boldsymbol{s}^l_i$, i.e., $\boldsymbol{s}^l_i=\mathlarger{\Sigma}^l_{v_j \in \mathcal{N}(v_i)}\boldsymbol{m}^l_{j,i}$.
-$v_i$'s aggregated vector $\boldsymbol{s}^l_i$ and its hidden vector $\boldsymbol{h}^l_i$ from the previous GNN layer are fed into the \emph{vertex updating} function $\gamma^l$ to calculate the output hidden vector $\boldsymbol{h}^{l+1}_i$ of the current layer $l$, i.e., $\boldsymbol{h}^{l+1}_i = \gamma^l(\boldsymbol{h}^l_i, \boldsymbol{s}^l_i)$
-The end-to-end training requires $\phi^l$ and $\gamma^l$ (like multi-layer perceptrons and GRU) and $\Sigma_l$ (like mean, sum, element-wise min/max) are \emph{differentiable} to make the whole GNN differentiable.
+Briefly, the behaviour of a graph neuron under the message-passing model can be defined as
+
+\begin{equation}
+      \MyVec{h}^{l+1}_x = \gamma^l(\MyVec{h}^l_x, \mathlarger{\Sigma}^l_{v_y \in \MyVec{N}(v_x)}{\phi^l(\MyVec{h}^l_y, \MyVec{h}^l_x,   \MyVec{e}_{y,x}, \dots)}, \dots).
+\end{equation}
+
+%The three functions are small neural networks and parameterized with trainable weight vectors or matrices.
+The end-to-end training requires $\phi^l$ and $\gamma^l$ (like multi-layer perceptrons and GRUs) and $\Sigma^l$ (like mean, sum, element-wise min/max) are \emph{differentiable} to make the whole GNN differentiable.
 
 Different GNNs have different definitions of the three functions.
-We regard $\phi$ and $\Sigma$ as the \emph{edge calculation} functions, since they are conducted over every edge in $\mathcal{G}$.
+%
+We regard $\phi$ and $\Sigma$ as \emph{edge calculation} functions, since they are conducted over every edge in $\mathcal{G}$.
+%
 We regard $\gamma$ as the \emph{vertex calculation} function, as it is conducted over every vertex in $\mathcal{G}$.
-\tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge functions and the vertex functions of typical GNNs, respectively.
-For ChebNet, we report its GNN sub-layer in the tables.
-A ChebNet layer consists of $K$ GNN sub-layers and a summation layer:
-$\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with the GNN sub-layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}^l$, $\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}^l$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$, where $\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
-For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
-For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))$, and the other three sub-layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
+%
+\tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge calculation functions and the vertex calculation functions of typical GNNs, respectively.
 
-\begin{table}
-    \centering
+It is noteworthy that some complex GNNs like GAT, GaAN and ChebNet require more than one message passing phase in each GNN layer.
+%
+We regard every message passing phase in a GNN layer as a \emph{sub-layer}.
+%
+Take GAT \cite{huang2018_gat} as an example.
+%
+A GAT layer has two sub-layers and each sub-layer has $K$ heads under the multi-head attention mechanism.
+%
+For the GAT layer $l$, it first transforms every hidden vector received from the previous GAT layer $\boldsymbol{h}^l_x$ with a weight matrix $\textcolor{blue}{\boldsymbol{W}^{l}_{(k)}}$ for each head $k$ ($\parallel$ represents the concatenation operator):
+%
+\begin{equation}
+   \hvec{x} = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x, \quad \text{denoting } \hvec{x}[k]=\Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x.
+\end{equation}
+%
+The GAT layer $l$ then calculates the hidden vector $\MyVec{h}^{l,0}_x$ of every vertex $v_x$ in the first sub-layer as:
+%
+\newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}[k] \parallel \hvec{x}[k]]))}
+\begin{equation}
+    \begin{aligned}
+        \MyVec{m}^{l,0}_{y,x} & = \phi^{l,0}(\MyVec{h}^l_y, \MyVec{h}^l_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\GATCalcWeight, \\
+        \MyVec{s}^{l,0}_{x} &= \mathlarger{\Sigma}_{v_y \in \mathcal{N}(v_x)}{\MyVec{m}^{l,0}_{y,x}}, \\
+        \MyVec{h}^{l,0}_{x} &= \gamma^{l,0}(\MyVec{h}^l_x, \MyVec{s}^{l,0}_{x})  = \MyVec{s}^{l,0}_{x}.
+     \end{aligned}
+\end{equation}
+%
+$\MyVec{h}^{l,0}_x$ stores the sum of adjacent edge weights of all heads for $v_x$.
+%
+It is passed to the second sub-layer as ($\delta$ represents the activation function):
+%
+\begin{equation}
+    \begin{aligned}
+        \MyVec{m}^{l,1}_{y,x} &= \phi^{l,1}(\MyVec{h}^{l,0}_y, \MyVec{h}^{l,0}_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}[k], \\
+        \MyVec{s}^{l,1}_x &= \mathlarger{\Sigma}_{v_y \in \mathcal{N}(v_x)} \MyVec{m}^{l,1}_{y,x}, \\
+        \MyVec{h}^{l,1}_x &= \gamma^{l,1}(\MyVec{h}^{l,0}, \MyVec{s}^{l,1}_x) = \delta(\MyVec{s}^{l,1}_x).
+    \end{aligned}
+\end{equation}
+%
+In the GAT layer $l$, the graph neuron corresponding to $v_x$ first transforms the hidden vector of $v_x$ from the previous layer $\boldsymbol{h}^l_x$ with a weight matrix $\textcolor{blue}{\boldsymbol{W}^{l,k}}\boldsymbol{h}_x^l$.
+calculates the weight (i.e., attention) of every adjacent edge dynamically with
+
+%For ChebNet, we report its GNN sub-layer in the tables.
+%A ChebNet layer consists of $K$ GNN sub-layers and a summation layer:
+%$\boldsymbol{H}^{l+1} = \sum_{k=1}^K{\boldsymbol{Z}^{(k)} \textcolor{blue}{\boldsymbol{W}^{(k)}}}$ with the GNN sub-layers $\boldsymbol{Z}^{(1)}=\boldsymbol{H}^l$, %$\boldsymbol{Z}^{(2)}=\hat{\boldsymbol{L}}\boldsymbol{H}^l$, and $\boldsymbol{Z}^{(k)}=2\hat{\boldsymbol{L}}\boldsymbol{Z}^{(k-1)} - \boldsymbol{Z}^{(k-2)}$, where $\boldsymbol{H}^l$ is the matrix of output hidden feature vectors of the layer $l-1$.
+%For GAT, a GAT layer consists of two sub-layers and it conducts part of the vertex calculation before the two sub-layers.
+%For GaAN, a GaAN layer consists of four sub-layers: the first sub-layer calculates the summation $\boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))$, and the other three sub-layers calculate $\boldsymbol{m}^l_{j,i,1}$/$\boldsymbol{m}^l_{j,i,2}$/$\boldsymbol{m}^l_{j,i,3}$.
+
+\begin{table}[h]
+    \hspace{-2em}
     \begin{footnotesize}
-        \begin{tabular}{ccp{8em}p{22em}r}
+        \begin{tabular}{cccp{22em}r}
             \toprule
@@
             Type                                                                                                                      &
-            $\Sigma$                                                                                                                  &
-            $\phi$                                                                                                                    &
+            $\Sigma^l$                                                                                                                  &
+            $\phi^l(\MyVec{h}^{l}_y, \MyVec{h}^l_x, \MyVec{e}_{y,x}, \dots)$                                                                                                                    &
             Complexity                                                                                                                  \\ \midrule
@@
             sum                                                                                                                       &
-            $\boldsymbol{m}_{j, i}^{(k)} = e_{j, i}\boldsymbol{z}_j^{(k-1)}$                                                          &
+            $\boldsymbol{m}_{y, x}^{l} = \MyVec{e}_{y, x}\boldsymbol{h}^{l}_y$                                                          &
             $O(d_{in})$                                                                                                   \\
@@
             sum                                                                                                                       &
-            $\boldsymbol{m}_{j, i}^l = e_{j, i} \boldsymbol{h}_j^l$                                                                   &
+            $\boldsymbol{m}^l_{y, x} = \MyVec{e}_{y, x} \boldsymbol{h}^l_y$                                                                   &
             $O(d_{in})$                                                                                                                 \\
@@
             sum                                                                                                                       &
-            $\boldsymbol{m}_{j, i}^l = \tilde{e}_{j, i}^l \boldsymbol{h}_j^l$                                                         &
+            $\boldsymbol{m}^l_{y, x} = \tilde{e}^l_{y, x} \boldsymbol{h}^l_y$                                                         &
             $O(d_{in})$                                                                                                                 \\
@@
             mean/LSTM                                                                                                                 &
-            $\boldsymbol{m}_{j, i}^l =  \boldsymbol{h}_j^l$                                                                           &
+            $\boldsymbol{m}_{y, x}^l =  \boldsymbol{h}_y^l$                                                                           &
             $O(1)$                                                                                                                      \\
@@
             max                                                                                                                       &
-            $\boldsymbol{m}_{j, i}^l =  \delta(\textcolor{blue}{\boldsymbol{W}^l_{pool}} \boldsymbol{h}_j^l + \textcolor{blue}{b^l})$ &
+            $\MyVec{m}_{y, x}^l =  \delta(\Param{\MyMat{W}^l_{pool}} \MyVec{h}_y^l + \Param{b^l})$ &
             $O(d_{in} * d_{out})$                                                                                                       \\
@@
             sum                                                                                                                       &
-            $\boldsymbol{m}_{j, i}^l = \boldsymbol{h}_j^l$                                                                            &
+            $\boldsymbol{m}_{y, x}^l = \boldsymbol{h}_y^l$                                                                            &
             $O(1)$                                                                                                                      \\
@@
             sum                                                                                                                       &
-            $\boldsymbol{m}_{j, i}^l = [\boldsymbol{x}_j \parallel \boldsymbol{h}_j^l]$                                               &
+            $\boldsymbol{m}_{y, x}^l = \MyVec{v}_y \parallel \boldsymbol{h}_y^l$                                               &
             $O(f+d_{in})$                                                                                                               \\
@@
             sum                                                                                                                       &
-            $\boldsymbol{m}_{j, i} = \textcolor{blue}{\boldsymbol{W}^l} \boldsymbol{h}_j^l$                                           &
+            $\MyVec{m}^l_{y, x} = \Param{\MyMat{W}^l}\MyVec{h}^l_y$                                           &
             $O(d_{in} * d_{out})$                                                                                                       \\
@@
                          & \text{Sub-layer 0:}                                                                                                                                                                                    \\
-                         & \boldsymbol{m}^{l,0}_{j,i,(k)} = \exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j, (k)}]))                                    \\
-                         & \text{Sub-layer 1:}                                                                                                                                                                                    \\
-                         & \alpha^l_{j, i, (k)} = \frac {\exp(LeakyReLU(\textcolor{blue}{\boldsymbol{a}^T} [\hat{\boldsymbol{h}}^{l}_{i,(k)} \parallel \hat{\boldsymbol{h}}^{l}_{j,(k)}] ))} {\hat{\boldsymbol{a}}^{l,0}_{i,(k)}} \\
-                         & \text{Multi-head concatenation}: \boldsymbol{m}_{j, i}^{l,1} = \parallel_{k=1}^K \alpha^l_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)}                                                         \\
-                         & \text{Multi-head average}: \boldsymbol{m}_{j, i}^{l,1} = \frac{1}{K} \sum_{k=1}^K \alpha^l_{j, i, (k)} \hat{\boldsymbol{h}}^{l}_{j,(k)}
+                         & \MyVec{m}^{l,0}_{y,x}  = \parallel_{k=1}^{K}\GATCalcWeight                                    \\
+                         & \text{Sub-layer 1 (multi-head concatenation):}                                                                                                                                                                                    \\
+                         & \MyVec{m}^{l,1}_{y,x} = \parallel_{k=1}^{K}\frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}[k] \\
+                         & \text{Sub-layer 1 (multi-head average)}: \\
+                         & \boldsymbol{m}_{j, i}^{l,1} = \frac{1}{K}\sum_{k=1}^K \frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}[k]                                                         \\
                     \end{aligned}$
@@
                     \text{average: } O(K * d_{out}) & \\
-                    \text{Two sub-layers}           &
+                    \text{Two Sub-layers}           &
                 \end{aligned}
@@
             Attention                                                                                                                 &
-            sum,max,mean                                                                                                              &
+            \begin{scriptsize}\makecell[t]{Sub-layer 0: \\sum\\ Sub-layer 1:\\sum\\Sub-layer 2:\\max\\Sub-layer 3:\\mean}\end{scriptsize}                                                                                                              &
             \begin{scriptsize}
@@
                          & \text{Sub-layer 0:}                                                                                                                                                                                                                                                                  \\
-                         & \boldsymbol{m}_{j, i, (k)}^{l,0}  = \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))                                   \\
+                         & \boldsymbol{m}_{y, x}^{l,0}  =\parallel_{k=1}^K \exp((\Param{\MyMat{W}^{l}_{(k), 1}}\MyVec{h}_y^l + \Param{\MyVec{b}^{l}_{(k),1}})^T (\Param{\MyMat{W}^{l}_{(k), 2}}\MyVec{h}_x^l + \Param{\MyVec{b}^{l}_{(k),2}}))                                   \\
+%                         & \boldsymbol{m}_{j, i, (k)}^{l,0}  =\parallel_{k=1}^K \exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))                                   \\
                          & \text{Sub-layer 1:}                                                                                                                                                                                                                                                                  \\
-                         & \alpha^l_{j, i, (k)} = \frac {\exp((\textcolor{blue}{W^{l, k}_{xa}} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_{xa}})^T (\textcolor{blue}{\boldsymbol{W}^{l, k}_{ya}} \boldsymbol{h}_i^l + \textcolor{blue}{\boldsymbol{b}^{l,k}_{ya}}))} {\hat{\boldsymbol{a}}^{l, 0}_{i, (k)}} \\
-                         & \boldsymbol{m}_{j, i}^{l, 1} = \parallel_{k=1}^K \alpha_{j, i, (k)} LeakyReLU(\textcolor{blue}{\boldsymbol{W}^{l, k}_v} \boldsymbol{h}_j^l + \textcolor{blue}{b^{l, k}_v})                                                                                                           \\
+                         & \alpha_{(k)} = \frac {\exp((\Param{\MyMat{W}^{l}_{(k), 1}}\MyVec{h}_y^l + \Param{\MyVec{b}^{l}_{(k),1}})^T (\Param{\MyMat{W}^{l}_{(k), 2}}\MyVec{h}_x^l + \Param{\MyVec{b}^{l}_{(k),2}}))} {\MyVec{h}^{l,0}_{x}[k]} \\
+                         & \boldsymbol{m}_{y, x}^{l, 1} = \parallel_{k=1}^K \alpha_{(k)} LeakyReLU(\Param{\boldsymbol{W}^{l}_{(k),v}} \MyVec{h}_y^l + \Param{\MyVec{b}^{l}_{(k),v}})                                                                                                           \\
                          & \text{Sub-layer 2:}                                                                                                                                                                                                                                                                  \\
-                         & \boldsymbol{m}_{j, i}^{l, 2} = \textcolor{blue}{\boldsymbol{W}^l_m} \boldsymbol{h}_j^{l} + \textcolor{blue}{\boldsymbol{b}^l_m}                                                                                                                                                      \\
+                         & \boldsymbol{m}_{y, x}^{l, 2} = \Param{\MyMat{W}^l_m} \MyVec{h}_y^{l} + \Param{\MyVec{b}^l_m}                                                                                                                                                      \\
                          & \text{Sub-layer 3:}                                                                                                                                                                                                                                                                  \\
-                         & \boldsymbol{m}_{j, i}^{l, 3} = \boldsymbol{h}_j^l
+                         & \boldsymbol{m}_{y, x}^{l, 3} = \MyVec{h}_y^l
                     \end{aligned}$
             \end{scriptsize}                                                                                            &
-            \makecell[r]{$O(max(d_a, d_m, d_v) * K * d_{in})$                                                                           \\
-            Four sub-layers}                                                                                                            \\
+            \makecell[tr]{$O(\max(d_a, d_v, d_m) * K * d_{in})$                                                                           \\
+                Four Sub-layers \\ 
+                $\Param{\MyMat{W}^l_{(k),1}} \in \mathbb{R}^{d_a \times d_{in}}$ \\
+                $\Param{\MyMat{W}^l_{(k),v}} \in \mathbb{R}^{d_v \times d_{in}}$ \\
+                $\Param{\MyMat{W}^l_{m}} \in \mathbb{R}^{d_m \times d_{in}}$ 
+            }                                                                                                            \\
             \bottomrule
@@
     \caption{Typical graph neural networks and their edge calculation functions.
-        $d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
+        $d_{in}$ and $d_{out}$ are the dimensions of the input and output hidden vectors, respectively.
         Blue variables are model parameters to learn.
+        $\delta$ is the activation function.
     }
@@
     \begin{footnotesize}
-        \begin{tabular}{cp{20em}r}
+        \begin{tabular}{clr}
             \toprule
             GNN                                                                                                                                                                                                              &
-            $\gamma$                                                                                                                                                                                                         &
+            $\gamma^l(\boldsymbol{h}^l_x, \boldsymbol{s}^l_x, \dots)$                                                                                                                                                                                                         &
             Complexity                                                                                                                                                                                                         \\ \midrule
             ChebNet \cite{defferrad2016_chebnet}                                                                                                                                                                             &
-            $\boldsymbol{z}_i^{(k)} = 2\boldsymbol{s}^{(k)}_{i} - \boldsymbol{z}_i^{(k-2)}$                                                                                                                                  &
+            $\MyVec{h}_x^{l+1} = 2\boldsymbol{s}^{l}_{x} - \boldsymbol{h}_x^{l-1}$                                                                                                                                  &
             $O(d_{out})$                                                                                                                                                                                                       \\
             \textbf{GCN} \cite{kipf2017_gcn}                                                                                                                                                                                 &
-            $\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l  \boldsymbol{s}_i^{l}$                                                                                                                              &
+            $\boldsymbol{h}_x^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l  \boldsymbol{s}_x^{l}$                                                                                                                              &
             $O(d_{in} * d_{out})$                                                                                                                                                                                              \\
             AGCN   \cite{li2018_agcn}                                                                                                                                                                                        &
-            $\boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l  \boldsymbol{s}_i^{l}$                                                                                                                              &
+            $\boldsymbol{h}_x^{l+1} = \textcolor{blue}{\boldsymbol{W}}^l  \boldsymbol{s}_x^{l}$                                                                                                                              &
             $O(d_{in} * d_{out})$                                                                                                                                                                                              \\
             GraphSAGE  \cite{hamilton2017_graphsage}                                                                                                                                                                         &
-            $\boldsymbol{h}_i^{l+1} =   \delta(\textcolor{blue}{\boldsymbol{W}}^l  [\boldsymbol{s}_i^{l} \parallel \boldsymbol{h}_i^l])$                                                                                     &
+            $\boldsymbol{h}_x^{l+1} =   \delta(\textcolor{blue}{\boldsymbol{W}}^l  [\boldsymbol{s}_x^{l} \parallel \boldsymbol{h}_x^l])$                                                                                     &
             $O(d_{in} * d_{out})$                                                                                                                                                                                              \\
             GraphSAGE-pool   \cite{hamilton2017_graphsage}                                                                                                                                                                   &
-            $\boldsymbol{h}_i^{l+1} = \boldsymbol{s}_i^l$                                                                                                                                                                    &
+            $\boldsymbol{h}_x^{l+1} = \boldsymbol{s}_x^l$                                                                                                                                                                    &
             $O(1)$                                                                                                                                                                                                             \\
             Neural FPs        \cite{duvenaud2015_neural_fps}                                                                                                                                                                 &
-            $\boldsymbol{h}_i^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}  (\boldsymbol{h}_i^l + \boldsymbol{s}_i^{l}))$                                                                           &
+            $\boldsymbol{h}_x^{l+1} = \delta(\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(v_i)|}  (\boldsymbol{h}_x^l + \boldsymbol{s}_x^{l}))$                                                                           &
             $O(d_{in} * d_{out})$                                                                                                                                                                                              \\
             SSE             \cite{han2018_sse}                                                                                                                                                                               &
-            $\boldsymbol{h}_i^{l+1} = (1 - \alpha)  \boldsymbol{h}_i^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 [\boldsymbol{x}_i \parallel \boldsymbol{s}_i^l]))$ &
+            $\boldsymbol{h}_x^{l+1} = (1 - \alpha)  \boldsymbol{h}_x^l +\alpha    \delta(\textcolor{blue}{\boldsymbol{W}}^l_1 \delta(\textcolor{blue}{\boldsymbol{W}}^l_2 [\boldsymbol{v}_x \parallel \boldsymbol{s}_x^l]))$ &
             $O((f + d_{in}) * d_{out})$                                                                                                                                                                                        \\
@@
                 $\begin{aligned}[t]
-                         & {\boldsymbol{z}}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}^z} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}^{sz}} + \textcolor{blue}{\boldsymbol{U}^z} \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}^{hz}})                    \\
-                         & \boldsymbol{r}_i^l = \delta ( \textcolor{blue}{\boldsymbol{W}^r} \boldsymbol{s}_i^l+ \textcolor{blue}{\boldsymbol{b}^{sr}} +\textcolor{blue}{\boldsymbol{U}^r} \boldsymbol{h}_i^{l} + \textcolor{blue}{\boldsymbol{b}^{hr}})                        \\
-                         & \boldsymbol{h}_i^{l+1} = tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_i^l + \textcolor{blue}{\boldsymbol{b}^s} + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_i^l \odot \boldsymbol{h}_i^{l}) + \textcolor{blue}{\boldsymbol{b}^h})) \\
-                         & \boldsymbol{h}_i^{l+1} = (1 - {\boldsymbol{z}}_i^l) \odot \boldsymbol{h}_i^l + {\boldsymbol{z}}_i^l \odot \boldsymbol{h}_i^{l+1}
+                         & {\boldsymbol{z}}_x^l = \delta ( \textcolor{blue}{\boldsymbol{W}^z} \boldsymbol{s}_x^l + \textcolor{blue}{\boldsymbol{b}^{sz}} + \textcolor{blue}{\boldsymbol{U}^z} \boldsymbol{h}_x^{l} + \textcolor{blue}{\boldsymbol{b}^{hz}})                    \\
+                         & \boldsymbol{r}_x^l = \delta ( \textcolor{blue}{\boldsymbol{W}^r} \boldsymbol{s}_x^l+ \textcolor{blue}{\boldsymbol{b}^{sr}} +\textcolor{blue}{\boldsymbol{U}^r} \boldsymbol{h}_x^{l} + \textcolor{blue}{\boldsymbol{b}^{hr}})                        \\
+                         & \boldsymbol{\bar{h}}_x^{l+1} = \tanh ( \textcolor{blue}{\boldsymbol{W}} \boldsymbol{s}_x^l + \textcolor{blue}{\boldsymbol{b}^s} + \textcolor{blue}{\boldsymbol{U}} ( \boldsymbol{r}_x^l \odot \boldsymbol{h}_x^{l}) + \textcolor{blue}{\boldsymbol{b}^h}) \\
+                         & \boldsymbol{h}_x^{l+1} = (1 - {\boldsymbol{z}}_x^l) \odot \boldsymbol{h}_x^l + {\boldsymbol{z}}_x^l \odot \boldsymbol{\bar{h}}_x^{l+1}
                     \end{aligned}$
@@
                          & \text{Preprocessing:}                                                                          \\
-                         & \hat{\boldsymbol{h}}^{l}_{i,(k)} = \textcolor{blue}{\boldsymbol{W}^{l,k}} \boldsymbol{h}_i^{l} \\
+                         & \hat{\boldsymbol{h}}^{l}_{x} = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x \\
                          & \text{Sub-layer 0:}                                                                            \\
-                         & \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}                              \\
+                         & \MyVec{h}^{l,0}_{x} = \MyVec{s}^{l,0}_{x}                              \\
                          & \text{Sub-layer 1:}                                                                            \\
-                         & \boldsymbol{h}_i^{l+1} = \delta(\boldsymbol{s}_i^{l,1})
+                         & \boldsymbol{h}_x^{l+1} = \delta(\boldsymbol{s}_x^{l,1})
                     \end{aligned}
@@
                     \text{average:} O(K*d_{in}*d_{out}) & \\
-                    \text{Two sub-layers}               &
+                    \text{Two Sub-layers}               &
                 \end{aligned}
@@
                 $\begin{aligned}[t]
-                         & \text{Sub-layer 0:}                                                                                                                                                                            \\
-                         & \hat{\boldsymbol{a}}^{l,0}_{i,(k)} = \boldsymbol{s}^{l,0}_{i,(k)}                                                                                                                              \\
-                         & \text{After sub-layer 0,1,2,3:}                                                                                                                                                                      \\
-                         & \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{W}^l_g}[\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}] + \textcolor{blue}{\boldsymbol{b}^l_g} \\
-                         & \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{W}^l_o} [\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i}^l \odot \boldsymbol{s}_{i}^{l, 1})] + \textcolor{blue}{\boldsymbol{b}^l_o}
+                         & \text{Sub-layer 0/1/2:}                                                                                                                                                                            \\
+                         & \MyVec{h}^{l,*}_{x} = \MyVec{s}^{l,*}_{x}                                                                                                                              \\
+                         & \text{Sub-layer 3:}                                                                                                                                                                      \\
+                         & \boldsymbol{g}_x^l = \textcolor{blue}{\boldsymbol{W}^l_g}[\boldsymbol{h}_x^{l} \parallel \boldsymbol{h}_{x}^{l, 2} \parallel \boldsymbol{s}_{x}^{l, 3}] + \textcolor{blue}{\boldsymbol{b}^l_g} \\
+                         & \boldsymbol{h}_x^{l+1} = \textcolor{blue}{\boldsymbol{W}^l_o} [\boldsymbol{h}_x^l \parallel (\boldsymbol{g}_{x}^l \odot \boldsymbol{h}_{x}^{l, 1})] + \textcolor{blue}{\boldsymbol{b}^l_o}
                     \end{aligned}$
             \end{scriptsize}                                                                                                                                                                                   &
-            \makecell[r]{$O(max(K * d_v + d_{in}, 2 * d_{in} + d_m) * d_{out})$                                                                                                                                                \\
-                Four sub-layers}
+            \makecell[r]{$O(\max(K * d_v + d_{in}$, \\ $2 * d_{in} + d_m) * d_{out})$                                                                                                                                                \\
+                Four Sub-layers}
             \\ \bottomrule
@@
     \caption{Typical graph neural networks and their vertex calculation functions.
-        $d_{in}$ and $d_{out}$ are dimensions of the input and output hidden feature vectors, respectively.
+        $d_{in}$ and $d_{out}$ are the dimensions of the input and output hidden vectors, respectively.
         Blue variables are model parameters to learn.
-        In Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for vertices with degree $|\mathcal{N}(i)|$ at layer $l$.
+        In Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for vertices with degree $|\mathcal{N}(i)|$ at the layer $l$.
+        $\delta$ is the activation function.
     }

### 2020-12-18 NEUROC/sec2-review-of-graph-neural-network.tex
更新典型图神经网络介绍章节。

@@
         & $\gamma^l$ & The vertex updating function of the GNN layer $l$. \\ 
-        & $\phi^{l,i}$/$\Sigma^{l,i}$/$\gamma^{l,i}$ & The messaging/aggregation/updating function of the $i$-th sub-layer of the GNN layer  $l$.\\
+        & $\phi^{l,i}$ / $\Sigma^{l,i}$ / $\gamma^{l,i}$ & The messaging/aggregation/updating function of the $i$-th sub-layer of the GNN layer  $l$.\\
         & $\textcolor{blue}{\boldsymbol{W}^l, \boldsymbol{W}^{(k)}/\boldsymbol{b}, \boldsymbol{a}}$ & The matrices/vectors represented by the blue characters are the weight matrices/vectors that need to be learned in the GNN.
@@
         & $\boldsymbol{s}_{x}^l$ & The aggregated vector of the vertex $v_x$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
-        & $\boldsymbol{h}_{x}^{l,i}$/$\boldsymbol{m}_{x,y}^{l,i}$/$\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
+        & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{x,y}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
 \\
@@
 %
-For the graph neuron corresponding to $v_x$ at the layer $l$, it receives the hidden vector of itself $\boldsymbol{h}^l_x$ and the hidden vectors of its adjacent vertices $\boldsymbol{h}^l_y$ with $v_y \in \mathcal{N}(v_x)$ from the previous GNN layer\footnote{For the GNN layer 0, graph neurons receive input feature vectors, i.e., $\boldsymbol{h}^0_i=\boldsymbol{v}_i$}.
+For the graph neuron corresponding to $v_x$ at the layer $l$, it receives the hidden vector of itself $\boldsymbol{h}^l_x$ and the hidden vectors of its adjacent vertices $\boldsymbol{h}^l_y$ with $v_y \in \mathcal{N}(v_x)$ from the previous GNN layer\footnote{For the GNN layer 0, graph neurons receive input feature vectors, i.e., $\boldsymbol{h}^0_x=\boldsymbol{v}_x$}.
 %
@@
 \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} list the edge calculation functions and the vertex calculation functions of typical GNNs, respectively.
-
-It is noteworthy that some complex GNNs like GAT, GaAN and ChebNet require more than one message passing phase in each GNN layer.
+%
+Some complex GNNs like GAT \cite{huang2018_gat} and GaAN  \cite{zhang2018_gaan} use more than one message passing phase in each GNN layer.
 %
@@
 %
-Take GAT \cite{huang2018_gat} as an example.
-%
-A GAT layer has two sub-layers and each sub-layer has $K$ heads under the multi-head attention mechanism.
-%
-For the GAT layer $l$, it first transforms every hidden vector received from the previous GAT layer $\boldsymbol{h}^l_x$ with a weight matrix $\textcolor{blue}{\boldsymbol{W}^{l}_{(k)}}$ for each head $k$ ($\parallel$ represents the concatenation operator):
-%
-\begin{equation}
-   \hvec{x} = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x, \quad \text{denoting } \hvec{x}[k]=\Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x.
-\end{equation}
-%
-The GAT layer $l$ then calculates the hidden vector $\MyVec{h}^{l,0}_x$ of every vertex $v_x$ in the first sub-layer as:
-%
-\newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}[k] \parallel \hvec{x}[k]]))}
-\begin{equation}
-    \begin{aligned}
-        \MyVec{m}^{l,0}_{y,x} & = \phi^{l,0}(\MyVec{h}^l_y, \MyVec{h}^l_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\GATCalcWeight, \\
-        \MyVec{s}^{l,0}_{x} &= \mathlarger{\Sigma}_{v_y \in \mathcal{N}(v_x)}{\MyVec{m}^{l,0}_{y,x}}, \\
-        \MyVec{h}^{l,0}_{x} &= \gamma^{l,0}(\MyVec{h}^l_x, \MyVec{s}^{l,0}_{x})  = \MyVec{s}^{l,0}_{x}.
-     \end{aligned}
-\end{equation}
-%
-$\MyVec{h}^{l,0}_x$ stores the sum of adjacent edge weights of all heads for $v_x$.
-%
-It is passed to the second sub-layer as ($\delta$ represents the activation function):
-%
-\begin{equation}
-    \begin{aligned}
-        \MyVec{m}^{l,1}_{y,x} &= \phi^{l,1}(\MyVec{h}^{l,0}_y, \MyVec{h}^{l,0}_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}[k], \\
-        \MyVec{s}^{l,1}_x &= \mathlarger{\Sigma}_{v_y \in \mathcal{N}(v_x)} \MyVec{m}^{l,1}_{y,x}, \\
-        \MyVec{h}^{l,1}_x &= \gamma^{l,1}(\MyVec{h}^{l,0}, \MyVec{s}^{l,1}_x) = \delta(\MyVec{s}^{l,1}_x).
-    \end{aligned}
-\end{equation}
-%
-In the GAT layer $l$, the graph neuron corresponding to $v_x$ first transforms the hidden vector of $v_x$ from the previous layer $\boldsymbol{h}^l_x$ with a weight matrix $\textcolor{blue}{\boldsymbol{W}^{l,k}}\boldsymbol{h}_x^l$.
-calculates the weight (i.e., attention) of every adjacent edge dynamically with
+We will give out more details on sub-layers when we introduce GAT.
 
@@
 
-\begin{table}[h]
+\newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}[k] \parallel \hvec{x}[k]]))}
+
+\begin{table}[H]
     \hspace{-2em}
@@
 
-\begin{table}
+\begin{table}[H]
     \centering
@@
                          & \text{Sub-layer 1:}                                                                            \\
-                         & \boldsymbol{h}_x^{l+1} = \delta(\boldsymbol{s}_x^{l,1})
+                         & \boldsymbol{h}_x^{l+1} = \MyVec{h}^{l,1}_x = \delta(\boldsymbol{s}_x^{l,1})
                     \end{aligned}
@@
                          & \boldsymbol{g}_x^l = \textcolor{blue}{\boldsymbol{W}^l_g}[\boldsymbol{h}_x^{l} \parallel \boldsymbol{h}_{x}^{l, 2} \parallel \boldsymbol{s}_{x}^{l, 3}] + \textcolor{blue}{\boldsymbol{b}^l_g} \\
-                         & \boldsymbol{h}_x^{l+1} = \textcolor{blue}{\boldsymbol{W}^l_o} [\boldsymbol{h}_x^l \parallel (\boldsymbol{g}_{x}^l \odot \boldsymbol{h}_{x}^{l, 1})] + \textcolor{blue}{\boldsymbol{b}^l_o}
+                         & \boldsymbol{h}_x^{l+1} = \MyVec{h}^{l,3}_x = \textcolor{blue}{\boldsymbol{W}^l_o} [\boldsymbol{h}_x^l \parallel (\boldsymbol{g}_{x}^l \odot \boldsymbol{h}_{x}^{l, 1})] + \textcolor{blue}{\boldsymbol{b}^l_o}
                     \end{aligned}$
@@
 
-\subsection{Classification of GNNs}
+\subsection{Representative GNNs}
 
-Since we focus on analyzing the performance bottleneck in training GNNs, we classify the typical GNNs from the view of time complexity.
+%Since we focus on analyzing the performance bottleneck in training GNNs, we classify the typical GNNs from the view of time complexity.
 We use $O_\phi$/$O_\Sigma$/$O_\gamma$ to denote the time complexity of the three functions in the message-passing model.
-The time complexity of a GNN layer is made up of two parts: the edge calculation complexity $m * (O_\phi$ + $O_\Sigma)$ and the vertex calculation complexity $n * O_\gamma$.
-
-In \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we list the edge and vertex calculation complexity, respectively.
+The time complexity of a GNN layer is made up of two parts: the edge calculation complexity $O_\phi$ + $O_\Sigma$ and the vertex calculation complexity $O_\gamma$.
+%
+In \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we list the edge and vertex calculation complexity of each GNN, respectively.
 The time complexity of a graph neuron is affected by the dimensions of the input/output hidden vectors $d_{in}$ and $d_{out}$ and the dimensions of the model parameters (like the number of heads $K$ in GAT and the dimensions of the view vectors $d_a$/$d_v$/$d_m$ in GaAN).
 
-We classify the typical GNNs into four quadrants based on their edge/vertex complexity as shown in \figurename~\ref{fig:gnn_complexity_quadrant}.
-We pick GCN, GGNN, GAT, and GaAN as the \emph{representative GNNs} of the four quadrants.
+Since we focus on analyzing the performance bottleneck in training GNNs, we classify the typical GNNs into four quadrants based on their edge/vertex complexity as shown in \figurename~\ref{fig:gnn_complexity_quadrant}.
+We pick GCN, GGNN, GAT, and GaAN as the \emph{representative} GNNs of the four quadrants.
 
-\begin{figure}
+\begin{figure}[h]
     \centering
@@
 
-\textbf{GCN} (low vertex \& edge calculation complexity): Graph convolution network (GCN \cite{kipf2017_gcn}) introduces the first-order approximation of the spectral-based graph convolutions.
-%By combining the advantages of both the spectral-based and the spatial-based convolution, it can learn the representation of the local topological structure and vertex features efficiently.
-It has only one parameter to learn at each layer, i.e. the weight matrix $\boldsymbol{W}^l$ in $\gamma$.
-A GCN graph neuron can be expressed as $\boldsymbol{h}^{l+1}_i = \boldsymbol{W}^l\sum_{v_j \in \mathcal{N}(v_i)}{e_{j,i}\boldsymbol{h}^l_j}$, where $e_{j,i}$ is the normalized weight of the edge $(v_j, v_i)$.
-%In the matrix view, $\boldsymbol{H}^{l+1} = (\boldsymbol{A}\boldsymbol{H}^l)\boldsymbol{W}^l$.
-According to the associative law of the matrix multiplication, $\boldsymbol{h}^{l+1}_i = \sum_{v_j \in \mathcal{N}(v_i)}{e_{j,i}\boldsymbol{W}^l\boldsymbol{h}^l_j}$.
-Since the dimension of $\boldsymbol{h}^{l+1}_i$ is usually smaller than $\boldsymbol{h}^l_i$ in practical GCNs, the implementation of GCN in PyTorch Geometric chooses to first conduct the vertex calculation $\hat{\boldsymbol{h}}^l_j = \boldsymbol{W}^l\boldsymbol{h}^l_j$ for each vertex $v_j$ and then conduct the edge calculation $\boldsymbol{h}^{l+1}_i=\sum_{v_j\in\mathcal{N}(v_i)}{e_{j,i}\hat{\boldsymbol{h}}^l_j}$.
-As $\hat{\boldsymbol{h}}^l_j$ has the same dimension as $\boldsymbol{h}^{l+1}_i$, the implementation significantly reduces the  computation cost of the edge calculation.
+\subsubsection{GCN (Low Vertex \& Low Edge Complexity)}
 
-\textbf{GGNN} (high vertex \& low edge calculation complexity):
-GGNN \cite{li2015_ggnn} introduces the gated recurrent unit (GRU) into the graph neural networks.
-The vertex updating function $\phi$ of GGNN is a modified GRU unit that has 12 model parameters to learn, having high computational complexity.
+Graph convolution network (GCN \cite{kipf2017_gcn}) introduces the first-order approximation of the spectral-based graph convolutions into graph neural networks.
+%
+It has only one parameter to learn at each layer, i.e. the weight matrix $\Param{\MyMat{W}^l}$ in the updating function $\gamma^l$.
+%
+A GCN graph neuron can be expressed as $\boldsymbol{h}^{l+1}_x = \Param{\MyMat{W}^l}\sum_{v_y \in \mathcal{N}(v_x)}{w_{y,x}\boldsymbol{h}^l_y}$, where $w_{y,x}$ is the normalized weight of the edge $e_{y,x}$.
+%
+According to the associative law of the matrix multiplication, $\boldsymbol{h}^{l+1}_x = \sum_{v_y \in \mathcal{N}(v_x)}{w_{y,x}\Param{\MyMat{W}^l}\boldsymbol{h}^l_y}$.
+%
+Since the dimension of $\boldsymbol{h}^{l+1}_x$ is usually smaller than $\boldsymbol{h}^l_x$ in practical GCNs, the implementation of GCN in PyG chooses to first conduct the vertex calculation $\hat{\boldsymbol{h}}^l_y = \Param{\MyMat{W}^l}\boldsymbol{h}^l_y$ for each vertex $v_y$ and then conduct the edge calculation $\boldsymbol{h}^{l+1}_x=\sum_{v_y\in\mathcal{N}(v_x)}{w_{y,x}\hat{\boldsymbol{h}}^l_y}$.
+%
+As $\hat{\boldsymbol{h}}^l_y$ has the same dimension as $\boldsymbol{h}^{l+1}_x$, the implementation significantly reduces the  computation cost of the edge calculation.
+
+\subsubsection{GGNN (High Vertex \& Low Edge Complexity)}
+
+GGNN \cite{li2015_ggnn} introduces the gated recurrent unit (GRU) into graph neural networks.
+%
+The updating function $\phi^l$ of GGNN is a modified GRU unit that has 12 model parameters to learn, having high computational complexity.
+%
 To lower the training cost, all GNN layers share the same group of parameters in GGNN.
+%
 GGNN further requires the dimension of $\boldsymbol{h}^{l+1}$ is equal to the dimension of $\boldsymbol{h}^l$.
-Since the messaging function $\phi$ only uses the hidden feature vector $\boldsymbol{h}^l_j$ of the source vertex $v_j$ of an edge $(v_j, v_i)$.
-In the implementation of PyG, GGNN conducts the pre-processing vertex calculation $\hat{\boldsymbol{h}}^l_i=\boldsymbol{W}\boldsymbol{h}^l_i$ for every vertex $v_i$ before the message-passing.
-The messaging function $\phi$ directly uses $\hat{\boldsymbol{h}}^l_j$ as the message vector for the edge $(v_j, v_i)$.
+%
+Since the messaging function $\phi^l$ only uses the hidden vector $\boldsymbol{h}^l_y$ of the source vertex $v_y$ for an edge $e_{y,x}$, in the implementation of PyG, GGNN conducts the pre-processing vertex calculation $\hat{\boldsymbol{h}}^l_x = \Param {\MyMat{W}^l}\boldsymbol{h}^l_x$ for every vertex $v_x$ before the message passing.
+%
+The messaging function $\phi^l$ directly uses $\hat{\boldsymbol{h}}^l_y$ as the message vector for every edge $e_{y, x}$.
+%
 In this way, GGNN further reduces the time complexity of the edge calculation to $O(1)$ without increasing the time complexity of the vertex calculation.
 
-\textbf{GAT} (low vertex \& high edge calculation complexity):
-GAT \cite{huang2018_gat} introduces the attention and multi-head mechanism into the graph neural networks.
-The $K$ heads generate $K$ independent views for an edge, where $K$ is a hyper-parameter.
+\subsubsection{GAT (Low Vertex \& High Edge Complexity)}
+
+GAT \cite{huang2018_gat} introduces the multi-head attention mechanism into graph neural networks.
+%
+Each GAT layer has $K$ heads that generate $K$ independent views for an edge, where $K$ is a hyper-parameter.
+%
 The views of $K$ heads can be merged by concatenating or by averaging.
-For concatenating, the dimension of the hidden feature vector of each head $d_{head}$ is $d_{out}/K$.
-For averaging, $d_{head}$ is $d_{out}$, multiplying the complexity by $K$.
-Each GAT layer consists of a preprocessing step and two sub-layers.
-In the preprocessing step, GAT calculates the attention vectors $\hat{\boldsymbol{h}}^{l}_{i,(k)}$ for every vertex $v_i$ in every head $k$.
-The first sub-layer uses the attention vectors to calculate the attention weights of every edge in every head $\boldsymbol{m}^{l,0}_{j,i,(k)}$.
-After aggregation, the first sub-layer gets the summation of attention weights of every vertex in every head $\hat{\boldsymbol{a}}^{l,0}_{i,(k)}$.
-The second sub-layer calculates the normalized attention weights $\alpha_{j, i, (k)}$ for every edge in every head and aggregates the hidden feature vectors with the normalized weights in the message-passing.
-GAT uses the aggregated vector $\boldsymbol{s}^{l,1}_i$ of the second sub-layer as the output hidden vector directly.
+%
+For concatenating, the dimension of the hidden vector of each head $d_{head}$ is $d_{out}/K$.
+%
+For averaging, $d_{head}$ is $d_{out}$.
 
-\textbf{GaAN} (high vertex \& edge calculation complexity):
+Each GAT layer consists of a vertex pre-processing phase and two sub-layers.
+
+The vertex pre-processing phase calculates the attention vector $\hat{\boldsymbol{h}}^{l}_{x}$ for every vertex $v_x$ by $\hvec{x} = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
+We denote the attention sub-vector generated by the $k$-th head as $\hvec{x}[k]=\Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
+
+The two sub-layers also follow the message-passing model.
+The first sub-layer (defined in Equation~\ref{eq:GAT-sub-layer-1}) uses the attention vectors to emit the attention weight vector for every edge $\boldsymbol{m}^{l,0}_{y,x}$ and aggregates the attention weight vectors for every vertex $v_x$ to get the weight sum vector $\MyVec{h}^{l,0}_x$.
+%
+\begin{equation}
+    \label{eq:GAT-sub-layer-1}
+    \begin{aligned}
+        \MyVec{m}^{l,0}_{y,x} & = \phi^{l,0}(\MyVec{h}^l_y, \MyVec{h}^l_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\GATCalcWeight, \\
+        \MyVec{s}^{l,0}_{x} &= \mathlarger{\Sigma}_{v_y \in \mathcal{N}(v_x)}{\MyVec{m}^{l,0}_{y,x}}, \\
+        \MyVec{h}^{l,0}_{x} &= \gamma^{l,0}(\MyVec{h}^l_x, \MyVec{s}^{l,0}_{x})  = \MyVec{s}^{l,0}_{x}.
+    \end{aligned}
+\end{equation}
+%
+The second sub-layer (defined in Equation~\ref{eq:GAT-sub-layer-2}) uses the weight sum vectors to normalize the attention weights for every edge and aggregates the attention vectors $\boldsymbol{\hat{h}}^l_y$ with the normalized weights.
+%
+The aggregated attention vectors $\MyVec{s}^{l,1}_x$ are transformed by an activation function $\delta$ and outputted as the hidden vectors of the current layer $\MyVec{h}^{l+1}_x$.
+%
+\begin{equation}
+        \label{eq:GAT-sub-layer-2}
+    \begin{aligned}
+        \MyVec{m}^{l,1}_{y,x} &= \phi^{l,1}(\MyVec{h}^{l,0}_y, \MyVec{h}^{l,0}_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}[k], \\
+        \MyVec{s}^{l,1}_x &= \mathlarger{\Sigma}_{v_y \in \mathcal{N}(v_x)} \MyVec{m}^{l,1}_{y,x}, \\
+        \MyVec{h}^{l+1}_x = \MyVec{h}^{l,1}_x &= \gamma^{l,1}(\MyVec{h}^{l,0}, \MyVec{s}^{l,1}_x) = \delta(\MyVec{s}^{l,1}_x).
+    \end{aligned}
+\end{equation}
+
+\subsubsection{GaAN (High Vertex \& High Edge Complexity)}
+
 Based on the multi-head mechanism, GaAN \cite{zhang2018_gaan} introduces a convolutional subnetwork to control the weight of each head.
-Each GaAN layer consists of four sub-layers. The first two sub-layers are similar to GAT, and the last two sub-layers build the convolutional subnetwork.
-The first sub-layer aims to get the summation of attention weights of every vertex in each head $\boldsymbol{\hat{a}}^{l,0}_{j, i, (k)}$.
-The second sub-layer aggregates the feature vectors with the normalized attention weights $\boldsymbol{\hat{a}}^{l,0}_{i,(k)}$.
-The third and fourth sub-layers aggregate feature vectors with element-wise max and element-wise mean operators separately.
-After the four sub-layers, the vertex updating funciton uses the aggregated vectors of last three sub-layers $\boldsymbol{s}^{l, 1}_i, \boldsymbol{s}^{l, 2}_i, \boldsymbol{s}^{l, 3}_i$ to generate the output hidden vector $\boldsymbol{h}^{l+1}_i$
+%
+Each GaAN layer consists of four sub-layers (as defined in Table~\ref{tab:gnn_overview_edge} and Table~\ref{tab:gnn_overview_vertex}).
+%
+The first two sub-layers are similar to GAT, and the last two sub-layers build the convolutional subnetwork.
+%
+The first sub-layer aims to get the sum of attention weights of every vertex in all heads $\MyVec{h}^{l,0}_x$.
+The second sub-layer aggregates the hidden vectors from the previous GaAN layer with the normalized attention weights for all heads $\alpha_{(k)}$.
+The third and fourth sub-layers aggregate the hidden vectors from the GaAN previous layer with the element-wise max and mean operators separately.
+The vertex updating funciton $\gamma^{l,4}$ of the fourth sub-layer uses the hidden vectors of the last two sub-layers $\MyVec{h}^{l, 1}_x, \MyVec{h}^{l, 2}_x$ to generate the output hidden vector $\MyVec{h}^{l+1}_x$.
 

### 2020-12-18 NEUROC/sec2-review-of-graph-neural-network.tex
统一论文中的符号使用。

@@
         & $e_{x,y}$ & The edge pointing from $v_x$ to $v_y$ of the input graph. \\
-        & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ \midrule
+        & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ 
+        & $\bar{d}$ & The average degree of the input graph. \\ \midrule
         \multirow[c]{6}{3em}{GNN Definition}& $L$ & The number of GNN layers. \\
@@
 \\  \midrule
-        \multirow[c]{8}{3em}{Vectors}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
+        \multirow[c]{8}{3em}{Vector}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
         & $\boldsymbol{e}_{x,y}$ & The feature vector of the edge $e_{x,y}$.  \\
@@
 \\
-        & $d_{in}$, $d_{out}$ &  The dimensions of the input/output hidden vectors of a graph neuron. \\
+        & $d^l_{in}$, $d^l_{out}$ &  The dimensions of the input/output hidden vectors of the GNN layer $l$. \\
+        & $dim(\MyVec{x})$ & The dimension of a vector $\MyVec{x}$. \\
         \bottomrule
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{figs/illustration/GNN_complexity_quadrant.pdf}
-    \caption{Complexity quadrants of typical GNNs. We compare the complexity according to the number of sub-layers, the Big-O notation and the number of parameters to train.}
+    \includegraphics[width=0.8\columnwidth]{figs/illustration/GNN_complexity_quadrant.pdf}
+    \caption{Complexity quadrants of typical GNNs. We compare the complexity according to the number of sub-layers, the Big-O notation, and the number of parameters to train.}
     \label{fig:gnn_complexity_quadrant}
@@
 Then it repeatedly samples the neighbors of those sampled vertices in the previous layer until the input layer.
-For every sampled vertex $v_i$ in the GNN layer $l$, GraphSAGE samples at most $S^l$ neighbors of $v_i$ in the previous GNN layer.
+For every sampled vertex $v_x$ in the GNN layer $l$, GraphSAGE samples at most $S^l$ neighbors of $v_x$ from the previous GNN layer.
 $S^l$ is the hyper-parameter that is usually much smaller than $|\mathcal{V}|$.
@@
 Given a training graph $\mathcal{G}$, it partitions $\mathcal{G}$ into dense clusters.
-For each mini-batch, it randomly pick $K$ clusters to form the sampled subgraph, where $K$ is the hyper-parameter.
+For each mini-batch, it randomly pick $N$ clusters to form the sampled subgraph, where $N$ is the hyper-parameter.

### 2020-12-18 NEUROC/sec3-experiment-design.tex
增加了Motivation各个数据集的代码
统一论文中的符号使用。

--- 2020-09-07 CCPE/Mauscript/sec3-experiment-design.tex
@@
 \paragraph{Experimental Environment}
-All the experiments were conducted in a CentOS 7 Linux server with kernel version 3.10.0.
+All the experiments were conducted in a CentOS 7 server with the Linux kernel version 3.10.0.
 The server had 40 cores and 90 GB main memory.
@@
 For the software environment, we adopted Python 3.7.7, PyTorch 1.5.0, and CUDA 10.1.
-We implemented all the GNNs with PyTorch Geometric 1.5.0.
+We implemented all the GNNs with PyG 1.5.0.
 
@@
 We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in the experiments, to explore the effects of graph topological characteristics (like the average degree) on the performance bottleneck.
-Input feature vectors of random graphs were random dense vectors with a dimension of 32.
+Input feature vectors of random graphs were random dense vectors with the dimension of 32.
 Vertices of random graphs were classified into 10 classes randomly.
@@
         \toprule
-        Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $dim(\boldsymbol{x})$ & \#Class & Directed \\
+        Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $dim(\boldsymbol{v})$ & \#Class & Directed \\
         \midrule
@@
     \end{tabular}
-    \caption{Dataset overview. $\bar{d}$ represents the average vertex degree. $dim(\boldsymbol{x})$ is the dimension of the input feature vector.}
+    \caption{Dataset overview. $\bar{d}$ represents the average vertex degree. $dim(\boldsymbol{v})$ is the dimension of the input feature vector.}
     \label{tab:dataset_overview}
@@
 \paragraph{GNN Implementation}
-We implemented the four typical GNNs (GCN, GGNN, GAT, GaAN) with PyTorch Geometric 1.5.0.
+We implemented the four typical GNNs (GCN, GGNN, GAT, GaAN).
 To compare the performance characteristics of four GNNs side-by-side, we used a unified GNN structure for them: Input Layer $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ Softmax Layer (to prediction).
-The structure was popular in the experimental evaluation of GCN \cite{kipf2017_gcn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan}.
-Since a GGNN layer requires the input and output hidden feature vectors have the same dimension, we added two multi-layer perceptron(MLP) layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
+The structure was popular in the experimental evaluation of GCN \cite{kipf2017_gcn}, GAT \cite{huang2018_gat}, and GaAN \cite{zhang2018_gaan}.
+Since a GGNN layer requires the input and output hidden vectors have the same dimension, we added two multi-layer perceptron (MLP) layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
 We stored the dataset and the model parameters on the GPU side.
-All the training was conducted on the GPU.
+All the training was conducted on the GPU side.
 
 \paragraph{Hyper-parameters}
-We use $dim(\boldsymbol{v})$ to denote the dimension of a vector $\boldsymbol{v}$.
+We use $dim(\boldsymbol{x})$ to denote the dimension of a vector $\boldsymbol{x}$.
 We picked the hyper-parameters of GNNs according to their popularity in the original papers.
-We used the same set of hyper-parameters for all the datasets. 
-Some hyper-parameters like the dimensions of hidden feature vectors were common in the four GNNs and we set them to the same values.
-For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_i = \boldsymbol{x}_i$, $dim(\boldsymbol{h}^1_i)=64$, and $dim(\boldsymbol{h}^2_i)=\#Classes$.
+Unless otherwise mentioned, we used the same set of hyper-parameters for all the datasets. 
+Some hyper-parameters like the dimensions of hidden vectors were common in the four GNNs and we set them to the same values.
+For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_x = \boldsymbol{v}_x$, $dim(\boldsymbol{h}^1_x)=64$, and $dim(\boldsymbol{h}^2_x)=\#Classes$.
 For GAT, we set the hyper-parameters according to its paper\cite{huang2018_gat}.
-The first GAT layer had 8 heads with the dimension of each head $d^0_{head}=8$. The first GAT layer merged the heads by concatenating.
-The second GAT layer used a single head with the dimension $d^1_{head}=d^1_{out}=\#Classes$.
-For GGNN, since it uses extra MLP layers to transform the dimensions of the input/output feature vectors, we set $dim(\boldsymbol{h}^0_i) = dim(\boldsymbol{h}^1_i) = dim(\boldsymbol{h}^2_i) = 64$.
+The first GAT layer had 8 heads with the dimension of 8. The first GAT layer merged the heads by concatenating.
+The second GAT layer used a single head with the dimension of the number of classes of the dataset.
+For GGNN, since it uses extra MLP layers to transform the dimensions of the input/output feature vectors, we set $dim(\boldsymbol{h}^0_x) = dim(\boldsymbol{h}^1_x) = dim(\boldsymbol{h}^2_x) = 64$.
 We used 8 heads in the both GaAN layers with $d_a=d_v=8$ and $d_m=64$.
@@
 
-We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical sampling techniques respectively.
-For the neighbor sampler, we set the neighborhood sample sizes as 25 for GNN Layer 1, and 10 for GNN Layer 0 and set the default batch size as 512 from its paper\cite{hamilton2017_graphsage}.
+We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical sampling techniques, respectively.
+%
+For the neighbor sampler, we set the neighborhood sample sizes as 25 for GNN Layer 1 and 10 for GNN Layer 0.
+%
+We set the default batch size as 512 from its paper\cite{hamilton2017_graphsage}.
+%
 For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to the parameters used in its paper\cite{chiang2019_cluster_gcn}.

### 2020-12-18 NEUROC/sec4-experiments.tex
增加了Motivation各个数据集的代码
统一论文中的符号使用。

@@
 The ranking of the training time is GaAN $\gg$ GAT $>$ GGNN $>$ GCN in all cases.
-Since the real-world graphs have more edges than edges ($m > n$), the time complexity of the edge calculation stage affects more than the vertex calculation stage.
+Since the real-world graphs have more edges than edges ($|\mathcal{E}| > |\mathcal{V}|$), the time complexity of the edge calculation stage affects more than the vertex calculation stage.
 The ranking is consistent with the time complexity analysis.
@@
 
-Since $dim(\boldsymbol{h^0})$ and $dim{\boldsymbol{h^1}}$ are determined by the dataset with $dim(\boldsymbol{h}^0=dim(\boldsymbol{x}))$ and $dim(\boldsymbol{h}^2)=\#Classes$,
-for GCN and GGNN, the only modifiable hyper-parameter is the hidden dimension $dim(\boldsymbol{h}^1)$ with $dim(\boldsymbol{h}^1) = d^0_{out} = d^1_{in}$.
-According to the time complexity analysis, if we fix other hyper-parameters but only increase $dim(\boldsymbol{h}^1)$, the computing costs of the GNN layer 0 and the GNN layer 1 both increase linearly with $dim(\boldsymbol{h}^1)$, causing the training time of the whole GNN also increasing linearly.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn} show that the training time of GCN and GGNN increased linearly with $dim(\boldsymbol{h}^1)$ when $dim(\boldsymbol{h}^1)$ is big, consistent with the time complexity analysis.
+$dim(\MyVec{h^0})$ and $dim(\MyVec{h}^1)$ are solely determined by the dataset with $d^0_{in} = dim(\MyVec{h}^0_x) = dim(\MyVec{v_x})$ and $d^1_{out} = dim(\boldsymbol{h}^2_x)=\#Class$.
+%
+For GCN and GGNN, the only modifiable hyper-parameter is the dimension of the hidden vectors $dim(\boldsymbol{h}^1_x)$ that are both the output hidden vectors for the GNN layer 0 and the input hidden vector for the GNN layer 1.
+%
+According to the time complexity analysis, if we fix other hyper-parameters but only increase $dim(\boldsymbol{h}^1_x)$, the computational costs of the GNN layer 0 and the GNN layer 1 both increase linearly with $dim(\boldsymbol{h}^1_x)$, causing the training time of the whole GNN also increasing linearly.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn} show that the training time of GCN and GGNN increased linearly with $dim(\boldsymbol{h}^1_x)$ when $dim(\boldsymbol{h}^1_x)$ is big, consistent with the time complexity analysis.
 
 For GAT, we modify the number of heads $K$ and the dimension of each head $d_{head}$ in the GAT layer 0.
-The dimension of the hidden feature vector is determined correspondingly as $d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1) = K d_{head}$.
-Thus, the computing costs of the GAT layer 0 and the GAT layer 1 increase linearly with K and $d_{head}$ separately. 
+The dimension of the hidden vectors $dim(\MyVec{h}^1_x)$ is determined as $dim(\boldsymbol{h}^1_x) = K d_{head}$.
+Thus, the computational costs of the GAT layer 0 and the GAT layer 1 should increase linearly with $K$ and $d_{head}$, separately. 
 \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} confirms the theoretical analysis.
@@
 For GaAN, it is also based on the multi-head mechanism.
-Its time complexity is affected by $dim(\boldsymbol{h}^1)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1)$), $d_a$, $d_v$, $d_m$ and the number of heads $K$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time increases linearly with the hyper-parameters, except for $dim(\boldsymbol{h}^1)$.
-As $dim(\boldsymbol{h}^1)$ increases, the training time increases first slightly and then linearly.
-We observe similar phenomena in GCN, GGNN, and GAT with low hyper-parameters.
-When the hyper-parameters is too low, the GNN training cannot make full use of the computing power of the GPU.
-When the hyper-parameter becomes high enough, the training time increases linearly, supporting the time complexity analysis.
+Its time complexity is affected by $dim(\boldsymbol{h}^1_x)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1_x)$), $d_a$, $d_v$, $d_m$, and the number of heads $K$.
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time increases linearly with the hyper-parameters, except for $dim(\boldsymbol{h}^1_x)$.
+As $dim(\boldsymbol{h}^1_x)$ increases, the training time increases first slightly and then linearly.
+We observe similar phenomena in GCN, GGNN, and GAT with low hyper-parameter values.
+When the values of hyper-parameters are too low, the GNN training cannot make full use of the computing power of the GPU.
+When the values of hyper-parameters become high enough, the training time increases linearly, supporting the time complexity analysis.
 
@@
 We further measured the effects of the hyper-parameters on the peak GPU memory usage in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
-The memory usage also increases linearly as the hyper-parameters increase for all GNNs, except for GaAN on $dim(\boldsymbol{h}^1)$.
-As the hidden feature vectors $\boldsymbol{h}^1$ consume a small proportion of memory in GaAN, the growth in the memory usage is not noticeable until $dim(\boldsymbol{h}^1)$ is large enough.
+The memory usage also increases linearly as the hyper-parameters increase for all GNNs, except for GaAN on $dim(\boldsymbol{h}^1_x)$.
+As the hidden vectors $\boldsymbol{h}^1_x$ consume a small proportion of memory in GaAN, the growth in the memory usage is not noticeable until $dim(\boldsymbol{h}^1_x)$ is large enough.
 
@@
 In those GNNs, the dimensions of the input/output feature vectors in the layer 0 are much larger than the dimensions in the layer 1.
-$d^0_{in}=dim(\boldsymbol{x})$, $d^0_{out}=d^1_{in}=64$ and $d^1_{out}=\#Class$ and $dim(\boldsymbol{x}) \gg \#Class$.
+$d^0_{in}=dim(\boldsymbol{v}_x)$, $d^0_{out}=d^1_{in}=64$ and $d^1_{out}=\#Class$ and $dim(\boldsymbol{v}_x) \gg \#Class$.
 For GaAN, since it requires the dimensions of the input/output feature vectors must be the same, the hyper-parameter are $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers is close.
@@
 In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collection, messaging, aggregation, and updating, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
-The edge index is a matrix with $M$ rows and 2 columns that holds the edge set of the graph, where $M=|\mathcal{E}|$.
+The edge index is a matrix with $|\mathcal{E}|$ rows and 2 columns that holds the edge set of the graph.
 The two columns of the matrix store the source vertex and the target vertex of each edge, respectively.

### 2020-12-19 main_memory.py
update

@@ -1,5 +1,5 @@
 """
-跟main.py相比为full文件的对比版本
+超参数对精度的影响实验代码
 """
 import torch
 import torch.nn.functional as F
@@ -16,14 +16,14 @@ from gat.models import GAT
 from gcn.models import GCN
 from sklearn.metrics import f1_score
 from utils import get_dataset, get_split_by_file, nvtx_push, nvtx_pop, log_memory, small_datasets
+from logger import Logger
 
 parser = argparse.ArgumentParser()
 parser.add_argument('--dataset', type=str, default='cora', help="dataset: [cora, flickr, com-amazon, reddit, com-lj,"
                                                                     "amazon-computers, amazon-photo, coauthor-physics, pubmed]")
-
 parser.add_argument('--model', type=str, default='gcn', help="gnn models: [gcn, ggnn, gat, gaan]")
-parser.add_argument('--runs', type=int, default=10, help="total runs")
-parser.add_argument('--epochs', type=int, default=100000, help="epochs for training")
+parser.add_argument('--runs', type=int, default=1, help="total runs")
+parser.add_argument('--epochs', type=int, default=50, help="epochs for training")
 parser.add_argument('--layers', type=int, default=2, help="layers for hidden layer")
 parser.add_argument('--hidden_dims', type=int, default=64, help="hidden layer output dims")
 parser.add_argument('--heads', type=int, default=8, help="gat or gaan model: heads")
@@ -40,8 +40,6 @@ parser.add_argument('--lr', type=float, default=0.01, help="adam's learning rate
 parser.add_argument('--weight_decay', type=float, default=0.0005, help="adam's weight decay")
 parser.add_argument('--no_record_shapes', action='store_false', default=True, help="nvtx or autograd's profile to record shape")
 parser.add_argument('--json_path', type=str, default='', help="json file path for memory")
-parser.add_argument('--fix_time', type=int, default=800, help="fix_time")
-
 
 args = parser.parse_args()
 gpu = not args.cpu and torch.cuda.is_available()
@@ -124,47 +122,78 @@ print(model)
 # set to gpu
 model, data = model.to(device), data.to(device)
 
+log_memory(flag, device, 'data load')
+
 def train(epoch):
+    t = time.time()
+
[…]

### 2020-12-19 main_sampling_batch_acc_cum_fix_batch.py

@@ -174,13 +174,11 @@ def train(optimizer, t0, bs_count, best_val_acc, test_acc):
             
             # 指定batch size下，进行汇报时间和精度
             bs_count += 1
-            if bs_count % 10 == 0:
-                accs = test()
-                if accs[1] > best_val_acc:
-                    best_val_acc = accs[1]
-                    test_acc = max(test_acc, accs[2])
-                print(f"Batch: {bs_count:03d}, train_acc: {accs[0]:.8f}, val_acc: {accs[1]:.8f}, best_val_acc: {best_val_acc: .8f}, best_test_acc: {test_acc:.8f}, cur_use_time: {(time.time() - t0):.4f}s")
-                
+            accs = test()
+            if accs[1] > best_val_acc:
+                best_val_acc = accs[1]
+                test_acc = accs[2]
+            print(f"Batch: {bs_count:03d}, loss:{loss.item():.8f}, train_acc: {accs[0]:.8f}, val_acc: {accs[1]:.8f}, best_val_acc: {best_val_acc: .8f}, best_test_acc: {test_acc:.8f}, cur_use_time: {cur_use_time:.4f}s")
             if bs_count == 1000:
                 sys.exit(0)
         except StopIteration:

### 2020-12-19 main_sampling_batch_acc_cum_fix_epoch.py

@@ -170,18 +170,15 @@ def train(optimizer, t0, bs_count, best_val_acc, test_acc):
             
             loss.backward()
             optimizer.step()
-            
-            print(f"Batch: {bs_count:03d}, train_loss: {loss:.8f}, train_time: {(time.time() - t1): .4f}s")
-            
+                        
             # 指定batch size下，进行汇报时间和精度
             bs_count += 1
-            if bs_count % 10 == 0:
-                accs = test()
-                if accs[1] > best_val_acc:
-                    best_val_acc = accs[1]
-                    test_acc = max(test_acc, accs[2])
-                print(f"Batch: {bs_count:03d}, train_acc: {accs[0]:.8f}, val_acc: {accs[1]:.8f}, best_val_acc: {best_val_acc: .8f}, best_test_acc: {test_acc:.8f}, cur_use_time: {(time.time() - t0):.4f}s")
-        except StopIteration:
+            accs = test()
+            if accs[1] > best_val_acc:
+                best_val_acc = accs[1]
+                test_acc = accs[2]
+            print(f"Batch: {bs_count:03d}, loss:{loss.item():.8f}, train_acc: {accs[0]:.8f}, val_acc: {accs[1]:.8f}, best_val_acc: {best_val_acc: .8f}, best_test_acc: {test_acc:.8f}, cur_use_time: {cur_use_time:.4f}s")
+    except StopIteration:
             break
     return bs_count, best_val_acc, test_acc
 

### 2020-12-19 main_sampling_batch_acc_cum_fix_time.py

@@ -28,7 +28,7 @@ parser.add_argument('--dataset', type=str, default='cora', help="dataset: [cora,
 
 parser.add_argument('--model', type=str, default='gcn', help="gnn models: [gcn, ggnn, gat, gaan]")
 parser.add_argument('--runs', type=int, default=1, help="total runs")
-parser.add_argument('--epochs', type=int, default=1000, help="epochs for training")
+parser.add_argument('--epochs', type=int, default=100000, help="epochs for training")
 parser.add_argument('--layers', type=int, default=2, help="layers for hidden layer")
 parser.add_argument('--hidden_dims', type=int, default=64, help="hidden layer output dims")
 parser.add_argument('--heads', type=int, default=8, help="gat or gaan model: heads")
@@ -170,21 +170,17 @@ def train(optimizer, t0, bs_count, best_val_acc, test_acc):
             
             loss.backward()
             optimizer.step()
-            
-            print(f"Batch: {bs_count:03d}, train_loss: {loss:.8f}, train_time: {(time.time() - t1): .4f}s")
-            
             # 指定batch size下，进行汇报时间和精度
             bs_count += 1
-            if bs_count % 10 == 0:
-                accs = test()
-                if accs[1] > best_val_acc:
-                    best_val_acc = accs[1]
-                    test_acc = max(test_acc, accs[2])
-                cur_use_time = time.time() - t0
-                print(f"Batch: {bs_count:03d}, train_acc: {accs[0]:.8f}, val_acc: {accs[1]:.8f}, best_val_acc: {best_val_acc: .8f}, best_test_acc: {test_acc:.8f}, cur_use_time: {cur_use_time:.4f}s")
-            
-                if cur_use_time > args.fix_time:
-                    sys.exit(0)   
+            accs = test()
+            if accs[1] >= best_val_acc:
+                best_val_acc = accs[1]
+                test_acc = accs[2]
+            cur_use_time = time.time() - t0
+            print(f"Batch: {bs_count:03d}, loss:{loss.item():.8f}, train_acc: {accs[0]:.8f}, val_acc: {accs[1]:.8f}, best_val_acc: {best_val_acc: .8f}, best_test_acc: {test_acc:.8f}, cur_use_time: {cur_use_time:.4f}s")
+        
+            if cur_use_time > args.fix_time:
+                sys.exit(0)   
         except StopIteration:
             break
     return bs_count, best_val_acc, test_acc

### 2020-12-19 main_sampling_memory.py

@@ -49,6 +49,7 @@ flag = not args.json_path == ''
 
 print(args)
 print(time.strftime('%Y-%m-%d %H:%M:%S', time.localtime(time.time())))
+device = torch.device(f'cuda: {args.gpu}' if gpu else 'cpu') # todo: model's device
 
 # 0. set manual seed
 np.random.seed(args.seed)
@@ -66,12 +67,12 @@ data = dataset[0]
 
 # add train, val, test split
 if args.dataset in ['amazon-computers', 'amazon-photo', 'coauthor-physics']:
-    file_path = osp.join("/data/wangzhaokang/wangyunpan", "data/" + args.dataset + "/raw/role.json")
+    file_path = osp.join("/home/wangzhaokang/wangyunpan/gnns-project/datasets", args.dataset + "/raw/role.json")
     data.train_mask, data.val_mask, data.test_mask = get_split_by_file(file_path, data.num_nodes)
 
 num_features = dataset.num_features
 if dataset_info[0] in small_datasets and len(dataset_info) > 1:
-    file_path = osp.join("/data/wangzhaokang/wangyunpan", "data/feats_x/" + '_'.join(dataset_info) + '_feats.npy')
+    file_path = osp.join("/home/wangzhaokang/wangyunpan/gnns-project/datasets", "data/feats_x/" + '_'.join(dataset_info) + '_feats.npy')
     if osp.exists(file_path):
         data.x = torch.from_numpy(np.load(file_path)).to(torch.float) # 因为这里是随机生成的，不考虑normal features
         num_features = data.x.size(1)
@@ -114,19 +115,19 @@ if args.model == 'gcn':
     model = GCN(
         layers=args.layers,
         n_features=num_features, n_classes=dataset.num_classes,
-        hidden_dims=args.hidden_dims, gpu=gpu, flag=flag, norm=norm, cluster_flag=args.mode == 'cluster'
+        hidden_dims=args.hidden_dims, gpu=gpu, flag=flag, norm=norm, device=device, cluster_flag=args.mode == 'cluster'
     )
 elif args.model == 'gat':
     model = GAT(
         layers=args.layers,
         n_features=num_features, n_classes=dataset.num_classes,
-        head_dims=args.head_dims, heads=args.heads, gpu=gpu, flag=flag
+        head_dims=args.head_dims, heads=args.heads, gpu=gpu, flag=flag, device=device
     )
 elif args.model == 'ggnn':
     model = GGNN(
         layers=args.layers,
[…]

### 2020-12-19 paper_exp1_super_parameters/gaan_memory.sh

@@ -24,7 +24,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_${hd}_64.json" ]; then # 断点续传
                 continue
             fi
-            python ../main.py --json_path "${dir_config}/config0_${model}_${data}_4_${hd}_64.json" --dataset ${data} --model ${model} --d_v ${hd} --d_a ${hd} --d_m ${hd} --heads 4 --hidden_dims 64
+            python ../main_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_4_${hd}_64.json" --dataset ${data} --model ${model} --d_v ${hd} --d_a ${hd} --d_m ${hd} --heads 4 --hidden_dims 64
         done
 
         # hidden_dims
@@ -35,7 +35,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_32_${hd}.json" ]; then # 断点续传
                 continue
             fi
-            python ../main.py --json_path "${dir_config}/config0_${model}_${data}_4_32_${hd}.json" --dataset ${data} --model ${model} --hidden_dims ${hd} --heads 4 --d_v 32 --d_a 32 --d_m 32
+            python ../main_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_4_32_${hd}.json" --dataset ${data} --model ${model} --hidden_dims ${hd} --heads 4 --d_v 32 --d_a 32 --d_m 32
         done
         
         # heads
@@ -46,7 +46,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_${h}_32_64.json" ]; then # 断点续传
                 continue
             fi
-            python ../main.py --json_path "${dir_config}/config0_${model}_${data}_${h}_32_64.json" --dataset ${data} --model ${model} --d_m 32 --d_v 32 --d_a 32 --heads ${h} --hidden_dims 64
+            python ../main_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_${h}_32_64.json" --dataset ${data} --model ${model} --d_m 32 --d_v 32 --d_a 32 --heads ${h} --hidden_dims 64
         done
     done
 done

### 2020-12-19 paper_exp1_super_parameters/gat_memory.sh

@@ -7,7 +7,7 @@ then
 fi
 
 datasets=(amazon-photo pubmed amazon-computers coauthor-physics flickr com-amazon)
-models=(gat gaan)
+models=(gat)
 hds=(8 16 32 64 128 256)
 heads=(1 2 4 8 16)
 
@@ -22,7 +22,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_${hd}.json" ]; then # 断点续传
                 continue
             fi
-            python ../main.py --dataset ${data} --model ${model} --head_dims ${hd} --d_v ${hd} --d_a ${hd} --heads 4 --json_path "${dir_config}/config0_${model}_${data}_4_${hd}.json"
+            python ../main_memory.py --device cuda:0 --dataset ${data} --model ${model} --head_dims ${hd} --d_v ${hd} --d_a ${hd} --heads 4 --json_path "${dir_config}/config0_${model}_${data}_4_${hd}.json"
         done
         for h in ${heads[@]}
         do
@@ -31,7 +31,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_${h}_32.json" ]; then # 断点续传
                 continue
             fi
-            python ../main.py --dataset ${data} --model ${model} --head_dims 32 --d_v 32 --d_a 32 --heads ${h} --json_path "${dir_config}/config0_${model}_${data}_${h}_32.json"
+            python ../main_memory.py --device cuda:0 --dataset ${data} --model ${model} --head_dims 32 --d_v 32 --d_a 32 --heads ${h} --json_path "${dir_config}/config0_${model}_${data}_${h}_32.json"
         done
     done
 done

### 2020-12-19 paper_exp1_super_parameters/gcn_ggnn_memory.sh

@@ -22,7 +22,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_${hd}.json" ]; then # 断点续传
                 continue
             fi
-            python ../main.py --dataset ${data} --model ${model} --json_path "${dir_config}/config0_${model}_${data}_${hd}.json" --epochs 5 --hidden_dims ${hd}
+            python ../main_memory.py --device cuda:0 --dataset ${data} --model ${model} --json_path "${dir_config}/config0_${model}_${data}_${hd}.json" --epochs 5 --hidden_dims ${hd}
         done
     done
 done

### 2020-12-19 paper_exp1_super_parameters/run_device_0.sh

@@ -1,2 +1,4 @@
-echo "run_gaan"
-bash gaan_exp_acc.sh
+echo "run_gat"
+bash gat_memory.sh >gat_memory.log 2>&1 
+echo "run_gcn_ggnn"
+bash gcn_ggnn_memory.sh >gcn_ggnn_memory.log 2>&1

### 2020-12-19 paper_exp1_super_parameters/run_device_1.sh

@@ -1,7 +1,2 @@
-# echo "run_gcn_ggnn"
-# date
-# bash gcn_ggnn_exp_acc.sh
-# echo "run_gat"
-# bash gat_exp_acc.sh
-# date
-bash gaan_exp_acc_2.sh
+# echo "run_gaan"
+bash gaan_memory.sh >gaan_memory.log 2>&1

### 2020-12-19 paper_exp4_relative_sampling/sampling_batch_memory.py

@@ -3,7 +3,7 @@ import time
 
 small_datasets =  ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr', 'com-amazon']
 
-algs = ['gaan']
+algs = ['gcn', 'ggnn', 'gat']
 cluster_batchs = [15, 45, 90, 150, 375, 750]
 
 graphsage_batchs = {

### 2020-12-19 paper_exp6_sampling_acc/handle_sampling_acc_fix_time.py

@@ -89,8 +89,7 @@ for data in datasets:
                                 df_accs[xticklabels[i]].append(float(match_line.group(1)))
                                 df_times[xticklabels[i]].append(float(match_line.group(2)))
             
-            # full 
-                              
+            # full    
             # 画精度关于时间的图像
             fig, ax = plt.subplots()
             ax.set_ylabel('Accucary')
@@ -111,4 +110,3 @@ for data in datasets:
             plt.close()    
             
 
-    

### 2020-12-19 paper_exp6_sampling_acc/sampling_acc_fix_time.py

@@ -38,7 +38,7 @@ fix_times = {
     'amazon-computers': 1400
 }
 
-dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "log_fix_time")
+dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "log_fix_time_new")
 if not os.path.exists(dir_path):
     os.makedirs(dir_path)
 
@@ -75,6 +75,6 @@ for i, mode in enumerate(['cluster', 'graphsage']):
                 full_log = os.path.join(dir_path, '_'.join([mode, alg, data, 'full']) + '.log')
                 full_sh = f"python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_full_batch_acc_cum.py --runs 1 --epochs 1000 --mode {mode} --model {alg} --data {data} --device cuda:{i} {config_str} >>{full_log} 2>&1"
                 sh_commands.append(full_sh)
-    with open("sh_" + mode + "_fix_time.sh", "w") as f:
+    with open("sh_" + mode + "_fix_time_new.sh", "w") as f:
         for sh in sh_commands:
             f.write(sh + '\n')

### 2020-12-19 paper_exp6_sampling_acc/save_full_acc.py

@@ -1,0 +1,106 @@
+import re
+import os, sys
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+plt.style.use("ggplot")
+plt.rcParams["font.size"] = 12
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+modes = ["cluster", "graphsage"]
+algs = ["gcn", "ggnn", "gat", "gaan"]
+datasets = ["amazon-photo", "coauthor-physics", "amazon-computers", "pubmed", "flickr"]
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+    'com-amazon': 'cam'
+}
+
+xticklabels = [1, 3, 6, 10, 25, 50]
+
+dir_in = "log_fix_time_new"
+dir_out = "res_fix_time_new"
+
+if not os.path.exists(dir_out + "/res_csv"):
+    os.makedirs(dir_out + "/res_csv")
+        
+def get_full_acc():
+    df = {}
+    for alg in algs:
+        df[alg] = {}
+        for data in datasets:
+            final_acc = 0.0
+            print("\n")
+            for mode in modes:
+                file_name = dir_in + "/" + mode + "_" + alg + "_" + data + "_full.log"
+                print(file_name)
+                with open(file_name) as f:
+                    for line in f:
+                        match_line = re.match(r"Batch: .*,.*best_test_acc: (.*), cur_use_time:.*", line)
+                        if match_line:
+                            acc = float(match_line.group(1))
+                final_acc += acc
+            final_acc /= 2
+            df[alg][data] = final_acc
+    pd.DataFrame(df).to_csv(dir_out + "/res_csv/full_acc.csv")
+
+
+for mode in modes:
+    for alg in algs:
+        df_accs= {}
+        for data in datasets:
[…]

### 2020-12-19 paper_exp6_sampling_acc/sh_cluster_fix_time_new.sh

@@ -1,0 +1,140 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 15 --hidden_dims 64 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_new/cluster_gcn_amazon-photo_15.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 45 --hidden_dims 64 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_new/cluster_gcn_amazon-photo_45.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 90 --hidden_dims 64 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_new/cluster_gcn_amazon-photo_90.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode cluster --model gcn --data amazon-photo --device cuda:0 --batch_partitions 150 --hidden_dims 64 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_new/cluster_gcn_amazon-photo_150.log 2>&1
[…]

### 2020-12-19 paper_exp6_sampling_acc/sh_graphsage_fix_time_new.sh

@@ -1,0 +1,140 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 77 --hidden_dims 64 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_new/graphsage_gcn_amazon-photo_77.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 230 --hidden_dims 64 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_new/graphsage_gcn_amazon-photo_230.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 459 --hidden_dims 64 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_new/graphsage_gcn_amazon-photo_459.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode graphsage --model gcn --data amazon-photo --device cuda:1 --batch_size 765 --hidden_dims 64 --fix_time 1000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_new/graphsage_gcn_amazon-photo_765.log 2>&1
[…]

### 2020-12-19 paper_exp7_inference_sampling/inference_sampling_memory.py

@@ -15,7 +15,7 @@ for alg in algs:
         if os.path.exists(file_path):
             continue
         print(file_path)
-        cmd = "python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model {} --data {} --epochs 10 --infer_json_path {}"
+        cmd = "python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model {} --data {} --epochs 10 --infer_json_path {}"
         sh_commands.append(cmd.format(alg, data, file_path))
 
 with open("inference_sampling_memory.sh", "w") as f:

### 2020-12-19 paper_exp7_inference_sampling/inference_sampling_memory.sh

@@ -1,4 +1,6 @@
-python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model gcn --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gcn_com-amazon.json
-python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model ggnn --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/ggnn_com-amazon.json
-python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model gat --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gat_com-amazon.json
-python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:1 --model gaan --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gaan_com-amazon.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model ggnn --data amazon-photo --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/ggnn_amazon-photo.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model ggnn --data pubmed --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/ggnn_pubmed.json
[…]

### 2020-12-19 NEUROC/Response-MajRev/response_letter.tex
回复R1Q1.

--- 2020-12-15 NEUROC/Response-MajRev/response_letter.tex
@@
 \usepackage{times}
+\usepackage{amsmath, amsthm, amsfonts}
+\usepackage{booktabs}
+\usepackage{makecell}
+\usepackage{multirow}
+\usepackage{lscape}
+\usepackage{xcolor}
+\usepackage{float}
+% Vector
+\newcommand{\MyVec}[1]{\boldsymbol{#1}}
+% Matrix
+\newcommand{\MyMat}[1]{\boldsymbol{#1}}
+% Vectors with hat
+\newcommand{\hvec}[1]{\hat{\boldsymbol{h}}_{#1}}
+% Model parameters
+\newcommand{\Param}[1]{\textcolor{blue}{#1}}
 
@@
 \begin{reply}
-	TODO
+    We apologize for the confusing use of symbols.
+    %
+    To clarify the symbol usage, we have checked the manuscript and unified the usage of symbol.
+    %
+    We avoid the problem of reusing symbols, so that each symbol only represents one meaning after the revision.
+    %
+    We summarize the frequently-used symbols in Table 1 in the revised manuscript.
+    %
+    We quote the table below:
+    \begin{table}[H]
+        \footnotesize
+        \centering
+    \begin{tabular}{p{3em}lp{35em}}
+        \toprule
+        Category & Symbol & Meaning \\
+        \midrule
+        \multirow[c]{4}{3em}{Graph Structure}& $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ & The simple undirected input graph with the vertex set $\mathcal{V}$ and the edge set $\mathcal{E}$. \\
+        & $v_x$ & The $x$-th vertex of the input graph. \\
+        & $e_{x,y}$ & The edge pointing from $v_x$ to $v_y$ of the input graph. \\
+        & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ 
+        & $\bar{d}$ & The average degree of the input graph. \\ \midrule
+        \multirow[c]{6}{3em}{GNN Definition}& $L$ & The number of GNN layers. \\
+        & $K$ & The number of heads in a GNN layer. \\
+        & $\phi^l$ & The messaging function of the GNN layer $l$. \\
+        & $\Sigma^l$ & The aggregation function of the GNN layer $l$. \\
+        & $\gamma^l$ & The vertex updating function of the GNN layer $l$. \\ 
+        & $\phi^{l,i}$ / $\Sigma^{l,i}$ / $\gamma^{l,i}$ & The messaging/aggregation/updating function of the $i$-th sub-layer of the GNN layer  $l$.\\
+        & $\textcolor{blue}{\boldsymbol{W}^l, \boldsymbol{W}^{(k)}/\boldsymbol{b}, \boldsymbol{a}}$ & The matrices/vectors represented by the blue characters are the weight matrices/vectors that need to be learned in the GNN.
+\\  \midrule
+        \multirow[c]{8}{3em}{Vector}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
+        & $\boldsymbol{e}_{x,y}$ & The feature vector of the edge $e_{x,y}$.  \\
+        & $\boldsymbol{h}_x^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$. \\
+        & $\boldsymbol{h}_x^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$.\\
+        & $\boldsymbol{m}_{x,y}^l$ & The message vector of the edge $e_{x,y}$ outputted by $\phi^l$ of the GNN layer $l$. \\
+        & $\boldsymbol{s}_{x}^l$ & The aggregated vector of the vertex $v_x$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
+        & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{x,y}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
+\\
+        & $d^l_{in}$, $d^l_{out}$ &  The dimension of the input/output hidden vectors of the GNN layer $l$. \\
+        & $dim(\MyVec{x})$ & The dimension of a vector $\MyVec{x}$. \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+    In the revised manuscript, we use $e_{x,y}$ to represent an edge and use $\boldsymbol{e}_{x,y}$ to represent its input feature vector.
+    %
+    The input feature vectors of all edges are same for all GNN layers.
+    %
+    We use $\boldsymbol{s}$ to represent aggregated vectors outputted by the aggregation function $\Sigma$ in graph neurons.
+    %
+    For every vertex $v_x$, we use $\boldsymbol{s}^l_x$ to denote its aggregated vector in the GNN layer $l$.
+    %
+    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents its aggregated vector in the $i$-th sub-layer.
+
+    To clarify the concept of \emph{sub-layers} in a GNN layer, we have added more description on it in the revised manuscript.
+    %
+    We first introduce the concept of sub-layer in Section 2.2 ``Graph Neuron and Message-passing Model'' as:
+    %
+    \begin{quote}
+        Some complex GNNs like GAT [6] and GaAN [7] use more than one message passing phase in each GNN layer.
+        %
+        We regard every message passing phase in a GNN layer as a \emph{sub-layer}.
+        %
+        We will give out more details on sub-layers when we introduce GAT.
+    \end{quote}
+    %
+    We then use GAT as an example to elaborate on the concept of sub-layers in Section 2.3 ``Representative GNNs'' as:
+    %
+    \begin{quote}
+        \newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}[k] \parallel \hvec{x}[k]]))}
+        Each GAT layer consists of a vertex pre-processing phase and two sub-layers (i.e., message-passing phases).
+
+        The vertex pre-processing phase calculates the attention vector $\hat{\boldsymbol{h}}^{l}_{x}$ for every vertex $v_x$ by $\hvec{x} = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
+We denote the attention sub-vector generated by the $k$-th head as $\hvec{x}[k]=\Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
+
+        The first sub-layer of GAT (defined in Equation~\ref{eq:GAT-sub-layer-1}) uses the attention vectors to emit the attention weight vector $\boldsymbol{m}^{l,0}_{y,x}$ for every edge $e_{y,x}$ and aggregates the attention weight vectors for every vertex $v_x$ to get the weight sum vector $\MyVec{h}^{l,0}_x$.
+        %
+        \begin{equation}
+            \footnotesize
+            \label{eq:GAT-sub-layer-1}
+            \begin{aligned}
+                \MyVec{m}^{l,0}_{y,x} & = \phi^{l,0}(\MyVec{h}^l_y, \MyVec{h}^l_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\GATCalcWeight, \\
+                \MyVec{s}^{l,0}_{x} &= {\Sigma}_{v_y \in \mathcal{N}(v_x)}{\MyVec{m}^{l,0}_{y,x}}, \\
+                \MyVec{h}^{l,0}_{x} &= \gamma^{l,0}(\MyVec{h}^l_x, \MyVec{s}^{l,0}_{x})  = \MyVec{s}^{l,0}_{x}.
+            \end{aligned}
+        \end{equation}
+        %
+        The second sub-layer of GAT (defined in Equation~\ref{eq:GAT-sub-layer-2}) uses the weight sum vectors to normalize the attention weights for every edge and aggregates the attention vectors $\boldsymbol{\hat{h}}^l_y$ with the normalized weights.
+        %
+        The aggregated attention vectors $\MyVec{s}^{l,1}_x$ are transformed by an activation function $\delta$ and are outputted as the hidden vectors of the current layer $\MyVec{h}^{l+1}_x$.
+        %
+        \begin{equation}
+            \footnotesize
+            \label{eq:GAT-sub-layer-2}
+            \begin{aligned}
+                \MyVec{m}^{l,1}_{y,x} &= \phi^{l,1}(\MyVec{h}^{l,0}_y, \MyVec{h}^{l,0}_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}[k], \\
+                \MyVec{s}^{l,1}_x &= {\Sigma}_{v_y \in \mathcal{N}(v_x)} \MyVec{m}^{l,1}_{y,x}, \\
+                \MyVec{h}^{l+1}_x = \MyVec{h}^{l,1}_x &= \gamma^{l,1}(\MyVec{h}^{l,0}, \MyVec{s}^{l,1}_x) = \delta(\MyVec{s}^{l,1}_x).
+            \end{aligned}
+        \end{equation}
+    \end{quote}  
 \end{reply}
@@
          The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks [8, 9, 10] (like node classification and link prediction) but also computer vision tasks (like human-object interaction [11], human parsing [12], and video object segmentation [13]).
-
     \end{quote}
@@
 
-\subsection*{Minor}
+\begin{point}
+There are some grammar errors and typos:
+\\
+  - `Take the demo GNN in Figure 1(a) as  the example.'
+\\
+ - `to calculate the  output hidden vector $h^{l+1}$ of the current layer l, i.e., $h^{l+1}$ = $\gamma^l(h^l,s^l)$ The end-to-end training requires…'
+\\
+ - `Implementing it with the specially optimized basic operators on the GPU is a potential optimization'
+\\
+ - The sentences in the experimental section should be unified.\\
+\end{point}
 
-% Use the short-hand macros for one-liners.
-\shortpoint{ Typo in line xy. }
-\shortreply{ Fixed.}
+\begin{reply}
+Thank you for pointing them out.
+%
+We have proofread our revised manuscript carefully to eliminate grammar errors and typos.
+%
+We have also unified the sentences that describe the experimental results  in the experimental section in the past tense.
+\end{reply}
 

### 2020-12-19 NEUROC/sec2-review-of-graph-neural-network.tex
回复R1Q1.

@@
 \\
-        & $d^l_{in}$, $d^l_{out}$ &  The dimensions of the input/output hidden vectors of the GNN layer $l$. \\
+        & $d^l_{in}$, $d^l_{out}$ &  The dimension of the input/output hidden vectors of the GNN layer $l$. \\
         & $dim(\MyVec{x})$ & The dimension of a vector $\MyVec{x}$. \\
         \bottomrule
-
     \end{tabular}
@@
     %
-    Take the demo GNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as the example.
+    Take the demo GNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as an example.
     %
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
     \centering
@@
             sum                                                                                                                       &
-            $\MyVec{m}^l_{y, x} = \Param{\MyMat{W}^l}\MyVec{h}^l_y$                                           &
+            $\MyVec{m}^l_{y, x} = \MyVec{\hat{h}}^l_y$                                           &
             $O(d_{in} * d_{out})$                                                                                                       \\
@@
                 $\begin{aligned}[t]
+                         & \text{Preprocessing: } \MyVec{\hat{h}}^l_x = \Param {\MyMat{W}^l}\boldsymbol{h}^l_x; \\
                          & {\boldsymbol{z}}_x^l = \delta ( \textcolor{blue}{\boldsymbol{W}^z} \boldsymbol{s}_x^l + \textcolor{blue}{\boldsymbol{b}^{sz}} + \textcolor{blue}{\boldsymbol{U}^z} \boldsymbol{h}_x^{l} + \textcolor{blue}{\boldsymbol{b}^{hz}})                    \\
@@
                 $\begin{aligned}[t]
-                         & \text{Preprocessing:}                                                                          \\
-                         & \hat{\boldsymbol{h}}^{l}_{x} = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x \\
+                         & \text{Preprocessing: } \hat{\boldsymbol{h}}^{l}_{x} = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x;        \\
                          & \text{Sub-layer 0:}                                                                            \\
@@
 %
-Since the messaging function $\phi^l$ only uses the hidden vector $\boldsymbol{h}^l_y$ of the source vertex $v_y$ for an edge $e_{y,x}$, in the implementation of PyG, GGNN conducts the pre-processing vertex calculation $\hat{\boldsymbol{h}}^l_x = \Param {\MyMat{W}^l}\boldsymbol{h}^l_x$ for every vertex $v_x$ before the message passing.
+Since the messaging function $\phi^l$ only uses the hidden vector $\boldsymbol{h}^l_y$ of the source vertex $v_y$ for an edge $e_{y,x}$, in the implementation of PyG, GGNN conducts the pre-processing vertex calculation $\MyVec{\hat{h}}^l_x = \Param {\MyMat{W}^l}\boldsymbol{h}^l_x$ for every vertex $v_x$ before the message passing.
 %
-The messaging function $\phi^l$ directly uses $\hat{\boldsymbol{h}}^l_y$ as the message vector for every edge $e_{y, x}$.
+The messaging function $\phi^l$ directly uses $\MyVec{\hat{h}}^l_y$ as the message vector for every edge $e_{y, x}$.
 %
@@
 
-Each GAT layer consists of a vertex pre-processing phase and two sub-layers.
+Each GAT layer consists of a vertex pre-processing phase and two sub-layers (i.e., message-passing phases).
 
@@
 
-The two sub-layers also follow the message-passing model.
-The first sub-layer (defined in Equation~\ref{eq:GAT-sub-layer-1}) uses the attention vectors to emit the attention weight vector for every edge $\boldsymbol{m}^{l,0}_{y,x}$ and aggregates the attention weight vectors for every vertex $v_x$ to get the weight sum vector $\MyVec{h}^{l,0}_x$.
+The first sub-layer of GAT (defined in Equation~\ref{eq:GAT-sub-layer-1}) uses the attention vectors to emit the attention weight vector $\boldsymbol{m}^{l,0}_{y,x}$ for every edge $e_{y,x}$ and aggregates the attention weight vectors for every vertex $v_x$ to get the weight sum vector $\MyVec{h}^{l,0}_x$.
 %
@@
 %
-The second sub-layer (defined in Equation~\ref{eq:GAT-sub-layer-2}) uses the weight sum vectors to normalize the attention weights for every edge and aggregates the attention vectors $\boldsymbol{\hat{h}}^l_y$ with the normalized weights.
+The second sub-layer of GAT (defined in Equation~\ref{eq:GAT-sub-layer-2}) uses the weight sum vectors to normalize the attention weights for every edge and aggregates the attention vectors $\boldsymbol{\hat{h}}^l_y$ with the normalized weights.
 %
-The aggregated attention vectors $\MyVec{s}^{l,1}_x$ are transformed by an activation function $\delta$ and outputted as the hidden vectors of the current layer $\MyVec{h}^{l+1}_x$.
+The aggregated attention vectors $\MyVec{s}^{l,1}_x$ are transformed by an activation function $\delta$ and are outputted as the hidden vectors of the current layer $\MyVec{h}^{l+1}_x$.
 %

### 2020-12-19 NEUROC/sec3-experiment-design.tex
回复R1Q1.

@@
 We design a series of experiments to explore the performance bottleneck in training graph neural networks.
-We first introduce the experimental setting in Section~\ref{sec:experimental_env} and then give out our experimental scheme in Section~\ref{sec:experimental_scheme}.
+We first introduce our experimental setting in Section~\ref{sec:experimental_env} and then give out our experimental scheme in Section~\ref{sec:experimental_scheme}.
 The evaluation results are presented and analyzed later in Section~\ref{sec:experiment_results}.
@@
 The server had 40 cores and 90 GB main memory.
-The server was equipped with an NVIDIA Tesla T4 GPU with 16GB GDDR6 memory.
+The server was equipped with an NVIDIA Tesla T4 GPU card with 16GB GDDR6 memory.
 For the software environment, we adopted Python 3.7.7, PyTorch 1.5.0, and CUDA 10.1.
-We implemented all the GNNs with PyG 1.5.0.
+We implemented all GNNs with PyG 1.5.0\footnote{https://pytorch-geometric.readthedocs.io/en/1.5.0/index.html}.
 
-\paragraph{Dataset}
+\paragraph{Datasets}
 We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervised, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
-For directed graphs, PyG converts them into undirected ones during the data loading.
+For directed graphs, PyG converts them into undirected ones during data loading.
 Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
-For an undirected graph, $\mathcal{E}$ already contains two-direction edges and $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
+For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
 For the \texttt{cam} dataset, we generated random dense feature vectors.
-We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in the experiments, to explore the effects of graph topological characteristics (like the average degree) on the performance bottleneck.
+We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in some experiments, to explore the effects of graph topological characteristics (like average degrees) on performance bottlenecks.
 Input feature vectors of random graphs were random dense vectors with the dimension of 32.
@@
         \midrule
-        pubmed (pub) \cite{yang2016_revisiting_semisupervised}  & 19,717          & 44,324          & 4.5       & 500                   & 3       & Yes      \\
-        amazon-photo (amp) \cite{shchur2018_pitfall_of_gnn}     & 7,650           & 119,081         & 31.1      & 745                   & 8       & Yes      \\
-        amazon-computers (amc) \cite{shchur2018_pitfall_of_gnn} & 13,752          & 245,861         & 35.8      & 767                   & 10      & Yes      \\
-        coauthor-physics (cph) \cite{shchur2018_pitfall_of_gnn} & 34,493          & 247,962         & 14.4      & 8415                  & 5       & Yes      \\
-        flickr (fli) \cite{zeng2020_graphsaint}                 & 89,250          & 899,756         & 10.1      & 500                   & 7       & No       \\
-        com-amazon (cam) \cite{yang2012_defining}               & 334,863         & 925,872         & 2.8       & 32                    & 10      & No       \\
+        pubmed (\texttt{pub}) \cite{yang2016_revisiting_semisupervised}  & 19,717          & 44,324          & 4.5       & 500                   & 3       & Yes      \\
+        amazon-photo (\texttt{amp}) \cite{shchur2018_pitfall_of_gnn}     & 7,650           & 119,081         & 31.1      & 745                   & 8       & Yes      \\
+        amazon-computers (\texttt{amc}) \cite{shchur2018_pitfall_of_gnn} & 13,752          & 245,861         & 35.8      & 767                   & 10      & Yes      \\
+        coauthor-physics (\texttt{cph}) \cite{shchur2018_pitfall_of_gnn} & 34,493          & 247,962         & 14.4      & 8415                  & 5       & Yes      \\
+        flickr (\texttt{fli}) \cite{zeng2020_graphsaint}                 & 89,250          & 899,756         & 10.1      & 500                   & 7       & No       \\
+        com-amazon (\texttt{cam}) \cite{yang2012_defining}               & 334,863         & 925,872         & 2.8       & 32                    & 10      & No       \\
         \bottomrule
@@
 We used the node classification as the target task in GNNs due to its popularity in real-world applications.
-We trained GNNs with the semi-supervised learning setting.
-All vertices and their input feature vectors were used, but only parts of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
+We trained GNNs in the semi-supervised learning setting.
+All vertices and their input feature vectors were used, but only a part of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
 The vertices with unseen labels were used in the evaluation phase to evaluate the accuracy of the current parameters.
@@
 \paragraph{GNN Implementation}
-We implemented the four typical GNNs (GCN, GGNN, GAT, GaAN).
-To compare the performance characteristics of four GNNs side-by-side, we used a unified GNN structure for them: Input Layer $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ Softmax Layer (to prediction).
+We implemented the four typical GNNs: GCN, GGNN, GAT, and GaAN.
+To compare performance characteristics of the four GNNs side-by-side, we used a unified GNN structure for them: Input Layer $\rightarrow$ GNN Layer 0 $\rightarrow$ GNN Layer 1 $\rightarrow$ Softmax Layer (to prediction).
 The structure was popular in the experimental evaluation of GCN \cite{kipf2017_gcn}, GAT \cite{huang2018_gat}, and GaAN \cite{zhang2018_gaan}.
-Since a GGNN layer requires the input and output hidden vectors have the same dimension, we added two multi-layer perceptron (MLP) layers to transform the dimensions of the input/output feature vectors of the whole GNN: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
-We stored the dataset and the model parameters on the GPU side.
-All the training was conducted on the GPU side.
+Since a GGNN layer requires the input and output hidden vectors have the same dimension, we added two multi-layer perceptron (MLP) layers to transform the dimensions of the input/output feature vectors: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
+Unless otherwise specified, we stored the dataset and the model parameters on the GPU side.
+The GNN training was conducted also on the GPU side.
 
@@
 We use $dim(\boldsymbol{x})$ to denote the dimension of a vector $\boldsymbol{x}$.
-We picked the hyper-parameters of GNNs according to their popularity in the original papers.
+%
+We picked the hyper-parameters of GNNs according to their popularity in their references \cite{kipf2017_gcn, li2015_ggnn, huang2018_gat, zhang2018_gaan}.
+%
 Unless otherwise mentioned, we used the same set of hyper-parameters for all the datasets. 
-Some hyper-parameters like the dimensions of hidden vectors were common in the four GNNs and we set them to the same values.
-For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_x = \boldsymbol{v}_x$, $dim(\boldsymbol{h}^1_x)=64$, and $dim(\boldsymbol{h}^2_x)=\#Classes$.
-For GAT, we set the hyper-parameters according to its paper\cite{huang2018_gat}.
-The first GAT layer had 8 heads with the dimension of 8. The first GAT layer merged the heads by concatenating.
-The second GAT layer used a single head with the dimension of the number of classes of the dataset.
-For GGNN, since it uses extra MLP layers to transform the dimensions of the input/output feature vectors, we set $dim(\boldsymbol{h}^0_x) = dim(\boldsymbol{h}^1_x) = dim(\boldsymbol{h}^2_x) = 64$.
-We used 8 heads in the both GaAN layers with $d_a=d_v=8$ and $d_m=64$.
+%
+Some hyper-parameters (like dimensions of hidden vectors) were common in the four GNNs and we set them to the same values.
+%
+For GCN/GAT/GaAN, we set $\boldsymbol{h}^0_x = \boldsymbol{v}_x$, $dim(\boldsymbol{h}^1_x)=64$, and $dim(\boldsymbol{h}^2_x)=\#Class$ (the number of classes in the dataset).
+%
+For GAT, the first GAT layer contained 8 heads, and the attention vector of each head had a dimension of 8.
+%
+The first GAT layer merged attention vectors of 8 heads by concatenating.
+%
+The second GAT layer used a single head with a dimension of $\#Class$.
+%
+For GGNN, we set $dim(\boldsymbol{h}^0_x) = dim(\boldsymbol{h}^1_x) = dim(\boldsymbol{h}^2_x) = 64$.
+%
+We used 8 heads in the both GaAN layers with $d_a=d_v=8$, and $d_m=64$.
 
@@
 
-We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical sampling techniques, respectively.
+We picked the neighbor sampler from GraphSAGE \cite{hamilton2017_graphsage} and the cluster sampler from ClusterGCN \cite{chiang2019_cluster_gcn} as the typical sampling techniques.
 %
-For the neighbor sampler, we set the neighborhood sample sizes as 25 for GNN Layer 1 and 10 for GNN Layer 0.
+For the neighbor sampler, we set the neighborhood sample sizes of the GNN layer 0 and the GNN layer 1 to 10 and 25, respectively.
 %
-We set the default batch size as 512 from its paper\cite{hamilton2017_graphsage}.
+We set the default batch size to 512, according to \cite{hamilton2017_graphsage}.
 %
-For the cluster sampler, we partitioned every input graph into 1500 partitions and used 20 partitions per batch according to the parameters used in its paper\cite{chiang2019_cluster_gcn}.
+For the cluster sampler, we partitioned the input graph into 1500 partitions and used 20 partitions per batch, according to \cite{chiang2019_cluster_gcn}.
 
@@
 
-To find out the performance bottleneck in GNN training, we conducted the experimental analysis with four questions.
-The answers to those questions will give us a more comprehensive view of the performance characteristics of GNN training.
+To find out performance bottlenecks in GNN training, we conducted the experimental analysis with four questions.
+%
+The answers to those questions will give us a more comprehensive view of performance characteristics of GNN training.
 
@@
 
-          Every GNN has a group of hyper-parameters like the number of GNN layers and the dimensions of hidden feature vectors.
-The hyper-parameters affect the training time per epoch and the peak memory usage during the training.
+          Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
+          %
+          The hyper-parameters affect the training time per epoch and the peak memory usage during training.
+          %
           To evaluate their effects, we measured how the training time per epoch and the peak memory usage (of the GPU) changed as we increased the values of the hyper-parameters.
-          Through the experiments, we want to verify the validity of the computational complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
-          If the complexity analysis is valid, we can analyze the bottleneck theoretically.
+          %
+          Through the experiments, we verified the validity of the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}.
+          %
+          The complexity analysis allowed us to analyze performance bottlenecks theoretically.
 
@@
 
-          We can decompose the training time on different levels: layer level, edge/vertex calculation level, and the basic operator level.
-          On each level, we decomposed the training time of an epoch into several stages. The most time-consuming stage is the performance bottleneck.
-          Optimizing its implementation can significantly reduce the training time.
+          We decomposed the GNN training time on different levels: the layer level, the edge/vertex calculation level, and the basic operator level.
+          %
+          On each level, we decomposed the training time of an epoch into several stages.
+          %
+          The most time-consuming stage was the performance bottleneck.
+          %
+          Optimizing its implementation will significantly reduce the training time.
 
@@
 
-          The limited memory capacity of a GPU is the main factor preventing us from training GNNs on big graphs.
-          We measured the peak memory usage of GNN training under different graph scales, input feature dimensions, and average vertex degrees.
-          Based on the results, we analyzed which is the most memory-consuming component in a GNN.
+          The limited memory capacity of a GPU prevents us from training GNNs on big graphs.
+          %
+          We measured the peak memory usage during GNN training under different graph scales, input feature dimensions, and average degrees.
+          %
+          Based on the results, we analyzed which was the most memory-consuming component in a GNN.
+          %
           Reducing its memory usage will enable us to train GNNs on bigger graphs under the same memory capacity.
 
-    \item[Q4] \emph{Can the sampling techniques remove the performance bottleneck in GNN training?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
+    \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
 
-          Theoretically, the sampling techniques can significantly reduce the number of graph neurons that participate in the training of a batch.
+          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training of a batch.
+          %
           Consequently, the training time and the memory usage should also decrease.
-          To validate the effectiveness of the sampling techniques, we measured the training time and peak memory usage under different batch sizes.
-          If the sampling techniques are effective, they are the keys to conduct GNN training on very big graphs.
-          If they are not effective, we want to find out which impairs its efficiency.
+          %
+          To validate effectiveness of sampling techniques, we measured the training time and peak memory usage under different batch sizes.
+          %
+          If sampling techniques were effective, they will be the keys to conduct GNN training on very big graphs.
+          %
+          If they were not effective, we want to find out which impairs its efficiency.
 \end{itemize}

### 2020-12-19 NEUROC/sec4-experiments.tex
回复R1Q1.

@@
 We answer the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
-Without otherwise mentioned, the reported training time per epoch is the average wall-clock training time of 50 epochs, excluding abnormal epochs \footnote{During the training of some epochs, there are extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increase the training time.
-Assume Q1 and Q3 are the 25\% and 75\% quantiles of the training time of 50 epochs, respectively.
-We regard the epochs with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epochs.}.
+Without otherwise mentioned, the reported training time per epoch was the average wall-clock training time of 50 epochs, excluding abnormal epochs \footnote{During the training of some epochs, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
+We denoted the 25\% and 75\% quantiles of the training time of 50 epochs as Q1 and Q3, respectively.
+We regarded the epochs with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epochs.}.
 
@@
 
-According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexities of $\phi$ and $\gamma$ are linear to each hyper-parameter separately.
+According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexity of the messaging function $\phi^l$ and the updating function $\gamma^l$ are linear to each hyper-parameter separately.
+%
 If we increase one of the hyper-parameters and fix the others, the training time should increase linearly.
 
-To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compare the training time of the four GNNs on the real-world datasets in \ref{tab:dataset_overview}.
-The ranking of the training time is GaAN $\gg$ GAT $>$ GGNN $>$ GCN in all cases.
-Since the real-world graphs have more edges than edges ($|\mathcal{E}| > |\mathcal{V}|$), the time complexity of the edge calculation stage affects more than the vertex calculation stage.
-The ranking is consistent with the time complexity analysis.
+To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the training time of the four GNNs.
+%
+The ranking of the training time was GaAN $\gg$ GAT $>$ GGNN $>$ GCN in all cases.
+%
+Since the real-world graphs had more edges than vertices ($|\mathcal{E}| > |\mathcal{V}|$), the time complexity of the edge calculation stage affected more than the vertex calculation stage.
+%
+The ranking was consistent with the time complexity analysis.
 
@@
 
-To further evaluate the effects of the hyper-parameters, we measure the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.
+To further evaluate effects of hyper-parameters on performance, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.
 
-\begin{figure}[tbp]
+\begin{figure}[H]
     \centering
-    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
+    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
     %
@@
 
-$dim(\MyVec{h^0})$ and $dim(\MyVec{h}^1)$ are solely determined by the dataset with $d^0_{in} = dim(\MyVec{h}^0_x) = dim(\MyVec{v_x})$ and $d^1_{out} = dim(\boldsymbol{h}^2_x)=\#Class$.
+For GCN and GGNN, $dim(\MyVec{h}^0_x)$ and $dim(\MyVec{h}^1_x)$ were solely determined by the dataset with $d^0_{in} = dim(\MyVec{h}^0_x) = dim(\MyVec{v_x})$ and $d^1_{out} = dim(\boldsymbol{h}^2_x)=\#Class$.
 %
-For GCN and GGNN, the only modifiable hyper-parameter is the dimension of the hidden vectors $dim(\boldsymbol{h}^1_x)$ that are both the output hidden vectors for the GNN layer 0 and the input hidden vector for the GNN layer 1.
+Therefore, the only modifiable hyper-parameter was the dimension of $\MyVec{h}^1_x$ that affected the dimension of output hidden vectors of the layer 0 $d^0_{out}$ and the dimension of input hidden vectors of the layer 1 $d^1_{in}$ simultaneously, i.e.
+$dim(\MyVec{h}^1_x)  = d^0_{out} = d^1_{in}$.
 %
-According to the time complexity analysis, if we fix other hyper-parameters but only increase $dim(\boldsymbol{h}^1_x)$, the computational costs of the GNN layer 0 and the GNN layer 1 both increase linearly with $dim(\boldsymbol{h}^1_x)$, causing the training time of the whole GNN also increasing linearly.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn} show that the training time of GCN and GGNN increased linearly with $dim(\boldsymbol{h}^1_x)$ when $dim(\boldsymbol{h}^1_x)$ is big, consistent with the time complexity analysis.
+According to the time complexity analysis, if we fixed other hyper-parameters but only increased $dim(\boldsymbol{h}^1_x)$, the computational costs of the GNN layer 0 and the GNN layer 1 should both increase linearly with $dim(\boldsymbol{h}^1_x)$, causing the training time of the whole GNN also increasing linearly.
+%
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn} show that the training time of GCN and GGNN increased linearly with $dim(\boldsymbol{h}^1_x)$ when $dim(\boldsymbol{h}^1_x)$ was big, consistent with the theoretical analysis.
 
-For GAT, we modify the number of heads $K$ and the dimension of each head $d_{head}$ in the GAT layer 0.
-The dimension of the hidden vectors $dim(\MyVec{h}^1_x)$ is determined as $dim(\boldsymbol{h}^1_x) = K d_{head}$.
-Thus, the computational costs of the GAT layer 0 and the GAT layer 1 should increase linearly with $K$ and $d_{head}$, separately. 
+For GAT, we modified the number of heads $K$ and the dimension of each head $d_{head}$ in the GAT layer 0.
+%
+The dimension of $\MyVec{h}^1_x$ is determined as $dim(\boldsymbol{h}^1_x) = K d_{head}$.
+%
+Thus, the computational costs of the GAT layer 0 and the GAT layer 1 should increase linearly with $K$ and $d_{head}$ separately. 
+%
 \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} confirms the theoretical analysis.
@@
 For GaAN, it is also based on the multi-head mechanism.
-Its time complexity is affected by $dim(\boldsymbol{h}^1_x)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1_x)$), $d_a$, $d_v$, $d_m$, and the number of heads $K$.
-\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time increases linearly with the hyper-parameters, except for $dim(\boldsymbol{h}^1_x)$.
-As $dim(\boldsymbol{h}^1_x)$ increases, the training time increases first slightly and then linearly.
-We observe similar phenomena in GCN, GGNN, and GAT with low hyper-parameter values.
-When the values of hyper-parameters are too low, the GNN training cannot make full use of the computing power of the GPU.
-When the values of hyper-parameters become high enough, the training time increases linearly, supporting the time complexity analysis.
+%
+Its time complexity shoud be affected by $dim(\boldsymbol{h}^1_x)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1_x)$), $d_a$, $d_v$, $d_m$, and the number of heads $K$.
+%
+\figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan} demonstrates that the training time increased linearly with the hyper-parameters, except for $dim(\boldsymbol{h}^1_x)$.
+As $dim(\boldsymbol{h}^1_x)$ increased, the training time increased first slightly and then linearly.
+We observed similar phenomena in GCN, GGNN, and GAT:
+When the values of hyper-parameters were too low, GNN training could not make full use of the computing power of the GPU.
+%
+When the values of hyper-parameters became high enough, training time increased linearly, supporting the time complexity analysis.
 
-\begin{figure}[tbp]
+We further measured the effects of the hyper-parameters on the peak GPU memory usage in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
+%
+The memory usage also increased linearly as the hyper-parameters increased for all GNNs, except for GaAN on $dim(\MyVec{h}^1_x)$.
+%
+As the hidden vectors $\MyVec{h}^1_x$ consumed a small proportion of memory in GaAN, the growth in the memory usage was not noticeable until $dim(\boldsymbol{h}^1_x)$ was large enough.
+
+\begin{figure}[H]
     \centering
@@
 
-We further measured the effects of the hyper-parameters on the peak GPU memory usage in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
-The memory usage also increases linearly as the hyper-parameters increase for all GNNs, except for GaAN on $dim(\boldsymbol{h}^1_x)$.
-As the hidden vectors $\boldsymbol{h}^1_x$ consume a small proportion of memory in GaAN, the growth in the memory usage is not noticeable until $dim(\boldsymbol{h}^1_x)$ is large enough.
-
 \paragraph{Summary}
@@
 The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} is valid.
-Fixing other hyper-parameters, each hyper-parameter itself affects the training time and the memory usage of a GNN Layer \textbf{in a linear way}.
+Fixing other hyper-parameters, each hyper-parameter itself affects the training time and the memory usage of a GNN Layer \emph{in a linear way}.
 Algorithm engineers can adjust hyper-parameters according to the time complexity to avoid explosive growth in the training time and memory usage.
@@
 In GCN, GAT, and GaAN, the time spent on the layer 0 is much larger than the layer 1.
-In those GNNs, the dimensions of the input/output feature vectors in the layer 0 are much larger than the dimensions in the layer 1.
-$d^0_{in}=dim(\boldsymbol{v}_x)$, $d^0_{out}=d^1_{in}=64$ and $d^1_{out}=\#Class$ and $dim(\boldsymbol{v}_x) \gg \#Class$.
-For GaAN, since it requires the dimensions of the input/output feature vectors must be the same, the hyper-parameter are $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers is close.
+In those GNNs, the dimensions of the input/output hidden vectors in the layer 0 are much larger than the dimensions in the layer 1: $d^0_{in}=dim(\boldsymbol{v}_x)$, $d^0_{out}=d^1_{in}=64$, $d^1_{out}=\#Class$, and $dim(\boldsymbol{v}_x) \gg \#Class$.
+For GaAN, since it requires the dimensions of the input/output hidden vectors must be the same, the hyper-parameters are set as $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers is close.
 
@@
 In \figurename~\ref{fig:exp_vertex_edge_cal_proportion}, GCN spends most of the training time on the edge calculation stage in most datasets.
-A special case is \texttt{cph} dataset.
+A special case is the \texttt{cph} dataset.
 The dimension of the input feature vectors is very high in \texttt{cph}, making the vertex calculation stage of the GCN Layer 0 spend considerable time.
@@
     \includegraphics[width=1\columnwidth]{figs/illustration/steps_in_edge_calculation.pdf}
-    \caption{Step decomposition of the edge calculation in the GNN layer $l$.}
+    \caption{Step decomposition of the edge calculation stage for the GNN layer $l$.}
     \label{fig:steps_in_edge_calculation}
@@
 
-In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collection, messaging, aggregation, and updating, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
+In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collection, messaging, aggregation, and vector updating, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
+%
 The edge index is a matrix with $|\mathcal{E}|$ rows and 2 columns that holds the edge set of the graph.
-The two columns of the matrix store the source vertex and the target vertex of each edge, respectively.
-The collection step copies the vertex feature vectors from the previous layer $\boldsymbol{h}_i^l$ to the ends of each edge
-in the edge index, to form the parameters tensor $[\boldsymbol{h}^l_i, \boldsymbol{h}^l_{j}, \boldsymbol{e}^l_{i,j}]$ of the messaging function $\phi$.
+%
+The two columns of the edge index store the source vertex and the target vertex of each edge, respectively.
+%
+The collection step copies the hidden vectors from the previous layer $\MyVec{h}^l_x$ and $\MyVec{h}^l_y$ to the both endpoints of each edge $e_{x,y}$ in the edge index, forming the parameter tensor $[\MyVec{h}^l_x, \MyVec{h}^l_{y}, \MyVec{e}_{x,y}]$ of the messaging function $\phi^l$.
+%
 This step only involves the data movement.
-The messaging step calls the messaging function $\phi$ to get message vectors of all edges $\boldsymbol{m}_{i, j}^l$.
-The aggregation step aggregates the message vectors with the same target vertex into an aggregated vector $\boldsymbol{s}^l_i$ with the aggregation operation $\Sigma$.
-The updating step is optional.
-It performs an additional transformation on the aggregated vectors (for example, adding bias in GCN).
-The aggregated vectors $\boldsymbol{s}^l_i$ (after the updating step) will be fed into the vertex updating function $\gamma$ as one of the input parameters.
+%
+The messaging step calls the messaging function $\phi^l$ on all edges to get message vectors $\MyVec{m}^l_{x,y}$.
+%
+The aggregation step aggregates the message vectors with the same target vertex into an aggregated vector $\MyVec{s}^l_x$ with the aggregation function $\Sigma^l$.
+%
+The vector updating step is optional.
+%
+It performs an additional transformation on the aggregated vectors (for example, adding the bias in GCN).
+%
+The aggregated vectors $\MyVec{s}^l_x$ will be fed into the vertex updating function $\gamma^l$ as one of the input parameters.
 
@@
 For GCN and GGNN with the low edge complexity, the proportions of the steps are close. 
-Since the messaging function $\phi$ of GGNN uses the pre-computed $\hat{\boldsymbol{h}}^l_i$ as the message vector directly, the time spent on the messaging step of GGNN is negligible.
+Since the messaging function $\phi^l$ of GGNN uses the pre-computed $\MyVec{\hat{h}}^l_y$ as the message vector directly, the time spent on the messaging step of GGNN is negligible.
 Although the collecting step does not conduct any computation and only involves data movement, it occupies noticeable execution time in all the GNNs.
@@
 Optimizing the implementation of $\phi$ can significantly reduce the training time.
-For the other GNNs, optimization should focus on reducing the costs of the collection and the aggregation steps.
+For the other GNNs, optimization should focus on reducing the costs of the collection and aggregation steps.
 Additionally, improving the efficiency of the collection step can benefit all GNNs.
@@
 
-The functions $\phi$, $\Sigma$ and $\gamma$ in the vertex and edge calculation are made up of a series of basic operators implemented on the GPU, like the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
+The functions $\phi$, $\Sigma$ and $\gamma$ in the vertex and edge calculation stages are made up of a series of basic operators implemented on the GPU, like the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
 \figurename~\ref{fig:exp_top_basic_ops} shows the five most time-consuming basic operators in each GNN, averaged over all the real-world graphs in \tablename~\ref{tab:dataset_overview}.
 
-\begin{figure}[tbp]
+\begin{figure}[h]
     \centering
@@
 The GNN training is suitable for GPUs.
-\textbf{The edge calculation stage is the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
+\emph{The edge calculation stage is the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
 The performance bottleneck in the edge calculation stage depends on the time complexity of the messaging function $\phi$.
 \begin{itemize}
-    \item If the time complexity of $\phi$ is \textbf{high}, the \textbf{efficiency of $\phi$} limits the performance.
+    \item If the time complexity of $\phi$ is {high}, the {efficiency of $\phi$} limits the performance.
 Reducing its computation cost (via optimizing its implementation or modifying the algorithm) can significantly reduce the training time.
-    \item If the time complexity of $\phi$ is \textbf{low}, the \textbf{collection step} and the \textbf{aggregation step} limit the performance.
+    \item If the time complexity of $\phi$ is {low}, the {collection step} and the {aggregation step} limit the performance.
 The collection step involves lots of data movement.
@@
 For example, GaAN is unable to train on \texttt{cph} dataset due to the out of memory exception.
-
-\begin{figure}[tbp]
-    \centering
-    \includegraphics[height=5cm]{figs/experiments/exp_memory_usage_stage_amp.pdf}
-    \caption{Memory usage of each phase. Dataset: \texttt{amp}.}
-    \label{fig:exp_memory_usage_stage_amp}
-\end{figure}
-
-\begin{figure}[tbp]
-    \centering
-    \includegraphics[height=4.5cm]{figs/illustration/ggnn_vertex_func_computation_graph.pdf}
-    \caption{Computation graph of the vertex updating function $\gamma$ of GGNN.}
-    \label{fig:ggnn_vertex_func_computation_graph}
-\end{figure}
 
@@
 
-\begin{figure}[tbp]
+\begin{figure}[h]
     \centering
-    \includegraphics[height=5cm]{figs/experiments/exp_memory_expansion_ratio.pdf}
-    \caption{Memory expansion ratios of typical GNNs.}
-    \label{fig:exp_memory_expansion_ratio}
+    \includegraphics[height=5cm]{figs/experiments/exp_memory_usage_stage_amp.pdf}
+    \caption{Memory usage of each phase. Dataset: \texttt{amp}.}
+    \label{fig:exp_memory_usage_stage_amp}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figs/illustration/ggnn_vertex_func_computation_graph.pdf}
+    \caption{Computation graph of the vertex updating function $\gamma$ of GGNN.}
+    \label{fig:ggnn_vertex_func_computation_graph}
 \end{figure}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[h]
     \centering
-    \includegraphics[height=5cm]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.pdf}
-    \caption{Memory expansion ratio under different dimensions of the input feature vectors. Dataset: \texttt{cam}.}
-    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
+    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_memory_expansion_ratio.pdf}
+    \caption{Memory expansion ratios of typical GNNs.}
+    \label{fig:exp_memory_expansion_ratio}
 \end{figure}
@@
 \figurename~\ref{fig:exp_memory_expansion_ratio} also indicates that the same GNN has different MERs for different datasets.
-Two characteristics of a dataset affect the MER: the dimension of the input feature vector and the average degree.
+Two characteristics of a dataset affect the MER: the dimension of the input feature vectors and the average degree of the graph.
 
@@
 
-\begin{figure}[tbp]
+\begin{figure}[h]
     \centering
-    \subfloat[Peak memory usage]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_peak_memory.pdf}}
-    \subfloat[Memory expansion ratio]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_expansion_ratio.pdf}}
-    \caption{Memory usage under different average degrees of the graph.
-The graph was generated with the R-MAT generator fixing the number of vertices at 10K and the dimension of the input feature vectors at 32.}
-    \label{fig:exp_memory_expansion_ratio_input_graph_number_of_edges}
+    \includegraphics[height=5cm]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.pdf}
+    \caption{Memory expansion ratio under different dimensions of the input feature vectors. Dataset: \texttt{cam}.}
+    \label{fig:exp_memory_expension_ratio_input_feature_dimension}
 \end{figure}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[h]
     \centering
-    \subfloat[Peak memory usage]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_peak_memory.pdf}}
-    \subfloat[Memory expansion ratio]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_expansion_ratio.pdf}}
-    \caption{Memory usage under different numbers of vertices of the graph.
-The graph was generated with the R-MAT generator fixing the number of edges at 500K and the dimension of the input feature vectors at 32.}
-    \label{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge}
+    \subfloat[Peak memory usage]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_peak_memory.pdf}}
+    \subfloat[Memory expansion ratio]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_expansion_ratio.pdf}}
+    \caption{Memory usage under different average degrees of the graph.
+The graph was generated with the R-MAT generator fixing the number of vertices at 10K and the dimension of the input feature vectors at 32.}
+    \label{fig:exp_memory_expansion_ratio_input_graph_number_of_edges}
 \end{figure}
@@
 It indicates that \emph{the intermediate results of the edge calculation stage dominated the memory usage during the GNN training}.
+
+\begin{figure}[h]
+    \centering
+    \subfloat[Peak memory usage]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_peak_memory.pdf}}
+    \subfloat[Memory expansion ratio]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_expansion_ratio.pdf}}
+    \caption{Memory usage under different numbers of vertices of the graph.
+The graph was generated with the R-MAT generator fixing the number of edges at 500K and the dimension of the input feature vectors at 32.}
+    \label{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge}
+\end{figure}
 
@@
 
-\begin{figure}[tbp]
+\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changes with the batch size.
+For the neighbor sampler, the relative batch size is the proportion of the sampled vertices of the last GNN layer in $|\mathcal{V}|$.
+For the cluster sampler, the relative batch size is the proportion of the sampled partitions to all partitions of the graph.
+The neighbor sampler is very sensitive to the batch size.
+As the batch size increases, the size of the sampled subgraph first increases quickly and then stabilizes.
+The cluster sampler is much less sensitive compared to the neighbor sampler.
+The number of vertices and the average degree of the sampled subgraphs increases linearly with the batch size.
+
+\begin{figure}[h]
     \centering
@@
     \label{fig:exp_sampling_minibatch_graph_info}
-\end{figure}
-
-\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changes with the batch size.
-For the neighbor sampler, the relative batch size is the proportion of the sampled vertices of the last GNN layer in $|\mathcal{V}|$.
-For the cluster sampler, the relative batch size is the proportion of the sampled partitions to all partitions of the graph.
-The neighbor sampler is very sensitive to the batch size.
-As the batch size increases, the size of the sampled subgraph first increases quickly and then stabilizes.
-The cluster sampler is much less sensitive compared to the neighbor sampler.
-The number of vertices and the average degree of the sampled subgraphs increases linearly with the batch size.
-
-\begin{figure}[tbp]
-    \centering
-    \includegraphics[width=0.4\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.pdf}
-    \caption{Vertex degree distribution of the sampled subgraph (relative batch size: 6\%) and the original graph. Dataset:\texttt{amp}.}
-    \label{fig:exp_sampling_minibatch_degrees_distribution}
 \end{figure}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.4\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.pdf}
+    \caption{Vertex degree distribution of the sampled subgraph (relative batch size: 6\%) and the original graph. Dataset:\texttt{amp}.}
+    \label{fig:exp_sampling_minibatch_degrees_distribution}
+\end{figure}
+
+\begin{figure}[h]
     \centering

### 2020-12-19 NEUROC/sec4-experiments.tex
统一实验部分的时态问题。

@@
 The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} is valid.
+%
 Fixing other hyper-parameters, each hyper-parameter itself affects the training time and the memory usage of a GNN Layer \emph{in a linear way}.
+%
 Algorithm engineers can adjust hyper-parameters according to the time complexity to avoid explosive growth in the training time and memory usage.
@@
 
-To find out which stage/step dominates the training time, we decompose the training time and analyze the performance bottleneck level by level.
+To find out which stage/step dominated the training time, we decomposed the training time and analyzed performance bottlenecks level by level.
 
@@
 
-\begin{figure}[tbp]
+\figurename~\ref{fig:exp_vertex_edge_cal_proportion} decomposes the training time of a GNN on the layer level.
+%
+The training time of each layer was the summation of the time in the forward, backward, and evaluation phases.
+%
+In GCN, GAT, and GaAN, the time spent on the layer 0 was much larger than the layer 1.
+%
+In those GNNs, the dimensions of the input/output hidden vectors in the layer 0 were much larger than the dimensions in the layer 1: $d^0_{in}=dim(\boldsymbol{v}_x)$, $d^0_{out}=d^1_{in}=64$, $d^1_{out}=\#Class$, and $dim(\boldsymbol{v}_x) \gg \#Class$.
+%
+For GaAN, since it required the dimensions of the input/output hidden vectors must be the same, the hyper-parameters were set to $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers was close.
+
+\begin{figure}[H]
     \centering
@@
     \caption{Training time breakdown on the layer level.
-The training time of each layer includes the time spent on the forward, backward and evaluation phases.
-Each layer is further decomposed into the vertex and the edge calculation stages.}
+The training time of each layer included the time spent on the forward, backward and evaluation phases.
+Each layer was further decomposed into the vertex and the edge calculation stages.}
     \label{fig:exp_vertex_edge_cal_proportion}
@@
 
-\figurename~\ref{fig:exp_vertex_edge_cal_proportion} decomposes the training time of a GNN on the layer level.
-The training time of each layer is the summation of the time in the forward, backward, and evaluation phases.
-In GCN, GAT, and GaAN, the time spent on the layer 0 is much larger than the layer 1.
-In those GNNs, the dimensions of the input/output hidden vectors in the layer 0 are much larger than the dimensions in the layer 1: $d^0_{in}=dim(\boldsymbol{v}_x)$, $d^0_{out}=d^1_{in}=64$, $d^1_{out}=\#Class$, and $dim(\boldsymbol{v}_x) \gg \#Class$.
-For GaAN, since it requires the dimensions of the input/output hidden vectors must be the same, the hyper-parameters are set as $d^0_{in}=d^0_{out}=d^1_{in}=d^1_{out}=64$ and the training time of both layers is close.
+Each GNN layer was further divided into the vertex and the edge calculation stages.
+%
+In \figurename~\ref{fig:exp_vertex_edge_cal_proportion}, GCN spent most of the training time on the edge calculation stage on most datasets.
+%
+A special case was the \texttt{cph} dataset.
+%
+The dimension of the input feature vectors was very high in \texttt{cph}, making the vertex calculation stage of the GCN Layer 0 spend considerable time.
+%
+GGNN also spent the majority of its training time on the edge calculation stage, but the high time complexity of its vertex updating function $\gamma^l$ made the proportion of the vertex calculation in the total training time much higher than the other GNNs.
+%
+For GAT and GaAN, due to their high edge calculation complexity, the edge calculation stage was the dominant stage.
 
-Each GNN layer can be further divided into the vertex and the edge calculation stages.
-In \figurename~\ref{fig:exp_vertex_edge_cal_proportion}, GCN spends most of the training time on the edge calculation stage in most datasets.
-A special case is the \texttt{cph} dataset.
-The dimension of the input feature vectors is very high in \texttt{cph}, making the vertex calculation stage of the GCN Layer 0 spend considerable time.
-GGNN also spends the majority of its training time on the edge calculation stage.
-But the high time complexity of its vertex updating function $\gamma$ makes the ratio of the vertex calculation in the total training time much higher than the other GNNs.
-%In \textit{pub} and cam dataset, the edge calculation cost, and the vertex calculation cost are close for GGNN
-%because the average degree of the two datasets is low (only 4.5 and 2.8).
-For GAT and GaAN, due to their high edge calculation complexity, the edge calculation stage is the absolutely dominant stage.
-In summary, \emph{the edge calculation stage is the most time-consuming stage in the GNN training}.
+The experimental results also indicated that the average degree of the dataset affected the proportion of the edge/vertex calculation time in the total training time.
+%
+For GaAN, the time spent on the vertex calculation stage exceeded the edge calculation stage on the \texttt{pub} and \texttt{cam} datasets, because the average degrees of the two datasets were low, making $|\mathcal{E}|$ and $|\mathcal{V}|$ much closer.
+%
+To evaluate the effects of the average degree, we generated random graphs with 50,000 vertices and average degrees ranging from 2 to 100.
+%
+\figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time} shows the training time of the four GNNs under different average degrees.
+%
+As the average degree increased, the training time of the edge calculation stage grew \emph{linearly}.
+%
+For GCN, GAT, and GaAN, the edge calculation stage dominated the entire training time even when the average degrees were small.
+%
+Only for GGNN that had high vertex and low edge calculation complexity, the training time of the vertex calculation stage exceeded the edge calculation stage under low average degrees ($<5$).
 
-\begin{figure}[tbp]
+In summary, \emph{the edge calculation stage was the most time-consuming stage in GNN training}.
+%
+Improving its efficiency is the key to reduce the GNN training time.
+
+\begin{figure}[H]
     \centering
@@
 
-The experimental results also indicate that the average degree of the dataset affects the time-consuming proportion of the edge/vertex calculation time.
-For GaAN, the time spent on the vertex calculation stage exceeds the edge calculation stage on the \texttt{pub} and \texttt{cam} datasets, because the average degrees of the two datasets are low, making $|\mathcal{E}|$ and $|\mathcal{V}|$ much closer.
-To evaluate the effects of the average degree, we used the R-MAT generator to generate random graphs with 50k vertices and the average degrees ranging from 2 to 100.
-\figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time} shows the training time of the four GNNs under different average degrees.
-As the average degree increases, the training time of the edge calculation stage grows \emph{linearly}.
-For GCN, GAT, and GaAN, the edge calculation stage dominates the entire training time even under small average degrees.
-Only for GGNN that has high vertex and low edge calculation complexities, the training time of the vertex calculation stage exceeds the edge calculation stage under low average degrees ($<5$).
-Therefore, \emph{improving the efficiency of the edge calculation stage is the key to reduce the GNN training time}.
-
 \subsubsection{Step Level in Edge Calculation}
 
-\begin{figure}[tbp]
-    \centering
-    \includegraphics[width=1\columnwidth]{figs/illustration/steps_in_edge_calculation.pdf}
-    \caption{Step decomposition of the edge calculation stage for the GNN layer $l$.}
-    \label{fig:steps_in_edge_calculation}
-\end{figure}
-
-In the implementation of PyG, the edge calculation stage can be decomposed into four steps: collection, messaging, aggregation, and vector updating, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
+We further investigated the most time-consuming step of the edge calculation stage.
 %
-The edge index is a matrix with $|\mathcal{E}|$ rows and 2 columns that holds the edge set of the graph.
+In the implementation of PyG, the edge calculation stage consists of four steps: collection, messaging, aggregation, and vector updating, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
 %
-The two columns of the edge index store the source vertex and the target vertex of each edge, respectively.
+The edge index is a matrix with $|\mathcal{E}|$ rows and two columns.
 %
-The collection step copies the hidden vectors from the previous layer $\MyVec{h}^l_x$ and $\MyVec{h}^l_y$ to the both endpoints of each edge $e_{x,y}$ in the edge index, forming the parameter tensor $[\MyVec{h}^l_x, \MyVec{h}^l_{y}, \MyVec{e}_{x,y}]$ of the messaging function $\phi^l$.
+It holds the edge set of the graph.
 %
-This step only involves the data movement.
+The two columns of the edge index store the source and the target vertex IDs of each edge.
+%
+The collection step copies the hidden vectors from the previous GNN layer $\MyVec{h}^l_x$ and $\MyVec{h}^l_y$ to the both endpoints of each edge $e_{x,y}$ in the edge index, forming the parameter tensor $[\MyVec{h}^l_x, \MyVec{h}^l_{y}, \MyVec{e}_{x,y}]$ of the messaging function $\phi^l$.
+%
+This step only involves data movement.
 %
@@
 %
-The aggregation step aggregates the message vectors with the same target vertex into an aggregated vector $\MyVec{s}^l_x$ with the aggregation function $\Sigma^l$.
+The aggregation step aggregates the message vectors with the same target vertex into an aggregated vector $\MyVec{s}^l_x$.
 %
@@
 It performs an additional transformation on the aggregated vectors (for example, adding the bias in GCN).
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\columnwidth]{figs/illustration/steps_in_edge_calculation.pdf}
+    \caption{Step decomposition of the edge calculation stage of the GNN layer $l$.}
+    \label{fig:steps_in_edge_calculation}
+\end{figure}
+
+We decomposed the execution time of the edge calculation stage in \figurename~\ref{fig:exp_edge_calc_decomposition}.
 %
-The aggregated vectors $\MyVec{s}^l_x$ will be fed into the vertex updating function $\gamma^l$ as one of the input parameters.
+In each GNN, the proportions of the four steps were rather stable, rarely affected by datasets. 
+%
+For GAT and GaAN with the high edge calculation complexity, the messaging step consumed most of the training time. 
+%
+For GCN and GGNN with the low edge complexity, the proportions of the steps were close. 
+%
+Since the messaging function $\phi^l$ of GGNN used the pre-computed $\MyVec{\hat{h}}^l_y$ as the message vector directly, the time spent on the messaging step of GGNN was negligible.
+%
+Although the collecting step did not conduct any computation and only involved data movement, it occupied noticeable execution time in the four GNNs.
 
-\begin{figure}[tbp]
+The results indicate that \emph{the performance bottlenecks of the edge calculation stage depend on the complexity of the messaging function $\phi^l$}.
+%
+When the time complexity of $\phi^l$ is high, the messaging step is the performance bottleneck.
+%
+Optimizing the implementation of $\phi$ can significantly reduce training time.
+%
+Otherwise, the collection and the aggregation steps are performance bottlenecks.
+%
+Improving the efficiency of the two steps can benefit all GNNs.
+
+\begin{figure}[H]
     \centering
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.pdf}}
-    \caption{Training time breakdown of the edge calculation stage (including both GNN layers).}
+    \caption{Training time breakdown of the edge calculation stage.}
     \label{fig:exp_edge_calc_decomposition}
@@
 
-We decompose the execution time of the edge calculation stage in \figurename~\ref{fig:exp_edge_calc_decomposition}.
-In each GNN, the proportions of the four steps are rather stable, rarely affected by datasets. 
-For GAT and GaAN with the high edge calculation complexity, the messaging step consumes most of the training time. 
-For GCN and GGNN with the low edge complexity, the proportions of the steps are close. 
-Since the messaging function $\phi^l$ of GGNN uses the pre-computed $\MyVec{\hat{h}}^l_y$ as the message vector directly, the time spent on the messaging step of GGNN is negligible.
-Although the collecting step does not conduct any computation and only involves data movement, it occupies noticeable execution time in all the GNNs.
-The experiments show that \emph{the performance bottleneck on the step level depends on the complexity of the messaging function $\phi$}.
-For GNNs with the high complexity, the messaging function $\phi$ is the performance bottleneck.
-Optimizing the implementation of $\phi$ can significantly reduce the training time.
-For the other GNNs, optimization should focus on reducing the costs of the collection and aggregation steps.
-Additionally, improving the efficiency of the collection step can benefit all GNNs.
-
 \subsubsection{Operator Level}
 
-The functions $\phi$, $\Sigma$ and $\gamma$ in the vertex and edge calculation stages are made up of a series of basic operators implemented on the GPU, like the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
-\figurename~\ref{fig:exp_top_basic_ops} shows the five most time-consuming basic operators in each GNN, averaged over all the real-world graphs in \tablename~\ref{tab:dataset_overview}.
+The functions $\phi$, $\Sigma$ and $\gamma$ in the edge and vertex calculation stages are made up of a series of basic operators implemented on the GPU side, such as the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
+%
+\figurename~\ref{fig:exp_top_basic_ops} shows the top-5 time-consuming basic operators in each GNN, averaged over all datasets.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gaan.pdf}}
-    \caption{Top 5 time-consuming basic operators of typical GNNs. The time proportion of each basic operator is averaged over all graphs with the error bar indicating the maximal and the minimal.}
+    \caption{Top 5 time-consuming basic operators of typical GNNs. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
     \label{fig:exp_top_basic_ops}
@@
 \paragraph{GCN}
-The most time-consuming basic operator is the matrix multiplication \texttt{mm} used in the vertex updating function $\gamma$.
-The elementwise multiplication \texttt{mul} used in the messaging function $\phi$ is also time-consuming.
-The other three operators are used in the edge calculation stage: \texttt{scatter\_add\_} for the aggregation step in the forward phase, \texttt{gather} for the aggregation step in the backward phase, and \texttt{index\_select} for the collection step.
-For GCN, the basic operators related to the edge calculation stage consume the majority of the training time.
+%
+The most time-consuming basic operator was the matrix multiplication \texttt{mm} used in the vertex updating function $\gamma$.
+%
+The elementwise multiplication \texttt{mul} used in the messaging function $\phi$ was also time-consuming.
+%
+The other three operators were used in the edge calculation stage: \texttt{scatter\_add\_} for the aggregation step in the forward phase, \texttt{gather} for the aggregation step in the backward phase, and \texttt{index\_select} for the collection step.
+%
+For GCN, the basic operators related to the edge calculation stage consumed the majority of the training time.
 
 \paragraph{GGNN}
-The top basic operator is \texttt{mm} used in the vertex updating function $\gamma$.
-Due to its high time complexity, the proportion of the \texttt{mm} is much higher than the other operators.
-The \texttt{thnn\_fused\_gru\_cell} operator used in the backward phase of $\gamma$ is also noticeable.
-The other three operators are used in the edge calculation stage.
+%
+The top basic operator was \texttt{mm} used in the vertex updating function $\gamma$.
+%
+Due to its high time complexity, the proportion of \texttt{mm} was much higher than the other operators.
+%
+The \texttt{thnn\_fused\_gru\_cell} operator was used in the backward phase of $\gamma$.
+%
+The other three operators were used in the edge calculation stage.
 
 \paragraph{GAT}
-All the top basic operators except for \texttt{mm} are related to the edge calculation stage.
-The \texttt{mm} operator is used in the vertex updating function $\gamma$.
+%
+All the top basic operators except for \texttt{mm} were related to the edge calculation stage.
+%
+The \texttt{mm} operator was used in the vertex updating function $\gamma$.
 
 \paragraph{GaAN}
-The top basic operator is \texttt{bmm} used in the messaging function $\phi$.
-The \texttt{addmm} operator and the \texttt{mm} operator are used in both the vertex and the edge calculation stages, where the edge calculation stage is dominant.
+%
+The top basic operator was \texttt{bmm} used in the messaging function $\phi$.
+%
+The \texttt{addmm} operator and the \texttt{mm} operator were used in both the vertex and the edge calculation stages, where the edge calculation stage was dominant.
 
-In general, the most time-consuming operator in the four GNNs, is still the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul}, \emph{making GNN training suitable for GPUs}.
-Although the aggregation step in the edge calculation stage is relatively simple (like sum and mean), the related operators \texttt{scatter\_add} and \texttt{gather} still consume a certain amount of the time.
-The operators have to synchronize between hardware threads to avoid updating the same aggregated vector at the same time.
-They also conduct non-regular memory access with the access pattern determined by the edge set dynamically.
-For GPUs, they are less efficient than \texttt{mm}.
-The index-based selection \texttt{index\_select} operator from the collection step consume around 10\% of the time in all GNNs.
-Though GPUs have high on-chip memory bandwidth, improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} can benefit the training of all kinds of GNNs.
+The most time-consuming operators in the four GNNs were the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul}, \emph{making GNN training suitable for GPUs}.
+%
+Although the aggregation step in the edge calculation stage was relatively simple (like sum and mean), the related operators--\texttt{scatter\_add} and \texttt{gather}--still consumed a certain amount of the time.
+%
+The two operators had to synchronize between hardware threads to avoid updating the same aggregated vector at the same time.
+%
+They also conducted non-regular memory access with the access pattern determined by the edge set dynamically.
+%
+For GPUs, they were less efficient than \texttt{mm}.
+%
+The index-based selection operator \texttt{index\_select} used in the collection step consumed about 10\% of the training time in all GNNs.
+%
+Improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} can benefit all kinds of GNNs.
 
-\paragraph{Summary}
+\paragraph{Summary of Training Time Breakdown}
+%
 The GNN training is suitable for GPUs.
+%
 \emph{The edge calculation stage is the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
 The performance bottleneck in the edge calculation stage depends on the time complexity of the messaging function $\phi$.
+%
 \begin{itemize}
-    \item If the time complexity of $\phi$ is {high}, the {efficiency of $\phi$} limits the performance.
-Reducing its computation cost (via optimizing its implementation or modifying the algorithm) can significantly reduce the training time.
-    \item If the time complexity of $\phi$ is {low}, the {collection step} and the {aggregation step} limit the performance.
+    \item If the time complexity of $\phi$ is {high}, {$\phi$} dominates the training time of the edge calculation stage.
+    %
+    Reducing its computation cost (via optimizing its implementation or modifying the algorithm design) can significantly reduce the training time.
+
+    \item Otherwise, the {collection step} and the {aggregation step} dominate the training time.
+    %
     The collection step involves lots of data movement.
+    %
     The aggregation step suffers from data synchronization and non-regular data access.
+    %
     Optimizing their implementations can significantly reduce the training time.

### 2020-12-20 NEUROC/sec4-experiments.tex
统一实验部分的时态问题。

@@
 %
-The GNN training is suitable for GPUs.
+The GNN training was suitable for GPUs.
 %
-\emph{The edge calculation stage is the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
-The performance bottleneck in the edge calculation stage depends on the time complexity of the messaging function $\phi$.
+\emph{The edge calculation stage was the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
 %
-\begin{itemize}
-    \item If the time complexity of $\phi$ is {high}, {$\phi$} dominates the training time of the edge calculation stage.
+The performance bottleneck in the edge calculation stage depended on the time complexity of the messaging function $\phi$.
 %
-    Reducing its computation cost (via optimizing its implementation or modifying the algorithm design) can significantly reduce the training time.
-
-    \item Otherwise, the {collection step} and the {aggregation step} dominate the training time.
+If the time complexity of $\phi$ was {high}, {$\phi$} dominated the training time of the edge calculation stage.
 %
-    The collection step involves lots of data movement.
+Optimizations should focus on improving its efficiency.
 %
-    The aggregation step suffers from data synchronization and non-regular data access.
+Otherwise, the {collection step} and the {aggregation step} dominated the training time.
 %
-    Optimizing their implementations can significantly reduce the training time.
-\end{itemize}
+The collection step suffered from lots of data movement.
+%
+The aggregation step suffered from data synchronization and non-regular data access.
 
@@
 
-During the GNN training, all data (including datasets and intermediate results) are stored in the on-chip memory of the GPU.
-Compared with the main memory on the host side, the capacity of the GPU memory is very limited.
-\emph{The GPU memory capacity limits the scales of the graphs that a GPU can train GNNs on}.
-For example, GaAN is unable to train on \texttt{cph} dataset due to the out of memory exception.
+During the GNN training, we stored all data (including datasets and intermediate results) in the on-chip memory of the GPU.
+%
+Compared with the main memory on the host side (90 GB), the capacity of the GPU memory (16 GB) was very limited.
+%
+\emph{The GPU memory capacity limited the scales of the graphs that it could handle}.
+%
+For example, GaAN was unable to train on the \texttt{cph} dataset due to the out of memory exception.
 
-\figurename~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each phase in the GNN training on the \texttt{amp} dataset.
-The trend is similar on the other datasets.
-\emph{The GNN training achieves its peak memory usage in the forward and the backward phases}.
-The forward phase generates lots of intermediate results.
-Some key intermediate results are cached, increasing memory usage.
-The cached results are used in the gradient calculation in the backward phase.
-\figurename~\ref{fig:ggnn_vertex_func_computation_graph} shows the computation graph of the vertex updating function $\gamma$ of GGNN.
-The computation graph has a large number of operators. Each operator generates an intermediate tensor.
+\figurename~\ref{fig:exp_memory_usage_stage_amp} shows the peak memory usage of each phase during the GNN training on the \texttt{amp} dataset.
+%
+The trends on the other datasets were similar.
+%
+\emph{The GNN training achieved its peak memory usage in the forward and the backward phases}.
+%
+The forward phase generated lots of intermediate results.
+%
+Some key intermediate results were cached for the gradient calculation in the backward phase, increasing memory usage.
+%
+For example, \figurename~\ref{fig:ggnn_vertex_func_computation_graph} shows the computation graph of the vertex updating function $\gamma^l$ of GGNN.
+%
+Each operator in the computation graph generated an intermediate tensor.
+%
 Some key intermediate tensors are cached.
-The cached tensors are the main source of memory usage in the loss phase.
-By the end of the backward phase, the cached tensors are released.
-Since the evaluation phase does not need to calculate the gradients, it does not cache intermediate tensors.
-Its memory usage declines sharply.
+%
+The cached tensors were the main source of memory usage in the loss phase.
+%
+By the end of the backward phase, the cached tensors were released.
+%
+Since the evaluation phase did not have to calculate the gradients, it did not cache intermediate tensors.
+%
+Its memory usage declined sharply.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
     \includegraphics[height=5cm]{figs/experiments/exp_memory_usage_stage_amp.pdf}
-    \caption{Memory usage of each phase. Dataset: \texttt{amp}.}
+    \caption{Memory usage of each phase during the GNN training. Dataset: \texttt{amp}.}
     \label{fig:exp_memory_usage_stage_amp}
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 
-The peak memory usage during the GNN training far exceeds the size of the dataset itself.
-We define the \emph{memory expansion ratio} (MER) as the ratio of the peak memory usage during the training to the memory usage after loading the dataset.
+The peak memory usage during the GNN training far exceeded the size of the dataset itself.
+%
+We defined the \emph{memory expansion ratio} (MER) as the ratio of the peak memory usage during the training to the memory usage after loading the dataset.
+%
 \figurename~\ref{fig:exp_memory_expansion_ratio} compares MER of different GNNs.
-GCN has the lowest MER (up to 15) while GaAN has the highest MER (up to 104).
-\emph{The high MER limits the data scalability of GNNs}, making GPUs unable to handle big graphs.
+%
+GCN had the lowest MER (up to 15) while GaAN had the highest MER (up to 104).
+%
+\emph{The high MERs limited the data scalability of GNNs}, making GPUs unable to handle big graphs.
+%
+\figurename~\ref{fig:exp_memory_expansion_ratio} also indicates that the same GNN had different MERs for different datasets.
+%
+Two characteristics of a dataset affected the MER: the dimension of the input feature vectors and the average degree of the graph.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 
-\figurename~\ref{fig:exp_memory_expansion_ratio} also indicates that the same GNN has different MERs for different datasets.
-Two characteristics of a dataset affect the MER: the dimension of the input feature vectors and the average degree of the graph.
+To find out how the dimension of input feature vectors affected the MER, we generated random input feature vectors with different dimensions for the \texttt{cam} dataset and measured the MER in \figurename~\ref{fig:exp_memory_expension_ratio_input_feature_dimension}.
+%
+Under the same hyper-parameters, \emph{the MER decreased as the dimension of input feature vectors increased}.
+%
+When the dimension of the input feature vectors was high, the size of the dataset itself was large.
+%
+The size became comparable to the size of intermediate results,  making MERs low.
 
-Given the same graph, the scales of the intermediate results are mainly affected by the hyper-parameters of the GNN.
-If the dimension of the input feature vectors is high (like the \texttt{cph} dataset), the size of the dataset is large.
-The size may become comparable to the scales of the intermediate results,  making the MER low.
-To find out how the dimension affects the MER, we generated random input feature vectors with different dimensions for the \texttt{cam} dataset and measured the MER in \figurename~\ref{fig:exp_memory_expension_ratio_input_feature_dimension}.
-For a GNN under the same hyper-parameters, \emph{the MER decreases as the dimension of the input feature vectors increases}.
-
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
     \includegraphics[height=5cm]{figs/experiments/exp_memory_expansion_ratio_input_feature_dimension_com-amazon.pdf}
-    \caption{Memory expansion ratio under different dimensions of the input feature vectors. Dataset: \texttt{cam}.}
+    \caption{Memory expansion ratio under different dimensions of input feature vectors. Dataset: \texttt{cam}.}
     \label{fig:exp_memory_expension_ratio_input_feature_dimension}
@@
 
-The average degree of the graph also affects MER by influencing the relative scales of the intermediate results from the edge/vertex calculation stages.
-Fixing the number of vertices $|\mathcal{V}|$, we used the R-MAT generator to generate random graphs with different average degrees.
-\figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage changes according to the average degrees.
-As the average degree $\bar{d}$ increases, the number of edges $|\mathcal{E}|$ increases and the peak memory usage increases \emph{linearly} with $\bar{d}$.
-The edge calculation stage gradually dominates the memory usage and \emph{the MER converges to a stable value}.
-The stable value is determined by the complexity of the edge calculation stage.
-Except for GGNN, the MER of the other GNNs increases as $\bar{d}$ increases.
-As GGNN has high vertex calculation complexity, the MER related to the vertex calculation stage is much larger than the edge calculation stage.
-When the edge calculation stage dominates the memory usage, its MER becomes smaller.
+Average degrees also affected MERs by influencing the relative sizes of intermediate results from the edge and the vertex calculation stages.
+%
+Fixing the number of vertices $|\mathcal{V}|$, we generated random graphs with different average degrees.
+%
+\figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_edges} shows how the memory usage changed according to the average degree.
+%
+As the average degree $\bar{d}$ increased, the peak memory usage increased \emph{linearly} with $\bar{d}$.
+%
+The edge calculation stage gradually dominated the memory usage and \emph{the MER converged to a stable value}.
+%
+The stable value was determined by the complexity of the edge calculation stage.
+%
+Except for GGNN, the MERs of the other GNNs increased as $\bar{d}$ increased.
+%
+As GGNN had high vertex calculation complexity, the MERs related to the vertex calculation stage were much higher than the edge calculation stage.
+%
+When the edge calculation stage dominated the memory usage, its MERs became smaller.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
     \subfloat[Memory expansion ratio]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_edges_expansion_ratio.pdf}}
-    \caption{Memory usage under different average degrees of the graph.
-The graph was generated with the R-MAT generator fixing the number of vertices at 10K and the dimension of the input feature vectors at 32.}
+    \caption{Memory usage under different average degrees. The random graphs were generated by fixing the number of vertices at 10K and the dimension of input feature vectors at 32.}
     \label{fig:exp_memory_expansion_ratio_input_graph_number_of_edges}
@@
 
-We also fixed the number of edges $|\mathcal{E}|$ in the graphs and generated random graphs with different $|\mathcal{V}|$.
-\figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows how the memory usage changes according to $|\mathcal{V}|$.
-All GNNs are insensitive to the changes in $|\mathcal{V}|$ compared to $|\mathcal{E}|$.
-Except for GGNN, the MERs of the other GNNs decline as $|\mathcal{V}|$ increases because the scales of the datasets increase more quickly than the scales of the intermediate results.
-As GGNN has high vertex calculation complexity, the scales of the intermediate results are much more sensitive to $|\mathcal{V}|$.
-It indicates that \emph{the intermediate results of the edge calculation stage dominated the memory usage during the GNN training}.
+We also fixed the number of edges $|\mathcal{E}|$ and generated random graphs with different $|\mathcal{V}|$.
+%
+\figurename~\ref{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge} shows how the memory usage changed according to $|\mathcal{V}|$.
+%
+MERs of all GNNs were insensitive to $|\mathcal{V}|$, compared to $|\mathcal{E}|$.
+%
+Except for GGNN, the MERs of the other GNNs declined as $|\mathcal{V}|$ increased because the sizes of the datasets increased more quickly than the sizes of the intermediate results.
+%
+As GGNN had high vertex calculation complexity, the sizes of the intermediate results were very sensitive to $|\mathcal{V}|$.
+%
+It indicated that \emph{the intermediate results of the edge calculation stage dominated the memory usage during the GNN training}.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
     \subfloat[Memory expansion ratio]{\includegraphics[height=4cm]{figs/experiments/exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge_expansion_ratio.pdf}}
-    \caption{Memory usage under different numbers of vertices of the graph.
-The graph was generated with the R-MAT generator fixing the number of edges at 500K and the dimension of the input feature vectors at 32.}
+    \caption{Memory usage under different numbers of vertices. The random graphs were generated by fixing the number of edges at 500K and the dimension of input feature vectors at 32.}
     \label{fig:exp_memory_expansion_ratio_input_graph_number_of_vertices_fixed_edge}
@@
 
-\paragraph{Summary}
-The \emph{high} memory expansion ratio severely restrictes the data scalability of the GNN training.
-The memory usage mainly comes from the intermediate results of the \emph{edge calculation stage}.
-Fixing the number of vertices, the memory usage increases \emph{linearly} along with the number of edges.
-Optimizing the memory usage of the edge calculation stage can significantly reduce the memory expansion ratio.
-Fixing the GNN structures and the hyper-parameters, increasing the dimension of the input feature vectors can also reduce the memory expansion ratio.
+\paragraph{Summary of Memory Usage}
+%
+The \emph{high} memory expansion ratio severely restricted the data scalability of GNN training.
+%
+The memory usage mainly came from the intermediate results of the \emph{edge calculation stage}.
+%
+Fixing the number of vertices, the memory usage increased \emph{linearly} along with the number of edges.
+%
+Fixing the GNN structure and the hyper-parameters, increasing the dimension of input feature vectors could reduce the memory expansion ratio.
+%
+To reduce the memory usage of GNN training, optimizations should focus on reducing memory footprints of the edge calculation stage.
 
@@
 
-With the sampling techniques, GNNs can be trained in a mini-batch manner.
-Each mini-batch updates the model parameters based on a small subgraph sampled from the original input graph.
-Thus, the training time per batch and the peak memory usage during the training should both decline significantly.
+With the sampling techniques, GNNs were trained in a mini-batch manner.
+%
+Each mini-batch updated the model parameters based on a small subgraph sampled from the original input graph.
+%
+Thus, the training time per batch and the peak memory usage during the training both declined significantly.
 
-In the implementation in PyG, the GNN model and the dataset resides on the GPU side.
-To process each epoch, PyG samples the original dataset in the main memory and generates several batches.
-Each batch is a small subgraph of the dataset.
-To train on each batch, PyG sends the sampled subgraph to the GPU, calculates the gradients on the subgraph, and updates the model parameters directly on the GPU.
-With the sampling techniques, the model parameters are updated by a stochastic gradient descent optimizer.
-PyG conducts the evaluation phase every several epochs (either on the CPU side or the GPU side) to determine whether to stop the training.
-In this section, the experiments focus on the training phase of each batch.
+In the implementation in PyG, the GNN model and the dataset resided on the GPU side.
+%
+To process each epoch, PyG sampled the original dataset in the main memory and generated several batches.
+%
+Each batch was a small subgraph of the dataset.
+%
+To train on each batch, PyG sent the sampled subgraph to the GPU, calculated the gradients on the subgraph, and updated the model parameters directly on the GPU.
+%
+With the sampling techniques, the model parameters were updated by a stochastic gradient descent optimizer.
+%
+PyG conducted the evaluation phase every several epochs or batches (either on the CPU side or the GPU side) to determine whether to stop the training.
+%
+In this section, the experiments focused on the training phase of each batch.
 
-\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changes with the batch size.
-For the neighbor sampler, the relative batch size is the proportion of the sampled vertices of the last GNN layer in $|\mathcal{V}|$.
-For the cluster sampler, the relative batch size is the proportion of the sampled partitions to all partitions of the graph.
-The neighbor sampler is very sensitive to the batch size.
-As the batch size increases, the size of the sampled subgraph first increases quickly and then stabilizes.
-The cluster sampler is much less sensitive compared to the neighbor sampler.
-The number of vertices and the average degree of the sampled subgraphs increases linearly with the batch size.
+\figurename~\ref{fig:exp_sampling_minibatch_graph_info} shows how the size of the sampled subgraph changed with the batch size.
+%
+For the neighbor sampler, the relative batch size was the proportion of the sampled vertices of the last GNN layer in $\mathcal{V}$.
+%
+For the cluster sampler, the relative batch size was the proportion of the sampled partitions in all partitions of the graph.
+%
+The neighbor sampler was very sensitive to the batch size.
+%
+As the batch size increased, the size of the sampled subgraph first increased quickly and then stabilized.
+%
+The cluster sampler was much less sensitive compared to the neighbor sampler.
+%
+The number of vertices and the average degree of the sampled subgraphs increased linearly with the batch size.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
     \subfloat[Cluster sampler]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_minibatch_realtive_graph_info_cluster_gcn.pdf}}
-    \caption{Sizes of the sampled subgraphs under different batch sizes.
-Each batch size was sampled 50 times and the average value was reported.
-The error bar indicates the standard deviation.
-The batch size is relative to the full graph.}
+    \caption{Sizes of sampled subgraphs under different relative batch sizes.
+The batch size was relative to the full graph.
+Each batch size was sampled 50 times and the average values were reported.
+The error bar indicates the standard deviation.}
     \label{fig:exp_sampling_minibatch_graph_info}
@@
 
-It is worth noting that the average degree of the sampled subgraph is \emph{much lower} than the average degree of the whole graph, especially when the relative batch size is low.
-Taking the neighbor sampler with the relative batch size of 6\% as an example, the average degree of the \texttt{amp} dataset is 31.1, but the average degree of the sampled subgraph is only 5.8.
-For the cluster sampler, the average degree is 3.0.
+The average degree of the sampled subgraph was \emph{much lower} than the average degree of the original graph, especially when the relative batch size is low.
+%
+Taking the neighbor sampler with the relative batch size of 6\% as an example, the average degree of the \texttt{amp} dataset was 31.1, but the average degree of the sampled subgraph was only 5.8.
+%
+For the cluster sampler, the average degree was 3.0.
+%
 \figurename~\ref{fig:exp_sampling_minibatch_degrees_distribution} compares the degree distribution of the sampled subgraphs with the original graph.
-The slopes of the curves are similar.
-It indicates that the sampled subgraphs still follow the power-law degree distribution.
-However, there are much less vertices in the sampled subgraphs, significantly lowering the average degrees.
-According to the experimental results in Section~\ref{sec:training_time_breakdown}, if the average degree becomes lower, the proportion of the training time spent on the vertex calculation stage will become higher, especially for GGNN.
+%
+The slopes of the curves were similar, indicating that the sampled subgraphs still followed the power-law degree distribution.
+%
+However, the numbers of high-degree vertices were much less than the original graph, lowering the average degrees.
+%
+According to the experimental results in Section~\ref{sec:training_time_breakdown}, if the average degree became lower, the proportion of the training time spent on the vertex calculation stage would become higher, especially for GGNN.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 
-\begin{figure}[h]
+To find out performance bottlenecks of the sampling techniques, we decomposed the training time per batch into three phases: \emph{sampling} on the CPU side, \emph{transferring} sampled subgraphs from the CPU side to the GPU side, and \emph{training} with the sampled subgraphs on the GPU side.
+%
+\figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.
+%
+For the neighbor sampler, the sampling technique reduced the training time per batch only when the batch size was very small.
+%
+When the batch became bigger, the sampling and the data transferring phases introduced noticeable overheads, making the training time exceed the full-batch training.
+%
+For the clustering sampler, the sampled subgraph was smaller than the neighbor sampler under the same relative batch size.
+%
+The reduction in the training time was more obvious than the neighbor sampler.
+%
+However, the overheads increased quickly as the relative batch size increased.
+%
+The training time under the 25\% relative batch size already exceeded the time of full-batch training.
+%
+The experimental results indicated that the current implementation of the sampling techniques in PyG was inefficient.
+%
+When the batch size was large, more than 50\% of the time had been spent on sampling and data transferring.
+%
+\emph{The sampling techniques were only efficient under small batch sizes.}
+
+\begin{figure}[H]
     \centering
@@
 
-To find out the performance bottleneck with the sampling techniques, we decompose the training time per batch into three phases: \emph{sampling} on the CPU, \emph{transferring} sampled subgraphs from the CPU to the GPU and \emph{training} with the subgraphs on the GPU.
-\figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.
-For the neighbor sampler, the sampling technique reduces the training time per batch only when the batch size is very small.
-When the batch becomes bigger, the sampling and the data transferring phases introduce noticeable overheads, making the training time exceed the full-batch training.
-For the clustering sampler, the sampled subgraph is smaller than the neighbor sampler under the same relative batch size.
-The reduction in the training time is more obvious than the neighbor sampler.
-However, the overheads increase quickly as the relative batch size increase.
-The training time under the 25\% relative batch size already exceede the time of full-batch training.
-The experimental results indicate that the current implementation of the sampling techniques in PyG is inefficient.
-When the batch size is slightly big, more than 50\% of the time has been spent on sampling and data transferring.
-\emph{The sampling techniques are only efficient under small batch sizes.}
+The main advantage of the sampling techniques was \emph{reducing the peak memory usage} during training.
+%
+\figurename~\ref{fig:exp_sampling_memory_usage} shows the memory usage under different batch sizes.
+%
+The peak memory usage declined significantly even under big batch sizes.
+%
+The sampling techniques made training GNNs on big graphs \emph{possible} for GPUs.
 
-\begin{figure}[tbp]
+\begin{figure}[H]
     \centering
@@
     \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=4cm]{figs/experiments/exp_sampling_memory_usage_relative_batch_size_cluster_flickr_peak_memory.pdf}}
-    \caption{Peak memory usage under different batch sizes. FULL means the full graph participates in the training.}
+    \caption{Peak memory usage under different batch sizes. FULL means that the full graph participated in the training.}
     \label{fig:exp_sampling_memory_usage}
@@
 
-The main advantage of the sampling technique is \emph{reducing the peak memory usage} during the training.
-\figurename~\ref{fig:exp_sampling_memory_usage} shows the memory usage under different batch sizes.
-The peak memory usage declines significantly even under big batch sizes.
-The sampling techniques make training GNNs on big graphs possible for GPUs.
+The disadvantage of the sampling technique was wasting GPU resources.
+%
+As the sampling techniques were only effective under small batch sizes, the sampled subgraphs were very small in those cases.
+%
+They could not make full use of the computing power of a GPU.
+%
+To simulate the situation, we generated random graphs with few vertices and measured the training time per batch in \figurename~\ref{fig:exp_small_graph_train_time}.
+%
+As the number of vertices increased, the training time was almost unchanged except for GaAN.
+%
+The training time of GaAN increased only with $|\mathcal{V}| \geq 4000$.
 
-\begin{figure}[tbp]
+\begin{figure}[H]
     \centering
@@
     \caption{Training time per epoch on small random graphs.
-For each number of vertices, we generated 50 random R-MAT graphs with the average degree of 4.0 and reported the average training time per epoch (without the evaluation phase).
+For each number of vertices, we generated 50 random graphs with the average degree of 4.0 and reported the average training time per batch (without the evaluation phase).
 The error bar indicates the standard deviation.}
@@
 
-The disadvantage of the sampling technique is wasting GPU resources.
-As the sampling techniques are only effective under small batch sizes, the sampled subgraphs will be very small in those cases.
-They cannot make full use of the computing power of a GPU.
-To simulate the situation, we generated random graphs with few vertices and measured the training time per epoch in \figurename~\ref{fig:exp_small_graph_train_time}.
-As the number of vertices increases, the training time is almost unchanged except for GaAN.
-The training time of GaAN increases only with $|\mathcal{V}| \geq 4000$.
+\paragraph{Summary of Sampling Techniques}
 
-\paragraph{Summary}
-The sampled subgraphs have lower average degrees than the whole graph.
-With small batch sizes, the sampling techniques can significantly reduce the training time per batch and the peak memory usage during the training.
-However, small batch sizes cannot make full use of the computing power of a GPU.
-With big batch sizes, the current implementation of the sampling techniques in PyG is inefficient.
-The time spent on the sampling phase and the data transferring phase even exceeds the training phase.
+The sampled subgraphs had lower average degrees than the original graph.
+%
+With small batch sizes, the sampling techniques could significantly reduce the training time per batch and the peak memory usage.
+%
+However, small batch sizes could not make full use of the computing power of a GPU.
+%
+With big batch sizes, the current implementation of the sampling techniques in PyG was inefficient.
+%
+The time spent on the sampling phase and the data transferring phase even exceeded the training phase.

### 2020-12-20 NEUROC/sec5-insights.tex
neuroc_final
增加了Motivation各个数据集的代码
回复R1Q1.
统一实验部分的时态问题。

--- 2020-08-29 CCPE/Mauscript/sec5-insights.tex
@@
 \begin{enumerate}
-    \item \emph{The time complexity in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} points out the performance bottleneck theoretically.}
+    \item \emph{The time complexity in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} points out performance bottlenecks theoretically.}
           The experimental results validate the time complexity analysis.
@@
                     For example, the attention mechanism in GNNs (like GAT and GaAN) requires an extra sub-layer to calculate the attention weight of each edge.
-                    Implementing it with the specially optimized basic operators on GPU is a potential optimization.
+                    Implementing the attention mechanism with specially optimized basic operators on the GPU side is a potential optimization.
               \item If the complexity of $\phi$ is low, the efficiency of the collection step and the aggregation step becomes critical.

### 2020-12-20 NEUROC/Response-MajRev/response_letter.tex
回复R1Q4.

@@
 \\
- - The sentences in the experimental section should be unified.\\
+ - The sentences in the experimental section should be unified.
 \end{point}
@@
 \begin{reply}
+
     Thank you for pointing them out.
@@
     %
-We have also unified the sentences that describe the experimental results  in the experimental section in the past tense.
+    We have also unified the tenses of the sentences in Section 3 ``Evaluation Design'' and Section 4 ``Evaluation Results and Analysis''.
+    %
+    We use the past tense to describe experimental methods, results and what they indicate.
+    %
+    We only use the present tense in the sentences that Figure/Table X are the subjects of the sentences.
+
+\end{reply}
+
+\begin{point}
+    Figures 6 and 7 should be adjusted. The figures and fonts are too small.
+\end{point}
+
+\begin{reply}
+
+    We appreciate your comment.
+    %
+    We have enlarged Figure 6 and Figure 7 in the revised manuscript.
+    %
+    Besides them, we have also enlarged fonts in other figures in the manuscript, to make sure that font sizes in figures are no less than the font size of figure captions.
+
+\end{reply}
+
+\begin{point}
+    In my view, computation efficiency is to describe the testing or validation process.
+Except for reporting and analyzing the training times, it is meaningful to discuss the inference time.
+This is also an important point of view for deep learning researchers to be concerned about.
+\end{point}
+
+\begin{reply}
+    %%% TODO %%%
 \end{reply}
@@
 	Our reply to it with reference to one of our points above using the \LaTeX's 
-	label/ref system (see also \ref{pt:foo}).
 \end{reply}

### 2020-12-20 NEUROC/sec4-experiments.tex
修改了Fig5,6,7,23的问题

@@
     \centering
-    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
-    %
+    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
+    \\
     \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}

### 2020-12-21 NEUROC/sec4-experiments.tex
更新sample实验的描述。

--- 2020-12-20 NEUROC/sec4-experiments.tex
@@
 
-In the implementation in PyG, the GNN model and the dataset resided on the GPU side.
+In the implementation in PyG, the GNN model resided on the GPU side and the dataset resided on the host side.
 %
@@
 %
-To train on each batch, PyG sent the sampled subgraph to the GPU, calculated the gradients on the subgraph, and updated the model parameters directly on the GPU.
+To train the GNN model with each batch, PyG sent the sampled subgraph to the GPU, calculated the gradients on the subgraph, and updated the model parameters directly on the GPU.
 %
@@
 %
-For the neighbor sampler, the relative batch size was the proportion of the sampled vertices of the last GNN layer in $\mathcal{V}$.
+For the neighbor sampler, the relative batch size was defined as the proportion of the sampled vertices of the last GNN layer in $\mathcal{V}$.
 %
-For the cluster sampler, the relative batch size was the proportion of the sampled partitions in all partitions of the graph.
+For the cluster sampler, the relative batch size was defined as the proportion of the sampled partitions in all partitions of the graph.
 %
-The neighbor sampler was very sensitive to the batch size.
+The experimental results indicated that the neighbor sampler was very sensitive to the batch size.
 %
@@
 %
-To simulate the situation, we generated random graphs with few vertices and measured the training time per batch in \figurename~\ref{fig:exp_small_graph_train_time}.
+To simulate the situation, we generated random graphs with few vertices and measured their training time per epoch in \figurename~\ref{fig:exp_small_graph_train_time}.
 %
@@
 %
-The training time of GaAN increased only with $|\mathcal{V}| \geq 4000$.
+The training time of GaAN increased only when $|\mathcal{V}| \geq 4000$.
 

### 2020-12-21 NEUROC/sec4-experiments.tex
更新图片的宽度.

@@
 
-To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the training time of the four GNNs.
+To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the training time of the four GNNs in \figurename~\ref{fig:exp_absolute_training_time}.
 %
@@
     \centering
-    \subfloat[\texttt{pub}\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}}
-    \subfloat[\texttt{aph}\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}}
-    \subfloat[\texttt{cph}\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}} \\
-    \subfloat[\texttt{amc}\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}}
-    \subfloat[\texttt{fli}\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}}
-    \subfloat[\texttt{cam}\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[height=4cm]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}}
+    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}
+    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}
+    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}
+
+    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}
+    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}
+    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}
+    %\subfloat[\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}}
+    %\subfloat[\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}}
+    %\subfloat[\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}} \\
+    %\subfloat[\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}}
+    %\subfloat[\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}}
+    %\subfloat[\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}}
     \caption{Distribution of the wall-clock training time of 50 epoches on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
@@
 
-To further evaluate effects of hyper-parameters on performance, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time}.
+To further evaluate effects of hyper-parameters on performance, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} to \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}.
 
@@
     \centering
-    \subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
-    \\
-    \subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}
-    \\
-    \subfloat[GAT\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}}
-    \\
-    \subfloat[GaAN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}]{\includegraphics[height=6cm]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}}
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN.}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
+\end{figure}
 
-    \caption{Effects of hyper-parameters on the edge/vertex calculation time.}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
 \end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN.}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
+\end{figure}
+
+%\begin{figure}[H]
+    %\centering
+    %\subfloat[GCN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}]{\includegraphics[width=0.6\textwidth]%{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}}
+%    \\
+    %\subfloat[GGNN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}]{\includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}
+%    \\
+    %\subfloat[GAT\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}]{\includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}}
+    %\\
+    %\subfloat[GaAN\label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}]{\includegraphics[width=0.9\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}}
+
+    %\caption{Effects of hyper-parameters on the edge/vertex calculation time.}
+    %\label{fig:exp_hyperparameter_on_vertex_edge_phase_time}
+%\end{figure}
 

### 2020-12-21 NEUROC/sec4-experiments.tex
更新实验图像。

@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
+    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
     \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN.}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
+    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
     \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
+    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GAT.}
     \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
+    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
     \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN.}

### 2020-12-21 NEUROC/sec4-experiments.tex
更新图片布局。

@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.pdf}}
-    \subfloat[GGNN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
-    \subfloat[GaAN]{\includegraphics[height=3cm]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.pdf}}
+    \subfloat[GCN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
+    \subfloat[GaAN]{\includegraphics[width=0.75\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.pdf}}
     \caption{Effects of hyper-parameters on the peak GPU memory usage during the training, excluding the memory used by the dataset and the model parameters.}

### 2020-12-21 NEUROC/sec2-review-of-graph-neural-network.tex
更新第二章

@@
 By default, GNNs are trained in a full-batch way, using the whole graph in each iteration.
-The full-batch gradient descent has two disadvantages \cite{chiang2019_cluster_gcn}.
-It has to cache intermediate results of all vertices in the forward phase, which consumes lots of memory space.
-It updates the parameters only once for each epoch, slowing the convergence of gradient descent.
+%
+The full-batch gradient descent has two disadvantages \cite{chiang2019_cluster_gcn}:
+%
+(1) it has to cache intermediate results of all vertices in the forward phase, which consumes lots of memory space;
+%
+(2) it updates the model parameters only once for each epoch, slowing the convergence of gradient descent.
 
-To train GNNs in a mini-batch way, the sampling techniques are proposed.
+To train GNNs in a mini-batch way, the sampling techniques \cite{hamilton2017_graphsage, ying2018_pinsage, chen2018_fastgcn, chen2018_sgcn, zeng2018_aesg, chiang2019_cluster_gcn, zeng2020_graphsaint} are proposed.
+%
 In each mini-batch, they sample a small subgraph from the whole graph $\mathcal{G}$ and uses the subgraph to update the model parameters.
+%
 The sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:gnn_sampling}.
-In active graph neurons and connections do not participate in the training of this mini-batch, saving lots of computation and storage costs.
+%
+Inactive graph neurons and connections do not participate in the training of this mini-batch, saving lots of computation and storage costs.
+%
 Moreover, it may reduce the risk of overfitting the training graph.
-The existing sampling techniques can be classified into two groups \textbf{neighbor sampling and graph sampling} based on whether different GNN layers sample different subgraphs.
+%
+The existing sampling techniques can be classified into two groups: \emph{neighbor sampling} and \emph{graph sampling}, based on whether different GNN layers sample different subgraphs.
 
 The neighbor sampling techniques \cite{hamilton2017_graphsage, ying2018_pinsage, chen2018_fastgcn, chen2018_sgcn, huang2018_adap} sample nodes or edges layer by layer.
-The sampled subgraphs of different GNN layers may be \emph{different}, as shown in \figurename~\ref{fig:gnn_sampling_neighbor_sampling}.
-GraphSAGE \cite{hamilton2017_graphsage} is the representative technique.
+%
+The sampled subgraphs of different GNN layers may be \emph{different}, as shown in \figurename~\ref{fig:gnn_sampling}(a).
+%
+GraphSAGE \cite{hamilton2017_graphsage} is a representative neighbor sampling technique.
+%
 The tecnnique first samples several vertices from $\mathcal{V}$ in the last GNN layer.
-Then it repeatedly samples the neighbors of those sampled vertices in the previous layer until the input layer.
-For every sampled vertex $v_x$ in the GNN layer $l$, GraphSAGE samples at most $S^l$ neighbors of $v_x$ from the previous GNN layer.
-$S^l$ is the hyper-parameter that is usually much smaller than $|\mathcal{V}|$.
-In this way, GraphSAGE limits the neighborhood sizes of the vertices in the sampled subgraph, especially high-degree vertices.
+%
+Then it repeatedly samples the neighbors of the sampled vertices from the previous layer until the input layer.
+%
+For every sampled vertex $v_x$ in the GNN layer $l$, GraphSAGE samples at most $\eta^l$ neighbors of $v_x$ from the previous layer.
+%
+$\eta^l$ is the hyper-parameter that is usually much smaller than $|\mathcal{V}|$.
+%
+By this way, GraphSAGE limits neighborhood sizes of vertices in the sampled subgraph, especially high-degree vertices.
 
-\begin{figure}
+\begin{figure}[H]
     \centering
-    \subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4.5cm]{figs/illustration/layer_sampling.pdf}}
+    \includegraphics[width=0.9\columnwidth]{figs/illustration/sampling_techniques.pdf}
+    %\subfloat[Neighbor sampling\label{fig:gnn_sampling_neighbor_sampling}]{\includegraphics[height=4.5cm]{figs/illustration/layer_sampling.pdf}}
     %
-    \subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4.5cm]{figs/illustration/graph_sampling.pdf}}
+    %\subfloat[Graph sampling\label{fig:gnn_sampling_graph_sampling}]{\includegraphics[height=4.5cm]{figs/illustration/graph_sampling.pdf}}
     \caption{Training a GNN with sampling techniques. The faded graph neurons and their connections are inactivated.}
@@
 
-The graph sampling techniques \cite{zeng2018_aesg, chiang2019_cluster_gcn, zeng2020_graphsaint} sample a subgraph for each mini-batch and use the same sampled graph for all GNN layers, as shown in \figurename~\ref{fig:gnn_sampling_graph_sampling}.
-They differ in the methods to sample subgraphs.
-The cluster sampler technique \cite{chiang2019_cluster_gcn} is the representative technique.
-Given a training graph $\mathcal{G}$, it partitions $\mathcal{G}$ into dense clusters.
+The graph sampling techniques \cite{zeng2018_aesg, chiang2019_cluster_gcn, zeng2020_graphsaint} sample a subgraph for each mini-batch and use the same sampled subgraph for all GNN layers, as shown in \figurename~\ref{fig:gnn_sampling}(b).
+%
+They differ in how to sample subgraphs.
+%
+The cluster sampler technique \cite{chiang2019_cluster_gcn} is a representative graph sampling technique.
+%
+Given a training graph $\mathcal{G}$, it partitions $\mathcal{G}$ into several dense clusters.
+%
 For each mini-batch, it randomly pick $N$ clusters to form the sampled subgraph, where $N$ is the hyper-parameter.

### 2020-12-21 NEUROC/sec4-experiments.tex
更新第二章

@@
     \centering
-    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}
-    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}
-    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}
+    \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}
+    \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}
+    \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}
 
-    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}
-    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}
-    \includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}
+    \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}
+    \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}
+    \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}
     %\subfloat[\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
     \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
     \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
     \caption{Effects of hyper-parameters on the vertex/edge calculation time of GAT.}

### 2020-12-21 NEUROC/sec3-experiment-design.tex
粗略修改了Q1

@@
 
+% added by wangyupan, 2020-12-21 ----start----
+In the precision experiment of hyper-parameters, we used the same training procedure for all the models. 
+%
+That is, we used the same optimizer (Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
+same initialization (weights initialized according to \cite{xavier2010_glorot}, biases initialized with zeros), same maximum epochs, and same early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}.
+%
+We trained for a maximum of 100k epochs. 
+%
+If total validation loss (loss on the data plus regularization loss) did not improve for 50 epochs, we would stop training. 
+%
+We reset the state of the weights of the step with the lowest validation loss and got the reported test accuracy.
+%
+Besides, in the precision experiment of sampling techniques, we selected the network structure corresponding to the highest accuracy in the hyperparameter experiment for each dataset of each model.
+% added by wangyupan, 2020-12-21 ----end----
+
 \paragraph{Sampling Techniques}
@@
 
+% added by wangyupan, 2020-12-21 ----start----
+In sampled-based inference experiment, according to \cite{weihua2020_ogb-benchmark}, we used neighbor sampler \cite{hamilton2017_graphsage} with batch size of 1024 and all neighbors were inclued in all layers.
+% added by wangyupan, 2020-12-21 ----end----
+
 \subsection{Experimental Scheme}
@@
 
-    \item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
-
+    \item[Q1] \emph{How do the hyper-parameters affect the training time, the memory usage, and the accuracy of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
+          % TODO: 进一步修改
           Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
@@
           %
-          To evaluate their effects, we measured how the training time per epoch and the peak memory usage (of the GPU) changed as we increased the values of the hyper-parameters.
+          To evaluate their effects, we measured how the training time per epoch, the peak memory usage (of the GPU), and the accuracy changed as we increased the values of the hyper-parameters.
           %

### 2020-12-22 NEUROC/sec2-review-of-graph-neural-network.tex
新增inference的过程介绍。

@@
 For each mini-batch, it randomly pick $N$ clusters to form the sampled subgraph, where $N$ is the hyper-parameter.
+
+In the implementation in PyG, the model parameters of GNNs resid on the GPU side and the input graph resides on the host side.
+%
+To process an epoch, PyG samples the original graph in the main memory and generates several batches for the epoch.
+%
+For each batch, PyG sends the sampled subgraph to the GPU, propagates the feature vectors of the sampled subgraph from the input layer to the prediction layer, calculates the gradients on the subgraph, and updates the model parameters based on the gradients directly on the GPU.
+%
+With the sampling techniques, the model parameters are updated by a stochastic gradient descent optimizer.
+%
+PyG conducts the evaluation phase every several epochs or batches (either on the CPU side or the GPU side) to determine whether to stop the training.
+
+\subsection{Inference with GNNs}
+
+The model parameters of a GNN are stored in the weight vectors/matrices of the prediction layer and the messaging/aggregation/updating functions of each GNN layer.
+%
+When we want to perform inference on a new graph based on a trained GNN, the structure of the GNN needs to be adjusted, but the hyper-parameters and the model parameters of the GNN remain unchanged.
+%
+The number of graph neurons in each GNN layer has to be adjusted to $|\mathcal{V}|$ of the new graph.
+%
+The connections of graph neurons between GNN layers also needs to be adjusted according to the edge set of the new graph.
+
+During inference, input feature vectors of the new graph are propagated forward from the input layer to the prediction layer to give out predicted labels.
+%
+The workflow of inference is the same as the workflow of the \emph{forward} phase during training.
+%
+The only difference from the forward phase is that there is no need to cache intermediate calculation results during inference, because inference does not need to prepare for gradient calculation.
+
+Inference methods can be divided into two types based on the range of input graphs involved in inference: full-batch inference and sample-based inference.
+%
+The full-batch inference performs inference on the whole input graph at once.
+%
+It can make full use of the computing power of GPUs, bringing high computation efficiency.
+%
+The full-batch inference is suitable for small graphs that the GPU memory can hold all feature vectors, models, and intermediate results.
+
+Different from the full-batch inference, the sample-based inference only predicts labels for part of vertices/edges each time, limiting the GPU memory usage during inference.
+%
+It first samples a subgraph related to inference from the input graph and then performs the full-batch inference on the sampled subgraph.
+%
+The sampling method depends on the prediction task.
+%
+Taking the node classification scenario as an example, if there are $L$ GNN layers in the GNN, the hidden vector outputted by the last GNN layer of each vertex $\MyVec{h}^L_x$ is only related to the $L$-hop neighborhood of $v_x$.
+%
+Thus, if we want to predict labels for a group of vertices, we only need to sample a subgraph that contains $L$-hop neighborhoods of all given vertices.
+%
+The sample-based inference is suitable for processing big graphs.
+%
+It stores the whole input graph and its feature vectors in the main memory.
+%
+It processes the whole graph in batches.
+%
+The subgraph of each batch is sampled on the CPU side and sent to the GPU side to perform inference.
+%
+By using small batch sizes, the peak memory usage during inference can be limited under the GPU memory capacity.

### 2020-12-22 NEUROC/sec4-experiments.tex
新增inference的过程介绍。

@@
 %
-Each mini-batch updated the model parameters based on a small subgraph sampled from the original input graph.
+Each epoch was decomposed into many batches.
 %
-Thus, the training time per batch and the peak memory usage during the training both declined significantly.
-
-In the implementation in PyG, the GNN model resided on the GPU side and the dataset resided on the host side.
+In each batch, PyG only sent the sampled subgraph to the GPU to train or inference.
 %
-To process each epoch, PyG sampled the original dataset in the main memory and generated several batches.
-%
-Each batch was a small subgraph of the dataset.
-%
-To train the GNN model with each batch, PyG sent the sampled subgraph to the GPU, calculated the gradients on the subgraph, and updated the model parameters directly on the GPU.
-%
-With the sampling techniques, the model parameters were updated by a stochastic gradient descent optimizer.
-%
-PyG conducted the evaluation phase every several epochs or batches (either on the CPU side or the GPU side) to determine whether to stop the training.
-%
-In this section, the experiments focused on the training phase of each batch.
+Since the sampled subgraphs could be much smaller than the original graph, the experiments in this section focused on finding out how the sample size affected the training time, the memory usage and the accuracy of GNNs.
 

### 2020-12-22 NEUROC/sec3-experiment-design.tex

--- 2020-12-19 NEUROC/sec3-experiment-design.tex
@@
 
+% added by wangyupan, 2020-12-21 ----start----
+In the precision experiment of hyper-parameters, we used the same training procedure for all the models. 
+%
+That is, we used the same optimizer(Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
+same initialization(weights initialized according to \cite{xavier2010_glorot}, biases initialized with zeros), same maximum epochs, and same early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}.
+%
+We trained for a maximum of 100k epochs. 
+%
+If total validation loss (loss on the data plus regularization loss) did not improve for 50 epochs, we would stop training. 
+%
+We reset the state of the weights of the step with the lowest validation loss and got the reported test accuracy.
+%
+Besides, in the precision experiment of sampling techniques, we selected the network structure corresponding to the highest accuracy in the hyperparameter experiment for each dataset of each model.
+% added by wangyupan, 2020-12-21 ----end----
+
 \paragraph{Sampling Techniques}
@@
 For the cluster sampler, we partitioned the input graph into 1500 partitions and used 20 partitions per batch, according to \cite{chiang2019_cluster_gcn}.
+
+% added by wangyupan, 2020-12-21 ----start----
+In sampled-based inference experiment, according to \cite{weihua2020_ogb-benchmark}, we used neighbor sampler \cite{hamilton2017_graphsage} with batch size of 1024 and all neighbors were inclued in all layers.
+% added by wangyupan, 2020-12-21 ----end----
 

### 2020-12-22 NEUROC/sec4-experiments.tex
4.1增加了超参数对精度影响的说明

--- 2020-12-21 NEUROC/sec4-experiments.tex
@@
 %
-Its time complexity shoud be affected by $dim(\boldsymbol{h}^1_x)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1_x)$), $d_a$, $d_v$, $d_m$, and the number of heads $K$.
+Its time complexity should be affected by $dim(\boldsymbol{h}^1_x)$ ($d^0_{out} = d^1_{in} = dim(\boldsymbol{h}^1_x)$), $d_a$, $d_v$, $d_m$, and the number of heads $K$.
 %
@@
 
+% added by wangyupan, 2020-12-22 ----start----
+In deep learning, accuracy is also an important indicator that algorithm engineers care about.
+%
+We adopted a unified standard (section \ref{sec:hyper-parameters}) to evaluate the effect of hyper-parameters on accuracy.
+%
+\figurename~\ref{fig:exp_hyperparameter_accuracy} shows how the accuracy varies with hyper-parameters.
+%
+For all models, we found that different datasets had different curve changes, that was, different datasets had different sensitivity to hyper-parameter changes.
+%
+This was because different datasets had different characteristics, which lead to different learning difficulties.
+%
+
+Except for the effect of the number of heads on GAT and the effect of $d_a$, $d_v$, $d_m$, the number of heads $K$ on GaAN, we found the same phenomena:
+the accuracy of the model was often low when hyper-parameters were low. When a certain threshold was reached, the accuracy began to fall within the range of fluctuations.
+%
+We conducted additional experiments for these exceptions. Taking the effect of the number of heads on GAT as an example, 
+\figurename~\ref{fig:exp_hyperparameter_accuracy_gat_small_info} shows the trend is similar to the phenomena discussed above when $d_{head}$ is adjusted to a smaller value such as 2 and 4.
+%
+This phenomenon showed some relationship between accuracy and model complexity.
+%
+When the hyper-parameter value was very small, the model complexity was often low, which limited the expressive ability of the model.
+%
+In this case, accuracy and model complexity were positively related.
+%
+However, when the hyper-parameter increased to a certain threshold, the model had sufficient learning ability, and the relationship between accuracy and model complexity was no longer certain.
+% added by wangyupan, 2020-12-22 ----end----
+
+\begin{figure}[H]
+    \centering
+    \subfloat[GCN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat.pdf}}\\
+    \subfloat[GaAN]{\includegraphics[width=0.75\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
+    \caption{Effects of hyper-parameters on accuracy of four models.}
+    \label{fig:exp_hyperparameter_accuracy}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat_small_info.pdf}
+    \caption{Effects of the number of heads on GAT ($d_{head}$=2,4)}
+    \label{fig:exp_hyperparameter_accuracy_gat_small_info}
+\end{figure}
+
 \paragraph{Summary}
 
-The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} is valid.
+The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} was valid.
 %
-Fixing other hyper-parameters, each hyper-parameter itself affects the training time and the memory usage of a GNN Layer \emph{in a linear way}.
+Fixing other hyper-parameters, each hyper-parameter itself affected the training time and the memory usage of a GNN Layer \emph{in a linear way}.
 %
-Algorithm engineers can adjust hyper-parameters according to the time complexity to avoid explosive growth in the training time and memory usage.
+Algorithm engineers could adjust hyper-parameters according to the time complexity to avoid explosive growth in the training time and memory usage.
+%
+% added by wangyupan, 2020-12-22 ----start----
+There was no definite relationship between accuracy and hyper-parameters. 
+%
+To obtain the optimal model, hyper-parameters needed to be manually adjusted by algorithm engineers.
+% added by wangyupan, 2020-12-22 ----end----
 

### 2020-12-22 NEUROC/sec3-experiment-design.tex
4.1增加了超参数对精度影响的说明
fix语法

--- 2020-12-21 NEUROC/sec3-experiment-design.tex
@@
 \paragraph{Hyper-parameters}
+\label{sec:hyper-parameters}
+
 We use $dim(\boldsymbol{x})$ to denote the dimension of a vector $\boldsymbol{x}$.
@@
 %
-That is, we used the same optimizer (Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
+That was, we used the same optimizer (Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
 same initialization (weights initialized according to \cite{xavier2010_glorot}, biases initialized with zeros), same maximum epochs, and same early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}.

### 2020-12-22 NEUROC/sec3-experiment-design.tex
更新response.

--- 2020-12-22 NEUROC/sec3-experiment-design.tex
@@
 
-    \item[Q1] \emph{How do the hyper-parameters affect the training time and the memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
+    \item[Q1] \emph{How do the hyper-parameters affect the training/inference time and memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
 
@@
           %
-          The hyper-parameters affect the training time per epoch and the peak memory usage during training.
+          The hyper-parameters affect the processing time per epoch and the peak memory usage during training and inference.
           %

### 2020-12-22 NEUROC/sec3-experiment-design.tex

--- 2020-12-22 NEUROC/sec3-experiment-design.tex
@@
 
-    \item[Q1] \emph{How do the hyper-parameters affect the training time, the memory usage, and the accuracy of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
-          % TODO: 进一步修改
+    \item[Q1] \emph{How do the hyper-parameters affect the training/inference time and memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
+
           Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
           %
-          The hyper-parameters affect the training time per epoch and the peak memory usage during training.
+          The hyper-parameters affect the processing time per epoch and the peak memory usage during training and inference.
           %

### 2020-12-22 NEUROC/sec3-experiment-design.tex
更新了Hyper-parameters中的表述

--- 2020-12-22 NEUROC/sec3-experiment-design.tex
@@
 % added by wangyupan, 2020-12-21 ----start----
-In the precision experiment of hyper-parameters, we used the same training procedure for all the models. 
+We used Adam \cite{diederik2015_adam} with a learning rate of 0.01 and a weight decay of 1e-5.
 %
-That was, we used the same optimizer (Adam \cite{diederik2015_adam} with a learning rate of 0.01 and L2 regularization of 1e-5), 
-same initialization (weights initialized according to \cite{xavier2010_glorot}, biases initialized with zeros), same maximum epochs, and same early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}.
+We initialized weights using initialization described in \cite{xavier2010_glorot} and initialized bias with zeros.
 %
-We trained for a maximum of 100k epochs. 
-%
-If total validation loss (loss on the data plus regularization loss) did not improve for 50 epochs, we would stop training. 
-%
-We reset the state of the weights of the step with the lowest validation loss and got the reported test accuracy.
-%
-Besides, in the precision experiment of sampling techniques, we selected the network structure corresponding to the highest accuracy in the hyperparameter experiment for each dataset of each model.
+In the accuracy experiment of hyper-parameters, we trained all models for a maximum of 10k epochs and used early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}.
+We stopped training if the validation loss did not improve for 50 epochs. We reported the test accuracy of the epoch with the lowest validation loss.
 % added by wangyupan, 2020-12-21 ----end----

### 2020-12-22 NEUROC/Response-MajRev/response_letter.tex

@@
 
-% Point one description 
+% R1Q1
 \begin{point}
@@
 
+% R1Q2
 \begin{point}
@@
 
+% R1Q3
 \begin{point}
@@
 
+% R1Q4
 \begin{point}
@@
 
+% R1Q5
 \begin{point}
@@
 \begin{reply}
-    %%% TODO %%%
+    Thank you for the insightful comment.
+    %
+    The efficiency of inference (including inference time and memory usage) is also important for deep learning researchers and engineers.
+    %
+    To discuss the efficiency of GNN inference on GPUs, we have added a new subsection (Section 2.5 ``Inference with GNNs'') in the revised manuscript to briefly review how to perform inference with GNNs.
+    %
+    We have also added corresponding analysis on GNN inference in every subsection of Section 4 ``Evaluation Results and Analysis'' in the revised manuscript:
+    %
+    \begin{enumerate}
+        \item In Section 4.1 ``Effects of Hyper-parameters on Performance'', 
+    \end{enumerate}
+
 \end{reply}

### 2020-12-22 NEUROC/sec3-experiment-design.tex
合并王云攀的修改。

@@
 
-% added by wangyupan, 2020-12-21 ----start----
-We used Adam \cite{diederik2015_adam} with a learning rate of 0.01 and a weight decay of 1e-5.
+We used Adam \cite{diederik2015_adam} as the gradient descent optimizer with a learning rate of 0.01 and a weight decay of 1e-5.
 %
-We initialized weights using initialization described in \cite{xavier2010_glorot} and initialized bias with zeros.
+We initialized weights in GNNs using the method described in \cite{xavier2010_glorot} and initialized bias as zeros.
 %
-In the accuracy experiment of hyper-parameters, we trained all models for a maximum of 10k epochs and used early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}.
-We stopped training if the validation loss did not improve for 50 epochs. We reported the test accuracy of the epoch with the lowest validation loss.
-% added by wangyupan, 2020-12-21 ----end----
+Without otherwise mentioned, in the experiments related to accuracy evaluation, we trained all GNNs for a maximum of 100k epochs and used the early stopping criterion according to \cite{shchur2018_pitfall_of_gnn}:
+%
+the training was stopped if the validation loss did not improve for 50 epochs.
+%
+We chose the model parameters that achieved the lowest validation loss as the final model parameters.
+%
+The accuracy on the test set was evaluated with the final model.
 

### 2020-12-22 NEUROC/sec3-experiment-design.tex
删除一些错误
撰写R2Q1 & R2Q2的回复意见.

@@
 
-% added by wangyupan, 2020-12-21 ----start----
-In sampled-based inference experiment, according to \cite{weihua2020_ogb-benchmark}, we used neighbor sampler \cite{hamilton2017_graphsage} with batch size of 1024 and all neighbors were inclued in all layers.
-% added by wangyupan, 2020-12-21 ----end----
-
 \subsection{Experimental Scheme}
@@
 
-    \item[Q1] \emph{How do the hyper-parameters affect the training/inference time and memory usage of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
+    \item[Q1] \emph{How do the hyper-parameters affect the training/inference time, memory usage and accuracy of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
 
@@
           %
-          To evaluate their effects, we measured how the training time per epoch, the peak memory usage (of the GPU), and the accuracy changed as we increased the values of the hyper-parameters.
+          They also affect the accuracy of a GNN.
+          %
+          Larger hyper-parameter values usually mean more model parameters and more complex models.
+          %
+          To evaluate their effects, we measured how the training/inference time per epoch, the peak memory usage (of the GPU), and the accuracy on the test set changed as we increased the values of the hyper-parameters.
           %
@@
 
-    \item[Q2] \emph{Which stage is the most time-consuming stage in GNN training?} (Section~\ref{sec:training_time_breakdown})
+    \item[Q2] \emph{Which stage is the most time-consuming stage in GNN training and inference?} (Section~\ref{sec:training_time_breakdown})
 
@@
           Optimizing its implementation will significantly reduce the training time.
+          %
+          For GNN inference, we conducted similar experimental analysis.
+          %
+          We discussed the differences in performance characteristics between training and inference.
 
@@
 
-    \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
+    \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training?
+Does the use of sampling techniques in training affect the test accuracy?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
 
-          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training of a batch.
+          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training/inference of a batch.
           %
-          Consequently, the training time and the memory usage should also decrease.
+          Consequently, the processing time and memory usage per batch should also decrease.
           %
-          To validate effectiveness of sampling techniques, we measured the training time and peak memory usage under different batch sizes.
+          The test accuracy of GNNs may also be affected.
           %
-          If sampling techniques were effective, they will be the keys to conduct GNN training on very big graphs.
+          To validate effectiveness of sampling techniques, we measured the training time, peak memory usage and test accuracy under different batch sizes.
           %
-          If they were not effective, we want to find out which impairs its efficiency.
+          If sampling techniques are effective, they will be the keys to conduct GNN training on very big graphs.
+          %
+          If they are not effective, we want to find out which impairs its efficiency.
+          %
+
 \end{itemize}

### 2020-12-22 NEUROC/sec3-experiment-design.tex
增加了内存分析部分内容

--- 2020-12-22 NEUROC/sec3-experiment-design.tex
@@
 
-We use $dim(\boldsymbol{x})$ to denote the dimension of a vector $\boldsymbol{x}$.
+We used $dim(\boldsymbol{x})$ to denote the dimension of a vector $\boldsymbol{x}$.
 %
@@
 
-          Every GNN has a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
+          Every GNN had a group of hyper-parameters, such as the number of GNN layers and the dimensions of hidden feature vectors.
           %
-          The hyper-parameters affect the processing time per epoch and the peak memory usage during training and inference.
+          The hyper-parameters affected the processing time per epoch and the peak memory usage during training and inference.
           %

### 2020-12-22 NEUROC/sec4-experiments.tex
更新了Hyper-parameters中的表述
删除一些错误
增加了内存分析部分内容

@@
 
+% added by wangyunpan, 2020-12-22 ----start----
+\paragraph{Inference Time Breakdown Analysis}
+We conducted the same experiments in the inference stage as above.
+%
+The results of layer level experiment, step Level in edge Calculation experiment and operator Level experiment were in general consistent with those in the Training stage.
+%
+The performance bottleneck analysis in the Training stage can also be applied to the inference stage.
+% added by wangyunpan, 2020-12-22 ----end----
+
 \subsection{Memory Usage Analysis}
@@
 %
-GCN had the lowest MER (up to 15) while GaAN had the highest MER (up to 104).
+GCN had the lowest MER (up to 15.2) while GaAN had the highest MER (up to 104.6).
 %
@@
 To reduce the memory usage of GNN training, optimizations should focus on reducing memory footprints of the edge calculation stage.
+
+% added by wangyunpan, 2020-12-22 ----start----
+\paragraph{Inference Stage Memory Usage Analysis}
+
+% 不同点: phase
+\begin{figure}[H]
+    \centering
+    \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_usage_stage_amp.pdf}
+    \caption{Memory usage of each phase during the GNN training. Dataset: \texttt{amp}.}
+    \label{fig:exp_inference_full_memory_usage_stage_amp}
+\end{figure}
+
+% 不同点： 膨胀比例
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}
+    \caption{Memory expansion ratios of typical GNNs.}
+    \label{fig:exp_inference_full_memory_expansion_ratio}
+\end{figure}
+
+% 不同点: input feature dims
+\begin{figure}[H]
+    \centering
+    \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_expansion_ratio_input_feature_dimension_com-amazon_expansion_ratio.pdf}
+    \caption{Memory expansion ratio under different dimensions of input feature vectors. Dataset: \texttt{cam}.}
+    \label{fig:exp_inference_full_memory_expension_ratio_input_feature_dimension}
+\end{figure}
+
+For the inference stage, we did the same experiment as above. The experimental results were as follows:
+\begin{itemize}
+    \item \figurename~\ref{fig:exp_inference_full_memory_usage_stage_amp} shows the peak memory usage of each phase during inference stage.
+    \figurename~\ref{fig:exp_inference_full_memory_expansion_ratio} compares MER of different GNNs on inference stage. We found that 
+    \item
+\end{itemize}
+
+% added by wangyunpan, 2020-12-22 ----end----
 

### 2020-12-22 NEUROC/Response-MajRev/response_letter.tex

--- 2020-12-20 NEUROC/Response-MajRev/response_letter.tex
@@
 
-\section*{Response to the reviewers}
+\section*{Response to the Reviewers}
 % General intro text goes here
-We thank the reviewers for their critical assessment of our work. 
+We thank the reviewers for their critical assessment and insightful comments of our work.
+%
+We have made extensive modifications to our manuscript.
+%
 In the following we address their concerns point by point.
+%
+We also prepare an \emph{annotated version} for our revised manuscript.
+%
+In the annotated version, changes corresponding to each point are all highlighted by red squares.
+
+\subsection*{Summary of Changes}
+
+%%%% TODO %%%
 
@@
 
-% Point one description 
+% R1Q0
+\begin{point}
+    The authors conduct an empirical analysis of performance bottlenecks in graph neural network training.
+The authors identify the edge-related calculation is the performance bottleneck.
+Experimental of several GNN variants, such as GCN, GGNNNN, GAT and GaAN on six real-world graph datasets verify the importance of the findings.
+The experimental analysis is sufficient.
+However, there are some tiny issues in this paper.
+\end{point}
+
+\begin{reply}
+    Thank you for your positive comments on our manuscript.
+    %
+    We have carefully revised the manuscript according to your comments. 
+    %
+    Based on the suggestions, we have made an extensive modification on the revised manuscript.
+    %
+    Please see the detailed responses below.
+    %
+    The changes corresponding to each issue were highlighted by red squares in the annotated version of our manuscript.
+
+\end{reply}
+
+% R1Q1
 \begin{point}
@@
 \begin{reply}
-    We apologize for the confusing use of symbols.
+    We apologize for the confusing use of symbols and thank you for pointing the problem out.
     %
@@
     %
+    We feel really sorry for our carelessness.
+    %
     We have proofread our revised manuscript carefully to eliminate grammar errors and typos.
@@
 \begin{reply}
+    Thank you for the insightful comment and suggestion.
+    %
+    The efficiency of inference (including inference time and memory usage) is indeed important for deep learning researchers and engineers.
+    %
+    In the revised manuscript, we have added a new subsection (Section 2.5 ``Inference with GNNs'') in the revised manuscript to briefly review how to perform inference with GNNs.
+    %
+    To discuss the efficiency of GNN inference on GPUs, we have added performance bottleneck analysis on GNN inference in every subsection of Section 4 ``Evaluation Results and Analysis'':
+    %
+    \begin{enumerate}
+
+        \item In Section 4.1 ``Effects of Hyper-parameters on Performance'', we have additionally measured how the inference time and the peak memory usage changed as we increased the values of the hyper-parameters.
+        %
+        We find that ...
         %%% TODO %%%
+
+        \item In Section 4.2 ``Time Breakdown Analysis'', we have additionally conducted the time breakdown analysis for GNN inference.
+        %
+        We find that the performance characteristics of GNN inference are similar to GNN training.
+        %
+        The performance bottenecks in GNN inference are also similar to the bottlenecks in training.
+        %
+        Therefore, we focus on discussing the differences between GNN training and inference in the revised manuscript.
+
+        \item In Section 4.3 ``Memory Usage Analysis'', we have additionally conducted the memory usage analysis for GNN inference.
+        %
+        We find that ... 
+        %%% TODO %%%
+
+        \item In Section 4.4 ``Effects of Sampling Techniques on Performance'', we have additionally evaluated the performance bottlenecks in sample-based GNN inference.
+        %
+        We find that ...
+        %%% TODO %%%
+    \end{enumerate}
+
 \end{reply}
@@
 \begin{point}
-	This is the first point of Reviewer \thereviewer. With some more words foo
-	bar foo bar ...
+    In the paper, authors accomplished a unique study and analysis on GNN models training complexity.  The articles first review and development history of GNNs and creatively model all architectures as input layers, intermediate layers of graph neurons and prediction layers.
+And they quantitatively summarize the time and space complexity of 4 representative GNNs, including graph convolution, gated recurrent graph net, graph attention net and GraphSage.
+Most importantly, the article first break down complexity into operator level and offered analysis of good granularity, giving reader more guidance in future study.
+At last, the solid experiments included the study of effects of hyper-parameters and a comparison of two major sampling techniques: neighbor sampling and cluster sampling.
 \end{point}
@@
 \begin{reply}
-	Our reply to it with reference to one of our points above using the \LaTeX's 
+    Thank you for your positive comments on our manuscript.
+    %
+    We have carefully revised the manuscript according to your comments.
+    %
+    We have revised our manuscript according to your kindly suggestions.
+    %
+    Please see the detailed responses below.
+    %
+    We have highlighted our modification point by point in the annotated version of the manuscript by red squares.
+\end{reply}
+
+\begin{point}
+    In general, the paper was well written and organized with good structure and clear narratives.
+Just some minor language errors like line Page 8, Line 208, "In active graph neurons" =\textgreater "Inactive graph neurons".
+\end{point}
+
+% R2Q1
+\begin{reply}
+    Thank you for pointing them out.
+    %
+    We feel really sorry for our carelessness.
+    %
+    We have proofread our revised manuscript carefully to eliminate such language errors as much as we can.
+\end{reply}
+
+% R2Q2
+\begin{point}
+    I was impressed by the way that authors categorize layers and operators in GNNs, very clear and instructive.
+
+    It is also pretty neat to divide layer time complexity into two buckets: vertex calculation and edge calculation.
+The data model pretty well summarizes mainstream GNN layer architectures.
+And this analysis is very insightful for layer profiling.
+
+    And the experimental evaluation were done over 6 large graph-structured datasets.
+\end{point}
+
+\begin{reply}
+    Thank you very much for your appreciation.	
+\end{reply}
+
+% R2Q3
+\begin{point}
+    While, one major drawback is that I did not clearly see the analysis complexity v.s.
+accuracy.
+For example, in Figure 19 and 20, I did not see network accuracy from those 4 GNNs.
+There is always tradeoff between model complexity and model performance, and in some scenarios where high complexity is allowed, a sophisticated model of more powerful representation capability is still needed.
+\end{point}
+
+\begin{reply}
 \end{reply}

### 2020-12-22 NEUROC/Response-MajRev/response_letter.tex
粘贴进来所有的问题。

@@
 
+\begin{point}
+    Sampling method is definitely going to reduce model complexity, since all models complexity depend on graph node number N, while performance is going to be compromised as well.
+I would like to see authors resolve the concern of significant accuracy drop after applying aggressive sampling of subgraphs.
+\end{point}
+
+\begin{reply}
+
+\end{reply}
+
+\begin{point}
+    Hope authors supplement the effect of sampling and GNNs on accuracy while comparing different complexity of model and sampling methods.
+\end{point}
+
+\begin{reply}
+
+\end{reply}
+
 \end{document}

### 2020-12-22 NEUROC/sec4-experiments.tex
修改sec4关于full-batch inference的时间和内存分析

@@
 For the inference stage, we did the same experiment as above. The experimental results were as follows:
-\begin{itemize}
-    \item \figurename~\ref{fig:exp_inference_full_memory_usage_stage_amp} shows the peak memory usage of each phase during inference stage.
-    \figurename~\ref{fig:exp_inference_full_memory_expansion_ratio} compares MER of different GNNs on inference stage. We found that 
-    \item
-\end{itemize}
+%
+\figurename~\ref{fig:exp_inference_full_memory_usage_stage_amp} shows the peak memory usage of each phase during inference stage.  
+%
+Compared with the results of training stage in \figurename~\ref{fig:exp_memory_usage_stage_amp}, the peak memory usage of inference stage was significantly lower.
+%
+This was because the inference stage didn't require backward propagation and the peak memory was only determined by the temporary variables generated during the computation.
+%
+
+\figurename~\ref{fig:exp_inference_full_memory_expansion_ratio} compares MER of different GNNs on inference stage. 
+%
+We found that the performance of GNNs on all datasets was consistent with the training stage (\figurename~\ref{fig:exp_memory_expansion_ratio}). 
+%
 

### 2020-12-22 NEUROC/sec3-experiment-design.tex
更新超参数对精度的影响实验结果。

--- 2020-12-22 NEUROC/sec3-experiment-design.tex
@@
 \paragraph{Datasets}
+
 We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervised, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
+%
 For directed graphs, PyG converts them into undirected ones during data loading.
+%
 Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
+%
 For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
-For the \texttt{cam} dataset, we generated random dense feature vectors.
+%
+For the \texttt{cam} dataset, since its vertices were not associated with feature vectors, we generated random dense feature vectors for it and excluded it from accuracy evaluation.
+%
 We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in some experiments, to explore the effects of graph topological characteristics (like average degrees) on performance bottlenecks.
+%
 Input feature vectors of random graphs were random dense vectors with the dimension of 32.
+%
 Vertices of random graphs were classified into 10 classes randomly.
 
-\begin{table}
+\begin{table}[H]
     \centering

### 2020-12-22 NEUROC/sec4-experiments.tex
更新超参数对精度的影响实验结果。

--- 2020-12-22 NEUROC/sec4-experiments.tex
@@
 We answer the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
-Without otherwise mentioned, the reported training time per epoch was the average wall-clock training time of 50 epochs, excluding abnormal epochs \footnote{During the training of some epochs, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
+%
+Without otherwise mentioned, the reported training time per epoch was the average wall-clock training time of 50 epochs, excluding abnormal epochs.
+%
+During the training of some epochs, there were extra profiling overheads from NVIDIA Nsight Systems and GC pauses from the Python interpreter that significantly increased the training time.
+%
 We denoted the 25\% and 75\% quantiles of the training time of 50 epochs as Q1 and Q3, respectively.
-We regarded the epochs with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epochs.}.
+%
+We regarded the epochs with the training time \emph{outside} the range of $[Q1 - 1.5 * (Q3-Q1), Q3 + 1.5 * (Q3-Q1)]$ as abnormal epochs.
 
@@
 
+The hyper-parameters of a GNN (such as the dimensions of hidden vectors and the number of heads) determined the model complexity of the GNN.
+%
+They affected the training/inference time, memory usage, and accuracy of the GNN at the same time.
+
+\paragraph{Effects on Training/Inference Time}
+
 According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexity of the messaging function $\phi^l$ and the updating function $\gamma^l$ are linear to each hyper-parameter separately.
 %
-If we increase one of the hyper-parameters and fix the others, the training time should increase linearly.
+If we increase one of the hyper-parameters and fix the others, the training/inference time should increase linearly in theory.
 
@@
     \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}
-    %\subfloat[\label{fig:exp_absolute_training_time_pubmed}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_pubmed.pdf}}
-    %\subfloat[\label{fig:exp_absolute_training_time_amazon-photo}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-photo.pdf}}
-    %\subfloat[\label{fig:exp_absolute_training_time_coauthor-physics}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_coauthor-physics.pdf}} \\
-    %\subfloat[\label{fig:exp_absolute_training_time_amazon-computers}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_amazon-computers.pdf}}
-    %\subfloat[\label{fig:exp_absolute_training_time_flickr}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_flickr.pdf}}
-    %\subfloat[\label{fig:exp_absolute_training_time_com-amazon}]{\includegraphics[width=0.32\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}}
     \caption{Distribution of the wall-clock training time of 50 epoches on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
@@
 
-To further evaluate effects of hyper-parameters on performance, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} to \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}.
+To further evaluate effects of hyper-parameters on training time, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} to \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}.
 
@@
 
-We further measured the effects of the hyper-parameters on the peak GPU memory usage in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
+\paragraph{Effects on Peak Memory Usage}
+
+We further measured the effects of the hyper-parameters on the peak GPU memory usage during training in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
 %
@@
     \subfloat[GaAN]{\includegraphics[width=0.75\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.pdf}}
-    \caption{Effects of hyper-parameters on the peak GPU memory usage during the training, excluding the memory used by the dataset and the model parameters.}
+    \caption{Effects of hyper-parameters on the peak GPU memory usage during training, excluding the memory used by the dataset and the model parameters.}
     \label{fig:exp_hyperparameter_memory_usage}
@@
 
-% added by wangyupan, 2020-12-22 ----start----
-In deep learning, accuracy is also an important indicator that algorithm engineers care about.
+\paragraph{Effects on Accuracy}
+
+The relationship between hyper-parameters of GNNs (i.e., model complexity) and accuracy is very complicated, and there is no clear theoretical analysis yet.
 %
-We adopted a unified standard (section \ref{sec:hyper-parameters}) to evaluate the effect of hyper-parameters on accuracy.
+Generally speaking, higher model complexity can bring stronger expressive ability and may bring higher accuracy, but it also increases the risk of overfitting.
 %
-\figurename~\ref{fig:exp_hyperparameter_accuracy} shows how the accuracy varies with hyper-parameters.
+To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the four typical GNNs under different hyper-parameters.
 %
-For all models, we found that different datasets had different curve changes, that was, different datasets had different sensitivity to hyper-parameter changes.
+\figurename~\ref{fig:exp_hyperparameter_accuracy} shows the experimental results.
+
+For GCN, the accuracy was sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$.
 %
-This was because different datasets had different characteristics, which lead to different learning difficulties.
+As $dim(\MyVec{h}^1_x)$ increased, the accuracy first increased quickly and then stabilized when $dim(\MyVec{h}_x^1) \geq 8$.
+%
+For GGNN, its accuracy curves showed similar trends as GCN.
+%
+However, GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN and the accuracy even decreased when $dim(\MyVec{h}_x^1) \geq 1024$.
+%
+Since GGNN had high model complexity (with 13 weight matrices/vectors to train), GGNN might occur overfitting in those cases.
+%%%% TODO %%%%
+
+%In deep learning, accuracy is also an important indicator that algorithm engineers care about.
+%
+%We adopted a unified standard (section \ref{sec:hyper-parameters}) to evaluate the effect of hyper-parameters on accuracy.
+%
+%\figurename~\ref{fig:exp_hyperparameter_accuracy} shows how the accuracy varies with hyper-parameters.
+%
+%For all models, we found that different datasets had different curve changes, that was, different datasets had different sensitivity to hyper-parameter changes.
+%
+%This was because different datasets had different characteristics, which lead to different learning difficulties.
 %
@@
     \centering
-    \subfloat[GCN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gcn.pdf}}
-    \subfloat[GGNN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat.pdf}}\\
-    \subfloat[GaAN]{\includegraphics[width=0.75\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
-    \caption{Effects of hyper-parameters on accuracy of four models.}
+    \subfloat[GCN]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[width=0.6\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat.pdf}}\\
+    \subfloat[GaAN]{\includegraphics[width=0.85\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
+    \caption{Effects of hyper-parameters on accuracy of the typical GNNs.}
     \label{fig:exp_hyperparameter_accuracy}
@@
 The aggregation step suffered from data synchronization and non-regular data access.
+
+\subsection{Inference Time Breakdown Analysis}
+% 该部分
+
+%
 

### 2020-12-22 NEUROC/sec4-experiments.tex

@@
 
-\subsection{Inference Time Breakdown Analysis}
-% 该部分
-
+% added by wangyunpan, 2020-12-22 ----start----
+\paragraph{Inference Time Breakdown Analysis}
+We conducted the same experiments in the inference stage as above.
 %
+The results of layer level experiment, step Level in edge Calculation experiment and operator Level experiment were in general consistent with those in the Training stage.
+%
+The performance bottleneck analysis in the Training stage can also be applied to the inference stage.
+% added by wangyunpan, 2020-12-22 ----end----
 
@@
 To reduce the memory usage of GNN training, optimizations should focus on reducing memory footprints of the edge calculation stage.
+
+% added by wangyunpan, 2020-12-22 ----start----
+\paragraph{Inference Stage Memory Usage Analysis}
+
+% 不同点: phase
+\begin{figure}[H]
+    \centering
+    \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_usage_stage_amp.pdf}
+    \caption{Memory usage of each phase during the GNN training. Dataset: \texttt{amp}.}
+    \label{fig:exp_inference_full_memory_usage_stage_amp}
+\end{figure}
+
+% 不同点： 膨胀比例
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}
+    \caption{Memory expansion ratios of typical GNNs.}
+    \label{fig:exp_inference_full_memory_expansion_ratio}
+\end{figure}
+
+% 不同点: input feature dims
+\begin{figure}[H]
+    \centering
+    \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_expansion_ratio_input_feature_dimension_com-amazon_expansion_ratio.pdf}
+    \caption{Memory expansion ratio under different dimensions of input feature vectors. Dataset: \texttt{cam}.}
+    \label{fig:exp_inference_full_memory_expension_ratio_input_feature_dimension}
+\end{figure}
+
+For the inference stage, we did the same experiment as above. The experimental results were as follows:
+%
+\figurename~\ref{fig:exp_inference_full_memory_usage_stage_amp} shows the peak memory usage of each phase during inference stage.  
+%
+Compared with the results of training stage in \figurename~\ref{fig:exp_memory_usage_stage_amp}, the peak memory usage of inference stage was significantly lower.
+%
+This was because the inference stage didn't require backward propagation and the peak memory was only determined by the temporary variables generated during the computation.
+%
+
+\figurename~\ref{fig:exp_inference_full_memory_expansion_ratio} compares MER of different GNNs on inference stage. 
+%
+We found that the performance of GNNs on all datasets was consistent with the training stage (\figurename~\ref{fig:exp_memory_expansion_ratio}). 
+%
+
+% added by wangyunpan, 2020-12-22 ----end----
 

### 2020-12-23 NEUROC/sec4-experiments.tex
change sec4

@@
 %
-We found that the performance of GNNs on all datasets was consistent with the training stage (\figurename~\ref{fig:exp_memory_expansion_ratio}). 
+We found that The performance of GNNs on all datasets was consistent with the training stage in \figurename~\ref{fig:exp_memory_expansion_ratio}, but the corresponding values were lower.
 %
 
+%
 % added by wangyunpan, 2020-12-22 ----end----

### 2020-12-23 exp_graphsage_hop.py
增加了很多绘图脚本

@@ -14,7 +14,7 @@ plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
 
 dir_out = "/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/exp_graphsage_hop"
 file_out = "exp_inference_sampling_degrees_distribution_"
-colors = plt.get_cmap('Dark2')(np.linspace(0.15, 0.85, 5))
+colors = 'rgb'
 markers = 'oD^sdp'
 
 def helper(edge_index, degrees):
@@ -37,46 +37,54 @@ def helper(edge_index, degrees):
         else:
             degrees[d_v[k]] += 1
     return degrees
-    
-for data_name in small_datasets:
-    data = get_dataset(data_name, normalize_features=True)[0]
 
-    # add train, val, test split
-    if data_name in ['amazon-computers', 'amazon-photo', 'coauthor-physics']:
-        file_path = osp.join('/home/wangzhaokang/wangyunpan/gnns-project/datasets', data_name + "/raw/role.json")
-        data.train_mask, data.val_mask, data.test_mask = get_split_by_file(file_path, data.num_nodes)
-    
-    subgraph_loader = NeighborSampler(data.edge_index, sizes=[-1] * 5, batch_size=1024,
-                                    shuffle=False, num_workers=40)
-    
-    total_batches = len(subgraph_loader)
-    total_degrees = {}
-    for i in range(5):
-        total_degrees[i] = {}
+
+def get_k_hop(k):
+    for data_name in small_datasets:
+        data = get_dataset(data_name, normalize_features=True)[0]
+
+        # add train, val, test split
+        if data_name in ['amazon-computers', 'amazon-photo', 'coauthor-physics']:
+            file_path = osp.join('/home/wangzhaokang/wangyunpan/gnns-project/datasets', data_name + "/raw/role.json")
+            data.train_mask, data.val_mask, data.test_mask = get_split_by_file(file_path, data.num_nodes)
         
-    for batch in subgraph_loader:
-        batch_size, n_id, adjs = batch
-        for i, (edge_index, e_id, size) in enumerate(adjs):
-            total_degrees[i] = helper(edge_index, total_degrees[i])
-        break
-    
-    # for i in range(5):
-    #     for k in total_degrees[i].keys():
-    #         total_degrees[i][k] = int(total_degrees[i][k] / total_batches)
[…]

### 2020-12-23 main_sampling_batch_acc_cum_fix_time.py

@@ -87,6 +87,8 @@ if dataset_info[0] in small_datasets and len(dataset_info) > 1:
     
 # 2. set sampling
 # 2.1 test_data
+subgraph_loader = NeighborSampler(data.edge_index, sizes=[-1], batch_size=1024,
+                                  shuffle=False, num_workers=args.num_workers)
 
 # 2.2 train_data: 为了统一对比，这里的结果为Transductive
 if args.mode == 'cluster':
@@ -144,6 +146,21 @@ def test():
         accs.append(acc)
     return accs
 
+@torch.no_grad()
+def test_sampling():  # Inference should be performed on the full graph.
+    t0 = time.time()
+    model.eval()
+    out = model.inference(data.x, subgraph_loader)
+
+    y_true = data.y.cpu()
+    y_pred = out.argmax(dim=-1)
+    t1 = time.time()
+    
+    accs = []
+    for mask in [data.train_mask, data.val_mask, data.test_mask]:
+        correct = y_pred[mask].eq(y_true[mask]).sum().item()
+        accs.append(correct / mask.sum().item())
+    return accs
 
 def train(optimizer, t0, bs_count, best_val_acc, test_acc):
     model.train()
@@ -172,7 +189,10 @@ def train(optimizer, t0, bs_count, best_val_acc, test_acc):
             optimizer.step()
             # 指定batch size下，进行汇报时间和精度
             bs_count += 1
-            accs = test()
+            if args.dataset == "coauthor-physics":
+                accs = test_sampling()
+            else:
+                accs = test()
             if accs[1] >= best_val_acc:
                 best_val_acc = accs[1]
                 test_acc = accs[2]

### 2020-12-23 main_sampling_graph_info.py

@@ -101,9 +101,6 @@ elif args.mode == 'graphsage':
                                num_workers=args.num_workers) # inductive learning
 loader_time = time.time() - loader_time
 
-#t1 = data.edge_index.numpy()
-#np.save("amp_graph.npy", t1)
-
 # 3. set model
 if args.model == 'gcn':
     # 预先计算edge_weight出来

### 2020-12-23 paper_exp1_super_parameters/gaan_exp.sh

@@ -1,6 +1,6 @@
 #!/usr/bin/env bash
-dir_config="dir_gaan_qdrep"
-dir_sqlite="dir_gaan_sqlite"
+dir_config="dir_gaan_inference_qdrep"
+dir_sqlite="dir_gaan_inference_sqlite"
 
 if [ ! -d ${dir_config} ]
 then
@@ -30,7 +30,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_${hd}_64.qdrep" ]; then # 断点续传
                 continue
             fi
-            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_4_${hd}_64" -w true python ../main.py --dataset ${data} --model ${model} --d_v ${hd} --d_a ${hd} --d_m ${hd} --heads 4 --hidden_dims 64
+            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_4_${hd}_64" -w true python ../main_inference.py --dataset ${data} --model ${model} --d_v ${hd} --d_a ${hd} --d_m ${hd} --heads 4 --hidden_dims 64
             nsys-exporter -s "${dir_config}/config0_${model}_${data}_4_${hd}_64.qdrep" "${dir_sqlite}/config0_${model}_${data}_4_${hd}_64.sqlite"
         done
 
@@ -42,7 +42,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_32_${hd}.qdrep" ]; then # 断点续传
                 continue
             fi
-            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_4_32_${hd}" -w true python ../main.py --dataset ${data} --model ${model} --hidden_dims ${hd} --heads 4 --d_v 32 --d_a 32 --d_m 32
+            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_4_32_${hd}" -w true python ../main_inference.py --dataset ${data} --model ${model} --hidden_dims ${hd} --heads 4 --d_v 32 --d_a 32 --d_m 32
             nsys-exporter -s "${dir_config}/config0_${model}_${data}_4_32_${hd}.qdrep" "${dir_sqlite}/config0_${model}_${data}_4_32_${hd}.sqlite"
         done
         
@@ -54,7 +54,7 @@ do
[…]

### 2020-12-23 paper_exp1_super_parameters/gaan_memory.sh

@@ -1,5 +1,5 @@
 #!/usr/bin/env bash
-dir_config="dir_gaan_json"
+dir_config="dir_gaan_inference_json"
 
 if [ ! -d ${dir_config} ]
 then
@@ -24,7 +24,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_${hd}_64.json" ]; then # 断点续传
                 continue
             fi
-            python ../main_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_4_${hd}_64.json" --dataset ${data} --model ${model} --d_v ${hd} --d_a ${hd} --d_m ${hd} --heads 4 --hidden_dims 64
+            python ../main_inference_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_4_${hd}_64.json" --dataset ${data} --model ${model} --d_v ${hd} --d_a ${hd} --d_m ${hd} --heads 4 --hidden_dims 64
         done
 
         # hidden_dims
@@ -35,7 +35,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_32_${hd}.json" ]; then # 断点续传
                 continue
             fi
-            python ../main_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_4_32_${hd}.json" --dataset ${data} --model ${model} --hidden_dims ${hd} --heads 4 --d_v 32 --d_a 32 --d_m 32
+            python ../main_inference_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_4_32_${hd}.json" --dataset ${data} --model ${model} --hidden_dims ${hd} --heads 4 --d_v 32 --d_a 32 --d_m 32
         done
         
         # heads
@@ -46,7 +46,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_${h}_32_64.json" ]; then # 断点续传
                 continue
             fi
-            python ../main_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_${h}_32_64.json" --dataset ${data} --model ${model} --d_m 32 --d_v 32 --d_a 32 --heads ${h} --hidden_dims 64
+            python ../main_inference_memory.py --device cuda:1 --json_path "${dir_config}/config0_${model}_${data}_${h}_32_64.json" --dataset ${data} --model ${model} --d_m 32 --d_v 32 --d_a 32 --heads ${h} --hidden_dims 64
         done
     done
 done

### 2020-12-23 paper_exp1_super_parameters/gat_exp.sh

@@ -1,6 +1,6 @@
 #!/usr/bin/env bash
-dir_config="dir_gat_qdrep"
-dir_sqlite="dir_gat_sqlite"
+dir_config="dir_gat_inference_qdrep"
+dir_sqlite="dir_gat_inference_sqlite"
 
 if [ ! -d ${dir_config} ]
 then
@@ -28,7 +28,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_${hd}.qdrep" ]; then # 断点续传
                 continue
             fi
-            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_4_${hd}" -w true python ../main.py --dataset ${data} --model ${model} --head_dims ${hd} --d_v ${hd} --d_a ${hd} --heads 4
+            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_4_${hd}" -w true python ../main_inference.py --dataset ${data} --model ${model} --head_dims ${hd} --d_v ${hd} --d_a ${hd} --heads 4
             nsys-exporter -s "${dir_config}/config0_${model}_${data}_4_${hd}.qdrep" "${dir_sqlite}/config0_${model}_${data}_4_${hd}.sqlite"
         done
         for h in ${heads[@]}
@@ -38,7 +38,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_${h}_32.qdrep" ]; then # 断点续传
                 continue
             fi
-            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_${h}_32" -w true python ../main.py --dataset ${data} --model ${model} --head_dims 32 --d_v 32 --d_a 32 --heads ${h}
+            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_${h}_32" -w true python ../main_inference.py --dataset ${data} --model ${model} --head_dims 32 --d_v 32 --d_a 32 --heads ${h}
             nsys-exporter -s "${dir_config}/config0_${model}_${data}_${h}_32.qdrep" "${dir_sqlite}/config0_${model}_${data}_${h}_32.sqlite"
         done
     done

### 2020-12-23 paper_exp1_super_parameters/gat_memory.sh

@@ -1,5 +1,5 @@
 #!/usr/bin/env bash
-dir_config="dir_gat_json"
+dir_config="dir_gat_inference_json"
 
 if [ ! -d ${dir_config} ]
 then
@@ -22,7 +22,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_4_${hd}.json" ]; then # 断点续传
                 continue
             fi
-            python ../main_memory.py --device cuda:0 --dataset ${data} --model ${model} --head_dims ${hd} --d_v ${hd} --d_a ${hd} --heads 4 --json_path "${dir_config}/config0_${model}_${data}_4_${hd}.json"
+            python ../main_inference_memory.py --device cuda:0 --dataset ${data} --model ${model} --head_dims ${hd} --d_v ${hd} --d_a ${hd} --heads 4 --json_path "${dir_config}/config0_${model}_${data}_4_${hd}.json"
         done
         for h in ${heads[@]}
         do
@@ -31,7 +31,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_${h}_32.json" ]; then # 断点续传
                 continue
             fi
-            python ../main_memory.py --device cuda:0 --dataset ${data} --model ${model} --head_dims 32 --d_v 32 --d_a 32 --heads ${h} --json_path "${dir_config}/config0_${model}_${data}_${h}_32.json"
+            python ../main_inference_memory.py --device cuda:0 --dataset ${data} --model ${model} --head_dims 32 --d_v 32 --d_a 32 --heads ${h} --json_path "${dir_config}/config0_${model}_${data}_${h}_32.json"
         done
     done
 done

### 2020-12-23 paper_exp1_super_parameters/gcn_ggnn_exp.sh

@@ -1,6 +1,6 @@
 #!/usr/bin/env bash
-dir_config="dir_gcn_ggnn_qdrep"
-dir_sqlite="dir_gcn_ggnn_sqlite"
+dir_config="dir_gcn_ggnn_inference_qdrep"
+dir_sqlite="dir_gcn_ggnn_inference_sqlite"
 
 if [ ! -d ${dir_config} ]
 then
@@ -27,7 +27,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_${hd}.qdrep" ]; then # 断点续传
                 continue
             fi
-            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_${hd}" -w true python ../main.py --dataset ${data} --model ${model} --hidden_dims ${hd}
+            nsys profile -t cuda,osrt,nvtx -o "${dir_config}/config0_${model}_${data}_${hd}" -w true python ../main_inference.py --dataset ${data} --model ${model} --hidden_dims ${hd}
             nsys-exporter -s "${dir_config}/config0_${model}_${data}_${hd}.qdrep" "${dir_sqlite}/config0_${model}_${data}_${hd}.sqlite"
         done
     done

### 2020-12-23 paper_exp1_super_parameters/gcn_ggnn_memory.sh

@@ -1,5 +1,5 @@
 #!/usr/bin/env bash
-dir_config="dir_gcn_ggnn_json"
+dir_config="dir_gcn_ggnn_inference_json"
 
 if [ ! -d ${dir_config} ]
 then
@@ -22,7 +22,7 @@ do
             if [ -f "${dir_config}/config0_${model}_${data}_${hd}.json" ]; then # 断点续传
                 continue
             fi
-            python ../main_memory.py --device cuda:0 --dataset ${data} --model ${model} --json_path "${dir_config}/config0_${model}_${data}_${hd}.json" --epochs 5 --hidden_dims ${hd}
+            python ../main_inference_memory.py --device cuda:0 --dataset ${data} --model ${model} --json_path "${dir_config}/config0_${model}_${data}_${hd}.json" --hidden_dims ${hd}
         done
     done
 done

### 2020-12-23 paper_exp1_super_parameters/run_device_0.sh

@@ -1,4 +1,9 @@
-echo "run_gat"
-bash gat_memory.sh >gat_memory.log 2>&1 
+export LD_LIBRARY_PATH=/home/wangzhaokang/anaconda3/envs/pyg1.5/lib/python3.7/site-packages/torch/lib:${LD_LIBRARY_PATH}
 echo "run_gcn_ggnn"
 bash gcn_ggnn_memory.sh >gcn_ggnn_memory.log 2>&1
+echo "run exp: gaan"
+bash gaan_exp.sh >gaan_exp.log 2>&1
+echo "run exp: gat"
+bash gat_exp.sh >gat_exp.log 2>&1
+echo "run exp: gcn_ggnn"
+bash gcn_ggnn_exp.sh >gcn_ggnn_exp.log 2>&1

### 2020-12-23 paper_exp1_super_parameters/run_device_1.sh

@@ -1,2 +1,2 @@
-# echo "run_gaan"
+echo "run_gaan"
 bash gaan_memory.sh >gaan_memory.log 2>&1

### 2020-12-23 paper_exp4_relative_sampling/pics_degrees_exp.py

@@ -1,0 +1,69 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import sys
+plt.style.use("ggplot")
+plt.rcParams['font.size'] = 12
+
+graph_path = "amp_graph.npy"
+cluster_path = "amp_cluster.npy"
+graphsage_path = "amp_graphsage.npy"
+
+paths = [graph_path, cluster_path, graphsage_path]
+names = ['Original Graph', 'Cluster Sampling', 'Neighbor Sampling']
+
+
+def get_degrees_counts(path):
+    # 1. 统计出每个节点的度数
+    in_degrees = {}
+    out_degrees = {}
+
+    graph = np.load(path)
+    for i in graph[0, :]:
+        if i not in in_degrees.keys():
+            in_degrees[i] = 1
+        else:
+            in_degrees[i] += 1
+
+    for i in graph[1, :]:
+        if i not in out_degrees.keys():
+            out_degrees[i] = 1
+        else:
+            out_degrees[i] += 1
+
+    degrees_counts = {}
+    for i in in_degrees.values():
+        if i not in degrees_counts.keys():
+            degrees_counts[i] = 1
+        else:
+            degrees_counts[i] += 1
+
+    for i in out_degrees.values():
+        if i not in degrees_counts.keys():
+            degrees_counts[i] = 1
+        else:
+            degrees_counts[i] += 1
+    return degrees_counts
+
+
+fig, ax = plt.subplots()
+
+#ax.set_yscale("symlog", basey=2)
+#ax.set_xscale("symlog", basey=2)
+ax.set_yscale('log')
+ax.set_xscale('log')
+ax.set_ylim(ymin=0.5, ymax=1e4)
+ax.set_xlim(xmin=0.5, xmax=1e4)
+ax.set_xlabel("Degrees")
+ax.set_ylabel("Numbers")
+
+markers = 'oD^'
+colors = 'rgb'
+for i, path in enumerate(paths):
+    degrees_counts = get_degrees_counts(path)
+    xs = list(degrees_counts.keys())
+    ys = [degrees_counts[d] for d in xs]
+    ax.scatter(xs, ys, color=colors[i], label=names[i], marker=markers[i])
+
+ax.legend()
+
+fig.savefig("exp_sampling_minibatch_degrees_distribution_amazon-photo.png")

### 2020-12-23 paper_exp5_paras_acc/gaan_ds_exp.sh

@@ -1,0 +1,28 @@
+#!/usr/bin/env bash
+dir_config="dir_gaan_ds_acc"
+
+if [ ! -d ${dir_config} ]
+then
+    mkdir -p $dir_config
+fi
+
+
+datasets=(amazon-photo pubmed amazon-computers coauthor-physics flickr)
+models=(gaan)
+ds=(1 2 4 8 16 32 64 128 256)
+
+for data in ${datasets[@]}
+do
+    for model in ${models[@]}
+    do
+        for hd in ${ds[@]}
+        do
+            val="model=${model}, dataset=${data}, heads=1, d_a, d_v, d_m=${hd}, hidden_dims=8"
+            echo ${val}
+            if [ -f "${dir_config}/config0_${model}_${data}_1_${hd}_8.log" ]; then # 断点续传
+                continue
+            fi
+            python ../main_kdd_criterion.py --device cuda:0 --dataset ${data} --model ${model} --d_v ${hd} --d_a ${hd} --d_m ${hd} --heads 1 --hidden_dims 8 1>"${dir_config}/config0_${model}_${data}_1_${hd}_8.log" 2>&1
+        done
+    done
+done

### 2020-12-23 paper_exp5_paras_acc/gaan_heads_exp.sh

@@ -1,0 +1,30 @@
+#!/usr/bin/env bash
+dir_config="dir_gaan_heads_acc"
+
+if [ ! -d ${dir_config} ]
+then
+    mkdir -p $dir_config
+fi
+
+
+datasets=(amazon-photo pubmed amazon-computers coauthor-physics flickr)
+models=(gaan)
+heads=(1 2 4 8 16)
+
+
+for data in ${datasets[@]}
+do
+    for model in ${models[@]}
+    do
+        # heads
+        for h in ${heads[@]}
+        do
+            val="model=${model}, dataset=${data}, heads=${h}, d_a, d_v, d_m=2, hidden_dims=4"
+            echo ${val}
+            if [ -f "${dir_config}/config0_${model}_${data}_${h}_2_4.log" ]; then # 断点续传
+                continue
+            fi
+            python ../main_kdd_criterion.py --device cuda:1 --dataset ${data} --model ${model} --d_m 2 --d_v 2 --d_a 2 --heads ${h} --hidden_dims 4 1>"${dir_config}/config0_${model}_${data}_${h}_2_4.log" 2>&1
+        done
+    done
+done

### 2020-12-23 paper_exp5_paras_acc/get_max_paras.py

@@ -3,7 +3,7 @@ import numpy as np
 import pandas as pd
 import matplotlib.pyplot as plt
 plt.style.use("ggplot")
-plt.rcParams["font.size"] = 12
+# plt.rcParams["font.size"] = 12
 plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
 
 datasets = ["amazon-photo", "pubmed", "amazon-computers", "coauthor-physics", "flickr", "com-amazon"]
@@ -219,24 +219,28 @@ def pics_gaan(dir_in="early_stopping1/acc_res", dir_out="early_stopping1/acc_res
     file_prefix = "exp_hyperparameter_on_accuracy_"
     xticklabels = [['1', '2', '4', '8', '16', '32', '64', '128', '256', '512', '1024', '2048'],
                    ['1', '2', '4', '8', '16', '32', '64', '128', '256'], ['1', '2', '4', '8', '16']]
-    xlabels = [r"Hidden Vector Dimension $dim(\mathbf{h}^1)$ (#Head=4, $d_a=d_v=d_m$=32)", r"$d_a, d_v, d_m$(#Head=4, $dim(\mathbf{h}^1)$=64)",  r"#Head ($dim(\mathbf{h}^1)$=64, $d_a=d_v=d_m$=32)"]
-   
+    xlabels = ["Dimension of Hidden Vectors\n" + r"$dim(\mathbf{h}^1_x)$ (#Head=4, $d_a=d_v=d_m$=32)", r"$d_a, d_v, d_m$" + "\n" + r"(#Head=4, $dim(\mathbf{h}^1_x)$=64)",  "#Head\n" + r"($dim(\mathbf{h}^1)$=64, $d_a=d_v=d_m$=32)"]
+  
+    fig, axes = plt.subplots(1, 3, figsize=(7, 7/3), sharey=True, tight_layout=True) 
+    # plt.rcParams["font.size"] = 8
     for i, mode in enumerate(['hds', 'ds', 'heads']):
         df = pd.read_csv(dir_in + "/gaan_" + mode + ".csv", index_col=0)
         df.index = xticklabels[i]
-        fig, ax = plt.subplots()
-        ax.set_ylabel('Accuracy')
-        ax.set_ylim(0, 1)
-        ax.set_xlabel(xlabels[i])
+        ax = axes[i]
+        if i == 0:
+            ax.set_ylabel('Test Accuracy', fontsize=9)
+        ax.set_ylim(0.4, 1)
[…]

### 2020-12-23 paper_exp5_paras_acc/handle_paras_acc_gaan_ds.py

@@ -1,0 +1,66 @@
+import os, re, sys
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+plt.style.use("ggplot")
+plt.rcParams["font.size"] = 12
+plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
+
+datasets = ["amazon-photo", "pubmed", "amazon-computers", "coauthor-physics", "flickr", "com-amazon"]
+datasets_map = ['amp', 'pub', 'amc', 'cph', 'fli', 'cam']
+
+models = ["gcn", "ggnn", "gat", "gaan"]
+gaan_ds = ["1", "2", "4", "8", "16", "32", "64", "128", "256"]
+
+def save_acc_to_csv(dir_work="./"): # 将统计得到的acc结果保存在csv文件中 
+    dir_config = "dir_gaan_ds_acc"
+    model = "gaan"
+    df_ds = {}
+    for data in datasets:
+        df_ds[data] = []
+        for d in gaan_ds:
+            file_name = f"{dir_work}/{dir_config}/config0_{model}_{data}_1_{d}_8.log"
+            if not os.path.exists(file_name):
+                df_ds[data].append(None)
+                continue
+            print(file_name)
+            acc = None
+            with open(file_name) as f:
+                for line in f:
+                    match_line = re.match("Final Test Acc: (.*)", line)
+                    if match_line:
+                        acc = format(float(match_line.group(1)), ".5f")
+                        break
+            df_ds[data].append(acc)
+    df = pd.DataFrame(df_ds, index=gaan_ds)
+    df.columns = datasets_map
+    df.to_csv(f"{dir_work}/acc_res/{model}_ds.csv")
+
+
+def pics_gaan_ds(dir_in="acc_res", dir_out="acc_res"):
+    datasets = ['amazon-photo', 'pubmed', 'amazon-computers', 'coauthor-physics', 'flickr']
+
+    file_prefix = "exp_hyperparameter_on_accuracy_"
+    xlabels =  r"$d_a, d_v, d_m$" + "\n" + r"(#Head=4, $dim(\mathbf{h}^1_x)$=64)"
+    xticklabels = ['1', '2', '4', '8', '16', '32', '64', '128', '256']
+    fig, ax = plt.subplots(figsize=(7/2, 7/2), sharey=True, tight_layout=True)
+    
[…]

### 2020-12-23 paper_exp5_paras_acc/handle_paras_acc_gaan_heads.py

@@ -53,7 +53,7 @@ def pics_gat(dir_in="acc_res", dir_out="acc_res"):
         df = pd.read_csv(dir_in + f"/gat_heads_{hd}.csv", index_col=0)
         df.index = xticklabels
         ax = axes[i]
-        ax.set_ylabel('Test Accuracy', fontsize=12)
+        ax.set_ylabel('Accuracy', fontsize=12)
         ax.set_ylim(0.4, 1)
         ax.set_xlabel(xlabels[i], fontsize=12)
         ax.set_xticks(list(range(len(xticklabels))))
@@ -61,11 +61,11 @@ def pics_gat(dir_in="acc_res", dir_out="acc_res"):
         markers = 'oD^sdp'
         for j, c in enumerate(df.columns[:-1]):
             ax.plot(df.index, df[c], marker=markers[j], label=c)
-        ax.legend(ncol=1, fontsize='xx-small')
+        ax.legend()
     fig.tight_layout() 
     fig.savefig(dir_out + "/" + file_prefix + f"gat_small_info.png")
     fig.savefig(dir_out + "/" + file_prefix + f"gat_small_info.pdf")
     plt.close()
 
-# save_acc_to_csv()
-pics_gat(dir_in="acc_res", dir_out="paras_figs")
+save_acc_to_csv()
+pics_gat()

### 2020-12-23 paper_exp6_sampling_acc/convergence_validation.py

@@ -30,24 +30,22 @@ datasets_maps = {
     'com-amazon': 'cam'
 }
 
-xticklabels = ['1%', '3%', '6%', '10%', '25%', '50%', 'FULL']
+xticklabels = ['1%', '3%', '6%', '10%', '25%', '50%']
 
-dir_in = "log_fix_time"
+dir_in = "log_fix_time_new"
 dir_out = "res_convergence_validation"
 
 for data in datasets:
     for model in models:
-        if not os.path.exists(f"{dir_out}/{model}/{data}"):
-            os.makedirs(f"{dir_out}/{model}/{data}")
+        if not os.path.exists(f"{dir_out}/{dir_in}"):
+            os.makedirs(f"{dir_out}/{dir_in}")
         for mode in modes:
-            print(data, model, mode)
             # 将数据存储到csv文件
             if mode == "cluster":
                 for i, cs in enumerate(cluster_batchs):
                     file_path = os.path.join(dir_in, '_'.join([mode, model, data, str(cs)]) + ".log")
                     if not os.path.exists(file_path):
                         continue
-                    print(file_path)
                     train_acc, val_acc = [], []
                     # 读取日志文件，获取bs_times, bs_accs: dims=100
                     with open(file_path) as f:
@@ -67,15 +65,15 @@ for data in datasets:
                         ax.plot(x, accs[i], color=c, label=labels[i])
                     ax.legend()
                     fig.tight_layout() 
-                    fig_path = '_'.join([mode, model, data, str(cs)]) + '_cluster.png'
-                    fig.savefig(f"acc_fig/{model}/{data}/{fig_path}")
+                    fig_path = '_'.join([mode, model, data, str(cs)]) + '.png'
+                    print(file_path)
+                    fig.savefig(f"{dir_out}/{dir_in}/{fig_path}")
                                          
             elif mode == "graphsage":
                 for i, gs in enumerate(graphsage_batchs[data]):
                     file_path = os.path.join(dir_in, '_'.join([mode, model, data, str(gs)]) + ".log")
                     if not os.path.exists(file_path):
                         continue
-                    print(file_path)
                     train_acc, val_acc = [], []
                     # 读取日志文件，获取bs_times, bs_accs: dims=100
                     with open(file_path) as f:
@@ -95,5 +93,6 @@ for data in datasets:
                         ax.plot(x, accs[i], color=c, label=labels[i])
                     ax.legend()
[…]

### 2020-12-23 paper_exp6_sampling_acc/handle_sampling_acc_fix_epoch.py

@@ -87,7 +87,7 @@ for data in datasets:
             if flag: continue
 
             # 获取full
-            file_path = file_path = os.path.join("batch_acc_cum_fix_batch", '_'.join([mode, alg, data]) + "_full.log")
+            file_path = os.path.join("batch_acc_cum_fix_batch", '_'.join([mode, alg, data]) + "_full.log")
             # 读取日志文件，获取bs_times, bs_accs: dims=100
             with open(file_path) as f:
                 df_times['FULL'], df_accs['FULL'] = [], []

### 2020-12-23 paper_exp6_sampling_acc/handle_sampling_acc_fix_time.py

@@ -32,40 +32,22 @@ datasets_maps = {
 
 xticklabels = ['1%', '3%', '6%', '10%', '25%', '50%']
 
-dir_in = "log_fix_time"
-dir_out = "res_fix_time"
+dir_in = "log_fix_time_new"
+dir_out = "sampling_acc_time_figs"
 
-for data in datasets:
-    if not os.path.exists(dir_out + "/" + data):
-        os.makedirs(dir_out + "/" + data)
-        
-"""
-目标：绘制不同BatchSize下，精度随Batch Nums的变化结果
-
-数据收集：
-算法, 采样方法，数据集，time/acc
-
-绘制图像：
-算法+采样方法+time/acc
-df.index: 图像的横坐标
-df.columns: 图像中的不同的线(不同的BatchSize)
-"""
-
+if not os.path.exists(dir_out):
+    os.makedirs(dir_out)
+    
 max_accs = pd.read_csv("/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp5_paras_acc/acc_res/alg_acc.csv", index_col=0)
 
-for data in datasets:
-    for alg in algs:
-        for mode in modes:
-            flag = False
+for mode in ["cluster"]:
+    for alg in ["gcn"]:
+        for data in ["amazon-computers"]:
             # 将数据存储到csv文件
             df_times, df_accs = {}, {}
             if mode == "cluster":
                 for i, cs in enumerate(cluster_batchs):
                     file_path = os.path.join(dir_in, '_'.join([mode, alg, data, str(cs)]) + ".log")
-                    if not os.path.exists(file_path):
-                        flag = True
-                        break
-                    print(file_path)
                     df_times[xticklabels[i]], df_accs[xticklabels[i]] = [], []
                     # 读取日志文件，获取bs_times, bs_accs: dims=100
                     with open(file_path) as f:
@@ -77,9 +59,6 @@ for data in datasets:
             elif mode == "graphsage":
                 for i, gs in enumerate(graphsage_batchs[data]):
                     file_path = os.path.join(dir_in, '_'.join([mode, alg, data, str(gs)]) + ".log")
-                    if not os.path.exists(file_path):
-                        flag = True
-                        break
                     df_times[xticklabels[i]], df_accs[xticklabels[i]] = [], []
                     # 读取日志文件，获取bs_times, bs_accs: dims=100
                     with open(file_path) as f:
@@ -89,24 +68,21 @@ for data in datasets:
[…]

### 2020-12-23 paper_exp6_sampling_acc/pics_exp6_sampling_batch_size_acc.py

@@ -1,0 +1,134 @@
+import re
+import os
+import sys
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+plt.style.use("ggplot")
+plt.rcParams['text.latex.preamble'] = [r"\usepackage{amsmath}"]
+
+datasets = ["amazon-photo", "pubmed",
+            "amazon-computers", "coauthor-physics", "flickr"]
+modes = ["cluster", "graphsage"]
+algs = ["gcn", "ggnn", "gat", "gaan"]
+
+cluster_batchs = [15, 45, 90, 150, 375, 750]
+
+graphsage_batchs = {
+    'amazon-photo': [77, 230, 459, 765, 1913, 3825],
+    'pubmed': [198, 592, 1184, 1972, 4930, 9859],
+    'amazon-computers': [138, 413, 826, 1376, 3438, 6876],
+    'coauthor-physics': [345, 1035, 2070, 3450, 8624, 17247],
+    'flickr': [893, 2678, 5355, 8925, 22313, 44625]
+}
+
+
+datasets_maps = {
+    'amazon-photo': 'amp',
+    'pubmed': 'pub',
+    'amazon-computers': 'amc',
+    'coauthor-physics': 'cph',
+    'flickr': 'fli',
+}
+
+algorithms = {
+    'gcn': 'GCN',
+    'ggnn': 'GGNN',
+    'gat': 'GAT',
+    'gaan': 'GaAN'
+}
+
+xticklabels = ['1%', '3%', '6%', '10%', '25%', '50%', 'FULL']
+
+dir_in = "log_fix_time_new"
+dir_out = "sampling_acc_figs"
+
+def save_acc_to_file():
+    for mode in modes:
+        for data in datasets:
+            df_accs = {}
+            for alg in algs:
+                df_accs[alg] = []
+                if mode == "cluster":
+                    for i, cs in enumerate(cluster_batchs):
+                        file_path = os.path.join(dir_in, '_'.join(
+                            [mode, alg, data, str(cs)]) + ".log")
+                        if not os.path.exists(file_path):
+                            df_accs[alg].append(np.nan)
+                            continue
+                        print(file_path)
+                        test_acc = 0
+                        # 读取日志文件，获取bs_times, bs_accs: dims=100
+                        with open(file_path) as f:
+                            for line in f:
+                                match_line = re.match(
+                                    r"Batch:.*best_test_acc: (.*), cur_use_time: (.*)s", line)
[…]

### 2020-12-23 paper_exp6_sampling_acc/sampling_acc_fix_time.py

@@ -32,49 +32,44 @@ datasets_maps = {
 
 fix_times = {
     'pubmed': 1000,
-    'coauthor-physics': 1000,
-    'flickr': 1750,
-    'amazon-photo': 1000,
-    'amazon-computers': 1400
+    'coauthor-physics': 2000,
+    'flickr': 2000,
+    'amazon-photo': 4000,
+    'amazon-computers': 4000
 }
 
-dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "log_fix_time_new")
+dir_path = os.path.join(os.path.dirname(os.path.realpath(__file__)), "log_fix_time_12_22")
 if not os.path.exists(dir_path):
     os.makedirs(dir_path)
 
-for i, mode in enumerate(['cluster', 'graphsage']):
+for i, mode in enumerate(['graphsage']):
     sh_commands = []
-    for alg in algs:
-        for data in small_datasets:
-            paras = str(config_paras.loc[datasets_maps[data], alg]).split('_')
-            if alg in ["gcn", "ggnn"]:
-                config_str = f"--hidden_dims {paras[0]}"
-            elif alg == "gat":
-                config_str = f"--heads {paras[0]} --head_dims {paras[1]}"
-            elif alg == "gaan":
-                config_str = f"--heads {paras[0]} --d_v {paras[1]} --d_a {paras[1]} --d_m {paras[1]} --hidden_dims {paras[2]}"
-            if mode == 'cluster':
-                cmd = "python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --mode {} --model {} --data {} --device cuda:{} --batch_partitions {} {} --fix_time {} >>{} 2>&1"
-                for cs in cluster_batchs:
-                    file_path = os.path.join(dir_path, '_'.join([mode, alg, data, str(cs)]) + '.log')
-                    if os.path.exists(file_path):
-                        continue
-                    print(file_path)
-                    sh_commands.append(cmd.format(mode, alg, data, i, str(cs), config_str, fix_times[data], file_path))
-                full_log = os.path.join(dir_path, '_'.join([mode, alg, data, 'full']) + '.log')
[…]

### 2020-12-23 paper_exp6_sampling_acc/save_full_acc.py

@@ -10,7 +10,7 @@ plt.rcParams['text.latex.preamble']=[r"\usepackage{amsmath}"]
 
 modes = ["cluster", "graphsage"]
 algs = ["gcn", "ggnn", "gat", "gaan"]
-datasets = ["amazon-photo", "coauthor-physics", "amazon-computers", "pubmed", "flickr"]
+datasets = ["amazon-photo", "pubmed", "amazon-computers", "coauthor-physics", "flickr"]
 cluster_batchs = [15, 45, 90, 150, 375, 750]
 
 graphsage_batchs = {
@@ -37,6 +37,9 @@ dir_out = "res_fix_time_new"
 
 if not os.path.exists(dir_out + "/res_csv"):
     os.makedirs(dir_out + "/res_csv")
+
+if not os.path.exists(dir_out + "/res_fig"):
+    os.makedirs(dir_out + "/res_fig")
         
 def get_full_acc():
     df = {}
@@ -96,11 +99,15 @@ for mode in modes:
                     df_accs[data].append(acc)
         df = pd.DataFrame(df_accs)
         df.index = xticklabels
-        df.to_csv(dir_out + "/res_csv/" + mode + "_" + alg + ".csv")
+        df.to_csv(dir_out + "/res_csv/" + alg + "_" + mode + ".csv")
         
-        print(df)
         fig, ax = plt.subplots()
         ax.set_ylabel("Accuracy")
         ax.set_xlabel("Relative Batch Size (%)")
         
+        markers = 'oD^sdp'
+        for i, c in enumerate(df.columns):
+            ax.plot(xticklabels, df[c], marker=markers[i], label=datasets_maps[c])
+        ax.legend()
+        fig.savefig(dir_out + "/res_fig/" + alg + "_" + mode + ".png")        
             

### 2020-12-23 paper_exp6_sampling_acc/sh_graphsage_fix_time.sh

@@ -1,0 +1,6 @@
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --lr 0.1 --mode graphsage --model gcn --data amazon-photo --device cuda:0 --batch_size 77 --hidden_dims 64 --fix_time 4000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_12_22/graphsage_gcn_amazon-photo_77.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --lr 0.1 --mode graphsage --model gcn --data amazon-photo --device cuda:0 --batch_size 230 --hidden_dims 64 --fix_time 4000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_12_22/graphsage_gcn_amazon-photo_230.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --lr 0.1 --mode graphsage --model gcn --data amazon-photo --device cuda:0 --batch_size 459 --hidden_dims 64 --fix_time 4000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_12_22/graphsage_gcn_amazon-photo_459.log 2>&1
+python -u /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_sampling_batch_acc_cum_fix_time.py --epochs 10000 --lr 0.1 --mode graphsage --model gcn --data amazon-photo --device cuda:0 --batch_size 765 --hidden_dims 64 --fix_time 4000 >>/home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp6_sampling_acc/log_fix_time_12_22/graphsage_gcn_amazon-photo_765.log 2>&1
[…]

### 2020-12-23 paper_exp7_inference_sampling/inference_sampling_memory.sh

@@ -1,6 +1,24 @@
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model gcn --data amazon-photo --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gcn_amazon-photo.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model gcn --data pubmed --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gcn_pubmed.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model gcn --data amazon-computers --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gcn_amazon-computers.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model gcn --data coauthor-physics --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gcn_coauthor-physics.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model gcn --data flickr --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gcn_flickr.json
+python /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/main_inference_sampling.py --device cuda:0 --model gcn --data com-amazon --epochs 10 --infer_json_path /home/wangzhaokang/wangyunpan/gnns-project/pyg-gnns/paper_exp7_inference_sampling/inference_sampling_memory/gcn_com-amazon.json
[…]

### 2020-12-23 NEUROC/sec4-experiments.tex
新增超参数对精度的影响实验。

@@
 %
-However, GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN and the accuracy even decreased when $dim(\MyVec{h}_x^1) \geq 1024$.
+However, GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN.
+%
+Its accuracy even decreased when $dim(\MyVec{h}_x^1) \geq 1024$.
 %
 Since GGNN had high model complexity (with 13 weight matrices/vectors to train), GGNN might occur overfitting in those cases.
-%%%% TODO %%%%
-
-%In deep learning, accuracy is also an important indicator that algorithm engineers care about.
 %
-%We adopted a unified standard (section \ref{sec:hyper-parameters}) to evaluate the effect of hyper-parameters on accuracy.
+For GAT, its accuracy was more sensitive to the dimension of each head $d_{head}$ than the number of heads.
 %
-%\figurename~\ref{fig:exp_hyperparameter_accuracy} shows how the accuracy varies with hyper-parameters.
+For GaAN, only $dim(\MyVec{h}_x^1)$ showed obvious impacts on accuracy.
 %
-%For all models, we found that different datasets had different curve changes, that was, different datasets had different sensitivity to hyper-parameter changes.
+The experimental results indicated the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was small.
 %
-%This was because different datasets had different characteristics, which lead to different learning difficulties.
+In those cases, the low model complexity limited the expressive power of the GNNs.
 %
-
-Except for the effect of the number of heads on GAT and the effect of $d_a$, $d_v$, $d_m$, the number of heads $K$ on GaAN, we found the same phenomena:
-the accuracy of the model was often low when hyper-parameters were low. When a certain threshold was reached, the accuracy began to fall within the range of fluctuations.
-%
-We conducted additional experiments for these exceptions. Taking the effect of the number of heads on GAT as an example, 
-\figurename~\ref{fig:exp_hyperparameter_accuracy_gat_small_info} shows the trend is similar to the phenomena discussed above when $d_{head}$ is adjusted to a smaller value such as 2 and 4.
-%
-This phenomenon showed some relationship between accuracy and model complexity.
-%
-When the hyper-parameter value was very small, the model complexity was often low, which limited the expressive ability of the model.
-%
-In this case, accuracy and model complexity were positively related.
-%
-However, when the hyper-parameter increased to a certain threshold, the model had sufficient learning ability, and the relationship between accuracy and model complexity was no longer certain.
-% added by wangyupan, 2020-12-22 ----end----
+As $dim(\MyVec{h}_x^1)$ or $d_{head}$ increased to a certain threshold, the GNNs had sufficient learning ability to achieve stable accuracy.
 
@@
     \subfloat[GAT]{\includegraphics[width=0.6\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat.pdf}}\\
-    \subfloat[GaAN]{\includegraphics[width=0.85\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
+    \subfloat[GaAN]{\includegraphics[width=0.9\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
     \caption{Effects of hyper-parameters on accuracy of the typical GNNs.}
@@
 
+\figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} compares the best accuracy that each GNN achieved on different datasets.
+%
+The best accuracy that the four GNNs achieved was very close.
+%
+It was also close to the accuracy reported in their original references \cite{kipf2017_gcn,li2015_ggnn,huang2018_gat,zhang2018_gaan}.
+%
+There was no clear winner in terms of accuracy.
+%
+The relative accuracy between GNNs varied greatly with different datasets.
+%
+GaAN achieved the highest accuracy in three out of five datasets.
+%
+GCN also achieved the highest or second highest accuracy in three out of five datasets, though its model was simplest.
+%
+It indicated that simple GNN models (such as GCN) could still achieve good accuracy with proper hyper-parameter settings.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=3in]{figs/experiments/exp_hyperparameter_on_accuracy_alg_contrast.pdf}
+    \caption{Best accuracy that each GNN achieved on different datasets.}
+    \label{fig:exp_hyperparameter_on_accuracy_alg_contrast}
+\end{figure}
+
 \paragraph{Summary}
@@
 %
-% added by wangyupan, 2020-12-22 ----start----
-There was no definite relationship between accuracy and hyper-parameters. 
+The accuracy of GNNs was much more sensitive to the dimension of hidden vectors/heads than the other hyper-parameters.
 %
-To obtain the optimal model, hyper-parameters needed to be manually adjusted by algorithm engineers.
-% added by wangyupan, 2020-12-22 ----end----
+The relative accuracy between GNNs varied greatly with different datasets.
 

### 2020-12-23 NEUROC/sec4-experiments.tex
更新了4.4

@@
 The time spent on the sampling phase and the data transferring phase even exceeded the training phase.
+
+% added by wangyunpan, 2020-12-23, ----start----
+\paragraph{Effects on Accuracy}
+%
+We were also concerned about whether the accuracy would be significantly dropped after the use of sampling techniques
+and the effect of batch size of accuracy.
+%
+For all datasets and sampling techniques, we had done experiments where the accuracy of GNNs varied with the batch size
+and compared them with the experimental results of full-batch training.
+%
+In order to make the results more reliable, we had selected the optimal network structure for each GNN experiment under each dataset.
+%
+The optimal network structure is taken from the result corresponding to the highest accuracy in the hyperparameter experiment.
+%
+The highest accuracy under different learning rates was selected as the final accuracy result.
+%
+\figurename~\ref{fig:fig:exp_sampling_relative_batch_size_accuracy} shows the results (we only shows two datasets, amc and fli).
+%
+
+%
+With the change of batch size, the accuracy relationship between GNNs is roughly the same.
+%
+For example, for neigbor sampler, the relationship between GNNs on \texttt{amc} was GCN < GGNN < GAT < GaAN and the relationship on \texttt{amc} was GCN > GGNN > GAT> GaAN.
+%
+But there was also a little exceptions (cluster sampler on \textt{amc}, relative batch size was 50\%).
+%
+To a certain extent, the increase of batch size could bring benefits to all GNNs.
+%
+However, for different datasets, the accuracy relationship between GNNs was not constant.
+%
+And this relationship was not related to model complexity.
+%
+In other words, it was not that the higher the algorithm complexity, the higher the corresponding accuracy.
+%
+For a specific dataset, in order to obtain high accuracy, the best model could only be selected by constantly trying various models.
+%
+
+When the batch size was small, as the batch size increased, the accuracy and the batch size would be positively correlated. 
+%
+However, when the batch size increases to a certain extent, there was no direct relationship between accuracy and batch size.
+%
+In other words, for sampling techniques, the batch size corresponding to the best accuracy may not be the maximum value, but may be another value. 
+%
+This phenomenon is consistent with the results in \cite{zeng2020_graphsaint}.
+
+%
+After using the sampling techniques, the optimal accuracy of some GNNs on certain datasets exceeded the accuracy of the full-batch training (neigbbor sampler on \texttt{amc}).
+%
+This showed that the application of sampling technology was very meaningful, because it may brought certain benefits to accuracy.
+%
+Different sampling techniques bring different gains to GNNs.
+%
+\begin{figure}[H]
+    \centering
+    \subfloat[Neighbor sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
+    \subfloat[Neighbor sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}} \\
+    \subfloat[Cluster sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
+    \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
+    \caption{Test Accuracy under different batch sizes. FULL means that the full graph participates in the training.}
+    \label{fig:exp_sampling_relative_batch_size_accuracy}
+\end{figure}
+
+% added by wangyunpan, 2020-12-23, ----end----

### 2020-12-23 NEUROC/Response-MajRev/response_letter.tex
更新超参数对精度的影响实验结果。

@@
 \usepackage{float}
+\usepackage{subfig}
+\usepackage{graphicx}
+\usepackage{framed}
 % Vector
@@
 \newcommand{\Param}[1]{\textcolor{blue}{#1}}
+
+\newenvironment{myquote}%
+{\begin{leftbar}\begin{quote}}
+{\end{quote}\end{leftbar}}
 
@@
     %
-    \begin{quote}
+    \begin{myquote}
         Some complex GNNs like GAT [6] and GaAN [7] use more than one message passing phase in each GNN layer.
@@
         We will give out more details on sub-layers when we introduce GAT.
-    \end{quote}
+    \end{myquote}
     %
@@
     %
-    \begin{quote}
+    \begin{myquote}
         \newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}[k] \parallel \hvec{x}[k]]))}
@@
         \end{equation}
-    \end{quote}  
+    \end{myquote}  
 \end{reply}
@@
 We quote the related sentence below:
-    \begin{quote}
+    \begin{myquote}
          The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks [8, 9, 10] (like node classification and link prediction) but also computer vision tasks (like human-object interaction [11], human parsing [12], and video object segmentation [13]).
-    \end{quote}
+    \end{myquote}
 \end{reply}
@@
 
-    We appreciate your comment.
+    Thank you for pointing the problem out.
     %
-    We have enlarged Figure 6 and Figure 7 in the revised manuscript.
+    Besides Figure 6 and Figure 7, we have adjusted all the figures in the revised manuscript to make sure that font sizes in figures are no less than the font size of figure captions.
     %
-    Besides them, we have also enlarged fonts in other figures in the manuscript, to make sure that font sizes in figures are no less than the font size of figure captions.
+    To make the figures more easy to read, we also splitted Figure 6 and Figure 7 into five figures (Figure 6 to 10) in the revised manuscript to enlarge the subfigures.
 
@@
 \begin{reply}
+    Thanks very much for your valuable suggestions.
+    %
+    The model complexity directly affected both the accuracy and the training time.
+    %
+    In order to analyze the relationship between model complexity and accuracy, we conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affected the accuracy of GNNs; (2) how the batch size in the sampling methods affected the accuracy of GNNs.
+
+    In this reply, we focus on the first kind of experiments.
+    %
+    We will introduce our results of the second kind of experiments in the next reply.
+
+    In the revised manuscript, we added an extra paragraph ``Effects on Accuracy'' at the end of Section 4.1 ``Effects of Hyper-parameters on Performance'' to analyze how the hyper-parameters affect the accuracy.
+    %
+    We had two main findings: (1) the accuracy of GNNs was much more sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$ (for GCN/GGNN/GaAN) and the dimension of each head $d_{head}$ (for GAT) than the other hyper-parameters; (2) the relative accuracy between the four typical GNNs varied greatly with different datasets.
+    %
+    We quote the related paragraphs from the revised manuscript below:
+
+    \begin{myquote}
+            %%% TO ADD QUOTE %%%
+    \end{myquote}
 \end{reply}

### 2020-12-23 NEUROC/sec4-experiments.tex

@@
 %
-Generally speaking, higher model complexity can bring stronger expressive ability and may bring higher accuracy, but it also increases the risk of overfitting.
+Generally speaking, higher model complexity can bring powerful representation capability and may bring higher accuracy, but it also increases the risk of overfitting.
 %

### 2020-12-23 NEUROC/sec4-experiments.tex

@@
 
-With the sampling techniques, GNNs were trained in a mini-batch manner.
+With the sampling techniques, GNNs were trained and inferenced in a mini-batch manner.
 %
@@
 %
-Since the sampled subgraphs could be much smaller than the original graph, the experiments in this section focused on finding out how the sample size affected the training time, the memory usage and the accuracy of GNNs.
+The batch size determined the size of the sampled subgraph.
+%
+Thus, it affected the accuracy, training/inference time and memory usage of GNNs simultaneously.
+
+\subsubsection{Size of Sampled Subgraphs}
 
@@
 
-To find out performance bottlenecks of the sampling techniques, we decomposed the training time per batch into three phases: \emph{sampling} on the CPU side, \emph{transferring} sampled subgraphs from the CPU side to the GPU side, and \emph{training} with the sampled subgraphs on the GPU side.
+\subsubsection{Effects on Accuracy}
+
+Since the size of sampled subgraph was much smaller than the original graph, it might affect the accuracy of the trained GNNs.
 %
-\figurename~\ref{fig:exp_sampling_batch_train_time} shows the time breakdown of the four GNNs under different relative batch sizes.
+To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes and compared their accuracy with the full-batch training in \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy}.
+%
+The experiemental results on other datasets were similar.
+%
+We used the same hyper-parameters for the sample-based training and the full-batch training.
+%
+For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy for the full-batch training, according to the experimental results in Section~\ref{sec:effects_of_hyper-parameters_on_performance}.
+
+\begin{figure}[H]
+    \centering
+    \subfloat[Neighbor sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
+    \subfloat[Neighbor sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}} \\
+    \subfloat[Cluster sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
+    \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
+    \caption{Test Accuracy under different batch sizes. FULL means that the full graph participates in the training.}
+    \label{fig:exp_sampling_relative_batch_size_accuracy}
+\end{figure}
+
+%
+With the change of batch size, the accuracy relationship between GNNs is roughly the same.
+%
+For example, for neigbor sampler, the relationship between GNNs on \texttt{amc} was GCN < GGNN < GAT < GaAN and the relationship on \texttt{amc} was GCN > GGNN > GAT> GaAN.
+%
+But there was also a little exceptions (cluster sampler on \texttt{amc}, relative batch size was 50\%).
+%
+To a certain extent, the increase of batch size could bring benefits to all GNNs.
+%
+However, for different datasets, the accuracy relationship between GNNs was not constant.
+%
+And this relationship was not related to model complexity.
+%
+In other words, it was not that the higher the algorithm complexity, the higher the corresponding accuracy.
+%
+For a specific dataset, in order to obtain high accuracy, the best model could only be selected by constantly trying various models.
+%
+
+When the batch size was small, as the batch size increased, the accuracy and the batch size would be positively correlated. 
+%
+However, when the batch size increases to a certain extent, there was no direct relationship between accuracy and batch size.
+%
+In other words, for sampling techniques, the batch size corresponding to the best accuracy may not be the maximum value, but may be another value. 
+%
+This phenomenon is consistent with the results in \cite{zeng2020_graphsaint}.
+
+%
+After using the sampling techniques, the optimal accuracy of some GNNs on certain datasets exceeded the accuracy of the full-batch training (neigbbor sampler on \texttt{amc}).
+%
+This showed that the application of sampling technology was very meaningful, because it may brought certain benefits to accuracy.
+%
+Different sampling techniques bring different gains to GNNs.
+%
+
+% added by wangyunpan, 2020-12-23, ----end----
+
+\subsubsection{Performance Bottlenecks Analysis}
+
+To find out performance bottlenecks of the sampling techniques, we decomposed the training/inference time per batch into three phases: \emph{sampling} on the CPU side, \emph{transferring} sampled subgraphs from the CPU side to the GPU side, and \emph{training/inference} with the sampled subgraphs on the GPU side.
+
+\paragraph{Training Time}
+
+\figurename~\ref{fig:exp_sampling_batch_train_time} shows the \emph{training} time breakdown of the four GNNs under different relative batch sizes.
 %
@@
 The time spent on the sampling phase and the data transferring phase even exceeded the training phase.
-
-% added by wangyunpan, 2020-12-23, ----start----
-\paragraph{Effects on Accuracy}
-%
-We were also concerned about whether the accuracy would be significantly dropped after the use of sampling techniques
-and the effect of batch size of accuracy.
-%
-For all datasets and sampling techniques, we had done experiments where the accuracy of GNNs varied with the batch size
-and compared them with the experimental results of full-batch training.
-%
-In order to make the results more reliable, we had selected the optimal network structure for each GNN experiment under each dataset.
-%
-The optimal network structure is taken from the result corresponding to the highest accuracy in the hyperparameter experiment.
-%
-The highest accuracy under different learning rates was selected as the final accuracy result.
-%
-\figurename~\ref{fig:fig:exp_sampling_relative_batch_size_accuracy} shows the results (we only shows two datasets, amc and fli).
-%
-
-%
-With the change of batch size, the accuracy relationship between GNNs is roughly the same.
-%
-For example, for neigbor sampler, the relationship between GNNs on \texttt{amc} was GCN < GGNN < GAT < GaAN and the relationship on \texttt{amc} was GCN > GGNN > GAT> GaAN.
-%
-But there was also a little exceptions (cluster sampler on \textt{amc}, relative batch size was 50\%).
-%
-To a certain extent, the increase of batch size could bring benefits to all GNNs.
-%
-However, for different datasets, the accuracy relationship between GNNs was not constant.
-%
-And this relationship was not related to model complexity.
-%
-In other words, it was not that the higher the algorithm complexity, the higher the corresponding accuracy.
-%
-For a specific dataset, in order to obtain high accuracy, the best model could only be selected by constantly trying various models.
-%
-
-When the batch size was small, as the batch size increased, the accuracy and the batch size would be positively correlated. 
-%
-However, when the batch size increases to a certain extent, there was no direct relationship between accuracy and batch size.
-%
-In other words, for sampling techniques, the batch size corresponding to the best accuracy may not be the maximum value, but may be another value. 
-%
-This phenomenon is consistent with the results in \cite{zeng2020_graphsaint}.
-
-%
-After using the sampling techniques, the optimal accuracy of some GNNs on certain datasets exceeded the accuracy of the full-batch training (neigbbor sampler on \texttt{amc}).
-%
-This showed that the application of sampling technology was very meaningful, because it may brought certain benefits to accuracy.
-%
-Different sampling techniques bring different gains to GNNs.
-%
-\begin{figure}[H]
-    \centering
-    \subfloat[Neighbor sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
-    \subfloat[Neighbor sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}} \\
-    \subfloat[Cluster sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
-    \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
-    \caption{Test Accuracy under different batch sizes. FULL means that the full graph participates in the training.}
-    \label{fig:exp_sampling_relative_batch_size_accuracy}
-\end{figure}
-
-% added by wangyunpan, 2020-12-23, ----end----

### 2020-12-23 NEUROC/sec4-experiments.tex
更新sample size对accuracy的影响.

@@
 %
-To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes and compared their accuracy with the full-batch training in \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy}.
+To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes and compared their accuracy with the full-batch training in \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster}.
 %
@@
     \centering
-    \subfloat[Neighbor sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
-    \subfloat[Neighbor sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}} \\
-    \subfloat[Cluster sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
-    \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
-    \caption{Test Accuracy under different batch sizes. FULL means that the full graph participates in the training.}
-    \label{fig:exp_sampling_relative_batch_size_accuracy}
+    \subfloat[\texttt{amp}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
+    \subfloat[\texttt{amc}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
+    \subfloat[\texttt{fli}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
+    \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
+    \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
 \end{figure}
 
+\begin{figure}[H]
+    \centering
+    \subfloat[\texttt{amp}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
+    \subfloat[\texttt{amc}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
+    \subfloat[\texttt{fli}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
+    \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
+    \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
+\end{figure}
+
+The relationship between the batch size and the accuracy was complex.
 %

### 2020-12-23 NEUROC/sec4-experiments.tex
更新sample size对accuracy的影响.

@@
 %
-To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes and compared their accuracy with the full-batch training in \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster}.
+To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes.
 %
-The experiemental results on other datasets were similar.
+\figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} compare their accuracy with the cases that we used the full graph participated in the training.
 %
-We used the same hyper-parameters for the sample-based training and the full-batch training.
-%
-For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy for the full-batch training, according to the experimental results in Section~\ref{sec:effects_of_hyper-parameters_on_performance}.
+For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section~\ref{sec:effects_of_hyper-parameters_on_performance}.
 

### 2020-12-23 NEUROC/sec4-experiments.tex
更新sample size对accuracy的影响.

@@
 
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat_small_info.pdf}
-    \caption{Effects of the number of heads on GAT ($d_{head}$=2,4)}
-    \label{fig:exp_hyperparameter_accuracy_gat_small_info}
-\end{figure}
+%\begin{figure}[H]
+    %\centering
+    %\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat_small_info.pdf}
+    %\caption{Effects of the number of heads on GAT ($d_{head}$=2,4)}
+    %\label{fig:exp_hyperparameter_accuracy_gat_small_info}
+%\end{figure}
 
@@
     \centering
-    \subfloat[\texttt{amp}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
-    \subfloat[\texttt{amc}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
-    \subfloat[\texttt{fli}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
+    \subfloat[\texttt{amp}\label{fig:exp_cluster_sampling_accuracy_on_amp}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
+    %
+    \subfloat[\texttt{amc}\label{fig:exp_cluster_sampling_accuracy_on_amc}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
+    %
+    \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
     \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
@@
 
-The relationship between the batch size and the accuracy was complex.
+The experimental results confirmed the effectiveness of the sampling methods in terms of model accuracy.
 %
-With the change of batch size, the accuracy relationship between GNNs is roughly the same.
+When the relative batch size was greater than or equal to 3\%, the accuracy of the model trained by sampling was close to the accuracy obtained by full-graph training.
 %
-For example, for neigbor sampler, the relationship between GNNs on \texttt{amc} was GCN < GGNN < GAT < GaAN and the relationship on \texttt{amc} was GCN > GGNN > GAT> GaAN.
+In most cases, the accuracy achieved by the sampling methods was slightly lower than the full-graph training.
 %
-But there was also a little exceptions (cluster sampler on \texttt{amc}, relative batch size was 50\%).
+However, there were some exceptions (like GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}), the accuracy achieved by sampling methods was even higher.
+
+The relationships between batch size and accuracy were complex.
 %
-To a certain extent, the increase of batch size could bring benefits to all GNNs.
+A large batch size did not always bring high accuracy.
 %
-However, for different datasets, the accuracy relationship between GNNs was not constant.
+For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} decreased as the batch size increased.
 %
-And this relationship was not related to model complexity.
+A small batch size sometimes could achieve higher accuracy.
 %
-In other words, it was not that the higher the algorithm complexity, the higher the corresponding accuracy.
+For example, in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}, the accuracy of GAT under 1\% relative batch size was even higher than the accuracy of the full-graph training.
 %
-For a specific dataset, in order to obtain high accuracy, the best model could only be selected by constantly trying various models.
+Given a sampling method, we found that the optimal batch size highly depended on the dataset and the GNN algorithm.
 %
+Our observations were similar to \cite{zeng2020_graphsaint}.
+%
+How to automatically select the proper batch size is a topic worth further studying.
 
-When the batch size was small, as the batch size increased, the accuracy and the batch size would be positively correlated. 
+Among the two sampling methods, the performance of the cluster sampler was stabler than the neighbor sampler.
 %
-However, when the batch size increases to a certain extent, there was no direct relationship between accuracy and batch size.
+With the cluster sampler, the model accuracy of different GNNs was very close to the accuracy of full-graph training.
 %
-In other words, for sampling techniques, the batch size corresponding to the best accuracy may not be the maximum value, but may be another value. 
-%
-This phenomenon is consistent with the results in \cite{zeng2020_graphsaint}.
-
-%
-After using the sampling techniques, the optimal accuracy of some GNNs on certain datasets exceeded the accuracy of the full-batch training (neigbbor sampler on \texttt{amc}).
-%
-This showed that the application of sampling technology was very meaningful, because it may brought certain benefits to accuracy.
-%
-Different sampling techniques bring different gains to GNNs.
-%
-
-% added by wangyunpan, 2020-12-23, ----end----
+With the neighbor sampler, the model accuracy of different GNNs showed more obvious differences.
 

### 2020-12-23 NEUROC/sec2-review-of-graph-neural-network.tex
更新response.
更新sample size对accuracy的影响.

@@
 By using small batch sizes, the peak memory usage during inference can be limited under the GPU memory capacity.
+%
+The sample-based inference is also suitable for the online inference scenario that the topology of the graph evolves over time.
+%
+When a graph update arrives, the subgraph affected by the update is sampled and inferences are only performed on the sampled subgraph.it.
+that are affected by , avoiding conducting repeated inferences for the whole graph.

### 2020-12-23 NEUROC/sec3-experiment-design.tex
更新sample size对accuracy的影响.

@@
     \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training?
-Does the use of sampling techniques in training affect the test accuracy?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
+Does the use of sampling techniques in training affect the model accuracy?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
 
-          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training/inference of a batch.
+          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training of a batch.
           %
@@
           %
-          The test accuracy of GNNs may also be affected.
+          The model accuracy of GNNs may also be affected.
           %

### 2020-12-24 NEUROC/Response-MajRev/response_letter.tex
更新R1Q5的回复。

@@
         %
-        We find that the performance characteristics of GNN inference are similar to GNN training.
+        We conducted the same set of experiments as in the training time anlaysis.
         %
-        The performance bottenecks in GNN inference are also similar to the bottlenecks in training.
+        We found that the performance characteristics of GNN inference were very similar to GNN training.
         %
-        Therefore, we focus on discussing the differences between GNN training and inference in the revised manuscript.
+        The processing time breakdowns on the layer level, step level and operator level of training and inference were all highly similar, as shown in Figure~\ref{} of the response.
+        %
+        Based on the time breakdown analysis, we concluded that the performance bottenecks of GNN training and inference were same.
+        %
+        The difference between training and inference process was mainly reflected in the elapsed time.
+        %
+        Given the same dataset and the same GNN, the inference time was only XX\% of the training time, as compared in Figure~\ref{} of the response.
+        %
+        The training process of each epoch consisted of three phases: forward propagation, backward propagation and evaluation.
+        %
+        The evaluation phase conducted inference for the vertices in the evaluation set.
+        %
+        Under the semi-supervised learning setting, the graph neurons of the whole graph participated in inference, but only the labels of the veritces in the evaluation set were used to calculate accuracy.
+        %
+        Therefore, the elapsed time of the evaluation phase was very close to the elapsed time of inference.
 

### 2020-12-24 NEUROC/sec3-experiment-design.tex
更新R1Q5的回复。

@@
 Vertices of random graphs were classified into 10 classes randomly.
+%
+For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the samples as the training/evaluation/test set, respectively.
+%
+For \texttt{pub}, we used 500/100 vertices as the evaluation/test set and the remained as the training set according to X.
+%
+For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to X.
 

### 2020-12-24 NEUROC/sec3-experiment-design.tex
增加了划分比例的参考文献

--- 2020-12-23 NEUROC/sec3-experiment-design.tex
@@
 Vertices of random graphs were classified into 10 classes randomly.
+%
+For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the samples as the training/evaluation/test set, respectively.
+%
+For \texttt{pub}, we used 500/100 vertices as the evaluation/test set and the remained as the training set according to \cite{chen2018_fastgcn}.
+%
+For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to \cite{zeng2020_graphsaint}.
 

### 2020-12-24 NEUROC/Response-MajRev/response_letter.tex
更新response.

@@
 \usepackage{framed}
+\usepackage[colorlinks=true]{hyperref}
 % Vector
@@
 
-\newenvironment{myquote}%
-{\begin{leftbar}\begin{quote}}
-{\end{quote}\end{leftbar}}
+\usepackage{blindtext}
+\usepackage[most]{tcolorbox} 
+\definecolor{block-gray}{gray}{0.95}
+
+\newtcolorbox{zitat}[2][]{%
+    colback=block-gray,
+    grow to right by=-10mm,
+    grow to left by=-10mm, 
+    boxrule=0pt,
+    boxsep=0pt,
+    breakable,
+    enhanced jigsaw,
+    borderline west={4pt}{0pt}{gray},
+    title={#2\par},
+    colbacktitle={block-gray},
+    coltitle={black},
+    fonttitle={\large\bfseries},
+    attach title to upper={},
+    #1,
+}
+
+\newenvironment{myquote}[1]%
+{\vspace{0.5em}\begin{zitat}{#1}}
+{\end{zitat}\vspace{0.5em}}
 
@@
     %
-    \begin{myquote}
+    \begin{myquote}{Section 2.2}
         Some complex GNNs like GAT [6] and GaAN [7] use more than one message passing phase in each GNN layer.
@@
     %
-    \begin{myquote}
+    \begin{myquote}{Section 2.3}
         \newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}[k] \parallel \hvec{x}[k]]))}
@@
 We quote the related sentence below:
-    \begin{myquote}
+    \begin{myquote}{Section 1}
          The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks [8, 9, 10] (like node classification and link prediction) but also computer vision tasks (like human-object interaction [11], human parsing [12], and video object segmentation [13]).
@@
     To discuss the efficiency of GNN inference on GPUs, we have added performance bottleneck analysis on GNN inference in every subsection of Section 4 ``Evaluation Results and Analysis'':
-    %
-    \begin{enumerate}
 
-        \item In Section 4.1 ``Effects of Hyper-parameters on Performance'', we have additionally measured how the inference time and the peak memory usage changed as we increased the values of the hyper-parameters.
+    In Section 4.1 ``Effects of Hyper-parameters on Performance'', we have additionally measured how the inference time and the peak memory usage changed as we increased the values of the hyper-parameters.
     %
@@
 
-        \item In Section 4.2 ``Time Breakdown Analysis'', we have additionally conducted the time breakdown analysis for GNN inference.
+    In Section 4.2 ``Time Breakdown Analysis'', we have additionally conducted the time breakdown analysis for GNN inference.
     %
@@
     %
-        The processing time breakdowns on the layer level, step level and operator level of training and inference were all highly similar, as shown in Figure~\ref{} of the response.
+    The processing time breakdowns of GCN on the layer level, step level and operator level of training and inference were all highly similar, as shown in Figure~\ref{fig:compare_layer_level_time_breakdown} to Figure~\ref{fig:compare_basic_operators} of the response.
+    %
+    We observed similar phenomena in other GNNs.
     %
@@
     %
-        Under the semi-supervised learning setting, the graph neurons of the whole graph participated in inference, but only the labels of the veritces in the evaluation set were used to calculate accuracy.
+    Under the semi-supervised learning setting, the graph neurons of the whole graph participated in inference, but only the predicted labels of the veritces in the evaluation set were used to calculate accuracy.
     %
@@
 
-        \item In Section 4.3 ``Memory Usage Analysis'', we have additionally conducted the memory usage analysis for GNN inference.
+    \begin{figure}[H]
+        \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_layer_time_proportion_gcn.pdf}}
+       % \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_layer_time_proportion_gcn.pdf}}
+        \caption{Time break down on the layer level of GCN.}
+        \label{fig:compare_layer_level_time_breakdown}
+    \end{figure}
+
+    \begin{figure}[H]
+            \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+            %\subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+            \caption{Effects of the average degree on the time proportion of the edge/vertex calculation of GCN. Graphs were generated by fixing the number of vertices as 50,000.}
+            \label{fig:compare_effect_of_degree}
+     \end{figure}
+
+    \begin{figure}[H]
+            \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_edge_calc_decomposition_gcn.pdf}}
+            %\subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
+            \caption{Time breakdown of the edge calculation stage of GCN.}
+            \label{fig:compare_time_breakdown_of_edge_calculation}
+     \end{figure}
+
+     \begin{figure}[H]
+             \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_top_basic_ops_gcn.pdf}}
+             %\subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}
+             \caption{Top 5 time-consuming basic operators of GCN. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
+             \label{fig:compare_basic_operators}
+      \end{figure}
+
+     In Section 4.3 ``Memory Usage Analysis'', we have additionally conducted the memory usage analysis for GNN inference and added related discussion in XXX.
+     %
+     Figure~\ref{fig:compare_memory_expasion_ratio} in the response (Figure X in the revised manuscript) compares the memory expansion ratios of typical GNNs during training and inference.
+     %
+     For GCN, the memory expansion ratios (MER) of training and inference were nearly same since GCN did not cache intermediate results during training.
+     %
+     For GGNN, the MERs of inference were 45\% to 83\% of training.
+     %
+     For GAT, the MERs of inference were 52\% to 61\% of training.
+     %
+     For GaAN, the MERs of inference were 37\% to 69\% of training.
+     %
+     Though the MERs of GGNN/GAT/GaAN decreased significantly compared with training, the values of MERs were still high.
+     %
+     The high memory usage still prevented us inferencing on big graphs.
+
+     \begin{figure}[H]
+        \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_memory_expansion_ratio.pdf}}
+        \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}}
+        \caption{Memory expansion ratios of typical GNNs.}
+        \label{fig:compare_memory_expasion_ratio}
+     \end{figure}
+
+     %%% TODO %%%
+
+     In Section 4.4 ``Effects of Sampling Techniques on Performance'', we have additionally evaluated the performance bottlenecks in sample-based GNN inference.
      %
@@
      %%% TODO %%%
-
-        \item In Section 4.4 ``Effects of Sampling Techniques on Performance'', we have additionally evaluated the performance bottlenecks in sample-based GNN inference.
-        %
-        We find that ...
-        %%% TODO %%%
-    \end{enumerate}
 
@@
 
-    \begin{myquote}
+    \begin{myquote}{Test}
             %%% TO ADD QUOTE %%%

### 2020-12-24 NEUROC/Response-MajRev/response_letter.tex
更新response.

@@
     %
-    We conducted the same set of experiments as in the training time anlaysis.
+    We found that the performance characteristics of GNN inference were similar to GNN training.
     %
-    We found that the performance characteristics of GNN inference were very similar to GNN training.
+    Figure~\ref{fig:compare_layer_level_time_breakdown} of the response (Figure X in the revised manuscript) compares the time breakdowns of GCN on the layer level.
+    %
+    It indicates that the time breakdowns on the layer level were very similar between inference and training.
+    %
+    Figure~\ref{fig:compare_effect_of_degree}
     %
@@
         \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_layer_time_proportion_gcn.pdf}}
-       % \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_layer_time_proportion_gcn.pdf}}
+        \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_layer_time_proportion_gcn.pdf}}
         \caption{Time break down on the layer level of GCN.}
@@
             \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_edge_calc_decomposition_gcn.pdf}}
-            %\subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
+            \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
             \caption{Time breakdown of the edge calculation stage of GCN.}
@@
              \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_top_basic_ops_gcn.pdf}}
-             %\subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}
+             \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}
              \caption{Top 5 time-consuming basic operators of GCN. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}

### 2020-12-24 NEUROC/Response-MajRev/response_letter.tex
更新response.

@@
             \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-            %\subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+            \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
             \caption{Effects of the average degree on the time proportion of the edge/vertex calculation of GCN. Graphs were generated by fixing the number of vertices as 50,000.}
@@
 There is always tradeoff between model complexity and model performance, and in some scenarios where high complexity is allowed, a sophisticated model of more powerful representation capability is still needed.
-\end{point}
+\end{point}gg
 
@@
     %
-    In order to analyze the relationship between model complexity and accuracy, we conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affected the accuracy of GNNs; (2) how the batch size in the sampling methods affected the accuracy of GNNs.
+    In order to analyze the relationship between model complexity and accuracy, we conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affected the accuracy of GNNs (in Section 4.1); (2) how the batch size in the sampling methods affected the accuracy of GNNs (in Section 4.4).
 
-    In this reply, we focus on the first kind of experiments.
+    In this reply, we focus on the first kind of experiments added in Section 4.1.
     %
-    We will introduce our results of the second kind of experiments in the next reply.
+    We will introduce our results of the second kind of experiments in the nextR reply.
 

### 2020-12-24 NEUROC/Response-MajRev/response_letter.tex
更新R1P6

@@
 
-    In Section 4.1 ``Effects of Hyper-parameters on Performance'', we have additionally measured how the inference time and the peak memory usage changed as we increased the values of the hyper-parameters.
+    In Section 4.1 ``Effects of Hyper-parameters on Performance'', we have additionally measured how the time and the peak memory usage changed as we increased the values of the hyper-parameters during \emph{inference}.
     %
-    We find that ...
-    %%% TODO %%%
+    \begin{itemize}
+    \item For all GNNs, we found that the effects of hyper-parameters on the \emph{inference time} were the same as the training time.
+        %
+        Taking GGNN as an example, Figure~\ref{fig:compare_effect_of_hyperparameter_on_time} in the response (Figure X and Figure X in the revised manuscript) compares the effects of the hidden vector dimension $dim(\MyVec{h}^1_x)$ on training/inference time.
+        %
+        As $dim(\MyVec{h}^1_x)$ increased, the vertex/edge calculation time of training time and inference time both grew linearly when the values of hyper-parameters were large enough.
+        %
+        We observed similar phenomena with the other GNNs.
+        %
+        The results indicated that the time complexity analysis of GNNs were applicable to both training and inference.
+
+        \begin{figure}[H]
+            \centering
+             \subfloat[Training]{\includegraphics[width=0.7\textwidth]{../figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}\\
+            \subfloat[Inference]{\includegraphics[width=0.7\textwidth]{../figs/experiments/exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn.pdf}}
+            \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
+            \label{fig:compare_effect_of_hyperparameter_on_time}
+        \end{figure}
+
+        \item For all GNNs, we found that the effects of hyper-parameters on inference memory usage were also same as training.
+        %
+        Taking GAT as an example, Figure~\ref{fig:compare_effect_of_hyperparameter_on_memory_usage} in the response (Figure X and Figure X in the revised manuscript) compares the peak memory usage during training and inference under different values of hyper-parameters.
+        %
+        The trends of the curves in Figure~\ref{fig:compare_effect_of_hyperparameter_on_memory_usage_training} and Figure~\ref{fig:compare_effect_of_hyperparameter_on_memory_usage_inference} were highly similar.
+        %
+        The memory usage of training and inference \emph{both} grew linearly as the dimension of each head and the number of heads increased.
+        %
+        We observed similar phenomena with the other GNNs.
+        %
+        \begin{figure}[H]
+            \centering
+            \subfloat[Training\label{fig:compare_effect_of_hyperparameter_on_memory_usage_training}]{\includegraphics[width=0.6\textwidth]{../figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
+            \subfloat[Inference\label{fig:compare_effect_of_hyperparameter_on_memory_usage_inference}]{\includegraphics[width=0.6\textwidth]{../figs/experiments/exp_hyperparameter_on_inference_memory_usage_gat.pdf}}
+            \caption{Effects of hyper-parameters on peak memory usage of GAT.}
+            \label{fig:compare_effect_of_hyperparameter_on_memory_usage}
+        \end{figure}
+
+    \end{itemize}
 

### 2020-12-24 NEUROC/sec4-experiments.tex
更新R1P6

@@
 
-\paragraph{Effects on Training/Inference Time}
+\paragraph{Effects on Training Time}
 
@@
 
-To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the training time of the four GNNs in \figurename~\ref{fig:exp_absolute_training_time}.
+To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the \emph{training} time of the four GNNs in \figurename~\ref{fig:exp_absolute_training_time}.
 %
@@
     \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN.}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN during training.}
     \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
@@
     \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN during training.}
     \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
@@
     \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GAT.}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GAT during training.}
     \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
@@
     \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN.}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN during training.}
     \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
@@
 
+\paragraph{Effects on Inference Time}
+
+For all GNNs, we found that the effects of hyper-parameters on the inference time were the same as the training time.
+%
+Taking GGNN as an exmple, \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} shows the effects of hyper-parameters on the inference time of GGNN.
+%
+By cross-comparing \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}, the effects of hyper-parameters on inference time and training time were the same: as $dim(\MyVec{h}^1_x)$ increased, the vertex and edge calculation time both grew linearly when $dim(\MyVec{h}^1_x)$ was large enough.
+%
+For the other GNNs, we observed similar phenomena.
+%
+The results indicated that the complexity analysis presented in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} were also applicable to inference.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN during inference.}
+    \label{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn}
+\end{figure}
+
 \paragraph{Effects on Peak Memory Usage}
@@
 As the hidden vectors $\MyVec{h}^1_x$ consumed a small proportion of memory in GaAN, the growth in the memory usage was not noticeable until $dim(\boldsymbol{h}^1_x)$ was large enough.
+%
+The effects of the hyper-parameters on inference memory usage were the same as training.
+%
+Taking GAT as an example, the peak memory usage during inference grew linearly as the values of hyper-parameters increased, as shown in \figurename~\ref{fig:exp_inference_hyperparameter_memory_usage_gat}.
+%
+By cross-comparing \figurename~\ref{fig:exp_inference_hyperparameter_memory_usage_gat} and \figurename~\ref{fig:exp_hyperparameter_memory_usage_gat}, the hyper-parameters affected the peak memory usage of training and inference in the same way.
+%
+For the other GNNs, we observed similar phenomena.
 
@@
     \subfloat[GGNN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
+    \subfloat[GAT\label{fig:exp_hyperparameter_memory_usage_gat}]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
     \subfloat[GaAN]{\includegraphics[width=0.75\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gaan.pdf}}
@@
     \label{fig:exp_hyperparameter_memory_usage}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_inference_memory_usage_gat.pdf}
+    \caption{Effects of hyper-parameters on the peak GPU memory usage during inference of GAT, excluding the memory used by the dataset and the model parameters.}
+    \label{fig:exp_inference_hyperparameter_memory_usage_gat}
 \end{figure}
@@
 
-The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} was valid.
+The complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} was valid for both training and inference.
 %
@@
 %
-Algorithm engineers could adjust hyper-parameters according to the time complexity to avoid explosive growth in the training time and memory usage.
+Algorithm engineers could adjust hyper-parameters according to the time complexity to avoid explosive growth in the training/inference time and memory usage.
 %
@@
 The relative accuracy between GNNs varied greatly with different datasets.
+%
+There was no clear winner for all datasets.
 

### 2020-12-24 NEUROC/Response-MajRev/response_letter.tex
将e_{x,y}表示与后文统一

@@
             & $v_x$ & The $x$-th vertex of the input graph. \\
-        & $e_{x,y}$ & The edge pointing from $v_x$ to $v_y$ of the input graph. \\
+            & $e_{y,x}$ & The edge pointing from $v_y$ to $v_x$ of the input graph. \\
             & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ 
@@
             \multirow[c]{8}{3em}{Vector}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
-        & $\boldsymbol{e}_{x,y}$ & The feature vector of the edge $e_{x,y}$.  \\
+            & $\boldsymbol{e}_{y,x}$ & The feature vector of the edge $e_{y,x}$.  \\
             & $\boldsymbol{h}_x^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$. \\
             & $\boldsymbol{h}_x^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$.\\
-        & $\boldsymbol{m}_{x,y}^l$ & The message vector of the edge $e_{x,y}$ outputted by $\phi^l$ of the GNN layer $l$. \\
+            & $\boldsymbol{m}_{y,x}^l$ & The message vector of the edge $e_{y,x}$ outputted by $\phi^l$ of the GNN layer $l$. \\
             & $\boldsymbol{s}_{x}^l$ & The aggregated vector of the vertex $v_x$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
-        & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{x,y}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
+            & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{y,x}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
 \\
@@
 
-    In the revised manuscript, we use $e_{x,y}$ to represent an edge and use $\boldsymbol{e}_{x,y}$ to represent its input feature vector.
+    In the revised manuscript, we use $e_{y,x}$ to represent an edge and use $\boldsymbol{e}_{y,x}$ to represent its input feature vector.
     %

### 2020-12-24 NEUROC/sec2-review-of-graph-neural-network.tex
将e_{x,y}表示与后文统一

@@
 %
-We use $v_x$ $(0 \leq x < |\mathcal{V}|)$ to denote a vertex and $e_{x,y}=(v_x, v_y)$ to denote the edge pointing from $v_x$ to $v_y$.
+We use $v_x$ $(0 \leq x < |\mathcal{V}|)$ to denote a vertex and $e_{y,x}=(v_y, v_x)$ to denote the edge pointing from $v_y$ to $v_x$.
 %
-The adjacency set of $v_x$ is $\mathcal{N}(v_x)=\{v|(v_x, v) \in \mathcal{E}\}$.
+The adjacency set of $v_x$ is $\mathcal{N}(v_x)=\{v|(v, v_x) \in \mathcal{E}\}$.
 %
@@
         & $v_x$ & The $x$-th vertex of the input graph. \\
-        & $e_{x,y}$ & The edge pointing from $v_x$ to $v_y$ of the input graph. \\
+        & $e_{y,x}$ & The edge pointing from $v_y$ to $v_x$ of the input graph. \\
         & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ 
@@
         \multirow[c]{8}{3em}{Vector}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
-        & $\boldsymbol{e}_{x,y}$ & The feature vector of the edge $e_{x,y}$.  \\
+        & $\boldsymbol{e}_{y,x}$ & The feature vector of the edge $e_{y,x}$.  \\
         & $\boldsymbol{h}_x^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$. \\
         & $\boldsymbol{h}_x^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$.\\
-        & $\boldsymbol{m}_{x,y}^l$ & The message vector of the edge $e_{x,y}$ outputted by $\phi^l$ of the GNN layer $l$. \\
+        & $\boldsymbol{m}_{y,x}^l$ & The message vector of the edge $e_{y,x}$ outputted by $\phi^l$ of the GNN layer $l$. \\
         & $\boldsymbol{s}_{x}^l$ & The aggregated vector of the vertex $v_x$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
-        & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{x,y}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
+        & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{y,x}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
 \\
@@
 %
-Every edge $e_{x,y}$ of $\mathcal{G}$ may also be attached with a feature vector $\boldsymbol{e}_{x,y}$.
+Every edge $e_{y,x}$ of $\mathcal{G}$ may also be attached with a feature vector $\boldsymbol{e}_{y,x}$.
 %
@@
     %
-    The graph neuron of $v_x$ in the first GNN layer is connected with the input unit of $v_y$  in the input layer only if there is an edge $e_{x,y}$ between $v_x$ and $v_y$ in $\mathcal{G}$.
+    The graph neuron of $v_x$ in the first GNN layer is connected with the input unit of $v_y$  in the input layer only if there is an edge $e_{y,x}$ between $v_y$ and $v_x$ in $\mathcal{G}$.
     %

### 2020-12-24 NEUROC/sec2-review-of-graph-neural-network.tex
修正了sec2的一些拼写错误

@@
 
-In the inpug layer, A GNN receives a graph $\mathcal{G}$ as the input.
+In the input layer, A GNN receives a graph $\mathcal{G}$ as the input.
 %
@@
 The third and fourth sub-layers aggregate the hidden vectors from the GaAN previous layer with the element-wise max and mean operators separately.
-The vertex updating funciton $\gamma^{l,4}$ of the fourth sub-layer uses the hidden vectors of the last two sub-layers $\MyVec{h}^{l, 1}_x, \MyVec{h}^{l, 2}_x$ to generate the output hidden vector $\MyVec{h}^{l+1}_x$.
+The vertex updating funciton $\gamma^{l,3}$ of the fourth sub-layer uses the hidden vectors of the last two sub-layers $\MyVec{h}^{l, 1}_x, \MyVec{h}^{l, 2}_x$ to generate the output hidden vector $\MyVec{h}^{l+1}_x$.
 
@@
 %
-The full-batch gradient descent has two disadvantages \cite{chiang2019_cluster_gcn}:
+But the full-batch gradient descent has two disadvantages \cite{chiang2019_cluster_gcn}:
 %
-(1) it has to cache intermediate results of all vertices in the forward phase, which consumes lots of memory space;
+(1) it has to cache intermediate results of all vertices in the forward phase, consuming lots of memory space, which is not scalable;
 %
@@
 
-In the implementation in PyG, the model parameters of GNNs resid on the GPU side and the input graph resides on the host side.
+In the implementation in PyG, the model parameters of GNNs reside on the GPU side and the input graph resides on the host side.
 %

### 2020-12-24 NEUROC/Response-MajRev/response_letter.tex
更新R1P6

@@
     %
-    To discuss the efficiency of GNN inference on GPUs, we have added performance bottleneck analysis on GNN inference in every subsection of Section 4 ``Evaluation Results and Analysis'':
+    To discuss the efficiency of GNN inference on GPUs, we have added corresponding analysis on GNN inference in every subsection of Section 4 ``Evaluation Results and Analysis''.
+    %
+    Below, we introduce our main findings subsection by subsection.
+
+    \paragraph{Section 4.1 ''Effects of Hyper-parameters on Performance''}
 
     In Section 4.1 ``Effects of Hyper-parameters on Performance'', we have additionally measured how the time and the peak memory usage changed as we increased the values of the hyper-parameters during \emph{inference}.
-    %
-    \begin{itemize}
-    \item For all GNNs, we found that the effects of hyper-parameters on the \emph{inference time} were the same as the training time.
+
+    For all GNNs, we found that the effects of hyper-parameters on the \emph{inference time} were the same as the training time.
     %
@@
 
-        \item For all GNNs, we found that the effects of hyper-parameters on inference memory usage were also same as training.
+    For all GNNs, we found that the effects of hyper-parameters on inference memory usage were also same as training.
     %
@@
 
-    \end{itemize}
+    \paragraph{Section 4.2 ``Time Breakdown Analysis''}    
+    In Section 4.2 ``Time Breakdown Analysis'', we have additionally conducted the time breakdown analysis for GNN inference, in order to find out its performance bottlenecks.
 
-    In Section 4.2 ``Time Breakdown Analysis'', we have additionally conducted the time breakdown analysis for GNN inference.
+    We found that the performance characteristics of GNN inference were highly similar to GNN training on the \emph{layer} level and the \emph{step} level.
     %
-    We found that the performance characteristics of GNN inference were similar to GNN training.
+    In this reply, we used GCN as an example.
     %
-    Figure~\ref{fig:compare_layer_level_time_breakdown} of the response (Figure X in the revised manuscript) compares the time breakdowns of GCN on the layer level.
+    We made similar observations about the other GNNs.
     %
-    It indicates that the time breakdowns on the layer level were very similar between inference and training.
+    Figure~\ref{fig:compare_layer_level_time_breakdown} in the response compares the time breakdowns of GCN on the layer level of training and inference.
     %
-    Figure~\ref{fig:compare_effect_of_degree}
+    The time breakdowns on the layer level were very similar between inference and training.
     %
-    The processing time breakdowns of GCN on the layer level, step level and operator level of training and inference were all highly similar, as shown in Figure~\ref{fig:compare_layer_level_time_breakdown} to Figure~\ref{fig:compare_basic_operators} of the response.
+    Figure~\ref{fig:compare_effect_of_degree} in the response compares the effects of the average degree on the proportion of edge/vertex calculation time during training and inference.
     %
-    We observed similar phenomena in other GNNs.
+    The curves in the two sub-figures of Figure~\ref{fig:compare_effect_of_degree} show very similar trends.
     %
-    Based on the time breakdown analysis, we concluded that the performance bottenecks of GNN training and inference were same.
+    The results indicated that the edge calculation dominated both the training and inference time.
     %
-    The difference between training and inference process was mainly reflected in the elapsed time.
+    Figure~\ref{fig:compare_time_breakdown_of_edge_calculation} in the response further compares the time breakdowns on the step level of the edge calculation stage of GCN.
     %
-    Given the same dataset and the same GNN, the inference time was only XX\% of the training time, as compared in Figure~\ref{} of the response.
+    The proportion of each step was very similar in training and inference.
     %
-    The training process of each epoch consisted of three phases: forward propagation, backward propagation and evaluation.
-    %
-    The evaluation phase conducted inference for the vertices in the evaluation set.
-    %
-    Under the semi-supervised learning setting, the graph neurons of the whole graph participated in inference, but only the predicted labels of the veritces in the evaluation set were used to calculate accuracy.
-    %
-    Therefore, the elapsed time of the evaluation phase was very close to the elapsed time of inference.
+    Therefore, \emph{the performance bottlenecks of training and inference were same on the layer level and step level}.
 
@@
             \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_layer_time_proportion_gcn.pdf}}
-        \caption{Time break down on the layer level of GCN.}
+            \caption{Time breakdowns on the layer level of GCN.}
             \label{fig:compare_layer_level_time_breakdown}
     \end{figure}
-
+    %
     \begin{figure}[H]
-            \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-            \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-            \caption{Effects of the average degree on the time proportion of the edge/vertex calculation of GCN. Graphs were generated by fixing the number of vertices as 50,000.}
+                \subfloat[Training\label{fig:compare_effect_of_degree_training}]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+                \subfloat[Inference\label{fig:compare_effect_of_degree_inference}]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+                \caption{Effects of the average degree on the proportion of the edge/vertex calculation time of GCN. Graphs were generated by fixing the number of vertices as 50,000.}
                 \label{fig:compare_effect_of_degree}
     \end{figure}
-
+    %
     \begin{figure}[H]
@@
                 \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
-            \caption{Time breakdown of the edge calculation stage of GCN.}
+                \caption{Time breakdowns on the step level of the edge calculation stage of GCN.}
                 \label{fig:compare_time_breakdown_of_edge_calculation}
@@
 
+    The main differences between training and inference were reflected in two aspects: the wall-clock time and the top time-consuming basic operators.
+
+    Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} in the response (Figure X in the revised manuscript) compares the wall-clock training/inference time on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
+    %
+    The results on the other datasets were similar.
+    %
+    Since the inference only conducted the forward propagation from the input layer to the prediction layer, the time of inference was very close to the time of the forward phase in training.
+    %
+    The inference time was only 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time for the four GNNs, averaged over datasets.
+
     \begin{figure}[H]
-             \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_top_basic_ops_gcn.pdf}}
-             \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}
-             \caption{Top 5 time-consuming basic operators of GCN. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
-             \label{fig:compare_basic_operators}
+        \centering
+        \subfloat[\texttt{amc}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-computers.pdf}}
+        \subfloat[\texttt{amp}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-photo.pdf}}
+        \subfloat[\texttt{fli}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
+        \caption{Wall-clock training/inference time on different datasets.}
+        \label{fig:compare_wall_clock_time_of_training_and_inference}
     \end{figure}
 
-     In Section 4.3 ``Memory Usage Analysis'', we have additionally conducted the memory usage analysis for GNN inference and added related discussion in XXX.
+    The top time-consuming basic operators of training and inference showed a certain degree of difference.
+    %
+    In All GNNs, some of the top time-consuming operators during training were replaced by new operators in inference.
+    %
+    Figure~\ref{fig:compare_top_time_consuming_basic_operators} in the response compares the top 5 time-consuming basic operators in training and inference.
+    %
+    For GCN, the \texttt{index} operator that was used in the prediction layer became the new top 5 time-consuming operator, replacing the \texttt{gather} operator used in the backward phase in training.
+    %
+    The basic operators related to the edge calculation (\texttt{scatter\_add}, \texttt{index\_select}, and \texttt{mul}) still consumed the majority of the inference time.
+    %
+    For GGNN, \texttt{index} operator in the prediction layer also became one of the top 5 time-consuming basic operators.
+    %
+    Due to the high time complexity of the vertex updating function $\gamma$ in GGNN, the basic operators related to the vertex calculation stage (\texttt{mm} and \texttt{thnn\_fused\_gru\_cell}) still consumed near half of the inference time.
+    %
+    For GAT, the \texttt{input\_put\_impl} operator (used in the backward phase) in Figure~\ref{fig:compare_top_time_consuming_basic_operators}e was replaced by the \texttt{scatter\_add} operator in Figure~\ref{fig:compare_top_time_consuming_basic_operators}f.
+    %
+    The \texttt{scatter\_add} operator was still related to the edge calculation step.
+    %
+    For GaAN, the \texttt{mm} operator of GaAN was replaced by the \texttt{cat} operator used in the vertex updating function.
+
+    Comparing the top basic operator distribution, GNN training and inference had common performance bottlenecks on the operator level.
+    %
+    The matrix multiplication \texttt{mm} and the element-wise multiplication \texttt{mul} operators were the common time-consuming operators, making GNN training and inference \emph{both suitable for GPUs}.
+    %
+    The basic operators related to the collection and aggregation steps in the edge calculation consumed consumed non-trivial time in both training and inference.
+
+    \begin{figure}[H]
+        \centering
+        \subfloat[GCN, Training]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_top_basic_ops_gcn.pdf}}
+         \subfloat[GCN, Inference]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}\\
+        \subfloat[GGNN, Training]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_top_basic_ops_ggnn.pdf}}
+         \subfloat[GGNN, Inference]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_ggnn.pdf}}\\
+        \subfloat[GAT, Training]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_top_basic_ops_gat.pdf}}
+         \subfloat[GAT, Inference]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gat.pdf}}\\
+        \subfloat[GaAN, Training]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_top_basic_ops_gaan.pdf}}
+         \subfloat[GaAN, Inference]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gaan.pdf}}\\
+
+         \caption{Top 5 time-consuming basic operators of typical GNNs.
+The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
+         \label{fig:compare_top_time_consuming_basic_operators}
+
+    \end{figure}
+
+    \paragraph{Section 4.3 ``Memory Usage Analysis''}
+
+     In Section 4.3 ``Memory Usage Analysis'', we have additionally conducted the memory usage analysis for GNN inference and added related discussion.
      %
@@
      %
-     For GCN, the memory expansion ratios (MER) of training and inference were nearly same since GCN did not cache intermediate results during training.
+     Since no intermediate results had to be cached during inference, the memory expansion ratios of inference were much less than training for GGNN, GAT, and GaAN.
      %
-     For GGNN, the MERs of inference were 45\% to 83\% of training.
+     The MERs of inference were 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training.
      %
-     For GAT, the MERs of inference were 52\% to 61\% of training.
-     %
-     For GaAN, the MERs of inference were 37\% to 69\% of training.
-     %
-     Though the MERs of GGNN/GAT/GaAN decreased significantly compared with training, the values of MERs were still high.
-     %
-     The high memory usage still prevented us inferencing on big graphs.
+     However, the values of MERs were still high, disallowing inferencing with big graphs.
 
@@
      %%% TODO %%%
+
+     \paragraph{Section 4.4 ``Effects of Sampling Techniques on Performance''}
 
@@
 There is always tradeoff between model complexity and model performance, and in some scenarios where high complexity is allowed, a sophisticated model of more powerful representation capability is still needed.
-\end{point}gg
+\end{point}
 

### 2020-12-24 paper_exp6_sampling_acc/pics_exp6_sampling_batch_size_acc.py
增加了sampling的绘图文件

@@ -94,25 +94,29 @@ def pics_relative_batch_acc():
         for data in datasets:
             df = pd.read_csv(dir_out + "/" + mode + "_" + data + ".csv", index_col=0)
     
-            locations = [-1.5, -0.5, 0.5, 1.5]
-            x = np.arange(len(xticklabels))
-            width = 0.2
-            colors = plt.get_cmap('Paired')(np.linspace(0.15, 0.85, len(locations)))
+            #locations = [-1.5, -0.5, 0.5, 1.5]
+            #x = np.arange(len(xticklabels))
+            #width = 0.2
+            
+            #colors = plt.get_cmap('Paired')(np.linspace(0.15, 0.85, len(locations)))
+            markers = "oD^sdp"
 
-            fig, ax = plt.subplots(figsize=(7, 6))
-            rects = []
+            fig, ax = plt.subplots(figsize=(7/3, 6/3), tight_layout=True)
+            #rects = []
             for i, c in enumerate(df.columns):
-                rects.append(ax.bar(x + locations[i] * width, list(df[c]) + [df_full.loc[datasets_maps[data], c]], width, label=algorithms[c], color=colors[i]))
+            #   rects.append(ax.bar(x + locations[i] * width, list(df[c]) + [df_full.loc[datasets_maps[data], c]], width, label=algorithms[c], color=colors[i]))
+                ax.plot(xticklabels, list(df[c]) + [df_full.loc[datasets_maps[data], c]], markersize=4, marker=markers[i], label=algorithms[c])
 
-            for r in rects:
-                ax = autolabel(r, ax)
+            #for r in rects:
+            #   ax = autolabel(r, ax)
 
-            ax.set_xlabel("Dataset")
-            ax.set_ylabel("Test Accuracy")
-            ax.set_ylim(0.4, 1.1)
-            ax.set_xticklabels([''] + xticklabels)
-
-            ax.legend(loc="upper right", ncol=4, fontsize="medium")
+            ax.set_xlabel("Relative Batch Size (%)", fontsize=10)
+            ax.set_ylabel("Test Accuracy", fontsize=10)
+            ax.set_ylim(0.4, 1)
+            ax.set_xticklabels(xticklabels, fontsize=8, rotation=30)
+            
+            ax.legend(fontsize="x-small", ncol=2)
+            #ax.legend(loc="upper right", ncol=4, fontsize="medium")
             # ax.legend()
[…]

### 2020-12-25 NEUROC/Response-MajRev/response_letter.tex
更新R1P6
更新R2P4

@@
     colback=block-gray,
-    grow to right by=-10mm,
-    grow to left by=-10mm, 
+    grow to right by=-5mm,
+    grow to left by=-5mm, 
     boxrule=0pt,
@@
     coltitle={black},
-    fonttitle={\large\bfseries},
+    fonttitle={\bfseries},
     attach title to upper={},
@@
 
-     %%% TODO %%%
-
      \paragraph{Section 4.4 ``Effects of Sampling Techniques on Performance''}
-
-     In Section 4.4 ``Effects of Sampling Techniques on Performance'', we have additionally evaluated the performance bottlenecks in sample-based GNN inference.
      %
-     We find that ...
-     %%% TODO %%%
+     Since the workflow of sample-based inference
 
@@
     %
-    We will introduce our results of the second kind of experiments in the nextR reply.
+    We will introduce our results of the second kind of experiments in the next reply.
 
-    In the revised manuscript, we added an extra paragraph ``Effects on Accuracy'' at the end of Section 4.1 ``Effects of Hyper-parameters on Performance'' to analyze how the hyper-parameters affect the accuracy.
+    Hyper-parameters determined the model complexity of a GNN.
     %
-    We had two main findings: (1) the accuracy of GNNs was much more sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$ (for GCN/GGNN/GaAN) and the dimension of each head $d_{head}$ (for GAT) than the other hyper-parameters; (2) the relative accuracy between the four typical GNNs varied greatly with different datasets.
+    Generally speaking, higher values of hyper-parameters brought higher model complexity, affecting model accuracy.
     %
-    We quote the related paragraphs from the revised manuscript below:
+    In the revised manuscript, we added extra paragraphs ``Effects on Accuracy'' at the end of Section 4.1 ``Effects of Hyper-parameters on Performance'' to analyze how the hyper-parameters affect the accuracy.
+    %
+    We had two main findings.
+    %
+    First, the accuracy of GNNs was much more sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$ (for GCN/GGNN/GaAN) and the dimension of each head $d_{head}$ (for GAT) than the other hyper-parameters.
+    %
+    Second, the relative accuracy between the four typical GNNs varied greatly with different datasets.
+    %
+    We quote the related paragraphs from the revised manuscript below.
 
-    \begin{myquote}{Test}
-            %%% TO ADD QUOTE %%%
+    \begin{myquote}{Section 4.1 ``Effects of Hyper-parameters on Performance''}
+    %
+    \emph{Effects on Accuracy}.
+    %
+    The relationship between hyper-parameters of GNNs (i.e., model complexity) and accuracy is very complicated, and there is no clear theoretical analysis yet.
+    %
+    Generally speaking, higher model complexity can bring powerful representation capability and may bring higher accuracy, but it also increases the risk of overfitting.
+    %
+    To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the four typical GNNs under different hyper-parameters.
+    %
+    \figurename~\ref{fig:exp_hyperparameter_accuracy} shows the experimental results.
+
+    For GCN, the accuracy was sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$.
+    %
+    As $dim(\MyVec{h}^1_x)$ increased, the accuracy first increased quickly and then stabilized when $dim(\MyVec{h}_x^1) \geq 8$.
+    %
+    For GGNN, its accuracy curves showed similar trends as GCN.
+    %
+    However, GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN.
+    %
+    Its accuracy even decreased when $dim(\MyVec{h}_x^1) \geq 1024$.
+    %
+    Since GGNN had high model complexity (with 13 weight matrices/vectors to train), GGNN might occur overfitting in those cases.
+    %
+    For GAT, its accuracy was more sensitive to the dimension of each head $d_{head}$ than the number of heads.
+    %
+    For GaAN, only $dim(\MyVec{h}_x^1)$ showed obvious impacts on accuracy.
+    %
+    The experimental results indicated the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was small.
+    %
+    In those cases, the low model complexity limited the expressive power of the GNNs.
+    %
+    As $dim(\MyVec{h}_x^1)$ or $d_{head}$ increased to a certain threshold, the GNNs had sufficient learning ability to achieve stable accuracy.
+
+    \begin{figure}[H]
+        \centering
+        \subfloat[GCN]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gcn.pdf}}
+        \subfloat[GGNN]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_ggnn.pdf}}\\
+        \subfloat[GAT]{\includegraphics[width=0.6\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gat.pdf}}\\
+        \subfloat[GaAN]{\includegraphics[width=0.9\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
+        \caption{Effects of hyper-parameters on accuracy of the typical GNNs.}
+        \label{fig:exp_hyperparameter_accuracy}
+    \end{figure}
+
+    %\begin{figure}[H]
+        %\centering
+        %\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat_small_info.pdf}
+        %\caption{Effects of the number of heads on GAT ($d_{head}$=2,4)}
+        %\label{fig:exp_hyperparameter_accuracy_gat_small_info}
+    %\end{figure}
+
+    \figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} compares the best accuracy that each GNN achieved on different datasets.
+    %
+    The best accuracy that the four GNNs achieved was very close.
+    %
+    It was also close to the accuracy reported in their original references [1][4][6][7].
+    %
+    There was no clear winner in terms of accuracy.
+    %
+    The relative accuracy between GNNs varied greatly with different datasets.
+    %
+    GaAN achieved the highest accuracy in three out of five datasets.
+    %
+    GCN also achieved the highest or second highest accuracy in three out of five datasets, though its model was simplest.
+    %
+    It indicated that simple GNN models (such as GCN) could still achieve good accuracy with proper hyper-parameter settings.
+
+    \begin{figure}[H]
+        \centering
+        \includegraphics[width=3in]{../figs/experiments/exp_hyperparameter_on_accuracy_alg_contrast.pdf}
+        \caption{Best accuracy that each GNN achieved on different datasets.}
+        \label{fig:exp_hyperparameter_on_accuracy_alg_contrast}
+    \end{figure}
+
     \end{myquote}
@@
 \begin{reply}
+
+    Thank you for your insightful comment and valuable suggestion.
+    %
 

### 2020-12-25 NEUROC/Response-MajRev/response_letter.tex
更新R1P6

@@
 \begin{reply}
-    We apologize for the confusing use of symbols and thank you for pointing the problem out.
+    We apologize for the confusing use of symbols.
     %
-    To clarify the symbol usage, we have checked the manuscript and unified the usage of symbol.
+    To clarify the symbol usage, we have checked our manuscript and unified the usage of symbol in the revised version.
     %
-    We avoid the problem of reusing symbols, so that each symbol only represents one meaning after the revision.
+    After revision, each symbol only represents one meaning.
     %
-    We summarize the frequently-used symbols in Table 1 in the revised manuscript.
+    We added Table 1 at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised version to summarize frequently-used symbols.
     %
@@
     %
-    The input feature vectors of all edges are same for all GNN layers.
+    %The input feature vectors of all edges are same for all GNN layers.
     %
@@
     %
-    For every vertex $v_x$, we use $\boldsymbol{s}^l_x$ to denote its aggregated vector in the GNN layer $l$.
+    For every vertex $v_x$, we use $\boldsymbol{s}^l_x$ to denote the aggregated vector in the graph neuron of $v_x$ in the GNN layer $l$.
     %
-    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents its aggregated vector in the $i$-th sub-layer.
+    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents the aggregated vector of $v_x$ in the $i$-th sub-layer.
 
-    To clarify the concept of \emph{sub-layers} in a GNN layer, we have added more description on it in the revised manuscript.
+    To clarify the concept of \emph{sub-layers} in a GNN layer, we have added more description in the revised manuscript.
     %
@@
     %
-    \begin{myquote}{Section 2.2}
+    \begin{myquote}{Section 2.2 ``Graph Neuron and Message-passing Model''}
         Some complex GNNs like GAT [6] and GaAN [7] use more than one message passing phase in each GNN layer.
@@
     %
-    \begin{myquote}{Section 2.3}
-        \newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}[k] \parallel \hvec{x}[k]]))}
+    \begin{myquote}{Section 2.3.3 ``GAT (Low Vertex \& High Edge Complexity)''}
+        \newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}^l[k] \parallel \hvec{x}^l[k]]))}
         Each GAT layer consists of a vertex pre-processing phase and two sub-layers (i.e., message-passing phases).
 
-        The vertex pre-processing phase calculates the attention vector $\hat{\boldsymbol{h}}^{l}_{x}$ for every vertex $v_x$ by $\hvec{x} = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
-We denote the attention sub-vector generated by the $k$-th head as $\hvec{x}[k]=\Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
+        The vertex pre-processing phase calculates the attention vector $\hat{\boldsymbol{h}}^{l}_{x}$ for every vertex $v_x$ by $\hvec{x}^l = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
+We denote the attention sub-vector generated by the $k$-th head as $\hvec{x}^l[k]=\Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
 
@@
             \begin{aligned}
-                \MyVec{m}^{l,0}_{y,x} & = \phi^{l,0}(\MyVec{h}^l_y, \MyVec{h}^l_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\GATCalcWeight, \\
+                \MyVec{m}^{l,0}_{y,x} & = \phi^{l,0}(\MyVec{h}^l_y, \MyVec{h}^l_x, \MyVec{e}_{y,x}, \hvec{y}^l, \hvec{x}^l) = \parallel_{k=1}^{K}\GATCalcWeight, \\
                 \MyVec{s}^{l,0}_{x} &= {\Sigma}_{v_y \in \mathcal{N}(v_x)}{\MyVec{m}^{l,0}_{y,x}}, \\
@@
             \begin{aligned}
-                \MyVec{m}^{l,1}_{y,x} &= \phi^{l,1}(\MyVec{h}^{l,0}_y, \MyVec{h}^{l,0}_x, \MyVec{e}_{y,x}, \hvec{y}, \hvec{x}) = \parallel_{k=1}^{K}\frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}[k], \\
+                \MyVec{m}^{l,1}_{y,x} &= \phi^{l,1}(\MyVec{h}^{l,0}_y, \MyVec{h}^{l,0}_x, \MyVec{e}_{y,x}, \hvec{y}^l, \hvec{x}^l) = \parallel_{k=1}^{K}\frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}^l[k], \\
                 \MyVec{s}^{l,1}_x &= {\Sigma}_{v_y \in \mathcal{N}(v_x)} \MyVec{m}^{l,1}_{y,x}, \\
@@
 \begin{reply}
-	Thank you for pointing out our shortcomings.
-Computer vision is indeed another important application area of graph neural networks.
-We have added the mentioned references in the INTRODUCTION section in the revised manuscript.
+	Thank you for pointing out missing references.
+Computer vision is indeed an important application area of graph neural networks.
+We have added the mentioned references in Section 1 ``Introduction'' in the revised manuscript.
 We quote the related sentence below:
-    \begin{myquote}{Section 1}
+    \begin{myquote}{Section 1 ``Introduction''}
          The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks [8, 9, 10] (like node classification and link prediction) but also computer vision tasks (like human-object interaction [11], human parsing [12], and video object segmentation [13]).
@@
     %
-    We only use the present tense in the sentences that Figure/Table X are the subjects of the sentences.
+    We only use the present tense in the sentences that FigureX/Table X are the subjects of the sentences.
 
@@
 
-    Thank you for pointing the problem out.
+    As you suggested, we have adjusted all the figures (besides Figure 6 and Figure 7) in the revised manuscript to make sure that font sizes in figures are no less than the font size of figure captions.
     %
-    Besides Figure 6 and Figure 7, we have adjusted all the figures in the revised manuscript to make sure that font sizes in figures are no less than the font size of figure captions.
-    %
-    To make the figures more easy to read, we also splitted Figure 6 and Figure 7 into five figures (Figure 6 to 10) in the revised manuscript to enlarge the subfigures.
+    To make the figures more easy to read, we also split Figure 6 and Figure 7 into five figures (Figure 6 to 10) in the revised manuscript to enlarge the subfigures.
 
@@
     %
-    In the revised manuscript, we have added a new subsection (Section 2.5 ``Inference with GNNs'') in the revised manuscript to briefly review how to perform inference with GNNs.
+    In the revised manuscript, we have added a new subsection (Section 2.5 ``Inference with GNNs'') to briefly review how to perform inference with GNNs.
     %
-    To discuss the efficiency of GNN inference on GPUs, we have added corresponding analysis on GNN inference in every subsection of Section 4 ``Evaluation Results and Analysis''.
+    We quote the added subsection below.
+
+    \begin{myquote}{Section 2.5 ``Inference with GNNs''}
+    The model parameters of a GNN consist of the weight vectors/matrices in the prediction layer and the messaging/aggregation/updating functions of each GNN layer.
+    %
+    For transductive learning, the input graphs of training and inference are same.
+    %
+    The structure of the GNN does not need to adjust. 
+    %
+    For inductive learning, the input graphs used in training and inference are different.
+    %
+    When we want to perform inference on a new graph with a pre-trained GNN, the structure of the GNN needs to be adjusted, but the hyper-parameters and the model parameters of the GNN remain unchanged.
+    %
+    The number of graph neurons in each GNN layer has to be adjusted to $|\mathcal{V}|$ of the new graph.
+    %
+    The connections of graph neurons between GNN layers are also adjusted according to the edge set of the new graph.
+    %
+    During inference, input feature vectors of the input graph are propagated forward from the input layer to the prediction layer to give out predicted labels.
+
+    When the memory capacity of the GPU is large enough to hold all of the input graph and intermediate results during inference, the inference can produce predicted labels for all vertices and edges at once, making full use of the computing power of the GPU.
+    %
+    When the memory capacity is not large enough, the sampling technique must be adopted.
+
+    The sample-based inference splits the test set into several batches.
+    %
+    For each batch, the sample-based inference samples a subgraph related to the batch from the input graph.
+    %
+    It performs inference on the sampled subgraph to produce predicted labels for the batch.
+    %
+    Since the sampled subgraph is usually much smaller than the original input graph, the memory usage during inference is limited.
+    %
+    The sampling method depends on the prediction task.
+    %
+    Taking the node classification task as an example, if there are $L$ GNN layers in the GNN, the hidden vector outputted by the last GNN layer of each vertex $\MyVec{h}^L_x$ is only related to the $L$-hop neighborhood of $v_x$.
+    %
+    Thus, if we want to predict labels for a group of vertices, we only need to sample a subgraph that contains $L$-hop neighborhoods of all given vertices.
+
+    The implementation of sample-based inference in PyG stores the whole input graph and its feature vectors in the main memory.
+    %
+    In the node classification task, it splits the vertices in the test set into batches accoding to a given batch size.
+    %
+    The subgraph corresponding to each batch is sampled on the CPU side and sent to the GPU side to perform inference.
+    %
+    %By using small batch sizes, the peak memory usage during inference can be limited under the GPU memory capacity.
+
+%    The sample-based inference is also suitable for the online inference scenario that the topology of the graph evolves over time.
+    %
+%    When a graph update arrives, the subgraph affected by the update is sampled and inferences are only performed on the sampled subgraph.it.
+that are affected by , avoiding conducting repeated inferences for the whole graph.
+    \end{myquote}
+
+    To discuss the efficiency of GNN inference on GPUs, we have added corresponding analysis in every subsection of Section 4 ``Evaluation Results and Analysis''.
     %
@@
 
-    \paragraph{Section 4.1 ''Effects of Hyper-parameters on Performance''}
+    \paragraph{Section 4.1 ``Effects of Hyper-parameters on Performance''}
 
-    In Section 4.1 ``Effects of Hyper-parameters on Performance'', we have additionally measured how the time and the peak memory usage changed as we increased the values of the hyper-parameters during \emph{inference}.
+    We added paragraphs ``Effects on Inference Time'' in the middle of Section 4.1 to discuss how the time and the peak memory usage of inference changed as we increased the values of the hyper-parameters.
 
@@
     %
-    Taking GGNN as an example, Figure~\ref{fig:compare_effect_of_hyperparameter_on_time} in the response (Figure X and Figure X in the revised manuscript) compares the effects of the hidden vector dimension $dim(\MyVec{h}^1_x)$ on training/inference time.
+    Taking GGNN as an example, Figure~\ref{fig:compare_effect_of_hyperparameter_on_time} in the response (Figure X and Figure X in the revised manuscript) shows the effects of the hidden vector dimension $dim(\MyVec{h}^1_x)$ on training/inference time.
     %
-    As $dim(\MyVec{h}^1_x)$ increased, the vertex/edge calculation time of training time and inference time both grew linearly when the values of hyper-parameters were large enough.
+    When $dim(\MyVec{h}^1_x)$ was large enough, the vertex/edge calculation time of training time and inference time both grew linearly with $dim(\MyVec{h}^1_x)$.
     %
-    We observed similar phenomena with the other GNNs.
+    We observed similar phenomena in the other GNNs.
     %
@@
 
-    For all GNNs, we found that the effects of hyper-parameters on inference memory usage were also same as training.
+    The effects of hyper-parameters on inference memory usage were also same as training.
     %
-    Taking GAT as an example, Figure~\ref{fig:compare_effect_of_hyperparameter_on_memory_usage} in the response (Figure X and Figure X in the revised manuscript) compares the peak memory usage during training and inference under different values of hyper-parameters.
+    Taking GAT as an example, Figure~\ref{fig:compare_effect_of_hyperparameter_on_memory_usage} in the response (Figure X and Figure X in the revised manuscript) shows the peak memory usage during training and inference under different values of hyper-parameters.
         %
@@
         %
-    We observed similar phenomena with the other GNNs.
+    We observed similar phenomena in the other GNNs.
         %
@@
     \paragraph{Section 4.2 ``Time Breakdown Analysis''}    
-    In Section 4.2 ``Time Breakdown Analysis'', we have additionally conducted the time breakdown analysis for GNN inference, in order to find out its performance bottlenecks.
+    We have added a new subsection Section 4.2.4 ``Performance Bottlenecks in Inference'' in Section 4.2 to conduct time breakdown analysis for GNN inference and compare the differences between training and inference.
 
-    We found that the performance characteristics of GNN inference were highly similar to GNN training on the \emph{layer} level and the \emph{step} level.
+    We found that the performance characteristics of GNN inference were highly similar to training on the \emph{layer} level and the \emph{step} level.
     %
@@
     %
-    We made similar observations about the other GNNs.
+    We made similar observations in the other GNNs.
     %
@@
     %
-    The time breakdowns on the layer level were very similar between inference and training.
+    The time breakdowns were very similar.
     %
-    Figure~\ref{fig:compare_effect_of_degree} in the response compares the effects of the average degree on the proportion of edge/vertex calculation time during training and inference.
+    Figure~\ref{fig:compare_effect_of_degree} in the response compares the effects of the average degree on the edge/vertex calculation time during training and inference.
     %
-    The curves in the two sub-figures of Figure~\ref{fig:compare_effect_of_degree} show very similar trends.
+    The curves in the two sub-figures of Figure~\ref{fig:compare_effect_of_degree} have similar trends.
     %
-    The results indicated that the edge calculation dominated both the training and inference time.
+    \emph{The edge calculation stage dominated both the training and inference time}.
     %
-    Figure~\ref{fig:compare_time_breakdown_of_edge_calculation} in the response further compares the time breakdowns on the step level of the edge calculation stage of GCN.
+    Figure~\ref{fig:compare_time_breakdown_of_edge_calculation} in the response further compares the time breakdowns on the step level of the edge calculation stage.
     %
-    The proportion of each step was very similar in training and inference.
+    The proportion of each step was very similar between training and inference.
     %
-    Therefore, \emph{the performance bottlenecks of training and inference were same on the layer level and step level}.
+    The results indicated that \emph{the performance bottlenecks of training and inference were same on the layer level and step level}.
 
@@
                 \subfloat[Inference\label{fig:compare_effect_of_degree_inference}]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-                \caption{Effects of the average degree on the proportion of the edge/vertex calculation time of GCN. Graphs were generated by fixing the number of vertices as 50,000.}
+                \caption{Effects of the average degree on the edge/vertex calculation time of GCN. Graphs were generated by fixing the number of vertices as 50,000.}
                 \label{fig:compare_effect_of_degree}
@@
 
-    Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} in the response (Figure X in the revised manuscript) compares the wall-clock training/inference time on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
+    The inference time was much less than the training time.
+    %
+    Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} in the response (Figure X in the revised manuscript) compares the wall-clock time of training and inference on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
     %
@@
     %
-    The inference time was only 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time for the four GNNs, averaged over datasets.
+    The inference time was 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time, averaged over all datasets.
 
@@
 
-    The top time-consuming basic operators of training and inference showed a certain degree of difference.
+    The top time-consuming basic operators of training and inference also showed a certain degree of difference.
     %
-    In All GNNs, some of the top time-consuming operators during training were replaced by new operators in inference.
+    Some of the top time-consuming operators during training were replaced by new operators in inference.
     %
-    Figure~\ref{fig:compare_top_time_consuming_basic_operators} in the response compares the top 5 time-consuming basic operators in training and inference.
+    Figure~\ref{fig:compare_top_time_consuming_basic_operators} in the response (Figure X in the revised manuscript) compares the top 5 time-consuming basic operators in training and inference.
     %
-    For GCN, the \texttt{index} operator that was used in the prediction layer became the new top 5 time-consuming operator, replacing the \texttt{gather} operator used in the backward phase in training.
+    For GCN, the \texttt{index} operator used in the prediction layer became the new top 5 time-consuming operator, replacing the \texttt{gather} operator used in the backward phase in training.
     %
-    The basic operators related to the edge calculation (\texttt{scatter\_add}, \texttt{index\_select}, and \texttt{mul}) still consumed the majority of the inference time.
+%    The basic operators related to the edge calculation (\texttt{scatter\_add}, \texttt{index\_select}, and \texttt{mul}) still consumed the majority of the inference time.
     %
@@
     %
-    Due to the high time complexity of the vertex updating function $\gamma$ in GGNN, the basic operators related to the vertex calculation stage (\texttt{mm} and \texttt{thnn\_fused\_gru\_cell}) still consumed near half of the inference time.
+%    Due to the high time complexity of the vertex updating function $\gamma$ in GGNN, the basic operators related to the vertex calculation stage (\texttt{mm} and \texttt{thnn\_fused\_gru\_cell}) still consumed near half of the inference time.
     %
-    For GAT, the \texttt{input\_put\_impl} operator (used in the backward phase) in Figure~\ref{fig:compare_top_time_consuming_basic_operators}e was replaced by the \texttt{scatter\_add} operator in Figure~\ref{fig:compare_top_time_consuming_basic_operators}f.
+    For GAT, the \texttt{input\_put\_impl} operator (used in the backward phase) in Figure~\ref{fig:compare_top_time_consuming_basic_operators}e was replaced by the \texttt{scatter\_add} operator used in the forward edge calculation in Figure~\ref{fig:compare_top_time_consuming_basic_operators}f.
     %
-    The \texttt{scatter\_add} operator was still related to the edge calculation step.
+%    The \texttt{scatter\_add} operator was related to the edge calculation step.
     %
-    For GaAN, the \texttt{mm} operator of GaAN was replaced by the \texttt{cat} operator used in the vertex updating function.
+    For GaAN, the \texttt{mm} operator was replaced by the \texttt{cat} operator used in the vertex updating function.
 
-    Comparing the top basic operator distribution, GNN training and inference had common performance bottlenecks on the operator level.
+    Although some specific time-consuming operators were different, the performance bottlenecks on the operator level were same for training and inference.
     %
-    The matrix multiplication \texttt{mm} and the element-wise multiplication \texttt{mul} operators were the common time-consuming operators, making GNN training and inference \emph{both suitable for GPUs}.
+    The matrix multiplication \texttt{mm} and the element-wise multiplication \texttt{mul} operators were still time-consuming for inference, making GNN inference also {suitable for GPUs}.
     %
-    The basic operators related to the collection and aggregation steps in the edge calculation consumed consumed non-trivial time in both training and inference.
+    The basic operators related to the collection and aggregation steps in the edge calculation still consumed non-trivial time in inference.
 
@@
 
-     In Section 4.3 ``Memory Usage Analysis'', we have additionally conducted the memory usage analysis for GNN inference and added related discussion.
+     In the end of Section 4.3, we added a new paragraph ``Memory Usage of Inference'' to compare the memory usage of inference and training.
      %
@@
      %
-     Since no intermediate results had to be cached during inference, the memory expansion ratios of inference were much less than training for GGNN, GAT, and GaAN.
+     Since no intermediate results had to be cached during inference of GGNN, GAT, and GaAN, the memory expansion ratios of inference were much less than training for the three GNNs.
      %
@@
      %
-     However, the values of MERs were still high, disallowing inferencing with big graphs.
+     However, the MERs were still high, disallowing inferencing with big graphs.
+     %
+     To handle big graphs, sample-based inference was necessary.
 
@@
      %
-     Since the workflow of sample-based inference
+     In Section 4.4, we added a new subsection  Section 4.4.4 ``Performance Bottlenecks in Inference'' to discuss the performance bottlenecks in sample-based inference.
 
+     Sample-based inference was an effective technique to handle big graphs.
+     %
+     Taking the node classification task as an example, to predict labels for a given set of vertices $\mathcal{V}_{predict}$, the inference sampler sampled a subgraph containing complete $L$-hop neighborhoods of all vertices in $\mathcal{V}_{predict}$, where $L$ was the number of GNN layers.
+     %
+     Since the real-world graphs often had small-world property, the size of the sampled subgraph increased quickly as the number of vertices in $\mathcal{V}_{predict}$ (i.e., batch size) increased.
+     %
+     Figure~\ref{fig:sampled_graph_size} (Figure X in the revised manuscript) shows how the relative batch size ($\frac{|\mathcal{V}_{predict}|}{|\mathcal{V}|}$) affected the average degree and the number of edges of the sampled subgraphs during inference.
+     %
+     When the relative batch size was 10\%, the number of edges in the sampled subgraphs were close to the number of edges in the whole graph.
+     %
+     In order to limit the memory usage during inference, the batch size used in inference should be very small.
+
+     \begin{figure}[H]
+        \centering
+        \includegraphics[width=0.6\columnwidth]{../figs/experiments/exp_inference_graph_info_edges}
+        \caption{Number of edges in the sampled subgraphs produced by the inference sampler under different relative batch sizes.}
+        \label{fig:sampled_graph_size}
+     \end{figure}
+
+     When the batch size was small, the overheads brought by sampling and data transfering from CPU to GPU became obvious.
+     %
+     Figure~\ref{fig:time_breakdown_of_inference_sampler} (Figure X in the revised manuscript) shows the time breakdown of sample-based inference on different datasets.
+     %
+     On the \texttt{amp} and \texttt{cam} datasets, the sampling time could account for near half of the total inference time.
+     %
+     The current implementation of inference sampling in PyG was also inefficient.
+     %
+     Improving its efficiency could significantly reduce the inference time.
+
+     \begin{figure}[H]
+        \centering
+        \subfloat[Batch Size = 1024]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_fix_batch_size_train_time_stack_1024.pdf}}
+        \subfloat[Batch Size = 2048]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_fix_batch_size_train_time_stack_2048.pdf}}
+        \caption{Inference time per batch breakdown under different batch sizes.}
+        \label{fig:time_breakdown_of_inference_sampler}
+     \end{figure}
 \end{reply}

### 2020-12-25 NEUROC/sec3-experiment-design.tex
fix sec3 mistakes

@@
 %
-For the \texttt{cam} dataset, since its vertices were not associated with feature vectors, we generated random dense feature vectors for it and excluded it from accuracy evaluation.
+For the \texttt{cam} dataset, we generated random dense feature vectors for it.
+%
+Since its vertices were not associated with feature vectors, we excluded it from accuracy evaluation.
 %
@@
 %
-For \texttt{pub}, we used 500/100 vertices as the evaluation/test set and the remained as the training set according to \cite{chen2018_fastgcn}.
+For \texttt{pub}, we used 500/1000 vertices as the evaluation/test set and the remained as the training set according to \cite{chen2018_fastgcn}.
 %

### 2020-12-25 NEUROC/Response-MajRev/response_letter.tex
更新R1P6

@@
 
-%%%% TODO %%%
+TODO
 
@@
      %
-     When the relative batch size was 10\%, the number of edges in the sampled subgraphs were close to the number of edges in the whole graph.
+     When the relative batch size was 10\%, the number of edges in the sampled subgraphs were close to the number of edges in the whole graph in most datasets.
      %
-     In order to limit the memory usage during inference, the batch size used in inference should be very small.
+     In order to limit the memory usage during inference, the batch size used should be very small.
 
@@
         \centering
-        \includegraphics[width=0.6\columnwidth]{../figs/experiments/exp_inference_graph_info_edges}
-        \caption{Number of edges in the sampled subgraphs produced by the inference sampler under different relative batch sizes.}
+        \subfloat[Average degree]{    \includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_graph_info_inference_sampler_avg_degrees.pdf}}
+        \subfloat[Number of edges]{    \includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_graph_info_inference_sampler_edges.pdf}}
+
+        \caption{Characteristics of the sampled subgraphs produced by the inference sampler under different relative batch sizes.}
         \label{fig:sampled_graph_size}
@@
 
-     When the batch size was small, the overheads brought by sampling and data transfering from CPU to GPU became obvious.
+     However, the overheads brought by sampling and data transfering from CPU to GPU became obvious when the batch size was small.
      %
-     Figure~\ref{fig:time_breakdown_of_inference_sampler} (Figure X in the revised manuscript) shows the time breakdown of sample-based inference on different datasets.
+     Figure~\ref{fig:time_breakdown_of_inference_sampler} (Figure X in the revised manuscript) shows the time breakdowns of sample-based inference on different datasets.
      %
-     On the \texttt{amp} and \texttt{cam} datasets, the sampling time could account for near half of the total inference time.
+     On the \texttt{amp} and \texttt{cam} datasets, the sampling time even accounted for near half of the total inference time.
      %
-     The current implementation of inference sampling in PyG was also inefficient.
+     The results indicated that the current implementation of inference sampler in PyG was also inefficient.
      %

### 2020-12-25 NEUROC/Response-MajRev/response_letter.tex

@@
     colback=block-gray,
-    grow to right by=-5mm,
-    grow to left by=-5mm, 
+    grow to right by=-0mm,
+    grow to left by=-0mm, 
     boxrule=0pt,
@@
      %
+
+     %
      Figure~\ref{fig:compare_memory_expasion_ratio} in the response (Figure X in the revised manuscript) compares the memory expansion ratios of typical GNNs during training and inference.
@@
         \centering
-        \subfloat[GCN]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gcn.pdf}}
-        \subfloat[GGNN]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_ggnn.pdf}}\\
-        \subfloat[GAT]{\includegraphics[width=0.6\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gat.pdf}}\\
-        \subfloat[GaAN]{\includegraphics[width=0.9\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
+        \subfloat[GCN]{\includegraphics[width=0.4\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gcn.pdf}}
+        \subfloat[GGNN]{\includegraphics[width=0.4\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_ggnn.pdf}}\\
+        \subfloat[GAT]{\includegraphics[width=0.8\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gat.pdf}}\\
+        \subfloat[GaAN]{\includegraphics[width=1.0\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
         \caption{Effects of hyper-parameters on accuracy of the typical GNNs.}
@@
         \centering
-        \includegraphics[width=3in]{../figs/experiments/exp_hyperparameter_on_accuracy_alg_contrast.pdf}
+        \includegraphics[width=3.5in]{../figs/experiments/exp_hyperparameter_on_accuracy_alg_contrast.pdf}
         \caption{Best accuracy that each GNN achieved on different datasets.}
@@
     %
+    The sampling methods indeed affect the test accuracy of GNN models \cite{}.% 这里加几个sample方法的文献
+    %
+    Without sampling, the GNN models are trained in a \emph{batch} gradient descent manner.
+    %
+    With sampling, the GNN models are trained with \emph{mini-bach} stochastic gradient descent.
+    %
+    The structure of the GNN remains unchanged between batches.
+    %
+    Each GNN layer always consists of $|\mathcal{V}|$ graph neurons, where $|\mathcal{V}|$ is the number of vertices in the graph.
+    %
+    But the numbers of \emph{activated} graph neurons are different for different batches.
+    %
+    In each batch, only the neurons corresponding to the vertices appearing in the sampled subgraph will be activated.
+    %
+    The model parameters were updated according to the gradients calculated on the sampled subgraph in each batch.
+    %
+    Thus, the achieved model accuracy may be different from the full-graph training.
+
+    To discuss how the sampling methods affect model accuracy, we have added a new subsection Section 4.2.2 ``Effects on Accuracy'' in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
+    %
+    We quote the added content below.
+
+    \begin{myquote}{Section 4.4.2 ``Effects on Accuracy''}
+
+    Since the size of the sampled subgraph was much smaller than the original graph, the model accuracy got by sampling techniques might be different from the full-batch training.
+    %
+    To find out how the batch size affected the test accuracy, we trained GNNs with different batch sizes.
+    %
+    \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} (in the reply) and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} (in the reply) compare the test accuracy achieved by sampling techniques with the test accuracy of the full-batch training.
+    %
+    For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.
+
+    \begin{figure}[H]
+        \centering
+        \subfloat[\texttt{amp}]{\includegraphics[width=2in]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
+        \subfloat[\texttt{amc}]{\includegraphics[width=2in]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
+        \subfloat[\texttt{fli}]{\includegraphics[width=2in]{../figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
+        \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
+        \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
+    \end{figure}
+
+    \begin{figure}[H]
+        \centering
+        \subfloat[\texttt{amp}\label{fig:exp_cluster_sampling_accuracy_on_amp}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
+        %
+        \subfloat[\texttt{amc}\label{fig:exp_cluster_sampling_accuracy_on_amc}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
+        %
+        \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
+        \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
+        \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
+    \end{figure}
+
+    The experimental results confirmed the effectiveness of the sampling methods in terms of accuracy.
+    %
+    When the relative batch size was greater than or equal to 3\%, the test accuracy of the GNNs trained with sampling was close to the accuracy obtained by full-batch training.
+    %
+    In most cases, the accuracy achieved by the sampling techniques was slightly lower than the full-batch training.
+    %
+    However, there were some exceptions (like GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc} in the reply) that the accuracy achieved by sampling was even higher.
+
+    The relationships between batch size and test accuracy were complex.
+    %
+    A larger batch size did not always bring higher accuracy.
+    %
+    For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} (in the reply) and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} (in the reply) decreased as the batch size increased.
+    %
+    A smaller batch size sometimes could achieve higher accuracy.
+    %
+    For example, GAT achieved a higher accuracy with 1\% relative batch size than the full-batch training in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc} (in the reply).
+    %
+    Given a sampling method, we found that the optimal batch size highly depended on the dataset and the GNN algorithm.
+    %
+    Our observations were similar to [31].
+    %
+    How to automatically select a proper batch size is a topic worth further studying.
+
+    Among the two sampling methods, the performance of the cluster sampler was stabler than the neighbor sampler.
+    %
+    With the cluster sampler, the test accuracy of different GNNs was very close to the accuracy of full-batch training.
+    %
+    With the neighbor sampler, the test accuracy of different GNNs showed more obvious differences.
+    \end{myquote}
 
@@
 
+    We are grateful for your insightful suggestion.
+    %
+    As suggested, we additionally evaluated the effects of model complexity on accuracy in Section 4.1 ``Effects of Hyper-parameters on Performance'' in the revised manuscript.
+    %
+    We added experimental results on how the hyper-parameters of GNNs affected the accuracy.
+    %
+    Since different GNNs had different model complexity, we further compared the test accuracy of different GNNs on the same dataset.
+    %
+    More details are available in the reply to Reviewer Point P2.4.
+
+    We also additionally evaluated the effects of sampling techniques on accuracy in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
+    %
+    We presented the experimental results in a new subsection Section 4.4.2 ``Effects on Accuracy''.
+    %
+    More details are available in the reply to Reviewer Point P2.5.
 \end{reply}

### 2020-12-25 NEUROC/Response-MajRev/response_letter.tex
response_letter添加了论文引用
更新了论文引用的问题

@@
     %
-    It was also close to the accuracy reported in their original references [1][4][6][7].
+    It was also close to the accuracy reported in their original references [34, 31].
     %
@@
     %
-    The sampling methods indeed affect the test accuracy of GNN models \cite{}.% 这里加几个sample方法的文献
+    The sampling methods indeed affect the test accuracy of GNN models [5, 28, 26, 31].% 这里加几个sample方法的文献
     %

### 2020-12-25 NEUROC/sec4-experiments.tex
更新R1P6
更新了论文引用的问题

@@
 %
-It was also close to the accuracy reported in their original references \cite{kipf2017_gcn,li2015_ggnn,huang2018_gat,zhang2018_gaan}.
+It was also close to the accuracy reported in their original references \cite{shchur2018_pitfall_of_gnn, zeng2020_graphsaint}.
 %
@@
 %
-The \texttt{thnn\_fused\_gru\_cell} operator was used in the backward phase of $\gamma$.
+The \texttt{thnn\_fused\_gru\_cell} operator was used in both the forward and backward phases of $\gamma$.
 %

### 2020-12-25 NEUROC/sec3-experiment-design.tex
update
更新Reviewer2

@@
 
+\paragraph{Learning Task}
+We used the node classification as the target task in GNNs due to its popularity in real-world applications.
+We trained GNNs in the semi-supervised learning setting.
+All vertices and their input feature vectors were used, but only a part of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
+The vertices with unseen labels were used in the evaluation phase to evaluate the accuracy of the current parameters.
+%Since model parameters of GNNs were not restricted by the topological structure of $\mathcal{G}$, the model learned from the semi-supervised learning can directly extrapolate to unseen vertices.
+
 \paragraph{Datasets}
@@
 %
-For the \texttt{cam} dataset, we generated random dense feature vectors for it.
+For the \texttt{cam} dataset, its vertices were not associated with feature vectors.
 %
-Since its vertices were not associated with feature vectors, we excluded it from accuracy evaluation.
+Thus, we generated random dense feature vectors for it and excluded it from accuracy evaluation.
+%
+For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the samples as the training/evaluation/test set, respectively.
+%
+For \texttt{pub}, we used 500/1000 vertices as the evaluation/test set and the remained as the training set according to \cite{chen2018_fastgcn}.
+%
+For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to \cite{zeng2020_graphsaint}.
 %
@@
 Vertices of random graphs were classified into 10 classes randomly.
-%
-For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the samples as the training/evaluation/test set, respectively.
-%
-For \texttt{pub}, we used 500/1000 vertices as the evaluation/test set and the remained as the training set according to \cite{chen2018_fastgcn}.
-%
-For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to \cite{zeng2020_graphsaint}.
 
@@
 \end{table}
-
-\paragraph{Learning Task}
-We used the node classification as the target task in GNNs due to its popularity in real-world applications.
-We trained GNNs in the semi-supervised learning setting.
-All vertices and their input feature vectors were used, but only a part of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
-The vertices with unseen labels were used in the evaluation phase to evaluate the accuracy of the current parameters.
-%Since model parameters of GNNs were not restricted by the topological structure of $\mathcal{G}$, the model learned from the semi-supervised learning can directly extrapolate to unseen vertices.
 
@@
 %
-The accuracy on the test set was evaluated with the final model.
+The accuracy of the test set was evaluated with the final model.
 

### 2020-12-25 NEUROC/sec3-experiment-design.tex
sec3修改数据集的问题, sec4修改了inference分析的问题

--- 2020-12-25 NEUROC/sec3-experiment-design.tex
@@
 
-We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervised, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
+We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{chen2018_fastgcn, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
 %
@@
         \midrule
-        pubmed (\texttt{pub}) \cite{yang2016_revisiting_semisupervised}  & 19,717          & 44,324          & 4.5       & 500                   & 3       & Yes      \\
+        pubmed (\texttt{pub}) \cite{chen2018_fastgcn}  & 19,717          & 44,324          & 4.5       & 500                   & 3       & Yes      \\
         amazon-photo (\texttt{amp}) \cite{shchur2018_pitfall_of_gnn}     & 7,650           & 119,081         & 31.1      & 745                   & 8       & Yes      \\

### 2020-12-25 NEUROC/sec4-experiments.tex
更新Reviewer2
sec3修改数据集的问题, sec4修改了inference分析的问题

@@
 %
-The collection step copies the hidden vectors from the previous GNN layer $\MyVec{h}^l_x$ and $\MyVec{h}^l_y$ to the both endpoints of each edge $e_{x,y}$ in the edge index, forming the parameter tensor $[\MyVec{h}^l_x, \MyVec{h}^l_{y}, \MyVec{e}_{x,y}]$ of the messaging function $\phi^l$.
+The collection step copies the hidden vectors from the previous GNN layer $\MyVec{h}^l_y$ and $\MyVec{h}^l_x$ to the both endpoints of each edge $e_{y,x}$ in the edge index, forming the parameter tensor $[\MyVec{h}^l_{y}, \MyVec{h}^l_{x}, \MyVec{e}_{y,x}]$ of the messaging function $\phi^l$.
 %
@@
 %
-The messaging step calls the messaging function $\phi^l$ on all edges to get message vectors $\MyVec{m}^l_{x,y}$.
+The messaging step calls the messaging function $\phi^l$ on all edges to get message vectors $\MyVec{m}^l_{y,x}$.
 %
@@
 %
-The results of layer level experiment, step Level in edge Calculation experiment and operator Level experiment were in general consistent with those in the Training stage.
+The results of layer level experiment, step Level in edge calculation experiment and operator Level experiment were in general consistent with those in the Training stage.
 %
@@
     \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_usage_stage_amp.pdf}
-    \caption{Memory usage of each phase during the GNN training. Dataset: \texttt{amp}.}
+    \caption{Memory usage of each phase during the GNN inference. Dataset: \texttt{amp}.}
     \label{fig:exp_inference_full_memory_usage_stage_amp}
@@
     \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_expansion_ratio_input_feature_dimension_com-amazon_expansion_ratio.pdf}
-    \caption{Memory expansion ratio under different dimensions of input feature vectors. Dataset: \texttt{cam}.}
+    \caption{Memory expansion ratio under different dimensions of input feature vectors during inference. Dataset: \texttt{cam}.}
     \label{fig:exp_inference_full_memory_expension_ratio_input_feature_dimension}

### 2020-12-25 NEUROC/sec3-experiment-design.tex
更正了数据集引用的问题

@@
 
-We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{chen2018_fastgcn, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
+We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{chen2018_fastgcn, zeng2020_graphsaint, shchur2018_pitfall_of_gnn, yang2012_defining}.
 %

### 2020-12-25 NEUROC/Response-MajRev/response_letter.tex
更新Reviewer2

@@
 \usepackage{framed}
-\usepackage[colorlinks=true]{hyperref}
+\usepackage{soul}
+\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
 % Vector
@@
 \begin{reply}
-    Thank you for your positive comments on our manuscript.
+    Thank you for your kindly comments on our manuscript.
     %
-    We have carefully revised the manuscript according to your comments. 
+    We have carefully revised the manuscript according to your suggestions. 
     %
-    Based on the suggestions, we have made an extensive modification on the revised manuscript.
+    Please see the replies below.
     %
-    Please see the detailed responses below.
-    %
-    The changes corresponding to each issue were highlighted by red squares in the annotated version of our manuscript.
+    The changes corresponding to each point are highlighted by red squares in the annotated version of our revised manuscript.
 
@@
     %
-    We have carefully revised the manuscript according to your comments.
+    We have carefully revised the manuscript according to your kindly comments and suggestions in the following points.
     %
-    We have revised our manuscript according to your kindly suggestions.
-    %
-    Please see the detailed responses below.
-    %
-    We have highlighted our modification point by point in the annotated version of the manuscript by red squares.
+    We highlight our modifications with red squares point by point in the annotated version of the revised manuscript.
 \end{reply}
@@
 \begin{reply}
-    Thank you for pointing them out.
-    %
     We feel really sorry for our carelessness.
     %
-    We have proofread our revised manuscript carefully to eliminate such language errors as much as we can.
+    We have proofread our revised manuscript to eliminate such language errors as much as we can.
 \end{reply}
@@
     %
-    The model complexity directly affected both the accuracy and the training time.
+    The model complexity directly affects both the accuracy and the training time.
     %
-    In order to analyze the relationship between model complexity and accuracy, we conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affected the accuracy of GNNs (in Section 4.1); (2) how the batch size in the sampling methods affected the accuracy of GNNs (in Section 4.4).
+    In order to analyze the relationship between model complexity and accuracy, we have conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affect the accuracy of GNNs (in Section 4.1); (2) how the batch size in the sampling methods affects the accuracy of GNNs (in Section 4.4).
 
-    In this reply, we focus on the first kind of experiments added in Section 4.1.
+    We have added more dataset description related to accuracy evaluation in Section 3.1 ``Experimental Setting''.
     %
-    We will introduce our results of the second kind of experiments in the next reply.
+    Newly added sentences are marked with underlines in the following quotation.
 
-    Hyper-parameters determined the model complexity of a GNN.
+    \begin{myquote}{Section 3.1 ``Experimental Setting''}
+    \emph{Datasets}.
     %
-    Generally speaking, higher values of hyper-parameters brought higher model complexity, affecting model accuracy.
+    We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} (in the reply) that were popular in the GNN evaluation [28,31,34,36].
     %
-    In the revised manuscript, we added extra paragraphs ``Effects on Accuracy'' at the end of Section 4.1 ``Effects of Hyper-parameters on Performance'' to analyze how the hyper-parameters affect the accuracy.
+    For directed graphs, PyG converts them into undirected ones during data loading.
     %
-    We had two main findings.
+    Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
     %
-    First, the accuracy of GNNs was much more sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$ (for GCN/GGNN/GaAN) and the dimension of each head $d_{head}$ (for GAT) than the other hyper-parameters.
+    For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
     %
-    Second, the relative accuracy between the four typical GNNs varied greatly with different datasets.
+    \ul{For the \texttt{cam} dataset, its vertices were not associated with feature vectors}.
     %
-    We quote the related paragraphs from the revised manuscript below.
+    \ul{Thus, we generated random dense feature vectors for it and excluded it from accuracy evaluation}.
+    %
+    \ul{For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the vertices as the training/evaluation/test set, respectively}.
+    %
+    \ul{For \texttt{pub}, we used 500/1000 vertices as the evaluation/test set and the remained as the training set according to [28]}.
+    %
+    \ul{For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to [31]}.
+    %
+    We also used random graphs generated by the R-MAT graph generator [35] in some experiments, to explore the effects of graph topological characteristics (like average degrees) on performance bottlenecks.
+    %
+    Input feature vectors of random graphs were random dense vectors with the dimension of 32.
+    %
+    Vertices of random graphs were classified into 10 classes randomly.
 
-    \begin{myquote}{Section 4.1 ``Effects of Hyper-parameters on Performance''}
+    \begin{table}[H]
+        \centering
+        \begin{tabular}{cccccccc}
+            \toprule
+            Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $dim(\boldsymbol{v})$ & \#Class & Directed \\
+            \midrule
+            pubmed (\texttt{pub}) [28]  & 19,717          & 44,324          & 4.5       & 500                   & 3       & Yes      \\
+            amazon-photo (\texttt{amp}) [34]     & 7,650           & 119,081         & 31.1      & 745                   & 8       & Yes      \\
+            amazon-computers (\texttt{amc}) [34] & 13,752          & 245,861         & 35.8      & 767                   & 10      & Yes      \\
+            coauthor-physics (\texttt{cph}) [34] & 34,493          & 247,962         & 14.4      & 8415                  & 5       & Yes      \\
+            flickr (\texttt{fli}) [31]                 & 89,250          & 899,756         & 10.1      & 500                   & 7       & No       \\
+            com-amazon (\texttt{cam}) [36]               & 334,863         & 925,872         & 2.8       & 32                    & 10      & No       \\
+            \bottomrule
+        \end{tabular}
+        \caption{Dataset overview. $\bar{d}$ represents the average vertex degree. $dim(\boldsymbol{v})$ is the dimension of the input feature vector.}
+        \label{tab:dataset_overview}
+    \end{table}
+
+    \end{myquote}
+
+    In this reply, we focus on the experiments related to hyper-parameters in Section 4.1.
     %
-    \emph{Effects on Accuracy}.
+    We introduce the experimental results of the sampling techniques in Section 4.4 in the next reply.
+
+    Hyper-parameters determine the model complexity of a GNN.
     %
-    The relationship between hyper-parameters of GNNs (i.e., model complexity) and accuracy is very complicated, and there is no clear theoretical analysis yet.
+    Generally speaking, higher values of hyper-parameters bring higher model complexity and increase representation capability.
     %
-    Generally speaking, higher model complexity can bring powerful representation capability and may bring higher accuracy, but it also increases the risk of overfitting.
+    In the revised manuscript, we add a new subsection Section 4.1.4 ``Effects on Accuracy'' at the end of Section 4.1 ``Effects of Hyper-parameters on Performance'' to analyze how hyper-parameters affect the accuracy.
     %
-    To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the four typical GNNs under different hyper-parameters.
+    We have two main findings.
     %
-    \figurename~\ref{fig:exp_hyperparameter_accuracy} shows the experimental results.
+    First, the accuracy of GNNs is much more sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$ (for GCN/GGNN/GaAN) and the dimension of each head $d_{head}$ (for GAT) than the other hyper-parameters.
+    %
+    Second, the relative accuracy of the four typical GNNs varies greatly with different datasets.
+    %
+    We quote from Section 4.1.4 of the revised manuscript to present our results.
 
-    For GCN, the accuracy was sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$.
+    \begin{myquote}{Section 4.1.4 ``Effects on Accuracy''}
+    %
+    The values of hyper-parameters determined the model complexity of a GNN.
+    %
+    The relationship between model complexity and accuracy was complex.
+    %
+    %As far as we know, there is little theoretical analysis yet.
+    %
+    Generally speaking, higher model complexity brought more powerful representation capability and might bring higher accuracy, but it also increased the risk of overfitting.
+
+    To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the typical GNNs with varying hyper-parameters.
+    %
+    \figurename~\ref{fig:exp_hyperparameter_accuracy} (in the reply) shows the experimental results.
+    %
+    For GCN, its accuracy was sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$.
     %
@@
     %
-    For GGNN, its accuracy curves showed similar trends as GCN.
-    %
-    However, GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN.
+    For GGNN, its accuracy curves showed similar trends as GCN, but GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN.
     %
@@
     %
-    The experimental results indicated the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was small.
+    The experimental results indicated that the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was too low.
     %
-    In those cases, the low model complexity limited the expressive power of the GNNs.
+    %The low model complexity limited the representation capability of the GNNs.
     %
-    As $dim(\MyVec{h}_x^1)$ or $d_{head}$ increased to a certain threshold, the GNNs had sufficient learning ability to achieve stable accuracy.
+    As $dim(\MyVec{h}_x^1)$ or $d_{head}$ increased to a certain threshold, the GNNs gained sufficient learning ability to achieve stable accuracy.
 
@@
 
-    \figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} compares the best accuracy that each GNN achieved on different datasets.
+    \figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} (in the reply) further compares the best accuracy that each GNN could achieve on different datasets.
     %
-    The best accuracy that the four GNNs achieved was very close.
+    The best accuracy of the typical GNNs was very close.
+    %
     %
@@
     %
-    There was no clear winner in terms of accuracy.
+    The results indicated that there was no clear winner.
     %
@@
     %
-    GCN also achieved the highest or second highest accuracy in three out of five datasets, though its model was simplest.
+    GCN achieved the highest or second highest accuracy in three out of five datasets, though its model was simplest.
     %
-    It indicated that simple GNN models (such as GCN) could still achieve good accuracy with proper hyper-parameter settings.
+    Simple GNN models (such as GCN) could still achieve good accuracy with proper hyper-parameter settings.
 
@@
 
-    Thank you for your insightful comment and valuable suggestion.
+    Thanks for the insightful comment and valuable suggestion.
     %
-    The sampling methods indeed affect the test accuracy of GNN models [5, 28, 26, 31].% 这里加几个sample方法的文献
+    The sampling methods indeed affect the test accuracy of GNN models [5, 28, 26, 31].
     %
-    Without sampling, the GNN models are trained in a \emph{batch} gradient descent manner.
+    Without sampling, the GNN models are trained with a \emph{batch} gradient descent manner.
     %
@@
     %
-    The model parameters were updated according to the gradients calculated on the sampled subgraph in each batch.
+    The model parameters are updated according to the gradients calculated on the sampled subgraph in each batch.
     %
-    Thus, the achieved model accuracy may be different from the full-graph training.
+    Thus, the test accuracy of the models trained with sampling techniques may be different from the full-graph training.
 
-    To discuss how the sampling methods affect model accuracy, we have added a new subsection Section 4.2.2 ``Effects on Accuracy'' in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
+    To discuss how the sampling techniques affect model accuracy, we have added a new subsection Section 4.2.2 ``Effects on Accuracy'' in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
     %
-    We quote the added content below.
+    We quote from Section 4.4.2 of the revised manuscript to present our results.
 
@@
 
-    Since the size of the sampled subgraph was much smaller than the original graph, the model accuracy got by sampling techniques might be different from the full-batch training.
+    Since the size of the sampled subgraph was much smaller than the original graph, the accuracy of the GNN models got by sampling techniques might be different from the full-batch training.
     %
@@
     %
-    For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.
+    For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.
 

### 2020-12-25 NEUROC/sec2-review-of-graph-neural-network.tex
新增精简版的response letter.
更新了inference介绍和Inference阶段的时间性能瓶颈分析

@@
 
-The model parameters of a GNN are stored in the weight vectors/matrices of the prediction layer and the messaging/aggregation/updating functions of each GNN layer.
+The model parameters of a GNN consist of the weight vectors/matrices in the prediction layer and the messaging/aggregation/updating functions of each GNN layer.
 %
-When we want to perform inference on a new graph based on a trained GNN, the structure of the GNN needs to be adjusted, but the hyper-parameters and the model parameters of the GNN remain unchanged.
+For transductive learning, the input graphs of training and inference are same.
+%
+The structure of the GNN does not need to adjust. 
+%
+For inductive learning, the input graphs used in training and inference are different.
+%
+When we want to perform inference on a new graph with a pre-trained GNN, the structure of the GNN needs to be adjusted, but the hyper-parameters and the model parameters of the GNN remain unchanged.
 %
@@
 %
-The connections of graph neurons between GNN layers also needs to be adjusted according to the edge set of the new graph.
+The connections of graph neurons between GNN layers are also adjusted according to the edge set of the new graph.
+%
+During inference, input feature vectors of the input graph are propagated forward from the input layer to the prediction layer to give out predicted labels.
 
-During inference, input feature vectors of the new graph are propagated forward from the input layer to the prediction layer to give out predicted labels.
+When the memory capacity of the GPU is large enough to hold all of the input graph and intermediate results during inference, the inference can produce predicted labels for all vertices and edges at once, making full use of the computing power of the GPU.
 %
-The workflow of inference is the same as the workflow of the \emph{forward} phase during training.
+When the memory capacity is not large enough, the sampling technique must be adopted.
+
+The sample-based inference splits the test set into several batches.
 %
-The only difference from the forward phase is that there is no need to cache intermediate calculation results during inference, because inference does not need to prepare for gradient calculation.
-
-Inference methods can be divided into two types based on the range of input graphs involved in inference: full-batch inference and sample-based inference.
+For each batch, the sample-based inference samples a subgraph related to the batch from the input graph.
 %
-The full-batch inference performs inference on the whole input graph at once.
+It performs inference on the sampled subgraph to produce predicted labels for the batch.
 %
-It can make full use of the computing power of GPUs, bringing high computation efficiency.
-%
-The full-batch inference is suitable for small graphs that the GPU memory can hold all feature vectors, models, and intermediate results.
-
-Different from the full-batch inference, the sample-based inference only predicts labels for part of vertices/edges each time, limiting the GPU memory usage during inference.
-%
-It first samples a subgraph related to inference from the input graph and then performs the full-batch inference on the sampled subgraph.
+Since the sampled subgraph is usually much smaller than the original input graph, the memory usage during inference is limited.
 %
@@
 %
-Taking the node classification scenario as an example, if there are $L$ GNN layers in the GNN, the hidden vector outputted by the last GNN layer of each vertex $\MyVec{h}^L_x$ is only related to the $L$-hop neighborhood of $v_x$.
+Taking the node classification task as an example, if there are $L$ GNN layers in the GNN, the hidden vector outputted by the last GNN layer of each vertex $\MyVec{h}^L_x$ is only related to the $L$-hop neighborhood of $v_x$.
 %
 Thus, if we want to predict labels for a group of vertices, we only need to sample a subgraph that contains $L$-hop neighborhoods of all given vertices.
+
+The implementation of sample-based inference in PyG stores the whole input graph and its feature vectors in the main memory.
 %
-The sample-based inference is suitable for processing big graphs.
+In the node classification task, it splits the vertices in the test set into batches accoding to a given batch size.
 %
-It stores the whole input graph and its feature vectors in the main memory.
+The subgraph corresponding to each batch is sampled on the CPU side and sent to the GPU side to perform inference.
 %
-It processes the whole graph in batches.
-%
-The subgraph of each batch is sampled on the CPU side and sent to the GPU side to perform inference.
-%
-By using small batch sizes, the peak memory usage during inference can be limited under the GPU memory capacity.
-%
-The sample-based inference is also suitable for the online inference scenario that the topology of the graph evolves over time.
-%
-When a graph update arrives, the subgraph affected by the update is sampled and inferences are only performed on the sampled subgraph.it.
-that are affected by , avoiding conducting repeated inferences for the whole graph.

### 2020-12-25 NEUROC/sec4-experiments.tex
更新了inference介绍和Inference阶段的时间性能瓶颈分析

@@
 
-\paragraph{Effects on Training Time}
+\subsubsection{Effects on Training Time}
 
@@
 
-\paragraph{Effects on Inference Time}
+\subsubsection{Effects on Inference Time}
 
@@
 
-\paragraph{Effects on Peak Memory Usage}
+\subsubsection{Effects on Peak Memory Usage}
 
@@
 
-\paragraph{Effects on Accuracy}
+\subsubsection{Effects on Accuracy}
 
@@
 
-\subsection{Training Time Breakdown}
+\subsection{Training/Inference Time Breakdown}
 \label{sec:training_time_breakdown}
@@
 
-% added by wangyunpan, 2020-12-22 ----start----
-\paragraph{Inference Time Breakdown Analysis}
-We conducted the same experiments in the inference stage as above.
+\subsubsection{Performance Bottlenecks in Inference}
 %
-The results of layer level experiment, step Level in edge calculation experiment and operator Level experiment were in general consistent with those in the Training stage.
+We also did all the above experiments for Inference.
 %
-The performance bottleneck analysis in the Training stage can also be applied to the inference stage.
-% added by wangyunpan, 2020-12-22 ----end----
+We found that the performance characteristics of GNN inference were highly similar to training on the \emph{layer} level and the \emph{step} level.
+%
+Here, we used GCN as an example. 
+%
+We made similar observations for all GNNs. 
+%
+\figurename~\ref{fig:inference_analysis_on_layer_edge_level_of_gcn} shows the results of GCN inference on the \emph{layer} level and the \emph{step} level.
+%
+Compared to the training time breakdown of GCN \figurename~\ref{fig:exp_vertex_edge_cal_proportion}(a), 
+\figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}(a), and \figurename~\ref{fig:exp_edge_calc_decomposition}(a),
+we could conclude that the time breakdowns were very similar.
+
+% GCN Inference结果对比图
+\begin{figure}[H]
+    \centering
+    \subfloat[\emph{layer} level]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+    \subfloat[the effect of average degree]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+    \subfloat[\emph{edge} level]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
+    \caption{Time breakdowns on the layer level and edge level, and the effect of average degree on the edge/vertex calculation of GCN Inference.}
+    \label{fig:inference_analysis_on_layer_edge_level_of_gcn}
+\end{figure}
+
+% 绝对时间对比图
+\begin{figure}[H]
+    \centering
+    \subfloat[\texttt{amc}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_amazon-computers.pdf}}
+    \subfloat[\texttt{amp}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_amazon-photo.pdf}}
+    \subfloat[\texttt{fli}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
+    \caption{Wall-clock training/inference time on different datasets.}
+    \label{fig:compare_wall_clock_time_of_training_and_inference}
+\end{figure}
+
+The main differences between training and inference were reflected in two aspects: the wall-clock time and the top time-consuming basic operators.
+%
+The inference time was much less than the training time.
+%
+Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} in the response (Figure X in the revised manuscript) compares the wall-clock time of training and inference on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
+%
+The results on the other datasets were similar.
+%
+Since the inference only conducted the forward propagation from the input layer to the prediction layer, the time of inference was very close to the time of the forward phase in training.
+%
+The inference time was 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time, averaged over all datasets.
+
+The top time-consuming basic operators of training and inference also showed a certain degree of difference.
+%
+Some of the top time-consuming operators during training were replaced by new operators in inference.
+%
+Figure~\ref{fig:exp_inference_top_basic_ops} in the response compares the top 5 time-consuming basic operators in inference.
+%
+For GCN, the \texttt{index} operator used in the prediction layer became the new top 5 time-consuming operator, replacing the \texttt{gather} operator used in the backward phase in training.
+%
+%    The basic operators related to the edge calculation (\texttt{scatter\_add}, \texttt{index\_select}, and \texttt{mul}) still consumed the majority of the inference time.
+%
+For GGNN, \texttt{index} operator in the prediction layer also became one of the top 5 time-consuming basic operators.
+%
+%    Due to the high time complexity of the vertex updating function $\gamma$ in GGNN, the basic operators related to the vertex calculation stage (\texttt{mm} and \texttt{thnn\_fused\_gru\_cell}) still consumed near half of the inference time.
+%
+For GAT, the \texttt{input\_put\_impl} operator (used in the backward phase) in Figure~\ref{fig:exp_top_basic_ops}(c) was replaced by the \texttt{scatter\_add} operator used in the forward edge calculation in Figure~\ref{fig:exp_inference_top_basic_ops}(c).
+%
+%    The \texttt{scatter\_add} operator was related to the edge calculation step.
+%
+For GaAN, the \texttt{mm} operator was replaced by the \texttt{cat} operator used in the vertex updating function.
+
+Although some specific time-consuming operators were different, the performance bottlenecks on the operator level were same for training and inference.
+%
+The matrix multiplication \texttt{mm} and the element-wise multiplication \texttt{mul} operators were still time-consuming for inference, making GNN inference also {suitable for GPUs}.
+%
+The basic operators related to the collection and aggregation steps in the edge calculation still consumed non-trivial time in inference.
+
+\begin{figure}[H]
+    \centering
+    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_inference_full_top_basic_ops_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_inference_full_top_basic_ops_gat.pdf}}
+    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_inference_full_top_basic_ops_gaan.pdf}}
+    \caption{Top 5 time-consuming basic operators of typical GNNs. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
+    \label{fig:exp_inference_top_basic_ops}
+\end{figure}
 

### 2020-12-25 NEUROC/sec4-experiments.tex
section4.3增加了Memory Usage of Inference, 增加了Section4.4.4 Performance Bottleneck in Inference

@@
 
-% added by wangyunpan, 2020-12-22 ----start----
-\paragraph{Inference Stage Memory Usage Analysis}
+\subsubsection{Memory Usage of Inference}
 
-% 不同点: phase
+Figure~\ref{fig:exp_inference_memory_expansion_ratio} shows the memory expansion ratios of typical GNNs during inference.
+%
+Since no intermediate results had to be cached during inference of GGNN, GAT, and GaAN,
+the memory expansion ratios of inference were much less than training for the three GNNs (\figurename~\ref{fig:exp_memory_expansion_ratio}).
+%
+The MERs of inference were 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training.
+%
+However, the MERs were still high, disallowing inferencing with big graphs.
+%
+To handle big graphs, sample-based inference was necessary.
+
 \begin{figure}[H]
    \centering
-    \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_usage_stage_amp.pdf}
-    \caption{Memory usage of each phase during the GNN inference. Dataset: \texttt{amp}.}
-    \label{fig:exp_inference_full_memory_usage_stage_amp}
+   \subfloat{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}}
+   \caption{Memory expansion ratios of typical GNNs in Inference.}
+   \label{fig:exp_inference_memory_expansion_ratio}
 \end{figure}
-
-% 不同点： 膨胀比例
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}
-    \caption{Memory expansion ratios of typical GNNs.}
-    \label{fig:exp_inference_full_memory_expansion_ratio}
-\end{figure}
-
-% 不同点: input feature dims
-\begin{figure}[H]
-    \centering
-    \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_expansion_ratio_input_feature_dimension_com-amazon_expansion_ratio.pdf}
-    \caption{Memory expansion ratio under different dimensions of input feature vectors during inference. Dataset: \texttt{cam}.}
-    \label{fig:exp_inference_full_memory_expension_ratio_input_feature_dimension}
-\end{figure}
-
-For the inference stage, we did the same experiment as above. The experimental results were as follows:
-%
-\figurename~\ref{fig:exp_inference_full_memory_usage_stage_amp} shows the peak memory usage of each phase during inference stage.  
-%
-Compared with the results of training stage in \figurename~\ref{fig:exp_memory_usage_stage_amp}, the peak memory usage of inference stage was significantly lower.
-%
-This was because the inference stage didn't require backward propagation and the peak memory was only determined by the temporary variables generated during the computation.
-%
-
-\figurename~\ref{fig:exp_inference_full_memory_expansion_ratio} compares MER of different GNNs on inference stage. 
-%
-We found that The performance of GNNs on all datasets was consistent with the training stage in \figurename~\ref{fig:exp_memory_expansion_ratio}, but the corresponding values were lower.
-%
-
-%
-% added by wangyunpan, 2020-12-22 ----end----
 
@@
 The time spent on the sampling phase and the data transferring phase even exceeded the training phase.
+
+\subsubsection{Performance Bottlenecks in Inference}
+
+Sample-based inference was an effective technique to handle big graphs.
+%
+Taking the node classification task as an example, to predict labels for a given set of vertices $\mathcal{V}_{predict}$, the inference sampler sampled a subgraph containing complete $L$-hop neighborhoods of all vertices in $\mathcal{V}_{predict}$, where $L$ was the number of GNN layers.
+%
+Since the real-world graphs often had small-world property, the size of the sampled subgraph increased quickly as the number of vertices in $\mathcal{V}_{predict}$ (i.e., batch size) increased.
+%
+Figure~\ref{fig:sampled_graph_size} (Figure X in the revised manuscript) shows how the relative batch size ($\frac{|\mathcal{V}_{predict}|}{|\mathcal{V}|}$) affected the average degree and the number of edges of the sampled subgraphs during inference.
+%
+When the relative batch size was 10\%, the number of edges in the sampled subgraphs were close to the number of edges in the whole graph in most datasets.
+%
+In order to limit the memory usage during inference, the batch size used should be very small.
+
+\begin{figure}[H]
+   \centering
+   \subfloat[Average degree]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_avg_degrees.pdf}}
+   \subfloat[Number of edges]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_edges.pdf}}
+
+   \caption{Characteristics of the sampled subgraphs produced by the inference sampler under different relative batch sizes.}
+   \label{fig:sampled_graph_size}
+\end{figure}
+
+However, the overheads brought by sampling and data transfering from CPU to GPU became obvious when the batch size was small.
+%
+Figure~\ref{fig:time_breakdown_of_inference_sampler} shows the time breakdowns of sample-based inference on different datasets.
+%
+On the \texttt{amp} and \texttt{cam} datasets, the sampling time even accounted for near half of the total inference time.
+%
+The results indicated that the current implementation of inference sampler in PyG was also inefficient.
+%
+Improving its efficiency could significantly reduce the inference time.
+
+\begin{figure}[H]
+   \centering
+   \subfloat[Batch Size = 1024]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_sampling_fix_batch_size_train_time_stack_1024.pdf}}
+   \subfloat[Batch Size = 2048]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_sampling_fix_batch_size_train_time_stack_2048.pdf}}
+   \caption{Inference time per batch breakdown under different batch sizes.}
+   \label{fig:time_breakdown_of_inference_sampler}
+\end{figure}

### 2020-12-25 NEUROC/Response-MajRev/response_letter-version2.tex

--- 2020-12-25 NEUROC/Response-MajRev/response_letter.tex
@@
 % General intro text goes here
-We thank the reviewers for their critical assessment and insightful comments of our work.
+We thank the reviewers for their critical assessment and insightful comments on our work.
 %
@@
 %
-We also prepare an \emph{annotated version} for our revised manuscript.
+%We also prepare an \emph{annotated version} for our revised manuscript.
 %
-In the annotated version, changes corresponding to each point are all highlighted by red squares.
+%In the annotated version, changes corresponding to each point are all highlighted by red squares.
 
@@
     %
-    We have carefully revised the manuscript according to your suggestions. 
+    We have revised the manuscript according to your suggestions. 
     %
     Please see the replies below.
-    %
-    The changes corresponding to each point are highlighted by red squares in the annotated version of our revised manuscript.
-
 \end{reply}
@@
     %
-    To clarify the symbol usage, we have checked our manuscript and unified the usage of symbol in the revised version.
+    To clarify the symbol usage, we have unified the usage of symbols in the revised manuscript.
     %
     After revision, each symbol only represents one meaning.
+
+    Specifically, we use $\boldsymbol{s}$ to represent aggregated vectors in graph neurons.
     %
-    We added Table 1 at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised version to summarize frequently-used symbols.
+    We use $\boldsymbol{s}^l_x$ to denote the aggregated vector of the graph neuron corresponding to the vertex $v_x$ in the GNN layer $l$.
     %
-    We quote the table below:
+    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents the aggregated vector of $v_x$ in the $i$-th sub-layer.
+    %
+    As for edges and their feature vectors, we use $e_{y,x}$ to represent an edge pointing from $v_y$ to $v_x$ and we use $\boldsymbol{e}_{y,x}$ to represent its feature vector.
+
+    In order to facilitate readers to quickly locate the meaning of  symbols, we have added Table~\ref{tab:symbols} at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised manuscript.
+
     \begin{table}[H]
         \footnotesize
+        \caption{Frequently-used Symbols}
+        \label{tab:symbols}
         \centering
@@
 
-    In the revised manuscript, we use $e_{y,x}$ to represent an edge and use $\boldsymbol{e}_{y,x}$ to represent its input feature vector.
-    %
-    %The input feature vectors of all edges are same for all GNN layers.
-    %
-    We use $\boldsymbol{s}$ to represent aggregated vectors outputted by the aggregation function $\Sigma$ in graph neurons.
-    %
-    For every vertex $v_x$, we use $\boldsymbol{s}^l_x$ to denote the aggregated vector in the graph neuron of $v_x$ in the GNN layer $l$.
-    %
-    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents the aggregated vector of $v_x$ in the $i$-th sub-layer.
-
-    To clarify the concept of \emph{sub-layers} in a GNN layer, we have added more description in the revised manuscript.
-    %
-    We first introduce the concept of sub-layer in Section 2.2 ``Graph Neuron and Message-passing Model'' as:
-    %
-    \begin{myquote}{Section 2.2 ``Graph Neuron and Message-passing Model''}
-        Some complex GNNs like GAT [6] and GaAN [7] use more than one message passing phase in each GNN layer.
-        %
-        We regard every message passing phase in a GNN layer as a \emph{sub-layer}.
-        %
-        We will give out more details on sub-layers when we introduce GAT.
-    \end{myquote}
-    %
-    We then use GAT as an example to elaborate on the concept of sub-layers in Section 2.3 ``Representative GNNs'' as:
-    %
-    \begin{myquote}{Section 2.3.3 ``GAT (Low Vertex \& High Edge Complexity)''}
-        \newcommand{\GATCalcWeight}{\exp(LeakyReLU(\Param{\MyVec{a}}^T[\hvec{y}^l[k] \parallel \hvec{x}^l[k]]))}
-        Each GAT layer consists of a vertex pre-processing phase and two sub-layers (i.e., message-passing phases).
-
-        The vertex pre-processing phase calculates the attention vector $\hat{\boldsymbol{h}}^{l}_{x}$ for every vertex $v_x$ by $\hvec{x}^l = \parallel_{k=1}^K \Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
-We denote the attention sub-vector generated by the $k$-th head as $\hvec{x}^l[k]=\Param{\MyMat{W}^l_{(k)}}\MyVec{h}^l_x$.
-
-        The first sub-layer of GAT (defined in Equation~\ref{eq:GAT-sub-layer-1}) uses the attention vectors to emit the attention weight vector $\boldsymbol{m}^{l,0}_{y,x}$ for every edge $e_{y,x}$ and aggregates the attention weight vectors for every vertex $v_x$ to get the weight sum vector $\MyVec{h}^{l,0}_x$.
-        %
-        \begin{equation}
-            \footnotesize
-            \label{eq:GAT-sub-layer-1}
-            \begin{aligned}
-                \MyVec{m}^{l,0}_{y,x} & = \phi^{l,0}(\MyVec{h}^l_y, \MyVec{h}^l_x, \MyVec{e}_{y,x}, \hvec{y}^l, \hvec{x}^l) = \parallel_{k=1}^{K}\GATCalcWeight, \\
-                \MyVec{s}^{l,0}_{x} &= {\Sigma}_{v_y \in \mathcal{N}(v_x)}{\MyVec{m}^{l,0}_{y,x}}, \\
-                \MyVec{h}^{l,0}_{x} &= \gamma^{l,0}(\MyVec{h}^l_x, \MyVec{s}^{l,0}_{x})  = \MyVec{s}^{l,0}_{x}.
-            \end{aligned}
-        \end{equation}
-        %
-        The second sub-layer of GAT (defined in Equation~\ref{eq:GAT-sub-layer-2}) uses the weight sum vectors to normalize the attention weights for every edge and aggregates the attention vectors $\boldsymbol{\hat{h}}^l_y$ with the normalized weights.
-        %
-        The aggregated attention vectors $\MyVec{s}^{l,1}_x$ are transformed by an activation function $\delta$ and are outputted as the hidden vectors of the current layer $\MyVec{h}^{l+1}_x$.
-        %
-        \begin{equation}
-            \footnotesize
-            \label{eq:GAT-sub-layer-2}
-            \begin{aligned}
-                \MyVec{m}^{l,1}_{y,x} &= \phi^{l,1}(\MyVec{h}^{l,0}_y, \MyVec{h}^{l,0}_x, \MyVec{e}_{y,x}, \hvec{y}^l, \hvec{x}^l) = \parallel_{k=1}^{K}\frac{\GATCalcWeight}{\MyVec{h}^{l,0}_x[k]}\hvec{y}^l[k], \\
-                \MyVec{s}^{l,1}_x &= {\Sigma}_{v_y \in \mathcal{N}(v_x)} \MyVec{m}^{l,1}_{y,x}, \\
-                \MyVec{h}^{l+1}_x = \MyVec{h}^{l,1}_x &= \gamma^{l,1}(\MyVec{h}^{l,0}, \MyVec{s}^{l,1}_x) = \delta(\MyVec{s}^{l,1}_x).
-            \end{aligned}
-        \end{equation}
-    \end{myquote}
 \end{reply}
@@
 We have added the mentioned references in Section 1 ``Introduction'' in the revised manuscript.
-We quote the related sentence below:
-    \begin{myquote}{Section 1 ``Introduction''}
-         The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks [8, 9, 10] (like node classification and link prediction) but also computer vision tasks (like human-object interaction [11], human parsing [12], and video object segmentation [13]).
-    \end{myquote}
 \end{reply}
@@
     %
-    We feel really sorry for our carelessness.
+    We feel sorry for our carelessness.
     %
-    We have proofread our revised manuscript carefully to eliminate grammar errors and typos.
+    We have proofread our revised manuscript to eliminate grammar errors and typos as much as we can.
     %
@@
     %
-    We use the past tense to describe experimental methods, results and what they indicate.
+    Specifically, we use the past tense to describe experimental methods, results and what they indicate.
     %
-    We only use the present tense in the sentences that FigureX/Table X are the subjects of the sentences.
+    We use the present tense in the sentences that FigureX or Table X is the subject of the sentences.
 
@@
 
-    As you suggested, we have adjusted all the figures (besides Figure 6 and Figure 7) in the revised manuscript to make sure that font sizes in figures are no less than the font size of figure captions.
+    As suggested, we have split Figure 6 and Figure 7 into five figures (Figure 6 to 10) in the revised manuscript to enlarge their subfigures.
     %
-    To make the figures more easy to read, we also split Figure 6 and Figure 7 into five figures (Figure 6 to 10) in the revised manuscript to enlarge the subfigures.
+    We have also adjusted font sizes in all figures (besides Figure 6 and Figure 7) to make sure that they are equal to or greater than the font size of figure captions.
 
@@
      \begin{figure}[H]
+%        \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{imagefile}}
+     \end{figure}
+
+     \begin{figure}[H]
         \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_memory_expansion_ratio.pdf}}
@@
     %
-    We highlight our modifications with red squares point by point in the annotated version of the revised manuscript.
+    %We highlight our modifications with red squares point by point in the annotated version of the revised manuscript.
 \end{reply}

### 2020-12-25 NEUROC/sec4-experiments.tex
section4.3 update
更新了Effects on Accuracy

@@
 
-The relationship between hyper-parameters of GNNs (i.e., model complexity) and accuracy is very complicated, and there is no clear theoretical analysis yet.
 %
-Generally speaking, higher model complexity can bring powerful representation capability and may bring higher accuracy, but it also increases the risk of overfitting.
+The values of hyper-parameters determined the model complexity of a GNN.
 %
-To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the four typical GNNs under different hyper-parameters.
+The relationship between model complexity and accuracy was complex.
 %
-\figurename~\ref{fig:exp_hyperparameter_accuracy} shows the experimental results.
+%As far as we know, there is little theoretical analysis yet.
+%
+Generally speaking, higher model complexity brought more powerful representation capability and might bring higher accuracy, but it also increased the risk of overfitting.
 
-For GCN, the accuracy was sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$.
+To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the typical GNNs with varying hyper-parameters.
+%
+\figurename~\ref{fig:exp_hyperparameter_accuracy} (in the reply) shows the experimental results.
+%
+For GCN, its accuracy was sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$.
 %
@@
 %
-For GGNN, its accuracy curves showed similar trends as GCN.
-%
-However, GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN.
+For GGNN, its accuracy curves showed similar trends as GCN, but GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN.
 %
@@
 %
-The experimental results indicated the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was small.
+The experimental results indicated that the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was too low.
 %
-In those cases, the low model complexity limited the expressive power of the GNNs.
+%The low model complexity limited the representation capability of the GNNs.
 %
-As $dim(\MyVec{h}_x^1)$ or $d_{head}$ increased to a certain threshold, the GNNs had sufficient learning ability to achieve stable accuracy.
+As $dim(\MyVec{h}_x^1)$ or $d_{head}$ increased to a certain threshold, the GNNs gained sufficient learning ability to achieve stable accuracy.
 
@@
 
-%\begin{figure}[H]
-    %\centering
-    %\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat_small_info.pdf}
-    %\caption{Effects of the number of heads on GAT ($d_{head}$=2,4)}
-    %\label{fig:exp_hyperparameter_accuracy_gat_small_info}
-%\end{figure}
-
-\figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} compares the best accuracy that each GNN achieved on different datasets.
+\figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} further compares the best accuracy that each GNN could achieve on different datasets.
 %
-The best accuracy that the four GNNs achieved was very close.
+The best accuracy of the typical GNNs was very close.
 %
-It was also close to the accuracy reported in their original references \cite{shchur2018_pitfall_of_gnn, zeng2020_graphsaint}.
 %
-There was no clear winner in terms of accuracy.
+It was also close to the accuracy reported in their original references [34, 31].
+%
+The results indicated that there was no clear winner.
 %
@@
 %
-GCN also achieved the highest or second highest accuracy in three out of five datasets, though its model was simplest.
+GCN achieved the highest or second highest accuracy in three out of five datasets, though its model was simplest.
 %
-It indicated that simple GNN models (such as GCN) could still achieve good accuracy with proper hyper-parameter settings.
+Simple GNN models (such as GCN) could still achieve good accuracy with proper hyper-parameter settings.
 
@@
 
-\subsubsection{Memory Usage of Inference}
+\paragraph{Memory Usage of Inference}
 
@@
 
-Since the size of sampled subgraph was much smaller than the original graph, it might affect the accuracy of the trained GNNs.
+Since the size of the sampled subgraph was much smaller than the original graph, the accuracy of the GNN models got by sampling techniques might be different from the full-batch training.
 %
-To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes.
+To find out how the batch size affected the test accuracy, we trained GNNs with different batch sizes.
 %
-\figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} compare their accuracy with the cases that we used the full graph participated in the training.
+\figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} (in the reply) and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} (in the reply) compare the test accuracy achieved by sampling techniques with the test accuracy of the full-batch training.
 %
-For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section~\ref{sec:effects_of_hyper-parameters_on_performance}.
+For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.
 
@@
 
-The experimental results confirmed the effectiveness of the sampling methods in terms of model accuracy.
+The experimental results confirmed the effectiveness of the sampling methods in terms of accuracy.
 %
-When the relative batch size was greater than or equal to 3\%, the accuracy of the model trained by sampling was close to the accuracy obtained by full-graph training.
+When the relative batch size was greater than or equal to 3\%, the test accuracy of the GNNs trained with sampling was close to the accuracy obtained by full-batch training.
 %
-In most cases, the accuracy achieved by the sampling methods was slightly lower than the full-graph training.
+In most cases, the accuracy achieved by the sampling techniques was slightly lower than the full-batch training.
 %
-However, there were some exceptions (like GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}), the accuracy achieved by sampling methods was even higher.
+However, there were some exceptions (like GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc} in the reply) that the accuracy achieved by sampling was even higher.
 
-The relationships between batch size and accuracy were complex.
+The relationships between batch size and test accuracy were complex.
 %
-A large batch size did not always bring high accuracy.
+A larger batch size did not always bring higher accuracy.
 %
-For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} decreased as the batch size increased.
+For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} (in the reply) and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} (in the reply) decreased as the batch size increased.
 %
-A small batch size sometimes could achieve higher accuracy.
+A smaller batch size sometimes could achieve higher accuracy.
 %
-For example, in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}, the accuracy of GAT under 1\% relative batch size was even higher than the accuracy of the full-graph training.
+For example, GAT achieved a higher accuracy with 1\% relative batch size than the full-batch training in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc} (in the reply).
 %
@@
 %
-Our observations were similar to \cite{zeng2020_graphsaint}.
+Our observations were similar to [31].
 %
-How to automatically select the proper batch size is a topic worth further studying.
+How to automatically select a proper batch size is a topic worth further studying.
 
@@
 %
-With the cluster sampler, the model accuracy of different GNNs was very close to the accuracy of full-graph training.
+With the cluster sampler, the test accuracy of different GNNs was very close to the accuracy of full-batch training.
 %
-With the neighbor sampler, the model accuracy of different GNNs showed more obvious differences.
+With the neighbor sampler, the test accuracy of different GNNs showed more obvious differences.
 

### 2020-12-25 NEUROC/sec4-experiments.tex
将4.4.2 Effects of Accuracy移动到了4.4的最后
删除了in this reply

@@
 %
-\figurename~\ref{fig:exp_hyperparameter_accuracy} (in the reply) shows the experimental results.
+\figurename~\ref{fig:exp_hyperparameter_accuracy} shows the experimental results.
 %
@@
 
-\subsubsection{Effects on Accuracy}
-
-Since the size of the sampled subgraph was much smaller than the original graph, the accuracy of the GNN models got by sampling techniques might be different from the full-batch training.
-%
-To find out how the batch size affected the test accuracy, we trained GNNs with different batch sizes.
-%
-\figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} (in the reply) and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} (in the reply) compare the test accuracy achieved by sampling techniques with the test accuracy of the full-batch training.
-%
-For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.
-
-\begin{figure}[H]
-    \centering
-    \subfloat[\texttt{amp}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
-    \subfloat[\texttt{amc}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
-    \subfloat[\texttt{fli}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
-    \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
-    \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \subfloat[\texttt{amp}\label{fig:exp_cluster_sampling_accuracy_on_amp}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
-    %
-    \subfloat[\texttt{amc}\label{fig:exp_cluster_sampling_accuracy_on_amc}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
-    %
-    \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
-    \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
-    \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
-\end{figure}
-
-The experimental results confirmed the effectiveness of the sampling methods in terms of accuracy.
-%
-When the relative batch size was greater than or equal to 3\%, the test accuracy of the GNNs trained with sampling was close to the accuracy obtained by full-batch training.
-%
-In most cases, the accuracy achieved by the sampling techniques was slightly lower than the full-batch training.
-%
-However, there were some exceptions (like GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc} in the reply) that the accuracy achieved by sampling was even higher.
-
-The relationships between batch size and test accuracy were complex.
-%
-A larger batch size did not always bring higher accuracy.
-%
-For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} (in the reply) and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} (in the reply) decreased as the batch size increased.
-%
-A smaller batch size sometimes could achieve higher accuracy.
-%
-For example, GAT achieved a higher accuracy with 1\% relative batch size than the full-batch training in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc} (in the reply).
-%
-Given a sampling method, we found that the optimal batch size highly depended on the dataset and the GNN algorithm.
-%
-Our observations were similar to [31].
-%
-How to automatically select a proper batch size is a topic worth further studying.
-
-Among the two sampling methods, the performance of the cluster sampler was stabler than the neighbor sampler.
-%
-With the cluster sampler, the test accuracy of different GNNs was very close to the accuracy of full-batch training.
-%
-With the neighbor sampler, the test accuracy of different GNNs showed more obvious differences.
-
 \subsubsection{Performance Bottlenecks Analysis}
@@
 \end{figure}
+
+\subsubsection{Effects on Accuracy}
+
+Since the size of the sampled subgraph was much smaller than the original graph, the accuracy of the GNN models got by sampling techniques might be different from the full-batch training.
+%
+To find out how the batch size affected the test accuracy, we trained GNNs with different batch sizes.
+%
+\figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} compare the test accuracy achieved by sampling techniques with the test accuracy of the full-batch training.
+%
+For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.
+
+\begin{figure}[H]
+    \centering
+    \subfloat[\texttt{amp}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
+    \subfloat[\texttt{amc}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
+    \subfloat[\texttt{fli}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
+    \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
+    \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \subfloat[\texttt{amp}\label{fig:exp_cluster_sampling_accuracy_on_amp}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
+    %
+    \subfloat[\texttt{amc}\label{fig:exp_cluster_sampling_accuracy_on_amc}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
+    %
+    \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
+    \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
+    \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
+\end{figure}
+
+The experimental results confirmed the effectiveness of the sampling methods in terms of accuracy.
+%
+When the relative batch size was greater than or equal to 3\%, the test accuracy of the GNNs trained with sampling was close to the accuracy obtained by full-batch training.
+%
+In most cases, the accuracy achieved by the sampling techniques was slightly lower than the full-batch training.
+%
+However, there were some exceptions (like GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}) that the accuracy achieved by sampling was even higher.
+
+The relationships between batch size and test accuracy were complex.
+%
+A larger batch size did not always bring higher accuracy.
+%
+For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} decreased as the batch size increased.
+%
+A smaller batch size sometimes could achieve higher accuracy.
+%
+For example, GAT achieved a higher accuracy with 1\% relative batch size than the full-batch training in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}.
+%
+Given a sampling method, we found that the optimal batch size highly depended on the dataset and the GNN algorithm.
+%
+Our observations were similar to [31].
+%
+How to automatically select a proper batch size is a topic worth further studying.
+
+Among the two sampling methods, the performance of the cluster sampler was stabler than the neighbor sampler.
+%
+With the cluster sampler, the test accuracy of different GNNs was very close to the accuracy of full-batch training.
+%
+With the neighbor sampler, the test accuracy of different GNNs showed more obvious differences.

### 2020-12-25 NEUROC/sec3-experiment-design.tex
sec3修改了问题部分,sec4修改了标题

@@
 
-    \item[Q3] \emph{Which consumes most of memory in GNN training?} (Section~\ref{sec:memory_usage_analysis})
+    \item[Q3] \emph{Which consumes most of memory in GNN training and inference?} (Section~\ref{sec:memory_usage_analysis})
 
@@
           %
-          We measured the peak memory usage during GNN training under different graph scales, input feature dimensions, and average degrees.
+          We measured the peak memory usage during GNN training/inference under different graph scales, input feature dimensions, and average degrees.
           %
@@
     \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training?
-Does the use of sampling techniques in training affect the model accuracy?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
+What is the performance bottleneck of sample-based inference?
+Does the use of sampling techniques in training affect the model accuracy?
+} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
 
@@
           %
+          % TODO: 补充Sample-based Inference的介绍
 

### 2020-12-25 NEUROC/sec4-experiments.tex
更改了[]的引用
sec3修改了问题部分,sec4修改了标题

@@
 
-We answer the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
+We answered the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
 %
@@
 %
-The dimension of $\MyVec{h}^1_x$ is determined as $dim(\boldsymbol{h}^1_x) = K d_{head}$.
+The dimension of $\MyVec{h}^1_x$ was determined as $dim(\boldsymbol{h}^1_x) = K d_{head}$.
 %
@@
 
-For GaAN, it is also based on the multi-head mechanism.
+For GaAN, it was also based on the multi-head mechanism.
 %
@@
 
-\paragraph{Summary of Memory Usage}
+\paragraph{Summary of Memory Usage in Training}
 %
@@
 
-The average degree of the sampled subgraph was \emph{much lower} than the average degree of the original graph, especially when the relative batch size is low.
+The average degree of the sampled subgraph was \emph{much lower} than the average degree of the original graph, especially when the relative batch size was low.
 %
@@
 
-\paragraph{Summary of Sampling Techniques}
+\paragraph{Summary of Sampling Techniques in Training}
 
@@
 %
-For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.
+For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.4.
 
@@
 %
-Our observations were similar to [31].
+Our observations were similar to \cite{zeng2020_graphsaint}.
 %

### 2020-12-26 NEUROC/sec4-experiments.tex
删除一个多余的空格
grammer过sec4.1的语法和图表

@@
 
-We answered the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
+We answer the four questions in Section~\ref{sec:experimental_scheme} one by one with experiments.
 %
@@
 
-According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexity of the messaging function $\phi^l$ and the updating function $\gamma^l$ are linear to each hyper-parameter separately.
+According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexity of the messaging function $\phi^l$ and the updating function $\gamma^l$ were linear to each hyper-parameter separately.
 %
-If we increase one of the hyper-parameters and fix the others, the training/inference time should increase linearly in theory.
+If we increased one of the hyper-parameters and fix the others, the training/inference time should increase linearly in theory.
 
@@
     \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}
-    \caption{Distribution of the wall-clock training time of 50 epoches on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
+    \caption{Distribution of the wall-clock training time of 50 epochs on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
     \label{fig:exp_absolute_training_time}
@@
 %
-According to the time complexity analysis, if we fixed other hyper-parameters but only increased $dim(\boldsymbol{h}^1_x)$, the computational costs of the GNN layer 0 and the GNN layer 1 should both increase linearly with $dim(\boldsymbol{h}^1_x)$, causing the training time of the whole GNN also increasing linearly.
+According to the time complexity analysis, if we fixed other hyper-parameters but only increased $dim(\boldsymbol{h}^1_x)$, the computational costs of the GNN layer 0 and the GNN layer 1 should both increase linearly with $dim(\boldsymbol{h}^1_x)$, causing the training time of the whole GNN also increased linearly.
 %
@@
 
-To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the typical GNNs with varying hyper-parameters.
+To evaluate the effects of hyper-parameters on the accuracy, we measured the accuracy of the typical GNNs with varying hyper-parameters.
 %
@@
     \subfloat[GaAN]{\includegraphics[width=0.9\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
-    \caption{Effects of hyper-parameters on accuracy of the typical GNNs.}
+    \caption{Effects of hyper-parameters on the accuracy of the typical GNNs.}
     \label{fig:exp_hyperparameter_accuracy}
@@
 %
-GCN achieved the highest or second highest accuracy in three out of five datasets, though its model was simplest.
+GCN achieved the highest or second-highest accuracy in three out of five datasets, though its model was simplest.
 %
@@
 %
-Improving its efficiency is the key to reduce the GNN training time.
+Improving its efficiency was the key to reduce the GNN training time.
 
@@
 %
-In the implementation of PyG, the edge calculation stage consists of four steps: collection, messaging, aggregation, and vector updating, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
+In the implementation of PyG, the edge calculation stage consisted of four steps: collection, messaging, aggregation, and vector updating, as shown in \figurename~\ref{fig:steps_in_edge_calculation}.
 %
-The edge index is a matrix with $|\mathcal{E}|$ rows and two columns.
+The edge index was a matrix with $|\mathcal{E}|$ rows and two columns.
 %
-It holds the edge set of the graph.
+It holded the edge set of the graph.
 %
-The two columns of the edge index store the source and the target vertex IDs of each edge.
+The two columns of the edge index stored the source and the target vertex IDs of each edge.
 %
-The collection step copies the hidden vectors from the previous GNN layer $\MyVec{h}^l_y$ and $\MyVec{h}^l_x$ to the both endpoints of each edge $e_{y,x}$ in the edge index, forming the parameter tensor $[\MyVec{h}^l_{y}, \MyVec{h}^l_{x}, \MyVec{e}_{y,x}]$ of the messaging function $\phi^l$.
+The collection step copied the hidden vectors from the previous GNN layer $\MyVec{h}^l_y$ and $\MyVec{h}^l_x$ to the both endpoints of each edge $e_{y,x}$ in the edge index, forming the parameter tensor $[\MyVec{h}^l_{y}, \MyVec{h}^l_{x}, \MyVec{e}_{y,x}]$ of the messaging function $\phi^l$.
 %
-This step only involves data movement.
+This step only involved data movement.
 %
-The messaging step calls the messaging function $\phi^l$ on all edges to get message vectors $\MyVec{m}^l_{y,x}$.
+The messaging step called the messaging function $\phi^l$ on all edges to get message vectors $\MyVec{m}^l_{y,x}$.
 %
-The aggregation step aggregates the message vectors with the same target vertex into an aggregated vector $\MyVec{s}^l_x$.
+The aggregation step aggregated the message vectors with the same target vertex into an aggregated vector $\MyVec{s}^l_x$.
 %
-The vector updating step is optional.
+The vector updating step was optional.
 %
-It performs an additional transformation on the aggregated vectors (for example, adding the bias in GCN).
+It performed an additional transformation on the aggregated vectors (for example, adding the bias in GCN).
 
@@
 %
-When the time complexity of $\phi^l$ is high, the messaging step is the performance bottleneck.
+When the time complexity of $\phi^l$ was high, the messaging step was the performance bottleneck.
 %
-Optimizing the implementation of $\phi$ can significantly reduce training time.
+Optimizing the implementation of $\phi$ could significantly reduce training time.
 %
-Otherwise, the collection and the aggregation steps are performance bottlenecks.
+Otherwise, the collection and the aggregation steps were performance bottlenecks.
 %
-Improving the efficiency of the two steps can benefit all GNNs.
+Improving the efficiency of the two steps could benefit all GNNs.
 
@@
 
-The functions $\phi$, $\Sigma$ and $\gamma$ in the edge and vertex calculation stages are made up of a series of basic operators implemented on the GPU side, such as the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
+The functions $\phi$, $\Sigma$ and $\gamma$ in the edge and vertex calculation stages were made up of a series of basic operators implemented on the GPU side, such as the matrix multiplication \texttt{mm}, the elementwise multiplication \texttt{mul} and the index-based selection \texttt{index\_select}.
 %
@@
 %
-Some key intermediate tensors are cached.
+Some key intermediate tensors were cached.
 %
@@
 %
-How to automatically select a proper batch size is a topic worth further studying.
+How to automatically select a proper batch size was a topic worth further studying.
 

### 2020-12-26 NEUROC/sec4-experiments.tex
修改了一些小错误和调整了summary的位置

@@
 
-\paragraph{Summary of Training Time Breakdown}
-%
-The GNN training was suitable for GPUs.
-%
-\emph{The edge calculation stage was the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
-%
-The performance bottleneck in the edge calculation stage depended on the time complexity of the messaging function $\phi$.
-%
-If the time complexity of $\phi$ was {high}, {$\phi$} dominated the training time of the edge calculation stage.
-%
-Optimizations should focus on improving its efficiency.
-%
-Otherwise, the {collection step} and the {aggregation step} dominated the training time.
-%
-The collection step suffered from lots of data movement.
-%
-The aggregation step suffered from data synchronization and non-regular data access.
+\subsubsection{Performance Bottlenecks in Inference}
 
-\subsubsection{Performance Bottlenecks in Inference}
-%
-We also did all the above experiments for Inference.
 %
@@
 %
-We made similar observations for all GNNs. 
-%
 \figurename~\ref{fig:inference_analysis_on_layer_edge_level_of_gcn} shows the results of GCN inference on the \emph{layer} level and the \emph{step} level.
 %
-Compared to the training time breakdown of GCN \figurename~\ref{fig:exp_vertex_edge_cal_proportion}(a), 
+By cross-comparing \figurename~\ref{fig:exp_vertex_edge_cal_proportion}(a), 
 \figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}(a), and \figurename~\ref{fig:exp_edge_calc_decomposition}(a),
 we could conclude that the time breakdowns were very similar.
+%
+For the other GNNs, we observed similar phenomena.
+%
 
@@
     \centering
-    \subfloat[\emph{layer} level]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-    \subfloat[the effect of average degree]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-    \subfloat[\emph{edge} level]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
-    \caption{Time breakdowns on the layer level and edge level, and the effect of average degree on the edge/vertex calculation of GCN Inference.}
+    \subfloat[Layer Level]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+    \subfloat[Effects of the average degree]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+    \subfloat[Edge Level]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
+    \caption{Time breakdowns on the layer level and edge level, and effects of average degree on the edge/vertex calculation of GCN inference.}
     \label{fig:inference_analysis_on_layer_edge_level_of_gcn}
@@
 %
-Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} in the response (Figure X in the revised manuscript) compares the wall-clock time of training and inference on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
+Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} compares the wall-clock time of training and inference on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
 %
@@
 \end{figure}
+
+\paragraph{Summary}
+% TODO:
+The GNN training/inference was suitable for GPUs.
+%
+\emph{The edge calculation stage was the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
+%
+The performance bottleneck in the edge calculation stage depended on the time complexity of the messaging function $\phi$.
+%
+If the time complexity of $\phi$ was {high}, {$\phi$} dominated the training time of the edge calculation stage.
+%
+Optimizations should focus on improving its efficiency.
+%
+Otherwise, the {collection step} and the {aggregation step} dominated the training time.
+%
+The collection step suffered from lots of data movement.
+%
+The aggregation step suffered from data synchronization and non-regular data access.
 
@@
 
-\paragraph{Summary of Memory Usage in Training}
-%
-The \emph{high} memory expansion ratio severely restricted the data scalability of GNN training.
-%
-The memory usage mainly came from the intermediate results of the \emph{edge calculation stage}.
-%
-Fixing the number of vertices, the memory usage increased \emph{linearly} along with the number of edges.
-%
-Fixing the GNN structure and the hyper-parameters, increasing the dimension of input feature vectors could reduce the memory expansion ratio.
-%
-To reduce the memory usage of GNN training, optimizations should focus on reducing memory footprints of the edge calculation stage.
-
 \paragraph{Memory Usage of Inference}
@@
 \end{figure}
+
+\paragraph{Summary of Memory Usage in Training}
+%TODO: 
+The \emph{high} memory expansion ratio severely restricted the data scalability of GNN training.
+%
+The memory usage mainly came from the intermediate results of the \emph{edge calculation stage}.
+%
+Fixing the number of vertices, the memory usage increased \emph{linearly} along with the number of edges.
+%
+Fixing the GNN structure and the hyper-parameters, increasing the dimension of input feature vectors could reduce the memory expansion ratio.
+%
+To reduce the memory usage of GNN training, optimizations should focus on reducing memory footprints of the edge calculation stage.
 
@@
 
-\paragraph{Summary of Sampling Techniques in Training}
-
-The sampled subgraphs had lower average degrees than the original graph.
-%
-With small batch sizes, the sampling techniques could significantly reduce the training time per batch and the peak memory usage.
-%
-However, small batch sizes could not make full use of the computing power of a GPU.
-%
-With big batch sizes, the current implementation of the sampling techniques in PyG was inefficient.
-%
-The time spent on the sampling phase and the data transferring phase even exceeded the training phase.
-
 \subsubsection{Performance Bottlenecks in Inference}
@@
 With the neighbor sampler, the test accuracy of different GNNs showed more obvious differences.
+
+\paragraph{Summary of Sampling Techniques}
+% TODO:
+The sampled subgraphs had lower average degrees than the original graph.
+%
+With small batch sizes, the sampling techniques could significantly reduce the training time per batch and the peak memory usage.
+%
+However, small batch sizes could not make full use of the computing power of a GPU.
+%
+With big batch sizes, the current implementation of the sampling techniques in PyG was inefficient.
+%
+The time spent on the sampling phase and the data transferring phase even exceeded the training phase.

### 2020-12-26 NEUROC/sec4-experiments.tex
grammer和检查了sec4.2

@@
     \caption{Training time breakdown on the layer level.
-The training time of each layer included the time spent on the forward, backward and evaluation phases.
+The training time of each layer included the time spent on the forward, backward, and evaluation phases.
 Each layer was further decomposed into the vertex and the edge calculation stages.}
@@
 %
-It holded the edge set of the graph.
+It held the edge set of the graph.
 %
@@
 %
-Improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} can benefit all kinds of GNNs.
+Improving the efficiency of \texttt{scatter\_add}/\texttt{gather}/\texttt{index\_select} could benefit all kinds of GNNs.
 
@@
 %
-Here, we used GCN as an example. 
-%
-\figurename~\ref{fig:inference_analysis_on_layer_edge_level_of_gcn} shows the results of GCN inference on the \emph{layer} level and the \emph{step} level.
+Taking GCN as an example, \figurename~\ref{fig:inference_analysis_on_layer_edge_level_of_gcn} shows the results of GCN inference on the \emph{layer} level and the \emph{step} level.
 %
@@
     \subfloat[\texttt{fli}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
-    \caption{Wall-clock training/inference time on different datasets.}
+    \caption{Wall-clock inference time on different datasets.}
     \label{fig:compare_wall_clock_time_of_training_and_inference}
@@
 %
-For GCN, the \texttt{index} operator used in the prediction layer became the new top 5 time-consuming operator, replacing the \texttt{gather} operator used in the backward phase in training.
+For GCN, the \texttt{index} operator used in the prediction layer became the new top 5 time-consuming operators, replacing the \texttt{gather} operator used in the backward phase in training.
 %
@@
 
-Although some specific time-consuming operators were different, the performance bottlenecks on the operator level were same for training and inference.
+Although some specific time-consuming operators were different, the performance bottlenecks on the operator level were the same for training and inference.
 %

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
更新Reviewer2

@@
 \usepackage{soul}
-\usepackage[colorlinks=true, linkcolor=blue]{hyperref}
+\usepackage[colorlinks=true, linkcolor=blue, citecolor=black]{hyperref}
+\usepackage{natbib}
 % Vector
@@
     %
-    We have proofread our revised manuscript to eliminate grammar errors and typos as much as we can.
+    We have proofread our revised manuscript to eliminate grammar errors and typos.
     %
@@
     %
-    In the revised manuscript, we have added a new subsection (Section 2.5 ``Inference with GNNs'') to briefly review how to perform inference with GNNs.
+    We add brief description on GNN inference in Section 2.5 ``Inference with GNNs'' in the revised manuscript.
     %
-    We quote the added subsection below.
+    As suggested, we also use the same methodology as the training phase to analyze the performance bottlenecks in the inference phase and we add corresponding experimental results in every subsection of Section 4 ``Evaluation Results and Analysis''.
+    %
+    \begin{enumerate}
 
-    \begin{myquote}{Section 2.5 ``Inference with GNNs''}
-    The model parameters of a GNN consist of the weight vectors/matrices in the prediction layer and the messaging/aggregation/updating functions of each GNN layer.
+    \item In Section 4.1 ``Effects of Hyper-parameters on Performance'', we conduct extra experiments on how the hyper-parameters of GNNs affect the time and peak memory usage of inference.
     %
-    For transductive learning, the input graphs of training and inference are same.
+    We find that the effects of hyper-parameters on the inference time and memory usage are the same as the training time.
     %
-    The structure of the GNN does not need to adjust. 
+    When the other hyper-parameters are fixed, each hyper-parameter itself affects the training time and memory usage in a linear way.
     %
-    For inductive learning, the input graphs used in training and inference are different.
+    The complexity analysis of GNNs holds for both training and inference.
     %
-    When we want to perform inference on a new graph with a pre-trained GNN, the structure of the GNN needs to be adjusted, but the hyper-parameters and the model parameters of the GNN remain unchanged.
+    We present specific experimental results in Section 4.1.2 ``Effects on Inference'' in the revised manuscript.
+
+    \item In Section 4.2 ``Time Breakdown Analysis'', we additionaly conduct time breakdown analysis for GNN inference and compare the similarites and differences between training and inference.
     %
-    The number of graph neurons in each GNN layer has to be adjusted to $|\mathcal{V}|$ of the new graph.
+    As for the similarities, we find that the performance characteristics of inference are highly similar to training on the layer level and the step level of edge calculation.
     %
-    The connections of graph neurons between GNN layers are also adjusted according to the edge set of the new graph.
+    The edge calculation stage is the main performance bottleneck for both training and inference.
     %
-    During inference, input feature vectors of the input graph are propagated forward from the input layer to the prediction layer to give out predicted labels.
+    The specific performance bottlenecks of the edge calculation stage depend on the time complexity of the messaging function $\phi$ of the GNN.
+    %
+    The differences between training and inference were mainly reflected in two aspects: the elapsed time and the top time-consuming basic operators.
+    %
+    The inference time is 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time on average, as shown in Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference}.
+    %
+    Since the inference only conducted the forward propagation from the input layer to the prediction layer, the inference time is very close to the time of the forward phase in training.
+    %
+    For the top time-consuming basic operators, some top operators from the backward phase in training are replaced by operators from the prediction layer in inference.
+    %
+    For example, Figure~\ref{fig:compare_top_basic_operators} shows that the \texttt{gather} operator used in the backward phase of training is replaced by the \texttt{index} operator used in the prediction layer of GCN.
+    %
+    Though the the top time-consuming basic operators are changed, they still indicates that GPUs are suitable for conducting GNN inference.
+    %
+    We present more details of time breakdown analysis on GNN inference in Section 4.2.4 ``Performance Bottlenecks in Inference'' in the revised manuscript.
 
-    When the memory capacity of the GPU is large enough to hold all of the input graph and intermediate results during inference, the inference can produce predicted labels for all vertices and edges at once, making full use of the computing power of the GPU.
-    %
-    When the memory capacity is not large enough, the sampling technique must be adopted.
-
-    The sample-based inference splits the test set into several batches.
-    %
-    For each batch, the sample-based inference samples a subgraph related to the batch from the input graph.
-    %
-    It performs inference on the sampled subgraph to produce predicted labels for the batch.
-    %
-    Since the sampled subgraph is usually much smaller than the original input graph, the memory usage during inference is limited.
-    %
-    The sampling method depends on the prediction task.
-    %
-    Taking the node classification task as an example, if there are $L$ GNN layers in the GNN, the hidden vector outputted by the last GNN layer of each vertex $\MyVec{h}^L_x$ is only related to the $L$-hop neighborhood of $v_x$.
-    %
-    Thus, if we want to predict labels for a group of vertices, we only need to sample a subgraph that contains $L$-hop neighborhoods of all given vertices.
-
-    The implementation of sample-based inference in PyG stores the whole input graph and its feature vectors in the main memory.
-    %
-    In the node classification task, it splits the vertices in the test set into batches accoding to a given batch size.
-    %
-    The subgraph corresponding to each batch is sampled on the CPU side and sent to the GPU side to perform inference.
-    %
-    %By using small batch sizes, the peak memory usage during inference can be limited under the GPU memory capacity.
-
-%    The sample-based inference is also suitable for the online inference scenario that the topology of the graph evolves over time.
-    %
-%    When a graph update arrives, the subgraph affected by the update is sampled and inferences are only performed on the sampled subgraph.it.
-that are affected by , avoiding conducting repeated inferences for the whole graph.
-    \end{myquote}
-
-    To discuss the efficiency of GNN inference on GPUs, we have added corresponding analysis in every subsection of Section 4 ``Evaluation Results and Analysis''.
-    %
-    Below, we introduce our main findings subsection by subsection.
-
-    \paragraph{Section 4.1 ``Effects of Hyper-parameters on Performance''}
-
-    We added paragraphs ``Effects on Inference Time'' in the middle of Section 4.1 to discuss how the time and the peak memory usage of inference changed as we increased the values of the hyper-parameters.
-
-    For all GNNs, we found that the effects of hyper-parameters on the \emph{inference time} were the same as the training time.
-    %
-    Taking GGNN as an example, Figure~\ref{fig:compare_effect_of_hyperparameter_on_time} in the response (Figure X and Figure X in the revised manuscript) shows the effects of the hidden vector dimension $dim(\MyVec{h}^1_x)$ on training/inference time.
-    %
-    When $dim(\MyVec{h}^1_x)$ was large enough, the vertex/edge calculation time of training time and inference time both grew linearly with $dim(\MyVec{h}^1_x)$.
-    %
-    We observed similar phenomena in the other GNNs.
-    %
-    The results indicated that the time complexity analysis of GNNs were applicable to both training and inference.
-
-    \begin{figure}[H]
-            \centering
-             \subfloat[Training]{\includegraphics[width=0.7\textwidth]{../figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}}\\
-            \subfloat[Inference]{\includegraphics[width=0.7\textwidth]{../figs/experiments/exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn.pdf}}
-            \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
-            \label{fig:compare_effect_of_hyperparameter_on_time}
-    \end{figure}
-
-    The effects of hyper-parameters on inference memory usage were also same as training.
-    %
-    Taking GAT as an example, Figure~\ref{fig:compare_effect_of_hyperparameter_on_memory_usage} in the response (Figure X and Figure X in the revised manuscript) shows the peak memory usage during training and inference under different values of hyper-parameters.
-        %
-    The trends of the curves in Figure~\ref{fig:compare_effect_of_hyperparameter_on_memory_usage_training} and Figure~\ref{fig:compare_effect_of_hyperparameter_on_memory_usage_inference} were highly similar.
-        %
-    The memory usage of training and inference \emph{both} grew linearly as the dimension of each head and the number of heads increased.
-        %
-    We observed similar phenomena in the other GNNs.
-        %
-    \begin{figure}[H]
-            \centering
-            \subfloat[Training\label{fig:compare_effect_of_hyperparameter_on_memory_usage_training}]{\includegraphics[width=0.6\textwidth]{../figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
-            \subfloat[Inference\label{fig:compare_effect_of_hyperparameter_on_memory_usage_inference}]{\includegraphics[width=0.6\textwidth]{../figs/experiments/exp_hyperparameter_on_inference_memory_usage_gat.pdf}}
-            \caption{Effects of hyper-parameters on peak memory usage of GAT.}
-            \label{fig:compare_effect_of_hyperparameter_on_memory_usage}
-    \end{figure}
-
-    \paragraph{Section 4.2 ``Time Breakdown Analysis''}    
-    We have added a new subsection Section 4.2.4 ``Performance Bottlenecks in Inference'' in Section 4.2 to conduct time breakdown analysis for GNN inference and compare the differences between training and inference.
-
-    We found that the performance characteristics of GNN inference were highly similar to training on the \emph{layer} level and the \emph{step} level.
-    %
-    In this reply, we used GCN as an example.
-    %
-    We made similar observations in the other GNNs.
-    %
-    Figure~\ref{fig:compare_layer_level_time_breakdown} in the response compares the time breakdowns of GCN on the layer level of training and inference.
-    %
-    The time breakdowns were very similar.
-    %
-    Figure~\ref{fig:compare_effect_of_degree} in the response compares the effects of the average degree on the edge/vertex calculation time during training and inference.
-    %
-    The curves in the two sub-figures of Figure~\ref{fig:compare_effect_of_degree} have similar trends.
-    %
-    \emph{The edge calculation stage dominated both the training and inference time}.
-    %
-    Figure~\ref{fig:compare_time_breakdown_of_edge_calculation} in the response further compares the time breakdowns on the step level of the edge calculation stage.
-    %
-    The proportion of each step was very similar between training and inference.
-    %
-    The results indicated that \emph{the performance bottlenecks of training and inference were same on the layer level and step level}.
-
-    \begin{figure}[H]
-            \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_layer_time_proportion_gcn.pdf}}
-            \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_layer_time_proportion_gcn.pdf}}
-            \caption{Time breakdowns on the layer level of GCN.}
-            \label{fig:compare_layer_level_time_breakdown}
-    \end{figure}
-    %
-    \begin{figure}[H]
-                \subfloat[Training\label{fig:compare_effect_of_degree_training}]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-                \subfloat[Inference\label{fig:compare_effect_of_degree_inference}]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-                \caption{Effects of the average degree on the edge/vertex calculation time of GCN. Graphs were generated by fixing the number of vertices as 50,000.}
-                \label{fig:compare_effect_of_degree}
-    \end{figure}
-    %
-    \begin{figure}[H]
-                \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_edge_calc_decomposition_gcn.pdf}}
-                \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
-                \caption{Time breakdowns on the step level of the edge calculation stage of GCN.}
-                \label{fig:compare_time_breakdown_of_edge_calculation}
-    \end{figure}
-
-    The main differences between training and inference were reflected in two aspects: the wall-clock time and the top time-consuming basic operators.
-
-    The inference time was much less than the training time.
-    %
-    Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} in the response (Figure X in the revised manuscript) compares the wall-clock time of training and inference on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
-    %
-    The results on the other datasets were similar.
-    %
-    Since the inference only conducted the forward propagation from the input layer to the prediction layer, the time of inference was very close to the time of the forward phase in training.
-    %
-    The inference time was 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time, averaged over all datasets.
-
-    \begin{figure}[H]
+    \begin{figure}[h]
         \centering
@@
         \subfloat[\texttt{fli}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
-        \caption{Wall-clock training/inference time on different datasets.}
+        \caption{Comparison of wall-clock training time and inference time on different datasets.}
         \label{fig:compare_wall_clock_time_of_training_and_inference}
@@
 
-    The top time-consuming basic operators of training and inference also showed a certain degree of difference.
-    %
-    Some of the top time-consuming operators during training were replaced by new operators in inference.
-    %
-    Figure~\ref{fig:compare_top_time_consuming_basic_operators} in the response (Figure X in the revised manuscript) compares the top 5 time-consuming basic operators in training and inference.
-    %
-    For GCN, the \texttt{index} operator used in the prediction layer became the new top 5 time-consuming operator, replacing the \texttt{gather} operator used in the backward phase in training.
-    %
-%    The basic operators related to the edge calculation (\texttt{scatter\_add}, \texttt{index\_select}, and \texttt{mul}) still consumed the majority of the inference time.
-    %
-    For GGNN, \texttt{index} operator in the prediction layer also became one of the top 5 time-consuming basic operators.
-    %
-%    Due to the high time complexity of the vertex updating function $\gamma$ in GGNN, the basic operators related to the vertex calculation stage (\texttt{mm} and \texttt{thnn\_fused\_gru\_cell}) still consumed near half of the inference time.
-    %
-    For GAT, the \texttt{input\_put\_impl} operator (used in the backward phase) in Figure~\ref{fig:compare_top_time_consuming_basic_operators}e was replaced by the \texttt{scatter\_add} operator used in the forward edge calculation in Figure~\ref{fig:compare_top_time_consuming_basic_operators}f.
-    %
-%    The \texttt{scatter\_add} operator was related to the edge calculation step.
-    %
-    For GaAN, the \texttt{mm} operator was replaced by the \texttt{cat} operator used in the vertex updating function.
-
-    Although some specific time-consuming operators were different, the performance bottlenecks on the operator level were same for training and inference.
-    %
-    The matrix multiplication \texttt{mm} and the element-wise multiplication \texttt{mul} operators were still time-consuming for inference, making GNN inference also {suitable for GPUs}.
-    %
-    The basic operators related to the collection and aggregation steps in the edge calculation still consumed non-trivial time in inference.
-
-    \begin{figure}[H]
+    \begin{figure}[h]
         \centering
-        \subfloat[GCN, Training]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_top_basic_ops_gcn.pdf}}
-         \subfloat[GCN, Inference]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}\\
-        \subfloat[GGNN, Training]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_top_basic_ops_ggnn.pdf}}
-         \subfloat[GGNN, Inference]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_ggnn.pdf}}\\
-        \subfloat[GAT, Training]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_top_basic_ops_gat.pdf}}
-         \subfloat[GAT, Inference]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gat.pdf}}\\
-        \subfloat[GaAN, Training]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_top_basic_ops_gaan.pdf}}
-         \subfloat[GaAN, Inference]{\includegraphics[width=0.35\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gaan.pdf}}\\
-
-         \caption{Top 5 time-consuming basic operators of typical GNNs.
-The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
-         \label{fig:compare_top_time_consuming_basic_operators}
-
+        \subfloat[Training]{\includegraphics[width=0.4\columnwidth]{../figs/experiments/exp_top_basic_ops_gcn.pdf}}
+        \subfloat[Inference]{\includegraphics[width=0.4\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}
+        \caption{Top 5 time-consuming basic operators of GCN. The time proportion of each basic operator is averaged over all datasets with the error bar indicating the maximum and the minimum.}
+        \label{fig:compare_top_basic_operators}
     \end{figure}
 
-    \paragraph{Section 4.3 ``Memory Usage Analysis''}
+    \item In Section 4.3 ``Memory Usage Analysis'', we conduct extra experiments to evaluate the peak memory usage during inference.
+    %
+    We find that the memory usage of inference also mainly comes from the edge calculation stage, same as training.
+    %
+    Compared with training, the memory expansion ratios of inference are much less, as shown by Figure~\ref{fig:compare_memory_expasion_ratio}.
+    %
+    The memory expansion ratios of inference are 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training.
+    %
+    GGNN, GAT and GaAN have to cache some intermediate results during training, the memory space of those results is saved during inference.
+    %
+    However, the memory expansion ratios of inference are still high, preventing us from inferencing on big graphs.
+    %
+    More details are available in Section 4.3.2 ``Memory Usage of Inference'' in the revised manuscript.
 
-     In the end of Section 4.3, we added a new paragraph ``Memory Usage of Inference'' to compare the memory usage of inference and training.
-     %
-
-     %
-     Figure~\ref{fig:compare_memory_expasion_ratio} in the response (Figure X in the revised manuscript) compares the memory expansion ratios of typical GNNs during training and inference.
-     %
-     Since no intermediate results had to be cached during inference of GGNN, GAT, and GaAN, the memory expansion ratios of inference were much less than training for the three GNNs.
-     %
-     The MERs of inference were 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training.
-     %
-     However, the MERs were still high, disallowing inferencing with big graphs.
-     %
-     To handle big graphs, sample-based inference was necessary.
-
-     \begin{figure}[H]
-%        \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{imagefile}}
-     \end{figure}
-
-     \begin{figure}[H]
+    \begin{figure}[h]
         \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_memory_expansion_ratio.pdf}}
@@
 
-     \paragraph{Section 4.4 ``Effects of Sampling Techniques on Performance''}
+    \item In Section 4.4 ``Effects of Sampling Techniques on Performance'', we additionally conduct experiments to analyze performance bottlenecks in sample-based inference.
     %
-     In Section 4.4, we added a new subsection  Section 4.4.4 ``Performance Bottlenecks in Inference'' to discuss the performance bottlenecks in sample-based inference.
+    Under the same batch size, we find that the subgraph sampler used in inference tends to produce larger subgraphs than the neighbor sampler used in training.
+    %
+    Thus, the batch size used in inference should be small to avoid the out of memory exception on the GPU side.
+    However, the overheads brought by sampling and data transfering from CPU to GPU become obvious when the batch size was small.
+    %
+    They account for near half of the total inference time on the \texttt{amp} and \texttt{cam} datasets, as shown in Figure~\ref{fig:time_breakdown_of_inference_sampler}.
+    %
+    The results indicate that the current implementation of inference sampler in PyG is still inefficient.
+    %
+    We present more details of our experimental analysis in the ``Inference Time'' paragraph of Section 4.4.3 ``Performance Bottlenecks Analysis''
 
-     Sample-based inference was an effective technique to handle big graphs.
-     %
-     Taking the node classification task as an example, to predict labels for a given set of vertices $\mathcal{V}_{predict}$, the inference sampler sampled a subgraph containing complete $L$-hop neighborhoods of all vertices in $\mathcal{V}_{predict}$, where $L$ was the number of GNN layers.
-     %
-     Since the real-world graphs often had small-world property, the size of the sampled subgraph increased quickly as the number of vertices in $\mathcal{V}_{predict}$ (i.e., batch size) increased.
-     %
-     Figure~\ref{fig:sampled_graph_size} (Figure X in the revised manuscript) shows how the relative batch size ($\frac{|\mathcal{V}_{predict}|}{|\mathcal{V}|}$) affected the average degree and the number of edges of the sampled subgraphs during inference.
-     %
-     When the relative batch size was 10\%, the number of edges in the sampled subgraphs were close to the number of edges in the whole graph in most datasets.
-     %
-     In order to limit the memory usage during inference, the batch size used should be very small.
-
-     \begin{figure}[H]
+     \begin{figure}[h]
             \centering           
-        \subfloat[Average degree]{    \includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_graph_info_inference_sampler_avg_degrees.pdf}}
-        \subfloat[Number of edges]{    \includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_graph_info_inference_sampler_edges.pdf}}
-
-        \caption{Characteristics of the sampled subgraphs produced by the inference sampler under different relative batch sizes.}
-        \label{fig:sampled_graph_size}
+            \includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_fix_batch_size_train_time_stack_2048.pdf}
+            \caption{Inference time per batch breakdown under the batch size of 2048.}
+            \label{fig:time_breakdown_of_inference_sampler}
     \end{figure}
 
-     However, the overheads brought by sampling and data transfering from CPU to GPU became obvious when the batch size was small.
-     %
-     Figure~\ref{fig:time_breakdown_of_inference_sampler} (Figure X in the revised manuscript) shows the time breakdowns of sample-based inference on different datasets.
-     %
-     On the \texttt{amp} and \texttt{cam} datasets, the sampling time even accounted for near half of the total inference time.
-     %
-     The results indicated that the current implementation of inference sampler in PyG was also inefficient.
-     %
-     Improving its efficiency could significantly reduce the inference time.
+    \end{enumerate}
 
-     \begin{figure}[H]
-        \centering
-        \subfloat[Batch Size = 1024]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_fix_batch_size_train_time_stack_1024.pdf}}
-        \subfloat[Batch Size = 2048]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_fix_batch_size_train_time_stack_2048.pdf}}
-        \caption{Inference time per batch breakdown under different batch sizes.}
-        \label{fig:time_breakdown_of_inference_sampler}
-     \end{figure}
 \end{reply}
@@
 \begin{reply}
-    We feel really sorry for our carelessness.
+    We feel sorry for our carelessness.
     %
-    We have proofread our revised manuscript to eliminate such language errors as much as we can.
+    We have proofread our revised manuscript to eliminate such language errors.
 \end{reply}
@@
 \begin{reply}
-    Thank you very much for your appreciation.	
+    Thank you for the positive comment.
 \end{reply}
@@
 \begin{reply}
-    Thanks very much for your valuable suggestions.
+    Thank you for the valuable suggestions.
     %
-    The model complexity directly affects both the accuracy and the training time.
+    The model complexity directly affects the accuracy.
     %
-    In order to analyze the relationship between model complexity and accuracy, we have conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affect the accuracy of GNNs (in Section 4.1); (2) how the batch size in the sampling methods affects the accuracy of GNNs (in Section 4.4).
+    In order to analyze the relationship between model complexity and accuracy, we have conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affect the accuracy of GNNs (in Section 4.1.4); (2) how the batch size in the sampling methods affects the accuracy of GNNs (in Section 4.4.3).
+    %
+    In this reply, we focus on the first kind of experiments.
+    %
+    We focus on the second kind of experiments in the next reply.
 
-    We have added more dataset description related to accuracy evaluation in Section 3.1 ``Experimental Setting''.
+    The hyper-parameters determine the model complexity of GNNs and thus affect accuracy.
     %
-    Newly added sentences are marked with underlines in the following quotation.
-
-    \begin{myquote}{Section 3.1 ``Experimental Setting''}
-    \emph{Datasets}.
-    %
-    We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} (in the reply) that were popular in the GNN evaluation [28,31,34,36].
-    %
-    For directed graphs, PyG converts them into undirected ones during data loading.
-    %
-    Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
-    %
-    For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
-    %
-    \ul{For the \texttt{cam} dataset, its vertices were not associated with feature vectors}.
-    %
-    \ul{Thus, we generated random dense feature vectors for it and excluded it from accuracy evaluation}.
-    %
-    \ul{For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the vertices as the training/evaluation/test set, respectively}.
-    %
-    \ul{For \texttt{pub}, we used 500/1000 vertices as the evaluation/test set and the remained as the training set according to [28]}.
-    %
-    \ul{For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to [31]}.
-    %
-    We also used random graphs generated by the R-MAT graph generator [35] in some experiments, to explore the effects of graph topological characteristics (like average degrees) on performance bottlenecks.
-    %
-    Input feature vectors of random graphs were random dense vectors with the dimension of 32.
-    %
-    Vertices of random graphs were classified into 10 classes randomly.
-
-    \begin{table}[H]
-        \centering
-        \begin{tabular}{cccccccc}
-            \toprule
-            Dataset                                                 & $|\mathcal{V}|$ & $|\mathcal{E}|$ & $\bar{d}$ & $dim(\boldsymbol{v})$ & \#Class & Directed \\
-            \midrule
-            pubmed (\texttt{pub}) [28]  & 19,717          & 44,324          & 4.5       & 500                   & 3       & Yes      \\
-            amazon-photo (\texttt{amp}) [34]     & 7,650           & 119,081         & 31.1      & 745                   & 8       & Yes      \\
-            amazon-computers (\texttt{amc}) [34] & 13,752          & 245,861         & 35.8      & 767                   & 10      & Yes      \\
-            coauthor-physics (\texttt{cph}) [34] & 34,493          & 247,962         & 14.4      & 8415                  & 5       & Yes      \\
-            flickr (\texttt{fli}) [31]                 & 89,250          & 899,756         & 10.1      & 500                   & 7       & No       \\
-            com-amazon (\texttt{cam}) [36]               & 334,863         & 925,872         & 2.8       & 32                    & 10      & No       \\
-            \bottomrule
-        \end{tabular}
-        \caption{Dataset overview. $\bar{d}$ represents the average vertex degree. $dim(\boldsymbol{v})$ is the dimension of the input feature vector.}
-        \label{tab:dataset_overview}
-    \end{table}
-
-    \end{myquote}
-
-    In this reply, we focus on the experiments related to hyper-parameters in Section 4.1.
-    %
-    We introduce the experimental results of the sampling techniques in Section 4.4 in the next reply.
-
-    Hyper-parameters determine the model complexity of a GNN.
-    %
-    Generally speaking, higher values of hyper-parameters bring higher model complexity and increase representation capability.
-    %
-    In the revised manuscript, we add a new subsection Section 4.1.4 ``Effects on Accuracy'' at the end of Section 4.1 ``Effects of Hyper-parameters on Performance'' to analyze how hyper-parameters affect the accuracy.
+    To find out the effects of hyper-parameters, we measure and compare the test accuracy of the four GNNs trained with different hyper-parameters.
     %
     We have two main findings.
+
+    First, the accuracy of GNNs is much more sensitive to the dimension of hidden vectors (for GCN/GGNN/GaAN) and the dimension of each head (for GAT) than the other hyper-parameters.
     %
-    First, the accuracy of GNNs is much more sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$ (for GCN/GGNN/GaAN) and the dimension of each head $d_{head}$ (for GAT) than the other hyper-parameters.
+    Figure~\ref{fig:effect_of_hyper_parameter_on_accuracy_of_gaan} shows the results of GaAN.
     %
-    Second, the relative accuracy of the four typical GNNs varies greatly with different datasets.
+    More results are available in Section 4.1.4 ``Effects on Accuracy'' in the revised manuscript.
     %
-    We quote from Section 4.1.4 of the revised manuscript to present our results.
+    The accuracy of the four GNNs is low when the dimensions are very low ($\leq 8$).
+    %
+    As the dimensions increase to a certain threshold, the GNNs gain sufficient representation capability to achieve good accuracy.
+    %
+    But very high dimensions ($\geq 2048$) are also harmful to accuracy in some cases, as they increase the risk of overfitting.
 
-    \begin{myquote}{Section 4.1.4 ``Effects on Accuracy''}
-    %
-    The values of hyper-parameters determined the model complexity of a GNN.
-    %
-    The relationship between model complexity and accuracy was complex.
-    %
-    %As far as we know, there is little theoretical analysis yet.
-    %
-    Generally speaking, higher model complexity brought more powerful representation capability and might bring higher accuracy, but it also increased the risk of overfitting.
+    \begin{figure}[h]
+        \includegraphics[width=1.0\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}
+        \caption{Effects of hyper-parameters on accuracy of GaAN.}
+        \label{fig:effect_of_hyper_parameter_on_accuracy_of_gaan}
 
-    To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the typical GNNs with varying hyper-parameters.
-    %
-    \figurename~\ref{fig:exp_hyperparameter_accuracy} (in the reply) shows the experimental results.
-    %
-    For GCN, its accuracy was sensitive to the dimension of hidden vectors $dim(\MyVec{h}^1_x)$.
-    %
-    As $dim(\MyVec{h}^1_x)$ increased, the accuracy first increased quickly and then stabilized when $dim(\MyVec{h}_x^1) \geq 8$.
-    %
-    For GGNN, its accuracy curves showed similar trends as GCN, but GGNN was more sensitive to $dim(\MyVec{h}_x^1)$ than GCN.
-    %
-    Its accuracy even decreased when $dim(\MyVec{h}_x^1) \geq 1024$.
-    %
-    Since GGNN had high model complexity (with 13 weight matrices/vectors to train), GGNN might occur overfitting in those cases.
-    %
-    For GAT, its accuracy was more sensitive to the dimension of each head $d_{head}$ than the number of heads.
-    %
-    For GaAN, only $dim(\MyVec{h}_x^1)$ showed obvious impacts on accuracy.
-    %
-    The experimental results indicated that the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was too low.
-    %
-    %The low model complexity limited the representation capability of the GNNs.
-    %
-    As $dim(\MyVec{h}_x^1)$ or $d_{head}$ increased to a certain threshold, the GNNs gained sufficient learning ability to achieve stable accuracy.
-
-    \begin{figure}[H]
-        \centering
-        \subfloat[GCN]{\includegraphics[width=0.4\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gcn.pdf}}
-        \subfloat[GGNN]{\includegraphics[width=0.4\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_ggnn.pdf}}\\
-        \subfloat[GAT]{\includegraphics[width=0.8\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gat.pdf}}\\
-        \subfloat[GaAN]{\includegraphics[width=1.0\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}}
-        \caption{Effects of hyper-parameters on accuracy of the typical GNNs.}
-        \label{fig:exp_hyperparameter_accuracy}
     \end{figure}
 
-    %\begin{figure}[H]
-        %\centering
-        %\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_accuracy_gat_small_info.pdf}
-        %\caption{Effects of the number of heads on GAT ($d_{head}$=2,4)}
-        %\label{fig:exp_hyperparameter_accuracy_gat_small_info}
-    %\end{figure}
+    Second, the relative accuracy between the four GNNs varies greatly with different datasets.
+    %
+    We compare the best accuracy that each GNN achives on every dataset in Figure~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast}.
+    %
+    The best accuracy of the four GNNs are very close.
+    %
+    It is also close to the accuracy reported in [\cite{shchur2018_pitfall_of_gnn, zeng2020_graphsaint}].
+    %
+    There is no clear winner in terms of accuracy.
+    %
+    GaAN that has the highest complexity performs slightly better than the other GNNs.
+    %
+    Simple GNN models (such as GCN) can still achieve good acuuracy with proper hyper-parameter settings.
 
-    \figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} (in the reply) further compares the best accuracy that each GNN could achieve on different datasets.
-    %
-    The best accuracy of the typical GNNs was very close.
-    %
-    %
-    It was also close to the accuracy reported in their original references [34, 31].
-    %
-    The results indicated that there was no clear winner.
-    %
-    The relative accuracy between GNNs varied greatly with different datasets.
-    %
-    GaAN achieved the highest accuracy in three out of five datasets.
-    %
-    GCN achieved the highest or second highest accuracy in three out of five datasets, though its model was simplest.
-    %
-    Simple GNN models (such as GCN) could still achieve good accuracy with proper hyper-parameter settings.
-
-    \begin{figure}[H]
+    \begin{figure}[h]
         \centering
         \includegraphics[width=3.5in]{../figs/experiments/exp_hyperparameter_on_accuracy_alg_contrast.pdf}
-        \caption{Best accuracy that each GNN achieved on different datasets.}
+        \caption{Best accuracy that each GNN achieves on different datasets.}
         \label{fig:exp_hyperparameter_on_accuracy_alg_contrast}
@@
 
-    \end{myquote}
+    In addition, we add more details on the proportions of  the train/evaluation/test sets of the datasets in Section 3.1 ``Experimental Setting'' in the revised manuscript.
+    %
+    Since the vertices of the \texttt{cam} dataset are not attached with feature vectors, we exclude it from the accuracy evaluation.
 \end{reply}
@@
 
-    Thanks for the insightful comment and valuable suggestion.
+    Thanks for the insightful comment.
     %
-    The sampling methods indeed affect the test accuracy of GNN models [5, 28, 26, 31].
+    %The sampling methods indeed affect the test accuracy of GNN models [\cite{hamilton2017_graphsage, chiang2019_cluster_gcn, zeng2020_graphsaint}].
     %
-    Without sampling, the GNN models are trained with a \emph{batch} gradient descent manner.
+    With or without the sampling methods, the structure of the GNN remains the same, but the gradients of the model parameters are calculated differently, affecting the accuracy of the GNN model.
+    %
+    With sampling, each GNN layer still consists of $|\mathcal{V}|$ graph neurons ($|\mathcal{V}|$ is the number of vertices in the graph), but only graph neurons corresponding to the vertices in the sampled subgraph are activated.
+    %
+    Thus, the model parameters are updated according to the gradients calculated on the sampled subgraph, instead of the whole graph.
+    %
+    In other words, the GNN models are trained in a \emph{batch} gradient descent manner (i.e., full-batch training) without sampling.
     %
     With sampling, the GNN models are trained with \emph{mini-bach} stochastic gradient descent.
+
+    To find out how the sampling techniques affect accuracy, we train the four typical GNNs with different batch sizes and compare the accuracy with the full-batch training.
     %
-    The structure of the GNN remains unchanged between batches.
+    For each combination of dataset and GNN, we use the hyper-parameters that achieve the highest accuracy under the full-batch training.
     %
-    Each GNN layer always consists of $|\mathcal{V}|$ graph neurons, where $|\mathcal{V}|$ is the number of vertices in the graph.
+    Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage}  and Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} shows the accuracy comparisons of the two typical sampling methods under different batch sizes.
     %
-    But the numbers of \emph{activated} graph neurons are different for different batches.
+    Results of the other datasets are available in Section 4.4.3 ``Effects on Accuracy'' in the revised manuscript.
     %
-    In each batch, only the neurons corresponding to the vertices appearing in the sampled subgraph will be activated.
+    In most cases, the test accuracy of the sampling methods is just slightly lower than the accuracy of the full-batch training when the relative batch size $\geq 3\%$.
     %
-    The model parameters are updated according to the gradients calculated on the sampled subgraph in each batch.
+    In several cases (like GaAN in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amp} and Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amc}), the accuracy of the neighbor sampler was even higher than the full-batch training.
     %
-    Thus, the test accuracy of the models trained with sampling techniques may be different from the full-graph training.
+    Among the two sampling methods, the performance of the cluster sampler is stabler than the neighbor sampler.
+    %
+    The test accuracy of the cluster sampler is close to the accuracy of full-batch training, while the test accuracy of the neighbor sampler shows more obvious differences for different GNNs.
 
-    To discuss how the sampling techniques affect model accuracy, we have added a new subsection Section 4.2.2 ``Effects on Accuracy'' in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
-    %
-    We quote from Section 4.4.2 of the revised manuscript to present our results.
-
-    \begin{myquote}{Section 4.4.2 ``Effects on Accuracy''}
-
-    Since the size of the sampled subgraph was much smaller than the original graph, the accuracy of the GNN models got by sampling techniques might be different from the full-batch training.
-    %
-    To find out how the batch size affected the test accuracy, we trained GNNs with different batch sizes.
-    %
-    \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} (in the reply) and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} (in the reply) compare the test accuracy achieved by sampling techniques with the test accuracy of the full-batch training.
-    %
-    For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.
-
-    \begin{figure}[H]
+    \begin{figure}[h]
             \centering
-        \subfloat[\texttt{amp}]{\includegraphics[width=2in]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
-        \subfloat[\texttt{amc}]{\includegraphics[width=2in]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
-        \subfloat[\texttt{fli}]{\includegraphics[width=2in]{../figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
+            \subfloat[\texttt{amp}\label{fig:exp_graphsage_sampling_accuracy_on_amp}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
+            \subfloat[\texttt{amc}\label{fig:exp_graphsage_sampling_accuracy_on_amc}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
+            \subfloat[\texttt{fli}\label{fig:exp_graphsage_sampling_accuracy_on_fli}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
             \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
@@
 
-    \begin{figure}[H]
+        \begin{figure}[h]
             \centering
@@
 
-    The experimental results confirmed the effectiveness of the sampling methods in terms of accuracy.
+    The results indicate that the relationships between batch size and test accuracy are complex, especially for the neighbor sampler.
     %
-    When the relative batch size was greater than or equal to 3\%, the test accuracy of the GNNs trained with sampling was close to the accuracy obtained by full-batch training.
+    A larger batch size does not always bring higher accuracy, like GAT in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_fli}. 
     %
-    In most cases, the accuracy achieved by the sampling techniques was slightly lower than the full-batch training.
+    Our observations are similar to \cite{zeng2020_graphsaint}.
     %
-    However, there were some exceptions (like GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc} in the reply) that the accuracy achieved by sampling was even higher.
-
-    The relationships between batch size and test accuracy were complex.
-    %
-    A larger batch size did not always bring higher accuracy.
-    %
-    For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} (in the reply) and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} (in the reply) decreased as the batch size increased.
-    %
-    A smaller batch size sometimes could achieve higher accuracy.
-    %
-    For example, GAT achieved a higher accuracy with 1\% relative batch size than the full-batch training in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc} (in the reply).
-    %
-    Given a sampling method, we found that the optimal batch size highly depended on the dataset and the GNN algorithm.
-    %
-    Our observations were similar to [31].
-    %
-    How to automatically select a proper batch size is a topic worth further studying.
-
-    Among the two sampling methods, the performance of the cluster sampler was stabler than the neighbor sampler.
-    %
-    With the cluster sampler, the test accuracy of different GNNs was very close to the accuracy of full-batch training.
-    %
-    With the neighbor sampler, the test accuracy of different GNNs showed more obvious differences.
-    \end{myquote}
-
+    How to automatically select a proper batch size is a topic worth studying.
 \end{reply}
@@
     %
-    As suggested, we additionally evaluated the effects of model complexity on accuracy in Section 4.1 ``Effects of Hyper-parameters on Performance'' in the revised manuscript.
+    As suggested, we additionally evaluate the effects of model complexity on accuracy in Section 4.1 ``Effects of Hyper-parameters on Performance'' in the revised manuscript.
     %
-    We added experimental results on how the hyper-parameters of GNNs affected the accuracy.
+    We add experimental results on how the hyper-parameters of GNNs affect the accuracy.
     %
-    Since different GNNs had different model complexity, we further compared the test accuracy of different GNNs on the same dataset.
+    We also compare the test accuracy of different GNN models on the same dataset.
+
+    We also additionally evaluate the effects of sampling techniques on accuracy in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
     %
-    More details are available in the reply to Reviewer Point P2.4.
-
-    We also additionally evaluated the effects of sampling techniques on accuracy in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
-    %
-    We presented the experimental results in a new subsection Section 4.4.2 ``Effects on Accuracy''.
-    %
-    More details are available in the reply to Reviewer Point P2.5.
+    We presented the experimental results in a new subsection Section 4.4.3 ``Effects on Accuracy''.
 \end{reply}
 
+\bibliographystyle{elsarticle}
+\bibliography{../gnnref.bib}
+
 \end{document}

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
update

@@
     %
-    We present more details of our experimental analysis in the ``Inference Time'' paragraph of Section 4.4.3 ``Performance Bottlenecks Analysis''
+    We present more details of our experimental analysis in the ``Inference Time'' paragraph of Section 4.4.3 ``Performance Bottlenecks in Inference''
 
@@
     %
-    In order to analyze the relationship between model complexity and accuracy, we have conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affect the accuracy of GNNs (in Section 4.1.4); (2) how the batch size in the sampling methods affects the accuracy of GNNs (in Section 4.4.3).
+    In order to analyze the relationship between model complexity and accuracy, we have conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affect the accuracy of GNNs (in Section 4.1.4); (2) how the batch size in the sampling methods affects the accuracy of GNNs (in Section 4.4.4).
     %
@@
     %
-    Results of the other datasets are available in Section 4.4.3 ``Effects on Accuracy'' in the revised manuscript.
+    Results of the other datasets are available in Section 4.4.4 ``Effects on Accuracy'' in the revised manuscript.
     %
@@
     %
-    We presented the experimental results in a new subsection Section 4.4.3 ``Effects on Accuracy''.
+    We presented the experimental results in a new subsection Section 4.4.4 ``Effects on Accuracy''.
 \end{reply}

### 2020-12-26 NEUROC/sec4-experiments.tex
update

@@
 %
-To handle big graphs, sample-based inference was necessary.
+To handle big graphs, the sample-based inference was necessary.
 
@@
 
-\paragraph{Summary of Memory Usage in Training}
+\paragraph{Summary}
 %TODO: 
-The \emph{high} memory expansion ratio severely restricted the data scalability of GNN training.
+The \emph{high} memory expansion ratio severely restricted the data scalability of GNN training and inference.
 %

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
更新Response.

--- 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
@@
 % command declarations for reviewer points and our responses
-\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule
-                  \section*{Reviewer \thereviewer}}
+\newcommand{\reviewersection}{\stepcounter{reviewer} \bigskip \hrule \setcounter{figure}{0}\section*{Reviewer \thereviewer}}
 
@@
 	\medskip}
+
+% Numbering figures according to reviewers
+\renewcommand{\thefigure}{\thereviewer{}.\arabic{figure}}
 
@@
 
-    \begin{table}[H]
-        \footnotesize
-        \caption{Frequently-used Symbols}
-        \label{tab:symbols}
-        \centering
-        \begin{tabular}{p{3em}lp{35em}}
-            \toprule
-            Category & Symbol & Meaning \\
-            \midrule
-            \multirow[c]{4}{3em}{Graph Structure}& $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ & The simple undirected input graph with the vertex set $\mathcal{V}$ and the edge set $\mathcal{E}$. \\
-            & $v_x$ & The $x$-th vertex of the input graph. \\
-            & $e_{y,x}$ & The edge pointing from $v_y$ to $v_x$ of the input graph. \\
-            & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ 
-            & $\bar{d}$ & The average degree of the input graph. \\ \midrule
-            \multirow[c]{6}{3em}{GNN Definition}& $L$ & The number of GNN layers. \\
-            & $K$ & The number of heads in a GNN layer. \\
-            & $\phi^l$ & The messaging function of the GNN layer $l$. \\
-            & $\Sigma^l$ & The aggregation function of the GNN layer $l$. \\
-            & $\gamma^l$ & The vertex updating function of the GNN layer $l$. \\ 
-            & $\phi^{l,i}$ / $\Sigma^{l,i}$ / $\gamma^{l,i}$ & The messaging/aggregation/updating function of the $i$-th sub-layer of the GNN layer  $l$.\\
-            & $\textcolor{blue}{\boldsymbol{W}^l, \boldsymbol{W}^{(k)}/\boldsymbol{b}, \boldsymbol{a}}$ & The matrices/vectors represented by the blue characters are the weight matrices/vectors that need to be learned in the GNN.
+%    \begin{table}[H]
+%        \footnotesize
+%        \caption{Frequently-used Symbols}
+%        \label{tab:symbols}
+%        \centering
+%        \begin{tabular}{p{3em}lp{35em}}
+%            \toprule
+%            Category & Symbol & Meaning \\
+%            \midrule
+%            \multirow[c]{4}{3em}{Graph Structure}& $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ & The simple undirected input graph with the vertex set $\mathcal{V}$ and the edge set $\mathcal{E}$. \\
+%            & $v_x$ & The $x$-th vertex of the input graph. \\
+%            & $e_{y,x}$ & The edge pointing from $v_y$ to $v_x$ of the input graph. \\
+%            & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ 
+%            & $\bar{d}$ & The average degree of the input graph. \\ \midrule
+%            \multirow[c]{6}{3em}{GNN Definition}& $L$ & The number of GNN layers. \\
+%            & $K$ & The number of heads in a GNN layer. \\
+%            & $\phi^l$ & The messaging function of the GNN layer $l$. \\
+%            & $\Sigma^l$ & The aggregation function of the GNN layer $l$. \\
+%            & $\gamma^l$ & The vertex updating function of the GNN layer $l$. \\ 
+%            & $\phi^{l,i}$ / $\Sigma^{l,i}$ / $\gamma^{l,i}$ & The messaging/aggregation/updating function of the $i$-th sub-layer of the GNN layer  $l$.\\
+%            & $\textcolor{blue}{\boldsymbol{W}^l, \boldsymbol{W}^{(k)}/\boldsymbol{b}, \boldsymbol{a}}$ & The matrices/vectors represented by the blue characters are the weight matrices/vectors that need to be learned in the GNN.
 \\  \midrule
-            \multirow[c]{8}{3em}{Vector}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
-            & $\boldsymbol{e}_{y,x}$ & The feature vector of the edge $e_{y,x}$.  \\
-            & $\boldsymbol{h}_x^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$. \\
-            & $\boldsymbol{h}_x^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$.\\
-            & $\boldsymbol{m}_{y,x}^l$ & The message vector of the edge $e_{y,x}$ outputted by $\phi^l$ of the GNN layer $l$. \\
-            & $\boldsymbol{s}_{x}^l$ & The aggregated vector of the vertex $v_x$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
-            & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{y,x}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
+%            \multirow[c]{8}{3em}{Vector}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
+%            & $\boldsymbol{e}_{y,x}$ & The feature vector of the edge $e_{y,x}$.  \\
+%            & $\boldsymbol{h}_x^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$. \\
+%            & $\boldsymbol{h}_x^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$.\\
+%            & $\boldsymbol{m}_{y,x}^l$ & The message vector of the edge $e_{y,x}$ outputted by $\phi^l$ of the GNN layer $l$. \\
+%            & $\boldsymbol{s}_{x}^l$ & The aggregated vector of the vertex $v_x$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
+%            & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{y,x}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
 \\
-            & $d^l_{in}$, $d^l_{out}$ &  The dimension of the input/output hidden vectors of the GNN layer $l$. \\
-            & $dim(\MyVec{x})$ & The dimension of a vector $\MyVec{x}$. \\
-            \bottomrule
-        \end{tabular}
-\end{table}
+%            & $d^l_{in}$, $d^l_{out}$ &  The dimension of the input/output hidden vectors of the GNN layer $l$. \\
+%            & $dim(\MyVec{x})$ & The dimension of a vector $\MyVec{x}$. \\
+%            \bottomrule
+%        \end{tabular}
+%\end{table}
 
@@
     %
-    %The sampling methods indeed affect the test accuracy of GNN models [\cite{hamilton2017_graphsage, chiang2019_cluster_gcn, zeng2020_graphsaint}].
+    The sampling methods indeed affect the test accuracy of GNN models [\cite{hamilton2017_graphsage, chiang2019_cluster_gcn, zeng2020_graphsaint}].
     %
-    With or without the sampling methods, the structure of the GNN remains the same, but the gradients of the model parameters are calculated differently, affecting the accuracy of the GNN model.
+    %With or without the sampling methods, the structure of the GNN remains the same, but the gradients of the model parameters are calculated differently, affecting the accuracy of the GNN model.
     %
-    With sampling, each GNN layer still consists of $|\mathcal{V}|$ graph neurons ($|\mathcal{V}|$ is the number of vertices in the graph), but only graph neurons corresponding to the vertices in the sampled subgraph are activated.
+    %With sampling, each GNN layer still consists of $|\mathcal{V}|$ graph neurons ($|\mathcal{V}|$ is the number of vertices in the graph), but only graph neurons corresponding to the vertices in the sampled subgraph are activated.
     %
-    Thus, the model parameters are updated according to the gradients calculated on the sampled subgraph, instead of the whole graph.
+    %Thus, the model parameters are updated according to the gradients calculated on the sampled subgraph, instead of the whole graph.
     %
-    In other words, the GNN models are trained in a \emph{batch} gradient descent manner (i.e., full-batch training) without sampling.
+    %In other words, the GNN models are trained in a \emph{batch} gradient descent manner (i.e., full-batch training) without sampling.
     %
-    With sampling, the GNN models are trained with \emph{mini-bach} stochastic gradient descent.
-
+    %With sampling, the GNN models are trained with \emph{mini-bach} stochastic gradient descent.
+    %
     To find out how the sampling techniques affect accuracy, we train the four typical GNNs with different batch sizes and compare the accuracy with the full-batch training.

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
更新Response.

@@
     %
-    As for the similarities, we find that the performance characteristics of inference are highly similar to training on the layer level and the step level of edge calculation.
+    As for the similarities, we find that the performance characteristics of inference and training are highly similar on the layer level and the step level of edge calculation.
     %
@@
     %
-    The specific performance bottlenecks of the edge calculation stage depend on the time complexity of the messaging function $\phi$ of the GNN.
+    %The specific performance bottlenecks of the edge calculation stage depend on the time complexity of the messaging function $\phi$ of the GNN.
     %
-    The differences between training and inference were mainly reflected in two aspects: the elapsed time and the top time-consuming basic operators.
+    As for the differences, training and inference are different mainly in two aspects: the elapsed time and the top time-consuming basic operators.
+    %
+    The inference time is much less than the training time.
+    %
+    The top time-consuming basic operators used in the backward phase of training are replaced by the basic operators used in the prediction layer of inference.
     %
@@
     %
-    Compared with training, the memory expansion ratios of inference are much less, as shown by Figure~\ref{fig:compare_memory_expasion_ratio}.
+    However, the memory expansion ratios of inference are much less than training.
     %
-    The memory expansion ratios of inference are 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training.
+    The memory expansion ratios of inference are 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training, as indicated by Figure~\ref{fig:compare_memory_expasion_ratio}.
     %
@@
     %
-    However, the memory expansion ratios of inference are still high, preventing us from inferencing on big graphs.
+    However, the memory expansion ratios of inference are still high, preventing us from inferencing with big graphs.
     %
@@
     %
+    We find that the batch size used in inference should be smaller than training to avoid the out of memory exception on the GPU side.
+    %
+    The current implementation of the sampler used in inference in PyG is still inefficient.
+    %
+    The overheads of sampling and data transfering are significant in the total inference time.
+    %
     Under the same batch size, we find that the subgraph sampler used in inference tends to produce larger subgraphs than the neighbor sampler used in training.
     %
-    Thus, the batch size used in inference should be small to avoid the out of memory exception on the GPU side.
-    However, the overheads brought by sampling and data transfering from CPU to GPU become obvious when the batch size was small.
+    Thus, the batch size must be small to avoid the out of memory exception on the GPU side.
+    %
+    At the same time, the overheads brought by sampling and data transfering from CPU to GPU become obvious when the batch size was small.
     %
     They account for near half of the total inference time on the \texttt{amp} and \texttt{cam} datasets, as shown in Figure~\ref{fig:time_breakdown_of_inference_sampler}.
-    %
-    The results indicate that the current implementation of inference sampler in PyG is still inefficient.
     %
@@
     %
-    More results are available in Section 4.1.4 ``Effects on Accuracy'' in the revised manuscript.
-    %
-    The accuracy of the four GNNs is low when the dimensions are very low ($\leq 8$).
+    The accuracy of GaAN is low when the dimensions are very low ($\leq 8$).
     %
@@
     %
-    But very high dimensions ($\geq 2048$) are also harmful to accuracy in some cases, as they increase the risk of overfitting.
+    But high dimensions ($\geq 2048$) are also harmful to accuracy on the \texttt{amp} dataset, as they increase the risk of overfitting.
+    %
+    The results of the other GNNs are available in Section 4.1.4 ``Effects on Accuracy'' in the revised manuscript.
+    %
 
@@
     %
+    There is no clear winner.
+    %
     We compare the best accuracy that each GNN achives on every dataset in Figure~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast}.
@@
     %
-    There is no clear winner in terms of accuracy.
-    %
-    GaAN that has the highest complexity performs slightly better than the other GNNs.
+    GaAN that has the highest complexity performs slightly better than the other GNNs, winning three out of five datasets.
     %
@@
     %
+    In most cases, the test accuracy of the sampling methods is just slightly lower than the accuracy of the full-batch training when the relative batch size $\geq 3\%$.
+    %
+    Among the two sampling methods, the performance of the cluster sampler is stabler than the neighbor sampler.
+    %
     Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage}  and Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} shows the accuracy comparisons of the two typical sampling methods under different batch sizes.
     %
-    Results of the other datasets are available in Section 4.4.3 ``Effects on Accuracy'' in the revised manuscript.
-    %
-    In most cases, the test accuracy of the sampling methods is just slightly lower than the accuracy of the full-batch training when the relative batch size $\geq 3\%$.
+    The results of the other datasets are available in Section 4.4.3 ``Effects on Accuracy'' in the revised manuscript.
     %
     In several cases (like GaAN in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amp} and Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amc}), the accuracy of the neighbor sampler was even higher than the full-batch training.
-    %
-    Among the two sampling methods, the performance of the cluster sampler is stabler than the neighbor sampler.
     %

### 2020-12-26 NEUROC/sec4-experiments.tex
grammer和修正了sec4.4的语法

@@
 
-With the sampling techniques, GNNs were trained and inferenced in a mini-batch manner.
+With the sampling techniques, GNNs were trained and inferred in a mini-batch manner.
 %
@@
 %
-Thus, it affected the accuracy, training/inference time and memory usage of GNNs simultaneously.
+Thus, it affected the accuracy, training/inference time, and memory usage of GNNs simultaneously.
 
@@
     \caption{Training time per epoch on small random graphs.
-For each number of vertices, we generated 50 random graphs with the average degree of 4.0 and reported the average training time per batch (without the evaluation phase).
+For each number of vertices, we generated 50 random graphs with an average degree of 4.0 and reported the average training time per batch (without the evaluation phase).
 The error bar indicates the standard deviation.}
@@
 
-Sample-based inference was an effective technique to handle big graphs.
+The sample-based inference was an effective technique to handle big graphs.
 %
@@
 %
-In order to limit the memory usage during inference, the batch size used should be very small.
+To limit the memory usage during inference, the batch size used should be very small.
 
@@
 
-However, the overheads brought by sampling and data transfering from CPU to GPU became obvious when the batch size was small.
+However, the overheads brought by sampling and data transferring from CPU to GPU became obvious when the batch size was small.
 %

### 2020-12-26 NEUROC/sec4-experiments.tex
grammer和修正了sec4.4的语法

@@
 %
-Figure~\ref{fig:sampled_graph_size} (Figure X in the revised manuscript) shows how the relative batch size ($\frac{|\mathcal{V}_{predict}|}{|\mathcal{V}|}$) affected the average degree and the number of edges of the sampled subgraphs during inference.
+Figure~\ref{fig:sampled_graph_size} shows how the relative batch size ($\frac{|\mathcal{V}_{predict}|}{|\mathcal{V}|}$) affected the average degree and the number of edges of the sampled subgraphs during inference.
 %
@@
 %
-How to automatically select a proper batch size was a topic worth further studying.
+How to automatically select a proper batch size is a topic worth further studying.
 

### 2020-12-26 NEUROC/sec2-review-of-graph-neural-network.tex
修改了sec2

@@
 \begin{table}[h]
-    \caption{Notations}
+    \caption{Frequently-used symbols}
     \label{tab:notations}
@@
 
-A GNN usually consists of more than one GNN layers.
+A GNN usually consists of more than one GNN layer.
 %
@@
 %
-We elaborate on details of graph neurons later.
+We elaborate on the details of graph neurons later.
 %
@@
 The traditional methods need to construct input feature vectors for vertices and edges manually or use embedding methods like DeepWalk \cite{bryan2014_deepwalk} and node2vec \cite{aditya2016_node2vec}.
-The feature vector generation is independent from the model training.
+The feature vector generation is independent of model training.
 Therefore, generated feature vectors may not be suitable for downstream prediction tasks.
 In GNNs, gradients are propagated from the prediction layer back to GNN layers layer by layer. 
-The model parameters in the GNN layers are updated based on the feedbacks from the downstream prediction task. 
+The model parameters in the GNN layers are updated based on the feedback from the downstream prediction task. 
 In a fully parameterized way, a GNN can automatically extract an embedding vector for each vertex from its $L$-hop neighborhood, tuned according to the specific prediction task.
@@
     %
-    \item  For every adjacent edge $(v_y, v_x)$ of $v_x$ ($v_y \in \mathcal{N}(v_x)$), the messaging function $\phi^l$ receives the output hidden vectors $\boldsymbol{h}^l_x$ and $\boldsymbol{h}^l_y$ from the previous GNN layer and the edge feature vector $\boldsymbol{e}_{y,x}$ (and other feature vectors associated with $v_x$/$v_y$ if necessary) as the input.
+    \item  For every adjacent edge $(v_y, v_x)$ of $v_x$ ($v_y \in \mathcal{N}(v_x)$), the messaging function $\phi^l$ receives the output hidden vectors $\boldsymbol{h}^l_y$ and $\boldsymbol{h}^l_x$ from the previous GNN layer and the edge feature vector $\boldsymbol{e}_{y,x}$ (and other feature vectors associated with $v_x$/$v_y$ if necessary) as the input.
     %
@@
             $\MyVec{m}^l_{y, x} = \MyVec{\hat{h}}^l_y$                                           &
-            $O(d_{in} * d_{out})$                                                                                                       \\
+            $O(1)$                                                                                                       \\
             \textbf{GAT}   \cite{huang2018_gat}                                                                                       &
@@
 %
-The updating function $\phi^l$ of GGNN is a modified GRU unit that has 12 model parameters to learn, having high computational complexity.
+The updating function $\gamma^l$ of GGNN is a modified GRU unit that has 12 model parameters to learn, having high computational complexity.
 %
@@
 %
-The tecnnique first samples several vertices from $\mathcal{V}$ in the last GNN layer.
+The technique first samples several vertices from $\mathcal{V}$ in the last GNN layer.
 %
@@
 %
-$\eta^l$ is the hyper-parameter that is usually much smaller than $|\mathcal{V}|$.
+$\eta^l$ is the hyper-parameter that is usually small.
 %
-By this way, GraphSAGE limits neighborhood sizes of vertices in the sampled subgraph, especially high-degree vertices.
+In this way, GraphSAGE limits neighborhood sizes of vertices in the sampled subgraph, especially high-degree vertices.
 
@@
 %
-For each mini-batch, it randomly pick $N$ clusters to form the sampled subgraph, where $N$ is the hyper-parameter.
+For each mini-batch, it randomly picks $N$ clusters to form the sampled subgraph, where $N$ is the hyper-parameter.
 
@@
 %
-For transductive learning, the input graphs of training and inference are same.
+For transductive learning, the input graphs of training and inference are the same.
 %
@@
 %
-In the node classification task, it splits the vertices in the test set into batches accoding to a given batch size.
+In the node classification task, it splits the vertices in the test set into batches according to the given batch size.
 %

### 2020-12-26 NEUROC/sec4-experiments.tex
更新Section 4.

@@
 
-According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexity of the messaging function $\phi^l$ and the updating function $\gamma^l$ were linear to each hyper-parameter separately.
+According to \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, the time complexity of the messaging function $\phi$ and the updating function $\gamma$ was linear to each hyper-parameter separately.
 %
-If we increased one of the hyper-parameters and fix the others, the training/inference time should increase linearly in theory.
+If we increased one of the hyper-parameters and fixed the others, the training time should increase linearly in theory.
 
-To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the \emph{training} time of the four GNNs in \figurename~\ref{fig:exp_absolute_training_time}.
+To verify the time complexity analysis in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex}, we first compared the {training} time of the four GNNs in \figurename~\ref{fig:exp_absolute_training_time}.
 %
@@
 %
-Since the real-world graphs had more edges than vertices ($|\mathcal{E}| > |\mathcal{V}|$), the time complexity of the edge calculation stage affected more than the vertex calculation stage.
+Since the real-world graphs had more edges than vertices ($|\mathcal{E}| > |\mathcal{V}|$), the time complexity of the edge calculation stage affected more obviously than the vertex calculation stage.
 %
@@
 
-\begin{figure}[htb]
+\begin{figure}[H]
     \centering
@@
     \includegraphics[width=0.3\textwidth]{figs/experiments/exp_absolute_training_time_comparison_com-amazon.pdf}
-    \caption{Distribution of the wall-clock training time of 50 epochs on different datasets. GaAN crashed due to out of memory exception on the \texttt{cph} dataset.}
+    \caption{Distribution of the wall-clock training time of 50 epochs on different datasets. GaAN crashed due to the out of memory exception on the \texttt{cph} dataset.}
     \label{fig:exp_absolute_training_time}
@@
 To further evaluate effects of hyper-parameters on training time, we measured the training time of each GNN with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn} to \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN during training.}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN during training.}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GAT during training.}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
-\end{figure}
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN during training.}
-    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
-\end{figure}
 
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN in training.}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN in training.}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
+\end{figure}
+
 For GAT, we modified the number of heads $K$ and the dimension of each head $d_{head}$ in the GAT layer 0.
@@
 \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat} confirms the theoretical analysis.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GAT in training.}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
+\end{figure}
 
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN in training.}
+    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
+\end{figure}
+
 \subsubsection{Effects on Inference Time}
@@
 %
-Taking GGNN as an exmple, \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} shows the effects of hyper-parameters on the inference time of GGNN.
+Taking GGNN as an exmple, \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} shows the effects of hyper-parameters on inference time of GGNN.
 %
-By cross-comparing \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}, the effects of hyper-parameters on inference time and training time were the same: as $dim(\MyVec{h}^1_x)$ increased, the vertex and edge calculation time both grew linearly when $dim(\MyVec{h}^1_x)$ was large enough.
+By cross-comparing \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}, the trends of inference time and training time were the same: as $dim(\MyVec{h}^1_x)$ increased, the vertex and edge calculation time both grew linearly when $dim(\MyVec{h}^1_x)$ was large enough.
 %
@@
     \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn.pdf}
-    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN during inference.}
+    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN in inference.}
     \label{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn}
@@
 %
-As the hidden vectors $\MyVec{h}^1_x$ consumed a small proportion of memory in GaAN, the growth in the memory usage was not noticeable until $dim(\boldsymbol{h}^1_x)$ was large enough.
+As the hidden vectors $\MyVec{h}^1_x$ in GaAN consumed a small proportion of memory, the growth in the memory usage was not noticeable until $dim(\boldsymbol{h}^1_x)$ was large enough.
 %
@@
 %
-Taking GAT as an example, the peak memory usage during inference grew linearly as the values of hyper-parameters increased, as shown in \figurename~\ref{fig:exp_inference_hyperparameter_memory_usage_gat}.
+Taking GAT as an example, \figurename~\ref{fig:exp_inference_hyperparameter_memory_usage_gat} shows that the peak memory usage during inference grew linearly with the increasing hyper-parameters.
 %
@@
     \subfloat[GCN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gcn.pdf}}
-    \subfloat[GGNN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.pdf}}\\
+    \subfloat[GGNN]{\includegraphics[width=0.25\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_ggnn.pdf}}
     \subfloat[GAT\label{fig:exp_hyperparameter_memory_usage_gat}]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_hyperparameter_on_memory_usage_gat.pdf}}\\
@@
 %
-The relationship between model complexity and accuracy was complex.
+The relationships between model complexity and accuracy were complex.
 %
@@
 
-To evaluate the effects of hyper-parameters on the accuracy, we measured the accuracy of the typical GNNs with varying hyper-parameters.
-%
-\figurename~\ref{fig:exp_hyperparameter_accuracy} shows the experimental results.
+To evaluate the effects of hyper-parameters on accuracy, we measured the accuracy of the typical GNNs with varying hyper-parameters in \figurename~\ref{fig:exp_hyperparameter_accuracy}.
 %
@@
 %
-Since GGNN had high model complexity (with 13 weight matrices/vectors to train), GGNN might occur overfitting in those cases.
+Since the model complexity of GGNN was high (with 13 weight matrices/vectors to train), GGNN might occur overfitting in those cases.
 %
@@
 %
-The experimental results indicated that the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was too low.
+The experimental results indicated that the accuracy of the GNNs was often low when $dim(\MyVec{h}_x^1)$ (for GCN/GGNN/GaAN) or $d_{head}$ (for GAT) was very low.
 %
@@
 
-\figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} further compares the best accuracy that each GNN could achieve on different datasets.
+\figurename~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast} further compares the best accuracy that every GNN achieved on different datasets.
 %
-The best accuracy of the typical GNNs was very close.
+The best accuracy of the four GNNs was very close.
 %
 %
-It was also close to the accuracy reported in their original references [34, 31].
+It was also close to the accuracy reported in \cite{}.
 %

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex

@@
 %
-We have made extensive modifications to our manuscript.
+We have made extensive modifications to our manuscript, including adding more experiments and improving the presentation.
 %
-In the following we address their concerns point by point.
+In the following, we first summarize the major changes we made.
 %
@@
 
-TODO
+\begin{enumerate}
+\item According to Reviewer 1's comments, we have added experiments on the performance bottleneck analysis of GNN inference.
+%
+We added experiments on how the hyper-parameters of GNNs affect the elapsed time and the memory usage of inference in Section 4.1.2 ``Effects on Inference Time'' and Section 4.1.3 ``Effects on Peak Memory Usage'', respectively.
+%
+We added time breakdown analysis of GNN inference in Section 4.2.4.
+%
+We also presented the memory usage analysis of GNN inference in Section 4.3.2.
+%
+The performance bottlenecks of sample-based inference were analyzed in Section 4.4.2.
+
+\item According to the Reviewer 2's comments, we have added experiments on how the model complexity and the sampling techniques affect the accuracy of GNNs.
+%
+Specifically, we evaluated the effects of hyper-parameters of GNNs on accuracy in Section 4.1.4.
+%
+We also compared the accuracy of the four typical GNNs in that section.
+%
+We analyzed the effects of the sampling techniques on accuracy in Section 4.4.3.
+
+\item We have adjusted the abstract, Section 1 ``Introduction'', and Section 5 ``Insights'' according to the new findings on inference time and accuracy.
+
+\item We have polished the presentation of our manuscript.
+%
+We unified the symbol usage through the manuscript and added a table to summarize the frequently-used symbols.
+%
+We improved the description of the sub-layer concept in Section 2.1 and Section 2.2.
+%
+We also replotted some figures to improve readability.
+
+\end{enumerate}
+
+We then respond to the concerns of reviewers point by point as follows.
 
@@
 
-    In order to facilitate readers to quickly locate the meaning of  symbols, we have added Table~\ref{tab:symbols} at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised manuscript.
+    In order to facilitate readers to quickly locate the meaning of  symbols, we have added Table 1 at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised manuscript.
 
@@
     %
-    Our observations are similar to \cite{zeng2020_graphsaint}.
+    Our observations are similar to [\cite{zeng2020_graphsaint}].
     %
@@
     %
-    We add experimental results on how the hyper-parameters of GNNs affect the accuracy.
+    We add discussion on how the hyper-parameters of GNNs affect the accuracy.
     %
@@
     %
-    We presented the experimental results in a new subsection Section 4.4.4 ``Effects on Accuracy''.
+    We present the experimental results and related discussion in a new subsection Section 4.4.3 ``Effects on Accuracy''.
 \end{reply}
 
-\bibliographystyle{elsarticle}
+\bibliographystyle{apalike}
 \bibliography{../gnnref.bib}

### 2020-12-26 NEUROC/sec7-conclusion.tex

--- 2020-08-25 Manuscript/sec7-conclusion.tex
@@
 
-\section*{Acknowledgement}
+\section*{Acknowledgements}
 
-This work is funded in part by National Key R\&D Program of China [grant number 2019YFC1711000]; China NSF Grants [grant number U1811461]; Jiangsu Province Industry Support Program [grant number BE2017155]; Natural Science Foundation of Jiangsu Province [grant number BK20170651]; Collaborative Innovation Center of Novel Software Technology and Industrialization; and the program B for Outstanding PhD candidate of Nanjing University.
+This work is funded in part by the National Key R\&D Program of China [grant number 2019YFC1711000], the China NSF Grants [grant number U1811461, 62072230], and the Collaborative Innovation Center of Novel Software Technology and Industrialization; and the program B for Outstanding PhD candidate of Nanjing University.

### 2020-12-26 NEUROC/sec3-experiment-design.tex
修改了sec2
grammer了sec3的内容

@@
 We trained GNNs in the semi-supervised learning setting.
-All vertices and their input feature vectors were used, but only a part of the vertices were attached with labels during the training and they were used to calculate the loss and gradients.
-The vertices with unseen labels were used in the evaluation phase to evaluate the accuracy of the current parameters.
+All vertices and their input feature vectors were used, but only a part of the vertices was attached with labels during the training and they were used to calculate the loss and gradients.
+The vertices with unseen labels were used in the evaluation and inference phase to evaluate the accuracy of GNN models.
 %Since model parameters of GNNs were not restricted by the topological structure of $\mathcal{G}$, the model learned from the semi-supervised learning can directly extrapolate to unseen vertices.
@@
 %
-For directed graphs, PyG converts them into undirected ones during data loading.
+For directed graphs, PyG converted them into undirected ones during data loading.
 %
@@
 %
-For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
+For an undirected graph, the average degree was defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
 %
@@
 %
-Input feature vectors of random graphs were random dense vectors with the dimension of 32.
+Input feature vectors of random graphs were random dense vectors with a dimension of 32.
 %
@@
 The structure was popular in the experimental evaluation of GCN \cite{kipf2017_gcn}, GAT \cite{huang2018_gat}, and GaAN \cite{zhang2018_gaan}.
-Since a GGNN layer requires the input and output hidden vectors have the same dimension, we added two multi-layer perceptron (MLP) layers to transform the dimensions of the input/output feature vectors: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
+Since a GGNN layer required the input and output hidden vectors had the same dimension, we added two multi-layer perceptron (MLP) layers to transform the dimensions of the input/output feature vectors: Input Layer $\rightarrow$ MLP $\rightarrow$ GGNN Layer 0 $\rightarrow$ GGNN Layer 1 $\rightarrow$ MLP $\rightarrow$ Softmax Layer.
 Unless otherwise specified, we stored the dataset and the model parameters on the GPU side.
@@
 %
-The answers to those questions will give us a more comprehensive view of performance characteristics of GNN training.
+The answers to those questions would give us a more comprehensive view of the performance characteristics of GNN training.
 
@@
 
-    \item[Q1] \emph{How do the hyper-parameters affect the training/inference time, memory usage and accuracy of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
+    \item[Q1] \emph{How did the hyper-parameters affect the training/inference time, memory usage and accuracy of a GNN?} (Section~\ref{sec:effects_of_hyper-parameters_on_performance})
 
@@
           %
-          They also affect the accuracy of a GNN.
+          They also affected the accuracy of a GNN.
           %
-          Larger hyper-parameter values usually mean more model parameters and more complex models.
+          Larger hyper-parameter values usually meant more model parameters and more complex models.
           %
@@
 
-    \item[Q2] \emph{Which stage is the most time-consuming stage in GNN training and inference?} (Section~\ref{sec:training_time_breakdown})
+    \item[Q2] \emph{Which stage was the most time-consuming stage in GNN training and inference?} (Section~\ref{sec:training_time_breakdown})
 
@@
           %
-          Optimizing its implementation will significantly reduce the training time.
+          Optimizing its implementation would significantly reduce the training time.
           %
-          For GNN inference, we conducted similar experimental analysis.
+          For GNN inference, we conducted a similar experimental analysis.
           %
@@
 
-    \item[Q3] \emph{Which consumes most of memory in GNN training and inference?} (Section~\ref{sec:memory_usage_analysis})
+    \item[Q3] \emph{Which consumed most of memory in GNN training and inference?} (Section~\ref{sec:memory_usage_analysis})
 
-          The limited memory capacity of a GPU prevents us from training GNNs on big graphs.
+          The limited memory capacity of a GPU prevented us from training GNNs on big graphs.
           %
@@
           %
-          Reducing its memory usage will enable us to train GNNs on bigger graphs under the same memory capacity.
+          Reducing its memory usage would enable us to train GNNs on bigger graphs under the same memory capacity.
 
-    \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training?
-What is the performance bottleneck of sample-based inference?
-Does the use of sampling techniques in training affect the model accuracy?
+    \item[Q4] \emph{Could sampling techniques remove performance bottlenecks in GNN training?
+What was the performance bottleneck of sample-based inference?
+Did the use of sampling techniques in training affect model accuracy?
 } (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
 
-          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training of a batch.
+          Theoretically, sampling techniques could significantly reduce the number of graph neurons that participated in the training of a batch.
           %
@@
           %
-          The model accuracy of GNNs may also be affected.
+          The model accuracy of GNNs might also be affected.
           %
-          To validate effectiveness of sampling techniques, we measured the training time, peak memory usage and test accuracy under different batch sizes.
+          To validate the effectiveness of sampling techniques, we measured the training time, peak memory usage, and test accuracy under different batch sizes.
           %
-          If sampling techniques are effective, they will be the keys to conduct GNN training on very big graphs.
+          If sampling techniques are effective, they would be the keys to conduct GNN training on very big graphs.
           %
-          If they are not effective, we want to find out which impairs its efficiency.
+          If they were not effective, we wanted to find out which impaired their efficiency.
           %

### 2020-12-26 NEUROC/sec4-experiments.tex
更新正文。

@@
 %
-It was also close to the accuracy reported in \cite{}.
+It was also close to the accuracy reported in \cite{shchur2018_pitfall_of_gnn, zeng2020_graphsaint}.
 %
@@
 %
-Fixing other hyper-parameters, each hyper-parameter itself affected the training time and the memory usage of a GNN Layer \emph{in a linear way}.
+Fixing other hyper-parameters, each hyper-parameter itself affected the training/inference time and the memory usage of a GNN layer \emph{in a linear way}.
 %
-Algorithm engineers could adjust hyper-parameters according to the time complexity to avoid explosive growth in the training/inference time and memory usage.
+Algorithm engineers could adjust hyper-parameters according to the complexity analysis to avoid explosive growth in training/inference time and memory usage.
 %
-The accuracy of GNNs was much more sensitive to the dimension of hidden vectors/heads than the other hyper-parameters.
+The accuracy of GNNs was much more sensitive to the dimensions of hidden vectors/heads than the other hyper-parameters.
 %
@@
 %
-There was no clear winner for all datasets.
+Simple GNN models (such as GCN) could achieve good accuracy with proper hyper-parameter settings.
 
-\subsection{Training/Inference Time Breakdown}
-\label{sec:training_time_breakdown}
+\subsection{Time Breakdown Analysis}
+\label{sec:time_breakdown_analysis}
 
-To find out which stage/step dominated the training time, we decomposed the training time and analyzed performance bottlenecks level by level.
+To find out which stage/step dominated the training/inference time, we decomposed the training/inference time and analyzed performance bottlenecks level by level.
+%
+We first analyzed the training time in Section~\ref{sec:time_breakdown_analysis_layer_level} to Section~\ref{sec:time_breakdown_analysis_operator_level}.
+%
+The similarities and differences between training and inference were analyzed in Section~\ref{sec:time_breakdown_analysis_inference}.
 
 \subsubsection{Layer Level}
+\label{sec:time_breakdown_analysis_layer_level}
 
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4.6cm]{figs/experiments/exp_layer_time_proportion_gcn.pdf}}
+    \subfloat[GCN\label{fig:exp_vertex_edge_cal_proportion_gcn}]{\includegraphics[height=4.6cm]{figs/experiments/exp_layer_time_proportion_gcn.pdf}}
     \subfloat[GGNN]{\includegraphics[height=4.6cm]{figs/experiments/exp_layer_time_proportion_ggnn.pdf}}\\
@@
 
-Each GNN layer was further divided into the vertex and the edge calculation stages.
+Each GNN layer was further divided into the vertex and edge calculation stages.
 %
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
+    \subfloat[GCN\label{fig:exp_avg_degree_on_vertex_edge_cal_time_gcn}]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
     \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_ggnn.pdf}}\\
@@
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_avg_degree_on_vertex_edge_cal_time_gaan.pdf}}
-    \caption{Effects of the average degree on the time proportion of the edge/vertex calculation. Graphs were generated with the R-MAT generator by fixing the number of vertices as 50,000. }
+    \caption{Effects of average degrees on the vertex/edge calculation time. Graphs were generated with the R-MAT generator by fixing the number of vertices as 50,000. }
     \label{fig:exp_avg_degree_on_vertex_edge_cal_time}
@@
 
-The results indicate that \emph{the performance bottlenecks of the edge calculation stage depend on the complexity of the messaging function $\phi^l$}.
+The results indicate that \emph{the performance bottlenecks of the edge calculation stage depend on the complexity of the messaging function $\phi$}.
 %
-When the time complexity of $\phi^l$ was high, the messaging step was the performance bottleneck.
+When the time complexity of $\phi$ was high, the messaging step was the performance bottleneck.
 %
@@
     \centering
-    \subfloat[GCN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gcn.pdf}}
-    \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gat.pdf}}
-    \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_edge_calc_decomposition_gaan.pdf}}
+    \subfloat[GCN\label{fig:exp_edge_calc_decomposition_gcn}]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_edge_calc_decomposition_gcn.pdf}}
+    \subfloat[GGNN]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_edge_calc_decomposition_ggnn.pdf}}\\
+    \subfloat[GAT]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_edge_calc_decomposition_gat.pdf}}
+    \subfloat[GaAN]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_edge_calc_decomposition_gaan.pdf}}
     \caption{Training time breakdown of the edge calculation stage.}
@@
 \subsubsection{Operator Level}
+\label{sec:time_breakdown_analysis_operator_level}
 
@@
 %
-\figurename~\ref{fig:exp_top_basic_ops} shows the top-5 time-consuming basic operators in each GNN, averaged over all datasets.
+\figurename~\ref{fig:exp_top_basic_ops} shows the top-5 time-consuming basic operators of training each GNN, averaged over all datasets.
 
@@
     \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gat.pdf}}
+    \subfloat[GAT\label{fig:exp_top_basic_ops_gat}]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gat.pdf}}
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_top_basic_ops_gaan.pdf}}
-    \caption{Top 5 time-consuming basic operators of typical GNNs. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
+    \caption{Top 5 time-consuming basic operators in training. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
     \label{fig:exp_top_basic_ops}
@@
 
-\subsubsection{Performance Bottlenecks in Inference}
+\subsubsection{Comparing Inference and Training}
+\label{sec:time_breakdown_analysis_inference}
 
@@
 %
-Taking GCN as an example, \figurename~\ref{fig:inference_analysis_on_layer_edge_level_of_gcn} shows the results of GCN inference on the \emph{layer} level and the \emph{step} level.
+Taking GCN as an example, \figurename~\ref{fig:inference_analysis_of_gcn} shows the time breakdowns of GCN inference on the \emph{layer} level and \emph{step} level of the edge calculation.
 %
-By cross-comparing \figurename~\ref{fig:exp_vertex_edge_cal_proportion}(a), 
-\figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time}(a), and \figurename~\ref{fig:exp_edge_calc_decomposition}(a),
-we could conclude that the time breakdowns were very similar.
+By cross-comparing \figurename~\ref{fig:exp_vertex_edge_cal_proportion_gcn} with \figurename~\ref{fig:inference_analysis_of_gcn_layer_level}, 
+\figurename~\ref{fig:exp_avg_degree_on_vertex_edge_cal_time_gcn} with \figurename~\ref{fig:inference_analysis_of_gcn_avg_degree}, and \figurename~\ref{fig:exp_edge_calc_decomposition_gcn} with \figurename~\ref{fig:inference_analysis_of_gcn_edge_level}, the time breakdowns of training and inference were very similar.
 %
 For the other GNNs, we observed similar phenomena.
-%
 
-% GCN Inference结果对比图
 \begin{figure}[H]
     \centering
-    \subfloat[Layer Level]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-    \subfloat[Effects of the average degree]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}
-    \subfloat[Edge Level]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
-    \caption{Time breakdowns on the layer level and edge level, and effects of average degree on the edge/vertex calculation of GCN inference.}
-    \label{fig:inference_analysis_on_layer_edge_level_of_gcn}
-\end{figure}
-
-% 绝对时间对比图
-\begin{figure}[H]
-    \centering
-    \subfloat[\texttt{amc}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_amazon-computers.pdf}}
-    \subfloat[\texttt{amp}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_amazon-photo.pdf}}
-    \subfloat[\texttt{fli}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
-    \caption{Wall-clock inference time on different datasets.}
-    \label{fig:compare_wall_clock_time_of_training_and_inference}
+    \subfloat[Layer level\label{fig:inference_analysis_of_gcn_layer_level}]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_layer_time_proportion_gcn.pdf}}
+    \subfloat[Effects of average degrees\label{fig:inference_analysis_of_gcn_avg_degree}]{\includegraphics[width=0.4\columnwidth]{figs/experiments/exp_inference_full_avg_degree_on_vertex_edge_cal_time_gcn.pdf}}\\
+    \subfloat[Step level of the edge calculation stage\label{fig:inference_analysis_of_gcn_edge_level}]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_edge_calc_decomposition_gcn.pdf}}
+    \caption{Time breakdowns of GCN inference.}
+    \label{fig:inference_analysis_of_gcn}
 \end{figure}
@@
 
+\begin{figure}[H]
+    \centering
+    \subfloat[\texttt{amc}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_amazon-computers.pdf}}
+    \subfloat[\texttt{amp}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_amazon-photo.pdf}}
+    \subfloat[\texttt{fli}]{\includegraphics[width=0.3\columnwidth]{figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
+    \caption{Wall-clock inference time on different datasets.}
+    \label{fig:compare_wall_clock_time_of_training_and_inference}
+\end{figure}
+
 The top time-consuming basic operators of training and inference also showed a certain degree of difference.
@@
 %
-Figure~\ref{fig:exp_inference_top_basic_ops} in the response compares the top 5 time-consuming basic operators in inference.
+Figure~\ref{fig:exp_inference_top_basic_ops} shows the top 5 time-consuming basic operators in inference.
 %
@@
 %
-For GGNN, \texttt{index} operator in the prediction layer also became one of the top 5 time-consuming basic operators.
+For GGNN, \texttt{index} operator in the prediction layer also became a time-consuming basic operators.
 %
@@
 %
-For GAT, the \texttt{input\_put\_impl} operator (used in the backward phase) in Figure~\ref{fig:exp_top_basic_ops}(c) was replaced by the \texttt{scatter\_add} operator used in the forward edge calculation in Figure~\ref{fig:exp_inference_top_basic_ops}(c).
+For GAT, the \texttt{input\_put\_impl} operator (used in the backward phase) in Figure~\ref{fig:exp_top_basic_ops_gat} was replaced by the \texttt{scatter\_add} operator used in the forward edge calculation in Figure~\ref{fig:exp_inference_top_basic_ops_gat}.
 %
@@
     \subfloat[GGNN]{\includegraphics[height=4cm]{figs/experiments/exp_inference_full_top_basic_ops_ggnn.pdf}}\\
-    \subfloat[GAT]{\includegraphics[height=4cm]{figs/experiments/exp_inference_full_top_basic_ops_gat.pdf}}
+    \subfloat[GAT\label{fig:exp_inference_top_basic_ops_gat}]{\includegraphics[height=4cm]{figs/experiments/exp_inference_full_top_basic_ops_gat.pdf}}
     \subfloat[GaAN]{\includegraphics[height=4cm]{figs/experiments/exp_inference_full_top_basic_ops_gaan.pdf}}
-    \caption{Top 5 time-consuming basic operators of typical GNNs. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
+    \caption{Top 5 time-consuming basic operators in inference. The time proportion of each basic operator was averaged over all datasets with the error bar indicating the maximum and the minimum.}
     \label{fig:exp_inference_top_basic_ops}
@@
 
-\paragraph{Summary}
-% TODO:
+\paragraph{Summary of Time Breakdown Analysis}
+
 The GNN training/inference was suitable for GPUs.
 %
-\emph{The edge calculation stage was the main performance bottleneck in most cases}, except for training GNNs with high vertex calculation complexity on low-average-degree graphs.
+{The edge calculation stage was the main performance bottleneck in most cases}, except for processing GNNs with high vertex calculation complexity on low-average-degree graphs.
 %
-The performance bottleneck in the edge calculation stage depended on the time complexity of the messaging function $\phi$.
+The performance bottlenecks in the edge calculation stage depended on the time complexity of the messaging function $\phi$.
 %
-If the time complexity of $\phi$ was {high}, {$\phi$} dominated the training time of the edge calculation stage.
+If the time complexity of $\phi$ was {high}, {$\phi$} dominated the training/inference time of the edge calculation stage.
 %
@@
 %
-Otherwise, the {collection step} and the {aggregation step} dominated the training time.
+Otherwise, the {collection step} and the {aggregation step} dominated the training/inference time.
 %
@@
 \label{sec:memory_usage_analysis}
+
+\paragraph{Training}
 
@@
 %
-According to the experimental results in Section~\ref{sec:training_time_breakdown}, if the average degree became lower, the proportion of the training time spent on the vertex calculation stage would become higher, especially for GGNN.
+According to the experimental results in Section~\ref{sec:time_breakdown_analysis}, if the average degree became lower, the proportion of the training time spent on the vertex calculation stage would become higher, especially for GGNN.
 

### 2020-12-26 NEUROC/sec3-experiment-design.tex
更新了sec3和4

@@
 
-    \item[Q4] \emph{Could sampling techniques remove performance bottlenecks in GNN training?
-What was the performance bottleneck of sample-based inference?
+    \item[Q4] \emph{Could sampling techniques remove performance bottlenecks in GNN training/inference?
 Did the use of sampling techniques in training affect model accuracy?
@@
           %
-          To validate the effectiveness of sampling techniques, we measured the training time, peak memory usage, and test accuracy under different batch sizes.
+          To validate the effectiveness of sampling techniques, we measured the training/inference time, peak memory usage, and test accuracy under different batch sizes.
           %
-          If sampling techniques are effective, they would be the keys to conduct GNN training on very big graphs.
+          If sampling techniques are effective, they would be the keys to conduct GNN training/inference on very big graphs.
           %
@@
           %
-          % TODO: 补充Sample-based Inference的介绍
 

### 2020-12-26 NEUROC/sec4-experiments.tex
更新了sec3和4

@@
 
-\paragraph{Memory Usage of Inference}
+\paragraph{Comparing Inference and Training}
 
-Figure~\ref{fig:exp_inference_memory_expansion_ratio} shows the memory expansion ratios of typical GNNs during inference.
+Figure~\ref{fig:memory_usage_analysis} shows the memory expansion ratios of typical GNNs during inference.
 %
@@
    \caption{Memory expansion ratios of typical GNNs in Inference.}
-   \label{fig:exp_inference_memory_expansion_ratio}
+   \label{fig:memory_usage_analysis}
 \end{figure}
 
-\paragraph{Summary}
-%TODO: 
+%
+We also did experiments about the effects of input feature dimension, average degrees, and the number of vertices on GNN inference memory usage.
+%
+The results were similar to the GNN training phase.
+%
+
+\paragraph{Summary of Memory Usage Analysis}
+%
 The \emph{high} memory expansion ratio severely restricted the data scalability of GNN training and inference.
@@
 %
-To reduce the memory usage of GNN training, optimizations should focus on reducing memory footprints of the edge calculation stage.
+To reduce the memory usage of GNN training and inference, optimizations should focus on reducing memory footprints of the edge calculation stage.
 
@@
 \paragraph{Summary of Sampling Techniques}
-% TODO:
+% 
 The sampled subgraphs had lower average degrees than the original graph.
 %
-With small batch sizes, the sampling techniques could significantly reduce the training time per batch and the peak memory usage.
+With small batch sizes, the sampling techniques could significantly reduce the training/inference time per batch and the peak memory usage.
 %
@@
 %
-The time spent on the sampling phase and the data transferring phase even exceeded the training phase.
+The time spent on the sampling phase and the data transferring phase even exceeded the training/inference phase.

### 2020-12-26 NEUROC/sec5-insights.tex
更新了sec5

@@
 
-Through the extensive experiments, we propose the following key findings and suggestions for how to optimize the performance of the GNN training.
+Through the extensive experiments, we propose the following key findings and suggestions for how to optimize the performance of the GNN training/inference.
 
@@
     \item \emph{The computational cost of a GNN layer is mainly affected by the dimensions of the input and the output hidden feature vectors.}
-          Theoretically and empirically, the training time and the memory usage of a GNN layer both increase \emph{linearly} with the dimensions of the input/output hidden feature vectors separately.
+          Theoretically and empirically, the training/inference time and the memory usage of a GNN layer both increase \emph{linearly} with the dimensions of the input/output hidden feature vectors separately.
           GNNs are friendly to high-dimensional scenarios. 
-          Algorithm engineers can use high-dimensional feature vectors to improve the expressive power of a GNN without worrying exponential growth in the training time and memory usage
+          Algorithm engineers can use high-dimensional feature vectors to improve the expressive power of a GNN without worrying exponential growth in the training/inference time and memory usage
     \item \emph{Performance optimizations should focus on improving the efficiency of the edge calculation stage.}
@@
                     The fused operator calculates the aggregated vectors directly from the input hidden feature vectors, minimizing the memory footprints and overlapping the memory accessing with computation.
-                    In this way, it significantly reduces the training time of GNNs with low edge calculation complexity (like GCN) \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph}.
+                    In this way, it significantly reduces the training/inference time of GNNs with low edge calculation complexity (like GCN) \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph}.
                     However, the applicable condition of the fused operator is very restricted.
@@
 \end{itemize}
-    \item \emph{The high memory usage caused by the intermediate results of the edge calculation stage limits the data scalability of the GNN training.}
+    \item \emph{The high memory usage caused by the intermediate results of the edge calculation stage limits the data scalability of the GNN training/inference.}
           The memory expansion ratios of the typical GNNs are very high, making GPUs unable to handle big graphs.
           One solution is to distribute the dataset among several GPUs and frequently swap parts of the dataset between GPUs and the main memory \cite{ma2019_neugraph}.
-          Another possible solution \cite{chen2016_training_deep} comes from the deep neural network training.
+          Another possible solution \cite{chen2016_training_deep} comes from the deep neural network training. % checkpoints only work for GNN training.
           It only checkpoints key intermediate results during the forward propagation and re-calculates the missing results on demand during the backpropagation.
-          Implementing the checkpoint mechanism in the GNN training is another potential optimization.
+          Implementing the checkpoint mechanism is another potential optimization for GNN training.
 
-    \item \emph{Sampling techniques can significantly reduce the training time and memory usage, but its implementation is still inefficient}.
+    \item \emph{Sampling techniques can significantly reduce the training/inference time and memory usage, but its implementation is still inefficient}.
           The sampling techniques are effective under small batch sizes.

### 2020-12-26 NEUROC/sec7-conclusion.tex
更新了sec7

@@
 
-In this work, we systematically explore the performance bottleneck in graph neural network training. 
+In this work, we systematically explore the performance bottleneck in graph neural network training and inference. 
 We model the existing GNNs with the message-passing framework. 
@@
 The experimental results validate our complexity analysis. Fixing other hyper-parameters, the training time and the memory usage increase linearly with each hyper-parameter of the four GNNs. 
-To find out the performance bottleneck in the training time, we decompose the training time per epoch on different levels. 
-The training time breakdown analysis indicates that the edge calculation stage and its related basic operators are the performance bottleneck for most GNNs. 
+To find out the performance bottleneck in the training/inference time, we decompose the training/inference time per epoch on different levels. 
+The time breakdown analysis indicates that the edge calculation stage and its related basic operators are the performance bottleneck for most GNNs. 
 Moreover, the intermediate results produced by the edge calculation stage cause high memory usage, limiting the data scalability. 
@@
 Our analysis indicates that the edge calculation stage should be the main target of optimizations. 
-Reducing its memory usage and improving its efficiency can significantly improve the performance of the GNN training. 
+Reducing its memory usage and improving its efficiency can significantly improve the performance of the GNN training and inference. 
 Based on the analysis, we propose several potential optimizations for the GNN frameworks. 
-We believe that our analysis can help developers to have a better understanding of the characteristics of GNN training.
+We believe that our analysis can help developers to have a better understanding of the characteristics of GNN training and inference.
 

### 2020-12-26 NEUROC/ms.tex
增加了Motivation各个数据集的代码
回复R1Q2.
更新R1P1
回复R1Q1.
更新Reviewer2
更新了摘要和Introduction

@@
-%! TEX root = ms.tex
-%! TEX program = pdflatex
+% !TEX program = pdflatex
 \documentclass{elsarticle}
@@
 \geometry{left=3cm, right=3cm, top=2.5cm, bottom=2.5cm} 
-\usepackage{lineno,hyperref}
-\usepackage{amsmath, amsthm}
+\usepackage{lineno}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage[colorlinks=true, allcolors=red]{hyperref}
+\usepackage{amsmath, amsthm, amsfonts}
 \usepackage{relsize}
 \usepackage{booktabs}
+\usepackage{multirow}
 \usepackage{makecell}
@@
 \usepackage{float}
+\usepackage{times}
 \modulolinenumbers[5]
 \bibliographystyle{elsarticle-num}
+
+% Vector
+\newcommand{\MyVec}[1]{\boldsymbol{#1}}
+% Matrix
+\newcommand{\MyMat}[1]{\boldsymbol{#1}}
+% Vectors with hat
+\newcommand{\hvec}[1]{\hat{\boldsymbol{h}}_{#1}}
+% Model parameters
+\newcommand{\Param}[1]{\textcolor{blue}{#1}}
 
@@
 
-	\title{Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs}
+	\title{Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs}
     \author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Rong Gu$^*$ \corref{correspondingauthor1}, Yihua Huang$^*$ \corref{correspondingauthor2}}
@@
 		Recently, various graph neural network libraries have emerged.They make the development of GNNs convenient, but their performance on large datasets is not satisfying. 
-		In this work, we analyze the performance bottleneck in training GNN with GPUs empirically. 
+		In this work, we analyze the performance bottleneck in training/inferring GNN with GPUs empirically. 
 		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts. 
@@
 
-\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
+%\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
 \bibliography{gnnref.bib}

### 2020-12-26 NEUROC/sec1-introduction.tex
更新了摘要和Introduction

@@
 
-To explore the essential performance bottleneck in the GNN training, we conduct a range of experimental analysis in deep in this work. 
-We focus on the efficiency bottleneck of GNN training instead of accuracy. 
+To explore the essential performance bottleneck in the GNN training/inference, we conduct a range of experimental analysis in deep in this work. 
+We focus on the efficiency bottleneck of GNN training/inference.
 We model the GNNs with the message-passing framework that decomposes a GNN layer into two parts: the vertex calculation and the edge calculation.  
@@
 We implement them with PyG and evaluate their efficiency with six real-world datasets on a GPU.
-We identify the most time-consuming stage in the GNN training by decomposing the training time per epoch from the layer level to the operator level.
-We also analyze the memory usage during the training to discover the main factor that limits the data scalability of GNN training on GPUs. 
+We identify the most time-consuming stage in the GNN training/inference by decomposing the training/inference time per epoch from the layer level to the operator level.
+We also analyze the memory usage during the training/inference to discover the main factor that limits the data scalability of GNN training/inference on GPUs. 
 Finally, we evaluate whether or not the sampling techniques affect the performance bottleneck. 
@@
 \begin{itemize}
-    \item \textbf{The training time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.}
-    Fixing other hyper-parameters, the training time and the memory usage of a GNN layer increase linearly as the input/output dimensions.
+    \item \textbf{The training/inference time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.}
+    Fixing other hyper-parameters, the training/inference time and the memory usage of a GNN layer increase linearly as the input/output dimensions.
     \item \textbf{The edge-related calculation is the performance bottleneck for most GNNs.}
-    For GNNs with high edge calculation complexity, most of the training time is spent on conducting the messaging function for every edge. 
-    For GNNs with low edge calculation complexity, the message collection and aggregation consumes most of the training time.
-    \item \textbf{The high memory usage of the edge calculation is the main factor limiting the data scalability of GNN training.}
+    For GNNs with high edge calculation complexity, most of the training/inference time is spent on conducting the messaging function for every edge. 
+    For GNNs with low edge calculation complexity, the message collection and aggregation consumes most of the training/inference time.
+    \item \textbf{The high memory usage of the edge calculation is the main factor limiting the data scalability of GNN training/inference.}
     The edge calculation generates and caches many intermediate results. 
     They are an order of magnitude larger than the dataset itself. 
-    As GPUs have limited on-chip memory, the high memory consumption prevents us from training big graphs on GNNs.
-    \item \textbf{The sampling techniques can significantly reduce training time and memory usage.}
+    As GPUs have limited on-chip memory, the high memory consumption prevents us from training/inferring big graphs on GNNs.
+    \item \textbf{The sampling techniques can significantly reduce training/inference time and memory usage.}
     They are essential for training big graphs on GPUs. 
     However, the existing implementation is still inefficient. 
-    Under big batch sizes, the time spent on the sampling may exceed the time spent on the training. 
+    Under big batch sizes, the time spent on the sampling may exceed the time spent on the training/inference. 
     Under small batch sizes, the sampled graphs are also small, wasting the computing power of GPUs.
@@
 \begin{itemize}
-      \item To reduce training time, \textbf{optimizations should focus on improving the efficiency of the edge calculation}. 
+      \item To reduce training/inference time, \textbf{optimizations should focus on improving the efficiency of the edge calculation}. 
       One may consider developing optimized operators for the messaging step that is the major source of computing costs in the edge calculation.
@@
 \end{itemize}
-We hope that our analysis can help the developers of the GNN libraries/systems have a better understanding of the characteristics of GNN training and propose more targeted optimizations.
+We hope that our analysis can help the developers of the GNN libraries/systems have a better understanding of the characteristics of GNN training/inference and propose more targeted optimizations.
 

### 2020-12-26 NEUROC/sec3-experiment-design.tex
更新Section 3.

@@
           %
-          To evaluate their effects, we measured how the training/inference time per epoch, the peak memory usage (of the GPU), and the accuracy on the test set changed as we increased the values of the hyper-parameters.
+          To evaluate their effects, we measured how the training/inference time per epoch, the peak memory usage (of the GPU), and the test accuracy changed as we increased the values of the hyper-parameters.
           %
@@
 
-    \item[Q2] \emph{Which stage was the most time-consuming stage in GNN training and inference?} (Section~\ref{sec:training_time_breakdown})
+    \item[Q2] \emph{Which stage was the most time-consuming stage in GNN training and inference?} (Section~\ref{sec:time_breakdown_analysis})
 
-          We decomposed the GNN training time on different levels: the layer level, the edge/vertex calculation level, and the basic operator level.
+          We decomposed the GNN training/inference time on different levels: the layer level, the edge/vertex calculation level, and the basic operator level.
           %
-          On each level, we decomposed the training time of an epoch into several stages.
+          On each level, we decomposed the time of an epoch into several stages.
           %
@@
           %
-          For GNN inference, we conducted a similar experimental analysis.
+          %For GNN inference, we conducted a similar experimental analysis.
           %
-          We discussed the differences in performance characteristics between training and inference.
+          %We discussed the differences in performance characteristics between training and inference.
 
@@
 
-          The limited memory capacity of a GPU prevented us from training GNNs on big graphs.
+          The limited memory capacity of a GPU prevented us from conducting training/inference on big graphs.
           %
@@
     \item[Q4] \emph{Could sampling techniques remove performance bottlenecks in GNN training/inference?
-Did the use of sampling techniques in training affect model accuracy?
+Did the use of sampling techniques in training sacrifice model accuracy?
 } (Section~\ref{sec:effects_of_sampling_techniques_on_performance})
@@
           %
-          If sampling techniques are effective, they would be the keys to conduct GNN training/inference on very big graphs.
+          If sampling techniques were effective, they would be the keys to conduct GNN training/inference on very big graphs.
           %
           If they were not effective, we wanted to find out which impaired their efficiency.
-          %
 

### 2020-12-26 NEUROC/ms.tex
更新了sec1

@@
 		Recently, various graph neural network libraries have emerged.They make the development of GNNs convenient, but their performance on large datasets is not satisfying. 
-		In this work, we analyze the performance bottleneck in training/inferring GNN with GPUs empirically. 
+		In this work, we analyze the performance bottleneck in GNN training and inference with GPUs empirically. 
 		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts. 
 		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation. 
-		We breakdown their training time and memory usage, evaluate the effects of hyper-parameters, and assess the efficiency of the sampling techniques.
-		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training time and memory usage.
-		Future optimization can focus on it. The sampling techniques are essential for training big graphs on GPUs, but their current implementations still have room for improvement.
+		We breakdown their running time and memory usage, evaluate the effects of hyper-parameters, and assess the efficiency of the sampling techniques.
+		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training and inference time and memory usage.
+		Future optimization can focus on it. The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementations still have room for improvement.
 	\end{abstract}

### 2020-12-26 NEUROC/sec1-introduction.tex
更新了sec1

@@
 \begin{itemize}
-    \item \textbf{The training/inference time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.}
+    \item \textbf{The training and inference time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.}
     Fixing other hyper-parameters, the training/inference time and the memory usage of a GNN layer increase linearly as the input/output dimensions.
     \item \textbf{The edge-related calculation is the performance bottleneck for most GNNs.}
-    For GNNs with high edge calculation complexity, most of the training/inference time is spent on conducting the messaging function for every edge. 
+    For GNNs with high edge calculation complexity, most of the training and inference time is spent on conducting the messaging function for every edge. 
     For GNNs with low edge calculation complexity, the message collection and aggregation consumes most of the training/inference time.
@@
     They are an order of magnitude larger than the dataset itself. 
-    As GPUs have limited on-chip memory, the high memory consumption prevents us from training/inferring big graphs on GNNs.
+    As GPUs have limited on-chip memory, the high memory consumption prevents us from training and inferring big graphs on GNNs.
     \item \textbf{The sampling techniques can significantly reduce training/inference time and memory usage.}

### 2020-12-26 NEUROC/sec4-experiments.tex

@@
 \subsubsection{Effects on Accuracy}
+\label{sec:hyper_parameter_accuracy}
 
@@
 
-\paragraph{Comparing Inference and Training}
+\paragraph{Inference}
 
@@
 Since no intermediate results had to be cached during inference of GGNN, GAT, and GaAN,
-the memory expansion ratios of inference were much less than training for the three GNNs (\figurename~\ref{fig:exp_memory_expansion_ratio}).
+the MERs of inference were much less than training for the three GNNs (compared with \figurename~\ref{fig:exp_memory_expansion_ratio}).
 %
@@
 %
-We also did experiments about the effects of input feature dimension, average degrees, and the number of vertices on GNN inference memory usage.
+We also conducted experiments about the effects of input feature dimensions, average degrees, and the number of vertices on the memory usage of inference.
 %
-The results were similar to the GNN training phase.
+The results were similar to GNN training.
 %
@@
 %
-Thus, it affected the accuracy, training/inference time, and memory usage of GNNs simultaneously.
+Thus, it affected the accuracy, training/inference time, and memory usage simultaneously.
 
@@
 
-\subsubsection{Performance Bottlenecks Analysis}
+\subsubsection{Performance Bottlenecks in Sample-based Training}
 
 To find out performance bottlenecks of the sampling techniques, we decomposed the training/inference time per batch into three phases: \emph{sampling} on the CPU side, \emph{transferring} sampled subgraphs from the CPU side to the GPU side, and \emph{training/inference} with the sampled subgraphs on the GPU side.
-
-\paragraph{Training Time}
 
@@
 
-The sample-based inference was an effective technique to handle big graphs.
+The sample-based inference was an effective technique to conduct inference on big graphs.
 %
@@
 %
-To limit the memory usage during inference, the batch size used should be very small.
+To limit the memory usage during inference, the batch size used should be very small in inference.
 
@@
 
-   \caption{Characteristics of the sampled subgraphs produced by the inference sampler under different relative batch sizes.}
+   \caption{Sizes of sampled subgraphs produced by the inference sampler under different relative batch sizes.}
    \label{fig:sampled_graph_size}
@@
 %
-Improving its efficiency could significantly reduce the inference time.
+Improving its efficiency could significantly reduce the sample-based inference time.
 
@@
 
-Since the size of the sampled subgraph was much smaller than the original graph, the accuracy of the GNN models got by sampling techniques might be different from the full-batch training.
+Since the size of the sampled subgraph was much smaller than the original graph, the accuracy of the GNN models trained with sampling techniques might be different from the full-batch training.
 %
@@
 %
-For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section 4.1.4.
+For each combination of dataset and GNN, we chose the hyper-parameters that achieved the highest accuracy according to the experimental results in Section~\ref{sec:hyper_parameter_accuracy}.
 
@@
 % 
-The sampled subgraphs had lower average degrees than the original graph.
+The sampled subgraphs produced by the neighbor sampler and the cluster sampler had lower average degrees than the original graph.
 %
@@
 %
-However, small batch sizes could not make full use of the computing power of a GPU.
+However, the batch size should be small to limit the memory usage, especially for inference.
 %
-With big batch sizes, the current implementation of the sampling techniques in PyG was inefficient.
+The current implementation of the sampling techniques in PyG was inefficient to handle small batches.
 %
-The time spent on the sampling phase and the data transferring phase even exceeded the training/inference phase.
+Small batches could not make full use of the computing power of a GPU.
+%
+The time spent on the sampling phase and the data transferring phase could even exceed the training/inference phase.

### 2020-12-26 NEUROC/sec1-introduction.tex
更新了sec1

@@
 
-However, what is the real performance bottleneck in the GNN training is still in doubt.
+However, what is the real performance bottleneck in the GNN training and inference is still in doubt.
 Yan et al. \cite{yan2020_characterizing_gcn} and Zhang et al. \cite{zhang2020_analysis_neugraph} experimentally analyze the architectural characteristics of the GNN \emph{inference}.
@@
 
-To explore the essential performance bottleneck in the GNN training/inference, we conduct a range of experimental analysis in deep in this work. 
-We focus on the efficiency bottleneck of GNN training/inference.
+To explore the essential performance bottleneck in the GNN training and inference, we conduct a range of experimental analysis in deep in this work. 
+We focus on the efficiency bottleneck of GNN training and inference.
 We model the GNNs with the message-passing framework that decomposes a GNN layer into two parts: the vertex calculation and the edge calculation.  
@@
 We implement them with PyG and evaluate their efficiency with six real-world datasets on a GPU.
-We identify the most time-consuming stage in the GNN training/inference by decomposing the training/inference time per epoch from the layer level to the operator level.
-We also analyze the memory usage during the training/inference to discover the main factor that limits the data scalability of GNN training/inference on GPUs. 
+We identify the most time-consuming stage in the GNN training and inference by decomposing the training and inference time per epoch from the layer level to the operator level.
+We also analyze the memory usage during the training and inference to discover the main factor that limits the data scalability of GNN training and inference on GPUs. 
 Finally, we evaluate whether or not the sampling techniques affect the performance bottleneck. 
@@
     \item \textbf{The training and inference time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.}
-    Fixing other hyper-parameters, the training/inference time and the memory usage of a GNN layer increase linearly as the input/output dimensions.
+    Fixing other hyper-parameters, the training and inference time and the memory usage of a GNN layer increase linearly as the input/output dimensions.
     \item \textbf{The edge-related calculation is the performance bottleneck for most GNNs.}
     For GNNs with high edge calculation complexity, most of the training and inference time is spent on conducting the messaging function for every edge. 
-    For GNNs with low edge calculation complexity, the message collection and aggregation consumes most of the training/inference time.
-    \item \textbf{The high memory usage of the edge calculation is the main factor limiting the data scalability of GNN training/inference.}
+    For GNNs with low edge calculation complexity, the message collection and aggregation consumes most of the training and inference time.
+    \item \textbf{The high memory usage of the edge calculation is the main factor limiting the data scalability of GNN training and inference.}
     The edge calculation generates and caches many intermediate results. 
     They are an order of magnitude larger than the dataset itself. 
-    As GPUs have limited on-chip memory, the high memory consumption prevents us from training and inferring big graphs on GNNs.
-    \item \textbf{The sampling techniques can significantly reduce training/inference time and memory usage.}
-    They are essential for training big graphs on GPUs. 
+    As GPUs have limited on-chip memory, the high memory consumption prevents us from performing training and inference big graphs on GNNs.
+    \item \textbf{The sampling techniques can significantly reduce training and inference time and memory usage.}
+    They are essential for performing training and inference big graphs on GPUs. 
     However, the existing implementation is still inefficient. 
-    Under big batch sizes, the time spent on the sampling may exceed the time spent on the training/inference. 
+    Under big batch sizes, the time spent on the sampling may exceed the time spent on the training and inference. 
     Under small batch sizes, the sampled graphs are also small, wasting the computing power of GPUs.
@@
 \begin{itemize}
-      \item To reduce training/inference time, \textbf{optimizations should focus on improving the efficiency of the edge calculation}. 
+      \item To reduce training and inference time, \textbf{optimizations should focus on improving the efficiency of the edge calculation}. 
       One may consider developing optimized operators for the messaging step that is the major source of computing costs in the edge calculation.
@@
 \end{itemize}
-We hope that our analysis can help the developers of the GNN libraries/systems have a better understanding of the characteristics of GNN training/inference and propose more targeted optimizations.
+We hope that our analysis can help the developers of the GNN libraries/systems have a better understanding of the characteristics of GNN training and inference and propose more targeted optimizations.
 

### 2020-12-26 NEUROC/sec5-insights.tex
更新后几章

@@
 
-Through the extensive experiments, we propose the following key findings and suggestions for how to optimize the performance of the GNN training/inference.
+Through the extensive experiments, we propose the following key findings and suggestions for how to optimize the performance for GNN training and inference.
 
@@
 
-    \item \emph{The computational cost of a GNN layer is mainly affected by the dimensions of the input and the output hidden feature vectors.}
-          Theoretically and empirically, the training/inference time and the memory usage of a GNN layer both increase \emph{linearly} with the dimensions of the input/output hidden feature vectors separately.
+    \item \emph{The computational cost of a GNN layer is mainly affected by the dimensions of the input and output hidden vectors.}
+          Theoretically and empirically, the training and inference time and the memory usage of a GNN layer both increase \emph{linearly} with the dimensions of the input/output hidden vectors separately.
           GNNs are friendly to high-dimensional scenarios. 
@@
               \item If the complexity of the messaging function $\phi$ is high, the implementation of $\phi$ is critical to performance.
-                    Improving its efficiency can significantly reduce the training time.
+                    Improving its efficiency can significantly reduce training/inference time.
                     For example, the attention mechanism in GNNs (like GAT and GaAN) requires an extra sub-layer to calculate the attention weight of each edge.
-                    Implementing the attention mechanism with specially optimized basic operators on the GPU side is a potential optimization.
+                    Implementing the attention mechanism with specially optimized basic operators on the GPU side is a potential optimization direction.
               \item If the complexity of $\phi$ is low, the efficiency of the collection step and the aggregation step becomes critical.
                     The existing GNN libraries \cite{DGL, PyG, ma2019_neugraph} already introduce the \emph{fused} operator to improve their efficiency.
-                    When the messaging function $\phi$ is an assignment or a scalar multiplication of the hidden feature vector of the source vertex, the libraries replace the collection, messaging, and aggregation steps with a single fused operator.
-                    The fused operator calculates the aggregated vectors directly from the input hidden feature vectors, minimizing the memory footprints and overlapping the memory accessing with computation.
+                    When the messaging function $\phi$ is an assignment or a scalar multiplication of the input hidden vector of the source vertex, the libraries replace the collection, messaging, and aggregation steps with a single fused operator.
+                    The fused operator calculates the aggregated vectors directly from the input hidden vectors, minimizing the memory footprints and overlapping the memory accessing with computation.
                     In this way, it significantly reduces the training/inference time of GNNs with low edge calculation complexity (like GCN) \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph}.
@@
                     It does not work for $\phi$ with more complex operations like matrix multiplication.
-                    A potential optimization is to develop composite CUDA kernels that can read the input hidden feature vectors and aggregate message vectors on the fly, without materializing the parameter vectors and the message vectors.
+                    A potential optimization is to develop composite CUDA kernels that can read the input hidden vectors and aggregate message vectors on the fly, without materializing the parameter vectors and the message vectors.
          \end{itemize}
-    \item \emph{The high memory usage caused by the intermediate results of the edge calculation stage limits the data scalability of the GNN training/inference.}
+    \item \emph{The high memory usage caused by the intermediate results of the edge calculation stage limits the data scalability of GNN training/inference.}
           The memory expansion ratios of the typical GNNs are very high, making GPUs unable to handle big graphs.
@@
     \item \emph{Sampling techniques can significantly reduce the training/inference time and memory usage, but its implementation is still inefficient}.
-          The sampling techniques are effective under small batch sizes.
-          Its current implementation brings considerable overheads when the batch size becomes large.
-          Improving the efficiency of the sampling is a potential optimization.
-          The sampled subgraphs are usually small.
-          They cannot make full use of the computing power of a GPU.
+          The sampling techniques are effective under small batch sizes for both training and inference.
+          However, its current implementation brings considerable overheads when the batch size is not big.
+          The sampled subgraphs that are usually small cannot make full use of the computing power of a GPU either.
+          Improving the efficiency of the sampling techniques is a potential optimization direction.
           How to improve the GPU utilization under small batch sizes is another problem to solve.
           One possible solution is to train multiple batches asynchronously on the same GPU and use the asynchronous stochastic gradient descent to speed up the converge.
-
 \end{enumerate}

### 2020-12-26 NEUROC/sec7-conclusion.tex
更新后几章

@@
 
-In this work, we systematically explore the performance bottleneck in graph neural network training and inference. 
+In this work, we systematically explore the performance bottlenecks in graph neural network training and inference. 
 We model the existing GNNs with the message-passing framework. 
-We classify the GNNs according to their edge and vertex calculation complexities to select four typical GNNs for evaluation. 
+We classify the GNNs according to their edge and vertex calculation complexity to select four typical GNNs for evaluation. 
 The experimental results validate our complexity analysis. Fixing other hyper-parameters, the training time and the memory usage increase linearly with each hyper-parameter of the four GNNs. 

### 2020-12-26 NEUROC/sec4-experiments.tex
更新后几章

@@
 %
+The 
+%
 On the \texttt{amp} and \texttt{cam} datasets, the sampling time even accounted for near half of the total inference time.
@@
 %
-With small batch sizes, the sampling techniques could significantly reduce the training/inference time per batch and the peak memory usage.
+With small batch sizes, the sampling techniques could significantly reduce the peak memory usage per batch.
 %
-However, the batch size should be small to limit the memory usage, especially for inference.
-%
-The current implementation of the sampling techniques in PyG was inefficient to handle small batches.
-%
-Small batches could not make full use of the computing power of a GPU.
+However, the current implementation of the sampling techniques in PyG was inefficient to handle small batches.
 %
 The time spent on the sampling phase and the data transferring phase could even exceed the training/inference phase.
+%
+Small batches could not make full use of the computing power of a GPU either.

### 2020-12-26 NEUROC/sec7-conclusion.tex
更新后几章

@@
 In this work, we systematically explore the performance bottlenecks in graph neural network training and inference.
+%
 We model the existing GNNs with the message-passing framework. 
+%
 We classify the GNNs according to their edge and vertex calculation complexity to select four typical GNNs for evaluation. 
-The experimental results validate our complexity analysis. Fixing other hyper-parameters, the training time and the memory usage increase linearly with each hyper-parameter of the four GNNs. 
-To find out the performance bottleneck in the training/inference time, we decompose the training/inference time per epoch on different levels. 
-The time breakdown analysis indicates that the edge calculation stage and its related basic operators are the performance bottleneck for most GNNs. 
+%
+The experimental results validate our complexity analysis.
+%
+Fixing other hyper-parameters, the training time, inference time and memory usage increase linearly with each hyper-parameter of the four GNNs.
+%
+To find out the performance bottlenecks in the training/inference time, we decompose the training/inference time per epoch on different levels.
+%
+The time breakdown analysis indicates that the edge calculation stage and its related basic operators are the performance bottlenecks for most GNNs.
+%
 Moreover, the intermediate results produced by the edge calculation stage cause high memory usage, limiting the data scalability.
-Adopting sampling techniques can reduce the training time and the memory usage significantly. 
+%
+Adopting sampling techniques can reduce the memory usage of training and inference significantly.
+%
 However, the current implementation of the sampling techniques in PyG brings considerable sampling overheads.
+%
 The small sampled subgraphs cannot make full use of the computing power of a GPU card either.
+% 
 Our analysis indicates that the edge calculation stage should be the main target of optimizations.
-Reducing its memory usage and improving its efficiency can significantly improve the performance of the GNN training and inference. 
-Based on the analysis, we propose several potential optimizations for the GNN frameworks. 
+%
+Reducing its memory usage and improving its efficiency can significantly improve the performance of GNN training and inference.
+%
+Based on the analysis, we propose several potential optimizations for the GNN libraries/systems.
+%
 We believe that our analysis can help developers to have a better understanding of the characteristics of GNN training and inference.

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
更新了顾老师对reponse的意见和修正语法问题

@@
 \begin{enumerate}
-\item According to Reviewer 1's comments, we have added experiments on the performance bottleneck analysis of GNN inference.
+\item According to reviewer 1's comments, we have added experiments on the performance bottleneck analysis of GNN inference.
 %
-We added experiments on how the hyper-parameters of GNNs affect the elapsed time and the memory usage of inference in Section 4.1.2 ``Effects on Inference Time'' and Section 4.1.3 ``Effects on Peak Memory Usage'', respectively.
+Specifically, we added experiments on how the hyper-parameters of GNNs affect the elapsed time and the memory usage of inference in Section 4.1.2 ``Effects on Inference Time'' and Section 4.1.3 ``Effects on Peak Memory Usage'', respectively.
 %
-We added time breakdown analysis of GNN inference in Section 4.2.4.
+We presented the time breakdown analysis of GNN inference in Section 4.2.4.
 %
-We also presented the memory usage analysis of GNN inference in Section 4.3.2.
-%
-The performance bottlenecks of sample-based inference were analyzed in Section 4.4.2.
+We also presented the memory usage analysis of GNN inference in Section 4.3.2., and the performance bottlenecks of sample-based inference were analyzed in Section 4.4.2.
 
-\item According to the Reviewer 2's comments, we have added experiments on how the model complexity and the sampling techniques affect the accuracy of GNNs.
+\item According to the reviewer 2's comments, we have added an evaluation on how the model complexity and the sampling techniques affect the accuracy of GNNs.
 %
@@
 %
-We analyzed the effects of the sampling techniques on accuracy in Section 4.4.3.
+Finally, we analyzed the effects of the sampling techniques on accuracy in Section 4.4.3.
 
@@
 %
-We unified the symbol usage through the manuscript and added a table to summarize the frequently-used symbols.
+We unified the symbol usage through the manuscript and added a table to summarize the frequently-used symbols as suggested by reviewer 1.
 %
@@
 
-We then respond to the concerns of reviewers point by point as follows.
+We then respond to all reviewers point by point as follows.
 
@@
 \begin{reply}
-    Thank you for your kindly comments on our manuscript.
+    Thank you for your comments on our manuscript.
     %
@@
 \begin{reply}
-	Thank you for pointing out missing references.
+	Thank you for pointing out the missing references.
 Computer vision is indeed an important application area of graph neural networks.
@@
     %
-    Specifically, we use the past tense to describe experimental methods, results and what they indicate.
+    Specifically, we use the past tense to describe experimental methods, results, and what they indicate.
     %
@@
     %
-    We add brief description on GNN inference in Section 2.5 ``Inference with GNNs'' in the revised manuscript.
+    We add a brief description of GNN inference in Section 2.5 ``Inference with GNNs'' in the revised manuscript.
     %
@@
 
-    \item In Section 4.2 ``Time Breakdown Analysis'', we additionaly conduct time breakdown analysis for GNN inference and compare the similarites and differences between training and inference.
+    \item In Section 4.2 ``Time Breakdown Analysis'', we additionally conduct time breakdown analysis for GNN inference and compare the similarities and differences between training and inference.
     %
@@
     %
-    Though the the top time-consuming basic operators are changed, they still indicates that GPUs are suitable for conducting GNN inference.
+    Though the top time-consuming basic operators are changed, they still indicate that GPUs are suitable for conducting GNN inference.
     %
@@
 
-    \item In Section 4.3 ``Memory Usage Analysis'', we conduct extra experiments to evaluate the peak memory usage during inference.
+    \item In Section 4.3 ``Memory Usage Analysis'', we conduct a group of experiments to evaluate the peak memory usage during inference.
     %
-    We find that the memory usage of inference also mainly comes from the edge calculation stage, same as training.
+    We find that the memory usage of inference also mainly comes from the edge calculation stage, the same as training.
     %
@@
     %
-    The overheads of sampling and data transfering are significant in the total inference time.
+    The overheads of sampling and data transferring are significant in the total inference time.
     %
@@
     %
-    At the same time, the overheads brought by sampling and data transfering from CPU to GPU become obvious when the batch size was small.
+    At the same time, the overheads brought by sampling and data transferring from CPU to GPU become obvious when the batch size was small.
     %
@@
     %
-    We have carefully revised the manuscript according to your kindly comments and suggestions in the following points.
+    We have carefully revised the manuscript according to your comments and suggestions in the following points.
     %
@@
     %
-    There is no clear winner.
+    There is no absolute winner.
     %
@@
     %
-    Simple GNN models (such as GCN) can still achieve good acuuracy with proper hyper-parameter settings.
+    Simple GNN models (such as GCN) can still achieve good accuracy with proper hyper-parameter settings.
 
@@
     %
-    Among the two sampling methods, the performance of the cluster sampler is stabler than the neighbor sampler.
+    Among the two sampling methods, the performance of the cluster sampler is more stable than the neighbor sampler.
     %
@@
     %
-    In several cases (like GaAN in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amp} and Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amc}), the accuracy of the neighbor sampler was even higher than the full-batch training.
+    In several cases (like GaAN in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amp} and Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amc}), the accuracy of the neighbor sampler is even higher than the full-batch training.
     %
@@
     %
-    A larger batch size does not always bring higher accuracy, like GAT in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_fli}. 
+    Larger batch size does not always bring higher accuracy, like GAT in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_fli}. 
     %
@@
     %
-    How to automatically select a proper batch size is a topic worth studying.
+    We believe that how to automatically select a proper batch size is a topic worth studying.
 \end{reply}
@@
     %
-    As suggested, we additionally evaluate the effects of model complexity on accuracy in Section 4.1 ``Effects of Hyper-parameters on Performance'' in the revised manuscript.
+    Followed your suggestion, we additionally evaluate the effects of model complexity on accuracy in Section 4.1 ``Effects of Hyper-parameters on Performance'' in the revised manuscript.
     %

### 2020-12-26 NEUROC/sec4-experiments.tex
更新了顾老师对reponse的意见和修正语法问题

--- 2020-12-26 NEUROC/sec4-experiments.tex
@@
 %
-Although the collecting step did not conduct any computation and only involved data movement, it occupied noticeable execution time in the four GNNs.
+Although the collecting step did not conduct any computation and only involved data movement, it occupied a noticeable execution time in the four GNNs.
 
@@
 %
-For GGNN, \texttt{index} operator in the prediction layer also became a time-consuming basic operators.
+For GGNN, \texttt{index} operator in the prediction layer also became a time-consuming basic operator.
 %
@@
 %
-However, the batch size should be small to limit the memory usage, especially for inference.
+However, the batch size should be small to limit memory usage, especially for inference.
 %

### 2020-12-26 NEUROC/sec5-insights.tex

@@
 
-    \item \emph{Sampling techniques can significantly reduce the training/inference time and memory usage, but its implementation is still inefficient}.
+    \item \emph{Sampling techniques can significantly reduce the memory usage per batch, but its implementation is still inefficient}.
+          %
           The sampling techniques are effective under small batch sizes for both training and inference.
-          However, its current implementation brings considerable overheads when the batch size is not big.
-          The sampled subgraphs that are usually small cannot make full use of the computing power of a GPU either.
+          %
+          With proper batch sizes, the accuracy of the sample-based training can be close to the accuracy of the full-batch training.
+          %
+          However, the current implementation of the sampling techniques in PyG brings considerable overheads when the batch size is small.
+          %
           Improving the efficiency of the sampling techniques is a potential optimization direction.
+          %
+          The small sampled subgraphs cannot make full use of the computing power of the GPU either.
+          %
           How to improve the GPU utilization under small batch sizes is another problem to solve.

### 2020-12-26 NEUROC/sec1-introduction.tex
更新introduction.

--- 2020-12-26 NEUROC/sec1-introduction.tex
@@
 In recent years, the graph neural network (GNN) becomes a hot research topic in the field of artificial intelligence.
+%
 Many GNNs~\cite{kipf2017_gcn, defferrad2016_chebnet, li2018_agcn,li2015_ggnn, hamilton2017_graphsage, huang2018_gat, zhang2018_gaan} are proposed.
+%
 They can learn the representation of vertices/edges in a graph from its topology and the original feature vectors in an \emph{end-to-end} manner.
-The powerful expression ability makes GNNs achieve good accuracy in not only graph analytical tasks \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020} (like node classification and link prediction) but also computer vision tasks (like human-object interaction \cite{qi2018_learning_humanobject}, human parsing \cite{wang2020_hierarchical_human_parsing}, and video object segmentation \cite{wang2019_zeroshot_video}).
+%
+The powerful expression capability makes GNNs achieve good accuracy in not only graph analytical tasks \cite{zhou2018_gnn_review, zhang2018_gnn_survey, comprehensive-survey-wu-2020} (like node classification and link prediction) but also computer vision tasks (like human-object interaction \cite{qi2018_learning_humanobject}, human parsing \cite{wang2020_hierarchical_human_parsing}, and video object segmentation \cite{wang2019_zeroshot_video}).
 
 To train GNNs easily, a series of GNN libraries/systems \cite{PyG, DGL, ma2019_neugraph, zhu2019_aligraph, PGL} are proposed.
+%
 PyTorch Geometric (PyG) \cite{PyG}, NeuGraph \cite{ma2019_neugraph}, PGL \cite{PGL} and Deep Graph Library (DGL) \cite{DGL} build upon the existing deep learning frameworks (PyG on PyTorch, NeuGraph on TensorFlow, PGL on PaddlePaddle, DGL on multiple backends).
-They provide users with a high-level programming models (the message-passing model for PyG/PGL/DGL and the SAGA-NN model for NeuGraph) to describe the structure of a GNN.
+%
+They provide users with a high-level programming models (the message-passing framework for PyG/PGL/DGL and the SAGA-NN model for NeuGraph) to describe the structure of a GNN.
+%
 They take advantage of the common tools provided by the underlying frameworks like the automatic differentiation to simplify the development.
-They utilize specially optimized CUDA kernels (like kernel fusion \cite{DGL} \cite{ma2019_neugraph}) and other implementation techniques (like 2D graph partitioning \cite{ma2019_neugraph}) to improve the speed of GNN training on GPUs.
+%
+They utilize specially optimized CUDA kernels (like kernel fusion \cite{DGL, ma2019_neugraph}) and other implementation techniques (like 2D graph partitioning \cite{ma2019_neugraph}) to improve the speed of GNN training on GPUs.
 
-However, what is the real performance bottleneck in the GNN training is still in doubt.
-Yan et al. \cite{yan2020_characterizing_gcn} and Zhang et al. \cite{zhang2020_analysis_neugraph} experimentally analyze the architectural characteristics of the GNN \emph{inference}.
-They find that the GNN inference is more cache-friendly than the traditional graph analysis tasks(like PageRank) and is suitable for GPUs.
+However, what is the real performance bottleneck in GNN training and inference is still in doubt.
+%
+Yan et al. \cite{yan2020_characterizing_gcn} and Zhang et al. \cite{zhang2020_analysis_neugraph} experimentally analyze the architectural characteristics of GNN \emph{inference}.
+%
+They find that the GNN inference is more cache-friendly than the traditional graph analysis tasks (like PageRank) and is suitable for GPUs.
+%
 They verify the effectiveness of the kernel fusion optimization in reducing the time of inference.
-Nevertheless, they only analyze the inference stage, ignoring the effects of the backpropagation during the training.
+%
+Nevertheless, they only analyze the inference stage, ignoring the effects of the backpropagation during training.
 
-To explore the essential performance bottleneck in the GNN training/inference, we conduct a range of experimental analysis in deep in this work. 
-We focus on the efficiency bottleneck of GNN training/inference.
+To explore essential performance bottlenecks in both GNN training and inference, we conduct a range of experimental analysis in this work.
+%
+We focus on the efficiency bottlenecks of GNN training and inference.
+%
 We model the GNNs with the message-passing framework that decomposes a GNN layer into two parts: the vertex calculation and the edge calculation.
-According to the time complexity of the two parts, we classify the typical GNNs into four quadrants(\{high, low\} complexity $\times$ \{vertex, edge\} calculation).
-We choose GCN \cite{kipf2017_gcn}, GGNN \cite{li2015_ggnn}, GAT \cite{huang2018_gat} and GaAN \cite{zhang2018_gaan} as representative GNNs of the four quadrants.
+%
+According to the time complexity of the two parts, we classify the typical GNNs into four quadrants (\{high, low\} complexity $\times$ \{vertex, edge\} calculation).
+%
+We choose GCN \cite{kipf2017_gcn}, GGNN \cite{li2015_ggnn}, GAT \cite{huang2018_gat}, and GaAN \cite{zhang2018_gaan} as representative GNNs of the four quadrants.
 
-We implement them with PyG and evaluate their efficiency with six real-world datasets on a GPU.
-We identify the most time-consuming stage in the GNN training/inference by decomposing the training/inference time per epoch from the layer level to the operator level.
-We also analyze the memory usage during the training/inference to discover the main factor that limits the data scalability of GNN training/inference on GPUs. 
-Finally, we evaluate whether or not the sampling techniques affect the performance bottleneck. 
+We implement them with PyG and evaluate their efficiency and accuracy with six real-world datasets on a GPU card.
+%
+We identify the most time-consuming stage in GNN training and inference by decomposing the training and inference time per epoch from the layer level to the operator level.
+%
+We also analyze the memory usage during training and inference to discover the main factor that limits the data scalability of GNN training and inference on GPUs. 
+%
+Finally, we evaluate whether or not the sampling techniques affect the performance bottlenecks and accuracy.
+%
 The key findings and insights are summarized below.
@@
 \begin{itemize}
-    \item \textbf{The training/inference time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden feature vectors.}
-    Fixing other hyper-parameters, the training/inference time and the memory usage of a GNN layer increase linearly as the input/output dimensions.
-    \item \textbf{The edge-related calculation is the performance bottleneck for most GNNs.}
-    For GNNs with high edge calculation complexity, most of the training/inference time is spent on conducting the messaging function for every edge. 
-    For GNNs with low edge calculation complexity, the message collection and aggregation consumes most of the training/inference time.
-    \item \textbf{The high memory usage of the edge calculation is the main factor limiting the data scalability of GNN training/inference.}
-    The edge calculation generates and caches many intermediate results. 
+    \item \emph{The training and inference time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden vectors.}
+    %
+    Fixing other hyper-parameters, the training and inference time and the memory usage of a GNN layer increase linearly with the dimensions.
+
+    \item \emph{The edge-related calculation is the performance bottleneck for most GNNs.}
+    For GNNs with high edge calculation complexity, most of the training and inference time is spent on conducting the messaging function for every edge.
+    %
+    For GNNs with low edge calculation complexity, the collection and aggregation of message vectors of all edges consume most of the training and inference time.
+
+    \item \emph{The high memory usage of the edge calculation stage is the main factor limiting the data scalability of GNN training and inference.}
+    %
+    The edge calculation generates (and caches) many intermediate results.
+    %
     They are an order of magnitude larger than the dataset itself.
-    As GPUs have limited on-chip memory, the high memory consumption prevents us from training/inferring big graphs on GNNs.
-    \item \textbf{The sampling techniques can significantly reduce training/inference time and memory usage.}
-    They are essential for training big graphs on GPUs. 
-    However, the existing implementation is still inefficient. 
-    Under big batch sizes, the time spent on the sampling may exceed the time spent on the training/inference. 
+    %
+    As GPUs have limited on-chip memory, the high memory consumption prevents us from performing training and inference on big graphs.
+
+    \item \emph{The sampling techniques can significantly reduce the memory usage of training and inference.}
+    %
+    The sampling techniques are essential for performing GNN training and inference on big graphs with GPUs.
+    %
+    However, the existing implementation of sampling is still inefficient.
+    % 
+    The time spent on sampling may exceed the time spent on training and inference.
     Under small batch sizes, the sampled graphs are also small, wasting the computing power of GPUs.
@@
 Based on the insights, we provide several potential optimization directions:
+
 \begin{itemize}
-      \item To reduce training/inference time, \textbf{optimizations should focus on improving the efficiency of the edge calculation}. 
+      \item To reduce training and inference time, \emph{optimizations should focus on improving the efficiency of the edge calculation}.
+      % 
       One may consider developing optimized operators for the messaging step that is the major source of computing costs in the edge calculation.
+      %
        Fusing operators of the collection step, messaging function and the aggregation step together is another way to reduce the overheads in the edge calculation.
-      \item To reduce memory usage, \textbf{optimizations should focus on reducing the intermediate results in the edge calculation}. 
+
+      \item To reduce memory usage, \emph{optimizations should focus on reducing the intermediate results in the edge calculation}.
+      %
       One may consider adopting the checkpoint mechanism to cache less intermediate results during the forward phase and re-calculate the needed data on the fly during the backpropagation.
-      \item To improve the efficiency of the sampling techniques, \textbf{one may consider overlapping the sampling on the CPU side with the training on the GPU side.} 
+      %
+      \item To improve the efficiency of the sampling techniques, \emph{one may consider overlapping the sampling on the CPU side with the training/inference on the GPU side.}
+      %
       Choosing a proper batch size automatically is another potential optimization.
 \end{itemize}
+
 We hope that our analysis can help the developers of the GNN libraries/systems have a better understanding of the characteristics of GNN training/inference and propose more targeted optimizations.
@@
 We briefly survey the typical GNNs in Section~\ref{sec:review_of_gnns}.
+%
 We introduce our experimental setting and targets in Section~\ref{sec:experimental_design}.
+%
 The experimental results are presented and analyzed in Section~\ref{sec:experiment_results}.
+%
 We summarize the key findings and give out potential optimization directions in Section~\ref{sec:insights}.
-We introduce the related work in Section~\ref{sec:related_work} and finally conclude our work in Section~\ref{sec:conclusion}.
+%
+We introduce the related work in Section~\ref{sec:related_work} and conclude our work in Section~\ref{sec:conclusion}.

### 2020-12-26 NEUROC/sec4-experiments.tex
fix inferring的表达错误

@@
 
-With the sampling techniques, GNNs were trained and inferred in a mini-batch manner.
+With the sampling techniques, GNNs were trained and performed inference in a mini-batch manner.
 %
@@
 
-Among the two sampling methods, the performance of the cluster sampler was stabler than the neighbor sampler.
+Among the two sampling methods, the performance of the cluster sampler was more stable than the neighbor sampler.
 %

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
更新response

@@
 %
-We also presented the memory usage analysis of GNN inference in Section 4.3.2., and the performance bottlenecks of sample-based inference were analyzed in Section 4.4.2.
+We also presented the memory usage analysis of GNN inference in Section 4.3., and the performance bottlenecks of sample-based inference were analyzed in Section 4.4.2.
 
@@
 %
-Finally, we analyzed the effects of the sampling techniques on accuracy in Section 4.4.3.
+Finally, we analyzed the effects of the sampling techniques on accuracy in Section 4.4.4.
 
@@
     %
-    More details are available in Section 4.3.2 ``Memory Usage of Inference'' in the revised manuscript.
+    More details are available in Section 4.3 ``Memory Usage of Inference'' in the revised manuscript.
 
@@
 \begin{point}
-    In the paper, authors accomplished a unique study and analysis on GNN models training complexity.  The articles first review and development history of GNNs and creatively model all architectures as input layers, intermediate layers of graph neurons and prediction layers.
+    In the paper, authors accomplished a unique study and analysis on GNN models training complexity.
+The articles first review and development history of GNNs and creatively model all architectures as input layers, intermediate layers of graph neurons and prediction layers.
 And they quantitatively summarize the time and space complexity of 4 representative GNNs, including graph convolution, gated recurrent graph net, graph attention net and GraphSage.

### 2020-12-26 NEUROC/sec2-review-of-graph-neural-network.tex

@@
 
-\subsection{Graph Neuron and Message-passing Model}
+\subsection{Graph Neuron and Message-passing Framework}
 
@@
 
-We follow the message-passing model \cite{gilmer_messgae_passing} to formally define a graph neuron.
+We follow the message-passing framework \cite{gilmer_messgae_passing} to formally define a graph neuron.
 %
-The message-passing model is widely used in the cutting-edge GNN libraries like PyG \cite{PyG} and DGL \cite{DGL}.
+The message-passing framework is widely used in the cutting-edge GNN libraries like PyG \cite{PyG} and DGL \cite{DGL}.
 %
-\figurename~\ref{fig:graph_neuron_structure} shows the internal structure of a graph neuron in the message-passing model.
+\figurename~\ref{fig:graph_neuron_structure} shows the internal structure of a graph neuron in the message-passing framework.
 %
@@
     \caption{Graph neuron of $v_3$ in the GNN layer $l$ with the demo graph $\mathcal{G}$ in \figurename~\ref{fig:general_structure_of_gnn}b.
-$\phi^l$/$\Sigma^l$/$\gamma^l$ are the messaging/aggregation/updating functions in the message-passing model, respecitvely.}
+$\phi^l$/$\Sigma^l$/$\gamma^l$ are the messaging/aggregation/updating functions in the message-passing framework, respecitvely.}
     \label{fig:graph_neuron_structure}
@@
 
-Briefly, the behaviour of a graph neuron under the message-passing model can be defined as
+Briefly, the behaviour of a graph neuron under the message-passing framework can be defined as
 
@@
 %Since we focus on analyzing the performance bottleneck in training GNNs, we classify the typical GNNs from the view of time complexity.
-We use $O_\phi$/$O_\Sigma$/$O_\gamma$ to denote the time complexity of the three functions in the message-passing model.
+We use $O_\phi$/$O_\Sigma$/$O_\gamma$ to denote the time complexity of the three functions in the message-passing framework.
 The time complexity of a GNN layer is made up of two parts: the edge calculation complexity $O_\phi$ + $O_\Sigma$ and the vertex calculation complexity $O_\gamma$.

### 2020-12-26 NEUROC/sec6-related-work.tex
更新后几章

--- 2020-08-30 CCPE/Mauscript/sec6-related-work.tex
@@
 We also evaluate the effects of the sampling techniques.
-Our work and \cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph} form a complementary study on the efficiency issue of GNNs.
+Our work and the related evaluation\cite{yan2020_characterizing_gcn, zhang2020_analysis_neugraph} form a complementary study on the efficiency issue of GNNs.
 
-\paragraph{Libraries/Systems of GNNs}
+\paragraph{Libraries/Systems for GNNs}
 
-PyG \cite{PyG} and DGL \cite{DGL} both adopt the message-passing model as the underlying programming model for GNNs and support training big datasets with the sampling techniques.
+PyG \cite{PyG} and DGL \cite{DGL} both adopt the message-passing framework as the underlying programming model for GNNs and support training big datasets with the sampling techniques.
 PyG \cite{PyG} is built upon PyTorch and it uses optimized CUDA kernels for GNNs to achieve high performance.

### 2020-12-26 NEUROC/ms.tex
更新abstract

@@
 		The graph neural network (GNN) has become a popular research area for its state-of-the-art performance in many graph analysis tasks.
-		Recently, various graph neural network libraries have emerged.They make the development of GNNs convenient, but their performance on large datasets is not satisfying. 
-		In this work, we analyze the performance bottleneck in GNN training and inference with GPUs empirically. 
+        %
+		Recently, various graph neural network libraries have emerged.
+        %
+        They make the development of GNNs convenient, but their performance bottlenecks on large datasets is not well studied.
+        %
+		In this work, we analyze the performance bottlenecks in GNN training and inference with GPUs empirically.
+        % 
 		A GNN layer can be decomposed into two parts: the vertex and the edge calculation parts.
+        %
 		According to their computational complexity, we select four representative GNNs (GCN, GGNN, GAT, GaAN) for evaluation.
+        % 
 		We breakdown their running time and memory usage, evaluate the effects of hyper-parameters, and assess the efficiency of the sampling techniques.
+        %
 		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training and inference time and memory usage.
-		Future optimization can focus on it. The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementations still have room for improvement.
+        %
+		%Future optimizations can focus on it.
+        %
+        The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementation still has room for improvement.
 	\end{abstract}

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
更新了response的语法

@@
 
-\item According to the reviewer 2's comments, we have added an evaluation on how the model complexity and the sampling techniques affect the accuracy of GNNs.
+\item According to reviewer 2's comments, we have added an evaluation of how the model complexity and the sampling techniques affect the accuracy of GNNs.
 %

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
update
检查了response的sec的引用

@@
 
-\item We have adjusted the abstract, Section 1 ``Introduction'', and Section 5 ``Insights'' according to the new findings on inference time and accuracy.
+\item We have adjusted the abstract, Section 1 ``Introduction'', Section 5 ``Insights'', and Section 7 ``Conclusion'' according to the new findings on inference time and accuracy.
 
@@
     %
-    We present the experimental results and related discussion in a new subsection Section 4.4.3 ``Effects on Accuracy''.
+    We present the experimental results and related discussion in a new subsection Section 4.4.4 ``Effects on Accuracy''.
 \end{reply}

### 2020-12-26 NEUROC/Response-MajRev/response_letter-version2.tex
更改了一遍语法

@@
 
-    In addition, we add more details on the proportions of  the train/evaluation/test sets of the datasets in Section 3.1 ``Experimental Setting'' in the revised manuscript.
+    Besides, we add more details on the proportions of the train/evaluation/test sets of the datasets in Section 3.1 ``Experimental Setting'' in the revised manuscript.
     %
@@
     %
-    We add discussion on how the hyper-parameters of GNNs affect the accuracy.
+    We add a discussion on how the hyper-parameters of GNNs affect the accuracy.
     %

### 2020-12-26 NEUROC/sec1-introduction.tex
更改了一遍语法

@@
 %
-They provide users with a high-level programming models (the message-passing framework for PyG/PGL/DGL and the SAGA-NN model for NeuGraph) to describe the structure of a GNN.
+They provide users with a high-level programming model (the message-passing framework for PyG/PGL/DGL and the SAGA-NN model for NeuGraph) to describe the structure of a GNN.
 %
@@
 \begin{itemize}
-    \item \emph{The training and inference time and the memory usage of a GNN layer is mainly affected by the dimensions of the input/output hidden vectors.}
+    \item \emph{The training and inference time and the memory usage of a GNN layer are mainly affected by the dimensions of the input/output hidden vectors.}
     %
@@
     %
-    As GPUs have limited on-chip memory, the high memory consumption prevents us from performing training and inference on big graphs.
+    As GPUs have limited on-chip memory, high memory consumption prevents us from performing training and inference on big graphs.
 

### 2020-12-26 NEUROC/sec2-review-of-graph-neural-network.tex
更改了一遍语法

@@
 %
-The sampling techniques only active the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:gnn_sampling}.
+The sampling techniques only activate the graph neurons and the connections that appear in the sampled subgraph between GNN layers, as shown in \figurename~\ref{fig:gnn_sampling}.
 %

### 2020-12-26 NEUROC/sec5-insights.tex
更改了一遍语法

@@
           GNNs are friendly to high-dimensional scenarios. 
-          Algorithm engineers can use high-dimensional feature vectors to improve the expressive power of a GNN without worrying exponential growth in the training/inference time and memory usage
+          Algorithm engineers can use high-dimensional feature vectors to improve the expressive power of a GNN without worrying about exponential growth in the training/inference time and memory usage
     \item \emph{Performance optimizations should focus on improving the efficiency of the edge calculation stage.}

### 2020-12-27 NEUROC/Response-MajRev/response_letter-version2.tex

@@
 % Numbering figures according to reviewers
-\renewcommand{\thefigure}{\thereviewer{}.\arabic{figure}}
+\renewcommand{\thefigure}{\thereviewer{}-\arabic{figure}}
 
@@
 %
-We also presented the memory usage analysis of GNN inference in Section 4.3., and the performance bottlenecks of sample-based inference were analyzed in Section 4.4.2.
+We also presented the memory usage analysis of GNN inference in Section 4.3, and the performance bottlenecks of the sample-based inference were analyzed in Section 4.4.3.
 
@@
 %
-We improved the description of the sub-layer concept in Section 2.1 and Section 2.2.
+We improved the description of the sub-layer concept in Section 2.2 and Section 2.3.
 %
@@
 
-We then respond to all reviewers point by point as follows.
+We then respond to the concerns of all reviewers point by point as follows.
 
@@
 
-    In order to facilitate readers to quickly locate the meaning of symbols, we have added Table 1 at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised manuscript.
+    To facilitate readers to quickly locate the meaning of symbols, we have added Table 1 at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised manuscript.
 
@@
 
-    As suggested, we have split Figure 6 and Figure 7 into five figures (Figure 6 to 10) in the revised manuscript to enlarge their subfigures.
+    As suggested, we have split Figure 6 into four figures (Figure 6 to 9) in the revised manuscript to enlarge their subfigures.
     %
-    We have also adjusted font sizes in all figures (besides Figure 6 and Figure 7) to make sure that they are equal to or greater than the font size of figure captions.
-
+    Besides Figure 6 and Figure 7, we have also adjusted font sizes in all figures to make them equal to or greater than the font size of figure captions.    
 \end{reply}
@@
     %
-    As suggested, we also use the same methodology as the training phase to analyze the performance bottlenecks in the inference phase and we add corresponding experimental results in every subsection of Section 4 ``Evaluation Results and Analysis''.
+    As suggested, we also use the same methodology as the training phase to analyze the performance bottlenecks in the inference phase.
+    %
+    We add corresponding experimental results in every subsection of Section 4 ``Evaluation Results and Analysis.''
     %
@@
     %
-    We present specific experimental results in Section 4.1.2 ``Effects on Inference'' in the revised manuscript.
+    We present specific experimental results in Section 4.1.2 ``Effects on Inference Time'' and Section 4.1.3 ``Effects on Peak Memory Usage'' in the revised manuscript.
 
@@
     %
-    GGNN, GAT and GaAN have to cache some intermediate results during training, the memory space of those results is saved during inference.
+    GGNN, GAT, and GaAN have to cache some intermediate results during training, the memory space of those results is saved during inference.
     %
-    However, the memory expansion ratios of inference are still high, preventing us from inferencing with big graphs.
+    However, the memory expansion ratios of inference are still high, preventing us from performing inference on big graphs.
     %
@@
     %
-    The current implementation of the sampler used in inference in PyG is still inefficient.
+    The current implementation of the inference sampler in PyG is still inefficient.
     %
@@
     %
-    We present more details of our experimental analysis in the ``Inference Time'' paragraph of Section 4.4.3 ``Performance Bottlenecks in Inference''
+    We present more details of our experimental analysis in Section 4.4.3 ``Performance Bottlenecks in Inference'' in the revised manuscript.
 
@@
     %
-    The model complexity directly affects the accuracy.
+    The model complexity directly affects accuracy.
     %
-    In order to analyze the relationship between model complexity and accuracy, we have conducted two kinds of extra experiments in the revised manuscript: (1) how the hyper-parameters of the GNNs (like the dimension of hidden vectors and the number of heads) affect the accuracy of GNNs (in Section 4.1.4); (2) how the batch size in the sampling methods affects the accuracy of GNNs (in Section 4.4.4).
+    To analyze the relationship between model complexity and accuracy, we have conducted two kinds of extra experiments in the revised manuscript: (1) how hyper-parameters of GNNs (like the dimension of hidden vectors and the number of heads) affect accuracy (in Section 4.1.4); (2) how the batch size in the sampling methods affects the accuracy of GNNs (in Section 4.4.4).
     %
@@
     %
-    Figure~\ref{fig:effect_of_hyper_parameter_on_accuracy_of_gaan} shows the results of GaAN.
+    Figure~\ref{fig:effect_of_hyper_parameter_on_accuracy_of_gaan} shows the results of GaAN as an example.
     %
@@
     %
-    As the dimensions increase to a certain threshold, the GNNs gain sufficient representation capability to achieve good accuracy.
+    As the dimensions increase to a certain threshold, GaAN gains sufficient representation capability to achieve better accuracy.
     %
-    But high dimensions ($\geq 2048$) are also harmful to accuracy on the \texttt{amp} dataset, as they increase the risk of overfitting.
+    But the high dimensions ($\geq 2048$) are also harmful to the accuracy of the \texttt{amp} dataset, as they increase the risk of overfitting.
     %
@@
     %
-    Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage}  and Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} shows the accuracy comparisons of the two typical sampling methods under different batch sizes.
+    Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} shows the accuracy of the two typical sampling methods under different batch sizes.
     %
-    The results of the other datasets are available in Section 4.4.3 ``Effects on Accuracy'' in the revised manuscript.
+    The results of the other datasets are available in Section 4.4.4 ``Effects on Accuracy'' in the revised manuscript.
     %
@@
     %
-    Followed your suggestion, we additionally evaluate the effects of model complexity on accuracy in Section 4.1 ``Effects of Hyper-parameters on Performance'' in the revised manuscript.
+    Followed your suggestion, we additionally evaluate the effects of model complexity on accuracy in a new subsection Section 4.1.4 ``Effects on Accuracy'' in Section 4.1 ``Effects of Hyper-parameters on Performance''.
     %
-    We add a discussion on how the hyper-parameters of GNNs affect the accuracy.
+    We add a discussion of how hyper-parameters of GNNs affect accuracy.
     %

### 2020-12-27 NEUROC/ms.tex
更改了一遍语法

@@
         %
-        They make the development of GNNs convenient, but their performance bottlenecks on large datasets is not well studied.
+        They make the development of GNNs convenient, but their performance bottlenecks on large datasets are not well studied.
         %
@@
         %
-        The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementation still has room for improvement.
+        The sampling techniques are essential for GNN training and inference on big graphs with GPUs, but their current implementation still has non-trivial overheads in sampling and data transferring.
 	\end{abstract}

### 2020-12-27 NEUROC/sec7-conclusion.tex
更改了一遍语法

@@
 %
-Fixing other hyper-parameters, the training time, inference time and memory usage increase linearly with each hyper-parameter of the four GNNs.
+Fixing other hyper-parameters, the training time, inference time, and memory usage increase linearly with each hyper-parameter of the four GNNs.
 %
@@
 %
-Adopting sampling techniques can reduce the memory usage of training and inference significantly.
+Adopting sampling techniques can reduce the memory usage of training and inference significantly, without sacrificing accuracy. 
 %

### 2020-12-27 NEUROC/sec7-conclusion.tex
更新致谢信息.

@@
 
-This work is funded in part by the National Key R\&D Program of China [grant number 2019YFC1711000], the China NSF Grants [grant number U1811461, 62072230], and the Collaborative Innovation Center of Novel Software Technology and Industrialization; and the program B for Outstanding PhD candidate of Nanjing University.
+This work is funded in part by the National Key R\&D Program of China (2019YFC1711000), the China NSF Grants (No.
+U1811461, 62072230), the Collaborative Innovation Center of Novel Software Technology and Industrialization, Alibaba Innovative Resarch Project, and the program B for outstanding PhD candidate of Nanjing University.

### 2020-12-27 NEUROC/Response-MajRev/response_letter-version2.tex
更新致谢信息.
放大response中的图片.

@@
         \centering
-        \subfloat[\texttt{amc}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-computers.pdf}}
-        \subfloat[\texttt{amp}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-photo.pdf}}
-        \subfloat[\texttt{fli}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
+        \subfloat[\texttt{amc}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-computers.pdf}}
+        \subfloat[\texttt{amp}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-photo.pdf}}
+        \subfloat[\texttt{fli}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
         \caption{Comparison of wall-clock training time and inference time on different datasets.}
@@
             \subfloat[\texttt{fli}\label{fig:exp_graphsage_sampling_accuracy_on_fli}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
-            \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
+            \caption{Test accuracy of the neighbor sampler under different batch sizes. FULL means that the full graph participated in the training.}
             \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
@@
             \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
-            \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
+            \caption{Test accuracy of the cluster sampler under different batch sizes. FULL means that the full graph participated in the training.}
             \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}

### 2020-12-27 NEUROC/sec4-experiments.tex
更新section 4.

@@
 %
-Taking GGNN as an exmple, \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} shows the effects of hyper-parameters on inference time of GGNN.
+Taking GGNN as an exmple, \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} shows the effects of hyper-parameters on the inference time of GGNN.
 %
-By cross-comparing \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}, the trends of inference time and training time were the same: as $dim(\MyVec{h}^1_x)$ increased, the vertex and edge calculation time both grew linearly when $dim(\MyVec{h}^1_x)$ was large enough.
+By cross-comparing \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}, the trends of the inference time and training time were the same: as $dim(\MyVec{h}^1_x)$ increased, the vertex and edge calculation time both grew linearly when $dim(\MyVec{h}^1_x)$ was large enough.
 %
@@
 
-We further measured the effects of the hyper-parameters on the peak GPU memory usage during training in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
+We further measured the effects of hyper-parameters on the peak GPU memory usage during training in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
 %
@@
 %
-The effects of the hyper-parameters on inference memory usage were the same as training.
+The effects of hyper-parameters on the inference memory usage were the same as the training.
 %

### 2020-12-27 NEUROC/sec4-experiments.tex

@@
 %
-Algorithm engineers could adjust hyper-parameters according to the complexity analysis to avoid explosive growth in training/inference time and memory usage.
+Algorithm engineers could adjust hyper-parameters according to the complexity analysis to avoid explosive growth in the training/inference time and memory usage.
 %
-The accuracy of GNNs was much more sensitive to the dimensions of hidden vectors/heads than the other hyper-parameters.
+The accuracy of GNNs was much more sensitive to the dimension of hidden vectors/heads than the other hyper-parameters.
 %

### 2020-12-27 NEUROC/sec4-experiments.tex
更新section 4.

@@
 %
-Since the inference only conducted the forward propagation from the input layer to the prediction layer, the time of inference was very close to the time of the forward phase in training.
+Since the inference only conducted the forward propagation from the input layer to the prediction layer, the inference time was very close to the time of the forward phase in training.
 %

### 2020-12-27 NEUROC/ms.tex
更新致谢信息.
更新其他材料
NEURO Computing R1

@@
         % 
-		We breakdown their running time and memory usage, evaluate the effects of hyper-parameters, and assess the efficiency of the sampling techniques.
+		We decompose their running time and memory usage, evaluate the effects of hyper-parameters and assess the efficiency of the sampling techniques.
         %
-		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training and inference time and memory usage.
-        %
-		%Future optimizations can focus on it.
+		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training/inference time and memory usage.
         %

### 2021-02-21 NEUROC/sec7-conclusion.tex
sec7增加了Future Work和response_letter-Rev2_version1

@@
 
+% start, added by wangyunpan, 2021-2-21
+In the future, we will focus on but not limited to the following directions:
+%
+\begin{enumerate}
+    \item \emph{Performance bottlenecks in training/inference with multi-GPUs or distributed environments.}
+    %
+    For massive data in the real world, multi-GPUs and distributed training/inference are often the more common methods\cite{zhang2020_analysis_neugraph, zhu2019_aligraph}.
+    %
+    These methods will inevitably introduce overheads such as communication between GPUs (inter-machines). 
+    %
+    How these overheads affect performance bottlenecks is worthy to focus on.
+    %
+    \item \emph{Impacts of different programming models on performance bottlenecks.}
+    %
+    Our work is based on the mainstream programming model---messaging framework.
+    %
+    However, some GNNs systems also proposed some new programming models.
+    %
+    For example, NeuGraph\cite{zhang2020_analysis_neugraph} proposed the SAGA framework, 
+    which includes four stages: Scatter, ApplyEdge, Gather, and ApplyVertex;
+    %
+    EuGN\cite{he2019_EnGN} provides an edge-centric programming model.
+    %
+    Whether different programming models will lead to changes in performance bottlenecks is worth discussing.
+    %
+    \item \emph{Impacts of spatial-temporal graph on performance bottlenecks.}
+    %
+    Spatial-temporal graphs appear in a variety of applications such as traffic speed forecasting\cite{li2018_DCRNN}, 
+    driver maneuver anticipation\cite{jain2016_SRNN}, and human action recognition\cite{yan2018_STGCN}.
+    %
+    Learning hidden patterns from spatial-temporal graphs becomes increasingly important.
+    %
+    Many GNNs are also proposed\cite{li2018_DCRNN, jain2016_SRNN, yan2018_STGCN, seo2018_SSGCN, yu2018_STGCN}.
+    %
+    Whether spatial-temporal graphs will affect performance is worthy of our attention.
+    %
+\end{enumerate}
+% end, added by wangyunpan, 2021-2-21
 \section*{Acknowledgements}

### 2021-02-21 NEUROC/sec7-conclusion.tex
修正了一些单复数的问题

@@
     %
-    \item \emph{Impacts of spatial-temporal graph on performance bottlenecks.}
+    \item \emph{Impacts of spatial-temporal graphs on performance bottlenecks.}
     %
@@
     %
-    Whether spatial-temporal graphs will affect performance is worthy of our attention.
+    Whether spatial-temporal graphs will affect performance bottlenecks is worthy of our attention.
     %

### 2021-02-22 NEUROC/sec7-conclusion.tex
更新Future work部分。

--- 2020-12-27 NEUROC/sec7-conclusion.tex
@@
-\section{Conclusion}
+\section{Conclusion and Future Work}
 \label{sec:conclusion}
@@
 
+In this work, we analyze performance bottlenecks in a \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
+%
+Performance bottlenecks in multi-GPU/distributed GNN training/inference, dynamic graphs and other GNN frameworks are also worth studying.
+%
+In the future, we plan to extend our analysis of performance bottlenecks in GNN training/inference with the following directions:
+%
+\begin{enumerate}
+    \item \emph{Multi-GPU or distributed environment.}
+    %
+    To handle large-scale graph datasets, multi-GPU and distributed training/inference are necessary.
+    %
+    These methods will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
+    %
+    How these overheads affect performance bottlenecks is worthy to focus on.
+    %
+    \item \emph{Spatial-temporal graph datasets.}
+    %
+    Spatial-temporal graphs have dynamic topology structures.
+    %
+    They appear in a variety of applications like traffic speed forecasting \cite{li2018_DCRNN} and human action recognition \cite{yan2018_STGCN}.
+    %
+    %Learning hidden patterns from spatial-temporal graphs becomes increasingly important.
+    %
+    Many new GNNs are proposed to handle this kind of graphs.
+    %
+    How the performance bottlenecks of these GNNs are different from the classic GNNs is also worthy of in-depth study.
+    %
+    %Whether spatial-temporal graphs will affect performance is worthy of our attention.
+    %
+    \item \emph{Other GNN frameworks.}
+    %
+    In this work, we conducted the anlaysis with the popular message-passing framework.
+    %
+    Some emerging GNN learning systems also adopt different GNN frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
+    %
+    Whether different frameworks lead to different performance bottlenecks is worth discussing.
+\end{enumerate}
+
 \section*{Acknowledgements}

### 2021-02-22 NEUROC/Response-MinorRev/response_letter-minor-rev.tex
更新response的情况.

--- 2020-12-27 NEUROC/Response-MajRev/response_letter-version2.tex
@@
 % General intro text goes here
-We thank the reviewers for their critical assessment and insightful comments on our work.
+We thank the reviewers for their insightful comments on our work.
 %
-We have made extensive modifications to our manuscript, including adding more experiments and improving the presentation.
-%
-In the following, we first summarize the major changes we made.
-%
-%We also prepare an \emph{annotated version} for our revised manuscript.
-%
-%In the annotated version, changes corresponding to each point are all highlighted by red squares.
-
-\subsection*{Summary of Changes}
-
-\begin{enumerate}
-\item According to reviewer 1's comments, we have added experiments on the performance bottleneck analysis of GNN inference.
-%
-Specifically, we added experiments on how the hyper-parameters of GNNs affect the elapsed time and the memory usage of inference in Section 4.1.2 ``Effects on Inference Time'' and Section 4.1.3 ``Effects on Peak Memory Usage'', respectively.
-%
-We presented the time breakdown analysis of GNN inference in Section 4.2.4.
-%
-We also presented the memory usage analysis of GNN inference in Section 4.3, and the performance bottlenecks of the sample-based inference were analyzed in Section 4.4.3.
-
-\item According to reviewer 2's comments, we have added an evaluation of how the model complexity and the sampling techniques affect the accuracy of GNNs.
-%
-Specifically, we evaluated the effects of hyper-parameters of GNNs on accuracy in Section 4.1.4.
-%
-We also compared the accuracy of the four typical GNNs in that section.
-%
-Finally, we analyzed the effects of the sampling techniques on accuracy in Section 4.4.4.
-
-\item We have adjusted the abstract, Section 1 ``Introduction'', Section 5 ``Insights'', and Section 7 ``Conclusion'' according to the new findings on inference time and accuracy.
-
-\item We have polished the presentation of our manuscript.
-%
-We unified the symbol usage through the manuscript and added a table to summarize the frequently-used symbols as suggested by reviewer 1.
-%
-We improved the description of the sub-layer concept in Section 2.2 and Section 2.3.
-%
-We also replotted some figures to improve readability.
-
-\end{enumerate}
-
-We then respond to the concerns of all reviewers point by point as follows.
+We have made modifications to our manuscript according to Reviewer 1's comments.
 
@@
 \begin{point}
-    The authors conduct an empirical analysis of performance bottlenecks in graph neural network training.
-The authors identify the edge-related calculation is the performance bottleneck.
-Experimental of several GNN variants, such as GCN, GGNNNN, GAT and GaAN on six real-world graph datasets verify the importance of the findings.
-The experimental analysis is sufficient.
-However, there are some tiny issues in this paper.
+    In the revised manuscript, the authors have addressed all my concerns, especially adding more computation efficiency discussion.
+Current version looks very impressive.
+Just a small issue left.
+Some discussions about limitations or future efforts should be better added.
 \end{point}
@@
 \begin{reply}
-    Thank you for your comments on our manuscript.
+    Thank you for the insightful suggesion.
     %
@@
 
-% R1Q1
-\begin{point}
-	There are lots of symbols in this paper. Some symbols are reused and confusing, such as s denotes sub-layers or edge features.
-\end{point}
-
-% Our reply
-\begin{reply}
-    We apologize for the confusing use of symbols.
-    %
-    To clarify the symbol usage, we have unified the usage of symbols in the revised manuscript.
-    %
-    After revision, each symbol only represents one meaning.
-
-    Specifically, we use $\boldsymbol{s}$ to represent aggregated vectors in graph neurons.
-    %
-    We use $\boldsymbol{s}^l_x$ to denote the aggregated vector of the graph neuron corresponding to the vertex $v_x$ in the GNN layer $l$.
-    %
-    If the GNN layer $l$ has sub-layers, $\boldsymbol{s}^{l,i}_x$ represents the aggregated vector of $v_x$ in the $i$-th sub-layer.
-    %
-    As for edges and their feature vectors, we use $e_{y,x}$ to represent an edge pointing from $v_y$ to $v_x$ and we use $\boldsymbol{e}_{y,x}$ to represent its feature vector.
-
-    To facilitate readers to quickly locate the meaning of symbols, we have added Table 1 at the beginning of Section 2 ``Review of Graph Neural Networks'' in the revised manuscript.
-
-%    \begin{table}[H]
-%        \footnotesize
-%        \caption{Frequently-used Symbols}
-%        \label{tab:symbols}
-%        \centering
-%        \begin{tabular}{p{3em}lp{35em}}
-%            \toprule
-%            Category & Symbol & Meaning \\
-%            \midrule
-%            \multirow[c]{4}{3em}{Graph Structure}& $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ & The simple undirected input graph with the vertex set $\mathcal{V}$ and the edge set $\mathcal{E}$. \\
-%            & $v_x$ & The $x$-th vertex of the input graph. \\
-%            & $e_{y,x}$ & The edge pointing from $v_y$ to $v_x$ of the input graph. \\
-%            & $\mathcal{N}(v_x)$ & The adjacency set of $v_x$ in the input graph. \\ 
-%            & $\bar{d}$ & The average degree of the input graph. \\ \midrule
-%            \multirow[c]{6}{3em}{GNN Definition}& $L$ & The number of GNN layers. \\
-%            & $K$ & The number of heads in a GNN layer. \\
-%            & $\phi^l$ & The messaging function of the GNN layer $l$. \\
-%            & $\Sigma^l$ & The aggregation function of the GNN layer $l$. \\
-%            & $\gamma^l$ & The vertex updating function of the GNN layer $l$. \\ 
-%            & $\phi^{l,i}$ / $\Sigma^{l,i}$ / $\gamma^{l,i}$ & The messaging/aggregation/updating function of the $i$-th sub-layer of the GNN layer  $l$.\\
-%            & $\textcolor{blue}{\boldsymbol{W}^l, \boldsymbol{W}^{(k)}/\boldsymbol{b}, \boldsymbol{a}}$ & The matrices/vectors represented by the blue characters are the weight matrices/vectors that need to be learned in the GNN.
-\\  \midrule
-%            \multirow[c]{8}{3em}{Vector}& $\boldsymbol{v}_x$ & The feature vector of the vertex $v_x$. \\
-%            & $\boldsymbol{e}_{y,x}$ & The feature vector of the edge $e_{y,x}$.  \\
-%            & $\boldsymbol{h}_x^{l}$ &  The {input} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$. \\
-%            & $\boldsymbol{h}_x^{l+1}$ &  The {output} hidden vector of the graph neuron corresponding to $v_x$ in the GNN layer $l$.\\
-%            & $\boldsymbol{m}_{y,x}^l$ & The message vector of the edge $e_{y,x}$ outputted by $\phi^l$ of the GNN layer $l$. \\
-%            & $\boldsymbol{s}_{x}^l$ & The aggregated vector of the vertex $v_x$ outputted by $\Sigma^l$ of the GNN layer $l$. \\
-%            & $\boldsymbol{h}_{x}^{l,i}$ / $\boldsymbol{m}_{y,x}^{l,i}$ / $\boldsymbol{s}_{x}^{l,i}$ & The hidden/message/aggregated vector of the vertex $v_x$ outputted by $\gamma^{l,i}$/$\phi^{l,i}$/$\Sigma^{l,i}$ of the $i$-th sub-layer of the GNN layer $l$.
-\\
-%            & $d^l_{in}$, $d^l_{out}$ &  The dimension of the input/output hidden vectors of the GNN layer $l$. \\
-%            & $dim(\MyVec{x})$ & The dimension of a vector $\MyVec{x}$. \\
-%            \bottomrule
-%        \end{tabular}
-%\end{table}
-
-\end{reply}
-
-% R1Q2
-\begin{point}
-    Some typical applications of GNNs should be included, such as video object segmentation [ref1], human-object interaction [ref2] and human-parsing [ref3].[1] Zero-shot video object segmentation via attentive graph neural networks,iccv 2019 [2] Learning human-object interactions by graph parsing neural networks, eccv 2018.
-[3] Hierarchical human parsing with typed part-relation reasoning, cvpr 2020.
-\end{point}
-
-\begin{reply}
-	Thank you for pointing out the missing references.
-Computer vision is indeed an important application area of graph neural networks.
-We have added the mentioned references in Section 1 ``Introduction'' in the revised manuscript.
-\end{reply}
-
-% R1Q3
-\begin{point}
-There are some grammar errors and typos:
-\\
-  - `Take the demo GNN in Figure 1(a) as  the example.'
-\\
- - `to calculate the  output hidden vector $h^{l+1}$ of the current layer l, i.e., $h^{l+1}$ = $\gamma^l(h^l,s^l)$ The end-to-end training requires…'
-\\
- - `Implementing it with the specially optimized basic operators on the GPU is a potential optimization'
-\\
- - The sentences in the experimental section should be unified.
-\end{point}
-
-\begin{reply}
-
-    Thank you for pointing them out.
-    %
-    We feel sorry for our carelessness.
-    %
-    We have proofread our revised manuscript to eliminate grammar errors and typos.
-    %
-    We have also unified the tenses of the sentences in Section 3 ``Evaluation Design'' and Section 4 ``Evaluation Results and Analysis''.
-    %
-    Specifically, we use the past tense to describe experimental methods, results, and what they indicate.
-    %
-    We use the present tense in the sentences that FigureX or Table X is the subject of the sentences.
-
-\end{reply}
-
-% R1Q4
-\begin{point}
-    Figures 6 and 7 should be adjusted. The figures and fonts are too small.
-\end{point}
-
-\begin{reply}
-
-    As suggested, we have split Figure 6 into four figures (Figure 6 to 9) in the revised manuscript to enlarge their subfigures.
-    %
-    Besides Figure 6 and Figure 7, we have also adjusted font sizes in all figures to make them equal to or greater than the font size of figure captions.    
-\end{reply}
-
-% R1Q5
-\begin{point}
-    In my view, computation efficiency is to describe the testing or validation process.
-Except for reporting and analyzing the training times, it is meaningful to discuss the inference time.
-This is also an important point of view for deep learning researchers to be concerned about.
-\end{point}
-
-\begin{reply}
-    Thank you for the insightful comment and suggestion.
-    %
-    The efficiency of inference (including inference time and memory usage) is indeed important for deep learning researchers and engineers.
-    %
-    We add a brief description of GNN inference in Section 2.5 ``Inference with GNNs'' in the revised manuscript.
-    %
-    As suggested, we also use the same methodology as the training phase to analyze the performance bottlenecks in the inference phase.
-    %
-    We add corresponding experimental results in every subsection of Section 4 ``Evaluation Results and Analysis.''
-    %
-    \begin{enumerate}
-
-    \item In Section 4.1 ``Effects of Hyper-parameters on Performance'', we conduct extra experiments on how the hyper-parameters of GNNs affect the time and peak memory usage of inference.
-    %
-    We find that the effects of hyper-parameters on the inference time and memory usage are the same as the training time.
-    %
-    When the other hyper-parameters are fixed, each hyper-parameter itself affects the training time and memory usage in a linear way.
-    %
-    The complexity analysis of GNNs holds for both training and inference.
-    %
-    We present specific experimental results in Section 4.1.2 ``Effects on Inference Time'' and Section 4.1.3 ``Effects on Peak Memory Usage'' in the revised manuscript.
-
-    \item In Section 4.2 ``Time Breakdown Analysis'', we additionally conduct time breakdown analysis for GNN inference and compare the similarities and differences between training and inference.
-    %
-    As for the similarities, we find that the performance characteristics of inference and training are highly similar on the layer level and the step level of edge calculation.
-    %
-    The edge calculation stage is the main performance bottleneck for both training and inference.
-    %
-    %The specific performance bottlenecks of the edge calculation stage depend on the time complexity of the messaging function $\phi$ of the GNN.
-    %
-    As for the differences, training and inference are different mainly in two aspects: the elapsed time and the top time-consuming basic operators.
-    %
-    The inference time is much less than the training time.
-    %
-    The top time-consuming basic operators used in the backward phase of training are replaced by the basic operators used in the prediction layer of inference.
-    %
-    The inference time is 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time on average, as shown in Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference}.
-    %
-    Since the inference only conducted the forward propagation from the input layer to the prediction layer, the inference time is very close to the time of the forward phase in training.
-    %
-    For the top time-consuming basic operators, some top operators from the backward phase in training are replaced by operators from the prediction layer in inference.
-    %
-    For example, Figure~\ref{fig:compare_top_basic_operators} shows that the \texttt{gather} operator used in the backward phase of training is replaced by the \texttt{index} operator used in the prediction layer of GCN.
-    %
-    Though the top time-consuming basic operators are changed, they still indicate that GPUs are suitable for conducting GNN inference.
-    %
-    We present more details of time breakdown analysis on GNN inference in Section 4.2.4 ``Performance Bottlenecks in Inference'' in the revised manuscript.
-
-    \begin{figure}[h]
-        \centering
-        \subfloat[\texttt{amc}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-computers.pdf}}
-        \subfloat[\texttt{amp}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-photo.pdf}}
-        \subfloat[\texttt{fli}]{\includegraphics[width=0.3\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
-        \caption{Comparison of wall-clock training time and inference time on different datasets.}
-        \label{fig:compare_wall_clock_time_of_training_and_inference}
-    \end{figure}
-
-    \begin{figure}[h]
-        \centering
-        \subfloat[Training]{\includegraphics[width=0.4\columnwidth]{../figs/experiments/exp_top_basic_ops_gcn.pdf}}
-        \subfloat[Inference]{\includegraphics[width=0.4\columnwidth]{../figs/experiments/exp_inference_full_top_basic_ops_gcn.pdf}}
-        \caption{Top 5 time-consuming basic operators of GCN. The time proportion of each basic operator is averaged over all datasets with the error bar indicating the maximum and the minimum.}
-        \label{fig:compare_top_basic_operators}
-    \end{figure}
-
-    \item In Section 4.3 ``Memory Usage Analysis'', we conduct a group of experiments to evaluate the peak memory usage during inference.
-    %
-    We find that the memory usage of inference also mainly comes from the edge calculation stage, the same as training.
-    %
-    However, the memory expansion ratios of inference are much less than training.
-    %
-    The memory expansion ratios of inference are 45\% to 83\% (GGNN), 52\% to 61\% (GAT), and 37\% to 69\% (GaAN) of training, as indicated by Figure~\ref{fig:compare_memory_expasion_ratio}.
-    %
-    GGNN, GAT, and GaAN have to cache some intermediate results during training, the memory space of those results is saved during inference.
-    %
-    However, the memory expansion ratios of inference are still high, preventing us from performing inference on big graphs.
-    %
-    More details are available in Section 4.3 ``Memory Usage of Inference'' in the revised manuscript.
-
-    \begin{figure}[h]
-        \subfloat[Training]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_memory_expansion_ratio.pdf}}
-        \subfloat[Inference]{\includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}}
-        \caption{Memory expansion ratios of typical GNNs.}
-        \label{fig:compare_memory_expasion_ratio}
-    \end{figure}
-
-    \item In Section 4.4 ``Effects of Sampling Techniques on Performance'', we additionally conduct experiments to analyze performance bottlenecks in sample-based inference.
-    %
-    We find that the batch size used in inference should be smaller than training to avoid the out of memory exception on the GPU side.
-    %
-    The current implementation of the inference sampler in PyG is still inefficient.
-    %
-    The overheads of sampling and data transferring are significant in the total inference time.
-    %
-    Under the same batch size, we find that the subgraph sampler used in inference tends to produce larger subgraphs than the neighbor sampler used in training.
-    %
-    Thus, the batch size must be small to avoid the out of memory exception on the GPU side.
-    %
-    At the same time, the overheads brought by sampling and data transferring from CPU to GPU become obvious when the batch size was small.
-    %
-    They account for near half of the total inference time on the \texttt{amp} and \texttt{cam} datasets, as shown in Figure~\ref{fig:time_breakdown_of_inference_sampler}.
-    %
-    We present more details of our experimental analysis in Section 4.4.3 ``Performance Bottlenecks in Inference'' in the revised manuscript.
-
-     \begin{figure}[h]
-            \centering           
-            \includegraphics[width=0.5\columnwidth]{../figs/experiments/exp_inference_sampling_fix_batch_size_train_time_stack_2048.pdf}
-            \caption{Inference time per batch breakdown under the batch size of 2048.}
-            \label{fig:time_breakdown_of_inference_sampler}
-    \end{figure}
-
-    \end{enumerate}
-
-\end{reply}
-
-% Begin a new reviewer section
-\reviewersection
-
-\begin{point}
-    In the paper, authors accomplished a unique study and analysis on GNN models training complexity.
-The articles first review and development history of GNNs and creatively model all architectures as input layers, intermediate layers of graph neurons and prediction layers.
-And they quantitatively summarize the time and space complexity of 4 representative GNNs, including graph convolution, gated recurrent graph net, graph attention net and GraphSage.
-Most importantly, the article first break down complexity into operator level and offered analysis of good granularity, giving reader more guidance in future study.
-At last, the solid experiments included the study of effects of hyper-parameters and a comparison of two major sampling techniques: neighbor sampling and cluster sampling.
-\end{point}
-
-\begin{reply}
-    Thank you for your positive comments on our manuscript.
-    %
-    We have carefully revised the manuscript according to your comments and suggestions in the following points.
-    %
-    %We highlight our modifications with red squares point by point in the annotated version of the revised manuscript.
-\end{reply}
-
-\begin{point}
-    In general, the paper was well written and organized with good structure and clear narratives.
-Just some minor language errors like line Page 8, Line 208, "In active graph neurons" =\textgreater "Inactive graph neurons".
-\end{point}
-
-% R2Q1
-\begin{reply}
-    We feel sorry for our carelessness.
-    %
-    We have proofread our revised manuscript to eliminate such language errors.
-\end{reply}
-
-% R2Q2
-\begin{point}
-    I was impressed by the way that authors categorize layers and operators in GNNs, very clear and instructive.
-
-    It is also pretty neat to divide layer time complexity into two buckets: vertex calculation and edge calculation.
-The data model pretty well summarizes mainstream GNN layer architectures.
-And this analysis is very insightful for layer profiling.
-
-    And the experimental evaluation were done over 6 large graph-structured datasets.
-\end{point}
-
-\begin{reply}
-    Thank you for the positive comment.
-\end{reply}
-
-% R2Q3
-\begin{point}
-    While, one major drawback is that I did not clearly see the analysis complexity v.s.
-accuracy.
-For example, in Figure 19 and 20, I did not see network accuracy from those 4 GNNs.
-There is always tradeoff between model complexity and model performance, and in some scenarios where high complexity is allowed, a sophisticated model of more powerful representation capability is still needed.
-\end{point}
-
-\begin{reply}
-    Thank you for the valuable suggestions.
-    %
-    The model complexity directly affects accuracy.
-    %
-    To analyze the relationship between model complexity and accuracy, we have conducted two kinds of extra experiments in the revised manuscript: (1) how hyper-parameters of GNNs (like the dimension of hidden vectors and the number of heads) affect accuracy (in Section 4.1.4); (2) how the batch size in the sampling methods affects the accuracy of GNNs (in Section 4.4.4).
-    %
-    In this reply, we focus on the first kind of experiments.
-    %
-    We focus on the second kind of experiments in the next reply.
-
-    The hyper-parameters determine the model complexity of GNNs and thus affect accuracy.
-    %
-    To find out the effects of hyper-parameters, we measure and compare the test accuracy of the four GNNs trained with different hyper-parameters.
-    %
-    We have two main findings.
-
-    First, the accuracy of GNNs is much more sensitive to the dimension of hidden vectors (for GCN/GGNN/GaAN) and the dimension of each head (for GAT) than the other hyper-parameters.
-    %
-    Figure~\ref{fig:effect_of_hyper_parameter_on_accuracy_of_gaan} shows the results of GaAN as an example.
-    %
-    The accuracy of GaAN is low when the dimensions are very low ($\leq 8$).
-    %
-    As the dimensions increase to a certain threshold, GaAN gains sufficient representation capability to achieve better accuracy.
-    %
-    But the high dimensions ($\geq 2048$) are also harmful to the accuracy of the \texttt{amp} dataset, as they increase the risk of overfitting.
-    %
-    The results of the other GNNs are available in Section 4.1.4 ``Effects on Accuracy'' in the revised manuscript.
-    %
-
-    \begin{figure}[h]
-        \includegraphics[width=1.0\columnwidth]{../figs/experiments/exp_hyperparameter_on_accuracy_gaan.pdf}
-        \caption{Effects of hyper-parameters on accuracy of GaAN.}
-        \label{fig:effect_of_hyper_parameter_on_accuracy_of_gaan}
-
-    \end{figure}
-
-    Second, the relative accuracy between the four GNNs varies greatly with different datasets.
-    %
-    There is no absolute winner.
-    %
-    We compare the best accuracy that each GNN achives on every dataset in Figure~\ref{fig:exp_hyperparameter_on_accuracy_alg_contrast}.
-    %
-    The best accuracy of the four GNNs are very close.
-    %
-    It is also close to the accuracy reported in [\cite{shchur2018_pitfall_of_gnn, zeng2020_graphsaint}].
-    %
-    GaAN that has the highest complexity performs slightly better than the other GNNs, winning three out of five datasets.
-    %
-    Simple GNN models (such as GCN) can still achieve good accuracy with proper hyper-parameter settings.
-
-    \begin{figure}[h]
-        \centering
-        \includegraphics[width=3.5in]{../figs/experiments/exp_hyperparameter_on_accuracy_alg_contrast.pdf}
-        \caption{Best accuracy that each GNN achieves on different datasets.}
-        \label{fig:exp_hyperparameter_on_accuracy_alg_contrast}
-    \end{figure}
-
-    Besides, we add more details on the proportions of the train/evaluation/test sets of the datasets in Section 3.1 ``Experimental Setting'' in the revised manuscript.
-    %
-    Since the vertices of the \texttt{cam} dataset are not attached with feature vectors, we exclude it from the accuracy evaluation.
-\end{reply}
-
-\begin{point}
-    Sampling method is definitely going to reduce model complexity, since all models complexity depend on graph node number N, while performance is going to be compromised as well.
-I would like to see authors resolve the concern of significant accuracy drop after applying aggressive sampling of subgraphs.
-\end{point}
-
-\begin{reply}
-
-    Thanks for the insightful comment.
-    %
-    The sampling methods indeed affect the test accuracy of GNN models [\cite{hamilton2017_graphsage, chiang2019_cluster_gcn, zeng2020_graphsaint}].
-    %
-    %With or without the sampling methods, the structure of the GNN remains the same, but the gradients of the model parameters are calculated differently, affecting the accuracy of the GNN model.
-    %
-    %With sampling, each GNN layer still consists of $|\mathcal{V}|$ graph neurons ($|\mathcal{V}|$ is the number of vertices in the graph), but only graph neurons corresponding to the vertices in the sampled subgraph are activated.
-    %
-    %Thus, the model parameters are updated according to the gradients calculated on the sampled subgraph, instead of the whole graph.
-    %
-    %In other words, the GNN models are trained in a \emph{batch} gradient descent manner (i.e., full-batch training) without sampling.
-    %
-    %With sampling, the GNN models are trained with \emph{mini-bach} stochastic gradient descent.
-    %
-    To find out how the sampling techniques affect accuracy, we train the four typical GNNs with different batch sizes and compare the accuracy with the full-batch training.
-    %
-    For each combination of dataset and GNN, we use the hyper-parameters that achieve the highest accuracy under the full-batch training.
-    %
-    In most cases, the test accuracy of the sampling methods is just slightly lower than the accuracy of the full-batch training when the relative batch size $\geq 3\%$.
-    %
-    Among the two sampling methods, the performance of the cluster sampler is more stable than the neighbor sampler.
-    %
-    Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and Figure~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster} shows the accuracy of the two typical sampling methods under different batch sizes.
-    %
-    The results of the other datasets are available in Section 4.4.4 ``Effects on Accuracy'' in the revised manuscript.
-    %
-    In several cases (like GaAN in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amp} and Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_amc}), the accuracy of the neighbor sampler is even higher than the full-batch training.
-    %
-    The test accuracy of the cluster sampler is close to the accuracy of full-batch training, while the test accuracy of the neighbor sampler shows more obvious differences for different GNNs.
-
-    \begin{figure}[h]
-            \centering
-            \subfloat[\texttt{amp}\label{fig:exp_graphsage_sampling_accuracy_on_amp}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
-            \subfloat[\texttt{amc}\label{fig:exp_graphsage_sampling_accuracy_on_amc}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
-            \subfloat[\texttt{fli}\label{fig:exp_graphsage_sampling_accuracy_on_fli}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
-            \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
-            \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
-        \end{figure}
-
-        \begin{figure}[h]
-            \centering
-            \subfloat[\texttt{amp}\label{fig:exp_cluster_sampling_accuracy_on_amp}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
-            %
-            \subfloat[\texttt{amc}\label{fig:exp_cluster_sampling_accuracy_on_amc}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
-            %
-            \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
-            \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
-            \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
-        \end{figure}
-
-    The results indicate that the relationships between batch size and test accuracy are complex, especially for the neighbor sampler.
-    %
-    Larger batch size does not always bring higher accuracy, like GAT in Figure~\ref{fig:exp_graphsage_sampling_accuracy_on_fli}. 
-    %
-    Our observations are similar to [\cite{zeng2020_graphsaint}].
-    %
-    We believe that how to automatically select a proper batch size is a topic worth studying.
-\end{reply}
-
-\begin{point}
-    Hope authors supplement the effect of sampling and GNNs on accuracy while comparing different complexity of model and sampling methods.
-\end{point}
-
-\begin{reply}
-
-    We are grateful for your insightful suggestion.
-    %
-    Followed your suggestion, we additionally evaluate the effects of model complexity on accuracy in a new subsection Section 4.1.4 ``Effects on Accuracy'' in Section 4.1 ``Effects of Hyper-parameters on Performance''.
-    %
-    We add a discussion of how hyper-parameters of GNNs affect accuracy.
-    %
-    We also compare the test accuracy of different GNN models on the same dataset.
-
-    We also additionally evaluate the effects of sampling techniques on accuracy in Section 4.4 ``Effects of Sampling Techniques'' in the revised manuscript.
-    %
-    We present the experimental results and related discussion in a new subsection Section 4.4.4 ``Effects on Accuracy''.
-\end{reply}
-
 \bibliographystyle{apalike}

### 2021-02-22 NEUROC/sec7-conclusion.tex
更新Section 7.

@@
 %
-Performance bottlenecks in multi-GPU/distributed GNN training/inference, dynamic graphs and other GNN frameworks are also worth studying.
+Performance bottlenecks in multi-GPU/distributed GNN training/inference with dynamic graphs and other GNN frameworks are also worth studying.
 %
@@
 \begin{enumerate}
-    \item \emph{Multi-GPU or distributed environment.}
+    \item \emph{Multi-GPU and distributed GNN training/inference.}
     %
@@
     %
-    %Learning hidden patterns from spatial-temporal graphs becomes increasingly important.
+    %Learning hidden patterns from spatial-temporal graphs become increasingly important.
     %
-    Many new GNNs are proposed to handle this kind of graphs.
+    Many new GNNs are proposed to handle this kind of graph.
     %
@@
     %
-    In this work, we conducted the anlaysis with the popular message-passing framework.
+    In this work, we analyzed with the popular message-passing framework of GNNs.
     %

### 2021-02-22 NEUROC/Response-MinorRev/response_letter-minor-rev.tex
更新response letter和正文.

@@
     %
-    We have revised the manuscript according to your suggestions. 
+    According to the suggestion, we have added a paragraph at the end of Section 7 ``Conclusion and Future Work'' to discuss limitations of our work and points out potential future research directions.
     %
-    Please see the replies below.
+    In this work, we mainly analyze performance bottlenecks of GNN training/inference in a \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
+    %
+    Performance bottlenecks in \emph{multi-GPU}/\emph{distributed} GNN training/inference with \emph{dynamic} graphs and \emph{other} GNN frameworks are also worth studying.
+    %
+    In the future, we plan to extend our work in the following directions:
+    %
+\begin{enumerate}
+    \item \emph{Multi-GPU and distributed GNN training/inference.}
+    %
+    To handle large-scale graph datasets, training/inferring GNNs with multiple GPUs or in a distributed environment is necessary.
+    %
+    Multi-GPU and distributed GNN training/inference will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
+    %
+    How these overheads affect performance bottlenecks is worthy to focus on.
+    %
+    \item \emph{Spatial-temporal graph datasets.}
+    %
+    Spatial-temporal graphs have dynamic topology structures.
+    %
+    They appear in a variety of applications like traffic speed forecasting [\cite{li2018_DCRNN}] and human action recognition [\cite{yan2018_STGCN}].
+    %
+    %Learning hidden patterns from spatial-temporal graphs become increasingly important.
+    %
+    Many new GNNs are proposed to handle this kind of dynamic graphs.
+    %
+    How the performance bottlenecks of these GNNs are different from the classic GNNs is also worthy of in-depth study.
+    %
+    %Whether spatial-temporal graphs will affect performance is worthy of our attention.
+    %
+    \item \emph{Other GNN frameworks.}
+    %
+    In this work, we conducted analysis with the message-passing framework that is popular among existing GNN learning systems.
+    %
+    Some emerging GNN learning systems also adopt different frameworks like SAGA framework [\cite{ma2019_neugraph}] and edge-centric framework [\cite{he2019_EnGN}].
+    %
+    Whether different frameworks lead to different performance bottlenecks is worth further investigation.
+\end{enumerate}
+
 \end{reply}

### 2021-02-22 NEUROC/sec7-conclusion.tex
更新response letter和正文.

@@
 
+\paragraph{Future Work}
+
 In this work, we analyze performance bottlenecks in a \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
@@
 %
-In the future, we plan to extend our analysis of performance bottlenecks in GNN training/inference with the following directions:
+In the future, we plan to extend our analysis of performance bottlenecks in the following directions:
 %
@@
     %
-    To handle large-scale graph datasets, multi-GPU and distributed training/inference are necessary.
+    To handle large-scale graph datasets, training/inferring GNNs with multiple GPUs or in a distributed environment is necessary.
     %
-    These methods will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
+    Multi-GPU and distributed GNN training will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
     %
@@
     %
-    Many new GNNs are proposed to handle this kind of graph.
+    Many new GNNs are proposed to handle this kind of dynamic graphs.
     %
@@
     %
-    In this work, we analyzed with the popular message-passing framework of GNNs.
+    In this work, we conducted analysis with the message-passing framework that is popular among existing GNN learning systems.
     %
-    Some emerging GNN learning systems also adopt different GNN frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
+    Some emerging GNN learning systems also adopt different frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
     %
-    Whether different frameworks lead to different performance bottlenecks is worth discussing.
+    Whether different frameworks lead to different performance bottlenecks is worth further investigation.
 \end{enumerate}

### 2021-02-22 NEUROC/sec7-conclusion.tex
更新了sec7

@@
     %
-    Many new GNNs are proposed to handle this kind of dynamic graphs.
+    Many new GNNs are proposed to handle this kind of dynamic graph.
     %
@@
     %
-    In this work, we conducted analysis with the message-passing framework that is popular among existing GNN learning systems.
+    In this work, we conducted the analysis with the message-passing framework that is popular among existing GNN learning systems.
     %

### 2021-02-25 NEUROC/sec7-conclusion.tex
更新sec7和minorRev, Rong和grammarly语法

@@
 
-In this work, we analyze performance bottlenecks in a \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
+Specifically, in this work, we mainly analyze performance bottlenecks of GNN training/inference in the \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
 %
-Performance bottlenecks in multi-GPU/distributed GNN training/inference with dynamic graphs and other GNN frameworks are also worth studying.
+In fact, performance bottlenecks of GNN training/inference over the multi-GPU or distributed environment, dynamic graphs, and other GNN frameworks are also worth studying.
 %
-In the future, we plan to extend our analysis of performance bottlenecks in the following directions:
+In the future, we plan to explore the GNN training/inference performance analysis under the following scenarios:
 %
 \begin{enumerate}
-    \item \emph{Multi-GPU and distributed GNN training/inference.}
+    \item \emph{Multi-GPU or distributed GNN training/inference.}
     %
-    To handle large-scale graph datasets, training/inferring GNNs with multiple GPUs or in a distributed environment is necessary.
+    To handle large-scale graph datasets, training/inferring GNNs with the multi-GPU environment or the distributed environment is essential.
     %
@@
     %
-    How these overheads affect performance bottlenecks is worthy to focus on.
+    How these overheads affect performance bottlenecks is worthy to study.
     %
@@
     %
-    Spatial-temporal graphs have dynamic topology structures.
+    Spatial-temporal graphs usually have dynamic topology structures.
     %
@@
     %
-    How the performance bottlenecks of these GNNs are different from the classic GNNs is also worthy of in-depth study.
+    The differences of performance impacting issues between these GNNs and the classic GNNs are also worthy of in-depth investigation.
     %
@@
     %
-    In this work, we conducted the analysis with the message-passing framework that is popular among existing GNN learning systems.
+    In this work, we analyzed the widely-used message-passing framework in GNN learning systems.
     %
-    Some emerging GNN learning systems also adopt different frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
+    However, some emerging GNN learning systems adopt different frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
     %
-    Whether different frameworks lead to different performance bottlenecks is worth further investigation.
+    It is interesting to research whether different frameworks would lead to different performance bottlenecks.
 \end{enumerate}

### 2021-02-25 NEUROC/Response-MinorRev/response_letter-minor-rev.tex
更新response letter.

--- 2021-02-22 NEUROC/Response-MinorRev/response_letter-minor-rev.tex
@@
-% !TEX program=pdflatex
+% !TEX program=xelatex
 % LaTeX rebuttal letter example. 
@@
 \documentclass[12pt]{article}
-\usepackage[utf8]{inputenc}
+\usepackage{fontspec} % For loading fonts
 \usepackage{lipsum} % to generate some filler text
 \usepackage{fullpage}
-\usepackage{times}
 \usepackage{amsmath, amsthm, amsfonts}
@@
 \usepackage{natbib}
+\setmainfont{Times New Roman}
 % Vector
@@
     %
-    We have revised the manuscript according to your suggestions. 
+    According to the suggestion, we have added a paragraph at the end of Section 7 ``Conclusion and Future Work'' to discuss the limitations of our work and point out potential future research directions.
     %
-    Please see the replies below.
+    Specifically, in this work, we mainly analyze performance bottlenecks of GNN training/inference in the single-GPU environment on static graphs with the message-passing framework.
+    %
+    In fact, performance bottlenecks of GNN training/inference over the multi-GPU or distributed environment, dynamic graphs and other GNN frameworks are also worth studying.
+    %
+    In the future, we plan to explore the GNN training/inference performance analysis under the following scenarios:
+    %
+\begin{enumerate}
+    \item \emph{Multi-GPU or distributed GNN training/inference.}
+    %
+    To handle large-scale graph datasets, training/inferring GNNs with the multi-GPU environment or the distributed environment is essential.
+    %
+    Multi-GPU and distributed GNN training/inference will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
+    %
+    How these overheads affect performance bottlenecks is worthy to study.
+
+    \item \emph{Spatial-temporal graph datasets.}
+    %
+    Spatial-temporal graphs usually have dynamic topology structures.
+    %
+    They appear in a variety of applications like traffic speed forecasting [\cite{li2018_DCRNN}] and human action recognition [\cite{yan2018_STGCN}].
+    %
+    Many new GNNs are proposed to handle this kind of dynamic graphs.
+    %
+    The differences of performance issues between these GNNs and the classic GNNs are also worthy of in-depth investigation.
+
+    \item \emph{Emerging GNN frameworks.}
+    %
+    In this work, we analyzed the widely-used message-passing framework in GNN learning systems.
+    %
+    However, some emerging GNN learning systems adopt different frameworks like SAGA framework [\cite{ma2019_neugraph}].
+    %
+    It is interesting to research whether different frameworks would lead to different performance bottlenecks.
+\end{enumerate}
+
 \end{reply}

### 2021-02-25 NEUROC/sec7-conclusion.tex
更新正文内容。

@@
 
-Specifically, in this work, we mainly analyze performance bottlenecks of GNN training/inference in the \emph{single-GPU} environment on \emph{static} graphs with the \emph{message-passing} framework.
+Specifically, in this work, we mainly analyze performance bottlenecks of GNN training/inference in the single-GPU environment on static graphs with the message-passing framework.
 %
@@
     %
-    Multi-GPU and distributed GNN training will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
+    Multi-GPU and distributed GNN training/inference will inevitably introduce overheads such as inter-GPU and inter-machine communication. 
     %
@@
     %
-    %Learning hidden patterns from spatial-temporal graphs become increasingly important.
+    Many new GNNs are proposed to handle this kind of dynamic graphs.
     %
-    Many new GNNs are proposed to handle this kind of dynamic graph.
+    The differences of performance issues between these GNNs and the classic GNNs are also worthy of in-depth investigation.
     %
-    The differences of performance impacting issues between these GNNs and the classic GNNs are also worthy of in-depth investigation.
-    %
-    %Whether spatial-temporal graphs will affect performance is worthy of our attention.
-    %
-    \item \emph{Other GNN frameworks.}
+    \item \emph{Emerging GNN frameworks.}
     %
@@
     %
-    However, some emerging GNN learning systems adopt different frameworks like SAGA framework \cite{ma2019_neugraph} and edge-centric framework \cite{he2019_EnGN}.
+    However, some emerging GNN learning systems adopt different frameworks like the SAGA framework \cite{ma2019_neugraph}.
     %
@@
 This work is funded in part by the National Key R\&D Program of China (2019YFC1711000), the China NSF Grants (No.
-U1811461, 62072230), the Collaborative Innovation Center of Novel Software Technology and Industrialization, Alibaba Innovative Resarch Project, and the program B for outstanding PhD candidate of Nanjing University.
+U1811461, 62072230), the Collaborative Innovation Center of Novel Software Technology and Industrialization, Jiangsu, China, Alibaba Innovative Research Project, and the program B for outstanding PhD candidate of Nanjing University.

### 2021-02-26 NEUROC/manuscript-submission-version/main.tex
增加干净的提交版本

--- 2020-12-27 NEUROC/ms.tex
@@
         %
-		The experimental evaluation indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training/inference time and memory usage.
+		The experimental evaluation with PyTorch Geometric indicates that the edge-related calculation is the performance bottleneck for most GNNs, dominating the training/inference time and memory usage.
         %

### 2021-02-27 NEUROC/sec5-insights.tex
更新了正文中的文字问题

@@
 
-    \item \emph{Sampling techniques can significantly reduce the memory usage per batch, but its implementation is still inefficient}.
+    \item \emph{Sampling techniques can significantly reduce the memory usage per batch, but their implementations are still inefficient}.
           %
           The sampling techniques are effective under small batch sizes for both training and inference.
+          %
+          The accuracy of the GNN models trained with the sampling techniques is close to the accuracy of full-batch training.
           %

### 2021-03-19 NEUROC/sec4-experiments.tex
更新了正文中的文字问题
更新了文字问题
Minor revision提交版本.

@@
    \subfloat{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}}
-   \caption{Memory expansion ratios of typical GNNs in Inference.}
+   \caption{Memory expansion ratios of typical GNNs in inference.}
    \label{fig:memory_usage_analysis}
@@
     \includegraphics[width=0.4\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.pdf}
-    \caption{Vertex degree distribution of the sampled subgraph (relative batch size: 6\%) and the original graph. Dataset:\texttt{amp}.}
+    \caption{Vertex degree distribution of the sampled subgraph (relative batch size: 6\%) and the original graph. Dataset: \texttt{amp}.}
     \label{fig:exp_sampling_minibatch_degrees_distribution}
@@
    \centering
-   \subfloat[Average degree]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_avg_degrees.pdf}}
-   \subfloat[Number of edges]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_edges.pdf}}
+   \subfloat[Average degree]{\includegraphics[width=0.4\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_avg_degrees.pdf}}
+   \subfloat[Number of edges]{\includegraphics[width=0.4\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_edges.pdf}}
 

### 2021-03-19 NEUROC/ms.tex
更新单位信息和致谢信息."

@@
     \ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, gurong, yhuang\}@nju.edu.cn}
-	\address{State Key Laboratory for Novel Software Technology, \\Department of Computer Science and Technology, Nanjing University, \\Nanjing 210023, China}
+	\address{State Key Laboratory for Novel Software Technology, Nanjing University, Nanjing 210023, China\\Department of Computer Science and Technology, Nanjing University, Nanjing 210023, China\\Collaborative Innovation Center of Novel Software Technology and Industrialization, Nanjing 210023, China}
 

### 2021-03-19 NEUROC/sec7-conclusion.tex
更新单位信息和致谢信息."

@@
 
-This work is funded in part by the National Key R\&D Program of China (2019YFC1711000), the China NSF Grants (No.
-U1811461, 62072230), the Collaborative Innovation Center of Novel Software Technology and Industrialization, Jiangsu, China, Alibaba Innovative Research Project, and the program B for outstanding PhD candidate of Nanjing University.
+This work is funded in part by the National Key R\&D Program of China [grant number 2019YFC1711000], National Natural Science Foundation of China [grant numbers U1811461, 62072230], Jiangsu Province Science and Technology Research Program [grant number BE2017155], Alibaba Innovative Research Project, and the Program B for outstanding PhD candidate of Nanjing University.

### 2021-03-27 NEUROC/sec2-review-of-graph-neural-network.tex
更新了2.3.4的问题

@@
     %
-    Take the demo GNN in \figurename~\ref{fig:general_structure_of_gnn}(a) as an example.
+    Take the demo GNN in \figurename~\ref{fig:general_structure_of_gnn}a as an example.
     %
@@
 The third and fourth sub-layers aggregate the hidden vectors from the GaAN previous layer with the element-wise max and mean operators separately.
-The vertex updating funciton $\gamma^{l,3}$ of the fourth sub-layer uses the hidden vectors of the last two sub-layers $\MyVec{h}^{l, 1}_x, \MyVec{h}^{l, 2}_x$ to generate the output hidden vector $\MyVec{h}^{l+1}_x$.
+The vertex updating funciton $\gamma^{l,3}$ of the fourth sub-layer uses the hidden vectors of the last three sub-layers $\MyVec{h}^{l, 1}_x, \MyVec{h}^{l, 2}_x, \MyVec{h}^{l, 3}_x$ to generate the output hidden vector $\MyVec{h}^{l+1}_x$.
 
